\setcounter{chapter}{ -1 }
\chapter{\textbf{4th Terminus Timeline} }




This is slightly amended from what we determined during session 11 because some of the \hl{timing just didn't add up correctly.}\footnote{\textbf{Nathaniel Ford }Honestly, timeline is one of the least-engineered parts of this game. If I'd been being good I would have figured out a more reasonable 'IG' roll of events, but alas, it will remain the somewhat hard-to-believe/suspend disbelief parts of the game. \textsubscript{08/10/14 9:56am}}\footnote{$\rightarrow$\textbf{Suko T }I don't mind it at all, I rather like it.  It makes it feel like a movie or tv series :D  Mostly I keep this up because Ion wanted to know how much time had been passing in game (particularly post-Milgram) and I didn't know. \textsubscript{08/11/14 3:32pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I mostly bring it up for any game-external users perusing. \textsubscript{08/11/14 4:47pm}}  Also had to change one time jump in session 9 or the dates really got off.  I got the chronology from the notes, but had to guess a lot, especially when time passage wasn't really spelled out.  Hopefully this is at least close. 



\textbf{?? years ago.} Bucket Skirmish.  Timon becomes Jonah



\textbf{2-3 years ago.}  Session 0. Taking back of DX Station.  Oliver is grievously wounded, Jonah is a medic there, along with Citizen Ogleby (our leader), Fili Judi, and Franchise ???.  



\textbf{Before first session.} Patrol Group is formed.  Jaya, Oliver and Jonah have been with the TA for a while.  Hayley is a raw trainee and has only been part of the TA for about a month and knows next to nothing.



\textbf{Day 1.} Session 1.  Pick up guy from the Bucket, deliver him to what turns out to be SAC-09.

\textbf{Day 8.} Session 1.  After cooling our heels for a while and moving boxes on and off of trains, we get our first big mission and are assigned to retrieve Trenton Hadef from New Station

\textbf{Day 9.} Session 2. Return to SAC-09 with Trenton, Signe and some of his family.  Go on Shore Leave.

\textbf{Day 11.} Session 3. After returning from Shore Leave, Hayley is put in the Tank for the first time and drowns in purple goo..

\textbf{Day 12.} Session 3 \& 4. Mission to Cardoza Station where we have to stop Cyril Magnin.  Oliver gains an archenemy (the Orc of Anglia).  Lackovich nearly dies, along with most of her squad. 

\textbf{Day 16.} Session 5. After a brief cross examination by TA authorities we hang out at SAC-09 and spend a few days recovering from the Cardoza mission. Jaya signs the team up for The Tank.  Everyone goes on Shore Leave.

\textbf{Day 18. }Session 5.  Everyone returns from Shore Leave, lots of talking.  Jonah learns more about the Tank.  Oliver talks with Agent Morgan.  Hayley gets a letter from Signe.

\textbf{Day 19. }Session 6.  Team is sent on mission to GC Station to retrieve info there.

\textbf{Day 20. }Session 6 \& 7. Arrive at GC Station, deal with the Water Rats, find the Shaft, find SAC-01. Get the stuff we need but then things go disastrously wrong and Patrol Group 2 has to rescue us.

\textbf{Day 23.} Session 8. Oliver, Hayley and Jaya wake up in SAC-09, missing memories of the past few days. Jonah is in a coma

\textbf{Day 26.} Session 8. Jaya, Oliver and Hayley head to Terminus to be debriefed by the Security Triumvirate. After returning from Terminus to SAC-09, 3-4 days pass without incident.

\textbf{Day 29.} Session 9.  Jaya is called to Ops and disappears.  She arrives in the Annex and gets her new assignment.

\textbf{Day 33.} Session 9. Another 4 days pass.  Jonah is still in coma, Jaya is still in the Annex, Oliver and Hayley are booooreed.

\textbf{Day 34.} Session 9. Jonah wakes up.

\textbf{Day 35.} Session 9. Oliver has an appt with Dr. Gerhauser to clear him for a 48 hour Shore Leave and establish baseline for tests.  Oliver and Hayley leave for Shore Leave.  Jonah has a smoke with Trenton.

\textbf{Day 36.} Session 11. Jonah has appt with Dr. Gerhauser, gets baseline and leaves for 3 day Shore Leave.

\textbf{Day 37.} Session 10. Oliver and Hayley return from Shore Leave and go into the Tank.  In the Tank, Hayley runs around in a strange place with Tanks.  In the Tank, Oliver seems to go to Nicklepan but doesn't.

\textbf{Day 38.} Session 11. Jonah returns from Shore Leave, well before Jaya returns from her week-long ``special assignment'' (water station job) and 3 day Shore Leave.  They find out that Hayley and Oliver are asleep in Medbay after having gone in the Tank.  Jaya is put in the brig for 24 hours.

\textbf{Day 39.} Session 11. Jaya is released from the brig.  Hayley wakes up and talks with Jonah and Jaya.  Oliver is still sleeping.  Jaya and Jonah get prepped and are put in the Tank.

\textbf{Day 40.} Session 12. Jaya and Jonah go through their first times in the Tank.  In the Tank, Jaya's team is very mean to her.  In the Tank, Jonah has to medic very injured people who keep threatening him.

\textbf{Day 41.} Session 12. Oliver, Jonah and Jaya wake up.  Oliver and Jonah return to their bunk.  Jaya is still in Medbay.

\textbf{Day 42.} Session 13. Morgan gives us a new Rec Room and Jaya gets us extra Shore Leave (even though we just went on Shore Leave 4-5 days ago).

\textbf{Day 43. }Session 14. Everyone goes on Shore Leave.  Hayley talks to Octavia and Gillian.  Oliver goes on a date with Hekate to Ogilby's lakehouse.  Jaya visits her sister.  Jonah gets some old Directorate train station maps.

\textbf{Day 44. }Session 14.  Hayley returns from Shore Leave.

\textbf{Day 45. }Session 14. Jaya returns from Shore Leave in the morning.  Oliver and Jonah return from Shore Leave late in the evening, on the last train.

\textbf{Day 46. }Session 14 \& 15 \& 16.  The team assembles (+Lackovich) and heads out to Nicklepan.  Discover a lot of dead bodies.  Get shot at and bombed a lot.  Bring back a dead soldier and some grave rot.  First mention of VTXs and Tertius (though Jaya reports it as ``Tetris'').

\textbf{Day 49}.  Session 16. Jaya and Hayley are discharged from Medbay, still injured but in stable condition.  Morgan does a debrief and then asks for reports.

\textbf{Day 50-53}.  Session 17.   Team takes a few days to compose/dictate their reports, and then leaves for Shore Leave.  Hayley goes on a date with Tim.  Oliver has a fractious conversation with his father and mentions Agent Morgan and that we found lots of dead bodies in Nicklepan. Jaya finds out that Padme has miscarried a baby girl.  Jonah learns that his sister Riva is dating someone.

\textbf{Day 54}. Session 17.  Jaya returns from Shore Leave.  Hayley gets promoted to full Constable.

\textbf{Day 55}. Session 17, 18 \& 19. Rest of team returns from Shore Leave and the Team completes Competency Tests.  Hayley tortures Jonah on an electric chair.  The team spends the rest of the day recovering. 

\textbf{Day 56}. Session 19. The next day they get their evaluations.  Jonah is silently furious and Hayley is a weepy mess.  They leave on Shore Leave.

\textbf{Day 58}.  Session 20.  Team returns from Shore Leave (some earlier than others).  

\sout{ \textbf{Day 60.} }\sout{   Session 20.  After hanging around for a day (SAC-09 is very busy), Jaya and Hayley are promoted to Agent, Jonah and Oliver are promoted to Operator.  Jaya and Hayley are instrumented for the first time and head out on a mission to rescue Lackovich and possibly kill/capture the Orc.  Oliver goes with (both in Hayley's head and physically), while Jonah stays at SAC-09, just working through Jaya. }

\textbf{Day 60.}  Session 21 \& 22 \& 23.  After hanging around for a day (SAC-09 is very busy), Jaya and Hayley are promoted to Agent.  Jonah and Oliver are promoted to Operator.  Jonah and Oliver go in the Tanks.  Jaya and Hayley are instrumented for the first time.  All four head out on a mission to Borrough Station to retrieve Lackovich and hopefully kill the Orc.  Once there, they all (to varying degrees) have a weird feeling that they've done this before.  Hayley's memories are clearest, while Jaya barely remembers anything.  They proceed with the mission anyway.  There are some scuffles with guys who turn out to be the Orc's constituents.  The Orc turns out to be the third Gerhauser sister.  Oliver fatally stabs the Orc, then falls into one of the portals to somewhere else and we can't get him back.  Lackovich is very wounded after being almost beaten to death by the Orc.  Jonah is able to stabilize her.  Jaya loses half her arm.  Jonah stabilizes her too.  Hayley is hurt but it's mostly narrative.  Jonah is mostly unhurt.  Drones start blowing up the city around Borrough Station, men in brown with guns start appearing.  The populace freaks out.  We barely make it to the Train. Rook picks up Jaya, Jonah, Hayley, Lackovich (yay we succeeded in our mission objective!) and \hl{two extra TA constables}\footnote{\textbf{Suko T }I just realized these must have been Breccan and Morley!  After all, they kinda just... appeared in session 33 nineteen days later.  And we took them with us so they know about our secret base (unless Rook kicked them off the train at the next station). Or am I the only one who missed making that connection? \textsubscript{05/08/15 5:46pm}} and gets the hell out of Dodge.  I mean Borrough Station.

\textbf{Day 61-68.} Session 24.  Arrive back at SAC-09.  Multiple surgeries, lots of conversations.  Morgan is severely wounded on a separate mission with PG2.  Davis is killed and Carruthers is not doing well.  She appears to have picked up his habit of bouncing a rubber ball against the wall.  Jaya finds her sister's place burnt down and brings back Jayce and Douglas to SAC-09. It appears that Oliver is still alive, but we need to find his location.  Everyone works intensely to figure out what is going on and how to find him, except for Jaya who just sleeps with Jayce.

\textbf{Day 69.} Session 25. We find Oliver but aren't able to rescue him.  We get pieces of him, and his memories.  The location is extremely far away.  Oliver dies. So.  Much.  Trauma.

\textbf{Day 70-74.} Session 26. Jaya and Jonah express their displeasure at how the last mission went. Hayley cries a lot and now limps and carries around a rifle with her all the time like a security blanket.  Jonah is very confused.  Jaya takes a lot of drugs and drinks.  We spend several days training with Rook. 

\textbf{Day 75.}  Session 27 \& 28 \& 29 \& 30 \& 31.  Mission briefing for next mission to convince Terminus to resist.  Take train to Terminus, visit with Station Chief Ogleby and Mr. Langdon, with middling to poor success.  Hayley and Jaya speak to Senator Bennett and discover he's Octavius' tool.  He issues an arrest warrant out for Hayley and Jaya (through SC Vargas). Jonah strikes a tentative bargain with Senator Marechenko.  

Agent Lorentz finds us and we chat at TA Agent HQ with him, Agent Vogel and Jaya's new rival, Agent Drake Malak. There's an explosion as the HQ is attacked.  (Session 30) During the explosion we have a weird vision of ``other us'' in someplace else (Washington DC).  We seem to be sort of ourselves but not ourselves.  Just as suddenly we are back at Agent HQ

We help eliminate the threat.  The ladies demonstrate their skillz at killing people, shooting through walls and scissorkicking grenades.  The guys mostly talk a lot.  Jaya retrieves a device that looks like the cylinders we've seen before, but wrapped in fiber optic cables and manages to talk Lorentz into letting us take it back with us.  Drake flirts with Hayley.  Hayley likes it.  We manage to make it back onto the train.  Jonah shows Rook the device Marechenko gave him.  Rook gives Jonah a choice- give Marechenko the real device or a fake one that Rook happened to have with him.  Morgan said Jonah can decide.  Jonah decides on the real one but Rook may have used a bit of sleight of hand to swap them out without Jonah knowing.  We head back to SAC-09 and get debriefed.  Jaya has a terribly misunderstood dinner with Jari and spars with Morgan.  Jonah gets asked to be Signe's Operator.

\textbf{Day 76.}  Session 31.  Hayley talks with Dr. G.  Jonah drinks with Trenton.  Hayley talks to Carruthers. 

\textbf{Day 77-78.}  Session 32.  Team heads out on shore leave.  Jaya tracks down Padme and learns that she'll need to get more money from Morgan to help Padme out.  Jonah goes to the Bucket, reveals his big secret to his family and brings them with him back to SAC-09.   Hayley acts as proxy for Gillian on some legal matters and finds out some dirt on key figures in Terminus and disturbing information about the history behind her scars.

\textbf{Day 79.} Session 33.  Team returns from Shore Leave.  Jaya and Jayce are diagnosed with Grave Rot.  \hl{Hayley attempts to seduce Jonah and gets a rain check.}\footnote{\textbf{Nathaniel Ford }Yeah. This happened. \textsubscript{10/03/14 10:32pm}}\footnote{$\rightarrow$\textbf{Suko T }Perhaps Hayley will ask Jaya for advice on what to try next.  That should go well. \textsubscript{10/04/14 1:07am}}

\textbf{Day 80-85.}  Session 33.  Various futzing around the base.  Jaya goes through withdrawal while she's on the antibiotics for the grave rot and does extra KP so she can send money to Padme.  Jonah visits his family as much as he can.

\textbf{Day 86.} Session 33.  Mission briefing, decide to go to SAC-04.  Jonah decides not to be Hayley's Operator.  Hayley gets new, custom tailored uniforms.  Jaya is a mess (still in withdrawal).  

\textbf{Day 87.} Session 33, 34, 35, 36.  \hl{Hayley gets a hug from Carruthers.}\footnote{\textbf{Nathaniel Ford }Glad this made the summary! \textsubscript{10/03/14 10:33pm}}\footnote{$\rightarrow$\textbf{Suko T }It was definitely note-worthy!  Poor Carruthers.  She shouldn't get too attached to Hayley.  It doesn't seem to end well for those that do.  Gillian...Oliver...Signe... \textsubscript{10/04/14 1:10am}}\footnote{$\rightarrow$\textbf{Suko T }Dammit. See?  Nobody listens to Zathrus.  And Signe's not safe because once Jaya figures things out she'll probably just shoot Signe in the head so that she can get Hayley back... \textsubscript{05/08/15 5:47pm}}  The teams are assembled PG1 and PG2, and we meet up with Drake and Agent Rust's teams on the train and head out to SAC-04.  It's crazy jungle greenery and mountains there and we find a guy pinned to rock who turns out to be The Omen and warns us not to wake Supay.  We find a river and Hayley crosses the bridge and there's a roar that echoes through the mountains.  A mysterious fog chases us up the mountain but through herculean effort Jaya gets most of the group to (relative) safety.  We enter a strange village of people with a creepy whitish film over their eyes.  Javier loses Carruthers as his Operator.

(Session 35) A grenade explodes over Jonah's head and suddenly he is elsewhere, maybe DC, having a meeting with some people in suits and with Riva (older) at his side.  A grenade also explodes near Hayley and she ends up connecting to Carruthers as her new Operator.   

Jonah, Drake, Jayce and Douglas head into SAC-04 while the rest of us fight off the village people/zombies.  Drake becomes Praetor of SAC-04.

\textbf{Day 88.}  Session 36. We go back to SAC-09 to a Code Blue.  Douglas is reunited with Subject Gamma Alpha One and they leave with Jayce.  There is a Code Gold. 
\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 08/09/15 1:12am}
% Exported @ 08/24/15 5:04pm
\end{flushright}

