\setcounter{chapter}{ -1 }
\chapter{\textbf{4th Terminus Timeline} }




This is slightly amended from what we determined during session 11 because some of the \hl{timing just didn't add up correctly.}\footnote{\textbf{Nathaniel Ford }Honestly, timeline is one of the least-engineered parts of this game. If I'd been being good I would have figured out a more reasonable 'IG' roll of events, but alas, it will remain the somewhat hard-to-believe/suspend disbelief parts of the game. \textsubscript{08/10/14 9:56am}}\footnote{$\rightarrow$\textbf{Suko T }I don't mind it at all, I rather like it.  It makes it feel like a movie or tv series :D  Mostly I keep this up because Ion wanted to know how much time had been passing in game (particularly post-Milgram) and I didn't know. \textsubscript{08/11/14 3:32pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I mostly bring it up for any game-external users perusing. \textsubscript{08/11/14 4:47pm}}  Also had to change one time jump in session 9 or the dates really got off.  I got the chronology from the notes, but had to guess a lot, especially when time passage wasn't really spelled out.  Hopefully this is at least close. 



\textbf{?? years ago.} Bucket Skirmish.  Timon becomes Jonah



\textbf{2-3 years ago.}  Session 0. Taking back of DX Station.  Oliver is grievously wounded, Jonah is a medic there, along with Citizen Ogleby (our leader), Fili Judi, and Franchise ???.  



\textbf{Before first session.} Patrol Group is formed.  Jaya, Oliver and Jonah have been with the TA for a while.  Hayley is a raw trainee and has only been part of the TA for about a month and knows next to nothing.



\textbf{Day 1.} Session 1.  Pick up guy from the Bucket, deliver him to what turns out to be SAC-09.

\textbf{Day 8.} Session 1.  After cooling our heels for a while and moving boxes on and off of trains, we get our first big mission and are assigned to retrieve Trenton Hadef from New Station

\textbf{Day 9.} Session 2. Return to SAC-09 with Trenton, Signe and some of his family.  Go on Shore Leave.

\textbf{Day 11.} Session 3. After returning from Shore Leave, Hayley is put in the Tank for the first time and drowns in purple goo..

\textbf{Day 12.} Session 3 \& 4. Mission to Cardoza Station where we have to stop Cyril Magnin.  Oliver gains an archenemy (the Orc of Anglia).  Lackovich nearly dies, along with most of her squad. 

\textbf{Day 16.} Session 5. After a brief cross examination by TA authorities we hang out at SAC-09 and spend a few days recovering from the Cardoza mission. Jaya signs the team up for The Tank.  Everyone goes on Shore Leave.

\textbf{Day 18. }Session 5.  Everyone returns from Shore Leave, lots of talking.  Jonah learns more about the Tank.  Oliver talks with Agent Morgan.  Hayley gets a letter from Signe.

\textbf{Day 19. }Session 6.  Team is sent on mission to GC Station to retrieve info there.

\textbf{Day 20. }Session 6 \& 7. Arrive at GC Station, deal with the Water Rats, find the Shaft, find SAC-01. Get the stuff we need but then things go disastrously wrong and Patrol Group 2 has to rescue us.

\textbf{Day 23.} Session 8. Oliver, Hayley and Jaya wake up in SAC-09, missing memories of the past few days. Jonah is in a coma

\textbf{Day 26.} Session 8. Jaya, Oliver and Hayley head to Terminus to be debriefed by the Security Triumvirate. After returning from Terminus to SAC-09, 3-4 days pass without incident.

\textbf{Day 29.} Session 9.  Jaya is called to Ops and disappears.  She arrives in the Annex and gets her new assignment.

\textbf{Day 33.} Session 9. Another 4 days pass.  Jonah is still in coma, Jaya is still in the Annex, Oliver and Hayley are booooreed.

\textbf{Day 34.} Session 9. Jonah wakes up.

\textbf{Day 35.} Session 9. Oliver has an appt with Dr. Gerhauser to clear him for a 48 hour Shore Leave and establish baseline for tests.  Oliver and Hayley leave for Shore Leave.  Jonah has a smoke with Trenton.

\textbf{Day 36.} Session 11. Jonah has appt with Dr. Gerhauser, gets baseline and leaves for 3 day Shore Leave.

\textbf{Day 37.} Session 10. Oliver and Hayley return from Shore Leave and go into the Tank.  In the Tank, Hayley runs around in a strange place with Tanks.  In the Tank, Oliver seems to go to Nicklepan but doesn't.

\textbf{Day 38.} Session 11. Jonah returns from Shore Leave, well before Jaya returns from her week-long ``special assignment'' (water station job) and 3 day Shore Leave.  They find out that Hayley and Oliver are asleep in Medbay after having gone in the Tank.  Jaya is put in the brig for 24 hours.

\textbf{Day 39.} Session 11. Jaya is released from the brig.  Hayley wakes up and talks with Jonah and Jaya.  Oliver is still sleeping.  Jaya and Jonah get prepped and are put in the Tank.

\textbf{Day 40.} Session 12. Jaya and Jonah go through their first times in the Tank.  In the Tank, Jaya's team is very mean to her.  In the Tank, Jonah has to medic very injured people who keep threatening him.

\textbf{Day 41.} Session 12. Oliver, Jonah and Jaya wake up.  Oliver and Jonah return to their bunk.  Jaya is still in Medbay.

\textbf{Day 42.} Session 13. Morgan gives us a new Rec Room and Jaya gets us extra Shore Leave (even though we just went on Shore Leave 4-5 days ago).

\textbf{Day 43. }Session 14. Everyone goes on Shore Leave.  Hayley talks to Octavia and Gillian.  Oliver goes on a date with Hekate to Ogilby's lakehouse.  Jaya visits her sister.  Jonah gets some old Directorate train station maps.

\textbf{Day 44. }Session 14.  Hayley returns from Shore Leave.

\textbf{Day 45. }Session 14. Jaya returns from Shore Leave in the morning.  Oliver and Jonah return from Shore Leave late in the evening, on the last train.

\textbf{Day 46. }Session 14 \& 15 \& 16.  The team assembles (+Lackovich) and heads out to Nicklepan.  Discover a lot of dead bodies.  Get shot at and bombed a lot.  Bring back a dead soldier and some grave rot.  First mention of VTXs and Tertius (though Jaya reports it as ``Tetris'').

\textbf{Day 49}.  Session 16. Jaya and Hayley are discharged from Medbay, still injured but in stable condition.  Morgan does a debrief and then asks for reports.

\textbf{Day 50-53}.  Session 17.   Team takes a few days to compose/dictate their reports, and then leaves for Shore Leave.  Hayley goes on a date with Tim.  Oliver has a fractious conversation with his father and mentions Agent Morgan and that we found lots of dead bodies in Nicklepan. Jaya finds out that Padme has miscarried a baby girl.  Jonah learns that his sister Riva is dating someone.

\textbf{Day 54}. Session 17.  Jaya returns from Shore Leave.  Hayley gets promoted to full Constable.

\textbf{Day 55}. Session 17, 18 \& 19. Rest of team returns from Shore Leave and the Team completes Competency Tests.  Hayley tortures Jonah on an electric chair.  The team spends the rest of the day recovering. 

\textbf{Day 56}. Session 19. The next day they get their evaluations.  Jonah is silently furious and Hayley is a weepy mess.  They leave on Shore Leave.

\textbf{Day 58}.  Session 20.  Team returns from Shore Leave (some earlier than others).  

\sout{ \textbf{Day 60.} }\sout{   Session 20.  After hanging around for a day (SAC-09 is very busy), Jaya and Hayley are promoted to Agent, Jonah and Oliver are promoted to Operator.  Jaya and Hayley are instrumented for the first time and head out on a mission to rescue Lackovich and possibly kill/capture the Orc.  Oliver goes with (both in Hayley's head and physically), while Jonah stays at SAC-09, just working through Jaya. }

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 08/09/15 1:12am}
% Exported @ 08/24/15 5:04pm
\end{flushright}

