\setcounter{chapter}{ 0 }
\chapter{\textbf{SAC-09, Intro} }

\subChapterTitle{``PG1 Assemble!''}


\deets{\hl{Missing}\footnote{\textbf{Rebecca S. }These notes were hand written. They have never been recovered. \textsubscript{08/21/15 9:20am}}}{June 7th, 2012}

\textit{\hl{The days pass with a regular, lightless rhythm.}}\footnote{\textbf{Suko T }From first session email 6/6/12
``(4T) Book One: Departure, Episode One: New Station'' \textsubscript{08/25/15 3:39pm}}\textit{ Mess happens like clockwork, PT twice a day on the stretch of concrete called the 'Ready Line'. Sometimes, Morgan watches from the catwalks above where her disgust is hidden in shadow. Tiburon shows you how to fill out the paperwork for the requisition cage and Jari slips Jaya some playing cards one night with her meal. The rest of the days are bounded by the dull grey walls of the barracks, and the faces of your team. Tomorrow, though, Tiburon says to be ready. Tomorrow you're going to New Station. Briefing is at oh-six hundred. Pre-ops to be complete by oh-eight hundred. What the hell are pre-ops?}

The team (Jaya, Oliver and Jonah) rolls out on what was thought to be a normal mission with their new squadmate, Hayley (who appears to be very poorly trained, if at all). That mission turns out to be collecting Victor from a bar located in the Bucket. We bring him in and then find out that we're to take him somewhere else... that turns out to be SAC-09.  We are officially brought into SAC-09 and meet the base personnel for the first time, Morgan, Rook, Jari and the doctor.

 \vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 08/25/15 3:41pm}
% Exported @ 08/26/15 9:13am
\end{flushright}
