\setcounter{chapter}{ 11 }
\chapter{\textbf{The Tank, Part 2} }






\textit{Notes:} Suko

\textit{Date:} December 6th, 2012



Wherein Jaya's squad is very mean to her and she does a lot of \hl{``strategic regrouping''}\footnote{\textbf{Suko T }Brave Brave Sir Jaya! \textsubscript{12/07/12 11:18pm}}.  Also, Jonah almost gets blown up at least three times.  Yay for Tank Time!



As always, please fill in the gaps and correct errors.  Also you should always feel free to add/correct the perspective of your character.



\noindent\hrulefill





 {\LARGE THE TANK } 


\jumpHeadline{THE TANK: Jonah }

The liquid in the tank does not feel like water. \hl{For perhaps the first time in his life}\footnote{\textbf{Suko T }My assumption \textsubscript{12/07/12 3:13pm}}\footnote{$\rightarrow$\textbf{q.google }I think that's correct.  I definitely don't think he could wrap his head around the idea that Oliver was \_actually\_ swimming. \textsubscript{12/07/12 11:34pm}}, Jonah is completely submerged in liquid.  Even though he is wearing the mask, it is hard not to freak out a little, especially as he can vaguely see Dr. Gerhauser and Technician Swan watching him through the walls of the tank.  



He can feel the drugs spreading through his system, and he closes his eyes, intending on taking a deep breath before the drowning begins -- but when he opens his eyes, he is somewhere else.  



Jonah is in a small room with crumbling walls.  There is an overpowering smell of dried blood in the air, and underneath that, the acrid stench of urine and putrid wounds.  He is wearing street medic clothes, and is carrying his old medic bag.  There is no sign of any goo anywhere.  Outside the window, he can see the flickering lights of fire.  Inside the room, there is a man, leaning up against a wall, and two people lying in bedrolls on the floor, looking like they have been treated recently.



\textit{{[}Trace: 4 Threat Tokens enter the pool{]}}



Jonah does a quick check, and realizes he is unhurt but feels a little groggy.  He quickly establishes where the exit to the room is.  He can hear yelling outside, but there are no explosions and he feels a sense of relief when he realizes this.  He walks over to the patients on the floor.



One of the patients is a young man/boy, barely 17 years old, if that.  He looks terrible, bundled up, with a unhealthy pallor to his skin, unfocused eyes, and a troubling hacking cough.  The other patient is an older woman, covered up neatly with a blanket from the shoulders down.  She looks \hl{uninjured}\footnote{\textbf{Suko T }In my head I gave her crushed legs/pelvis and probable spinal injury.  Lack of incapacitating pain was damaged nerve pathways \textsubscript{12/07/12 3:15pm}}\footnote{$\rightarrow$\textbf{q.google }Ah!  As far as Jonah could tell she was likely injured but not that injured: her complaints were those of someone who was scared not of someone who was dying.  (Notably he didn't check though.) \textsubscript{12/07/12 11:37pm}}\footnote{$\rightarrow$\textbf{Suko T }That's how I was hoping it to go, although my vague plan was to have you dismiss it and then be horribly wrong.  Maybe next time! :D \textsubscript{12/08/12 11:40pm}} and watches Jonah's approach with alert eyes.



Without rising, she puts out a hand and says, ``Do you have it?'' and insists that Jonah had promised her something (presumably for the pain).  The boy coughs and Jonah goes over to him to evaluate him. He has a terrible abdominal wound and his bandages are soaked through.  The boy's shirt is made of some odd plastic material that Jonah has never seen before, but the rest of his outfit is made of regular canvas. The boy's name is Bryan.



Jonah looks up at the man who is standing.  He appears uninjured and is dressed like Jonah, with a Street Medic bag.  The other man asks Jonah if they can go yet.  He seems irritated that Jonah is checking the two injured people out, saying they've already been looked at.  When Jonah challenges him about it, asking what his diagnosis is, the other man tersely says that they don't have time for this.  \hl{Jonah insists that the man's bandages need changing}\footnote{\textbf{q.google }What's going on is that he's just trying to get oriented.  Leaving people injured is probably a bad idea regardless of where he is.  Even though he's getting the idea this might be a war zone. \textsubscript{12/07/12 11:44pm}}, because they haven't been changed and are infected.  The other man, angrier now, asks why he needs to check them \textit{again} and insists there isn't time.



\textit{{[}Challenge: Get the other medic to stay until the injured man is re-bandanged 2{]}}.  Jonah re-bandages Bryan's wounds and then tells the other medic they are ready to go.  The two Street Medics start walking toward the door, when there is a click of a gun behind them.  They both instinctively duck and roll out of the way.  The woman is still prone but has lifted up her head enough to aim the gun she is holding at them.  She demands that they stay.  ``No, I'm not going to let you go. It's an order!  If you don't stay, I \textit{will} shoot you.  Don't you know who I am?'' she says desperately.



The other medic murmurs to Jonah, ``You know they're both dead anyway, right?''

``Well, she might not, but \textit{he} is,'' says Jonah to Bryan's dismay.



Meanwhile, the shouting outside is getting louder.



\textit{{[}Challenge: Convince the woman to let them leave 2{]}} Jonah convinces the woman that the best chance of her recovery is for him to get out there and get her better medicine.  She eventually believes him and lowers the gun, but insists that he \textit{is} coming back.



Out in the street there are several bodies. One of them is in riot gear, his body twisted in unnatural angles.  The area looks like the Bucket, and (unfortunately) smells like it too. Jonah feels awake but things are a little off.  He feels a little distant from everything.  A bit ``numb around the edges.''



\textit{{[}Nominal enters the pool.  8 threat tokens{]}}



Jonah realizes that he has left some of his Medkit supplies back in the room with Bryan and the woman \textit{{[}Refresh: Street Medic{]}. }  The other medic is extremely angry, telling him that they are in an extremely dangerous situation and can't be losing track of their medicine.  He attempts to find out if the other medic has enough supplies.  The other man seems to takes this a request for to trade for supplies and asks what Jonah's got.  Jonah, irritated, though unsure whether at the other man or at himself tells him he doesn't need anything he just doesn't want to leave the two of them undersupplied.  The other man insists on a trade.  \textit{{[}Challenge: Find out his companion's inventory and get access to it 2{]}}.  After promising to replenish the other medic's supplies with \hl{an IOU}\footnote{\textbf{Rebecca S. }so adorable! \textsubscript{12/07/12 11:40pm}}, Jonah gets a few hypos of morphine (the type he's more used to seeing at SAC-09 than on the street).



They make their way down the street.  The other medic is making himself obvious, flashing his bag with the big medic insignia on it.  He's not foolishly walking into danger, but he's not being as cautious as Jonah would like either.  After a bit of exploring, the other medic says that ``We might be hemmed in on all sides, we have to head back.''  



The fact that he can't remember who this guy is, despite the guy's familiar demeanor, starts to bother Jonah \textit{{[}Challenge: Do I recognized him? 2{]}}.  He's also frustrated that the other man doesn't seem to know where they are going and won't tell him.  Jonah shoves away that concern as he tries to keep them from being too exposed or out in the open.  This only seems to annoy the other medic, who starts accusing Jonah of ``mothering him'' and begins behaving \hl{increasingly recklessly}\footnote{\textbf{q.google }Honestly, no discipline at all.  He's going to get them both killed.  Killed I tell you! \textsubscript{12/07/12 11:52pm}}.



\textit{{[}Challenge: Where do you live? 1{]}} Jonah tries to remember where he lives but gets distracted when there's a whistling noise and the sound of metal bouncing off of rocks, followed by a ``pop.''

\textit{{[}Challenge: Notice Bomb 2{]}} Jonah dives through a window, avoiding the explosion but losing track of the other medic in the process. \textit{{[}Refresh: Vigilant{]}. }



Jonah finds himself in another small room with two wounded people in the floor.  There is a grizzled old man in uniform with three stars on his collar \textit{{[}Challenge: What do the three stars mean? 1{]}}.  He appears to be wounded and and has a bandage over one eye.  The other person is a young woman, who is bundled up in blankets and appears to be shivering intensely.  ``You came back!'' she stutters.



``Come over here Corpsman and change these bandages!'' orders the old man.  When Jonah is reluctant, even a little belligerent \textit{{[}Refresh: Social Chameleon{]}, }the old man says he's Jonah's commanding officer.  ``Oh yeah, then what's my name?'' challenges Jonah.  ``I don't need to tell you your name,'' says the old man.  ``All you need to know is I'm your commanding officer!''.  Jonah refuses the order, unclear on where he is or what is happening, but extremely annoyed at being pushed around.  He tells the old man that he's not his commanding officer, and demands to know what authority he has.  The old man responds by telling him he has all the authority right here, and pulls out a grenade.



\textit{{[}Challenge: Avoid blast 3{]}} Jonah dives out the door and avoids getting blown up.  Right before the room explodes, Jonah thinks he can hear the woman's voice cry out, ``Jonah, no!''  Except that it's not the woman's voice, it's his sister, Riva.



Jonah wanders the streets in a daze \textit{{[}Refresh: Streetwise{]}. }Eventually he comes across a street where at the end of it, he can see a group of people in riot gear, beating up some other people.  They are being pretty brutal about it.  Between them and Jonah, midway down the street, Jonah can see the other medic, who is lying on the ground, clutching his side in pain.  Jonah walks out into the street, in plain view and goes to the other medic \textit{{[}Refresh: Conceal{]}. }The Bro Squad at the end of the street spot him and yell ``Hey there's another one!''  Jonah shows them his bag with the medic symbol on it and they jeer, ``Oh another one trying that trick, eh?''.  Jonah denies it loudly, telling them he has no weapons.  The other medic yells at him to get out of the way, ``The medic bag isn't protection anymore!  They shot me!''



Jonah sees that the other medic has been shot in the abdomen and helps him to his feet.  The Bro Squad yell, ``Hey they're trying to get away!'' and turn toward them.  \textit{{[}}\textit{\hl{Challenge: Escape Bro Team Alpha 2}}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{12/07/12 11:44pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }\textless 3 \textsubscript{01/22/13 9:44pm}}\textit{{]}}  Jonah successfully gets himself and his injured companion away from them and hides out in a small room.  There's a pile of rags in the room.  



Jonah attempts to treat the guy's injuries \textit{{[}Challenge: Fix the guy 2{]}}.  As he treats him, Jonah asks him to keep talking and stay conscious, that what he's going to ask is a little strange but he needs him to keep talking.  He asks him to tell Jonah something about himself and say what he knows about Jonah.  The guy starts taunting Jonah that he knows what Jonah really wants.  ``I don't know what you have that I want,'' says Jonah. The guy laughs somewhat bitterly and pulls down the collar of his shirt \hl{to show him his barcode tattoo}\footnote{\textbf{q.google }That's the point at which it's clear, OOG, who he is supposed to be. \textsubscript{12/07/12 11:56pm}}.



There's another whistling sound and the plink of a metal object hitting rocks (or a wall).  \textit{{[}Challenge: Avoid being blown up 2{]}}.  Jonah ducks for cover but is getting a little paranoid about things falling out of the sky (and exploding) on him.  He is uninjured from the explosion but is deafened. 



The other guy is alive and laughing maniacally now.  Jonah can see that the skin around the barcode is bruised and starting to bleed.  The other guy reaches into his bag and pulls out a pair of scissors.  Jonah yells at the guy to keep talking, especially now since he can't hear him anyway and takes the scissors away from him.  He demands for the injured man to say his name again  \textit{{[}Challenge: Tell me your name 2{]}}.



The other man mouths a name that looks like he says Jonah Gemayel, and Jonah can see that he looks like the original Jonah.  But oddly, even though he is deafened, Jonah can hear the man very clearly say the name ``\hl{Trevor Gunn}\footnote{\textbf{Suko T }Jonah never followed up on this, did he? \textsubscript{12/05/14 4:52pm}}``.



The same voice says, ``Look out behind you!''  Jonah turns, there is a flash of light and in that space between, he decides to return rather than continue.



\textit{\textbf{{[}0 tokens left on Nominal for Jonah, hasn't started Solid yet{]}}}


\jumpHeadline{THE TANK: Jaya }

Because of Jaya's drug tolerance, it takes a while for her to conk out.  She spends most of the time making awkward eye contact with Dr. Gerhauser and Swan and anyone else staring at her in the Tank.  But then she blinks and she's walking into a bar.



\textit{{[}Trace enters the pool.  4 threat tokens{]}}

{[}{\color[RGB]{17,85,204} \hl{Queue epic soundtrack for Jaya's tank scene} }{]}\footnote{\textbf{Suko T }Sweet!  Saiorse was so amazing in that movie. \textsubscript{12/08/12 12:05am}}



Jaya's dressed in clean street clothes.  They're new and she's feeling rather good about herself.  She saunters in and up to the bar and orders a drink, only to realize that she's sitting in between Oliver and Jonah.  Jaya slams the drink back, says she's off duty and attempts to walk away.



Oliver and Jonah say that she asked them to meet her there and accuse her of being late while Jonah orders another round for her.  Jaya asks about Hayley and is told that Hayley had been ``injured due to Jaya's incompetence'' and may never walk again.  Both of them are being quite aggressively mean and provocative.



Jaya becomes agitated at their odd behavior and declares she's going to her sister's and orders them to leave her alone.  Oliver tells her that she's not in charge anymore and Jonah mockingly calls her ``Chief'' and uses airquotes.  Jaya starts to get in Oliver's face but her wrath is diverted at the last second by the evil that is air quotes so she grabs and smashes a mug from the bar onto Jonah's head.  \textit{{[}Challenge: Knock Jonah out 2{]}}  Jonah goes sprawling to the ground.



The bartender, Bishop, comes out from behind the bar and tells Jaya, ``You should apologize.''  Jaya refuses, the bird is possibly flipped, and she starts walking for the door.  Oliver grabs her by her spiffy new shirt collar and says sternly, ``You're not going anywhere, Junior Constable.''



\textit{{[}Challenge: Break hold 2{]}} Jaya turns and snarls in Oliver's face, managing to slip his grip.  Rather then press the issue, she turns and darts out the door.  She hurries down the street and starts crying.  Her fate is distressing but not entirely inconceivable to her at this point.   \textit{{[}Refresh: Grim Visage{]}}.  \textit{{[}Challenge: Avoid sister seeing her like this 1{]}} She sees her sister through the window and manages to pull her shit together before her sister sees her tears.



Inside the tattoo parlor, Jaya is delighted to find Hayley getting a pretty sweet tribal tattoo on her shoulder and neck.  Hayley's legs appear to be fine, despite what Oliver said earlier and the discontinuity is quickly forgotten. Jaya's pleased about the tattoo but Hayley starts whining about it and how Jaya made her do it, even though she knew that Hayley didn't want to look like ``low class scum.''  Jaya lets that one slide by and starts talking about how cool the tattoos make her look.  Hayley says that they look terrible and people are always laughing at Jaya behind her back.



Padme nods in agreement and \hl{starts needling Jaya about how only suckers get tattoos.}\footnote{\textbf{Suko T }Thanks for adding all this detail, the whole section but this paragraph and the later one with the letter in particular.  It's really cool to see Jaya's vulnerabilities like this. \textsubscript{12/08/12 11:32pm}} She's just in the business for the money and tattoos are unquestionably lame.  Padme then gives Jaya shit about how she doesn't have kids, the real source of money and usefulness, of which Padme's had 6, almost 7 at this point.  She says that even Hayley would be more successful at that then Jaya.  Heated words are exchanged and it's heavily implied that Jaya is a weakling and unable to back up what she's been saying.  To drive this point home, Padme suckerpunches Jaya in the face.  \textit{{[}Challenge: Punch sister in the nose 2{]}} \textit{ }Jaya punches Padme in the nose.  Padme gets up and takes off her shirt, wearing just a military tanktop underneath and the two sisters start spoiling for a fight.  Hayley offers to fight Padme for Jaya, saying nastily that's what she usually does for Jaya, but Jaya cannot be distracted from this fight.



Jaya reaches for her sidearm, and somehow, it's there.   She doesn't pull it from the holster, but she realizes that Padme has the advantage in this fight.  Several gut punches really drive the point home.  \textit{{[}Challenge: Headbutt Padme 2{]}}  Jaya's not going out like a pansy though and rushes Padme, headbutting her right in the nose again.  Her sister goes reeling, gushing blood, knocks into an inking station and goes down. 



Hayley gets up off the tattoo table and \hl{something falls out of her pocket}\footnote{\textbf{Adam Kenney }Huh.  What was it? \textsubscript{12/08/12 7:17am}}\footnote{$\rightarrow$\textbf{Suko T }I'm guessing it may have been the letter that shows up later?  Nate mentioned it but we never followed up on it so it's in my notes but nothing more. \textsubscript{12/08/12 11:29pm}}. Hayley goes to restrain Jaya, saying in a surprised tone that this isn't like her to be fighting like this.  Jaya flails around ineffectually \textit{{[}Refresh: Adrenaline Junkie{]} }freaking out \hl{but unwilling to lash out at Hayley quite yet.}\footnote{\textbf{Suko T }Aww, Jaya's such a softie inside :) \textsubscript{12/08/12 11:28pm}}



At this moment, Oliver, Jonah and Morgan walk in.  Stunned, Jaya attempts to salute Morgan. ``Agent!  Sir. Ma'am.''  Truly at wits end she asks \hl{``Are you here to get some ink?''}\footnote{\textbf{Adam Kenney }Hahahaha! \textsubscript{12/08/12 7:18am}}



``She's worse than we thought,'' says Jonah, looking at Jaya disdainfully.  Jaya shoots back that this is a domestic dispute and that everyone who isn't her sister needs to leave.   No one budges.  The SAC-9 people begin to advance on Jaya, talking about how crazy \textit{she's} behaving and Jaya takes this as a cue to get the hell out.  She starts towards the back door. 



Morgan strides up and grabs Jaya's arm.  ``Fucking let go, you bitch!'' snarls Jaya \textit{{[}Challenge: Get Morgan to let her go 2{]}} as she pulls her gun, forcing Morgan back up.  Jaya raises up her sidearm and continues backing away.  She can see Oliver's rifle snapping up in response- never mind how he had been concealing it.  



\textit{{[}Challenge: Avoid getting shot by Oliver 3{]}} The terror of knowing how easily Oliver can kill with that rifle spurs Jaya to drug-fueled action and she manages to duck out of the way through the back door and flees.  There's a moment of dissociation but Jaya pushes onward.



\textit{{[}Solid enters the pool.  12 threat tokens added{]}}



Jaya heads for one of the drug dens she knows about.  It should be reasonably secure and off of Morgan's radar (she hopes).  Once she gets inside, Jaya immediately starts looking for a weapon \textit{{[}Refresh: Truncheon{]}}, not paying much attention to anyone or anything else in the drug den.  She manages to find a blackjack but when she yanks it out of some guy's hand, he protests and sits up.  It's Jayce.



Jayce demands that she return the weapon and begins berating her for the abuse he suffered at her hands.  Jaya ineffectually tries to throw her weight around \textit{{[}Refresh: Senior Constable{]} }only managing to piss off another patron, whom she literally smacks down with the blackjack.



Jayce is still angry and tries to get his blackjack back.  Threats in all directions are exchanged.

``You need to calm down!'' demands Jaya.  

``Calm down?  Calm down??  You probably killed that guy!'' says Jayce.

``Er, he was like that before,'' says Jaya a little sheepishly.

``You just attack people for no reason!''



\textit{{[}Challenge: Don't feel bad about what she did to Jayce 2{]}} Jaya gets a grip and wields her TA authority more effectively.  ``It wasn't 'no reason'.  I had a job to do and I did it.  I was protecting my team from what I perceived to be a threat at that time.''



Jaya dramatically rips her sleeve a to reveal her ``Nobody Fucks With the TA'' tattoo, although it now looks childish and badly done.  Jaya feels foolish \textit{{[}Refresh: Grim Visage{]} }and attempts to tuck her torn sleeve back up. 



Overcome with distress, Jaya decides what she needs now to make everything better are some good old drugs.    She scrounges around the drug den, ignoring a knock on the door, and attempting to replenish her stash \textit{{[}Refresh: Stash{]}.  }A cigarette is offered, which she hastily accepts, and slowly realizes was produced by Jonah, whom she didn't even notice walking in.  She slumps against a wall and starts blubbering a little as she hits bottom \textit{{[}Refresh: Adrenaline Junkie{]}}.  The cigarette is lit and her situation is not improved.   



Jayce pulls a crumpled piece of paper out of his pocket.  Jaya notices and cheers up a little.  She tries to grab the paper, saying it's hers and it shows how awesome she is.



Jonah gets the paper and reads it.  It's a letter of reprimand for Jaya- citing her many egregious acts outside of the code of the Directorate.  She is discharged dishonorably, without pay and without pension.



After reading it herself, Jaya numbly holds her cigarette to it and lets it burn.  \hl{Jayce taunts her about the letter and her fate for which Jaya tries to get rid of him \textit{{[}Challenge: Bully Jace 3{]}}.}\footnote{\textbf{Rebecca S. }Oh Jayce... there's no way he's not coming back again, right?  .... right?
....
right?? \textsubscript{11/17/14 5:58pm}} She hits him in the tummy, yanks his head head up by a fistfull of hair, and snarls ``Fuck off'' as she tosses him out of the den.  Jaya attempts to talk Jonah into helping her out, perhaps letting her stay at his place while she cleans up her act, but he says ``not again'' and that Oliver wouldn't be very happy with that.  As if things couldn't get much worse, it is at this point that both Oliver and Morgan walk through the door.  



Jaya notices that her clothing is ragged and filthy, covered in dried vomit and other disgusting things.  She remembers when they were new and awesome looking \textit{{[}Challenge: Ignore shitty state of clothes 2{]}}.  Luckily her drug-addled state makes her not care- it's not like this hasn't happened before. 



The gang continues to give her shit, including Haley who has somehow shown up.  It is implied that she's to be thrown back in the brig.  It all proves too much for Jaya who attempts to lash out at \hl{Jonah}\footnote{\textbf{Rebecca S. }was it Jonah or Oliver? \textsubscript{12/08/12 12:59am}}\footnote{$\rightarrow$\textbf{Suko T }I thought it was Jonah due to him being nearer to her at the time after offering her a cigarette, but it's possible it was Oliver.  I suppose either is better than it being Morgan :) \textsubscript{12/08/12 1:18am}}\footnote{$\rightarrow$\textbf{Adam Kenney }Yes, it was Jonah. \textsubscript{12/08/12 7:20am}} and she takes a wild swing at him with the blackjack. \textit{{[}Refresh: Truncheon{]} } This completely fails and is made worse by Jonah easily stepping aside and smacking her as she stumbles past.  \textit{{[}Challenge: Avoid going down like a bitch 3{]}}.  Her sense of authority drains out of her and she sits there \textit{{[}Refresh: Senior Constable{]} }until she is dragged to her feet by Oliver who restrains her wrists behind her back.  Jonah comes at her with a scalpel saying she needs to have her tattoos removed or.. \hl{something else.}\footnote{\textbf{Rebecca S. }.... die? \textsubscript{12/08/12 12:59am}}\footnote{$\rightarrow$\textbf{q.google }No, Mr. Bond, I expect you to... \textsubscript{01/27/13 2:16am}}  Neither option is acceptable to Jaya who flails about in vain... and eventually blacks out.



\textit{\textbf{{[}8 tokens left on Solid for Jaya{]}}}



 {\LARGE SAC-09 } 


\jumpHeadline{Jaya and Jonah }

Jaya wakes up in Medbay feeling very weak.  She rolls out of the bed and falls onto the floor, ripping out her IV.  The huge crash and thud wakes up Jonah who is in the next bed over.



Swan walks in and asks what all the noise was about. Jaya is a little incoherent and wild-eyed, so he injects her with a sedative and puts her back on the bed.



``Where are we?'' Jonah asks Swan.

``SAC-09.''

``What's your name?''

``Do you not remember my name?'' says Swan with some surprise. ``I'm Technician Swan.''

``No I just want to make sure. Could I get a stimulant?  A mild one?''

``I'll have to go ask Dr. Gerhauser.''



Swan leaves and returns with a mild stimulant and leaves.  With no one watching, Jonah cries silently.



Late in the afternoon the next day, Dr. Gerhauser comes by and says Jonah seems recovered enough to return to his bunk.



Jaya wakes up and asks Dr. Gerhauser, ``Is this real life?  Am I awake?''

Assured that everything is ok, Jaya launches into a rant about how she has had some bad drug trips before but this one was by far the worse.  She seems angry and confused as to why she had to endure such a shitty trip.  

``Your reaction is unusually orthogonal,'' says Dr. Gerhauser.

Jaya cracks a joke about Jonah's brain activity (or lack thereof) but she's the only one who laughs.



Jaya demands to see her squad.  She tries to order Dr. Gerhauser to summon her team.



``Do you understand the chain of command?'' asks Dr. Gerhauser.

``Yes.  I'm a Senior Constable...right?'' states Jaya, ending on a note of uncertainty as her eyes dart around the room.

``True,'' acknowledges Dr. Gerhauser to Jaya's obvious relief. Dr. Gerhauser continues in a musing tone, almost to herself.  ``I often wonder what rank I am.''  Jaya hurries to assure her that she has the utmost respect for doctors.  



Dr. Gerhauser says that she will ask if Jaya's team will come down and see Jaya, but she won't order them to do so.


\jumpHeadline{Oliver and Hayley (and later Jonah) }

Oliver wakes up and returns to his bunk.  Hayley is there and she greets him with a smile.  ``Welcome back!  I changed your bed, it was....soggy.''

``What happened?''

``I don't want to know.''

Oliver shakes his head and lets it pass.

``Did you do the experiment?'' he asks.

``Yes.  I got further this time.  But I still failed.'' pouts Hayley.  ``How did you do?  Did you win?'' she asks eagerly.

``What do you mean?''

``Oh, uh, um, did you get to the end?  Oh I mean, I guess there isn't an end.  So I don't know how we win.'' babbles Hayley unhelpfully.



Oliver tells Hayley that from now on he's going to swim by himself.  Hayley does not seem saddened by this, and cheerfully thanks him for his help in teaching her to swim. ``It was helpful!''



Jonah walks in.  Hayley lights up, ``You're back!''



Jonah says nothing and walks to his bunk and lies down.  Hayley trails after him, asking if there are things she can do for him.  She asks how it was for him.  He doesn't say much of anything.  Oliver eventually tells Hayley that perhaps they should leave Jonah alone for a while and let him rest.  Hayley looks disappointed but she stops interrogating him.  She pulls up a chair and settles in with the ease of someone used to sitting in a chair for hours.  



Tiburon knocks on the door. Oliver answers the door but only opens the door slightly, blocking the view of the room with his body.  Tiburon tells him that Jaya has requested to see them, but that it is not an order they must obey.  Oliver thanks him and shuts the door.  Hayley asks what Agent Rook wanted, and \hl{Oliver says it was nothing}\footnote{\textbf{Suko T }Poor Jaya!  We're going to have to be extra special nice to her next session :) \textsubscript{12/07/12 10:47pm}} and goes to bed.



Hayley stays awake all night, sitting the chair, \hl{just watching over them.}\footnote{\textbf{Suko T }It's definitely weird and probably a little creepy if you are particularly sensitive to such things. 

She's not staring at him like a stalker though.  She doesn't even directly look at him that often, although he's always in her peripheral vision.  Her body language is set to ``watchful guardian/bodyguard'' mode. She has an air of meditative stillness and professionalism that I suppose it could even be reassuring if you are reassured by such a thing. \textsubscript{12/07/12 6:28pm}}  She doesn't read or play a game, she just sits there, like she's meditating but with her eyes wide open and alert to any movements.  Jonah doesn't sleep but they don't speak, other than Hayley's occasional offer to get him food or water when he stirs.



Midway through the night, they can hear Oliver tossing and turning as his sleep is troubled.  Hayley re-angles her chair so she can watch over them both.





\underline{  {\LARGE Challenges \& Refreshes }  }



\begin{itemize}
\item Challenge: Get the other medic to stay until the injured man is rebandaged 2.  Street Medic 2 (Jonah) → Matched
\item Challenge: Convince the woman to let them leave 2.  Social Chameleon 3 → Overcome! \textbf{2 VP (Jonah)}
\item Refresh: Street Medic (Jonah)
\item Challenge: Find out his companion's inventory and get access to it 2. Business Contacts 2 (Jonah) → Matched
\item Challenge: Do I recognized him? 2.  Concealment 1 (Jonah) → Sent back to pool
\item Challenge: Where do you live? 1. → Sent back to pool
\item Challenge: Notice Bomb 2. Vigilant 3 → Overcome! \textbf{2 VP (Jonah)}
\item Refresh: Vigilant (Jonah)
\item Challenge: What do the three stars mean? 1. → Sent back to pool
\item Refresh: Social Chameleon (Jonah)
\item Challenge: Avoid blast 3. Vigilant 3 (Jonah) + Streetwise 1 (Jonah) + Small Unit Tactics 2 (Jonah) + \textbf{ {\color[RGB]{255,0,0}Flaw: } }\textbf{ {\color[RGB]{255,0,0}\hl{Haunted}} }\footnote{\textbf{Suko T }this comes up most when you are not well rested \textsubscript{12/07/12 10:59pm}}\textbf{ {\color[RGB]{255,0,0} 1{[}0{]}} } → Overcome! \textbf{3 VP (Jonah)}
\item Refresh: Streetwise (Jonah)
\item Refresh: Concealment (Jonah)
\item Challenge: Escape Bro Team Alpha 2. Concealment 1 (Jonah) + Streetwise 1 (Jonah) → Matched
\item Challenge: Fix the guy 2.  Street Medic 2 (Jonah) → Matched
\item Challenge: Avoid being blown up 2. \textbf{ {\color[RGB]{255,0,0}Flaw: Fear of falling objects 1{[}0{]}} } → Sent back to pool
\item Challenge: Tell me your name 2. Social Chameleon 3 → Overcome! \textbf{2 VP (Jonah)}
\item Challenge: Knock Jonah out 2. Truncheon 2 (Jaya) → Matched
\item Challenge: Break hold 2. Grim Visage 2 (Jaya) → Matched
\item Refresh: Grim Visage (Jaya)
\item Challenge: Avoid sister seeing her like this 1. Air of Command 1 (Jaya) → Matched
\item Challenge: Punch sister in the nose 2.  Adrenaline Junkie 2 (Jaya) → Matched
\item Challenge: Headbutt Padme 2. Grim Visage 2 (Jaya) → Matched
\item Refresh: Adrenaline Junkie (Jaya)
\item Challenge: Get Morgan to let her go 2.  Intimidate 3 (Jaya) → Overcome! \textbf{2 VP (Jaya)}
\item Challenge: Avoid getting shot by Oliver 3. Adrenaline Junkie 2 (Jaya) + Stash 2 (Jaya) → Matched
\item Refresh: Truncheon (Jaya)
\item Refresh: Senior Constable (Jaya)
\item Challenge: Don't feel bad about what she did to Jace 2.  Senior Constable 2 (Jaya) → Matched
\item Refresh: Grim Visage (Jaya)
\item Refresh: Stash (Jaya)
\item Refresh: Adrenaline Junkie (Jaya)
\item Challenge: Bully Jace 3.  Truncheon 2 (Jaya) + Grim Visage 2 (Jaya) → Matched
\item Challenge: Ignore shitty state of clothes 2.  Stash 2 (Jaya) → Matched
\item Refresh: Truncheon (Jaya)
\item Challenge: Avoid going down like a bitch 3. Adrenaline Junkie 2 (Jaya) → Sent back to pool
\item Refresh: Senior Constable (Jaya)
\end{itemize}



\underline{  {\LARGE Ongoing Challenges }  }

\begin{itemize}
\item \hl{(}\footnote{\textbf{Suko T }Is this right?  Or was this just mentioned as a possible thing to throw at when it gets refreshed?  I didn't know if you had it to use or not. \textsubscript{12/07/12 11:17pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }I was thinking about it (although really it would have been from last session, unless I play out further ramifications).

Also, Hardened is a 3 these days. O\_o \textsubscript{12/09/12 9:52am}}\footnote{$\rightarrow$\textbf{Suko T }OK I moved it and updated it. :) \textsubscript{12/09/12 12:22pm}}
\end{itemize}



\underline{  {\LARGE Tank Challenge Levels }  }

Trace: Green

Nominal: Yellow

Solid: Orange

Synchronous: Red



\underline{  {\LARGE VP TOTALS }  }

Jaya: 2

Jonah: 9



\underline{  {\LARGE Quotes }  }



``So my sister is kind of winning the fight.  I would like to tackle the problem of making Jaya win the fight.''

\extraIndent{        -Rebecca}


\quotedDialog{
``You need to calm down!'' 

``Calm down?  Calm down??  You probably killed that guy!''

``Er, he was like that before.''
}
\extraIndent{        -Jaya and Jayce}


\quotedDialog{
``I hit him in the tummy!''

``I see that someone hasn't been reading Dr. Gerhauser's Anatomy books.''
}
\extraIndent{        -Rebecca and Adam}


\quotedDialog{
``Am I naked?''

``You're unconscious.  You should have thought about that earlier.''
}
\extraIndent{        -Rebecca and Nate}



``Your reaction is unusually orthogonal.''

\extraIndent{        -Dr. Gerhauser}


\quotedDialog{
``Welcome back!  I changed your bed, it was....soggy.''

``What happened?''

``I don't want to know.''
}
\extraIndent{        -Hayley and Oliver}



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/23/15 10:51pm
\end{flushright}

