\setcounter{chapter}{ 12 }
\chapter{\textbf{SAC-09, Interlude} }



\subChapterTitle{``Is this a kissing book?''} 

\deets{Suko}{\hl{December 27th, 2012}\footnote{\textbf{q.google }If there is a theme to this session for me, it's that the whole is less than the sum of its parts.  There is valuable information trapped in pockets.  All four of the team members learn useful concrete things from their contacts: Jaya from Morgan and Rook, Oliver from Dr. Gerhauser and Jaya, Jonah from Trenton, Hayley from Morgan.  None of them share it with the others (though Hayley clearly intends to).  The team members, for all of their flaws, are each quite competent in their own way (point buys help! ;) but they are not really a team.

Yet. \textsubscript{01/27/13 3:34pm}}\footnote{$\rightarrow$\textbf{Suko T }This session and the following session.  We really really need to have a team chat at some point... \textsubscript{01/27/13 11:20pm}}}



Lots of talking, but also some smooches (!) and a date!  ``Is this a kissing book?``



These notes have more gaps and thin spots than usual (I tried to put at least something down but some places I just had to put {[}....{]}), so please amend and append!  Have at ye. :)


\jumpHeadline{Capability purchases } 

Ion: Social Chameleon (3--\textgreater 4)

Adam: Hardened (3--\textgreater 4)

Suko: Hand to Hand (0--\textgreater 1), \hl{Memory for Details (0--\textgreater 1), possibly some others}\footnote{\textbf{Adam Kenney }The juxtaposition of these two phrases is pretty funny. \textsubscript{01/03/13 8:58pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{01/03/13 9:51pm}}



\jumpHeadline{Communal assets purchases (pending approval) } 

\begin{itemize}
\item Armor 3, which lets us have four level 1 armors, or two level 2's (basically a flak jacket we can wear under our uniforms?).  Cost: 12 communal VP
\item \hl{Silencer Level 1, to silence one rifle. Cost: 2 communal VP}\footnote{\textbf{Suko T }Forgot about this- we really should have equipped Oliver with this before going to Nicklepan. \textsubscript{01/24/13 1:21am}}
\item Forensic kit 1 to help with environmental detail Notice challenges.  Cost: 2 communal VP
\item \hl{Notice Aid @ 3 to help with Notice Challenges related to hearing (parabolic antenna) or vision (rangefinder binoculars)}\footnote{\textbf{Suko T }collapsed into one level 3 ``Notice Aid'' item, which shouldn't change the cost or the ability to split it into two level 2 items like we did. \textsubscript{01/24/13 1:20am}}  Cost: 12 communal VP
\item Armory 1--\textgreater 2  More rifles!  Cost: 4 communal VP
\end{itemize}



Total spend: 32



\jumpHeadline{ SAC-09 } 


\sceneHeadline{Bunk}

Jonah finally sleeps for a few hours.  When he wakes and gets up, Hayley wishes him a good morning, gets dressed for bed and goes to sleep peacefully.  Oliver wakes up not long after this and tells Jonah that he is going to speak to Dr. Gerhauser.  Hayley wakes up enough to sleepily ask Oliver to tell Dr. Gerhauser that she needs to speak with her on a non-urgent matter, and then goes back to sleep.


\sceneHeadline{Medbay}

Oliver and Jonah head down to Medbay and find Technician Swan there.  They briefly discuss Jaya but Swan has little information for them since he has not spoken with her yet. 



Oliver and Jonah go in to speak with Jaya.  Jaya wakes up suddenly and instinctively rolls to one side when she senses people looming over her hospital bed.  She's relieved to see that it is Jonah and Oliver. ``It's good that you didn't die,'' she says with relief.  ``It was a fucked up trip.''

``Did you almost die?'' asks Jonah.

``Yeah.  So it's important that you give me a report.  Because I'm your \textit{Senior Constable},'' she says with emphasis, watching Oliver and Jonah carefully as she says it.

She's pleased when Jonah and Oliver start talking but they don't really saying anything specific and instead ask her about her experience. 

Jaya vents a little, ``That was one of the most fucked up drug trips.''

``Was that what it was like for you?'' asks Oliver.

Jaya leans forward and taps her head.  ``Are you okay?  I've had a lot of bad trips, so I can handle it, but I don't know if you can handle it.''

``Hayley seemed to think it was a walk in the park,'' says Jonah. ``But what she said happened, didn't seem to happen.  She says she was in a tank and tried to escape.''

``This is Hayley we're talking about, she's sweet, but when you reach the bounds of her imagination...'' \hl{Jaya}\footnote{\textbf{Rebecca S. }Pretty sure that was my line... but the sad thing is, I'm not 100\% certain... but I'mma gonna' steal it back anyway \textsubscript{01/03/13 9:58am}}trails off, shaking her head.



Dr. Gerhauser walks in, removes the IV, and tells Jaya that she's to report to Ops right now.  Jaya hobbles out in her sad little medical gown.  Oliver makes some sort of parting quip and Jaya flips him the bird.  Dr. Gerhauser asks how Jonah and Oliver are, and after their perfunctory and vague answers, she leaves. 



Jonah pulls Oliver aside and asks, ``without asking for specifics, you didn't experience being in goo?''

``No,'' replies Oliver.

``Do you think she actually tried to break out or just thought that she did?''

``Does it matter?'' asks Oliver.

``Yeah, I just don't know what it means.  We should ask her.  What she described is not what happened to any of us.''

``What do you think the purpose of all this is?'' asks Oliver.

Jonah thinks.  ``\hl{I have limited experience with machines like this.  I don't know what they are for, but I think Morgan wants a team that can survive difficult situations}\footnote{\textbf{q.google }This is what Jonah said but he's not talking like Jonah... RP fail.  This should probably say something like: ``I don't know much about this, 'bout machines you put people in.  I don't know what they are for -- but I think Morgan wants people who can stay alive in a hard place.  Maybe that's what this is about.'' \textsubscript{01/27/13 11:23am}}.''

``Were you other people?''

``I don't think so, but it was very hazy.  Like in a dream when you think that you know someone but when you wake up you realize that they are not the faces you know.  I can't guess what this does but I can guess what they want.  What do you think?''

``I think it's experiential.  No answer they can tell us will make us more likely to succeed.''

``Did Dr. Gerhauser tell you that?  I don't see on what she's getting out of this.  But the Agent wants to be able to throw crazy stuff at us and we don't blink.''

``Well if that's what she wants, she's going about it all wrong.''

``But that's why I'm asking about Hayley, she's seen some very strange things.  Otherwise, why pick someone who has such a hard time with normal things?''

``I think they chose her because she's docile.''

\hl{``She almost got herself killed-''

``She didn't die, I did,'' points out Oliver.

``Yeah okay,'' says Jonah a little dismissively, ``but I still think I'll ask Hayley.''}\footnote{\textbf{Suko T }My notes are very thin on this part- all I remember for sure is that Jonah somewhat blewoff/downplayed/discounted Oliver's dying and that didn't go over so well. :D \textsubscript{12/30/12 10:57pm}}\footnote{$\rightarrow$\textbf{q.google }It was not intended to be dismissive.  It really wasn't: Jonah is quite sensitive about almost dying.  But the key here is in the \_almost\_.  Jonah would like that to continue to be part of the sentence. \textsubscript{01/27/13 11:26am}}

``Yeah, good luck with that,'' says Oliver shortly and walks away.

``If I learn anything, do you want me to tell you?'' asks Jonah to Oliver's back.  Oliver says nothing.


\sceneHeadline{Bunk}

Jaya bursts into the bunk room, waking Hayley.  Jaya slams around the room, getting dressed.  Hayley blinks slowly and orients herself, and then sits up.  Jaya is pleased to see Hayley and asks, \hl{``If I gave you an order, and we weren't on a mission, would you follow it?''}\footnote{\textbf{q.google }Isn't this a somewhat military organization?  In which case, as long as Hayley isn't on shore leave, mission or no, doesn't she have to follow Jaya's orders?

This is actually a serious question.  Makes a big difference especially going forward. \textsubscript{01/27/13 11:28am}}\footnote{$\rightarrow$\textbf{Suko T }A good question to ask her. There's a very good reason Hayley is asking for military protocol training.  She actually DOESN'T really know that this is likely the case.  Nothing but nothing should supersede her contract holder's orders.  Everyone outranks Hayley, so the fact that Jaya is her superior officer only means that she follows her orders over Jonah and Oliver's.  That's about it.  Morgan's orders would override Jaya's (and did in one subtle case at New Station), and her contract holder would override Morgan's, if they ever directly conflicted.

Remember she had barely a month of training with the TA before joining the squad, and I get the impression that most of it wasn't even with the TA since there was a lot of contract negotiations.  I expect she learned even less than the rawest recruit.  She may have only been in uniform for a few days before she joined Jaya's squad. \textsubscript{01/27/13 11:30pm}}

``If it did not contradict my contract holder's orders, it would depend.  Most likely yes,'' answers Hayley.

``What if it contradicted your contract holder's orders?''

``Then no.''

``Would I be able to see a copy of your contract holder's orders?''

``No.''

``Well okay then, ta!''



As they talk, Hayley tucks in Jaya's shirt, buttons the collar, and smooths her hair somewhat.  Jaya hardly even notices and runs out of the room to Ops, passing Oliver along the way.


\sceneHeadline{Ops \& new Exercise Room}

Jaya walks into Ops to find Morgan and Larissa (??) in the room.  Morgan is looking at a tablet and there's a duffle bag on the table.  Morgan looks up and asks, ``How are you feeling?''

``My team-'' begins Jaya.

``I mean, how are you physically?'' clarifies Morgan.

``Good.''

Morgan tosses Jaya the dufflebag and indicates she should follow her out of the room.  Jaya peeks into the bag, accidentally dropping a few of the items in it- a few rolls of cloth tape and gloves.  They get into the elevator and head up.  It opens into a corridor and Morgan turns left and keys open a door. 

They walk down a long corridor and Morgan asks, ``Did you find the tank experience enlightening?''

``Not really, Ma'am Sir,'' says Jaya honestly, pauses slightly and then adds, ``It was incredibly mentally taxing, and I think my team needs some extra Shore Leave to recover from such a tripping-'' she catches herself and says instead: ``\textit{extreme} experience.''

``Granted,'' says Morgan with surprising agreeableness. ``But before you go, you will need to pick your next mission.  There are a couple of likely targets, or you can go back into the Tank.  \hl{Of course}\footnote{\textbf{Adam Kenney }Of course! \textsubscript{01/03/13 9:02pm}}you will be able to choose your auxiliary support.''



They step into a corridor hewn out of rock, and head up a staircase that looks like it might have been there before the corridor was made (the rock extends onto the stair treads).  The rock walls are oddly shiny but feel like rock when touched.  



``What do you mean 'auxiliary'?'' asks Jaya.

``One person beyond Rook.  The personnel here are valuable so choose carefully.''  Morgan replies as she opens a box on the wall and flips a large toggle switch.  Lights go on and reveal a huge empty concrete room.



``Hayley has been requesting an exercise space.  I thought that you could do something with this to do training.''  Morgan reaches into the duffel bag, tosses a pair of gloves to Jaya and starts wrapping her hands with the cloth tape.  ``I was hoping you'd be willing to train now.''



Jaya looks around at the empty room and begins to look a little worried.  ``Are you suggesting \textit{we} train?'' she stalls.

``There are few people at my level here,'' says Morgan.  ``And you always seem ready for this kind of thing...''

``I just...well... you know...'' says Jaya, and then shrugs and pulls on the gloves.

Morgan tosses Jaya a helmet.  ``Fisticuffs only?''

Jaya checks the room and duffel bag for any other weapons and then nods.



They spar.  Morgan is relaxed and takes it a bit easy on Jaya.  Her fighting style is more about blocking than dodging.  Jaya lands a few blows but Morgan always makes her pay for them as Jaya overextends and leaves openings.



After about 30 minutes, Jaya is panting with exhaustion and Morgan calls a halt.

``That was good.''

``Anytime,'' wheezes Jaya, leaning against a cement pillar to stay upright.

``Anytime you want to talk things out, let me know.  Get your team in here and set up what you need.''

``Can we set up a shooting range in here?''

``For that we may have to put you somewhere with more sound proofing, otherwise you might blow your eardrums out.''


\sceneHeadline{Cafeteria and Medbay}

Elsewhere, Oliver asks Jari to get an appointment with Agent Morgan.   Jonah goes to talk to Technician Swan to get more information about the machines in the MedBay room. 



Hayley goes to speak to Jari and asks him if he can teach her how to keep \hl{track of things}\footnote{\textbf{q.google }She could carry a pad of paper and a pen... \textsubscript{01/27/13 11:32am}}\footnote{$\rightarrow$\textbf{Suko T }She could, but probably pulling out a notebook and laboriously writing down notes would be even slower than trying to use a memory palace.... \textsubscript{01/27/13 11:35pm}}.  How to remember details so she can report them back. He gives her a quick lesson in \hl{building a memory palace}\footnote{\textbf{q.google }... or she could build a memory palace.
(Seriously, do you know what the rent is like on a memory palace?  Even a memory hovel is hard to maintain.  A small pad of paper is \_much\_ less work.) \textsubscript{01/27/13 11:33am}}\footnote{$\rightarrow$\textbf{Suko T }Are you kidding?  In this world, paper is way more precious than rent in brainspace.  It seems like there are lots of empty brains not being used while their owners work to death on Plantations and in drone jobs at various Corporations :D \textsubscript{01/27/13 11:35pm}}.  There is an awkward moment when he tells her to think of a place she knows well and the place she thinks of is a door-less cell, but he manages to steer her to a more appropriate place and the lesson goes much better from there.


\sceneHeadline{Bunk \& New Exercise Room}

Everyone congregates into the bunk room and Jaya comes in, excited to show off the new space that she's found for us.  She says that she gets to choose our next mission and that she got us more Shore Leave that we can take immediately.  The team explores the new exercise room a bit.  \hl{Oliver and Jonah keep their counsel}\footnote{\textbf{Suko T }I recall something about Oliver not being terribly impressed with the space and not thinking it would be that useful to him. \textsubscript{01/01/13 10:13pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Yeah... gimpy boy pouting because he can't run circles here like everyone else... also, he pointed out he already has his pool thing that works just fine thank-you-very-much \textsubscript{01/03/13 9:43am}}\footnote{$\rightarrow$\textbf{Adam Kenney }I think Oliver was pissed that Jaya got to choose the next mission.  As his issues with command hierarchies continue to evolve in delightful ways! \textsubscript{01/03/13 9:04pm}}\footnote{$\rightarrow$\textbf{q.google }Pissed that she got to choose \_at all\_? \textsubscript{01/27/13 11:35am}}\footnote{$\rightarrow$\textbf{Adam Kenney }Well, that we weren't consulted. \textsubscript{01/27/13 }}but Hayley is visibly thrilled to finally have an exercise space.  Jaya takes off to go to the Ops room, and Oliver leaves soon after to go speak with Agent Morgan.


\sceneHeadline{Ops}

Jaya heads to the Ops room and finds Rook there.  After greeting him and sitting down, she says, ``I was told I could pick our next mission?''



Rook calls up a Map of the Directorate, with two additional lines extending off from the usual TA station map.  The two additions are Portal and Downtown Nicklepan.

``Are they presumed hostile?'' asks Jaya, pulling out her notebook to take notes.

``I'm glad you asked.  We have had no communication with Nicklepan for some time now.  Portal is interesting, no one has been there in a long time.  Based on the information you retrieved from SAC-01, we think that there is a Beacon at Portal with the location of other facilities we may be interested in.  You will need telemetry.''



Jaya hems and haws, clearly stumped by the phrase 'telemetry' but trying to fish for more information.  Agent Rook stops her and points out he's here to help her, everything is confidential, yadda yadda yadda.  Eventually Jaya mans up and asks what telemetry is and learns that it is a type of math. Apparently, Swan and Jari could maybe do it, although Swan's knowledge is outdated due to his recent focus on medical knowledge.  The best candidate is Trenton but of course Jaya doesn't want to work with him.  Rook warns that it could be dangerous.  ``We can do danger,'' says Jaya proudly, but then adds honestly, ``Well, not in our heads.  That sucked.  But otherwise, we can handle it.''



Jaya asks for Rook's opinion on which mission is best.  Rook says that Agent Morgan is more interested in what is going on in Nicklepan than what can be found in Portal, so of course Jaya signs her team up for the Nicklepan mission.



Rook says that he can give her some names of people to talk to who were a part of the local equivalent of the TA.  He asks if Jaya intends to go in stealthily or openly.  



``\hl{Well, we don't have Langston's {[}sic{]} experience.  Jonah could blend in, but Hayley and I would stick out like sore thumbs}\footnote{\textbf{q.google }This is an insight I don't think Jaya would have had before SAC-09.  As she notes sticking out like a sore thumb isn't normally a negative for a TA constable.  It's how they get work done.

I wonder if/when she'll make the next step. \textsubscript{01/27/13 11:40am}}.  We're TA constables to the core!''  brags Jaya.  ``How much time will this take and do you want us to bring back any.... emissaries?''

Rook says solemnly, ``No, we don't need any kidnapping.''

``Is there anyone with experience in Nicklepan?''

``Lackovich does.''

``That's a shame,'' Jaya thinks for a moment and says with a look of delight, ``Would she be reporting to me?''

``No she would report to me.''

``But in the field, if I gave her an order, she would have to follow it.  We need an unambiguous chain of command.  I'm not saying she has to be demoted....'' Jaya gives Rook a significant look, but he just looks at her blandly, ``but it has to be clear.''

``Very well, you'll be going to Nicklepan then?'' says Rook.



Jaya pauses, senses a trap, but doesn't know what else to say.  ``Yes,'' she says and briskly closes her notebook, which is as blank as it was when she opened it.



As she gets up to leave, Rook tells her, ``\hl{Please inform your team that with their new access you can visit floors 1, 2, 3 (Medbay), and 5 (storage).  You are not authorized to go to Alpha Zed sector, or to floors 4 (Brig), 6 or 7}\footnote{\textbf{q.google }I've added a note about this to the SAC-09 doc.  Please fill out/amend. \textsubscript{01/27/13 11:45am}}.''  The barrage of numbers and code words is clearly too much for Jaya and her visible discomfort and confused muttering manages to signal what her words somewhat fail to- Rook says he'll send a sheet down with the information.  


\sceneHeadline{Morgan's Office}

Oliver goes to Morgan's office.  He asks about the Orc of Anglia and mentions how he is using scare tactics against his family.  Morgan tells him to just skip to his actual question and he asks for information to allow him to go on the offensive, rather than being defensive all the time.

``I'm always on the defense, rather like being hunted like a rat.  I don't know anything about him.  I don't know what's important to him,'' says Oliver.  \hl{``I was given a chance to bow out of the Tank sessions, but I didn't take it.''}\footnote{\textbf{Adam Kenney }Oliver volunteered this - it wasn't a comment or question from Morgan. \textsubscript{01/03/13 9:07pm}}

``Why?''

``\hl{Because I have a good feeling we're on the same side, at least in these things}\footnote{\textbf{Adam Kenney }I think I also threw in something along the lines of, ``If I'm not mistaken, you have no love for Anglia - and with good reason.'' (referring to what Oliver learned from Dr. Gerhauser about her and Agent Morgan's origin story) \textsubscript{01/03/13 9:09pm}}.  Consider it a gesture of goodwill.''

Morgan thinks for a moment and replies, ``The Orc of Anglia is motivated by pathological hatred.  Right now he's focused on you.  If the Orc's masters tug on his leash, he'd go elsewhere but right now they are letting things stay as they are.  As a gesture of good faith, I will put a piece into play.  He enjoys psychological warfare, and rarely avoids the chance for a challenge.  \hl{If we were to give him another target}\footnote{\textbf{q.google }This is tantalizing in a terrible sort of way.  I'm guessing the target knows that they are a target, but it might not be the case.... \textsubscript{01/27/13 11:50am}}, we could lure him out.  If you want, I will think about it.''

{[}...{]}

\hl{``To lay a card of my own on the table.''

``Nice for someone else to know what it's like.'}\footnote{\textbf{Suko T }I have these snippets of dialog but several sentences are missing.  Can anyone fill in the missing lines? \textsubscript{12/30/12 11:37pm}}

``There's something else I was hoping you could help with,'' says Oliver.  ``My father's in hot water because of my careless actions in Cardoza.''

\hl{``You want me to interfere?'' says Morgan, somewhat disdainfully.}\footnote{\textbf{Nathaniel Ford }I think she said something along the lines of 'You want me to help your father with his money troubles' or the like. The focus was the money, anyway. \textsubscript{01/01/13 10:48pm}}\footnote{$\rightarrow$\textbf{Suko T }That sounds likely. \textsubscript{01/02/13 4:44pm}}\footnote{$\rightarrow$\textbf{q.google }That's what I remember too. \textsubscript{01/27/13 11:51am}}

``No, I just want to know why it's a problem.  The funds were used to help us in an anti-terrorist action, so why is is this becoming a problem for him?''

``He's actually the one who uncovered the charges, but they suggest that he has inordinate control over the TA.  Which is patently false,'' laughs Morgan, ``But doesn't help him any.''  



Oliver leaves and Morgan asks him to send up Hayley when he sees her.


\sceneHeadline{Exercise Room}

Meanwhile, Hayley and Jonah are still in the exercise room.  Hayley is pacing the room with a measured step, counting softly to herself, clearly figuring out the dimensions of the space and where things could go.  



\hl{Seemingly out of the blue, Hayley asks if Jonah knows much about Senators and mentions that it would be useful if our squad shared what we knew and talked about it since it seems like they are important to what is going on.  Jonah seems surprised at the question and motivation behind it but approves of the idea.}\footnote{\textbf{Suko T }added this in, forgot about it the first time through the notes.  Poor Jonah, no witnesses to Hayley making a team strategy suggestion. :D \textsubscript{01/03/13 2:19am}}\footnote{$\rightarrow$\textbf{q.google }Why do you think Jonah \_wants\_ witnesses? \textgreater ;) \textsubscript{01/27/13 11:52am}}



Jonah asks Hayley questions about her experiences in the Tank.  She is a little less garbled this time with her answers, but when Jonah asks for more details about the other people there she says that she is not supposed to tell him anything about that.  She confirms that there were other people there, but only the second time.



As his questions continue, Hayley stops roaming the room and comes to stand near him.  As she answers, she steps closer and closer to him, her answers getting more and more distracted and incomplete as she gazes at his face.  When she gets too close, Jonah starts pacing and Hayley trails after him.  He asks why she exercises and she says that you have to hurt to get stronger, exercising tears muscles and makes them stronger when they heal. \hl{Jonah seems surprised that Hayley knows this}\footnote{\textbf{q.google }Surprised but not the obvious way.  Hayley has ``hurt to get stronger'' wired into her so deep he's surprised she's thought to put it into words.  As for muscles, Jonah himself has only just learned this from the medical textbooks, but its not surprising if Hayley might have picked it up from someone Citizen-y. \textsubscript{01/27/13 11:55am}}\footnote{$\rightarrow$\textbf{Suko T }Yeah, she knows a lot of medical buzz words.  When she says stuff like this, if sounds like she's parroting what someone else told her repeatedly, there's a good reason for that :D \textsubscript{01/27/13 11:38pm}}.  Hayley offers to let him examine her muscle tone but he declines politely.  She demonstrates some of her exercise routine for him, being totally obvious about peeking at him to see if he's watching her.



Jonah starts heading to the door and Hayley steps in front of him.  He pauses and she asks if she can ask him a question.  ``It may make you uncomfortable though, so I won't ask if you don't want me to,'' she says, watching his face somewhat anxiously.  Jonah says she can ask.  \hl{``Can I kiss you?'' asks Hayley, looking hopeful.}\footnote{\textbf{Suko T }What follows is my best guess at the giggle-tastic line of questioning that they went through before kissing.  Feel free to fix it. \textsubscript{01/01/13 10:17pm}}

``You want to kiss me? Why?'' asks Jonah.

``Because I want to.''

\hl{Jonah pauses.}\footnote{\textbf{q.google }It's the sort of pause between short and long with the very unfortunate label of ``pregnant''. \textsubscript{01/27/13 11:56am}}

``You know this means no kissing anywhere else.''

``Why would I want to?  I don't want to kiss \hl{anyone}\footnote{\textbf{q.google }It's clear from the text but Jonah didn't say \_anyone\_ he said \_anywhere\_. \textsubscript{01/27/13 11:57am}}\footnote{$\rightarrow$\textbf{Suko T }Yup, but definitely she'd read that the wrong way. \textsubscript{01/27/13 11:40pm}} else.''

``Usually when someone kisses someone else, they want to kiss them again.''

``Why?''

``Have you kissed anyone before?''

``Oh yes many times.''

``And you didn't want to kiss them again?''

``No, I hated it.''

``Why did you do it then?''

``Because I had to.'' 

``So is this the first time you'll kiss someone because you want to?''

``Yes,'' says Hayley looking excited and hopeful.

\hl{``Okay then.''}\footnote{\textbf{Suko T }so romantic! :P \textsubscript{01/02/13 4:45pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Was there a heavy sigh of resignation as well?  You know, to add to the mood  :) \textsubscript{01/03/13 9:51am}}\footnote{$\rightarrow$\textbf{Suko T }I think so!  That makes it even better :D  I do recall it was said with a sense of unenthusiasm and reluctance.  Which was very funny and also mattered not one bit to Hayley.  Land of the one-way streets, this girl.  I was rather surprised that he did it at all but hey, she IS awfully pretty :D \textsubscript{01/03/13 10:37am}}\footnote{$\rightarrow$\textbf{q.google }She \_is\_ awfully pretty.  And the characters are all in their early 20s at best and Jonah is a normal guy.  He's decidedly not unenthusiastic about kissing a girl who looks like Hayley.  He's wary of kissing a girl who has the landmines Hayley has in her head. \textsubscript{01/27/13 12:01pm}}\footnote{$\rightarrow$\textbf{q.google }And knowing what he knows about Hayley that she wants to do it is a big deal.  If she was doing it out of obligation he wouldn't have done it.  (I don't see Jonah as worrying about the ethics of this if it was a one night stand.  A co-worker who works with you -- in \_firefights\_ -- is rather a different story.) \textsubscript{01/27/13 12:04pm}}\footnote{$\rightarrow$\textbf{Suko T }Yeah, I can't wait to have Hayley try to explain what she thinks a ``workplace romance'' is :D \textsubscript{01/27/13 11:41pm}}



They kiss and it's a proper kiss too.  Hayley's quite good at it and Jonah gives as good as he gets.  Hayley looks happy afterward, and \hl{if this was an anime, her eyes would be huge and sparkling}\footnote{\textbf{q.google }Aieeeee! \textsubscript{01/27/13 12:05pm}}.



They head back to the bunk, consciously not acting any differently than before.  Hayley gives Jonah a page of equations to ask Trenton about.  They run into Jari and Oliver along the way.  Jari tells Jonah that Trenton wants to speak to him and Oliver tells Hayley that she is to report to Agent Morgan.


\sceneHeadline{Trenton's Lab}

Jonah goes to speak to Trenton in his lab.  Victor, the guy we captured on one of our first missions is there, his head down and working intently on something at one of the benches/consoles.  Jonah recognizes him but gives no indication of having noticed him.  Jonah asks what Trenton knows about the Tank, but he doesn't know very much.  He mentions that although the experiences have been different for each of us, that eventually we'll get on the same track.

``Do you know what it's for?'' asks Jonah.

``\hl{I was hoping you could tell me,}\footnote{\textbf{q.google }Ditto, Trenton, ditto. \textsubscript{01/27/13 12:09pm}}`` says Trenton.

``Each of our experiences were different.  Unpleasant.  For Senior Constable Jaya, it was like a bad trip.''

``\hl{There are no bad trips}\footnote{\textbf{q.google }Only bad \_people\_. \textsubscript{01/27/13 12:08pm}}.'' says Trenton with a sly smile.  ``Anyway, Morgan said I had to give you a card in case you need equipment for the training area.  Don't mess with anything and don't disturb the 'Talent'. gesturing at Victor. `` He hands Jonah an access card.  ``Say, do you have any thoughts on her? Charlie Gamma 2?'' and he points to the woman whom we brought in from SAC-01.

``Has anyone talked to her?''

``Sure,'' Trenton points to Victor, ``He won't go in there anymore, she won't talk to me.  We don't speak the same language.''

``What does that mean?''

Trenton points to some pages of symbols on one of the screens.  ``That's another language, \hl{Alemán}\footnote{\textbf{q.google }http://en.wiktionary.org/wiki/alem\`an \textsubscript{01/27/13 12:11pm}}, actually.''

``It is?  \hl{That's a language}\footnote{\textbf{q.google }As noted, the idea Directorate people have about ``languages'' isn't the same as ours, since they basically are only aware of one, and rarely if ever hear or read others. \textsubscript{01/27/13 12:12pm}}?'' Jonah says incredulously and shakes his head.  ``What were the SACs for, if there are eight of them?''

``A very good question.'' says Trenton unhelpfully.

Jonah continues to ruminate out loud, ``We can't be too far from the known train stations because we aren't on the train that long.  Couldn't you \hl{triangulate}\footnote{\textbf{q.google }Ha!  Vocabulary word! \textsubscript{01/27/13 12:13pm}} our location?''

``We would need a beacon and transceivers to detect those beacons.''

Jonah doesn't completely follow the explanation but does understand that if they could get a beacon and transceiver onto a train they could learn a lot.  The trick is how to do it without being noticed.  \hl{Trenton implies that there is equipment to do it just lying around the room where he works.  Jonah notes that unfortunately he isn't allowed to come up to that room on his own.  Trenton say that's too bad.}\footnote{\textbf{q.google }The tone here is entirely one of ``it would be a great pity if one of these devices were to disappear from my desk''.  They both agree on what should happen when the chance arises. \textsubscript{01/27/13 2:41pm}}

They turn back to discussing Charlie Gamma 2.  Jonah tries to feel out what they've asked her already.  Trenton seems to suggest that he and Victor have already tried everything they can think of, \hl{and asks if Jonah would like to try}\footnote{\textbf{q.google }Trenton's apparent admission of limitations seemed unusual to me.  Jonah is pretty tempted by the offer, the first taste he's had in a while of what it might be like to be Trenton, interested in something for sheer curiosity's sake. \textsubscript{01/27/13 2:43pm}}\footnote{$\rightarrow$\textbf{Suko T }I sort of got the impression of Trenton wanting to let someone else get yelled at and possibly attacked by angry Charlie Gamma 2.  Trenton's big on not messing up his pretty face :D \textsubscript{01/27/13 11:44pm}}.  Jonah's curiosity is piqued but he's non-commital, though his interest shows.

Jonah says he's got a lot to work with and thanks Trenton.  Almost as an afterthought, as he's leaving, he tell Trenton about Hayley's request for Signe to join Trenton here.  Trenton says, somewhat wistfully, that Morgan probably wouldn't allow it since he works better when deprived of ``companionship.''  Jonah is sympathetic, and doesn't mention that this presumably includes Hayley too.


\sceneHeadline{Bunk}

Everyone re-congregates back in the bunk and Jaya announces that she's picked our next mission. ``We're going to Nicklepan!'' she announces enthusiastically, deliberately not looking at Oliver.



\hl{Jonah and Oliver are upset at the news and the lack of details that Jaya has}\footnote{\textbf{q.google }It's actually a pity. Jaya was doing very well up until this point in being both strategic and diplomatic (for her) when talking with Morgan and Rook.  If she'd presented the problem in even slightly more detail, and explained her thoughts, while Oliver might still have been upset with the result, Jonah would have been \_much\_ less disturbed by it. \textsubscript{01/27/13 2:55pm}}.  Somehow hand waving about popping in, checking out the situation, and leaving doesn't fly with the team.  Oliver starts pushing back hard and Jaya tells Hayley and Jonah to give them some privacy and walks to the back of the room.  Hayley leaves, but Jonah stays.  \hl{When he interrupts Jaya}\footnote{\textbf{q.google }Interrupting her like this is very incautious for him under most circumstances but Jonah is trying to take Oliver's side out of sheer frustration.  His tank experience has the war fresh in his mind, and the battle Oliver was injured in even fresher.    He's having a hard time containing the emotion attached with being sent into a possible battlefield carelessly.  His empathy for Oliver here is visceral rather than collegial: he's not actually distinguishing between the image of Oliver being injured and his own fear. \textsubscript{01/27/13 2:55pm}}\footnote{$\rightarrow$\textbf{Suko T }Yeah, that's why I wanted to include the timeline highlights in the next session summary, because a lot of these memories are very fresh for our characters and should be affecting them like you had them affect Jonah.  Lackovich's anger at our Squad for what happened in Cardoza hasn't really had time to cool off.  It wasn't over 6 months ago like it was for us OOG, it was 4 1/2 weeks ago IG.  She's barely healed from her grievous injuries, much less emotionally recovered. \textsubscript{01/27/13 11:49pm}}, she angrily directly orders him to get out of the room.  Jonah silently complies, his stony expression showing displeasure obvious to anyone but Jaya.



Jonah attempts to push the door open to eavesdrop but Hayley holds the door shut and does not let him listen in.  ``Senior Constable Parvadi asked for privacy,'' she says firmly.  Jonah is visibly angry and after a few attempts to browbeat/order Hayley into opening the door or stepping aside, which she calmly refuses to do, he tells Hayley that she can come get him when Jaya comes out and changes her order.  And he stalks off.



Inside the room Jaya and Oliver are arguing.  Oliver says that it sounds like we're going to war.  Jaya agrees but amends that it's an Information War, and we have to win it.  Things are looking like they're going to get really ugly.

 {[}....{]}

``People are going to recognize me in Nicklepan.''

``Who?''

``You don't forget the person who shoots you.''

``Really?'' says Jaya with honest surprise.

``What if I see someone that I need to deal with while we're in Nicklepan?''

Jaya pauses and in \hl{a moment of tactical brilliance}\footnote{\textbf{Adam Kenney }yeah... \textsubscript{01/03/13 9:12pm}}, offers to help Oliver with whatever personal quest he's got going on.  ``\hl{You can't go hunting him down}\footnote{\textbf{Adam Kenney }Actually, I don't know that she said anything this specific or restrictive.  I pretty much got a carte blanche, I just also have to help the team accomplish the mission. \textsubscript{01/03/13 9:13pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }I'm fuzzy on this as well... but I'm pretty sure it was along the lines of ``you gotta' help us win the mission'' and anything that didn't hinder/heavily distract was hand waved away as being ``fine'' \textsubscript{01/04/13 11:56pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Yup, that lines up with how I (fuzzily) member it. \textsubscript{01/05/13 11:57am}}\footnote{$\rightarrow$\textbf{q.google }She \_did\_ say Oliver can't go chasing his target down on his own.  But the key idea of ``you help complete the mission, and this can happen without sidetracking it, and I'll help you do it.''  Best leadership we've seen in a while. \textsubscript{01/27/13 3:21pm}}, but if you find that person, we'll help you deal with him.  \hl{We're a team and team members back each other up. And avenge each other!}\footnote{\textbf{q.google }For want of a nail: real pity Jonah didn't hear this. \textsubscript{01/27/13 3:22pm}}''

``Really?  Even if we have to resort to unconventional methods?'' asks Oliver with surprise.

Jaya shrugs.  ``Whatever.  Do we have an agreement?''  They shake on it. 

``Have fun on Shore Leave,'' says Jaya.

Jaya leaves the room to find Hayley patiently waiting in the hallway.  Not finding Jonah to yell at, she heads off with hopes of shore-leaving it ASAP.  Hayley goes to fetch Jonah from the cafeteria.  When comes back he asks Jonah asks if Oliver is okay with the mission as described.  Oliver nods but his jaw is set and he doesn't look happy.  Jonah asks if Oliver feels they need more information.  Oliver agrees but doesn't seem inclined to seek it out.  Jonah tells Oliver that he's going to go find out more about their mission from Rook.


\sceneHeadline{Ops}

Jonah finds Rook in the Ops room and asks for more information about their mission.  He phrases it so that it sounds like he's doing the busy work that Jaya is too important to do herself.  He opens his notebook and actually takes notes.



``We haven't heard from Nicklepan in several weeks,'' says Rook.  ``We need to determine why they pulled back, and then you can leave.  We have agents in the area that haven't reported back but since there are no trains into that area, they may not be able to.  We are not going to release their names to you for their safety.''



``How can we blend in?'' asks Jonah, taking notes.

``Well it will be difficult because when we enter the station they will see us.  It would be possible to pass ourselves off as traders or lost travellers but it would be hard.  The difficulty is if they have become hostile.  It could become a conflict situation quickly.  They are having a water shortage like we are, and they may have lost control of the train stations.''



Jonah goes back to the bunk and reports this information to Oliver, saying that the reason Jaya's report was so vague was because there actually wasn't that much to know.  It is an information-gathering mission.  Oliver kind of brushes off Jonah's report and doesn't really engage with him.  Oliver leaves to go speak with Dr. Gerhauser.


\sceneHeadline{Medbay}

Oliver finds Dr. Gerhauser in the Medbay, eating a sandwich.

``You ever leave this place?'' he asks.

``To sleep,'' she says.

``All work and no play...'' he says teasingly, which earns him a raised eyebrow. ``If you went on leave, where would you go?''

Dr. Gerhauser pauses and says slowly, ``I'll assume you didn't mean to give any offense with that question.''

``You're right, I didn't.  Sorry.  But there's a whole world out there.''  

{[}...{]}

Oliver asks, ``Why do we get leave?''

``Most react better to stressful situations when they are given time to relax.  They perform better.  They found that rotating soldiers off the front lines, helped them last longer.  Since it benefits most, we find it easiest to give the leave to everyone. I simply have nowhere to go where I might unwind any more than I do here.''

``I have somewhere to show you, if you want,'' offers Oliver.

``Where?''

``In Cardoza.  It's nice, it has a view.''

``Well, I'm guessing that won't freak Morgan out too much,'' says Dr. Gerhauser thoughtfully.

``Your work will still be here,'' says Oliver.

``Okay,'' says Dr. Gerhauser. ``I'll go pack my things.''

Oliver looks a little surprised that it worked, but pleased.

As he turns to leave, Dr. Gerhauser says, ``Just to be clear, you did just ask me out, right?''

\hl{``Um, yeah,'' says Oliver, with a smile.}\footnote{\textbf{Adam Kenney }If I could ret-con any one thing in the session, I think I would have a distinct tone of surprise in Oliver's voice here. \textsubscript{01/03/13 9:15pm}}\footnote{$\rightarrow$\textbf{Suko T }Do you mean he wasn't surprised she said yes?  I was! \textsubscript{01/03/13 10:17pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }No, I mean that he should have been more surprised to realize that he just asked her out.  Obviously he's wanted to for a long time, but the actual urge to march down to MedBay and bluntly do so (well, as blunt as a Citizen gets) was not planned. It was more of a reaction to the interpersonal stresses within Team 1, like a ``let's get the hell out of here'' feeling. \textsubscript{01/05/13 12:02pm}}\footnote{$\rightarrow$\textbf{Suko T }Ah yes, makes sense.  Also I misread your first comment and thought you said ``remove the distinct tone of surprise'' so that's why my comment probably didn't make much sense. \textsubscript{01/27/13 11:51pm}}


\sceneHeadline{Morgan's Office}

Hayley goes to speak with Agent Morgan.  She doesn't sit or ask to sit.  She thanks Morgan for her time and says she will keep it brief.  After clarifying what she is allowed to tell her contract holder and what she isn't, Hayley asks Morgan can do anything to help Ms. Vorrutyer while Hayley is here in SAC-09.   She learns that Ms. Vorrutyer may be ``compromised'' and that the more Hayley does here, the more she will be helping Ms. Vorrutyer, which seems to cheer up Hayley a great deal and gives her courage to ask the next question.  She prefaces it with asking permission because it will be rude.  Morgan gives her the okay.

\hl{``Why are you so nice to us?'' asks Hayley frankly.}\footnote{\textbf{Suko T }Ah!  I had forgotten this.  So Hayley  had been to Morgan's office before. Looks like Hayley's 2/2 in saying something Morgan didn't expect (though it was handled admirably both times) \textsubscript{12/05/14 4:59pm}}

Morgan looks a little surprised, ``I don't think that the rest of your team feels the same way, in fact I would guess that Constable Langdon feels the exact opposite.  What do you mean?''

Hayley frowns and thinks hard, ``You allow us so much time to just sit around do nothing.  We're not training or learning or doing anything.''

``Do you feel your training is insufficient?'' says Morgan with a hint of warning in her voice.

``Yes, there are things I need to learn that I'm not,'' says Hayley, oblivious or unmoved by Morgan's tone.

``Like what?''

``Like, um...like the chain of command!  For example, you're called at least three different things-''

``You can call me Agent Morgan or Agent Gerhauser,'' interrupts Morgan.

``Um yes of course I do,'' says Hayley, a bit confused, ``but I mean that it's not really clear how things go, um...''

``You mean protocol?''

``Yes!'' says Hayley in relief, ``Yes, the protocol around here.  I don't know it.  It's confusing.''

``What else?''

``Training!  We need to exercise.  Our stamina is terrible, and our flexibility isn't so great either.  Our strength is okay, some of them work at that, but not regularly.  A regular regimen would be good.  Thank you for the new exercise space, that is going to help a lot.''

``Anything else?''

``Yes, but I can't think of it now.''

``Submit a list of items you want training in to Jari.''

``Okay,'' says Hayley cheerfully, looking pleased. ``Thank you.  Oh and I wanted to confirm with you that I have been told to follow your orders like I would follow my contract holder's.  I just want you to hear me acknowledge that and that I understand what it means.''

Morgan nods. ``Dismissed.''


\sceneHeadline{Addendum }\textbf{\hl{(what Hayley writes to Jari)}}\footnote{\textbf{Suko T }This may be amended after Shore Leave but this is the basics. \textsubscript{12/31/12 5:09pm}}\footnote{$\rightarrow$\textbf{q.google }Oh nice!  That's much more concrete than just ``protocol'' and ``training''. \textsubscript{01/27/13 3:31pm}}\footnote{$\rightarrow$\textbf{Suko T }I'm really interested to see what will happen from this request. \textsubscript{01/27/13 11:54pm}}

Mr. Jari, here is my list of skills I wish to learn.  Plus some questions.  Please ignore them if they are not appropriate and I apologize for any offense for the stupid questions.  Thank you for your time.


\textit{Training in:}

{
\parskip=0pt
\begin{itemize}
\item Military protocol and discipline procedures
\item Determining which details are important to notice and which are not
\item How to open doors with keypads locking them
\item Group combat and teamwork, so we know what we can do and how to react in stressful situations
\item How to incapacitate/restrain someone without hurting them or killing them
\item How to avoid people shooting at you
\item Using a knife in combat
\item How to disarm someone who is armed
\item Hand to hand combat with multiple attackers or someone who is much stronger than me
\item How to identify different weapons and machines
\end{itemize}
}


\textit{Questions:}

\begin{enumerate}
\item Who is at SAC-09 and what skills do they have that we can learn that we don't know about?
\item Would other members of SAC-09 like to work out with us?  A regular exercise regimen is good for everyone.  More people to spar with would be helpful, especially since I would do best if I could spar with someone who is not one of my immediate superior officers.  And not a Citizen either, because I really am not supposed to hit them unless they are a threat. 
\end{enumerate}



Thank you.



Hayley

Constable Trainee


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/23/15 11:04pm
\end{flushright}

