\setcounter{chapter}{ 13 }
\chapter{\textbf{Shore Leave} }




\subChapterTitle{``Swan Lake''}

\deets{Suko \& Rebecca}{January 23rd, 2013}



Many awkward conversations.  We learn things.  Now if only we'd actually \textit{talk to each other}....



Please comment, amend and append... you know the drill :D



\jumpHeadline{Timing notes: } 



It's all in the timeline (which you're welcome to change if the timing isn't right), but since it came up, I thought it might be useful to recap some timing highlights for context:



It has been approximately:

6 days since Jonah and Jaya went in the Tank.  

9 days since Oliver and Hayley went in the Tank.

22 days since Jonah woke from his coma.

25 days since Oliver died (but got better).

26 days since we found SAC-01.  

34 days since Cyril Magnin \& Cardoza where the Orc slaughtered Lackovich's first squad. 

and only 46 (not 60 like I misremembered) days since our very first mission (to find Victor)



I can probably pad out a few days here and there but it's not likely to add more than a week given the scripted timing of several events.  It's amazing we're keeping it together as well as we are, honestly.  Morgan may wish to consider hiring a psychotherapist or use those resurrecting drugs more often for their amnesia side effects...



\jumpHeadline{Shore Leave } 


\sceneHeadline{\hl{Shore Leave: Hayley} }\footnote{\textbf{Suko T }Thanks for taking the notes for this section Rebecca.   Heh, I think now you understand when I whine about all the talking- it's murder to keep up with it, isn't it? :D  Recording both expression and word choice is tough.  Something is always going to get missed and dropped.  Thankfully the fact that everyone can edit and amend these docs will usually fix the most egregious errors.  Go power of communal review go! :) \textsubscript{01/25/13 2:18pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{01/27/13 4:00pm}}

Hayley goes to see Gillian, who has temporarily moved to Terminus and is staying with a friend until her new quarters are habitable.  Hayley waits for a few hours at the friend's house and then is told to meet Gillian at one of the Citizen clubs in the area.  Hayley, familiar with this sort of place, changes into appropriate clothing, freshens her toilette and heads over.  



The club is fairly busy.  She finds Gillian chatting with some other ladies of her social group.  Gillian acknowledges Hayley with a nod and returns to her conversation.  Hayley gives a friendly wave to some of the other bodyguards that she recognizes from other Citizen socializing occasions and waits patiently.  After a while, Gillian excuses herself and Hayley follows.  They greet each other, and Hayley says that she has been worried about Gillian and is glad that she is still alive.  Gillian leads Hayley to a room with tables tucked into discreet alcoves, designed for private conversations. 



Hayley looks at Gillian expectantly, ``Did you have something you needed me to do?''

``No.  But update me.''

``Okay.  But first I have to ask a question.  What does 'compromised' mean?''

Gillian looks concerned, ``Are you compromised?''

``No, but I heard that you might be.''  Gillian looks taken aback. ``So I wanted to know if it's a bad thing.  It sounded bad.''``Who said it?''

``Agent Morgan.''

``Yes.  I suppose she would,'' Gillian looks frustrated.  ``People have always had it out for me.  She underestimates me.''

``Well she doesn't really know you.  She hasn't really had a chance to.  She's always at the station.''

Gillian looks surprised, ``Really?  It seems like she's everywhere.''

``Well she does have a lot of informants everywhere.''

``Hmmm, well perhaps because I know her name, I notice her everywhere.  I hear of her meeting with Senators all the time.''

``Oh, is there a connection between Agents and Senators?''

``Well someone has to pay the bills.''

``Oh.  That reminds me.  I have question.  When you said that people were interested in talking to Citizen Langdon's son, who were they?  Can you tell me?''

``Yes of course.  Let me think.  The Security Triumvirate for certain, and some Senators.  People interested in that whole sordid mess with DeVries.''

``Can you tell me their names?''

``Why do you want to know?''

``I think it would be useful.  It seems like various Senators keep appearing in our lives and you told me to look for patterns.  It seems like it could be useful to know the names so I can ask others who they know.''

``Which Senators?''

``The ones in the Security Triumvirate, Senator Marechenko, Senator Bennett and Senator Timmons.  I don't think Senator Bennett likes Constable Langdon's father.  Ahh.... oh, remember in my report where we were in Cardoza and there was another Patrol Group there sent by another Senator?  The ones caused problems for us?''

``You mean they sent the other Patrol Group?''``Oh no, I don't think so.  I think it was someone else.  But it would be good to find out who.''

Gillian thinks.  ``I can give you some names, but I want to think carefully about what I want to share.  With you reporting to Morgan, that makes things difficult, although I think in this case it will be okay.  There is a lot to keep track of.  I am certain Agent Morgan is doing the same thing.''

Hayley smiles, ``She seems to think a lot like you do.''

``I'm not sure how to take that,'' says Gillian, then continues, ``Is there anything else?''

Hayley shifts uncomfortably in her chair and looks away. ``May I ask something?  It hasn't come up before, so I don't know how to ask about it.''

``Go ahead.''

``Is kissing people without payment okay?''  Hayley babbles nervously over Gillian's surprise. ``I ask because I know I am very valuable, so I don't want to be devaluing myself.''

``Was this an order?'' 

``Oh no!  I wanted to.  I asked permission!'' assures Hayley anxiously.

``So are you actually interested in someone?'' asks Gillian, still sounding shocked.

``Yes,'' says Hayley, smiling.

``Who?''

``Constable Gemayel.''

``But you work with him.''

``Yes.''  \textit{Pause}.  ``I don't understand, is that a bad thing?''

``Well, workplace relationships... you know how these things --'' Gillian realizes who she's talking to, and stops herself mid sentence.  ``Er, well if you should decide you don't like each other anymore, it could get awkward and affect your ability to work together.''

``Why?'' asks Hayley, uncomprehending.

``Well maybe not for you, but he may feel awkward.''

``Oh,'' says Hayley, still not really understanding.  ``Um.  We're only supposed to kiss in the exercise room.  Does that help?''

``Well don't tell Morgan.''

``Why?''

``She might frown upon it.''

``Is this a military protocol thing?''  Hayley frowns.  ``It is so very confusing, I need to learn more about military protocol.''

``If you need a young man of your own, we could probably arrange something,'' offers Gillian, seeming to have her equilibrium back.

``Why would I want that?  I wouldn't know him.  How do I know if I would like him?''

``Ah, well, there is that.'' \textit{Pause}.  ``Is he serious?''

``I don't know.  He hasn't asked me to marry him, if that's what you mean.''  Hayley thinks hard and adds, ``And he hasn't asked me to have sex with him either.  So maybe he isn't very serious.''  She looks a little sad at that realization, but shakes it off to say,  ``I won't kiss him if you don't want me to.''

``I don't,'' says Gillian firmly.  ``Is there anything else?''

``Yes!  Did you know if I ask to learn something, they will teach me?  And it doesn't have to be directly related to an order either.  Is there anything I should learn?''

``Number one thing is to be safe.  Learning physical skills to keep yourself safe is good.  And learn your numbers better.''  Gillian sighs.  ``It's not a question I can answer in a specific sense.  Do you like anything?  Are you finding anything particularly interesting?''

``Not really, but I will work on it,'' says Hayley earnestly. 

``It could be more than one thing you know.''

Hayley looks a little alarmed, ``I'll start with just one.''

``Anything that won't get you killed or hurt.  You should also learn what skills are required to command at the TA.  If you could become a batsman to your commander, make yourself indispensable, that would be good.''

Hayley nods.  ``I have one more question.  Why does mentioning Nicklepan upset people?''

``We were at war with them and many people died.''

``Yes I understand that, but why is war upsetting?  People die all the time.''

``The ones who die have people who care about them.  War is very straining on the psyche, or so I hear.  It is hard on those who get hurt --''



At this point, Octavia walks in the room, looking gorgeous as always.  Hayley immediately stands and curtsies respectfully.  Gillian also stands and gives a socially appropriate curtsey.  Octavia asks to speak to Gillian.  Octavia \hl{asks}\footnote{\textbf{q.google }It came across as a strong hint rather than an ask, and Gillian deliberately standing ground on it. \textsubscript{01/27/13 4:06pm}}\footnote{$\rightarrow$\textbf{Suko T }It was certainly an unspoken ``how much do you trust/rely on this servant-class person?'' ``I trust her this much'' message going on between the two of them. \textsubscript{01/27/13 11:58pm}}\footnote{$\rightarrow$\textbf{q.google }I heard it as: ``Your servant shouldn't be here, this is a serious matter'' ``I think I'll keep her here thanks''. \textsubscript{01/28/13 11:33am}} if Hayley should be excused, but Gillian says she can stay.  



``Lady Vorrutyer, we received your request to visit for a bit with Lord Stanislav.  We will provide security according to your accommodations.  You wish to stay for a week, correct?  And you have some staff you would like to bring with you?''

``Yes, if it won't be too much trouble,'' replies Gillian.

``Oh no trouble, just let us know how many and if they have any special accommodations needed.''

``Thank you,'' says Gillian.  ``Could you give us a moment?''

``Of course,'' says Octavia \hl{graciously}\footnote{\textbf{q.google }Again, to me, Octavia seemed slightly put out by being asked to give way to Hayley. \textsubscript{01/27/13 4:06pm}}\footnote{$\rightarrow$\textbf{Suko T }To be fair though, she should be, it was somewhat rude and also pointed.  Definitely a ``you are doing me a favor but you don't own me'' message there, at least that's what I was getting. \textsubscript{01/27/13 11:59pm}} and steps away from the table.



``Do you think you could get 2 weeks off?'' Gillian asks Hayley intently.

``I've never asked for that long of a break, I don't know if I can.''

``Do it.  I'll send you the tickets with the exact dates soon.''``Yes of course, I'll make the request as soon as possible,'' says Hayley.



Gillian goes to speak to Octavia and Hayley stays a respectful distance away, keeping an eye on anyone else entering the room.  She also observes Octavia's graceful movements and lovely face with admiration and some wistfulness.



Octavia walks up to Hayley. ``I understand you will be joining us.  Very good.  There is some paperwork for you to sign.''

``But I'm not allowed to legally sign most documents --'' says Hayley, looking a little alarmed.

``Don't worry, \hl{it will be fine}\footnote{\textbf{Nathaniel Ford }I may have muffed this but she actually said, ``Don't worry, we will find you.'' \textsubscript{01/25/13 9:54pm}}\footnote{$\rightarrow$\textbf{Suko T }She did say that, but I am fairly certain she also said it would be fine, which was the part that was important to Hayley (and thus what I remember).  I can change it the former is what you intended.  Really Hayley doesn't care, so long as she told them that she can't sign things.  How they figure out how to make it work is not her problem :D \textsubscript{01/25/13 10:01pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I want to say it was this, ``It will be fine. You needn't worry; we will find you.'' \textsubscript{01/26/13 12:46am}}\footnote{$\rightarrow$\textbf{Suko T }Works for me! \textsubscript{01/26/13 1:28am}}\footnote{$\rightarrow$\textbf{Suko T }Also, I hope I can work out the situation where I can actually relay this message as spoken since there are those who might be alarmed that Octavia could so easily find Hayley... y'know secret base and all... :D \textsubscript{01/28/13 12:00am}}. You needn't worry; we will find you,'' says Octavia sweetly but firmly.

``Okay.''



Octavia leaves and Hayley watches her leave, sighing a little.  Hayley escorts Gillian to her next appointment and departs back to SAC-09.


\sceneHeadline{Shore Leave: Oliver }

Oliver calls up his friend \hl{James Ogleby}\footnote{\textbf{q.google }Noting, because we weren't certain about this: James Ogleby is the one who rescued Oliver at the battle of Transit Minor after he'd been shot.

(Yes, it's also on the Character spreadsheet.) \textsubscript{01/27/13 4:08pm}} and asks to use his home in Cardoza.  James is happy to oblige and grants Oliver free run of the place, sympathizing with the need to get away from ``the parents'' every now and again.



Dr. Gerhauser subtly arranges to have her own room, and they make plans to meet up again for dinner.  She goes to settle in and after a bit, Oliver can hear the sounds of her playing the harmonica.  She's not amazing but she's not too bad either.  



Oliver makes arrangements for a meal out on the balcony.  The reality of the situation begins sinking in.  This ``started as a journey of revenge against life'' but now he's on a date.  He paces, tries on several different outfits, and tries to read a book to pass the time.  



He goes to talk with the footman to get some information on the local scene.  The footman says there is a music performance that night at the Chapter House.  It's a quartet from Anglia, so Oliver doesn't think that will work.  There was a footrace last week but nothing scheduled for this week so far as the footman knows.  There's a museum in town though.



Oliver gets a glass of wine and then walks out onto the balcony, instinctively evaluating its defensiveness.  He checks for possible sniper positions and visibility (which is fairly good) and then sits with his back to a wall.



Dr. Gerhauser walks in, dressed in slacks and a black tunic.  Oliver gets the impression that this is what she is usually wearing under her doctor's coat.  She's carrying a small book.  She looks a little surprised to see Oliver dressed up and asks, ``You nervous?''

``No,'' lies Oliver.  ``Yourself?''

``Well, I am now... but....''

``Wine?  I didn't know that you played music.''

``Yes, it helps me think.''

``What were you thinking of?''

``Work.''

Oliver laughs, ``I guess you can take the doctor out of the lab, but not the lab out of the doctor.''

\textit{\textless Awkward pause\textgreater }

He turns and gestures to the city below, ``How about that view?''

``It's fine,'' says Dr. Gerhauser politely, looking around.  She doesn't look impressed but she isn't disdainful either.

``Well I can't take credit for it.''

``You should.  Why not?''

\textit{\textless Awkward pause\textgreater }

``What would you like to do?  I haven't planned anything past this dinner,'' says Oliver.  Dr. Gerhauser shrugs, ``I don't know.''

\textit{\textless Awkward pause\textgreater }

Oliver indicates the book Dr. Gerhauser is holding and asks, ``What are you reading?''

``Less reading, more writing.  Or re-reading.  It helps me think,'' Dr. Gerhauser pauses and says a little awkwardly.  ``Sorry, I shouldn't have brought it, I suppose.''

``Well if you read it during dinner, I might complain,'' teases Oliver.

``Do you find that to be a problem with your dates?'' asks Dr. Gerhauser curiously.

``No, I haven't been on a lot of dates recently,'' admits Oliver.

\textit{\textless Long awkward pause\textgreater }

``So you've dated a lot then?'' asks Dr. Gerhauser.

``When I was younger.''

``Strange.  Most of your compatriots are married.''

``You mean my squadmates?''

``No.''

``Ah, you mean the other Citizens in the TA.  Let's just say that I never made corporal and my career trajectory....'' Oliver trails off and then adds, ``Or maybe I just never met the right person.  Depends on if you ask my father or myself.''

``So he's a romantic then,'' says Dr. Gerhauser with a straight face, but then joins him in laughing.

She asks, ``My sister... what kind of guy do you think would be for her?''

``I can't guess who your sister would like.  But why your sister and not yourself?''

``You indicated a correlation between rank and prospects.''

``What rank are you?''

``Nothing in the TA,'' says Dr. Gerhauser and then offers, ``But I'm a 3rd Rank Master at the Academy.''  There is a small pause and she asks, ``do you read?''

``Sure, sometimes.  I brought a novel with me, the Red Gate.  Have you read it?''

``No, I have quite a queue of books to read \hl{{[}from the Academy{]}}\footnote{\textbf{Suko T }I think I missed part of this sentence so I'm just guessing here. \textsubscript{01/25/13 11:35am}},'' says Dr. Gerhauser with a heavy sigh.

``What would you change?'' asks Oliver curiously.

``Don't get me started, your entrance requirements \hl{are ridiculous}\footnote{\textbf{q.google }I'm curious whether she means ``too hard'', ``too easy'', ``too sexist'' or something else.... \textsubscript{01/27/13 4:24pm}}.''

``Have you always been studious?''

``No. I was a child once.''

``Yeah... I didn't think I was, but my father would say I still am.  It's all a matter of perspective.''

``Hmm,'' comments Dr. Gerhauser.



Food is served. 



``Do you dance?'' asks Oliver.

``Not if I can help it.''

``Probably for the best,'' says Oliver, and then gestures to his leg, ``these days I have two left feet.''

``My sister liked it,'' offers Dr. Gerhauser.

``I thought perhaps we could go to a museum tomorrow.  I haven't been in a long time.''

``I don't know your art.''

``Yeah, you probably still know more than I do, you seem the sort who remembers things well.''  Oliver continues briskly, ``So, we'll start in the morning at the museum, then have lunch and then head back.''

``Okay.''

\textit{\textless Awkward pause\textgreater }

Dr. Gerhauser breaks the silence by asking, ``So did you grow up here?''

``Yeah.''

``Did you like it?  No offense but it seems a little dreary.''

``It seems so now, but maybe any place where bullets aren't flying at your head seems nice now.''  Oliver smiles and amends, ``although I suppose bullets were flying here too now.''

``That was an interesting thing you found.''

``What was it?''

``A \hl{track switching device}\footnote{\textbf{q.google }I want to know more about this. \textsubscript{01/27/13 4:25pm}}, one that could be used remotely.''

``Does Trenton know how it works?''

``That's another interesting find.''

``Yeah, he's an odd fellow.''

``True.  \hl{It's not often that you find people who are that attractive and smart at the same time}\footnote{\textbf{q.google }She really walked right into that. \textsubscript{01/27/13 5:44pm}}\footnote{$\rightarrow$\textbf{Suko T }I didn't transcribe the rest of the dialog there which I think went on to say that usually you get one or the other (smarts or looks) but not both.  Which was really just digging the hole deeper.  Hilarious! :D \textsubscript{01/28/13 12:02am}}\footnote{$\rightarrow$\textbf{q.google }Yes, and that it was curious the two didn't overlap more, since she expected people would be selecting for both.

{[}To which I would reply: they aren't necessarily.  In particular people may want ``prettier than I am'' but they don't necessarily want ``smarter than I am''.  And even if they are they can't necessarily \_get\_ both.  Add that ``pretty'' varies by taste and culture, and you end up with much more of a mix.  But we likely have many more people to read on this subject than she does, and certainly many more people debating it.{]} \textsubscript{01/28/13 11:37am}}.''

``Well I guess it's like finding someone who is attractive and a good shot,'' says Oliver, sounding a little piqued.

Dr. Gerhauser goes a little white, then her expression goes blank and her face flushes red.  ``Uh, right.  I don't actually like working with him.  I like working with Victor better.  He's quiet.''

``Who?''

``Victor, you brought him in from the Bucket on one of your missions.  You bring me all the smart guys.  He had some ideas at the Academy that turned out to be right.''

``What's he doing with Trenton?''

``Mathematical theories.''

``So he wasn't just some random guy.''

``My sister does very little that is random.''

There's another small silence and Oliver picks up the conversation, ``so have you never been to Cardoza before?''

``No.''

``Well I thought tomorrow we could walk through the Promenade a bit so you could see the city.''

``I'd like that,'' says Dr. Gerhauser and then excuses herself to turn in for the night.  \hl{She leaves behind her book}\footnote{\textbf{q.google }Freudian slip?  It seems a very strange thing to do \_completely\_ by accident.  There are a handful of things I consider so valuable I notice immediately if they are missing.  If this is not such a thing for her, why didn't she leave it upstairs where she wouldn't have had to answer questions from Oliver?  If it is such a thing why did she leave it behind?  I can't put down the notion that, even if she didn't completely intend to do it, it's not a total accident the book got left behind. \textsubscript{01/28/13 11:43am}}.



Oliver remains out on the balcony and smokes a cigarette, something he does rarely, and waits almost half an hour before opening the book.  It is filled with tightly written notes, some comprehensible, some not.  There seem to be quotes from books written at 90 degree angles to the main text.  It seems to be mostly about technical matters, maybe some mechanical things as well.  Scattered randomly among the book are sketches of people: Rook, Larissa and Oliver.  They're not super good but they are recognizable.



As he flips through the book, a photo falls out of the book.  First Oliver takes it for a drawing, not being very familiar with photos.  It is made of a hard, yet flexible substance, and feels very durable.  The picture is of three girls, sitting on a fountain.  They are teenaged, probably a few years apart.  All of them have red streaks in their hair, although their actual hair ranges from blond to brunette.  It is possible that \hl{they are the Gerhauser sisters}\footnote{\textbf{q.google }If they are the Sisters G, there is at least one not present in SAC-09.... \textsubscript{01/28/13 11:39am}} but it's not certain.  The photo was taken at night, and the fountain they are sitting on is large and lit up with lights.  Their clothing is strange, it seems to be some sort of fitted jumpsuit, but stylish.  The girls seem happy.



Oliver takes the photo and \hl{places it on the book}\footnote{\textbf{q.google }I thought that was well done. \textsubscript{01/28/13 11:40am}} and then goes to Dr. Gerhauser's room.  He knocks and when she opens the door, he hands both to her and says, ``You left this outside.''

``Oh,'' she says and pales.  She takes the book and photo and closes the door without another word.  Oliver stands outside the door for a moment, with mixed expression- half smiling, half frowning and then goes to his room.



The next day, Dr. Gerhauser makes a concerted effort to keep up the conversation with small talk.  She keeps the conversation light and asks only superficial things, shying away from anything personal.  The day is very stilted and after lunch Oliver sees Dr. Gerhauser off on the train.  He says that he has a few more things to take care of in Cardoza and she just nods and they part ways.



Oliver proceeds to get wasted at a local slightly seedy bar, almost getting into a fight, and ends up taking someone to a hotel room for the night. \footnote{\textbf{Adam Kenney }I think I said he actually did take someone back to his hotel room. Which is going to be awkward the next time Dr. Gerhauser asks her baseline questions. \textsubscript{01/26/13 9:34am}}\footnote{$\rightarrow$\textbf{Suko T }Oh really?  Ah so it was just the fight that he avoided.  Yes, that will be fun :) \textsubscript{01/26/13 4:45pm}}\footnote{$\rightarrow$\textbf{q.google }Frankly if it's \_not\_ awkward that bodes worse for the overall relationship.... \textsubscript{01/28/13 11:44am}} He barely makes it to the last train to SAC-09.


\sceneHeadline{Shore Leave: Jaya }

Jaya heads to L.A. Ink, eager to see her sister and \hl{wash away the bad memories from her time in the Tank}\footnote{\textbf{q.google }Drowning her sorrows in ink. \textsubscript{01/28/13 11:44am}}.  She walks into the tattoo shop, tosses her bag on a chair and gives Padme a big hug.  Padme is tattooing a customer and only barely gets the needle away from their skin in time.

``What's up with you?'' says Padme, suspicious of Jaya in such a good mood.

``I'm just excited to see family.  How is...uh....my nephew?'' says Jaya, \hl{obviously forgetting his name}\footnote{\textbf{q.google }This is an interesting trait she has.  It's easily explained out-of-game: there's no reason for any of us to remember the name of a character who has had all of ten seconds of attention during the game.  But if you play it straight, Jaya appears to me to have the most trouble with the names of people she isn't sure how to manage, specifically her most challenging subordinate (''Long John'') and the child her sister tries to pressure her with into having children of her own. \textsubscript{01/28/13 11:49am}}.

``He's fine, he's being watched in the back.''  Padme finishes the section she was working on and then kicks the customer out and tells him to come back later to have it finished.  ``So really, what's up with you?''

Jaya protests, ``I'm just excited to see you. And I have money, so you should be excited to see me!''

``Well that's good,'' says Padme, resting her hand protectively on her belly.

``You sure?'' asks Jaya, indicating her belly.

``Yeah.''

``Cheers!'' says Jaya, pouring herself and Padme a drink. ``You are like a machine.''  Jaya tosses back the drink and pounds her fist on the table emphatically.

``You seem upset.''

``No.  So how do you do it?  I mean, how come they keep coming back?''

\hl{``Well if you leave them smiling... they usually don't mind coming back.''  Padme sighs, ``That's your problem Jaya, you leave them exhausted.''}\footnote{\textbf{q.google }This is an amazingly good line :) \textsubscript{01/28/13 11:50am}}

Jaya smirks and then moves onto her latest tattoo request.  ``I want you to put the word 'loyalty' right here under my ear.  I know there's not a lot of room, but I know you can work it in.''

``Loyalty?''

``Yeah, it's important!'' says Jaya as she casually starts buzzing off her hair on that side.  She stops partway through when Padme says she's ready to start.



Padme starts the tattoo and then stops.  ``Did you get shot??'' she says with some shock and concern.``Yeah but I got better, it's fine.  It's part of the job you know.''

``Are you \textit{on }something?''

``It's only uppers.  You know, good clean shit.''

``You know if you ever want to talk about this...''

``There's nothing to talk about,'' says Jaya firmly.

Padme continues with the tattoo then points to a spot behind Jaya's ear.  ``There's a little space back here, should I add something?''

``No, just 'loyalty'.  It's important.  \hl{I know you have my back and I have yours}\footnote{\textbf{q.google }Jaya's tone here emphasized ``you''. \textsubscript{01/28/13 1:40pm}}.  High five!''

Padme high fives her and says, ``Business is good, I get a lot of folks from your area --''

``TA chumps?''

``Yeah, a lot of people rolling through.  Things are okay.  Water prices are sky high but a lot of people are taking contracts though.''

``If you ever stop having kids, you should think about coming to work for the TA.  I could talk to, uh.... someone....''

``I don't know, it's just you, me and seven kids.  Well I guess I don't have to worry about two of them,'' says Padme with somewhat chilling practicality.

Jaya frowns a little but says nothing.



Padme breaks the small silence, ``So how's base life?''

``Good, good.  I''m getting some respect, and picking my missions.  It's pretty good, I'm getting more money...'' Jaya trails off, muttering something under her breath like a mantra.  ``They are doing some crazy brain drug stuff.''

``Crazy brain drug stuff??'' says Padme.

``But they pay for it.  \hl{There's a bitch on base but I'm going to own her.}\footnote{\textbf{Nathaniel Ford }More than anything, I want to see how the Jaya-Lackovitch relationship resolves. \textsubscript{05/27/14 12:44am}}  I own that base, well except for the ones in charge.  But otherwise...''



The sisters continue to banter until Padme finishes up the tattoo.  Jaya makes a hasty escape before she can get roped into babysitting and goes to a bar.  She scores some drugs from a new supplier, low grade stuff.  They talk a bit as Jaya susses him out.  He asks if she'd want a regular supply and offers to deliver it to her.  Jaya declines but he presses the issue and offers again.

Jaya drops the casual attitude and leans forward.  She speaks slowly and deliberately, with menacing intensity, ``\textbf{No deliveries}. You don't come to my place, you don't talk to my friends, you don't deliver anything.   I pick up my own shit.''

Cowed, but never dropping his smile, the guy agrees and Jaya sits back, all smiles again herself.


\sceneHeadline{Shore Leave: Jonah }

Jonah meets up with Zara, with his package of\hl{promised items ready for trade}\footnote{\textbf{Suko T }The relevant section from Session 05 for context: {[}Jonah{]} asks Zara for a subway map but one of the old ones, a higher quality one than the ones you get for free at the train stations.  Zara says he may be able to find something like that.  His first price is 3 flashlights and the name of the person who gave Jonah the flashlights.  He then reduces that to 3 flashlights and just the name of the station where Jonah got the flashlights.  They haggle a little longer and then settle on one TA flashlight now, and two on delivery and Jonah asks his contact if they'd be open to working with Zara.  Zara asks Jonah if he knows anything about the (presumably) elite team that those flashlights came from.  Jonah is not willing to sell that information at this time. \textsubscript{01/25/13 2:29pm}}.  Zara is playing a simple game which seems to involve using a stick to hit rocks into specific targets in an alley.



Zara greets Jonah, ``Good to see you, I think I made progress on your request.  Did you need the original?  People lock up that old paper pretty carefully.''

``No, I don't need the original.''

``Good, I thought so.  It's a copy, a little smaller than the original.  Some spots were kind of illegible or damaged but we marked those.  The guy I use is pretty good.''

``As long as it's legible and accurate.  If my buyer likes it, he may want more, so tell the guy you use that he may get more requests.''

``Sure, he'd like that.  More work is good.  He doesn't want to go to the plantations.''



``So how is life going?'' asks Jonah.

``Good.''

``Say have you heard anything about the Cardoza thing?''

``Cardoza?  Man that was crazy.  \hl{I hear there's going to be public executions or something}\footnote{\textbf{q.google }I wish I'd had time to ask more about that. \textsubscript{01/28/13 1:44pm}}.''

``Interesting.  What about the Annex?''

``Eh the rich people aren't interested in what goes on there.  It's pretty much blown over.  Lots of people signing up to work on the plantations though.  Water prices are still really high.''

``I heard that the TA pounded on some people there.''

``Yeah I guess there was some of that.  But the water shortage was really bad.  Prices are high but the situation is getting a bit better.  Anglia has been really good for us.''



Zara first asks to see the flashlights.  \hl{Jonah takes them out and demonstrates them.}\footnote{\textbf{q.google }These are taken from SAC-09.  They were deliberately chosen from the throwaways, both because they are less likely to be noticed, and because the general high quality of most of the gear would be too revealing otherwise. \textsubscript{01/28/13 2:13pm}}  They are of varying quality and appearance but they all work.  Zara is impressed by the quality.   He doesn't ask about where they came from this time, and \hl{Jonah doesn't volunteer it}\footnote{\textbf{q.google }Nate, if you want Zara to ask about this we can retcon or you can ask me next time.  I'll need help coming up with a suitable answer!  We can also retcon the deal, since the informal protocol this time seems to have been: you can ask about the other person's sources for context but you can't try to identify them directly. \textsubscript{01/28/13 2:11pm}}.  They agree that Jonah can get more at some point if Zara wants.



Zara takes out the map and shows it to Jonah.  It has the usual TA Directorate map lines but there are many extra lines, some of them intersecting the known lines at 90 deg or 45 deg angles.  There are some labels too: Directorate, Anglia, Nicklepan.  Jonah takes the opportunity to show Zara one use for the flashlights: reading old maps.



``This was in the \hl{300 year section}\footnote{\textbf{q.google }This can be interpreted as ``from the year 300'' or ``300 years ago''.  Neither notion makes much sense to the speakers, as they don't track time that accurately (per conversation with Nate about calendars).  Zara emphasized that he wasn't sure what the term meant. \textsubscript{01/28/13 1:46pm}},'' says Zara.  ``One contact I have swore that the Nicklepan part of the map is wrong.  He said he went there as a kid.  Said the stations are backward.  Stuff like this station here on the edge, City Station A, was actually in the middle.  And some stations are missing.  He couldn't find Transit Station.''

``You mean Transit \hl{Minor}\footnote{\textbf{q.google }Also from clarifying with Nate: ``Minor'' is just a word.  People in the Directorate at large don't think of there being a corresponding ``Transit Major''.

(Come to think of it, do they even know what ``Transit'' means?) \textsubscript{01/28/13 1:47pm}}?''

``Nah some other station.  He said he heard a rumor that this was an important station. Everything went through there.  Everything connected to it, it was practically its own Directorate.''

``Hmmm.  Okay, I'm not asking for a source, \hl{but is this coming through the Academy}\footnote{\textbf{q.google }Jonah wants to know if this is what the Academy thinks so he can compare notes with Trenton.  He's not sure yet whether Academy people really know anything useful - both in general and in this specific case, since its possible Trenton may have already seen them if they are from there.  (He hasn't but Jonah doesn't understand the scale of the Academy.) \textsubscript{01/28/13 1:49pm}}?'' asks Jonah.

``Apparently there's some guy there. They talk about that stuff.  And then people argue with them.  Can you believe they get paid for that?  For people to argue with them?'' Zara shakes his head in disbelief.  ``This is the oldest map I could find.  Oh and the guy says that there should be a station between Gateway and Burroughs.''

``What?  How can you lose a station?  It's one thing if one was blown in the war or something but this is one is right between two other stations!''

Zara shrugs.  ``Bricked over or something, I guess.''



Jonah decides to steer the conversation back to the Annex incident.  ``I have a friend who was hurt there.  He described something weird about one of the TA people.  Could you look into it?  Find out who it was that hurt my friend?''

``That's not really my area...'' hedges Zara.

``Just if you hear something, could you let me know?''  Jonah emphasizes this isn't a request to seek out information, \hl{just keeping an ear to the ground}\footnote{\textbf{q.google }This may or may not be an unusual request.  I'm trying to emphasize that this one Jonah's regular reliable contacts.  They tend to do well by each other and throw useful business each other's way.  Of such informal networks is most commerce made. \textsubscript{01/28/13 2:18pm}}.

``Sure, I could do that.''



Jonah and Zara complete their transaction and part amicably.  Jonah makes a simple copy of the map and then stashes the original in a safe place (not his apartment).  He takes care of a few errands and catches the last train back to SAC-09, running into Oliver who is waiting for the same train.





\sceneHeadline{SAC-09} 



Returning to base a whole day before any of the rest of her squad get back, Hayley goes immediately to speak to Jari and asks how she makes a request for time off.  Jari advises her to just talk to Agent Morgan directly.  Hayley puts in a request for a meeting with Agent Morgan but it is not responded to.  Under Jari's advice, she then tries to meet with Agent Rook but he's not on base at the moment.  She puts in the requests again, and goes to the exercise room.



Hayley spends the day working on the exercise room, making a list of required equipment or at least items that they could use.  She's excited to finally be able to go through her full exercise regimen.  If anyone stops by, they will probably see Hayley running, doing some weird stretching exercises and practicing her ballet exercises.  She is often frowning about how out of practice she is.  She pushes herself hard, perhaps harder than she should, clearly working out some emotional issues through sheer exhaustion.  She exercises and practices until she is practically passing out with exhaustion, showers, sleeps, and then she wakes up early and returns to the exercise room and continues to work out.



Jaya returns that morning and immediately goes to Ops.  Morgan is there, \hl{looking angry}\footnote{\textbf{q.google }It seemed obvious at the time but since I may be wrong, and we may not remember: it's not clear what Morgan is angry about.  She didn't call Jaya up, so she's not angry at her, and in any event her attitude towards Jaya seems harsh mostly by coincidence. \textsubscript{01/28/13 2:20pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Not that that subtle difference particularly mattered to Jaya... ;-) \textsubscript{01/29/13 5:16pm}}\footnote{$\rightarrow$\textbf{q.google }Of course not.  It matters to the audience so they can talk about it on the boards! \textsubscript{02/13/13 8:53pm}}.  She indicates the bandage on Jaya's neck. ``May I ask what happened?''

``I got a sweet tattoo,'' says Jaya, a little nervous but still proud.

``What are you here for?''

``I wanted to get the details for our mission.  Uh, you know, to hear your final decision on our extra team member, and departure time and stuff like that.''

``Hmm, yes.  About that.  Why did you pick Senior Constable Lackovich?''

``I was assisted in arriving at that decision,'' says Jaya.

``Who assisted you?''

``Agent Rook said she would be the best --''

Morgan cuts her off, ``When I ask you to make a decision, I expect you to make it yourself, and that you be clear in your head about the reasons why.''

``Um... Yes.  Agent.  Sir.  Ma'am.''

``Your team has 8 hours of rest and then they will deploy.  Let me know the moment they arrive back at base.''

Jaya nods and starts sidling for the door.  ``Is that all?''

``No.''

Jaya's shoulders slump and she stops trying to make a break for it.

``Will you be able to work with Lackovich?'' asks Morgan.

``If she is clear that she is to report to me, and follow my orders, then we will have no problems.''

\hl{``I will sign off on this, and I will make the situation clear to her,}\footnote{\textbf{Suko T }I feel like there was some other comment, some sort of warning about how Jaya better not misuse/abuse this additional personnel or something, but I have nothing in my notes. \textsubscript{01/25/13 4:58pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Morgan avoided saying that Lackovich would be under her command, but said she'd make the situation clear to Lackovich. \textsubscript{01/25/13 10:04pm}}``  Morgan says and dismisses Jaya to Jaya's relief.



That evening, Jonah and Oliver show up.  Jaya meets them at the train platform and says only ``You have 8 hours'' and then walks off.



\hl{Jonah and Oliver puzzle a bit over}\footnote{\textbf{q.google }Actually Jonah puzzles over it.  Oliver mostly doesn't care at least overtly (he's still got the weekend with Dr. G. on his mind).  The open puzzling in front of Oliver is deliberate on Jonah's part. \textsubscript{01/28/13 2:22pm}} that unusual behavior but mostly just let it go.



Jaya goes up the elevator to Morgan's office.  She's so intent on rehearsing her report that she hardly notices the elevator door opening.  Dr. Gerhauser walks into the elevator, almost bumping into Jaya.  ``Are you getting out?'' she says coldly.



Jaya quickly steps out of the elevator and Dr. Gerhauser gets into the elevator and leaves.



Morgan is looking very calm, but it's a very tense calm.  Before Jaya can even say anything, Morgan says, ``I know.  Thank you for your report.''

``Oh uh.  Good.  I will go then,'' fumbles Jaya and turns to leave.

``Do you need rest, or can you spar?'' asks Morgan before she can make it to the elevator.

Jaya turns back to Morgan after a quick look behind her and around the room.  ``Yes...'' she says, a little hesitantly.

Morgan stands, grabs her gym bag, and walks over by Jaya, and they stand at the elevator together.  

``Do you mind if I smoke?'' asks Jaya, trying to hide her nervousness.

``I do mind.''

Jaya puts the unlit cigarette in her mouth and fiddles with it nervously.



They go down to the exercise room.  They spar and this time Morgan does not hold back as much as she did before.  She is careful not to take advantage of Jaya's unhealed tattoo, but she otherwise pretty much beats the crap out of her for an hour.  She doesn't do any lasting damage and occasionally will stop herself from kicking Jaya, a reticence that Jaya takes full advantage of (usually to her subsequent regret).



Entirely focused on Morgan, Jaya doesn't even notice that Hayley is in the room.  Hayley stops exercising and watches the two spar with great interest.  She even starts mimicking some of Morgan's moves. 



When Morgan finally calls a halt, Hayley offers Jaya some water.  She watches Jaya panting and groaning and says, ``I think we need to exercise more.  You could really use more stamina.  You should not be breathing this hard.''

``Oh yeah?  Well you try going one on one with Morgan and then you can talk to me,'' says Jaya angrily and then walks off.

``Okay,'' says Hayley to Jaya's back.  Jaya misses Hayley's thoughtful look.



The next morning, the team pulls themselves together and gets their equipment from the Requisition Cage.



Jaya: Notice Aid (vision- range finder binoculars) 2, Basic Uniform 1

Oliver: Notice Aid (hearing- parabolic antenna) 2, Med Kit 1, \hl{Silencer 1}\footnote{\textbf{Suko T }We didn't actually assign him this but we really should have, is this ret-con-able? \textsubscript{01/25/13 4:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Yes. \textsubscript{01/25/13 10:05pm}}, Basic Uniform 1

Jonah:  Armor 2, Med Kit 1, Forensic Kit 1, Urban Camo 1, Basic Uniform 1

Hayley: Armor 2, Rifle 2, Basic Uniform 1



Geared up, they assemble in the ready line room.  Lackovich is there, to everyone's surprise except Jaya's. \hl{Jonah nods at her}\footnote{\textbf{q.google }Within the next minutes he'll become quite clear on it, but as of that instant Jonah still has no idea the rest of the team has had trouble with Lackovich.  They didn't brief him about it and everyone has avoided talking about (or to) her since. \textsubscript{01/28/13 2:27pm}} and she instinctively nods back but catches herself and ends up with an awkward half-nod.



Morgan walks in and Lackovich smartly steps up to the ready line.  Jaya scrambles to do the same and then tries to do one better by saluting.  Lackovich throws her a look and follows suit.  The rest of the team steps up to the ready line.



``This is a recon mission,'' says Morgan.  ``You are to find out what's wrong and report back.  I have attached Senior Constable Lackovich to this mission.  She is to be \hl{used as a consultant}\footnote{\textbf{q.google }I forget who explains that she's a consultant about Nicklepan, but it becomes clear somewhere. \textsubscript{01/28/13 2:29pm}}.''



The train arrives, with Rook at the helm.  The team boards the train, and it takes a few minutes for everyone to work out the seating.  Hayley sits as far away from Lackovich as possible.  Jonah sits near Lackovich.  Jaya and Oliver seat themselves somewhere in the middle.



Jaya asks Lackovich if she's going to stay on the train or if she's able come with them on the missions.  She needles Lackovich, saying that she'd understand if Lackovich is not up for going on such a taxing and important mission.  Lackovich replies that she can keep up with Jaya and the pissing contest ends in a \hl{draw.}\footnote{\textbf{Suko T }Though I'm sure Jaya would say that she won it. :) \textsubscript{01/25/13 5:16pm}}



Seeing that none of the others are doing so Jonah approaches Lackovich to talk about Nicklepan.  He \hl{deliberately defers to her}\footnote{\textbf{q.google }Partly a general policy when trying to get information from someone but also to try and diffuse some of the tension between her and the others that might disincline her to be helpful. \textsubscript{01/28/13 2:35pm}}\footnote{$\rightarrow$\textbf{Suko T }Reviewing Session 4's notes, yeah, he's got the best chance of doing that of anyone on the team, but that's a tough road to take.  Hayley has already pissed her off by asking the wrong questions, Jaya was Jaya and Oliver had actually walked past the wounded Lackovich in Cardoza, muttering ``Useless'' after she couldn't tell him anything about who attacked them, and left her and her dead comrade Rupley on the stairs. \textsubscript{01/28/13 3:09pm}}, calling her by her rank (even though this may risk Jaya's ire), and asks what advice she has.  Lackovich explains that she wasn't in Nicklepan proper but was on the border and knows a little bit about them.  The team will be there \hl{openly as TA officials}\footnote{\textbf{q.google }This has Jonah's internal alarm bells ringing even louder than they are for visiting Nicklepan in the first place. \textsubscript{01/28/13 2:33pm}}\footnote{$\rightarrow$\textbf{Suko T }Yeah, well, sneaky is not our forte.  Wait let me amend that, the half of the group that is not capable of being subtle or sneaky will totally negate the other half :)  So best to just walk in with swagger. \textsubscript{01/28/13 3:10pm}}, so Jonah wants to know if there are topics to avoid or pursue.  Lackovich teaches him a little local slang.  Jonah also asks about local train station names \hl{so as to be able to appear less of a stranger}\footnote{\textbf{q.google }Well, that, and to confirm station names that he's seen on the map he's gotten.  They match insofar as he can tell. \textsubscript{01/28/13 2:32pm}}.  Jonah thanks her and turns his attention to the others.



Hayley calls out to Jaya, ``Senior Constable, do you think we will meet Angela in Nicklepan?''

Jaya has no idea who she's talking about and walks closer to Hayley and asks ``Who?''

``Angela.  You know, the lady we met while retrieving Mr. Hadef.''

``Mr. Who?''

``Mr. Trenton --''

``Ugh,'' comments Jaya immediately. ``And why would we meet her?''

``Because I thought she was a Nicklepan agent.  Wasn't she?''

``Well I don't know about that, but I doubt we'll see her.  It's a big place.''

``It seems like she would have been helpful to find and talk to before going to Nicklepan.''

``I don't know how we'd find her.  And don't even \textit{think} about asking Trenton -- hey...'' says Jaya with dawning suspicion, ``are you only asking about her because you want to see him?''

``What?  Uh, no,'' says Hayley, surprised and confused.

``Yes you are!  Oh my god, you are totally thinking about him, aren't you?''

``No, I'm not, I'm thinking about Angela,'' protests Hayley, but it falls on deaf ears and the conversation dies.



Jaya sits and paces.  Jonah and Lackovich talk.  Hayley practices loading, readying and shouldering her new rifle.  Oliver gives her some helpful tips.



The train gets close to the City Station A and Rook asks Jaya what the plan is for the train.  Jaya says that once the team has left visual contact range of the train, the train should leave, for security purposes.  Oliver and Jonah both contradict, the former arguing for half an hour the latter for an hour.  Jaya tries to split the difference, but Jonah presses her to take Oliver's suggestion instead.  After some negotiation and suggestions from the team\footnote{\textbf{Adam Kenney }Oliver is lobbying for the train to circle back more frequently because he's expecting Nickelpan to turn into a war zone at any moment. \textsubscript{01/26/13 9:44am}}\footnote{$\rightarrow$\textbf{Suko T }Agreed.  Even every 30 min is a rather long time if we are under heavy fire. \textsubscript{01/26/13 4:47pm}}\footnote{$\rightarrow$\textbf{q.google }Jonah agrees. \textsubscript{01/28/13 2:37pm}}, Jaya tells Rook to circle back every 30 minutes, just in case they need a quick extraction.  Rook agrees, barring \hl{unexpected hazards}\footnote{\textbf{q.google }Meaning ``expect it will take longer than that''. \textsubscript{01/28/13 2:39pm}}.



The team readies their weapons.  ``Going in hot, I take it?'' comments Lackovich.  ``Just want to be ready for any situation,'' says Jaya.



The doors open....



\jumpHeadline{City Station A Challenges } 



The Iron Road (Green)

The Stone Road (Green)

The Glass Road (Green)

The Covered Road (Green)

The Bad Road (Red)



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/23/15 11:13pm
\end{flushright}

