\setcounter{chapter}{ 16 }
\chapter{\textbf{Shore Leave \& Backlash} }




\subChapterTitle{``We Call Him Tim''}

\deets{Suko}{March 11th, 2013}



Lots of Shore Leave angst and Competency Tests for the team!  Uh oh....


\jumpHeadline{ SAC-09 Interlude } 



Oliver approaches Jonah to talk about their reports.  Since they were on their own for a while, Oliver wants to make sure their stories line up.  \hl{Oliver is emphasizing the ``find out what happened to Nickelpan'' angle as the reason for bagging one of the enemies instead of trying to talk or immediately withdrawing.}\footnote{\textbf{Suko T }Thanks for adding all this detail Adam! \textsubscript{04/02/13 10:57am}}Jonah says that he's fairly certain that the soldiers who attacked the team weren't Nicklepan.  Without explicitly saying so, they agree to cooperate by putting pressure on management in different areas, without either person's report undermining the other's argument.  Oliver says that he's going to emphasize the need for better armor and weaponry in his report.  Jonah agrees to emphasize the need for more tactical training.



After dragging out her recovery to get a few more days of pain meds, Jaya ends up dictating her report to Swan.  She describes the uniforms of the other soldiers.  She mentions that her radio got damaged and lost.  She goes into enthusiastic detail about her combat with the guy on the roof, and adds that he said something but then she shot him in the face.  She graciously notes that Lackovich didn't fuck up, and reports over and over how proud she is of her team and how well they performed on this mission.



Oliver's report asks for more tech.  He describes seeing the dead bodies and then seeing the forces that likely killed those people.  He says that he brought the body back so that they can find out more about the attackers.  He goes into deep technical detail about the incidents when he was firing upon the enemy (angle of attack, strategies used).  He leaves out any report of dialog. He concludes with another request for more/better tech and equipment.



\sceneHeadline{Shore Leave: Hayley }

Hayley goes to visit Signe, politely sending a message ahead to let Signe know she's coming.  She seems to gain a lot of comfort just by being around Signe, even though they don't talk too much.  She says that she asked for Signe to come to the base but isn't sure it will happen.  Signe says that Trenton won't be able to come see her for a while, which makes her sad.  Signe shows Hayley a stack of letters from Trenton, in a somewhat messy scrawl, with random doodles and drawings in the margins.  Hayley mentions that she will be meeting Tim and invites Signe along.  Signe says that she will go if Hayley feels unsafe but otherwise she doesn't leave the building much.  Hayley says it is not necessary and trots off to her date.



Hayley arrives at the bar where Tim told her to meet him.  She is dressed in her non-TA clothes which are far nicer than what everyone else is wearing in the bar.  There's a lull in the conversation as the bar patrons notice Hayley's entrance, but she is oblivious to their stares and scans the crowd for Tim.  Tim waves her over to his table.  He moves to hug her but stops awkwardly when she doesn't reciprocate the gesture and instead gestures for her to sit.  He has ordered some beer-like drinks and some beer nut equivalents.

``How have you been?'' he asks.

``I am doing well, I am mostly healed.''

``From what??''

``Um, three bruised ribs and a knife wound.''

``What??  I didn't think being a TA agent was so dangerous!  Were you in a riot?''

Hayley doesn't know what a riot is, but when it is explained, she says no.

``Was it a robbery?''

``No,'' says Hayley thinking hard.  ``I don't think we stole anything.''

Tim eventually gives up trying to figure out what went on and tries a different tack, encouraging her to have a beer.   She refuses because she doesn't drink alcohol.  There is a lengthy and somewhat confused discussion on why she doesn't drink and what it does to livers and why would anyone want to poison themselves?  Hayley asks if Tim would be angry if she doesn't drink, and he says no, although his disappointment is clear (to everyone but Hayley).  



Tim asks what Hayley does in her free time, and she replies: exercise, practice and memorizing rules.  She complains that there are just so many rules to remember.  She asks Tim if he has memorized all the rules and he jokes about it but the humor is lost on her.



Part way into his second beer at this point, he tries to convince her to have another drink, which she again refuses, but says that she would accept some tea or water instead.  When he returns with her drink, she tries to pay for her drink but is gallantly refused.

``Do you have a boyfriend?'' Tim asks.

``No.  I'm not allowed to,'' says Hayley to Tim's disappointment.  ``But,'' she says slowly, ``I think it is okay to just have sex with someone.'' which cheers him up considerably.

There is more awkwardness where Hayley discovers that this is supposed to be a date and has to ask Tim to explain what a date is.  She says she has never been on a date before.  They fumble their way through more awkward conversation.  Tim gets increasingly horrified/confused at the details Hayley drops about the injuries she sustains on missions.  

At one point he asks her, ``What station are you at?''

``I don't think I can tell you,'' she replies.  The color drains from his face and there is a long pause in the conversation as he just stares at her.  The pause is long enough for even Hayley to notice it, and she says, ``Oh!  I am supposed to ask you what you do for work.''



Tim says his job isn't that interesting but Hayley asks him to explain and listens with flattering attention.  Tim offers her a job, which Hayley seems pleased by but says sadly that she doesn't think she will be able to work there because she can't choose where she works.  Tim \hl{quickly}\footnote{\textbf{Nathaniel Ford }For some definition of 'quickly' \textsubscript{03/21/13 9:28pm}}figures out that she must be Incorporated.  Hayley offers to leave since she knows that some people don't like associating with people of her class.   Tim laughs and says that she's higher class than anyone in this bar.



They continue to talk and as Tim gets increasingly drunk, he is more and more frank about asking Hayley to sleep with him.  Eventually she figures out what he is asking and considers it carefully.  She says that kissing is okay, but no sex, because she doesn't know him well enough yet.  Tim is okay with that compromise and she helps him back to his place.  They make out, Tim gets handsy but \hl{Hayley is able to keep all her clothes on}\footnote{\textbf{Suko T }I assume.  Because if not, she may have to injure him to keep her scars secret.  And she doesn't want to do that, he seems nice. \textsubscript{03/12/13 1:53am}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{03/16/13 4:22pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{03/21/13 9:29pm}}.



Afterward, she leaves his house and returns to Signe's place.  Signe asks her for the details and they spend the evening going over what happened in great detail.  Hayley spends the night again in Signe's bed.


\sceneHeadline{Shore Leave: Jaya }

Jaya shows up at LA Ink, slightly tipsy from drinking half of her ``Hazard Pay'' bonus, clutching a \hl{500}\footnote{\textbf{Suko T }equivalent to a beer ``40'' \textsubscript{03/12/13 1:40pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }500 cc's? \textsubscript{03/16/13 4:22pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }The term 'cc' wasn't used, but it's about that much. \textsubscript{03/20/13 6:53am}} in one hand.  Padme is sobbing and their aunt is fussing over her. 



Jaya tries to cheer Padme up by dropping a wad of water credits on the table but Auntie tells her that money's not going to help, Padme lost the baby.  This doesn't stop Auntie from taking the money to stash it away though.



``What happened?'' asks Jaya, placing her drink in front of Padme.

Padme sniffles and wails, ``I should have eaten better.  I knew it but I didn't.  You have to eat better.''  Padme looks up at Jaya somewhat accusingly and angrily knocks the 500 to the ground.  Jaya attempts to placate her with more money, but that just angers Padme more.  \hl{``Where were you?  Why aren't you here?'' she yells, getting to her feet.

``I'm working!  Earning money for this family!'' says Jaya, her defensiveness turning to anger.}\footnote{\textbf{q.google }In light of how session 18 ends: parts of Jaya's tank experience are starting to come true, and this is one of them. \textsubscript{04/06/13 1:32pm}}\footnote{$\rightarrow$\textbf{q.google }Which is interesting because, for Oliver and Jonah, the tank experience combined parts of things which already came true, in their pasts. \textsubscript{04/06/13 1:33pm}}

``And getting shot at! Last time you lost most of your ear - what's next?  I can't have someone else dying on me!'' At that, Padme's anger shifts back to misery and she starts crying again.



Auntie returns at this point and yells at Jaya for upsetting Padme at such a difficult time.  



Jaya attempts to pull Auntie aside to find out more of what happened, but Auntie starts hustling Jaya out of the shop.  ``You need to leave.  You are just making things worse.''

``What happened?  I mean it's not like --''

``You'd be upset too if you lost a daughter,'' says Auntie grimly.

Jaya is speechless at this revelation, clearly \hl{the loss of a girl-child hits her particularly hard}\footnote{\textbf{q.google }Because it wasn't obvious to me, noting that all of Padme's surviving children are boys. \textsubscript{04/06/13 1:34pm}}\footnote{$\rightarrow$\textbf{Suko T }Her family is super matriarchal which I assume means that all three of them are devastated by this loss even more than they would be if it was yet another boy. \textsubscript{04/06/13 4:22pm}}.  She leaves the shop without protest.



She heads to a bar and gets into a bar fight that goes poorly since she has forgotten how injured her arms are.  Nursing a few more bruises and cuts, she heads back to SAC-09.



\newpage
\sceneHeadline{Shore Leave: Oliver }

% there's a gnarly page break here because TOO MANY FOOTNOTES!
Oliver returns home.  Their butler, \hl{Jeffries}\footnote{\textbf{Nathaniel Ford }Did we really call him that? Really? REALLY? And by 'we' I mean 'me'. :P \textsubscript{03/21/13 9:30pm}}\footnote{$\rightarrow$\textbf{Suko T }I believe some amount of beer may have influenced this decision. :)  It certainly caused no small amount of laughter at the time. \textsubscript{04/02/13 10:56am}}\footnote{$\rightarrow$\textbf{q.google }I believe you said ``Zhafriz''.  We Anglicized it: cultural influences on psycho-linguistic frameworks are notably strong contributors to audial interpretation of words. \textsubscript{04/06/13 1:36pm}}\footnote{$\rightarrow$\textbf{Suko T }Really?  I thought it was proposed as a joke because it was so awfully cliche, and it was so funny that we just went with it.  No one could think of better and honestly, we had other things on our minds at the time (like the Orc of Anglia!).  It was decided way back in Session 9. \textsubscript{04/06/13 4:24pm}}\footnote{$\rightarrow$\textbf{q.google }No, not really.  I was just having fun spinning up an explanation.  I apparently wasn't being ridiculous enough ;).

(I confess I like ``Zhafriz'' :). \textsubscript{04/06/13 6:12pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Hmm. Seems his full name is 'Zhafriz Jeffries'. Who knew!? ;-D

(Which is to say I like both staying true to the 'source material' and the name Zhafriz, but why not do both?) \textsubscript{04/06/13 6:31pm}}\footnote{$\rightarrow$\textbf{q.google }Oh but that's the whole thing: we already are doing both. The name is \_pronounced\_ the same, it's just the \_spelling\_ that's ``Anglicized'' from an ``Arabic'' form.  It's the same old name, we just happened to transliterate it that way.  We're like a culturally sensitive Ellis Island :P. \textsubscript{04/06/13 8:08pm}}\footnote{$\rightarrow$\textbf{Suko T }Ha!  I like that as a full name.  It is fitting. :) \textsubscript{04/06/13 11:14pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Entered into the character spreadsheet: 

``Zhafriz Jeffries'': It is an interesting cultural footnote that whilst members of the Citizen class distinguish between Mr. Jeffries given and family names, those of the Incorporated and Franchise classes are already cognizant of the explicit duplication: ``Zhafriz'' in the proper pronunciation produces a sound nearly indistinguishable from ``Jeffries'' to most educated and (perhaps ironically) culturally unaware Citizens. Their steadfast reluctance to address the lower classes by their given names prevent them from noticing that the family name is almost certainly therefore a bastardization: written down these two names are obviously different, but the given would never be spoken aloud. This blind spot is not unknown to the lower classes, though rarely mentioned due to societal pressures not to point out the self-centered idiocy that Citizens often engage in. \textsubscript{04/07/13 1:22am}}\footnote{$\rightarrow$\textbf{q.google } \textsubscript{04/07/13 2:15pm}}, answers the door and informs him that his mother isn't there but his father is in his study.  Oliver offers to come back later, but Jeffries says, ``If I may, I know this is very forward, but you may wish to speak to him now.''

``Is everything okay?'' asks Oliver, concerned.

Jeffries makes a noncommittal noise.



Oliver heads to his father's study.  He finds his father there, seated behind the heavy desk that he remembers so well from his childhood.  Antique guns are spread over the surface of the desk and Oliver's father is cleaning one of them.  He doesn't even look up as Oliver steps into the room.

``Didn't expect to see you.'' grouses Mr. Langdon.

``Had some shore leave, thought I'd stop by.''

``As always, we are blessed by your presence,'' says Mr. Langdon, sarcastically.

``How is everything going?'' asks Oliver, gamely ignoring his father's tone.

``I'm under house arrest while the investigation goes forward.''

``That doesn't seem right - it was just the one incident.  How long are you going to be under house arrest?''

``Who knows?  They seem to think I have been using you as a go-between.  They keep asking the same questions.  You're running around who knows where and I'm being hung out to dry.''

At this point Oliver notices the mostly empty bottle of whiskey on the desk and says, ``I can't imagine you'd be any happier if I was shirking my duties.''

``Oh really? What are you doing?  It can't be the front lines because well....'' he casts a dismissive glance at Oliver and his damaged leg. 

``You can do a surprising amount of good behind the scenes,'' says Oliver evenly.

``What can you do?  Do you have proof that I wasn't involved?''

``Well, not as such.  It's all political missions.''

``Really?  Like what?'' says Mr. Langdon.

``We were there to hunt down Cyril Magnin.  It was a TA mission, it was under orders.''

``Oh?  Whose orders?''

Oliver pauses and says, ``What does it matter?''

\hl{``What matters is that my son apparently has friends that he has more loyalty to than his family.  But I suppose in the grand scheme of things, it's fine so long as you are \textit{happy}.'' says Mr. Langdon viciously.}\footnote{\textbf{q.google }I'm starting to think Mr. Langdon is played by Charles Dance. \textsubscript{04/06/13 1:39pm}}

``If I wanted to be happy, I wouldn't be doing what I am doing.''

There is a long pause while Oliver looks at his father, who keeps cleaning his guns and ignoring Oliver.

``Agent Morgan Gerhauser calls the shots, if that name means anything to you,'' says Oliver finally.

Mr. Langdon actually looks a little thoughtful, ``How do I know that name?  Hmm. So she has you doing political work.''

``Some of it in Nicklepan -''

``HA!  Now I know you're lying.'' interrupts Mr. Langdon.

``- Or what is left of it.'' finishes Oliver.

``What??''

``Bodies piled high on the streets, buildings destroyed.  I was there.  I saw it.''

``When was this?''

``A couple of days ago.''

``I don't believe you,'' says Mr. Langdon sneering at Oliver.  ``It's too far fetched.''

``You'll believe me when you hear it in the news soon.''

``Your mother will be home in a few hours for dinner.  Best that you aren't here.'' says Mr. Langdon dismissively and goes back to cleaning his guns.

Oliver quietly leaves.




\sceneHeadline{Shore Leave: Jonah }

Jonah meets up with one of his contacts, 'Zhok (Ashok).   'Zhok is a merchant and is Jonah's go-between for getting some of his money to his family without anyone knowing.  Jonah (or Tibari as he is known to 'Zhok) gives 'Zhok money and 'Zhok passes it along to Jonah's family in the form of discounted prices on supplies.



'Zhok offers Jonah his latest price list and mentions that prices have gone up because trade is getting more difficult.  ``You know the Berian war, some 100 years ago?  So we got some stations from them, but trade is falling off.  There's some trade from Anglia but not enough.''

``What about Nicklepan?'' asks Jonah.

``Since the war, not a lot of dependence between us.''

``Are people sticking around?''

``Lots are going to New Station and the Plantations.''

``New Station...'', says Jonah, \hl{somewhat distantly}\footnote{\textbf{q.google }The idea that one would go live there is still barely registering in his mind.  But see below. \textsubscript{04/06/13 1:48pm}}.

``Yeah.  Listen, there's something I want to tell you about.  Not sure if it's my business exactly but, well, it may affect our business, so....''

``Go ahead.''

``Your sister has guy she's hanging out with.  They are... rather friendly.''

Jonah raises an eyebrow.  ``Oh yeah?''

``Yeah.  I'm thinking it's not unlikely your family may have another mouth to feed soon.''  He pauses, letting the change in the price that this might imply go unsaid.

Jonah is silent for an uncharacteristically long time.  This complication isn't one he is ready for.  ``Is the guy decent?''.

``Couldn't really say.''  \hl{His expression makes it clear that this is an understandable but silly question: the guy's decency isn't part of the decision.}\footnote{\textbf{Suko T }Nice. \textsubscript{04/06/13 4:30pm}}

Jonah nods.  \hl{``New Station eh...''}\footnote{\textbf{q.google }It occurs to him that if the guy \_is\_ decent he'd be willing to follow the family if it moves.  And if he's not willing to follow that solves that problem. \textsubscript{04/06/13 2:04pm}}

Jonah offers 'Zhok a little extra money and 'Zhok promises to keep an eye out, for how things progress.



Jonah leaves and walks away a few blocks before \hl{allowing himself to freak out}\footnote{\textbf{q.google }Family always gets to you, even when you try to keep your distance.  Some survival of the species nonsense. \textsubscript{04/06/13 1:46pm}}.  A passerby stops in concern and Jonah pulls himself together.





\jumpHeadline{ Backlash:  \hl{It has begun} } \footnote{\textbf{q.google }ROFL \textsubscript{04/06/13 2:04pm}}


\sceneHeadline{SAC-09  {[}38 Backlash Tokens{]}}

When Jaya gets off of the train at SAC-09, Rook gets off the train also and stops her.

``Agent Morgan has requested your presence in her office.''

``Now?'' says Jaya, who had been hoping to head to her bunk to clean up a little.

Rook just gives her a look and Jaya sighs and tries to neaten herself up as best she can without  a mirror, slicking down her hair with her fingers, trying to rub out some blood stains with spit and straightening her collar.



When Jaya steps out of the elevator into Morgan's office, Morgan is typing and looks up at her.

``Senior Constable, have a seat.''  Jaya sits down and slumps back.  Then she quickly remembers where she is, straightens up and leans forward attentively. Morgan looks at her, ``Senior Constable, I know we have a working relationship, but usually one salutes a senior officer.''

Jaya clumsily salutes with her off hand and apologies, ``Sorry Sir, it's just that my shoulder, uh, the damage....'' in her nervousness, she removes the wad of bloody tissue from her nose and drops it on the floor and shoves in some clean tissue.

Morgan waves off Jaya's apology. ``I'll keep it between us.  Now, regarding your report, I have some questions.''

Jaya frantically tries to remember what she wrote down in her report.

``You said that he attempted to say something,'' continues Morgan.

``Yes before I shot him in the face.  Did you get that part?  And then with my supervision and assistance, Trainee Hayley threw him off the roof -''

``Yes I understand that part,'' interrupts Morgan.  ``But I mean before that.  What did he say?''

``Uh, just nonsense.''

``What kind of nonsense?  Like this'' and Morgan says something in a different language. ``Or was it words you understood but just not put together in a way that made sense?''

``Uhhhhh.... he called me a name?'' says Jaya tentatively.  ``He called me a.... tetris?''

``Could it have been 'Tertius'?''

``It could have been that, but it really sounded like \hl{tetris}\footnote{\textbf{q.google }Maybe we are in a video game, but I didn't think it was Tetris.... \textsubscript{04/06/13 2:07pm}}\footnote{$\rightarrow$\textbf{Suko T }I rather love that she insisted that it was Tetris after Morgan corrected her.  It's so Jaya and also very funny OOG. \textsubscript{04/06/13 4:25pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{04/07/13 1:23am}}.''

``Hmm.  Now onto the other matter.  You have been cleared for active duty but are you ready?  You seem...distracted.'' says Morgan pointedly looking at Jaya's new bruises and cuts.

``Uh, I don't know how your shore leaves go but sometimes you need time to recover from them, you know?'' says Jaya, absently dropping another wad of bloody tissue on the floor.  ``If I can just have a little time to rest, and see my team, I'll be ready, 100 percent!  Er, is Lackovich a part of my team now?  Because she performed okay.  She didn't fall down this time or get us killed.'' says Jaya magnanimously.

Morgan doesn't comment and continues, ``If you had to break your team into pairs, how would you do it?''

Jaya talks around the subject, claiming that her team is so good that any combination would be optimal, but when Morgan presses her for specifics, Jaya says, ``Uh, well, I'm the most experienced so I should be paired with the least experienced.  And the boys can be together.  Those would be good subteams, you know, teams within the team that would be optimal...teams.....''  Jaya's babbling trails off.

``We're off the record here,'' reminds Morgan.

``Really?'' says Jaya, more confused than comforted by the knowledge.

``Because if you have any qualms, I want to hear them.''

``I don't need to be replaced!'' says Jaya with alarm. ``I am fully capable - My experience - It's just best to spread the skill levels because I'm a Senior Constable -''

``I understand your rank,'' says Morgan, interrupting Jaya's disorganized argument.

Morgan hands Jaya an envelope, which Jaya promptly opens, looking for money (there is only a letter inside).

``Hayley is being promoted to Constable, please deliver this letter to her.''  

Jaya nods and skims over the letter.  ``Cool.  Does this mean she gets a raise and stuff?''

``As an Incorporated, no, although something may be worked out with her contract holder.''

``Oh, uh, okay.'' says Jaya, and stuffs the letter into one of her blood stained pockets.

``Now to return to my earlier question, who would your subteams be?''

``Well, I'd take Gemayel.  Leaving...uh....'' Jaya stalls while she tries to remember Oliver's name, ``uh.... \textit{Oliver }to work with Trainee, I mean Constable Hayley.''

``Hayley has certain skills...''

``Well Jonah is a medic and I want a medic with me.''

``If it matters, I concur.''

``Great minds think alike!'' says Jaya with a grin.``So I hear.'' says Morgan dryly.

``So, will there be promotions for the rest of us?''

\hl{``Possibly. There will some competency tests.}\footnote{\textbf{Suko T }I didn't get all the notes here but this is the gist, I think. \textsubscript{03/14/13 12:36am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }That's the basic gist. Jaya did ask after what sort of competency, but didn't get very far. \textsubscript{03/20/13 6:48am}}Dismissed.''

Jaya leaves.



The next day, \hl{Hayley}\footnote{\textbf{Suko T }Hayley looks more relaxed and happy than you have seen her look in a while.  Unlike Jonah and Oliver, it seems like her Shore Leave actually refreshed her. :) \textsubscript{03/14/13 12:55am}}\footnote{$\rightarrow$\textbf{q.google }Wait.  Shore Leave is supposed to be \_refreshing\_???

Does Nate know? \textsubscript{04/06/13 2:09pm}}\footnote{$\rightarrow$\textbf{q.google }Oh \_wait\_ I see the source of the confusion: it refreshes \_capabilities\_.  That makes sense now.  Except we had ours refreshed too didn't we?
 \textsubscript{04/06/13 2:10pm}}, Jonah and Oliver return.  



They return to their bunks where Jaya is asleep.  Hayley notices Jaya's stained and dirty clothing and attempts to undress Jaya to wash her up.  This wakes up Jaya and she pulls the letter out of the pocket of her shirt and waves it at Hayley. ``Guess what this is?'' she says gleefully.

Hayley just shakes her head and says, ``I don't know.''

``It's for you, look!'' Jaya hands her the letter but before Hayley can even open the letter Jaya blurts out, ``It's a promotion!  You're a Constable now!''

Hayley looks confused, ``What?''

This wasn't the joyful reaction she was expecting, so Jaya says, ``You've been promoted!''

``What?  Oh no!  Does that mean I'm leaving?'' Hayley seems close to tears.

``Hey, hey, it's a good thing.  Try to act excited or something!'' says Jaya.

Hayley smiles weakly but is still clearly upset.

``It's a good thing Hayley, it means you did a good job.'' says Jonah.

``Congratulations,'' says Oliver dryly.

``Yeah, you're not going anywhere,'' adds Jaya.

``Oh!  Thank you.'' Hayley says in relief and then smiles in earnest.  She opens the letter to read it.



Jari walks in and drops a \hl{duffle bag}\footnote{\textbf{q.google }-duffle bag- bombshell.
FTFY. \textsubscript{04/06/13 2:12pm}} on the floor.  ``Maneuvers start in 3 hours for the competency tests.''

``For \textit{what}?'' asks Oliver.

``Senior Constable knows,'' says Jari and leaves.

``What is he talking about?''  Oliver asks Jaya.

``We're taking Competency Tests for promotions!  I'm going to be a Station Inspector!'' says Jaya proudly.

``What tests?''

``I, uh, didn't ask.''

``You didn't ask?!?'', both Oliver and Jonah exclaim.

\hl{``Have you ever had a conversation with Agent Morgan go the way you wanted it to?'' says Jaya defensively}\footnote{\textbf{q.google }That's \_almost\_ a good argument.  (A better one is this: she \_did\_ ask.) \textsubscript{04/06/13 2:13pm}}.

``Sometimes.''

``Oh, we should talk about that then.''

``Well, I'm not taking this test,'' says Oliver firmly.

``Yes you will,'' says Jaya intently. ``Don't be a coward.''

At this, Oliver rises to his feet and Jaya starts to pace away, trying to hide her nervousness.

``\hl{You can't call me coward}\footnote{\textbf{q.google }Seriously.  If anything Oliver's coward quotient is alarmingly low. \textsubscript{04/06/13 2:14pm}}.  I am the only one who bagged someone and brought them back.  But you couldn't even remember to ask what tests we will be taking,'' says Oliver, stepping forward angrily.

``Well why don't you go ask her yourself then?'' says Jaya with bravado.

``I will,'' says Oliver and turns and leaves.



As Oliver passes the Ops room, Rook comes out of the room and stops him.  ``Just the man I was looking for.  Do you have a moment?''

Oliver is antsy but nods and follows Rook into the room.  Rook excuses Larissa and sits down.

Rook says, ``This is off the record.  I've been asked to provide a recommendation and I wanted to ask your input.  If we had to pair two people from your team together, who would you pick?''

``Just two?  In what situation?''

``Say it is anything you have come across so far.  Remember this is hypothetical.''

``Myself and Constable Gemayel,'' says Oliver promptly.

``Why?''

``Because we would cover most of the skills needed for almost any situation.''

``And the other two?''

``Depends on the situation.''

``Do you believe the Senior Constable and Hayley would work well together?''

``Yeah.''  Rook waits for him to elaborate, but Oliver says nothing.

``Is there anything else?''

``No.  Wait.  Actually, do you know anything about these tests?''

``I'm not at liberty to discuss HR matters.''

``Okay then, what would you suggest we do to prepare?''

``In your case, I would study any test information about Operators.''

``What is that position?  It's not in the handbook.''

``It is not often used, it's found as a footnote really.  \hl{But if you keep a journal or something along those lines you could note this term for posterity.  To pass along to your distant descendants}\footnote{\textbf{q.google }Ok, did anyone else want to know what the hell he meant? \textsubscript{04/06/13 2:16pm}}\footnote{$\rightarrow$\textbf{Suko T }Oh certainly *I* do, but alas the characters... :) \textsubscript{04/06/13 4:27pm}}.'' says Rook cryptically.  ``Of course none of this can leave the base, as per your security clearance agreement.''



Oliver returns to the bunk, looking confused.

``What did she have to say?'' says Jaya.

Oliver doesn't reply and pulls out the Patrol Handbook and starts flipping through it.  ``Do you know the Operator Competencies?'' he asks.

No one knows.  He looks up Operator and the competences are fairly basic - firearms, truncheon, protocols, basic operations... but then it says ``Coordinated, Dominant''.



At this moment, the door opens and Micah walks in with a stopwatch.  ``Present your team at the ready line!'' he says and starts the watch.  Luckily Jonah had gone through the duffel bag that Jari delivered earlier and passed out the training uniforms that were within.  {[}\textit{Challenge: Get ready in mediocre time 2 $\rightarrow$ Matched}{]}.  \hl{Hayley leaps into action and practically dresses Jaya as she stands there in bewilderment}\footnote{\textbf{q.google }I think that's actually a Challenge, and worth VP :). \textsubscript{04/06/13 2:17pm}}\footnote{$\rightarrow$\textbf{Suko T }There are few things Hayley has been trained for but this is one of them.  So this was nuthin'.  Especially since it wasn't a haute couture gown with all the fancy undergarments, accessories and necessary complimentary hair styling. :D \textsubscript{04/06/13 4:29pm}}, and then makes sure everyone else's uniforms are up to snuff.



Jaya's patrol group gets to the ready line.  Lackovich's patrol group is already there and assembled on the ready line. 



``We are beginning training group exercises to determine the competencies for Patrol Groups 1 and 2,'' says Morgan. ``Sound off!''

Jaya is 1, Oliver is 2, Jonah is 3 and Hayley is 4.  Jonah notes who is which numbers in PG2.

``Odds fall back!''

Jaya and Jonah step back from the ready line, along with Lackovich and Davis.

``Evens, drop and give me 50,'' barks Micah.  {[}\textit{Challenge: Win 50 pushup test $\rightarrow$ Overcome!}{]}



``Odds are with me,'' says Jari.  Because they were slightly closer to the door, Jaya is able to keep an early lead, and with Jonah keeping pace with her, Lackovich is forced to run behind them.  Jari leads them to a training room on a floor above PG1's usual training room.  The cement pillars are marked.  



``Alright, go around the pillars, relay.  Five miles.  Go!''  {[}\textit{Challenge: Beat other team at running 3 $\rightarrow$ Matched}{]}  Jaya manages to time her laps so that she can sneak a little something extra from her stash when hidden by a pillar.  She also deliberately provokes and ``accidentally'' elbows Lackovich a few times so that Lackovich expends too much energy fighting back and tires herself out.   They get into a couple of scuffles during the run but Jaya is simply inexhaustible, even bruised and bleeding as she is.  Jonah has managed to pace himself very well so that between the two of them, by the last few laps, they have built up a fair lead and they finish the 5 miles before Lackovich and Davis.  Halfway through the 5 miles, Morgan and Rook walk into the training room and ask Jari for the patrol group's status.



Back at the ready line, Micah announces that they will have a 2 minute rest.  Oliver whines about the short break {[}\textit{Reduce Flaw: Showoff 1 $\rightarrow$ 0}{]} and pisses off Micah enough to cut the rest short.



``Alright, Assembly next!'' says Micah and starts his stopwatch again, and Carruthers and Javier head for some crates against the back wall.  In the crates are parts of a handgun, rifle and sniper rifle, including ammunition.  {[}\textit{Challenge: Win gun assembly 3 $\rightarrow$ Matched}{]}



Used to working together on this sort of task from Oliver training Hayley on rifles, they are able to accomplish the task swiftly and well.  Micah inspects the weapons and finds some small mistakes with Carruther's and Javier's weapon assembly.  Another soldier takes the weapons and racks them.



Micah looks at his watch and then hits a button.  There is an answering two beeps and Micah says, ``Looks like we have some time, another 50 pushups!''



Morgan, Rook, Jari and the runners come back down to the ready line.  The two patrol groups reassemble.   Morgan pairs the teams off: Jaya \& Hayley, Jonah \& Oliver, Lackovich \& Carruthers, and Javier \& Davis.

``Senior Constable Parvadi, since your team has done the best so far, you will pick first.''  Morgan indicates herself, Rook, Jari and Micah. ``You will demonstrate how to perform an arrest.''  Jaya chooses Rook (because he looks the smallest), Lackovich picks Morgan (who smiles at the choice), Oliver picks Jari, and Javier is left with Micah.



Morgan picks up a clipboard and nods to Jaya.  ``Proceed with the arrest.''



Hayley just looks at Jaya for instructions, so Jaya steps forward and says to Rook, almost apologetically, ``Sir you are under arrest.''

``Where is your warrant?'' says Rook.

``Uh, we saw you commit the crime, so under the TA authority we can arrest you without a warrant,'' says Jaya.

\hl{``That is correct,'' says Rook calmly.  He then steps back and raises his hands. ``But since you have no warrant I'm afraid I'm going to have to resist arrest.''}\footnote{\textbf{Nathaniel Ford }Actually, Rook didn't resist until they failed to request he comply and come peacefully. \textsubscript{03/20/13 6:51am}}\footnote{$\rightarrow$\textbf{Suko T }Wait, you can *do* that?  Was that page torn out of Jaya's Patrol Handbook? :D \textsubscript{03/20/13 5:56pm}}

``Should I go cover the back door now?'' asks Hayley, which causes several to snicker.

``No, we will now proceed with the arrest,'' says Jaya as she gets her game face on.  She steps forward and pulls out her truncheon....



\textbf{{[}28 Backlash Tokens left{]}}



\jumpHeadline{ Backlash Challenges }  



\begin{itemize}
\item Challenge: Get ready in mediocre time 2.  Ladies' Maid 2 (Hayley) $\rightarrow$ Matched
\item Challenge: Win 50 pushup test. Athletics 2 (Hayley) + Armstrength 1 (Oliver) +  {\color[RGB]{255,0,0}Flaw: Show off 1}  (Oliver) $\rightarrow$ Overcome! (\textbf{1 VP Oliver, 1 VP Hayley})
\item Challenge: Beat other team at running 3.  Stash 2 (Jaya) + Adrenaline Junkie 2 (Jaya) $\rightarrow$ Matched
\item Reduce Flaw: Showoff 1 via Anti-authoritarian 1 (Oliver) $\rightarrow$ 0
\item Challenge: Win gun assembly 3. Sniper Rifle 2 (Oliver) + Memory for Details 1 (Hayley) + Rifle 1 (Hayley)  $\rightarrow$ Matched
\end{itemize}


\jumpHeadline{VP Totals }

Hayley 1

Oliver 1


\jumpHeadline{Quotes }

``Blood is just weakness leaving the body.''

\extraIndent{ -Rebecca}
\vspace{\fill}


\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 8:38am
\end{flushright}

