\setcounter{chapter}{ 17 }
\chapter{\textbf{``Training Day'' } }





\subChapterTitle{(Backlash 2/2)}

\deets{Suko}{April 3rd, 2013}



Buttons were pushed.  Literal and emotional.  Hopefully next session there will be an earth-shattering kaboom!  


\jumpHeadline{ Welcome to the  Backlash } 


\sceneHeadline{SAC-09  {[}28 Backlash Tokens{]}}

Jaya advances toward Rook, cuffs in one hand, truncheon in the other.  He just stands there calmly.  Jaya instructs Hayley to circle around behind Rook incase he tries to make a break for it.  ``Get down on the ground and put your hands behind your back!'' yells Jaya, continuing to advance.  Rook doesn't move.  Jaya repeats herself, yelling louder but also looking at Rook and Morgan for hints on how far she should take this.  Getting no hints from them, she raises her truncheon and instructs Hayley, ``Constable Trainee, please, uh, take this person into custody.''



{[}\textit{Challenge 3: Take down Rook without ending up in a compromising position --\textgreater  Matched}{]}  Hayley executes some incongruously formal ballet plies and then spins around and tries to kick Rook's feet out from under him.  He falls, but manages to twist enough to fall onto Hayley, immobilizing her, and pulls his fist back to punch her.  Jaya starts swinging her truncheon and he changes his attack midway and blocks her blow instead.  He rolls away and gets to his feet.



``You have now assaulted a TA officer, you will stand down and be taken into custody!'' says Jaya forcefully.



``I didn't assault a TA officer,'' says Rook, calmly, ``But given how the situation is going, I will surrender.''  He puts his hands up.  Morgan ends the exercise and calls Jari over.  Tells him something and he leaves.



Lackovich and Carruther's arrest of Morgan doesn't go so well.  Lackovich asks Morgan to come peacefully and Morgan offers up her hands without a fight.  Clearly suspicious, Lackovich orders Carruthers to cuff Morgan.  As Carruthers attempts it, there is a flurry of motion and suddenly Carruthers is in a headlock and her gun is in Morgan's hand, pointing at Lackovich.  Lackovich fires - the bullets aren't real, but the situation devolves from there.  \hl{They fail to make the arrest}\footnote{\textbf{q.google }Technically true.  But if the perp has a your partner in a headlock and has a gun pulled on you, firing is a reasonable course of action.  And this would have happened to any pair who tried to arrest Morgan. \textsubscript{04/06/13 2:58pm}}\footnote{$\rightarrow$\textbf{Suko T }Given how Micah's arrest went, I don't think the firing of the gun was why their arrest was deemed a failure, it was the fact that even with the firefight, they were unable to subdue Morgan in any way.  So no arrest at all.  

But yes, I think anyone of the combos would have had a hard time with this one. \textsubscript{04/06/13 4:34pm}}\footnote{$\rightarrow$\textbf{q.google }Seriously: How \_do\_ you arrest Morgan?  OOG I don't see how to do it. \textsubscript{04/06/13 6:33pm}}\footnote{$\rightarrow$\textbf{Suko T }Sometimes the only way to win is not to play. :P \textsubscript{04/06/13 10:56pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }As a minor note no one actually *said* it was a failure, though there was the implication they didn't make the arrest. What qualifies as failure was left unstated. \textsubscript{04/15/13 11:16pm}}.



Jari returns, accompanied by a pudgy guy in a well-tailored and tidy TA uniform.  There is no visible rank insignia on the uniform. We have not seen him before.  He is smiling and stands to one side without comment.



Jari goes to stand in front of Jonah and Oliver and Morgan gives the nod to begin.  Jonah addresses Jari, ``Are you Jari of Midtown in the Bucket?''

``Yes,'' says Jari politely.

``May I ask you to come with us?'' says Jonah with equal politeness.

``Why?''

``We have a warrant for your arrest for turnstile jumping.''

Jari protests, and then tries to buy some time by asking to leave a letter for his mom.  \hl{During this whole exchange, Oliver is standing at a 90 degree angle to Jari and watching him carefully}\footnote{\textbf{q.google }The idea, as we discussed it, is not to pin him between the two officers, but, if he decides to run, to restrict his best choice of direction to an area of our choosing. \textsubscript{04/06/13 2:59pm}}.

``\hl{That will not be necessary}\footnote{\textbf{q.google }I like the verbal judo in that phrase. \textsubscript{04/06/13 3:00pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{05/26/14 11:05pm}}, please come with us now,'' says Jonah.  ``Please turn around.''

Jonah looks for signs that Jari is about to flee.  Oliver tries to predict when/if Jari will make a break for it and approaches him warily.   However, Jari turns around and allows Oliver to cuff him without a fight.  They place their hands on his shoulders and have their truncheons at the ready and walk him forward toward the area they deemed the ``TA station''.  



``Do you make many arrests?'' asks Jari conversationally.  ``I don't see many ribbons.''

{[}\textit{Challenge 3: Notice what Jari is up to --\textgreater  Matched}{]}  Jari is very convincing but his conversational gambit does not distract them and their vigilance pays off when they see that he has managed to escape the cuffs.  Jonah says sternly, ``None of that, get on the ground NOW.'' and hits Jari with the truncheon.



Jari takes the blow and goes to the ground.  ``Good,'' says Morgan and ends the exercise.



Davis and Javier vs Micah is much splashier than any of the other arrests.  Javier says that Micah is under arrest. In a display of more emotion than any of us have previously seen, Micah screams, ``FUCK YOU!'' and pulls out two guns.  There is lots of bullet-less gunfire as Davis and Javier return fire.  Eventually it turns into a scuffle.  Javier gets a black eye but he and Davis manage to eventually wrestle Micah to the ground.  Jaya cat-calls her approval, and everyone but Jaya notices Morgan's face get stonier.  \hl{``Good,'' says Morgan to Davis and Javier}\footnote{\textbf{q.google }Seriously.  They were actually \_injured\_ in this scenario.  They earned it
:). \textsubscript{04/06/13 3:02pm}}\footnote{$\rightarrow$\textbf{Suko T }I dunno, it was kind of...messy.  Jonah and Oliver also got a ``good'' :) \textsubscript{04/06/13 4:35pm}}, and ends it.  Jaya slow claps.



Morgan announces, ``15 minute rest and then we'll come get you in your bunks.''



Back at their bunks, Oliver swaps out his training rifle for his real rifle {[}\textit{Refresh: Sniper Rifle}{]} and Jaya calms her nerves with a healthy dose of alcohol {[}\textit{Refresh: Adrenaline Junkie}{]}.  Hayley quietly reminds Jaya that Hayley is a Constable now, not a Constable Trainee.  Jaya apologizes and praises Hayley for bringing it up privately instead of publically and possibly embarrassing Jaya. \hl{Jaya loudly says that perhaps Hayley should instruct some of the other members on the team about such smart behavior}\footnote{\textbf{q.google }You know, I missed that completely.... \textsubscript{04/06/13 3:02pm}}\footnote{$\rightarrow$\textbf{Suko T }And Oliver pointedly ignored it.  Poor Jaya. \textsubscript{04/06/13 4:35pm}}\footnote{$\rightarrow$\textbf{q.google }No I don't mean Jonah missed it.  I didn't hear the conversation at all. \textsubscript{04/06/13 6:35pm}}.


\sceneHeadline{Jaya and Hayley}

After what happened earlier, Hayley makes sure that everyone is dressed and ready at the 15 minute mark.  At the 20 minute mark, Jari comes in and says, ``Senior Constable Parvadi, Constable Hayley, come with me.''  Jari then goes to PG2's bunk and calls out Lackovich and Carruthers.  Jaya suggests Javier and Davis instead but Jari says that Agent Morgan has her reasons.



He leads the four ladies to the elevator and takes them down to one of the lower levels.  On the ride down, Jaya ``consoles'' Lackovich on her poor showing at the arrest.  

``\hl{At least I'm not a coward}\footnote{\textbf{q.google }What is she talking about?  Is this the arrests, Nicklepan, or all the way back at Magnin's place? \textsubscript{04/06/13 3:05pm}}\footnote{$\rightarrow$\textbf{Suko T }I believe the answer is ``yes''. \textsubscript{04/06/13 4:36pm}},'' says Lackovich quietly but clearly.  Jaya misunderstands and thinks Lackovich is talking about Jari, and admonishes Lackovich for talking badly about Jari when he's standing right there.  

``But she was talking about you!'' blurts out Carruthers.  \hl{Jaya doesn't get it and before she can understand how she'd been insulted}\footnote{\textbf{q.google }I really liked this.  Jaya has plenty of flaws, but cowardice is so far down on the list that it doesn't even register :). \textsubscript{04/06/13 3:04pm}}, the elevator arrives and Jari leads them to a large open area.  It turns out to be the space underneath the readyline.  There are some tracks in the ground, as well as a piece of unfamiliar machinery and some large cylinders set into the floor.   It is about 50 yards up to the ready line, and distantly they can see Morgan standing on the gantry 50 yards above that, looking down.



Jari drops a large duffle bag on the floor and says, ``You must get to the ready line.  You cannot go through any doors.  Your time starts now.''



Jaya tears into the duffle bag and finds some rope, some straps and some metal pitons.  Hayley has wandered over to one of the walls and is testing cracks and breaks in the wall for handholds.  Jaya grabs some of the metal pitons and attempts to drive them into the wall unsuccessfully.



{[}\textit{Challenge 1: }\textit{\hl{Notice machinery}}\footnote{\textbf{q.google }Why was this a challenge?  The machinery wasn't useful to the exercise as it turned out.  Or was this for later? \textsubscript{04/06/13 3:06pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Well, to a degree it tells you more about the nature of the machinery there. That is potentially useful; sometimes, on the fly, it's difficult to determine if low-level stuff like this is worthy of a challenge. \textsubscript{04/07/13 1:29am}}\footnote{$\rightarrow$\textbf{q.google }Ah ok.  I wasn't sure if there was something you wanted us to see that we'd missed OOG. \textsubscript{04/07/13 2:17pm}}\textit{ --\textgreater  Overcome!}{]} Tossing aside the piton in disgust, Jaya switches her attention to the machinery in the corner.  Her colorful background has taught her how to notice anything around her that might be useful in achieving her goals.  The machinery has some warning signs on it that she ignores.  She notices that there are some buttons protected by clear box covers.  Looking up she sees some tracks far above them, with a platform hanging from them.



Meanwhile, Carruthers has measured the rope to be just shy of 50 yards long. She has helpfully pointed out that the other wall is more climbable and Hayley has tied the end of the rope around her waist and is attempting climb it.  Jaya calls to Hayley to stop what she's doing and get over to her.   {[}\textit{Refresh: Athletics}{]} Hayley gets startled and misses her grip and falls to the ground in a tangle of limbs and rope {[}\textit{Challenge 1: Not look like an idiot --\textgreater  sent back to pool}{]}. Luckily she didn't climb very far and is unhurt.  



Hayley heads over to where Jaya is and is equally mystified on how to get the machine to work.  Jaya grabs onto of the pitons and smashes the clear box protecting the button.  Hayley asks why they are doing this when they should be climbing.  Jaya points to the rope dismissively and says, ``That's a decoy.''   \hl{Hayley relays this information to Lackovich and Carruthers, much to Jaya's annoyance}\footnote{\textbf{q.google }Re: Rook's question to Oliver about whether Jaya and Hayley would work well together... in this case, not really. \textsubscript{04/06/13 3:07pm}}\footnote{$\rightarrow$\textbf{Suko T }Actually I think Hayley and Jaya worked together just fine, it was Jaya + Lackovich that was the problem.  If it was Davis and Javier or even Carruthers and one of the guys, I suspect the whole exercise would have gone differently. \textsubscript{04/06/13 4:37pm}}\footnote{$\rightarrow$\textbf{q.google }No that's true.  I just mean that it was a case where Hayley was blithely \_contradicting\_ Jaya.  What Jaya appears to like about Hayley is that Hayley does what she says so readily, so this was unusual. \textsubscript{04/06/13 8:00pm}}\footnote{$\rightarrow$\textbf{Suko T }I can see what you're saying but I don't know if it's so unusual.  Hayley blabs private stuff all the time :D  If Jaya had told her it was a secret, Hayley wouldn't have said anything.  But generally, Hayley will share any information she's not told to keep secret.  So yeah, she's got a lot of ``don't tell anyone this'' rules.   I have a list. :) \textsubscript{04/06/13 11:00pm}}\footnote{$\rightarrow$\textbf{q.google }Right but I don't mean that.  I mean that Hayley doesn't usually end up zinging Jaya in front of other people.  Jaya usually reserves that to herself :). \textsubscript{04/07/13 2:23pm}}\footnote{$\rightarrow$\textbf{Suko T }Ha!  True enough. \textsubscript{04/07/13 9:45pm}}.



Jaya presses the button and nothing happens, except a faint alarm starts going off.  Over Jari's walkie talkie we hear Morgan tell Larissa to turn off Alarm 5 (sounds like it is a circuit breaker of some kind).



Jaya looks at the button, trying to figure out what to do next.

``Maybe it's one of the other buttons?'' suggests Hayley.

``Out of curiosity, what did you think that was going to do?'' asks Lackovich.  ``Do you know what this button does?''

``It triggers Alarm 5,'' says Hayley.

``The signs warn about high voltage,'' says Carruthers.

Abandoning the buttons, they turn back to the rope.  Hayley offers to climb up the wall again.  Carruthers, almost shyly, offers to climb too, saying she's okay at it.  Not as good as Hayley but not bad.  Hayley doesn't know what to do with the offer but says that if she fails, Carruthers can try it next if she wants.



Lackovich hands Hayley the pitons and then hands her a hammer.  

``Where did you get that?'' says Jaya accusingly.  

``It was in the dufflebag under the rope,'' replies Lackovich.

``\hl{Well, if I had known there was such a tool, I would have been using it}\footnote{\textbf{q.google }''If I had a hammer...''

(Or maybe: ``To a woman with a hammer...'') \textsubscript{04/06/13 3:07pm}}!'' Jaya says loudly. She grabs the hammer and starts waving it around emphatically.

``You need to calm the fuck down,'' hisses Lackovich, looking over at Jari, who has been watching everything.

``I have a tool now and I am going to assist you in this mission!'' says Jaya even more loudly, pointedly ignoring Lackovich.  Jaya walks up to the wall and hammers one of the pitons into the wall.



Carruthers watches this exchange with wide eyes.  ``I can see why Lackovich doesn't like your Senior Constable,'' she whispers to Hayley.

``She doesn't?!'' exclaims Hayley in surprise.

``Oh...'' stammers Carruthers and flushes pink.  She watches Jaya hammer in another piton and loudly explain to Hayley what she is supposed to do next.  ``I'm sorry,'' Carruthers says to Hayley with sympathy.

``It's okay, she's like that all the time,'' says Hayley cheerfully.



Hayley begins to climb the wall.  This time she goes slowly and practices hammering in the pitons a few times before even starting to get off the ground, and pauses to plot out a climbing course.  Jaya shouts encouragement and useless but very loud advice.  {[}\textit{Challenge 3: Climb the wall to the ready line --\textgreater  Matched}{]}  It takes Hayley a while to get the hang of it and she smashes her fingers a few times with the hammer, but she's able to hang on through the pain and eventually makes it up to the ready line platform and ties off the rope to the railing.



As Carruthers had estimated, the rope dangles far above the floor.  To reach it, someone will need to boost the other up to grab the rope.  Lackovich boosts up Carruthers, who climbs part way up and then stops and waits for the other two to start climbing.



Lackovich and Jaya argue about what to do next.  Finally Lackovich \hl{``plays Jaya like a fiddle by implying she's not strong enough to lift her up''}\footnote{\textbf{Suko T }had to keep this as noted by Adam, hee! \textsubscript{04/05/13 10:05pm}}.  Jaya easily tosses Lackovich up to catch the rope.  But Lackovich can't quite reach down far enough to grab Jaya.  Besides Jaya is not too pleased with the idea of having to get Lackovich's help to climb up the rope.  



Jaya dithers some more, desperately trying to find any alternative to having to climb up Lackovich.  Carruthers climbs the rest of the way up and joins Hayley on the ready line.  They both wait for the others to climb up.  And wait some more.  Eventually Hayley calls down, ``How is the last person going to get up?  \hl{Shall I climb down and boost the last person up}\footnote{\textbf{Suko T }yeah she really didn't think that through.  Dammit Jim, she's a tank, not a strategian :D \textsubscript{04/05/13 1:20am}}?  Or I could throw down my uniform and you could tie it to the rope for more length.''



The two down below do not respond to the suggestions.  \hl{Lackovich sighs and ties the rope around her ankle and then slowly and painfully inverts herself}\footnote{\textbf{q.google }Poor Lackovich ;P \textsubscript{04/06/13 3:09pm}}\footnote{$\rightarrow$\textbf{Suko T }No kidding.  This is not the first time she's had to save our butts and it will probably not be the last. \textsubscript{04/06/13 4:38pm}}.  Jaya can now grab her hands but doesn't, and continues to try to think of other alternatives.  ``She can't do that for very long, you need to hurry,'' Carruthers yells worriedly.  



Hayley seems to come to some sort of internal conclusion.  She slides down the rope, climbs down Lackovich and joins Jaya on the ground.  {[}\textit{Challenge 2: Climb the rope}{]} She then boosts Jaya up to climb up the rope, and then leaps up, catches Lackovich's hands and climbs up herself.  She tries to help Lackovich climb up but it's just too awkward.  Hayley climbs up and they watch Lackovich painfully re-invert herself and start climbing.  About halfway up she just can't keep going and Carruthers says that they will have to pull her up the rest of the way.  All three team up and pull Lackovich up to the ready line.


\sceneHeadline{Oliver and Jonah}

After Jaya and Hayley leave, there's a knock on the door.  Micah enters. Oliver salutes.  Micah leads the two of them to the Cistern level but a different room.  In the room is Dr. Gerhauser, Larissa, Swan, Trenton and \hl{Karil}\footnote{\textbf{Suko T }the other guard who is not Micah. \textsubscript{04/05/13 1:34am}}\footnote{$\rightarrow$\textbf{q.google }Official acronym: TOGWINM. \textsubscript{04/06/13 3:10pm}}. 



Dr. Gerhauser says, ``This is a test of coordination.  These four people have marks on their foreheads.  They are all injured.  Trenton is an Anglian with info.  Larissa and Karil are TA but not of any great importance.  Swan is a Station Chief.  Jonah, you will not do anything that Oliver does not tell you to do.  Please start when you are ready.''



Oliver tells Jonah, ``Assess the Anglian, The Chief and then the others.''  Jonah picks up the medical bag and goes over to Trenton.  The symbol on Trenton's forehead says  ``immediate medical attention required.''



``I've got a bullet wound above my sniper insignia and all the badges showing how many I've killed,'' says Trenton.  ``See?  Right here.  Bleeding all over alllllll these badges.''  Trenton needles Jonah a bit more, trying to provoke him, but Jonah just reports the injuries to Oliver and moves on to Swan.  



``I've got a major leg wound and a gut wound.  You can see my intestines,'' reports Swan.  The mark on Swan's forehead is the Street Medic symbol for ``imminent''.



``This one is not going to make it,'' reports Jonah to Oliver.  ``I can administer painkillers but that's it.''

``Do it,'' says Oliver.



Jonah evaluates Larissa (leg wound, barely conscious, symbol says ``stable'') and Karil (\hl{??}\footnote{\textbf{Suko T }don't remember what his injury was \textsubscript{04/06/13 2:31am}}, symbol says the same as Trenton's).

``Search the Anglian,'' orders Oliver.  

Trenton laughs and tells Jonah that he finds a pistol and slyly adds that he has his ``other'' weapon right here...and makes a crude gesture.

``Don't make me disarm you,'' says Oliver, sarcastically.



Because there are two patients in need of immediate medical attention, Jonah has to conscript Oliver into helping with Karil {[}\textit{Challenge 2: Teach Oliver to treat the patient --\textgreater  Overcome!}{]} while Jonah attempts to heal Trenton {[}\textit{Challenge 2: Heal Trenton --\textgreater  Matched}{]}



Jonah's attention lapses due to Trenton's banter, and the realization he hasn't gotten to talk to Trenton about the maps and he fumbles his medical treatment {[}\textit{Refresh: Street Medic}{]}. ``I need some help with this one,'' he says to Oliver.  

``Just one minute,'' says Oliver a little absently as he has become engrossed in the medical tasks he just learned to do {[}\textit{Refresh: Focused}{]}.

Jonah checks on Swan, and is told that the Station Chief has expired.



Dr. Gerhauser ends the exercise and tells Oliver to report to another room.

She asks Jonah to accompany her and walks with him to another section of the base.  As they walk, she asks him, ``You have saved some people, but not others.  How do you feel about that?''

``Well we saved some,'' replies Jonah.  ``Where were we supposed to be anyway?''

``A war-like situation,'' says Dr. Gerhauser.  ``So you saved the Anglian over the Station Chief.  How do you feel about that?''

``He was going to die, there was nothing I could do about that.''

``Hmm,'' says Dr. Gerhauser.  ``In your professional opinion, how do you think you did?''

``First, let me ask, \textit{was} there a way to save the Station Chief?''

``Possibly, given the right medical equipment.''

``Well if there were other choices, then maybe I made the wrong one,'' says Jonah.  ``But if this was during war?  You save who you can.  That's all you can do.''


\sceneHeadline{Jaya and Oliver}

Jari finds Jaya and tells her that she needs to report below.  He takes her to the brig level, which makes Jaya a little nervous and she starts sweating.  However he turns down a different hallway into a new room.  Oliver is standing in front of the door.

``How were things?'' asks Oliver.

``We completed our objectives,'' says Jaya.  She looks around.  ``Where's Jonah?''  Oliver doesn't know.



Jari opens the door to the room. Inside is a counter with sound-dampening headsets, and two sets of rifles and pistols on it.  There are six tracks in the ceiling with chains hanging from them.  Oliver says to Jaya, ``I'm keeping my rifle, you can have those weapons.''



Jari nods says, ``For this purpose that is acceptable.  For this situation you will need to use your imaginations a little.''  Jaya pulls out her notebook and looks at Jari attentively.  He continues, ``You will be in a strategic location, which is this room.  Once you leave this door, you may not re-enter.  There are these weapons available to you, as well as that crate with additional clips.  At the beginning of the simulation, paper targets attached to chains will be presented.  They will be dropped from the chains when they have been sufficiently damaged.  Red paper can get to you from halfway across the room.  Orange paper needs to get to three quarters of the way across the room, and the yellow paper has to get all the way to you.  If too many get to you, a red light will go off and you will be deemed killed.''

``Why would we leave the room?'' asks Oliver.

``I'm glad you asked.  Both of you have sensitive information that you must protect.  To clarify, the red light means that you are incapacitated, but not necessarily dead.''

``Why not just leave now?'' asks Jaya.

``You have been ordered to hold your ground because this is a strategically advantageous position.  The simulation will end when both of your red lights have gone off or you have left the room.  You will have 3 minutes to discuss this situation.  Good luck.''  Jari leaves the room.



``You go orange, I'll go red,'' says Oliver, setting up a stack of clips in front of him.

``You let me know if you get overwhelmed,'' says Jaya, making sure all of the weapons are loaded and ready to go.  

``Likewise.''

They both put on the headsets.

``Fucking bring it on!'' yells Jaya and raises her weapon.



Yellow paper starts moving toward them.  {[}\textit{Challenge 1: yellow paper --\textgreater  sent back}{]}.  They ignore those and wait for the orange and reds to start appearing.  {[}\textit{Challenge 2: Orange and a few red paper --\textgreater  Matched}{]}.  Oliver easily dispatches them before they get very far. 



At this point they each hear something different over their headsets.  Jaya hears Agent Morgan say, ``This is Agent Morgan.  Citing Codex 3, your priority is the safety of your team.''  Oliver hears, ``This is Agent Morgan, the sensitive information that your commanding officer has is vital information and must not be lost.''



More red paper starts appearing and they start moving faster and faster.  {[}\textit{Challenge 3: more red paper --\textgreater  Matched}{]}  Jaya dispatches these but she's running low on ammo and she's barely keeping up.  She rips off her headset and yells, ``This is getting insane!''

``Leave the room, I'll hold this position.   That's an order!'' says Oliver commandingly.

``Fuck You!'' snarls Jaya and they both continue to shoot at the targets.



\textit{{[}Challenge 4: }\textit{\hl{Don't die from paper cuts}}\footnote{\textbf{q.google }  ROFL \textsubscript{04/06/13 3:24pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{04/07/13 1:31am}}\textit{ --\textgreater  Matched{]}}  The paper targets are flying at them extremely fast at this point.  It is now very hard to see the red targets behind the flurry of yellow and orange.  Jaya's light goes off, indicating she's died.  She fires off the remaining rounds in her pistol and throws the pistol at one of the targets, ripping it from the track.  

Oliver grabs her arm and shoves her toward the door.

``It's just a simulation!'' protests Jaya, pulling away.

``Shut up, you're dead!'' says Oliver and then shoves her out into the hallway.  He closes the door behind her and turns back to the targets in the room.

Jaya starts ranting about unfair the whole situation was.  Jari just listens without comment.



\textbf{Jonah and Hayley (and }\textbf{\hl{Milgram}}\footnote{\textbf{q.google }http://nature.berkeley.edu/ucce50/ag-labor/7article/article35.htm

http://www.scientificamerican.com/article.cfm?id=what-milgrams-shock-experiments-really-mean \textsubscript{04/06/13 3:29pm}}\textbf{'s sadistic cousin)}



Dr. Gerhauser leads Jonah to another unfamiliar room.  In the room is just a chair.  ``Please sit in the chair.  For this next part, your goal is \hl{to get Hayley to adhere to her orders as long as possible}\footnote{\textbf{q.google }What he thinks: ``Are you fucking \_kidding\_?''

What he would have thought if he had more time (and less pain): ``There must be something else to this.  They \_know\_ Hayley will always follow orders.  What's the catch?''

What he should have thought: ``Oh @\$\%!.  This is going to \_hurt\_.'' \textsubscript{04/06/13 3:31pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{04/06/13 4:42pm}}.  This is going to be somewhat painful for you, but not life threatening.  Do you have any questions?'' 

``What exactly is this?''

``It's a behavioral observation.  I'm going to have to strap you in, but there is a button here,'' she points to a button right at his fingertips, ``that will release the straps immediately.''  She places some leads on his chest.

``Can we test it?''

``Yes.''  Jonah presses the button and the straps release explosively and the leads fall off.  Dr. Gerhauser re-attaches everything.

Jonah assumes a relaxed posture and says, ``Okay, ready when you are.''



Hayley is standing on the ready line with Lackovich and Carruthers, although Hayley is standing as far away from Lackovich as she can.  Morgan shows up and tells Hayley to come with her. They go to the elevator.  ``I am currently your commanding officer, do you understand what that means?'' asks Morgan.

``Er... yes?  You mean other than Senior Constable?  Oh wait, is she no longer my commanding officer?  But she should be, isn't she?'' babbles Hayley confusedly.

Morgan sighs.  ``Do you at least understand of the chain of command?''

``I'm learning it, I'm still reading that part.  I'm sorry.  I read really slow.''  There is a small pause and Hayley asks suddenly, ``Do you think you could teach me how you fight like you do?''

``We can talk about that some other time.  Is there ever any time that you do not follow an order?'' asks Morgan.

``Yes!'' says Hayley promptly,''Whenever someone of higher rank countermands that order.  Or if I'm unconscious.  Or physically incapable.  But otherwise I try.''

``Is that all?''

``Ummm, I think so.    I can't think of any other situations right now.''

``Good.''

``Is this going to be a test of imagination?  Because I'm not very creative,'' says Hayley, worriedly. 



They enter a small room with a large one-way mirror in the wall.  Through the mirror, Hayley can see Jonah, strapped to a chair.  In front of Hayley is a panel with a button on it, with a gauge next to it.



``Hayley, press the button.''

Hayley presses the button and \hl{Jonah is shocked painfully}\footnote{\textbf{Suko T }Screw you Milgram, we don't do the pansy ``fake shocks'' here in SAC-09! \textsubscript{04/06/13 2:08am}}\footnote{$\rightarrow$\textbf{q.google }Yes.  Although in another sense this version is (slightly) less damning: these are people in a military organization being given orders, and not following them can get you in a heap of trouble.  The real experiment had no such official authority or consequences. \textsubscript{04/06/13 3:33pm}}\footnote{$\rightarrow$\textbf{Suko T }Good point! 

Reading through the first link you included above, I'd say that all three of the items cited that contributed to submission were in play (especially \#1 and \#3!). 

I've been thinking about it and I'm not sure that Hayley falls into any of Migram's three response groups.  Nominally the first one but she will readily take full responsibility for her actions so I'm not sure how that works.  She is angry but she actually isn't angry at Morgan for the orders per se.  It's a different reason. \textsubscript{04/06/13 11:13pm}}.

Hayley looks up at Morgan in alarm but Morgan's face reveals nothing.  ``Press the button.''

Hayley presses the button again and Jonah is shocked again.

``Press the button,'' says Morgan for the third time.

``Is this hurting him?'' asks Hayley nervously, as she presses the button again.

``Press the button.''  

When Hayley does, Jonah screams.

``I don't think he's very comfortable,'' says Hayley, starting to get upset.

``Press the button.''

Hayley does, whining that she doesn't like this.

``Really?  Why do you think that matters?''

``I was told to say when I was upset.''

``By whom?'' asks Morgan.

``I can't say,'' says Hayley.

``This is a direct order, who said that?'' says Morgan intensely.

``You're just my commanding officer, not my contract holder!'' says Hayley stubbornly, just shy of pouting.

``I \textit{am} your contract holder,'' says Morgan and pulls Hayley's contract out of her pocket.  ``Go ahead, read it.''

Hayley is speechless.  She tries to read the contract but cannot get far into the legalese and looks a little lost.

``What do you think?  Will you do it now?'' asks Morgan.

``I think I don't like it,'' says Hayley looking down at the contract.  She then looks up at Morgan and says in a small voice, ``but I'll do it.  It was the doctors and nurses at Redemarrer who taught me that.''

``Press the button Hayley,'' says Morgan.

Hayley presses the button and Jonah screams again.  \textit{{[}Challenge 1: Help Hayley follow her orders --\textgreater Overcome!{]}} This time he speaks, ``Stay the course Hayley!''

``What course?'' asks Hayley, starting to cry, not knowing he can't hear her.

\hl{``Don't give up.  Trust yourself,''}\footnote{\textbf{q.google }He's actually talking more to himself than to her.  He's also hoping against all hope she'll actually find the courage to do the right thing.  (He has not really accepted that she's doing this to him.) \textsubscript{04/06/13 3:38pm}} says Jonah, trying not to sound as pained as he feels.

Hayley looks more befuddled than strengthened by the words of encouragement.

``Can I stop now?'' whimpers Hayley.

``Press the button.''

Hayley hesitates.

``PRESS THE BUTTON!'' orders Morgan forcefully.

Hayley does but she presses it as lightly as possible.

``Why are you hesitating?''

``Because I don't like this!  Someone else is getting hurt! It's supposed to be me!  Not them,'' Hayley sobs.

``Welcome to life,'' says Morgan mercilessly.  ``Press the button.''

Hayley presses the button and then claps her hands over her ears trying to block out the sound of Jonah screaming.

``Hayley, look at the gauge next to the button.  When it turns red, he will die.  Now, press the button.

Hayley presses the button and Jonah screams again. {[}\textit{Challenge 2: Fake seizure and faint --\textgreater  }\textit{\hl{Overcome}}\footnote{\textbf{q.google }I'm smugly pleased about this move.  It both followed orders technically but also was used as a protest, both to Gerhauser (Dr., Jonah hasn't seen Agent), and to Hayley. \textsubscript{04/06/13 3:40pm}}\footnote{$\rightarrow$\textbf{Suko T }How was this a protest to Hayley?  Just curious.  So far as it seemed to me, it looked like Jonah trying to make it easier on Hayley by acting insensible. \textsubscript{04/06/13 5:11pm}}\footnote{$\rightarrow$\textbf{q.google }I'm breaking it down more finely than I think he would but it's something like this: She insists on following orders without (to his eyes) thinking about them.  He worries that this going to get him hurt or killed.  Well this is a case where he \_clearly\_ is going to be hurt.  And yet she is still doing it.  Is she \_really\_ willing to hurt him badly?  Screaming in pain normally is a sign to him that he should stop, unless he absolutely has to continue (as happens to street medics).  So this is his sign to her. \textsubscript{04/06/13 8:04pm}}\footnote{$\rightarrow$\textbf{Suko T }Ahhh... I see. Yeah, that's going to go right over her head.  Let's just say in her world, screaming doesn't mean stop. \textsubscript{04/06/13 11:04pm}}\textit{!}{]}  His body convulses mightily and then falls limp.  Hayley screams and flings herself at the window, pounding at it and calling out to Jonah.

``Hayley, press the button.'' says Morgan, implacably.

Hayley looks rather shellshocked and stares down at the button for a moment.  Then she takes a deep breath and she seems to get unnaturally calm and she stops crying.  She looks a little glassy but she presses the button firmly and watches Jonah twitch.  Jonah tries not to look conscious but fails and it just looks strange.  {[}\textit{Challenge 2: Don't break down --\textgreater  sent back to pool}{]}. Hayley sways a little but stays on her feet and presses the button again when Morgan orders her to.



The last shock was incredibly painful and Jonah starts feeling an impending sense of doom. He will not be able to take much more of this.  He is tempted to press the button to release the straps {[}\textit{Challenge 2: don't push the button --\textgreater  }\textit{\hl{sent back to pool}}\footnote{\textbf{q.google }I thought about matching it but Jonah doesn't really want to support this particular game by this point, so he isn't fighting hard against the temptation.  It didn't quite fit to use up the threat. \textsubscript{04/06/13 3:43pm}}{]} but doesn't.



``Hayley, what color is the gauge?''

``Crimson,'' says Hayley quietly.

``Hayley, kill Jonah,'' orders Morgan.

Hayley looks up at Morgan and then back down at the button.  {[}\textit{Challenge 2: Resist the order to kill Jonah --\textgreater  Matched}{]}.  Her fingers twitch toward the button but her hands stop and fall to her sides and she does not press the button.  Everything goes a little fuzzy after that point and the next thing she knows, she is waking up in MedBay.



Dr. Gerhauser enters the room where Jonah is and releases him from the straps. She injects him with something that makes him feel much better almost immediately.  Dr. Gerhauser looks sad.

``What was the purpose of all this?'' says Jonah angrily.

``Hayley has very strong conditioning.  She needs to face that here rather than in the field.''

``So that was \textit{Hayley} doing that?'' says Jonah, sounding furious.

``Yes but -''

Jonah doesn't let her finish and leaves the room.  His parting shot as he leaves is ``Have you tried that chair yourself? \textless pauses long enough to start considering this might be a non-rhetorical question\textgreater  You really should.''


\sceneHeadline{The whole team....sorta...}

Oliver exits the shooting gallery room and Jaya immediately slugs him.  Oliver catches himself and manages to shove Jaya.  They scuffle a little.  Jari just watches them and stays out of it. 

``Now you know what it is like to follow bullshit orders!'' says Oliver and he storms off.

Jaya just sputters angrily, unable to think of a clever rejoinder quickly enough.



Oliver returns to the bunk, showers and then goes to the Cistern to swim and have some privacy.



Jaya heads back to the bunk area but dawdles enough that she doesn't run into Oliver in the hallway.  While she's lurking around the bunk area, Carruthers walks by.  ``Are you okay?'' she says, with friendly concern.

``I'm fine, I'm just out here for a smoke,'' Jaya lights up a cigarette she clearly didn't have out before.

``Uh o-o-kay...'' stammers Carruthers and looks away.

Emboldened by Carruther's deference, Jaya snarls at Carruthers, ``You just need to stay out of my face okay?  Get the fuck away from me!''

Carruthers stumbles back in surprise and then walks off.

Jaya continues to wander around the base and picks a few fights.



\hl{Jonah goes to Trenton's lab.}\footnote{\textbf{q.google }I may want to amend how this goes depending on what's possible at session start. \textsubscript{04/06/13 3:46pm}}  



Hayley wakes up in Medbay.  She asks to stay in MedBay, but is told that when it is not being used, they shut off the lights (``It's okay!  I'm used to being in the dark!'') and the ventilation (``Oh I guess that would be a problem'').  She looks sad.  Swan makes the mistake of asking if she's okay.``No.''

``Oh, ah, do you want to talk about it?''

``Oh I can \textit{do} that?'' says Hayley with awed wonder.

\hl{Swan looks very uncomfortable}\footnote{\textbf{q.google }I think we should call this bit in Rook's memoirs ``God help you Mr. Swan''. \textsubscript{04/06/13 3:47pm}}\footnote{$\rightarrow$\textbf{Suko T }+1  Let's hope that he pawns this one off on someone else.  Like perhaps Jaya.  That could be hilarious. :) \textsubscript{04/06/13 11:05pm}}.



Agent Morgan finds Jaya and they head to the Ops room to talk.  Morgan kicks out whomever is in the room and then sits down and indicates that Jaya should sit also.

``How do you think your team did?''

Jaya visibly swallows and babbles nervously, ``I haven't spoken with my team yet but I know that they will be performing optimally so I know that we will have succeeded, but I just haven't talked to them yet...''

``Jaya I need you to concentrate on what I am about to say.''

``Uh, I left my notebook in the other room.. I can just go get it...''

``No.  You'll just have to concentrate a little harder.  Are you ready?''

``Yes...'' says Jaya faintly, looking terrified.

``\hl{Things are going to get more dangerous from now on.  Your team is a mess.  You have no skills as a leader.  Hayley is nothing but a puppet.  Your sniper has authority issues.  Your medic -'' Morgan pauses and looks at Jaya scornfully, ``do you know what he is hiding?}\footnote{\textbf{q.google }And this part is called ``Agent Morgan cuts loose''. \textsubscript{04/06/13 3:51pm}}''

``Uh, what?''

``I thought so.  At the very least do you trust him?''

``Jonah?  Yes.''

``\hl{With your life}\footnote{\textbf{q.google }Not to contradict Morgan's main point, but Jaya effectively \_does\_ trust Jonah with her life every time she's injured in the field. \textsubscript{04/06/13 3:49pm}}?''

``Do I trust him to do his job?  Yes!  But with my life?  Hell no.  I don't trust anyone with that.  I don't trust \textit{you} with that!  My life is my own!'' says Jaya passionately.

Morgan looks displeased.  ``Your team is at a decision point.  The time to prepare is limited.  \hl{Your}\footnote{\textbf{Suko T }Clearly not ``The'' or ``Our'' \textsubscript{04/06/13 2:18am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }She did say ``Your''. \textsubscript{04/07/13 1:34am}}\footnote{$\rightarrow$\textbf{Suko T }Oh yes, that was subtly done but quite clear (and repeated later).  I just wanted to point it out in the notes that this wasn't a typo.  :) \textsubscript{04/07/13 9:47pm}}Directorate is about to go to war.''

``Does this mean we get promotions?'' says Jaya.

Morgan ignores the interruption, ``People are going to die.  That may include yourself.''

``Ha!'' laughs Jaya scornfully, ``not me!  I'll be fine,'' she says smugly.

``Oh really?'' says Morgan angrily.  ``Do you think you can take me?''  She pulls out her gun and Jaya leaps to her feet nervously.  Morgan removes and tosses aside the clip and places the gun on the table.  ``I don't need this to kill you.  I can kill you with my bare hands,'' she hisses and advances on Jaya.

``I know that!  Shit!  I know!'' says Jaya, starting to get really freaked out now.  She starts retreating around the table, knocking over a chair over in front of Morgan.

``When I say your Directorate is going to war, I mean your life is in danger.  You need to decide if you are in this fight 100\% or not.  \hl{You will bring this question to your team}\footnote{\textbf{q.google }Morgan may be very smart, but she really isn't grasping the weak link in this process is she? \textsubscript{04/06/13 3:54pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{04/08/13 7:23pm}}.''  Morgan says as she continues to stalk inexorably toward Jaya, kicking aside the fallen chair effortlessly.



The situation has grown so odd that\hl{Jaya finally realizes that she must be tripping}\footnote{\textbf{q.google }This is the Tank, foreseeing the future again.... \textsubscript{04/06/13 3:54pm}} and takes a swing at Morgan.....



\textbf{{[}2 Backlash Tokens left{]}}



\jumpHeadline{ Backlash Challenges }  



\begin{itemize}
\item Challenge 3: Take down Rook without ending up in a compromising position.  Unashamed 1 (Hayley) + Dancer 1 (Hayley) + Truncheon 2 (Jaya) $\rightarrow$ Matched
\item Challenge 3: Notice what Jari is up to.  Vigilant 3 (Jonah) $\rightarrow$ Matched
\item Refresh: Sniper Rifle 2 (Oliver)
\item Refresh: Adrenaline Junkie 2 (Jaya)
\item Challenge 1: Notice machinery.  Senior Constable 2 (Jaya)  --\textgreater  Overcome! (\textbf{1 VP Jaya})
\item Refresh: Athletics 2 (Hayley)
\item Challenge 1: Not look like an idiot --\textgreater  sent back to pool
\item Challenge 3: Climb the wall to the ready line. Nose for Breadcrumbs 2 + Conditioned 2 (Hayley) --\textgreater  Matched
\item Challenge 2: Climb the rope. Athletics 2 (Hayley) --\textgreater  Matched
\item Challenge 2: Teach Oliver to treat the patient.  Street Medic 2 (Jonah) + Focused 2 (Oliver) --\textgreater  Overcome! (\textbf{1 VP Jonah, 1 VP Oliver})
\item Challenge 2: Heal Trenton.   {\color[RGB]{255,0,0}Flaw 2 Lost his cool (Jonah)}  --\textgreater  Matched
\item Refresh: Street Medic 2 (Jonah)
\item Refresh: Focused 2 (Oliver)
\item Challenge 1: Yellow paper --\textgreater  sent back
\item Challenge 2: Orange and a few red paper.  Sniper Rifle 2 (Oliver)  --\textgreater  Matched
\item Challenge 3: more red paper.  Sidearm 3 (Jaya) --\textgreater  Matched
\item Challenge 4: Don't die from paper cuts.  Adrenaline Junkie 2 (Jaya) +  {\color[RGB]{255,0,0}Flaw 2 die in simulation (Jaya)}  + Crackshot 3 (Oliver) --\textgreater  Matched
\item Challenge 1: ???.  ???  --\textgreater  Overcome! (\textbf{1 VP Jonah})
\item Challenge 2: Fake seizure and faint.  Social Chameleon 4 (Jonah) --\textgreater  Overcome! (\textbf{2 VPs Jonah})
\item Challenge 2: Don't break down.  Protocol 1 (Hayley) --\textgreater  sent back to pool
\item Challenge 2: Don't push the button.   {\color[RGB]{255,0,0}Flaw 1 exhausted (Jonah)}  --\textgreater  sent back to pool
\item Challenge 2: Resist the order to kill Jonah.   {\color[RGB]{255,0,0}Flaw 2 catatonic (Hayley)}  --\textgreater  Matched 
\end{itemize}



Backlash Tokens generated from Flaws from this session: 7

Leftover Backlash in pool from previous sessions: 2
\textbf{Total Backlash Pool: 9}

\jumpHeadline{VP Totals }

Jaya 1

Jonah 4

Oliver 1


\jumpHeadline{Quotes }

``Negotiation requires words.  I just use my face.''

\extraIndent{-Rebecca}



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 8:47am
\end{flushright}

