\setcounter{chapter}{ 18 }
\chapter{\textbf{``You Talkin' to Me?''} }




\begin{center}
 {\LARGE \textbf{(Backlash 3/2 \& Shore Leave)} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} April 8th, 2013



Words were said.  Many many words.  Some of them were even quite nice.  Some decidedly less so.  Information was shared.  Huzzah!



\noindent\hrulefill




\jumpHeadline{Backlash }
\sceneHeadline{SAC-09  {[}9 Backlash Tokens{]}}

\textbf{Jaya and Morgan}



Fairly certain she's tripping, Jaya headbutts Agent Morgan and causes Morgan to step back.  Morgan's nose is bleeding.  Morgan stands there looking at Jaya while Jaya looks back, her body tensed for a fight and her eyes looking a little wild with her eyelid twitching.



Morgan walks over to the table and picks up her gun.  Jaya straights up the chair she knocked over but keeps her hands on the chair.  Morgan reaches down and picks up the clip off the ground and loads it into the gun and checks the chamber.  Jaya watches her warily and shifts her grip on the chair to pick it up slightly.  Morgan slides the gun into her holster and turns to face Jaya.  Jaya sets the chair down.



Jaya starts backing toward the door, ``Should I go back to the barracks?''

``I should apologize,'' says Morgan unexpectedly.

Jaya's eyes go wide.  ``No need!'' she says hastily. `` I can just go.  We don't need to talk about this.  Ever.''

``\hl{I was surprised to find someone with the family you do, who has this attitude toward women}\footnote{\textbf{q.google }Jaya's family makes a lot of sense to me.  It's not as common in the U.S. but it's pretty common elsewhere. \textsubscript{04/15/13 11:46pm}},'' says Morgan.  Jaya goes pale (or as pale as she can anyway).  \hl{Morgan continues conversationally, ``I had a younger sister once.  I never realized until now how much you remind me of her.''}\footnote{\textbf{Rebecca S. }OH SHIT! 
DOES THIS MEAN JAYA REMINDS MORGAN OF ESTER?!?!

WHAT DOES THAT MEAN?! \textsubscript{05/18/14 10:08pm}}\footnote{$\rightarrow$\textbf{Suko T }Unpredictable and cunning- I think it's a complement? :)  Okay maybe if you leave out the sadistic and CRAZY part. \textsubscript{05/19/14 11:47pm}}

Jaya says something noncommittal and keeps edging toward the door.  She bolts as soon as Morgan dismisses her.


\sceneHeadline{Jonah and Trenton}

Jonah goes to Trenton's lab.  Rook is there talking with Trenton.  ``She left the station with two Mark 2's and two of those.....???\footnote{\textbf{Suko T }This whole convo was not noted very well, I was catching up on Jaya vs Morgan notes.  Please fix if you can. \textsubscript{04/09/13 11:18pm}}''  ``You should ask Jari about that.'' ``Anything up to and including rifles''\footnote{\textbf{Suko T }This whole convo was not noted very well, I was catching up on Jaya vs Morgan notes.  Please fix if you can. \textsubscript{04/09/13 11:18pm}}  

Rook asks Jonah, ``Can I help you?''  At Jonah's no, Rook leaves the lab.

``Can I help you?'' asks Trenton.

``Not really.  I was wondering if you had a chance to look at those maps,'' says Jonah.

``Ahhhh right.  About that....'' Trenton looks around.  ``I've been a little busy...''

Jonah says leadingly, ``I don't know if you read our reports-''

Trenton laughs.  

``Do you want to know?  Can you talk about it?  I mean, I haven't seen anything like it,'' says Jonah.

``Yeah but I bet these guys have.''

``\textit{Have} they?  'Cause they don't ...'' \textit{\textless pauses}\textgreater .  ``Does anyone at University have experience in a fight?  Getting shot?'' asks Jonah.

``Nah, not really,'' Trenton shrugs.  ``I mean, \textit{I} have, back when I was at New Station.''

``Gang fights aren't war though.  In gang fights whole buildings don't disappear.''

``\hl{Well, they didn't really disappear, more like they just exploded}\footnote{\textbf{q.google }Oh, that's ok then. \textsubscript{04/15/13 11:49pm}}.''

``What?  How???'' asks Jonah

``Victor has some ideas, but they would take a massive amount of energy.  Morgan has some ideas but they haven't been confirmed.  You know, Morgan's not a scientist.  Neither is Dr. Gerhauser,'' says Trenton somewhat conspiratorially.

``What do you mean?  She's not a doctor?''

``No, she is, but she's mostly self taught if you take my meaning.  She knows things but...think of it this way.  Do you know how to drive a train?''

``No.''

``But you've seen trains and you've ridden in lots of trains, right?''

\hl{``You mean reading about how something works is different than seeing it.  Yes.  That's been happening a lot lately.''}\footnote{\textbf{q.google }Did he say that?  I seem to just remember giving him a slightly wild look.  (As in ``\_What do you mean she's not a doctor\_?  Does she not know what she's doing?!'')   But even if he didn't say that it flows well, so leaving it alone. \textsubscript{04/15/13 11:51pm}}

\hl{``You should ask Larissa,'' says Trenton}\footnote{\textbf{Nathaniel Ford }There was another comment Jonah made that prompted Trenton to get off-topic here, something about staying sane I think. \textsubscript{04/12/13 12:27am}}.

``What?'' says Jonah, thrown by the change of topic.

``She seems nice,'' Trenton says archly.  At Jonah's look of puzzlement, he shakes his head in mock disappointment.  ``Ah sorry I thought you were talking about something else.''



With alarming swiftness, Jonah pulls out his gun and points it at Trenton's head.  Trenton flings his hands up in a placating gesture.  Jonah, asks, \hl{with forced calmness}\footnote{\textbf{q.google }This is, to a slight degree, an act.  Jonah \_is\_ freaked out, but using that to get Trenton to tell him what he needs to know will work in a pinch. \textsubscript{04/15/13 11:54pm}}, ``What is going through your head right now?  I read things, so I know that there's adrenaline and that adrenaline can be useful for heart problems.  It can cause them too.''

``Whoa okay okay!'' says Trenton. ``What do you want?  Sorry I didn't know it was that bad!''

``It's not so great is it?  To be in these dangerous situations all the time.''

``Okay I get your point!  Can you put the gun down now?'' says Trenton earnestly, looking quite alarmed.  ``I don't think they send you out to die.''

``They want us to go out and then come back?''

``Yes''

``That's news to me,'' says Jonah bitterly.  ``You haven't been out there.  If you want people to come back, you don't put them where bullets are flying.  Why are they doing all this?  If we're valuable, why put us through this?''

``I think that you need to have traumatic shared experiences for the Tank.''

``Do you know how this Tank thing works?''

``Well Gerhauser knows better --''

``Tell me what \textit{you} know.''

``Uhhh sure!  But how about a drink?''

``Yeah.  Sure,'' says Jonah and holsters his gun.  With forced joviality: ``I don't want to shoot anyone.  But the good news is if there \textit{was} shooting, I'm a medic.''

\hl{Trenton looks only marginally comforted}\footnote{\textbf{q.google }That's the idea.  The ``forced joviality'' \_is\_ an act.  He wants Trenton to be both afraid, and see a way out of being afraid. \textsubscript{04/15/13 11:56pm}} by this news.  Trenton pulls out a bottle of fairly nice alcohol and pours two glasses.

Trenton says, ``It works on a neurological framework.  It operates on the neural sheath to open a new pathway.  Your brain can't make this happen by itself.''

``Why us?''

``Let's just say that the device only fits over certain shapes of heads.  And you all have the same shape of head in this analogy that I'm making up.''

``What about Team 2?''

``\hl{They have a different shape of head, that is 15-18\% less effective than yours}\footnote{\textbf{q.google }This was a hysterical line.  I had to hold back to not laugh. \textsubscript{04/15/13 11:57pm}}.''

``What do you mean by 'effective'?''

``When you were in the Tank, what did you see?''

``It was like being in a war all over again.''

``So it was stuff you remember but there was some other stuff you don't remember, right?  That stuff was the other pathway opening up.''

``What will these pathways do?''

``Communication, like when you use the radios.''

``Communication with who?''

``Only a couple of people can do it.''

``Are they alive?''

``Well those people are you guys.''

``How did they find us?''

``When you joined the TA, they took a genetic sample.  You know, your tattoo has everything in it.''

\hl{A look of fear}\footnote{\textbf{q.google }I love this bit.  It's not just fear: it's a flash of near \_total\_ panic.  It's got layers: If they know how to do that then they know who really is.  But the far worse thing is if they \_don't know\_.  Because if they don't then they think he's the original bearer of the tattoo ... and that means he may \_not\_ be the right person for the Tank.  And despite what Trenton says that could mean \_anything\_ could go wrong.  This is primal fear, and it's all intense and then almost immediately hidden away. \textsubscript{04/16/13 12:03am}}\footnote{$\rightarrow$\textbf{q.google }(They know of course.  And he knows they know.  He just can't admit it to himself because he has no idea how to deal with it.) \textsubscript{04/16/13 12:03am}} briefly passes over Jonah's face and he asks with studied casualness, ``What happens if you have the wrong profile?''``I don't know.  It doesn't work I guess.''

``Nothing happens?''``Well it would be like a bad trip, but not a useful one.  But we double checked all of you when you got to the base,'' says Trenton attempting to be reassuring.

``Let me get this straight, you are trying to turn us into radios?''

``It's a bit more complicated than that.''

``It's an awful lot of effort for just radios.''

``Yeah but it's more sophisticated -- you don't have to talk to the other person to be heard.''

``Who hears you?''

``\hl{The person on the other end}\footnote{\textbf{q.google }\_They can hear what we are thinking\_ \textsubscript{04/16/13 12:04am}},'' shrugs Trenton.

There's a tone over the intercom and Dr. Gerhauser says, ``Do you have the report for me?''

Trenton sighs and stands.  ``I've got to go take care of this.''  He gestures to the bottle.  ``You can drink the rest, just leave me some of the good stuff okay?''

He leaves, and Jonah follows soon after, taking the bottle with him.


\sceneHeadline{Hayley and Swan}

Swan sits down next to Hayley.   {[}\textit{Ongoing Challenge: Gerhauser Sisters.  Get Swan to confront Dr. Gerhauser over what is being done to the team.  Gorgeous 3}{]}  Hayley is looking particularly woebegone and this seems to distress Swan.  Hayley says that she has never done something like that before and she hated it.  She starts crying and saying that she hears Jonah screaming every time she closes her eyes and it makes her feel awful.  She repeats over and over that she's the one who is supposed to get hurt, not others, everything is all wrong and backward and confusing.  Also she's a failure because she didn't follow orders even though nothing prevented her from doing so.  Thinking of this makes her stop crying and instead she looks horrified.

``Do I need to kill Jonah?'' she asks Swan, her eyes huge and scared.

Swan goes pale, ``NO!  No you don't.''

Hayley smiles at him in relief. ``Okay.''  Then she frowns, remembering something. ``But I do need to hear that confirmed by Agent Morgan.''

Swan hurries out of the room.  Hayley gets another hour in MedBay, which she mostly spends trying and failing to fall asleep.



Morgan calls Hayley over the intercom.

``Constable Hayley, this is Agent Morgan.  I am countermanding my order to kill Jonah.  Do you understand?''

``Yes''

``Good.  Is there anything else?''

``Yes.''

When Hayley doesn't elaborate, Morgan prompts, ``What?''

``There are things I need to ask you.''

``That will be dealt with later.  Please relinquish the Medbay.''

``Is that an order?'' says Hayley, rather sulkily.

Hayley can hear Morgan click the intercom off and on.

``Hayley. \hl{Please relinquish the Medbay}\footnote{\textbf{q.google }I really liked how she didn't answer the question, because she can't really answer either ``yes'' or ``no''. \textsubscript{04/16/13 12:06am}},'' says Morgan sternly.

``Okay,'' says Hayley.  She gets prepared to leave but does so as slowly as possible.  She gets dressed, she tends to her healing wounds, she makes the bed, she folds her hospital gown....you get the idea.  On the way out of the Medbay, Hayley passes an operating room and through the window, she sees \hl{Swan yelling at Dr. Gerhauser}\footnote{\textbf{q.google }It's interesting to speculate exactly what Swan is yelling about. \textsubscript{04/16/13 12:20am}} who is not yelling back but is very tense.  Hayley pauses when she sees Swan and waves at him.  Dr. Gerhauser sees Hayley and comes out into the hallway.



``It has been brought to my attention that you may not be in the best psychological condition,'' says Dr. Gerhauser, somewhat grimly.

``No, I'm not,'' says Hayley.

``Are you still able to perform your duties?''

``No.  Not to the best of my abilities.''

``Well can you perform them well enough?''``I don't know.''

``Are you a danger to yourself or others?''

``Not to myself,'' says Hayley promptly.

``But to others?  Who?''

``It depends on the orders.''

``But you think you would hurt someone else?  You are not in the best psychological condition right now.''``No.  I am angry and upset.''

``Well I hear you have requested Shore Leave, you should go rest. Go home.''

``I can't.  I have no home.''

This leads to a discussion of Hayley's contract and who is her legal owner.  Dr. Gerhauser has to explain about liens and how Agent Gerhauser is only temporarily Hayley's contract holder.  If Hayley wants to, she could go see Gillian.  She doesn't have to avoid her.  Hayley misses Gillian terribly but has no precedent for this situation and says she will have to think about it.  Dr. Gerhauser leaves.  Swan and Hayley look at each other for a long moment.  When he says nothing, Hayley turns and leaves Medbay.


\sceneHeadline{Oliver and Morgan}

Oliver goes to PG2's barracks and settles into a game of cards with Carruthers, Javier and Davis.  After a while, there is a knock on the door and Jari tells Oliver that Morgan needs to speak with him.



When Oliver shows up in her office, Morgan is uncharacteristically staring off into space.  She has a bandage on her nose.  Oliver salutes. 



``Have a seat.  This is off the record,'' she says.  ``Congratulations on your testing results.  There will be more details later.  Myself and \hl{the Triumvirate are pleased}\footnote{\textbf{q.google }Whoa. \textsubscript{04/16/13 12:20am}}.''

``Triumvirate?  Ah, the guy who showed up during testing.''

Morgan nods.  ``Do you still have the desire to go after the Orc of Anglia?''``I still have this desire.''

``I don't want to send you alone.''

``It will be dangerous.''

``Yes, but you wouldn't survive.''  Oliver starts to say something but Morgan continues, ``And you wouldn't succeed either.''

``Okay,'' says Oliver.  After a small pause, he asks, ``So the testing went well?''

``The testing was... more stressful than anticipated,'' says Morgan. ``Have you talked to your team?''

``No.''

``Would you say that's characteristic of your team?''

``Well I deliberately avoided them for a while so I'd say yes.  What happened?''

Morgan says slowly ``I... may have judged by a metric not suitable to the situation.  I expect that Jonah and Hayley will be more stressed than normal.''  She continues more briskly, ``but \hl{since you will be paired with Hayley}\footnote{\textbf{q.google }I think this is the best clue about the breakdown between Operators and Agents.  Not that we really need clues for something that will come clear soon. \textsubscript{04/16/13 12:22am}}, I expect that will work out.''

``To go after the Orc of Anglia?  What about the others?  Why Hayley?''

``You can teach her a skill set that we believe she should pick up very quickly.''

Oliver looks thoughtful, ``I tried to take her under my wing a while ago, I don't know what came of that.''

``When the time comes, you will have to make that shot and others may also die.''

``That is what I am trying to avoid,'' says Oliver.

``You will not be able to,'' says Morgan.

``I live to serve,'' says Oliver.

``Enjoy your shore leave,'' says Morgan, dismissing him.

``I will do what I can to pull the team together,'' promises Oliver as he leaves.


\sceneHeadline{Jonah and Dr. Gerhauser}

Jonah hunts down Dr. Gerhauser, but doesn't manage to see her.  He eventually gets an appointment with Swan after claiming a headache.  He rattles off a lot of medical jargon at Swan, who patiently listens and eventually prescribes him an ibuprofen.



\textbf{{[}}\textbf{\hl{0}}\footnote{\textbf{Suko T }Correct? \textsubscript{04/10/13 12:50am}}\textbf{ Backlash Tokens left{]}}


\sceneHeadline{\hl{Ops Room}}\footnote{\textbf{Suko T }Notes are sketchy in this part due to all of the participants and me being in the scene, so please fill in missing convo, actions, and descriptions pls! \textsubscript{04/10/13 12:30am}}

Everyone is called to the Ops Room.  Jaya arrives first, and Oliver arrives not long after.  They are the only ones in the room and sit across the table from each other (slightly offset).

``Looks like someone gave Morgan hell,'' says Oliver conversationally.

Jaya glares at him.

``Nice job on the firing range,'' tries Oliver again.

``I died first,'' grumbles Jaya.

``\hl{So? I died right after that,'' says Oliver}\footnote{\textbf{q.google }Those of you who were there should fill this in but what I remember is Oliver trying to convince Jaya that it was a no-win scenario, which he thinks they won (or at least handled well enough to be seen as excelling at). \textsubscript{04/16/13 12:24am}}.



Hayley shows up, looking pale and somewhat ill.

Jaya praises her for her job on the rope climbing exercise, but Hayley's mind is clearly stuck on something else and she will not be cheered up.  Although she does thank Jaya for the praise, she contradicts Jaya when Jaya says that Hayley did a great job.

``I didn't follow orders,'' says Hayley.

``What do you mean?'' asks Jaya.

``I failed to kill Jonah,'' says Hayley miserably.  Oliver and Jaya are alarmed and Hayley gives a few details about electroshocking Jonah but doesn't get very far before she turns green and asks to be excused and runs from the room.



REBECCAxxBEGINxxHIGHLIGHTxxJaya looks at Oliver.  ``Are we in the Tank?''

``No.''xxENDxxHIGHLIGHT\footnote{\textbf{q.google }:) :) :) \textsubscript{04/16/13 12:25am}}



Jonah shows up.  Jaya and Oliver congratulate him on not being dead.  He's less than placated by the congrats.  He is clearly very angry and upset, but avoids their questions and is non-committal.



Dr. Gerhauser and Rook show up and ask where Hayley is.  Jaya goes to go fetch her and manages to track her down.  Hayley's being sick in one of the bathrooms.  Jaya does her best to comfort and clean her up and gets her back to the Ops Room.



Hayley sits down next to Jaya (across from Oliver) and looks at Jonah.  She smiles at him and says, ``I'm so glad you're not dead.'' And bursts into tears.  Jonah is stone-faced and silent.  

Rook says, ``This was to be a report on your performance on the tests, but we can postpone until later.''

Dr. Gerhauser attempts to calm Hayley down.  ``Just focus on something, and take deep breaths...''

\hl{``I know all the tricks,'' sniffles Hayley.  ``I'm just not very good at them.''}\footnote{\textbf{Adam Kenney }+1 \textsubscript{04/14/13 5:16pm}}

Jaya turns Hayley to face her, ``Constable Hayley, I am giving you a direct order.  Just stare at Oliver, listen to what Agent Rook has to say and stop crying.''

\hl{This works amazingly well}\footnote{\textbf{q.google }Yeah, that was exactly the right medicine. \textsubscript{04/16/13 12:26am}} and Hayley's sobs slow to just the occasional sniffle and a few tears.  She takes some deep hiccupy breaths and fixes her gaze on Oliver.  Oliver looks a little uncomfortable.



Once everyone is settled, Rook starts giving the report.  ``Naturally we had to use a sampling method to perform some of these tests due to the limitations at this base.  Therefore the results will be done as a group, rather than as individuals.  \hl{You may wish to keep that in mind when you talk to HR for future career moves in the TA.}\footnote{\textbf{q.google }Rook is something else. \textsubscript{04/16/13 12:28am}}\footnote{$\rightarrow$\textbf{Suko T }by which you mean awesome, right? :) \textsubscript{04/16/13 11:06am}}  For Weapons Assembly, you did well.  Everything was within established parameters.  During the Fitness Test, there was a bit of aggressiveness but due to the participants involved we actually feel this was an asset.  Demonstrating an Arrest.  Excellent job Jaya and Hayley, if I do say so myself,'' Rook says with a smile.  Oliver doesn't quite stifle a chortle at that.  Rook continues, ``Jari wants to pass along his compliments.  He believes that the best performance goes to Oliver and Jonah.  It was book perfect and you caught onto the twist in the situation very quickly and dealt with it appropriately.  Inter-team Teamwork exercises with the other team worked.  As a brief aside - less destruction of base property next time, please.''



Jaya says indignantly, ``Well if that information had been provided to us, that might not have happened.  If we had better mission information, we would have done better.  We performed excellently given the tools that we were given.  And if you don't tell us what the rules are, you can't expect us to follow them.''



Rook actually nods in agreement, ``A fair point.  Next time we will attempt to be clearer.  Well, despite the destruction of base property, as valuable as it was, the exercise was successful and your competency was within acceptable parameters.  The Medical and Leadership test was as expected.  You demonstrated leadership and the ability to overlook personal prejudices to achieve mission parameters.  The Extreme Duress Test went well.  It was a test of performance under a stressful situation.  Agent Gerhauser was very happy with the results.''

``What did you learn?'' asks Oliver.

``The immediate decision to hold your ground spoke well of you, as well as your choice to assist your fallen commander.''

Jaya makes a noise of protest, but Rook nods to her and continues smoothly, ``And you demonstrated Leadership in being the first to fall and your choice of targets.  Please be aware that it was not a situation where you could win.''

``\hl{That's stupid because you should always be able to win,}\footnote{\textbf{q.google }http://www.imdb.com/title/tt0084726/trivia?item=qt0454866

All we have to do is find the simulator. \textsubscript{04/16/13 12:34am}}`` says Jaya, clearly annoyed.

``That's a commendable attitude,'' says Rook.  He pauses and looks at Dr. Gerhauser.  ``For the last assessment, I'll have Gerhauser speak to the results.''



Dr. Gerhauser stands.  ``This is off the record.  You are to keep what you hear amongst yourselves only.  This information is not to be shared.  Do you agree?''

Oliver agrees.

Jaya says, ``Well who would we tell?'' which Dr. Gerhauser takes as agreement.

Jonah says, after a long silence.  ``On one condition.''  He pauses.  ``I may have some comments.''



Dr. Gerhauser nods.  ``Constable Hayley has some very deep conditioning.  It was necessary to test the degree.''

``If that's what you were doing, why me?'' asks Jonah.

``\hl{A judgement was made that Constable Gemayel was the only one who she might react to strongly enough to break her conditioning}\footnote{\textbf{q.google }If Jonah wasn't so pissed off he'd only be disappointed that didn't work.  (It may have worked, but he doesn't know that.) \textsubscript{04/16/13 12:36am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{04/16/13 11:04am}},'' says Dr. Gerhauser.  Jaya looks somewhat suspiciously at Jonah and Hayley at this news.  Dr. Gerhauser continues, ``\hl{She needs to learn when orders are bad}\footnote{\textbf{q.google }This is interesting because I think ``when orders are bad'' is something the whole team has strong but very varied opinions about. \textsubscript{04/16/13 12:38am}}\footnote{$\rightarrow$\textbf{Suko T }Indeed, it should be interesting to see how that is explained to Hayley.  I could see this going....poorly. \textsubscript{04/16/13 11:04am}}.''  Dr. Gerhauser addresses Jonah directly, ``Thank you for your service.  You will receive extra hazard pay for your service.''  She shifts to address the whole team.  ``Going forward, please be aware that it is our desire that she put her teammates above her orders.''

``Who did this to her?'' asks Oliver.

``It was a conglomerate of interests called Redemarrer.  It was broken up and sold off for parts not long after the war with Nicklepan.  It is a little hard to say exactly what they did, but suffice to say they created a group of people who are extremely pliable and obedient.  From Redemarrer, eventually Hayley's contract was purchased by Samson Vorrutyer and upon his death, passed on to his daughter, Gillian.''



``I have a comment,'' says Jonah.  ``You could have given me more information on the test,'' \hl{he says angrily, his voice getting louder and louder until he is yelling}\footnote{\textbf{q.google }Retrospectively, I consider this scene one long refresh for Social Chameleon.... \textsubscript{04/16/13 9:40am}}, ``you could have prepared us for Nicklepan.  Did you know what was going on there?  Why didn't you tell us?  Do you have any idea what we saw?  Instead you sent us in to a place where people were ordered to kill us!  They killed everyone there!  There was no one left!''



Dr. Gerhauser looks down, her knuckles turning white.  She looks over at Rook who smoothly takes over.  He says placatingly, ``We understand the stresses you were under.  We didn't know what was going on in Nicklepan.  We expected that it was a local political disturbance, something that you could have found out from the local news and then returned to to base.  We didn't expect what happened, or mean to put you in that situation.  You are the only ones who can use this technology, and this technology will be necessary for the long term survival of your nation.''

``Not '\textit{your} nation'?'' asks Oliver \sout{ \hl{Jonah} }\footnote{\textbf{Adam Kenney }I think Oliver said this. Ever the patriot... \textsubscript{04/14/13 5:19pm}}\footnote{$\rightarrow$\textbf{Suko T }Heh, true enough. I'll change it and Ion can change it back if he wants to claim it. :) \textsubscript{04/15/13 1:08am}}\footnote{$\rightarrow$\textbf{q.google }No I agree, I think Oliver said it. \textsubscript{04/16/13 12:43am}} pointedly.

``Agent Morgan, Dr. Gerhauser and myself... none of us are natives of this nation,'' says Rook matter-of-factly.

``But you work for the TA.  Doesn't that make this your nation too?''

``Not in the same way it is for you.  We don't belong to it like you do,'' replies Rook.  He changes topic, ``Your question of preparation is a good one.  We can provide training --''



Jonah interrupts, ``What training?!  Nothing we are doing here is anything we can have any previous experience of.  You've been in a war?''  At Rooks nod, Jonah continues, ``It's nothing like being a beat cop.  On a beat, you fight with people.  In a war, bullets don't care who you are.  People die randomly all the time.  There needs to be more than this.''

Rook replies, ``At the conclusion of this meeting, you will go on Shore Leave.  You can choose to go your own way at that point, and we will not force you to return.''

Jaya immediately jumps in and claims that her team will be returning to the base, of course, no question.

Jonah interrupts her.  ``Chief, you're a great cop.  But...''.  She glares at him.  He trails off and pauses.  ``We can talk about that later.''



Rook looks at the team.  ``Are there any more questions?''

Hayley looks away from Oliver for the first time and raises her hand.  ``I have a question for Dr. Gerhauser.''  She looks at Dr. Gerhauser and asks, ``Why didn't you ask me?''

``Ask you... what?'' says Dr. Gerhauser, uncertain what Hayley is referring to.

``Ask me what would have worked best.   For the test.  If that's what you wanted, why didn't you tell me?  I know myself.  I know myself better than you.  I know very little about anything else, but I have spent 19 years of my life learning how I learn best.  So, why didn't you just ask me?'' she repeats plaintively.

``What should we have done?''

``Explain it to me.  Give me a goal.  Tell me what I was supposed to do, what I needed to achieve.  \hl{If I was supposed to put my teammates' safety above orders, that was never explained to me}\footnote{\textbf{q.google }I love this line :P. \textsubscript{04/16/13 12:56am}},'' Hayley says petulantly.  

``A h- I believe it is repeated several times in the TA handbook,'' \hl{points out Rook.}\footnote{\textbf{Suko T }I \textless 3 Rook.  He's definitely got the Agent Coulson vibe going on.

https://www.youtube.com/watch?v=QAMgkpQYOSQ \textsubscript{04/10/13 2:16am}}

``Oh.  I never read it before now.  How did you not know that?''

``Everyone is required to read it, how were we to know you did not?'' asks Rook.

\hl{``Because of our poor performance,'' says Hayley.}\footnote{\textbf{Adam Kenney }+1 \textsubscript{04/14/13 5:20pm}}\footnote{$\rightarrow$\textbf{q.google }LOL. \textsubscript{04/16/13 12:57am}}  She tilts her head thoughtfully. ``That reminds me, I had another question.''

``Yes?''

``What do you mean when you say we will get training?''``What do you mean by that?'' asks Rook.

``I requested training two weeks ago and nothing has happened.''

``Ah, yes,'' says Rook, ``I admit it was not made a priority.''

``\hl{So you don't actually think it is important that we get trained}\footnote{\textbf{q.google }Go, Hayley :) \textsubscript{04/16/13 12:58am}}\footnote{$\rightarrow$\textbf{Suko T }Hayley may not do anything about broken promises but she remembers them. \textsubscript{04/16/13 11:06am}}?'' says Hayley intently.

``It is, and you will.  We just had other priorities at the time.''

Hayley says nothing further but furrows her brow and is clearly thinking hard about something.



``Any other questions?'' asks Rook

``Yeah,'' says Jonah.  ``Have you seen what they did to Nicklepan? Their technology is so far beyond ours that I don't know what you think we can do.''

``What you brought back, the body and the armor, has been extremely helpful in that regard,'' says Rook.

``We need guns and armor like that,'' says Oliver.

``And more information if we are going to go into another situation like that,'' adds Jonah.

``You know we can't guarantee your safety,'' says Rook.

``I think we are all in agreement on that,'' says Jonah bitterly.



``We need you to think about what you want,'' says Rook.  ``Also you should know that two of you are scheduled to be promoted to Operator, and two to Agent. On a provisional basis of course.  Both are specialist ranks, and would have separate promotional tracks.''

Jaya perks up at the word promotions and asks Rook, ``If we were to be Agents, would we be the same rank as yourself?''

``No,'' says Rook.  ``But for example, among all Senior Constables, you would outrank them.  A Station Chief wouldn't necessarily follow your orders but just about everyone else at the station would.  The random person on the street wouldn't be aware of a difference.  There aren't many Agents in the TA after all.  Also, we are using some obscure specialized terms. At times, depending on the situation, an Operator can be a higher rank than an Agent.  If you do return, you will be fitted for certain equipment for you to practice with.''

``Is Patrol Group 2 receiving the same equipment?'' asks Jonah.

``Our resources for this are extremely limited.  If you do not return, we will accelerate the process with them and they will use the equipment,'' says Rook.



With no further questions, Rook and Dr. Gerhauser leave. 



Jaya attempts to leave but Jonah starts talking. She waves him off, ``We can talk about this later, I've got Shore Leave to go on.''

``What if your promotion is based on whether or not you have a team when you come back?'' says Jonah.

This makes Jaya pause and she turns to Jonah and slams her hands on the table angrily, ``What the FUCK Jonah!!!  What are you trying to say?''``As your medic, I'm \textit{trying} to save your life,'' says Jonah more quietly but no less angrily.  He takes a deep breath.  ``Here'' he says, ``Let's start with some medicine.''

He offers Jaya (and everyone else) some of Trenton higher quality booze.

``Now, your talkin'.''

``Listen.  Do you remember, about three weeks in?  This was before Hayley was here, our fourth was Joe.  We walk into that bar on 97th Street, and there were 15 of them and just four of us.  I thought we were going to get hurt.  But the Senior Constable - yes that's you - walked up them and said, 'The first person to cross this line gets their heads caved in.  Okay, who's first?'  Chief, I've been following you ever since because of what you did then.  But now -''

``We still have crazy objectives and shitty support,'' says Jaya.

``The difference between then and now is that you could use your fists to fight these enemies.  But now, bullets don't care who you are.  You can't just walk down the street like you did in Nicklepan - you will get shot!!!'' yells Jonah.

Oliver interjects, ``The way I see it, it's not going to war.  The war is coming to us.  We're being treated like canaries in a mine.  We're going to be by ourselves, in the dark.  All we can do is be smarter than the people holding our chain.  Jaya, I wouldn't want to face you with a truncheon, but you are not a big picture thinker.''

``If you want us to work for you, you have to work for us,'' says Jonah, fiercely, but also almost pleading.  ``\hl{Who do you trust with your life}\footnote{\textbf{q.google }OOG, quoting Morgan, because it seemed thematic. \textsubscript{04/16/13 1:11am}}?''

``I would've said Hayley but now... I guess none of you,'' says Jaya honestly.

``How are you going to run this team if you don't trust any of us?'' asks Oliver calmly.

``That doesn't come into it!  We are a team!''

Oliver replies with a barely-suppressed irritation, ``Very good, sir.  Enjoy your shore leave.'' Jaya storms out of the room.



Oliver waits a beat and then turns to Jonah and Hayley and says, ``It doesn't matter if Jaya wants to take responsibility for leading us or not. She only cares if we call her 'Sir.' So the real question is, how are we going to run this team?''

Jonah and Oliver discuss things and agree that we need to start sharing what information we have.  Hayley mostly stares at her hands, it's hard to tell if she's listening.

Oliver starts first, ``Look I'll tell you everything.  You remember that guy? The one who killed Lackovich's team?''

Hayley raises her head at that and says, ``Oh!  The one with the damaged face?  I don't remember his name.''

``The burn scars, yes.  He is the Orc of Anglia.  He is extremely dangerous and he has threatened my family.  Agent Morgan has decided to take him out.  It's going to be me who takes that shot.  Some of us may die.''

Hayley nods.



For the first time since sitting down, Jonah addresses Hayley, ``Hayley, we need to know what orders you have that will get us hurt.  Do you have any right now?''

``I don't think so.  I don't understand.  How do I know which orders those are?''

``We can't go into a situation \hl{on a mission}\footnote{\textbf{q.google }If I said ``give you an order'' that was a mistake. \textsubscript{04/16/13 1:23am}}\footnote{$\rightarrow$\textbf{Suko T }Was it?  Because I assumed that Jonah was referring to the situation in Nicklepan where he gave Hayley an order and she ignored it because other orders superseded it. \textsubscript{04/16/13 11:07am}} and find out later that some other order countermands it.  That's dangerous.  You need to tell us what orders will be a problem,'' says Jonah, sounding frustrated.

``Oh.  I don't know which those might be.  I will have to think about it,'' says Hayley.

``Hayley, you have to learn when to follow orders and when not to,'' says Jonah.

``Oh!  I do?''

``Yes!  That's what they were telling you,'' says Oliver.

``Oh.  Is that what they meant?  But how do I do that?'' asks Hayley, bewildered.

``You use your judgement.''

``I have no judgement.''

Oliver pauses, looks at Hayley and says, ``I'll try to help you with that.''

``Thank you,'' she says, looking both grateful and terrified.



\underline{  {\LARGE Shore Leave }  }


\sceneHeadline{Shore Leave: Jonah and Dr. Gerhauser}

Jonah has failed to track down Dr. Gerhauser and finally gets on board the train to head home.  Dr. Gerhauser is on the train.  She addresses him, ``You wanted to talk to me and I thought that this would be the best time to do that.''

``Any later and it would have been a very bad time,'' \hl{says Jonah}\footnote{\textbf{q.google }There's a bit here I can't remember well enough to work back in without breaking the flow so here is it for reference:

Jonah suggests to Dr. G. that she's on the train because they can't be overheard there.  It's partly because he wants to see if she'll reveal if they are being listened to (she doesn't), but mostly to say ``I don't usually see you on the train, so here's why I'm going to think you are here.''  I think of this as Jonah's instinctive looking for cover stories to keep secrets, which is kicking in even as he's getting ready to say ``we need fewer secrets.''

It isn't easy to run, or even step, away from ourselves. \textsubscript{04/16/13 9:47am}}.

``What did you want to talk about?''

``The test. Why was it necessary that it be quite so... painful?''

``We debated for a long time on that matter.  Hayley is uncannily perceptive about certain things and we felt that a simulation of the situation would not be convincing enough to elicit the effect we wanted,'' says Dr. Gerhauser.

``Have any of you ever been in the chair?'' asks Jonah.

``Morgan was tortured for several weeks, and I believe it involved electrocution, so yes,'' says Dr. Gerhauser.

Jonah looks grim, but ever so slightly mollified.

``Explain to me about what you are trying to do to us with these \hl{machines}\footnote{\textbf{Suko T }somewhere in the conversation I believe it is clear that he's referring to the Tank now, not the electric chair. \textsubscript{04/11/13 1:21am}}\footnote{$\rightarrow$\textbf{q.google }Yes, he just moved on.  The theme was the same: do you take your own medicine? \textsubscript{04/16/13 1:26am}}. Have any of you tried it?''

``It doesn't work that way.  It is like skin grafting or blood transfusions, only certain people-''

``NO, I'm asking if any of you have \textit{tried} it.''

``And I'm trying to explain to you that It. Doesn't. Work. That. Way.  To make it work, you are injected with the machine.  It will only bond to certain neural sheath types.  If it doesn't engage the neural sheath it just floats around in your bloodstream.''

``So nothing happens?''

``Well there is always a chance that a few will bond no matter the compatibility, but it's only very few so the experience would be so diluted as to be insignificant.''

``Were people blown up where you came from?''

``Yes.''

``Did you watch it happen?''

Dr. Gerhauser looks at Jonah squarely, ``What are you really asking?''

``You want me to trust you.  You want us to do things for you, and then do things like the Tank and the chair, with no warning.'' says Jonah, intensely..

``Do you think I'm having a ball?'' says Dr. Gerhauser bitterly.

``I don't know.  That is the problem!  You won't trust me with what I need to know to stay sane.  I won't be able to do what you need me to do if you don't tell me things.  You can keep your secrets, that's fine.  \hl{I have secrets of my own to keep}\footnote{\textbf{q.google }Somewhere in here he hinted to her that she might know his secret to see if she would confirm it, but she seemed confused, and he wasn't able to outright say it. \textsubscript{04/16/13 1:32am}}.  But you need to be straight with me.  If something's going to hurt me or something is going to be dangerous, you need to tell me!  \textit{We} need to know.''

Dr. Gerhauser looks at him consideringly and then stands up and walks over to him and holds out her hand.

{[}\textit{Ongoing Challenge: Gerhauser Sisters.  Get Dr. Gerhauser to treat Jonah more like a colleague and give up more information.  Social Chameleon 4{]}}

``You understand that the first time you went into the Tank, we could not tell you anything, right?'' asks Dr. Gerhauser.

``Yes, I understand.  But that is \textit{not} true now,'' says Jonah.


\sceneHeadline{Shore Leave: Oliver and Dr. Gerhauser}

Oliver gets off of the train.  Night is falling and there is a light rain misting the air.  As he walks down the darkened street, up ahead of him he can see a tall cloaked figure detach from the shadows and start walking toward him.  Oliver alters his path to avoid them, arranging things so that he ends up on a side street just off the main road.  He sets his bag down and pulls out his handgun and waits for the figure to approach.



When the figure gets closer, they stop, reach up and pulls back their hood.  It is Dr. Gerhauser.  Oliver's tension breaks and he smiles, ``Give me some warning next time!''

``\hl{I'm not supposed to be off base}\footnote{\textbf{q.google }That's ... interesting. \textsubscript{04/16/13 9:41am}},'' she says quietly, stepping closer until she is within arm's reach.  ``I have a favor to ask.  We've all lost pieces of ourselves along the way.  Everyone is \hl{somebody's daughter or sister}\footnote{\textbf{q.google }As is this. \textsubscript{04/16/13 9:41am}}.  I just need you to think twice about....''

``You're talking about the meeting we just had?'' asks Oliver.

``Not exactly no.  I can't stay.  It's important for you to know that Morgan is extremely driven.  But she doesn't always make the best choices.  You know what this means,'' she says and casts a significant look at the backpack at his feet.

``I'm touched by your concern,'' says Oliver.  ``But especially after everything you've gone through, I'm surprised that you of all people...''

Dr. Gerhauser reaches out a hand and gently touches his face.  ``I would have failed \hl{you}\footnote{\textbf{Nathaniel Ford }She was specifically referring to Oliver's intent desire to get himself killed. \textsubscript{04/12/13 12:16am}} on the duress test,'' she says softly and then pulls her hood back up and walks away.

Oliver looks after her with an unreadable expression.


\sceneHeadline{Shore Leave: Jaya and Oliver}

Jaya watches this scene, but she is too far away to recognize Dr. Gerhauser.  She's hanging around outside of Oliver's house after realizing that she really REALLY doesn't want to go home to LA Ink right now, none of her old gang friends will talk to her because she sold out to the TA, and Oliver's address was the only one she could find.



Jaya kicks over some boxes, drawing Oliver's attention to her.

``Sorry I slugged you,'' says Jaya, but then adds honestly, ``Not really.  We cool?''

``Sorry I gave you an order.  We cool?'' responds Oliver.

``No, but, uh, I'm the Senior Constable and I want the team to be cohesive.''

``I'm not the one to talk to,'' says Oliver.

``Yeah... yours was the only address I could find.  Say you know of any good place to drink around here?''

``No, I don't drink around here.''

Jaya frowns and then offers Oliver some of the bottle she is holding.  When he takes a swig, it's awful cheap rotgut.  ``Where did you get this?'' he chokes.

``Not at a Citizen's bar!'' grins Jaya.

Oliver decides that a night out drinking with Jaya beats an evening with his father, so the two go to a bar together.  They don't hang out together once they get there though.


\sceneHeadline{Shore Leave: }\textbf{\hl{Hayley and Octavia}}\footnote{\textbf{q.google }I don't know this is possible, but this manages to be the most painful Hayley conversation I can remember. \textsubscript{04/16/13 9:53am}}

Hayley decides not to go see Gillian because she is feeling too upset to be useful.  She actually spends time reading the Patrol Handbook, washing all of her clothes and uniforms, cleaning the barracks until they are sparkling and then exercising again until she is so exhausted that she can finally sleep for a few hours.  



The next day, Swan shows up and says, ``I know you've decided to stay here, but Ms. Vorrutyer is going to be leaving soon and if you want to see her, you better go now.''

Hayley looks alarmed and scrambles to get ready.  She packs up everything (except Signe's letter) that was not given to her by the TA: all her civilian clothes, shoes and notebooks, and neatly stores it in her duffle bag.



She arrives at Gillian's new apartment in Terminus.  The door is slightly ajar which makes her nervous.  She looks around for Gillian's security detail, and then listens for a minute at the door.  When she hears nothing, she announces herself.  



A voice with a familiar accent invites her in.  The apartment is dim, the furniture covered with white sheets.  It is a very nicely appointed apartment, which Hayley notices idly, but the bulk of her attention is captured by Octavia, standing in the middle of the room.



Hayley gets a big goofy smile like a fangirl when she sees Octavia, and she fidgets bashfully with the dufflebag which she has forgotten to set down.



``I was wondering when you would drop by,'' Octavia says with false sweetness.  ``Unfortunately, Gillian had to leave on vacation early.  She made some business deals that her fiancé found... unpleasant.  She may be gone longer than expected.''

``Oh!  Okay, thank you for telling me,'' says Hayley, flustered.  

``Aren't you a dear,'' Octavia says, stepping closer to Hayley.  She touches Hayley's cheek and then trails her hand along Hayley's shoulder and down her arm.  Octavia smiles at Hayley, ``Do take care of yourself.'' and squeezes Hayley's arm in the exact spot where Hayley was knifed recently.  Hayley winces but does not pull away.  But she stops smiling quite so dopily.

Octavia continues, ``By the way... you've been spending a lot of time in the Warehouse District.  Do you know someone there?''``Oh yes, several people,'' says Hayley, proudly.

``Really? Like whom?  Perhaps I would like to meet them.  What do they look like?''

\hl{Hayley happily describes Signe and Tim and several other random people she met in the Warehouse District}\footnote{\textbf{q.google }Arrrrrgh! ;P \textsubscript{04/16/13 9:52am}}\footnote{$\rightarrow$\textbf{Suko T }Yup, totally sold them out.  She's going to feel really bad about that when she finds out. This is what happens when you have zero guile and have a Flaw that wants to please people more powerful than you. :)  Hopefully I'll be able to work in telling others about this so she can learn better. \textsubscript{04/16/13 11:11am}}.  She doesn't know their last names, she never asked.

``Will Ms. Vorrutyer be okay?'' asks Hayley anxiously.  ``I'm worried about who is guarding her if I'm not there.''

``Don't worry, she's very well guarded,'' says Octavia, patronizingly.

``I'm worried about her,'' Hayley continues to fret.

``How delightful!'' says Octavia like her pet dog just did a trick.

``Not for me,'' frowns Hayley.  ``It's very unpleasant.''

``I suppose that's your problem,'' says Octavia as she walks to the door.  ``Good bye.  We'll meet again.''

``When will that be?'' asks Hayley.

Octavia just smirks and walks through the door.

``I ask because I might be dead soon,'' says Hayley.

Octavia pauses and turns back to look at Hayley briefly but then turns away and leaves.



Hayley looks around the empty apartment sadly.  She carefully stows the duffle bag in one of the closets and then lets herself out, locking the door behind her.


\sceneHeadline{Backlash Token Pool: 0}

\underline{  {\LARGE Ongoing Challenges }  }

\begin{itemize}
\item Ongoing Challenge: The Gerhauser Sisters 
\end{itemize}

Get Swan to confront Dr. Gerhauser over what is being done to the team.

\extraIndent{→ Gorgeous 3 (Hayley)}

Get Dr. Gerhauser to treat Jonah more like a colleague and give up more information.

\extraIndent{ → Social Chameleon 4 (Jonah)}




\jumpHeadline{Quotes }

 ``I don't want to shoot anyone.  But the good news is if there \textit{was} shooting, I'm a medic.''

        - Jonah

``Let me get this straight, you are trying to turn us into \textit{radios}?''

        - Jonah



``Let's just say that the device only fits over certain shapes of heads.  And you all have the same shape of head in this analogy that I'm making up.''

        - Trenton



``When all else fails, try leadership.''

        - Adam


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: This whole convo was not noted very well, I was catching up on Jaya vs Morgan notes.  Please fix if you can., unable to correctly match (exceeded acceptable limit):Expected???  You should ask Jari about that.”
“Anything up to and including rifles”

	Unable to highlight for footnote: This whole convo was not noted very well, I was catching up on Jaya vs Morgan notes.  Please fix if you can. because:GivenExpected“You should ask Jari about that.” “Anything up to and including rifles”???  You should ask Jari about that.”
“Anything up to and including rifles”


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 05/12/15 12:50am}
% Exported @ 08/24/15 8:58am
\end{flushright}

