\setcounter{chapter}{ 1 }
\chapter{\textbf{New Station, Part 2} }




\subChapterTitle{``His August Person, The Provider Poseidon''}

\deets{Suko}{June 20, 2012}

\noindent\hrulefill





Last session lead-in: After killing Merlin with a well placed headshot, we were told by Angela that ``Poseidon had granted an audience with his august presence.''



We step away from Angela and chat for a while to create a loose plan.  Basically Jonah will do the talking and the rest of us will do our best to shut up.



Angela leads us inside a large building and through a surprisingly clean lobby to an elevator, guarded by two teenage boys.  We ask Angela to accompany us into the elevator.  Despite some misgivings, we step into the elevator and it goes slowly up, while sitar music plays tinnily through the crappy speakers.



Hayley asks Angela about the proper address for Poseidon (His August Person, The Provider Poseidon) and what we could do to make him like us better or at least not dislike us (nothing).  As we step out of the elevator, Hayley asks what Poseidon is to Angela, to which she replies that they work together occasionally.



The elevator opens into a large room, well lit.  There are many women there and several children (infant to about 6 years old).  There are five men on the floor, one by the elevator, the other four by several corridors/exits that branch off of the main room.  They are all standing and have pistols, but they are holstered.



Hayley notices with her Bodyguard training that there are strange packages bolted to the walls with wires coming out of them.  She doesn't report this to the rest of her team.



We go through some double doors at the far end of the room and are in a room with raised platform in it and a bay of windows.  There is a man lounging on a couch on the platform, with a young, very pretty girl beside him who looks at us vacantly.  Jonah's medical training tells him that she's probably hale but there's something wrong with her focus.



They are the only other people in the room besides us and Angela.



Jonah steps forward to address the man and Hayley interrupts him to make sure he knows the proper address.  She bows and addresses Poseidon by the title Angela told her.  Poseidon claps and then Hayley steps back to let Jonah speak.



Jonah starts negotiating with Poseidon, hampered by the fact that he can't actually offer anything of value in return or make any real promises and assurance.  But he appears to make Poseidon at least consider the situation.  



Angela is asked to leave the room when it becomes clear that we will have to be specific about who Poseidon/Trenton is and that we have orders from the TA to bring him home.



While he never directly confirms it, Trenton implies that he is who we are looking for and that he even has some idea of why we are being sent for him.  Certainly more of an idea than we have.  Trenton wants to know where we are stationed and where he is going.  Jonah is cagey and doesn't tell him but Oliver eventually tells Trenton that we are in SAC-09, which causes Trenton to look something up in a book filled with numbers and equations.  Trenton tells us that the trains require particular key sequences to get to certain stations, so if he wanted to, we wouldn't be able to return here via train.



Oliver and Jaya intimidate him into feeling less secure in his cozy little fiefdom, and Jonah uses Social Chameleon to lean on the opening and convince Trenton that it is a good idea to go with us willingly.



Wanting to know who gave us the order to fetch him, we initially tell him Agent Tiburon Rook but then later Oliver describes Agent Morgan who Trenton calls Gerhauser.  This seems to interest him and he appears to know her.  He says she runs in ``strange circles'' but that he hasn't seen her in a while (for obvious reasons).



He eventually agrees to go if we agree to let him bring as many of his family as will fit in the train.



He leaves the room to make arrangements, and we sit around waiting.  Jaya hands a cup to the woman and asks, then orders her to put it away.  The woman, Signe, freaks out.  Jaya backpedals enough that Signe doesn't attack her, and instead Signe stalks away, her posture full of tension.  Hayley, following Jonah's instructions to keep an eye on Signe, follows her.  When Signe asks, Hayley tells her that she was instructed to keep an eye on her.  Not wanting to make things worse, Jonah and Oliver tell Hayley to leave Signe alone.  Jonah scolds Hayley for telling Signe about the order to watch her. 



Trenton returns and discovers that Signe is missing and that we upset her. He gets upset and says he can't leave without her.  Apparently she's got some emotional issue that he's helping her work through, and the last time she freaked out, it took days to find her.



Jaya tells Hayley to look for her, and then amends it to ``to the best of her abilities ascertain where Signe is'' {[}Note by Suko: this was a very smart order change on Rebecca's part- the former order would have had almost totally useless, if potentially funny, results{]}.  Hayley goes out to the women and asks them for information.  Things almost get derailed when Hayley tells the women that Merlin is dead, but eventually one of the women mention that sometimes Signe goes up to the roof.  Hayley and Oliver head up to the roof while Jaya and Jonah go downstairs to ask the guards there if they saw anything.



Oliver uses the scope on his sniper rifle to find Signe who is extremely hard to spot.  She is on the edge of the roof and her eyes go in and out of focus as she seems more or less aware of where she is and what's going on.



Hayley and Oliver eventually talk her down, and Hayley makes Signe a personal promise that Signe will be welcome to go with the rest of Trenton's family and will not be hurt (nor the rest of the family be hurt).  Hayley escorts Signe back downstairs while Oliver lingers behind so that his sniper rifle (initially used to find Signe) won't upset Signe further.



Jaya and Jonah head downstairs to the lobby but don't find Signe.  Jonah finds Angela and talks with her.  He tries to get some information out of her but ends up accidentally feeding her information about the current state of affairs between the Directorate and Anglia {[}refreshing Vigilant{]}.



We all reconvene on Trenton's floor and the leavetaking scene is so heartbreaking that both Hayley and Jonah get flaws of Guilt. It is clear that we are ripping apart a family and a community.



Eventually we get everyone bundled onto the train, much to Tiburon's trepidation.



We stop briefly at DX Station where a diplomatic envoy from Anglia is passing through.  Trains are backed up and being rerouted to accommodate this.



Hayley and Oliver stay in the train car (former due to her promise to Signe and the later due to PTS from his time trapped at DX Station during the war).  Jaya goes with Jonah to investigate what is going on.  She sees the delegates, followed by two extraordinarily beautiful women.  Jaya manages to get herself noticed (senior TA authority) and one of the women comes over to her and smiles and takes her hand.  She thanks Jaya for our hospitality, and then moves on to others in the crowd.



After about 45 minutes, the traffic snarl starts smoothing out and we eventually make it back to SAC-09.


\jumpHeadline{Quotes }

``She smiles slightly but her eyes don't really focus on you.''

``So she IS like the girls I used to date!''

\extraIndent{ - Nate (describing Signe's reaction to Oliver) and Adam}



``I'm not magic.  Well actually I kind of am.''

\extraIndent{- Trenton (Poseidon)}



``Yeah you stay here...I'll go upstairs and, uh, cover our tracks.''

\extraIndent{- Jaya, to Jonah}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 05/29/15 11:01pm}
% Exported @ 08/22/15 12:54pm
\end{flushright}
