\setcounter{chapter}{ 20 }
\chapter{\textbf{``Redux''} }




\begin{center}
 {\LARGE \textbf{(Borrough Station, ver 2.0, part 1)} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} February 21st, 2014



We get a do-over to try to rescue Lackovich and kill the Orc of Anglia again!   It should go better this time around, RIGHT?





\noindent\hrulefill




\sceneHeadline{SAC-09}

Time rewinds {[}OOG- see note in Session 20{]}.  We are back at SAC-09.  The mission is that Lackovich is gone, AWOL and she's armed with unauthorized weapons.  She was last seen in the Bucket near Borrough Station, and the Orc has also been spotted in the area.  The mission objective is to retrieve Senior Constable Lackovich.  Should we find/engage with the Orc, we can kill him. 


\sceneHeadline{Oliver and Jonah}

Oliver and Jonah are put in the tanks. Oliver flirts a little with Dr. Gerhauser, Jonah asks many questions about what is about to happen to them.  Oliver asks for clarification about the Orc.  



This time though, things go differently.  Swan starts counting the synchronization percentages.  When he reaches 73\%, Larissa says ``We have waveform.''  Victor says, ``We have a problem!'' and Oliver and Jonah black out.


\sceneHeadline{Hayley and Jaya}

Hayley and Jaya go to the ready room with Rook and Jari.  Hayley sits and waits calmly, Jaya paces around despite Rook's advice to sit down.  They feel a vibration in the floor and then their vision goes....strange. Sorta sideways, and then there are bright lights.  Jaya waves her gun around, but blinded by the lights, she ends up confronting a wall before she passes out.  Hayley, seated, mentions quietly, ``I feel dizzy'' and faints gracefully.


\sceneHeadline{Primus- Jaya and Jonah}

Jaya wakes up and she's standing at a train station.  Jonah is there.  ``What the fuck, Jonah!''

``Where are we, Chief?'' he replies

``Primus station.  Constable, report last status!'' orders Jaya.

``The train is about to leave''

``I asked to you to give a report!   Who is that behind you?''

``Who is that girl behind you?''

``No, behind YOU,'' says Jaya impatiently.

The train arrives.

``Run for it!'' says Jonah loudly.

``But the train is here,'' says Jaya, not moving.

``It's not our train.'' says Jonah.

Jonah hears a scream, Jaya hears a baby cry and they both black out again.


\sceneHeadline{Primus- Oliver and Hayley}

Oliver says we have to go, the train is almost here.   Hayley is too scared to move.  ``It's safe here.''

Oliver says that the train is bound for Tertius and Hayley mentions that they are at Primus.

``Who is that man?'' she asks Oliver.  ``I don't think I like him.''  

The train arrives.  Hayley starts crying, ``I don't want to keep hurting him.''

The train doors open.

Oliver hears a gunshot that sounds like the word ``son''.  Hayley hears the familiar sound of cracking ribs.


\sceneHeadline{Back at SAC-09}

\textbf{Oliver and Jonah}



Oliver and Jonah wake up in the tank.  They are a little disoriented.  Swan hastens to unplug them while Oliver clenches his hands into fists and tells Swan to hurry up.



Victor and Trenton are talking, or rather, Victor seems to be yelling lots of technobabble, and Trenton is responding more reasonably, also with technobabble.  Larissa says to Gerhauser, ``The midline frontline theta didn't stabilize!''

 

When Oliver gets out of the tank he asks, ``Did we get the Orc or not?''

``What happened?'' asks Jonah.

``We are working on figuring that out,'' replies Larissa.


\sceneHeadline{Hayley and Jaya}

Jaya and Hayley wake up feeling fantastic- well rested and energetic.  Jaya hasn't felt this clear-headed since before she started taking drugs.  She starts bouncing around the room excitedly.  Hayley quietly enjoys feeling good.



Morgan walks in and Jaya salutes cheerfully, ``Sir ma'am ma'am sir ma'am Agent!''

Morgan gives her a look and then looks over at Rook.

She addresses Jaya, ``Are you ready to go on your mission?''

``Yes!  I don't know where the rest of my team is but Hayley and I GOT this!'' Jaya says with conviction.

``Very well,'' says Morgan.  ``You may request two personnel to assist you.''

``Davis and Javier,'' says Jaya promptly.

Morgan leaves.

Jaya challenges Jari to an arm-wrestling match.  When he declines, she challenges Hayley to an arm wrestling match and loses, to her annoyance.


\sceneHeadline{Jonah and Oliver}

Dr. Gerhauser walks over to Oliver and Jonah to start answering some of their questions.  ``You have been instrumented.  The tech connects you more closely to your teammates.  Like a walky-talky, but better.  Better bandwidth, if you will.''

``The tech is inside me?'' asks Oliver, not sounding very happy about this.

``You've been augmented, like clothing and guns augment you.''

``But you can put down guns,'' says Jonah.

``We can turn this tech off,'' replies Dr. Gerhauser.



``What day is it?'' Jonah asks again.

``Thursday.''

``Did we complete the mission?'' asks Oliver.

``None of you left the base,'' says Swan

``But we did!  Or rather Hayley and Jaya did...and so did I.''

``I promise, you didn't leave here.''

Victor starts shouting incoherently.

``You may experience some hallucinations.  Let me know if you have a persistent migraine-''

``What *time* is it?'' Jonah asks.

``11am.''  {[}OOC- so far as they remember, they got into the tank around 10:30am on a Thursday{]}

``We've been gone a \textit{week}??'' says Jonah, \hl{bewildered}\footnote{\textbf{Suko T }It's still only an hour later, it just doesn't feel that way, hence his confusion. \textsubscript{02/24/14 10:51pm}}.



Morgan enters and she confers with Dr. Gerhauser.  Morgan addresses Oliver and Jonah, ``Your patrol leader says you are ready for your mission.''

``Another mission?'' asks Oliver.

``I told you so!'' yells Victor.

Jonah says the yelling isn't helping and Victor is escorted from the room.

Oliver looks at Morgan, ``Let me clarify, this mission is to get Lackovich and kill the Orc.''

``Yes,'' says Morgan.

``Alright then, let's go.  Just give me a minute to clean up.''

``Do you have anything to drink?'' says Jonah.



{[}OOG- the memories of last session, starting from the time Jonah and Oliver got in the tank, are like a dream.  The details are as fuzzy or clear as we the players remembered them.  The train platform scene also feels like a dream/memory.{]}


\sceneHeadline{Ready Line}

\hl{Equip:}\footnote{\textbf{Suko T }Did I forget anything or mis-assign something?  Jaya later gives Hayley her Gauss pistol but I'll switch that narratively.  Incidentally the Battle Dress Uniforms come with a rifle but I think we can assume Jaya swapped it for her pistol, Betsy. \textsubscript{02/24/14 11:10pm}}

Jaya: Combat Armor 2, Gauss Pistol 2

Oliver: His rifle, Battle Dress Uniform 2, Radio Network 2, Parabolic Antenna 2, Rangefinder Binoculars 2, Urban Camouflage 1, Med Kit 1

Hayley: Combat Armor 2, Med Kit 1

Jonah: Battle Dress Uniform 2, Forensic Bag 1



They get cleaned up and geared up and head to the ready line.  The train arrives and Rook boards.  Morgan says that she can't assign Davis and Javier but she hands Jaya a letter that will allow her to conscript some people from the TA personnel stationed at Borrough Station.



Everyone starts boarding the train and Hayley freezes and doesn't move off of the ready line.  ``I don't want to go.  I'm scared.''



Jaya gets impatient and Jonah and Oliver attempt to explain to her why they need to leave and how the train is fine and whatever she thinks she remembers, it was just ``practice''.  This is not the same train.  At some point, some argument must have gotten through (not clear what) because \hl{Hayley suddenly looks at Oliver}\footnote{\textbf{Suko T }Operator mojo here. \textsubscript{02/24/14 10:54pm}} and says, ``Okay,'' with a smile and boards the train without hesitation.



Oliver speaks to Hayley, but she seems mostly fine now that she's on the train.  She asks Oliver to explain to her how to figure out what a bad order is.  Oliver says he can't really do that right now, maybe later.  Hayley pushes for an answer now because, ``based on the practice, I think I really need to learn this.''  But he can't tell her and gets that thousand yard stare.



Jonah and Jaya talk {[}OOG- about?{]}




\sceneHeadline{Borrough Station}

\jumpHeadline{Borrough Station Threat Levels }

Upper Deck: Green

The Apartment Tower: Green

The Yard: Yellow

The Factory: Orange

The Vengeance of Octavian: Red



They arrive at Borrough Station, and work their way to the TA offices.  Station Chief Hughes is there.  Jaya, more confident this time, hands him the letter and says that her team is on a secret mission and is conscripting several of his constables to help.  Hughes choses four constables (because they work in pairs) Franke, Dev, Diego and Leah.  He also hands Jaya the key to the brig.  Hayley confuses Franke by greeting him like they know each other.



Jaya says this situation shouldn't be too bad, but Hughes says wryly, ``No offense, but they don't send in Agents to 'not too bad' situations.''



Oliver looks around with dead eyes, making the constables in the office very nervous {[}\textit{Refresh: Hardened 4 (Oliver)}{]}.  Hayley creeps out Jaya a bit by predicting certain things before they happened, or knowing things she's not supposed to know (like where Franke lives and which book Lackovich looked through).



Jonah chats up the Station Chief and looks over the maps of the area.  They find the book that Lackovich looked through and leaf through it.  She headed out to a warehouse.  Jaya instructs Franke to lead them there.  With the four redshirts in tow, the crew heads out.  The constables seem pretty junior.  Diego is totally checking out Hayley's ass. 



\textbf{{[}Upper Deck Activated.  6 Tokens enter the Pool{]}}



Oliver falls behind again, not just his limp but he's also looking and listening for snipers {[}\textit{Challenge: Notice Snipers 1. Binoculars 2 (Oliver) → Overcome! }\textit{\textbf{1 VP (Oliver)}}{]}



He hears something in the upper floors of an apartment building.  They discuss what to do- go to the warehouse or the apartment building.  Jaya wants to go after Lackovich, Oliver wants to go after the Orc.  Jaya is confused as to why they're talking about getting the Orc when they are supposed to get Lackovich...right?  Hayley attempts to explain that ``Lackovich is the Objective, while the Orc is the Target.''  They head to the Apartment building.



Jonah and Oliver start talking strategy as we approach the Apartment Building.

``Four people could be helpful or a problem,'' says Jonah quietly.

``Well we need someone to use as a distraction,'' says Oliver.

``I'd rather not deal with a corpse this time,'' says Jonah.

``Hey, I was the one who brought back the corpse,'' corrects Oliver, loudly enough to be overheard.  The redshirts get nervous.  {[}\textit{Challenge: Don't frighten the Norms 2.  Social Chameleon 4 (Jonah) → Overcome! }\textit{\textbf{2 VP (Jonah)}}{]}



Oliver finds out that Dev was in the war and has some combat experience. {[}\textit{Challenge: }\textit{\hl{Coach Dev into helping be a sniper}}\footnote{\textbf{Adam Kenney }This was actually more of a social challenge to win his trust and get him to cover Oliver's back. \textsubscript{02/27/14 3:01pm}}\textit{1. Veteran 2 (Oliver) → Overcome! }\textit{\textbf{1 VP (Oliver)}}{]}



{[}\textit{Challenge: Calm down Diego 1. Gorgeous 3 (Hayley) → Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}  Hayley smiles at Diego and he swallows his nerves so he doesn't look nervous in front of the pretty girl.



{[}\textit{Challenge: Calm down Franke 1. Small Unit Tactics 2 (Jonah) → Overcome! }\textit{\textbf{1 VP (Jonah)}}{]} Jonah gives Franke some tactical advice that calms him down so he knows there is a good plan. 



Unfortunately Jonah totally misjudges Leah {[}\textit{Refresh: Social Chameleon 4 (Jonah)}{]} and instead of calming her down, freaks her out even more.  {[}\textit{Challenge: Calm down freaked out Leah 2. Stash 2 (Jaya) →  Matched}{]} Luckily Jaya knows just what to do and pulls Leah aside and slips her a pill from her Stash.  From the deft way Leah takes the pill, it's clear she is very familiar with chemical enhancements.



Oliver directs Dev to one of the buildings near the Apartment, and he takes the other so that they can cover most of the building's exterior and exits between them.  Asked about the Apartment building, Franke says the upper floors aren't habitable, due to the instability, but the building is pretty solid, considering that it has been standing for hundreds of years.



Jaya and Jonah instruct the other three Constables that they are to search the Apartment building.  ````Look for anything unusual!  Like an assassin, or an explosion, or a tripwire,'' says Jaya, helpfully.  



\textbf{{[}Apartment Activated.  6 Tokens enter the Pool{]}}



Leah stops to talk to a kid, encouraging her to go home.  Jaya rounds the corner and scowls at the kid- ``Fuck off and go home.''  The kid screams and runs away.  ``We don't have time for this shit, let's keep moving,'' Jaya explains.



An old guy comes out of an apartment and starts hassling Diego to find out what's going on.  Diego calms him down enough to shove him back into his apartment and close the door.  Hayley is grossed out by seeing such an old person.



Oliver, \hl{listening carefully with the Parabolic Antenna}\footnote{\textbf{Adam Kenney }I think this was a challenge? \textsubscript{02/27/14 3:02pm}}\footnote{$\rightarrow$\textbf{Suko T }Seems like it should be, but I thought Nate had more than 1 Token left over at the end.  Did I miss a Refresh somewhere? \textsubscript{03/11/14 11:07am}}, relays that the first four floors are occupied and noisy, then next two are quiet and then the 7th has activity.  



Jaya instructs Leah and Diego to start searching door to door.  She and Hayley will head up the main/most stable staircase.  Jonah and Franke take the less stable staircase up to the 7th floor.



{[}\textit{Challenge: Notice 1. Concealment 1 (Jonah) → Matched}{]} Around the 5th/6th floor, Jonah notices something out of place- a cable/conduit running up and down the stairwell wall.  It is camouflaged to escape easy notice.  The technology of the cable is beyond the tech in the building, and closer to what Jonah sees at SAC-09.  He reports that he has found a wire.



Jaya tells him to cut it.  He's reluctant because it may set off an alarm or an explosion.  For different reasons, both Jaya and Hayley think that this is backwards- you cut wires to \textit{stop }alarms and explosions.



Jaya and Hayley have reached the 7th floor.  There is a faint humming from the room.  Jaya and Jonah agree that he will cut the wire on her mark.  Jaya peers into the space on the 7th floor and sees some of the tripods that she'd seen in Nicklepan- the ones that seemed to summon more soldiers.  There is a console and wires and cables are plugged into them.

She ducks back and whispers over the radio, ``Shit!  Cut the wire!  Cut the wire!''



Jonah realizes that he has nothing good to cut the wire with (nothing that wouldn't conduct electricity). Eventually he pulls out a bottle and breaks it to create a sort of knife.  The glass cuts through the outer sheath only to shatter.  It appears that under the skin of the cable is a hard, glass-like conduit.  It is dark and he can see some sparkles in it.



As Jaya demands he cut the cable, Jonah pulls out his gun and shoots it with the gauss pistol.  He tries to muffle the sound with the coat of his uniform but doesn't silence the noise altogether. Franke is impressed (and deafened) by the gauss pistol ``What the hell kind of gun is that?''  

``What the hell kind of cable was that?'' asks Jonah.



On the 7th floor, Jaya hears a voice say, ``Who do I have the pleasure of speaking to?''  The voice is young and unfamiliar.



Jaya yells, ``It's the fucking Transit Authority!  Raise your hands above your head and stand down!  Go stand by the window!'' she orders the unknown person.  

``I'm already standing by the window,'' he replies.  Oliver can't see him, so it means he's on a different  \sout{Devi's}\hl{ side of the buildin}\footnote{\textbf{Nathaniel Ford }Actually, on neither; Dev and Oliver weren't on opposite sides but adjacent ones. \textsubscript{02/25/14 8:10pm}}g.  Oliver starts running downstairs to get another angle on the building.



Jaya peers around a corner and sees a man in miner's clothing standing by a large window with his hands above his head.



``Cover him!'' Jaya orders Hayley.

\hl{Hayley spreads her hands, indicating her weaponless state}\footnote{\textbf{Adam Kenney }Somewhere around this time, Oliver used Operator whatnot to see what Hayley was seeing. This is why he changed course and instead of trying to get into a new sniper position to shoot through the window, he started walking towards Lackovich at street level. \textsubscript{02/27/14 3:06pm}}\footnote{$\rightarrow$\textbf{Suko T }Yes I think it was around when Hayley got close enough to the guy (and thus the window) that Oliver could see the Yard. \textsubscript{03/11/14 11:09am}}.  Jaya swears and gives Hayley her Gauss pistol.  Jaya pulls out her trusty sidearm Betsy.  



``I'm here to negotiate a prisoner exchange,'' says the man, conversationally.

``Shut up!  You're our prisoner!'' yells Jaya.  Hayley walks toward the man, while Jaya starts moving toward the console and tripods.



``Back off, spare parts,'' warns the man, addressing Hayley.  Hayley pauses briefly but ignores the warning and steps closer, aiming the pistol at him.



``I'm here to make a prisoner exchange,''\footnote{\textbf{Suko T }Or something along these lines \textsubscript{02/25/14 4:48pm}} says the man to Jaya.

``Exchange for who?'' asks Jaya.

``The one you call Lackovich for Langdon,'' he replies.



``I'm going to lower my hands now,'' says the man.

``Don't fucking move!'' orders Jaya.  ``Hayley, if he moves, take care of him.''  Jaya starts ripping cables out of the console and unplugging things.  The console and tripods seem to be powering down.



The man starts lowering his hands and Hayley tackles him.  {[}\textit{Challenge: The Window is not a healthy Exit Strategy 3. Athletics 3 (Hayley) + Hand to Hand 2 (Hayley) + Saltremachy 2 (Hayley)→ Overcome! }\textit{\textbf{3 VP (Hayley)}}{]}.  The man tries to use Hayley's momentum against her and hurl her through the window but she sees it coming and twists out of the way.  She attempts to grab him but instead of fighting her, he moves towards the window, clearly intending to jump out himself.  Hayley viciously kicks him in the knee, probably breaking it.  She remembers the soldiers in Nicklepan and immobilizes his hands so he can't trigger any devices.  The man stares out the window.



Hayley asks the man, ``Excuse me, but what is your name?''

He rattles off a long sequence of numbers, with some odd symbols/words in there that she doesn't recognize, like ``aleph''.  



Jonah and Franke have arrived on the 7th floor.  Jonah looks out the window {[}\textit{Challenge: Notice 1. Vigilant 3 (Jonah)  → Overcome! }\textit{\textbf{1 VP (Jonah)}}{]} and can see a building with a large open area.  In the middle of the open area is a figure, seated in a chair.  It is too far to be certain who it is but \hl{it seems very possible that it is Lackovich}\footnote{\textbf{Suko T }or was this verified with a challenge that I missed?  Oliver has the binocs and the sniper scope so I didn't think we had any means of distance vision. \textsubscript{02/25/14 4:54pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Oliver confirmed it at the end of the session, yes. \textsubscript{02/25/14 8:12pm}}\footnote{$\rightarrow$\textbf{Suko T }Cool.  I couldn't recall if he was able to get eyes on the yard or not. \textsubscript{02/25/14 9:46pm}}.



Diego and Leah burst onto the floor, startling everyone but the ``prisoner''.  Diego helps secure the man.



Jonah looking at the prisoner and he smirks back at him.  The smirk just gets deeper and deeper until it's clear that his face is distorting abnormally.  The man appears to be \footnote{\textbf{Nathaniel Ford }Less melting, and more like a stroke: muscles seizing in an abnormal and asymmetric pattern. \textsubscript{02/25/14 8:13pm}}\footnote{$\rightarrow$\textbf{Suko T }Right- amended. :) \textsubscript{02/25/14 9:46pm}}having a stroke.  Hayley backs away in horror.



Oliver tries to get to a position where he can see the yard from a lower level/the ground, but it is difficult with all the buildings in the way.



{[}\textit{\textbf{\hl{2 Tokens}}}\footnote{\textbf{Suko T }yes? \textsubscript{02/25/14 12:32am}}\textit{\textbf{ left in pool}}{]}





\underline{  {\LARGE Challenges \& Refreshes }  }



\begin{itemize}
\item Refresh: Hardened 4 (Oliver)
\item Challenge: Notice Snipers 1. Binoculars 2 (Oliver) → Overcome! \textbf{1 VP (Oliver)}
\item Challenge: Don't frighten the Norms 2.  Social Chameleon 4 (Jonah) → Overcome! \textbf{2 VP (Jonah)}
\item Challenge: Coach Dev into helping be a sniper 1. Veteran 2 (Oliver) → Overcome! \textbf{1 VP (Oliver)}
\item Challenge: Calm down Diego 1. Gorgeous 3 (Hayley) → Overcome! \textbf{1 VP (Hayley)}{]} 
\item Challenge: Calm down Franke 1. Small Unit Tactics 2 (Jonah) → Overcome! \textbf{1 VP (Jonah)}
\item Refresh: Social Chameleon 4 (Jonah)
\item Challenge: Calm down freaked out Leah 2. Stash 2 (Jaya) →  Matched
\item Challenge: Notice 1. Concealment 1 (Jonah) → Matched
\item Challenge: The Window is not a viable Exit Strategy 3. Athletics 3 (Hayley) + Hand to Hand 2 (Hayley) + Saltremachy 2 (Hayley)→ Overcome! \textbf{3 VP (Hayley)}
\item Challenge: Notice 1. Vigilant 3 (Jonah)  → Overcome! \textbf{1 VP (Jonah)}
\end{itemize}





\underline{  {\LARGE VP TOTALS }  }

Hayley: 4

Jonah: 4

Oliver: 2


\jumpHeadline{Quotes }

``No offense, but they don't send in Agents to 'not too bad' situations.''

        - Nate



``Look for anything unusual!  Like an assassin, or an explosion, or a tripwire.'' 

        -Rebecca


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: Or something along these lines because:GivenExpected“I’m here to make a prisoner exchange,”“I thought you would be interested in an exchange,”

	Unable to highlight for footnote: Less melting, and more like a stroke: muscles seizing in an abnormal and asymmetric pattern., unable to correctly match (exceeded acceptable limit):ExpectedThe man appears to be melting


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 10:35am
\end{flushright}

