\setcounter{chapter}{ 21 }
\chapter{\textbf{``Constituents''} }


\subChapterTitle{(Borrough Station, ver 2.0, part 2)} 

\deets{Suko}{March 13th, 2014}



\hl{We enter a crazy-backward world where Oliver leads, Jaya is the voice of reason \& caution, Hayley asks intelligent questions, and Jonah is speechless.  We must be in the Tank!}\footnote{\textbf{q.google }Mirror, mirror. \textsubscript{05/01/14 12:31pm}}



Oh and Lackovich sorta gets rescued (by Jaya!!  more proof of opposite-land!) and we start hunting down the Orc in earnest.  Orc's (possible) identity revealed!



And holy crap so many Refreshes.  I probably missed some.






\jumpHeadline{Current Equipment: }

{
\parskip=0pt
Jaya: Combat Armor 2

Oliver: His rifle, Battle Dress Uniform 2, Radio Network 2, Parabolic Antenna 2, Rangefinder Binoculars 2, Urban Camouflage 1, Med Kit 1

Hayley: Combat Armor 2, Med Kit 1, Gauss Pistol 2

Jonah: Battle Dress Uniform 2, Forensic Bag 1
}

\jumpHeadline{Borrough Station Threat Levels }

{
\parskip=0pt
Upper Deck: Green {[}CLEARED{]}

The Apartment Tower: Green {[}CLEARED{]}

The Yard: Yellow

The Factory: Orange

The Vengeance of Octavian: Red
}


\newpage
\jumpHeadline{Borrough Station}

\textbf{{[}2 Tokens from last session{]}}



As Oliver gets a better angle on the Yard, he can see that Lackovich is breathing.  



``Status report,'' he says over the radio.  



There is a bit of confusion as Jaya claims they killed the Orc, and Hayley says they didn't.  \hl{Jaya stuffs parts from the tripods into her pockets}\footnote{\textbf{Suko T }See Jonah, we *did* bring back some future tech, and the person who did it is Jaya! :D \textsubscript{05/01/14 2:00pm}}and makes sure the equipment is shut down.  Hayley asks Jaya how the dead man knew what she was called at Redemarrer.  Jaya ignores the question but Jonah asks what she means.  \hl{Hayley says that he called her ``spare parts'', a name that only some of the folks at Redemarrer called her.  Mostly the guards and keepers called her by that name (and other things)}\footnote{\textbf{q.google }We should follow up on \_this\_ too. \textsubscript{05/01/14 12:34pm}}\footnote{$\rightarrow$\textbf{Suko T }Sure, that would be fun.  But I suspect it's just going to make Jonah more paranoid... :) \textsubscript{05/01/14 2:02pm}}.  The doctors and scientists usually called her ``Subject 16''.  Jonah relays some of this information to Oliver, who gets a bit confused with the Agent/Operator thing and tells to Hayley that he should have called her ``Agent'' and zones out for a while {[}\textit{Refresh Operator 1 (Oliver)}{]}



Jonah asks her a bit about Redemarrer and she said she was born there, \hl{then corrected herself to say they ``made'' her}\footnote{\textbf{q.google }That would explain a lot of things... especially if you consider who ``they'' actually might be. \textsubscript{05/01/14 12:35pm}} and she was with them until she was 19.  She's just turned 23.   Hayley is concerned that the man knowing that name is like how Octavia knew about where she was injured. 



There is a muddled discussion on what to do next.  Diego, Leah and Franke are very confused by all this.  Jaya starts looking for Dev, peering out of windows.  Hayley moves with her, keeping a firm grip on the back of Jaya's uniform so she doesn't fall out.  Jonah is too distracted by everything going on to help search for Dev. {[}\textit{Refresh Vigilant 3 (Jonah)}{]}.  Jaya can't find him and asks Hayley to help.  {[}\textit{Challenge: Find Dev 2. Nose for Breadcrumbs 2 (Hayley) $\rightarrow$ Matched}{]}



They see someone in a TA uniform leaving a building near the Yard and Jaya waves to him and he waves back.



Oliver radios that he's getting into position.  Hayley decides to head out to help him.  Jaya follows.  Jonah stays with the red shirts.  They are not very impressed with Jaya and Hayley's lack of Agent-y professionalism.



Oliver and Jonah can see figures walking out from the Factory next to the Yard.   They stop and one of them waves at someone outside of the Yard, somewhat of a beckoning gesture.



Jaya and Hayley make it down the ground floor (after hip-checking some old dude out of the way).  Oliver gets into position on the first floor of a building near the Yard.



{[}\textit{Challenge: Notice 1.  Small Unit Tactics 2 (Jonah) $\rightarrow$ Overcome! }\textit{\textbf{1 VP (Jonah)}}{]}  Jonah notices that the \#2 guy (nearest to Lackovich) has pulled out a pistol.  Guy \#1 is looking toward the Apartment in Jaya/Hayley/Dev's general direction. 



There is another discussion/argument on what to do.  Oliver takes control of the plan and says to send someone out, someone expendable.  Hayley immediately volunteers but Jaya holds her back and instead goes back into the building and drags out a random civilian.  Jonah and Hayley object (the former because it's not right, the latter because he isn't trained in parlay so he would be a terrible representative for the TA).   Jonah gets confused {[}\textit{Refresh Operator 1 (Jonah)}{]}.



As they argue, the civilian runs off.  Giving up on a more subtle plan, Hayley and Jaya just start walking toward the Yard.  Jaya pauses, worried about landmines, but Hayley says they could try to trigger them with rocks.  So they start chucking rocks out into the Yard.  This draws the attention of Guy \#2.



They are about to walk out into the open together when Hayley tells Jaya that she should stay here and Hayley should go alone.  No sense in both of them dying and Jaya's more important than Hayley.  Jaya agrees with this sensible plan.  She switches Hayley's radio so that it is microphone only: everyone with the radios can hear what Hayley says or what is said around her, but it doesn't broadcast their chatter (so she can't hear them if they try to speak to her).



\textbf{{[}The Yard activated.  15 Tokens enter the Pool{]}}



Hayley walks up to Lackovich and Guy \#2, making no effort to sneak or move in a defensive manner. She can see that Lackovich is gagged and wrapped up in cloth, like a straightjacket. She is tied to a chair.  Her head isn't moving for some reason and her eyes are wide open.



Guy \#2 speaks to Hayley, ``you really shouldn't have killed my constituent.''

Hayley looks puzzled at the word, but replies, ``Sorry.  What is a constituent?''

``I'm not going to talk to you.  We want the one you call Langdon.  Just to talk.''



Jonah reports over the radios, ``Hayley is in the line of fire.''

``I sent Hayley in,'' says Jaya.



This snaps Oliver out of his daze and he starts paying attention to what is going on.

He activates Operator and tells Hayley to say what he is thinking, and she agrees easily.

``This is Langdon,'' Olivery/Hayley says. ``You have my attention.  Let's talk.''

\hl{As Hayley speaks,}\footnote{\textbf{Suko T }Convo is very patchy because I was speaking during it and not taking many notes.  Please fill in missing parts/amend misremembered parts, if you can. \textsubscript{03/14/14 1:39am}} Jaya can see Hayley's posture shifting, going from perfect and balanced posture to listing slightly to one side and favoring one leg.



Guy \#2 frowns, ``We want to speak with you, face to face.''

``So do I,'' says Oliver/Hayley.  ``Guess neither of us will get what we want.''

``I guess this will do,'' says Guy \#2.  ``We want you to stop interfering.''

``I could say the same about you,'' replies Oliver/Hayley.



``You are resisting our control of the Directorate.  If you don't stop, we will be forced to take measures, both impersonal and \textit{very} personal,'' says Guy \#2.



``Who do you work for?'' asks Guy \#2

``The Transit Authority.''

``Really?  The TA or Gerhauser?''

``Who do \textit{you }work for?'' asks Oliver/Hayley.``Myself.''



``Who is this 'We'?  What do you mean you control the Directorate?'' asks Oliver/Hayley.

``If you have to ask, I'm not going to tell you who is in our pocket.''



Oliver thinks, ``Yeah, Gerhauser is a bitch but she...''

Hayley can't bring herself to repeat such rude words, even if she agrees with the sentiment, and the resistance breaks the already fraying connection.



Oliver tries to push it to keep the connection {[}\textit{Refresh Operator 1 (Oliver)}{]} and instead he feels a sudden shock of pain like knives slicing into his back.  He pitches forward.  {[}\textit{Challenge 3: Don't set off gun.  Hardened 4 (Oliver) $\rightarrow$ Overcome! }\textit{\textbf{3 VP (Oliver)}}{]}



Hayley feels odd...her head is suddenly much emptier than usual.  She pauses for a long moment, in her head thinking loudly: ``Operator Langdon?  Oliver?  Helllllooooo?''



After a while, she turns back to Guy \#2.  ``Sorry, I think Operator Langdon isn't available right now, we seem to have lost the connection.  You will have to wait.''

``You're wrong,''

``No, I am pretty certain he is not communicating with me.''

``Not about that.  You're wrong that we have to wait.''

``Hmm, well you can speak to me,'' says Hayley.

``We need an answer.'' 

``I told you he is not available.  I'll keep trying though.''

``You can answer.''

``No I can't,'' says Hayley.

Guy \#2 thinks and then says, ``Have you been on a boat?''

``Yes, three times,'' says Hayley, unfazed by the non-sequitur.

``\hl{You and Langdon are on the same boat.}\footnote{\textbf{q.google }But not so unfazed by metaphor ;). \textsubscript{05/01/14 12:38pm}}  So your answer speaks for him too.''

``Oh,'' says Hayley. ``I don't think I can....''  in her head she calls out to Oliver again.  When there is no reply, she asks Guy \#2, ``What are you planning on doing?''

``I'm not going to tell you.''

``If you don't, how do we know how to not interfere with you, if we don't know what it is that you are doing?  \hl{Gerhauser}\footnote{\textbf{Suko T }She doesn't use the title Agent.  I think some of Oliver's anti-establishment attitude is still getting through :) \textsubscript{03/16/14 2:47am}}won't tell us what she is doing.''

``Just get Gerhauser to stop what she is doing.  \hl{You don't need to know what it is}\footnote{\textbf{q.google }Oh sure.  That's simple then.  Us: ``Hey, highly outranking superior officer: stop what you are doing!''
Them: ``What's that then?''
Us: ``We don't know.  But you should stop it.'' \textsubscript{05/01/14 12:39pm}}.''



Hayley looks at the three other figures and says curiously to Guy \#2, ``Are these all your constituents?  Are you with all of them?''

``Are you stupid?''

``Yes.  That is why I am asking.''

Guy \#2 pauses and looks at the guy next to him then answers, ``This is clearly above your level of understanding.  I am, but in some ways, of course I'm not.''



{[}\textit{Challenge: Notice 2.  Vigilant 3 (Jonah)  $\rightarrow$ Overcome! }\textit{\textbf{2 VP (Jonah)}}{]}  At this point, Jonah notices a rod strapped to one of the legs of the chair.  It is odd-looking, clearly advanced technology.



{[}\textit{Refresh: Small Unit Tactics 2 (Jonah)}{]}  Jonah orders everyone to head out on his mark, but then gets distracted by noticing the tech on Lackovich's chair and doesn't actually complete the command action.



Hayley moves toward Lackovich and Guy \#2 tries to grab her.  She tries to get out of the way but moves in just the wrong direction.  {[}\textit{Refresh: Saltaremachy 2 (Hayley)}{]}.  {[}\textit{Challenge: Don't get grabbed 4.  Sidearm 3 (Jaya) + Crack Shot 3 (Oliver) $\rightarrow$ Matched}{]}.  Jaya and Oliver both fire on the guy and he takes a hit to the ribs and goes reeling back.



{[}\textit{Challenge: Notice 1.  Ladies' Maid 2 (Hayley) $\rightarrow$ Overcome! }\textit{\textbf{1 VP (Hayley)}}{]} Guy \#2's cloak is torn and his armor is somewhat damaged.  He pulls back his visor and Hayley can see his face.  His skin is well moisturized and his cheekbones are fabulous.  \hl{She's momentarily distracted by his handsome good looks and excellent skincare.}\footnote{\textbf{q.google } \textsubscript{05/01/14 12:43pm}}  She doesn't recognize him.



Two of the other guys throw something up in the air that explode and starts releasing black smoke.



Jaya rushes Guy \#1.  {[}\textit{Challenge: Knock over Guy \#1 2.  Adrenaline Junkie 2 (Jaya) + Pistol 2 (Jaya)  $\rightarrow$ Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}.  She knocks him to the ground.



Guy \#2 starts moving toward Lackovich.  Hayley also starts running toward Lackovich.  Oliver uses Operator to tell Hayley to step aside, giving him a clear shot at Guy \#2 but delaying her reaching Lackovich.  Guy \#2 reaches Lackovich and kicks the leg of the chair out that had the rod attached to it.  He kneels down, and starts doing something to the ground.  {[}\textit{Challenge: Body Shot 3.  Sniper 3 (Oliver) $\rightarrow$ Matched}{]}.  Oliver shoots the guy and he stumbles back away from Lackovich.



Jaya starts punching Guy \#1.  He says, ``I'm going to kill your sister.'' which enrages Jaya.  {[}\textit{Challenge: Crush face to bloody pulp 2.  Truncheon 3 (Jaya)  $\rightarrow$ Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}.  She beats his face in and kills him..



{[}\textit{Refresh Operator 1 (Jonah)}{]} Jonah chooses to tap into Jaya's mind at precisely the wrong moment and is disturbed by the visual and rush of feelings he gets from Jaya.



The ground below Lackovich starts moving.  It is a grate that is opening downward.  Lackovich's chair (with her still tied to it) starts to fall.  



{[}\textit{Refresh Crackshot 3 (Oliver)}{]}  Oliver reloads.

{[}\textit{Refresh Pistol 2 (Jaya)}{]}  Jaya reloads.



{[}\textit{Challenge: Keep Lackovich from falling 2.  Conditioned 2 (Hayley) $\rightarrow$ Matched}{]}  Hayley dives to grab Lackovich, the deadweight of her body and the chair wrenching Hayley's arms painfully, but she hangs on.  From this vantage point, she can see that below Lackovich there is just darkness and an odd noise.  There is a rush of air as the air and smoke are sucked into the darkness below.



Guy \#2 aims his gun at Hayley and says, ``We said that you would do.''



{[}\textit{Challenge: Not get shot 4.  Armor 2 (Hayley) + Grim Visage 2 (Jaya) + Saltremachy 2 (Hayley) + Flaw: Shot in the ribs 2 (Hayley) $\rightarrow$ Matched}{]}  Jaya screams at the guy and rushes at him, distracting him.  Hayley manages to twist just enough to take \hl{the gunshot to her ribs instead of a more immediately lethal area}\footnote{\textbf{Rebecca S. }wait, what? isn't getting shot in the ribs pretty lethal? \textsubscript{04/24/14 8:55pm}}\footnote{$\rightarrow$\textbf{Suko T }All a matter of degree.  It's less immediately lethal than the back of her head. :)  She can survive having a hole in her lungs longer than a hole in her skull.... \textsubscript{04/24/14 9:28pm}}, and not lose her grip on Lackovich.



Guy \#2 spins toward Jaya and runs toward the Factory.  Jaya pursues.



{[}\textit{Refresh: Sniper Rifle 3 (Oliver)}{]}  As Guy \#2 clears the smoke, Oliver lines up a perfect shot on Guy \#2 but his gun jams.  Over the radio, they can hear him cursing.



{[}\textit{Refresh: Sidearm 2 (Jaya)}{]}  Jaya fires wildly at the guy, completely missing in all the smoke, and is forced to pause to reload.



{[}\textit{Refresh: Stash 2 (Jaya)}{]}  Needing a hit to steady her nerves, Jaya takes a big lungful of the black smoke and starts coughing.



There is a weird ``pop'' noise and the air stops being pulled into the hole.



Jaya goes over to Hayley and helps pull up Lackovich.  As Hayley staggers to her feet, Jaya cuts Lackovich free.  Lackovich's expression is not the ego-stroking look of humiliation or gratitude that Jaya was expecting.



Jaya assists Hayley off the Yard, with Lackovich walking after them.  Everyone (on the TA side, minus Dev) regroups in one of the buildings near the Yard.  Jonah instructs Franke, Diego and Leah to go back to the Apartment, fetch all of the tech that was there and the body of the dead guy and take all of that (plus the body of Guy \#1) to the TA Station and stay there until further instructions.



Jonah treats Hayley's wounds. {[}\textit{Challenge: Reduce Flaw 2 (Hayley).  Street Medic 2 (Jonah) $\rightarrow$ Flaw 1 injured ribs (Hayley)}{]}. 



\textit{{[}Refresh: Adrenaline Junkie 2 (Jaya)}{]} \hl{Jaya advises that we pause and think this through.}\footnote{\textbf{q.google }Ok, that's \_it\_.  Tackle the evil clone to the ground! \textsubscript{05/01/14 12:45pm}}  This looks dangerous, we're injured, we achieved the Mission objective (Lackovich) and can just return to SAC-09.  Oliver says that he's still going after the Orc.  Lackovich supports this plan, saying this is our best chance to find him.  Jonah tries to find a compromise.  Hayley just waits until someone tells her what to do.



While they argue, Hayley asks where Lackovich's weapons are, and why she went \hl{AWOL}\footnote{\textbf{Suko T }I seem to recall the implication but not outright statement that Morgan sent her on the mission covertly with plausible deniability.  Or did Lackovich just cowboy up on her own? \textsubscript{03/17/14 2:18am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }There was an implication of something, but what the implication was precisely may not have been clear. \textsubscript{03/19/14 4:46pm}}\footnote{$\rightarrow$\textbf{Suko T }Cool.  Hayley's not exactly the best person to interrogate Lackovich for information either way :) \textsubscript{03/19/14 11:00pm}}.  Lackovich says she was ambushed and they took her weapons.



When Jaya pushes harder to quit now, {[}\textit{Refresh: Hardened 4 (Oliver)}{]}  Oliver just leaves.  Lackovich grabs a gun and heads after Oliver.  Jaya runs after them.  Jonah and Hayley follow.



Lackovich and Oliver approach the Factory.  Lackovich enters first.



\textbf{{[}The Factory activated.  25 Tokens enter the Pool{]}}



It is full of old, rusted equipment.  It is very dark and we must use our flashlights.



{[}\textit{Challenge: Notice 1.  Forensics 2 (Jonah) $\rightarrow$ Overcome! }\textit{\textbf{1 VP (Jonah)}}{]}  Jonah notices that there are marks of someone being dragged into the Factory.  Lackovich says that it wasn't her.  We follow the drag marks to a room and find Dev's body hanging from a chain.  We get his body down. He is dead.



{[}\textit{Refresh: Truncheon 3 (Jaya)}{]}  With somewhat chilling practicality.  Jaya replaces her missing truncheon with Dev's.



{[}\textit{Refresh: Operator 1 (Oliver)}{]}  Oliver feels very guilty about Dev's death and while he can control his expression, those feelings spill over into Hayley.  Overcome with unexpected feelings of guilt over this random person she's barely met and a strong compulsion not to show it, Hayley falls to her knees and claps her hands over her mouth to keep from crying out.



\hl{{[}\textit{Refresh: Operator 1 (Jonah)}{]} }\footnote{\textbf{Suko T }?? Can't remember what happened for this Refresh. \textsubscript{03/18/14 12:57am}}



{[}\textit{Refresh: Ladies' Maid 2 (Hayley)}{]} Bewildered and uncertain how to cope with these feelings, Hayley gets obsessed with tidying Dev's body and laying him out with respect.  She cannot be deterred from this task until Jonah drags her away forcibly, causing them to be fairly delayed in following after Oliver, Lackovich and Jaya.



Oliver starts climbing a ladder with Lackovich not far behind.  Oliver reaches the top of the ladder and a figure attacks him.  Lackovich and Jaya can hear a scuffle but aren't close enough to assist.  ``I would love to help you, but all I can do is shoot a gun,'' yells Jaya.  {[}\textit{Challenge: Don't get grabbed 5.  Hardened 4 (Oliver) + Sniper Rifle 3 (Oliver) + }\textit{ {\color[RGB]{255,0,0}Flaw: Winded 2 (Oliver)} }\textit{ + }\textit{ {\color[RGB]{255,0,0}Flaw: damaged gun 2 (Oliver)} }\textit{ $\rightarrow$ Matched}{]}.  Oliver pulls free but his rifle is damaged in the process and he gets the wind knocked out of him.



Oliver sees a backlit figure in a cloak.  A raspy voice says ``Don't you want to know who you are hunting?''



Lackovich and Jaya are trying to climb up the ladder and Lackovich is getting in Jaya's way.  



``Tell them to stop,'' the Orc tells Oliver.

``Stand back,'' Oliver says to Lackovich and Jaya.



``I know exactly what I need to know about you,'' Oliver says to the figure.  He tries to fire his gun but it misfires from the damage earlier.   The Orc moves defensively out of the way and then realizes the gun is not functioning.  \hl{The Orc grabs Oliver's collar and leans in close}\footnote{\textbf{Nathaniel Ford }The Orc grabbed his BDU collar and pulled him close before saying, ``Are you sure?'' Then Oliver was slammed into the wall before the Orc took off. \textsubscript{03/19/14 11:34am}}\footnote{$\rightarrow$\textbf{Suko T }Cool, thanks!  Fixed. \textsubscript{03/19/14 11:01pm}}.  ``Are you sure?'' says the Orc.  \hl{A strand of dark hair with reddish highlights brushes Oliver's face}\footnote{\textbf{q.google }Cue dramatic music!  The boards are talking about this for days afterwards. \textsubscript{05/01/14 12:48pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Google really needs to implement a +1 on comments. Seriously. They integrated G+ everywhere else. \textsubscript{05/01/14 3:24pm}} as the Orc slams him against the wall.  {[}\textit{Challenge: Stay in the fight 3.  Battle dress uniform 2 (Oliver) + Arm Strength 1 (Oliver) + }\textit{ {\color[RGB]{255,0,0}Flaw: Stunned 1 (Oliver)} }\textit{ $\rightarrow$ Matched}{]}  The Orc leaves.





{[}\textit{\textbf{25 Tokens}}\textit{\textbf{ left in pool}}{]}





\jumpHeadline{ Challenges \& Refreshes }  



\begin{itemize}[noitemsep,topsep=0pt]
\item Refresh Operator 1 (Oliver)
\item Refresh Vigilant 3 (Jonah)
\item Challenge: Find Dev 2. Nose for Breadcrumbs 2 (Hayley) $\rightarrow$ Matched
\item Challenge: Notice 1.  Small Unit Tactics 2 (Jonah) $\rightarrow$ Overcome! \textbf{1 VP (Jonah)}
\item Refresh Operator 1 (Jonah)
\item Refresh Operator 1 (Oliver)
\item Challenge 3: Don't set off gun.  Hardened 4 (Oliver) $\rightarrow$ Overcome! \textbf{3 VP (Oliver)}
\item Challenge: Notice 2.  Vigilant 3 (Jonah)  $\rightarrow$ Overcome! \textbf{2 VP (Jonah)}
\item Refresh: Small Unit Tactics 2 (Jonah)
\item Refresh: Saltremachy 2 (Hayley)
\item Challenge: Don't get grabbed 4.  Sidearm 3 (Jaya) + Crack Shot 3 (Oliver) $\rightarrow$ Matched
\item Challenge: Notice 1.  Ladies' Maid 2 (Hayley) $\rightarrow$ Overcome! \textbf{1 VP (Hayley)}
\item Challenge: Knock over Guy \#1 2.  Adrenaline Junkie 2 (Jaya) + Pistol 2 (Jaya)  $\rightarrow$ Overcome! \textbf{2 VP (Jaya)}
\item Challenge: Body Shot 3.  Sniper 3 (Oliver) $\rightarrow$ Matched
\item Challenge: Crush face to bloody pulp 2.  Truncheon 3 (Jaya)  $\rightarrow$ Overcome! \textbf{2 VP (Jaya)}
\item Refresh Operator 1 (Jonah)
\item Refresh Crackshot 3 (Oliver)
\item Refresh Pistol 2 (Jaya)
\item Challenge: Keep Lackovich from falling 2.  Conditioned 2 (Hayley) $\rightarrow$ Matched
\item Challenge: Not get shot 4.  Armor 2 (Hayley) + Grim Visage 2 (Jaya) + Saltremachy 2 (Hayley) + Flaw: Shot in the ribs 2 (Hayley) $\rightarrow$ Matched
\item Refresh: Sniper Rifle 3 (Oliver)
\item Refresh: Sidearm 2 (Jaya)
\item Refresh: Stash 2 (Jaya)
\item Reduce Flaw 2 (Hayley).  Street Medic 2 (Jonah) $\rightarrow$  {\color[RGB]{255,0,0}Flaw 1 injured ribs (Hayley)} 
\item Refresh: Adrenaline Junkie 2 (Jaya)
\item Refresh: Hardened 4 (Oliver)
\item Challenge: Notice 1.  Forensics 2 (Jonah) $\rightarrow$ Overcome! \textbf{1 VP (Jonah)}
\item Refresh: Truncheon 3 (Jaya)
\item Refresh: Operator 1 (Oliver)
\item Refresh: Ladies' Maid 2 (Hayley)
\item Refresh: Operator 1 (Jonah)
\item Challenge: Don't get grabbed 5.  Hardened 4 (Oliver) + Sniper Rifle 3 (Oliver) +  {\color[RGB]{255,0,0}Flaw: Winded 2 (Oliver)}  +  {\color[RGB]{255,0,0}Flaw: damaged gun 2 (Oliver)}  $\rightarrow$ Matched
\item Challenge: Stay in the fight 3.  Battle dress uniform 2 (Oliver) + Arm Strength 1 (Oliver) +  {\color[RGB]{255,0,0}Flaw: Stunned 1 (Oliver)}  $\rightarrow$ Matched
\end{itemize}





\jumpHeadline{ VP TOTALS }  

{
\parskip=0pt
Jaya: 4

Jonah: 4

Oliver: 3

Hayley: 1
}



\jumpHeadline{Quotes }

\quotedDialog{
``You have one job, which you are totally unqualified for...'' - Nate

``Welcome to the TA.'' - Adam
}


``Doesn't anyone have, I don't know, 'eyesight'?'' 
\extraIndent{- Jaya}


\quotedDialog{
``I guess becoming an Agent is more of a lottery thing.'' - Diego (Nate)

``Let me put it this way, it may start out as a lottery but the training is not.'' - Jonah

``You've had training??'' - Franke (Nate)

``Yeah.'' - Jonah

``Well you sorta seem to know what you're doing.'' - Diego

``That's the training.'' - Jonah
}


``I use psychology to access his inner death wish.'' 
\extraIndent{- Rebecca}



``I would love to help you, but all I can do is shoot a gun.'' 
\extraIndent{- Jaya}


\quotedDialog{
``Is {[}Lackovich{]} blocking me?'' -Rebecca 

``It's kind of her narrative role.'' -Nate\\[4mm] % need 4mm break to prevent quote blocks from running together!
}

\quotedDialog{
``Are these all your constituents?  Are you with all of them?'' - Hayley

``Are you stupid?'' - Agent \#2

``Yes.  That is why I am asking.'' - Hayley
}



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 10:45am
\end{flushright}

