\setcounter{chapter}{ 23 }
\chapter{\textbf{``Be careful what you wish for''} }




\subChapterTitle{(Backlash)}



\textit{Notes:} Suko

\textit{Date:} May 1st, 2014



Some silver linings but they're attached to rather dark clouds.  Jonah got tons of information but mostly it was terrifying. Hayley was so happy to see Signe was okay, but Trenton's mad at her for some reason and it probably has to do with the corpse in his lab.  Jaya got an awesome cyborg arm but her sister's shop got firebombed and Padme is in the wind.  And we have no idea where Oliver is, though some think he may still be alive.



\noindent\hrulefill





\jumpHeadline{Backlash } 


\sceneHeadline{SAC-09  {[}30 Backlash Tokens{]}}

The train arrives at SAC-09.  Lackovich and Jaya are mostly unconscious at this point and Hayley's fading in and out from bloodloss.  Jonah sees a lot of equipment and guns piled up somewhat haphazardly on the platform. Dr. Gerhauser, Swan and Larissa are there with several stretchers.  For the first time that we can remember, the gun nest is active (though no one is manning it at the moment).



Dr. Gerhauser boards the train and asks Jonah who is the most injured.  Jonah indicates Lackovich.  Rook and Jonah load Lackovich onto a stretcher.  Dr. Gerhauser evaluates Jaya and tells Hayley to go get another stretcher.  She then asks Jonah if he's able to do a surgery assist.  Jonah says he's never done surgery before.  Dr. Gerhauser says that if he read the books that she gave him, he'll be fine.  Plus he'll just be assisting.  She and Swan will do the primary surgical procedures.  Jonah agrees to help, and when given the choice, chooses to assist with Lackovich.

Jaya groggily registers his choice. ``Hey!''

``You ever operate on a friend?'' says Jonah.

``We're friends??'' says Jaya, surprised.

Hayley returns with the stretcher and is instructed to cart Jaya to MedBay.




\sceneHeadline{Jonah assists in Lackovich's surgery}

Jonah and Larissa assist Dr. Gerhauser with Lackovich's surgery.  She's in pretty bad shape.  Lots of trauma, many blunt force injuries as well as some smaller incisions.  Many were stitched up or semi-healed in some way.   Dr. Gerhauser uses equipment and some procedures that are far beyond Jonah's experience as a field medic.  They keep Lackovich sedated but conscious.  At one point Dr. Gerhauser asks for a certain procedure and Larissa pauses.  ``That might affect reproduction,'' Larissa cautions.  

``She's already lost it, so that won't matter,'' replies Dr. Gerhauser.

``Right.  I had forgotten,'' said Larissa and proceeds with Dr. Gerhauser's instructions.


\sceneHeadline{Hayley gets a Theta3 scan}

Once Jaya is set up and sedated, \hl{Swan examines Hayley}\footnote{\textbf{Nathaniel Ford }Note that Hayley also went through post-mission surgery, though to a lesser extent than Jaya. \textsubscript{05/10/14 12:55am}}.  She has some fractured ribs, some bleeding, and is covered in deep bruises from the gunshot impacts, but is not in too terrible shape (for her).  He moves swiftly through the exam, and is clearly a bit disconcerted at how good Hayley is at helping him examine her.



Swan has her lie down and places a cap on her head with leads attached to it.  He then passes a device (wand-like) over her body.  He looks concerned at the readings and \hl{types things}\footnote{\textbf{Nathaniel Ford }This was methodical and intense. And different from note-taking that may have been seen in the past. \textsubscript{05/10/14 12:59am}} into the computer for a while.  He seems to think about what he wants to say and tells Hayley, ``Your readings are... hmm.  If anyone else wants to run a Theta3 Scan on you, please contact me first.  That scanner I just used, that is a Theta3 test.''

``Okay.''  Then Hayley thinks for a moment.  ``Anyone?  Even Dr. Gerhauser?''Swan pauses and then says, ``Yes, even Dr. Gerhauser.''

``Okay.''

``Good.  I, er, have to go.''

``Of course, I can finish up by myself,'' says Hayley, already starting to clean up the used bandages and put the medical equipment away.


\sceneHeadline{Jonah and Hayley talk to Dr. G.}

Jonah and Hayley are summoned to the Ops room.  Hayley changes out of her hospital gown and dresses in a tech jumpsuit, the only spare clothing available in the Medbay.



Dr. Gerhauser is there, seated at the table.  One of the Tanks behind her is occupied.  Inside is Carruthers, who moves and speaks occasionally (though it is hard to hear what she is actually saying).  Larissa is also there, typing at a computer.  Dr. Gerhauser debriefs Jonah and Hayley.  Hayley tells Dr. Gerhauser that the Orc (or one of the Orc's constituents, Hayley isn't certain that was the Orc) said to ``tell her sisters goodbye and that she'll be seeing you soon.''  Dr. Gerhauser responds, ``She always did have an odd sense of humor.''



Jonah quizzes Dr. Gerhauser on what was going on with the Orc.  Were they all Operators and Agents?  Dr. Gerhauser explains that they are using a different version of the tech, one where there aren't really Operators and Agents.

``And they are much better looking,'' chimes in Hayley.

Right at that moment, Carruthers says clearly, ``Morgan's been shot.''




\sceneHeadline{Jaya and Rook and her new arm}

Jaya groggily comes in and out during her surgery.  Some of it is a bit confusing, the noises sounding more like she is in a machine shop than a surgery room.  She tries to keep reminding them that her hand is in her backpack, Jonah knows where it is.  She sees Agent Rook there occasionally.



She comes to, seated in a chair.  She's in pain but the edge is blunted with drugs and it's difficult to move at all.  There's a cone around her left arm, preventing her from seeing it.  Agent Rook is there.  He says conversationally, ``You know what?  All this ink is really incredible.  I always wanted to tell you that.''

Jaya flirts, ``Did you see the one on my thigh? I did that one myself.''

\hl{Rook is unfazed.}\footnote{\textbf{q.google }There are three certainties in life: death, taxes, and the demeanor of Agent Rook. \textsubscript{05/11/14 11:33am}}  ``Indeed, that one is very nice.''  He looks at her in concern.  ``You should be more careful in the future.  You have this great history, it would be a shame to lose it all.''

Jaya is flattered but confused.  ``Yeah, tattoos are great.''

``It is wonderful how you have marked your history on your skin like that.''

``Well.... some of them weren't the best decisions, ya know?''

``But it is still a record of your experiences,'' says Rook.

Warming to the topic now, Jaya says with all the enthusiasm she can muster, given all the drugs she's on, ``Yeah, I keep trying to tell Hayley to get one, but she won't.  Hey, maybe you should talk to her about it!''

``I'll keep that in mind.''

``So what's going on?  Did you find my hand?'' asks Jaya.

``Ah. I see no one has told you yet.''

``Told me what?''

``You lost your left arm.  It has been replaced-''

``What?  No, it's in my backpack!''

``Take a deep breath and tell me you love me,'' says Rook calmly.

``What the fuck?'' exclaims Jaya.

``Just repeat the words.''

``The FUCK you say!!''

Rook sighs.  ``You don't have to say them to me.  Think of someone else if you like.''``No.  No way.''

``Just say it.'' says Rook, his tone getting a bit more emphatic.

``Fine!  I'm just saying it, it doesn't mean anything.''  Jaya turns her head and mumbles, ``I love you.''

There is an emphatic 'clunk' and Rook removes the cone from her arm, to display the stump, capped with metal. He is holding a mechanical forearm-and-hand. He holds it up so Jaya can see it.  Jaya struggles through the drugs to raise her hand and pets it.

``It won't hold ink,'' cautions Rook.  ``So you won't be able to get any with tattoos.''

Jaya misunderstands, ``I'll get any tattoos I want!  I'm still on the ink road!''

``The ink road is fine.  I'm quite jealous.''


\sceneHeadline{Jonah and Rook}

Jonah and Hayley leave Ops.  Hayley heads back to Medbay.   Jonah goes to the firing range to practice.  Rook finds him there and asks if he has a moment to talk.

Rook tells Jonah that they gave Jaya a prosthetic and she's in recovery now.  The reason he wanted to talk to Jonah is that there is a lot of unrest going on out there.  If Jonah wants to see his family, this may be his last chance to do so for a while.  Jonah says he wants to see them.  Rook asks why.

``I just want to see that they are safe and to get them out,'' replies Jonah.

``Get them out where?'' asks Rook

``Someplace safer.''

``Where would that be?''

``I - I don't know.  I'd have to think about it,'' says Jonah.

``I suspected that might be the case.''  Rook hands Jonah a stack of documents.  ``Here, these are travel authorization papers and some letters of marque.  Use them at your discretion.''  Rook pauses and adds.  ``You can, if you like, have them brought here.  But this is not necessarily any safer.''

Jonah nods and Rook leaves.  After Rook is already out of the door, Jonah looks up suddenly and asks, ``Wait, what's a prosthetic?''


\sceneHeadline{Hayley, Trenton and Swan (and Signe)}

Hayley is paged in Medbay: ``Trenton would like to see you in Lab 4''.



Hayley heads down to Lab 4.  It is dimly lit.  Trenton is not looking at her, he's looking at some computer monitors which have images of a human form on them.  There is a cart on the left side with a cloth-draped body lying on it.  



Trenton doesn't even turn to look.  ``Take off your shirt.''

``I don't have a shirt on, if I take off my jumpsuit, I take off everything,'' says Hayley.

``Fine, whatever.  Just take it off.''  He's not asking.

Hayley starts to obey and then pauses, holding the neck of her jumpsuit closed.  ``Are you allowed to see me naked?  I have secrets I'm not supposed to show.'' 

``I probably know them,'' Trenton replies flatly, with none of his usual flirtation or innuendo.  Hayley thinks he sounds upset, maybe?

Hayley disrobes and stands there.  She doesn't try to cover herself but her face and posture show how uncomfortable she is.  Trenton just looks at her scars.  He tells her to turn around so he can see her back, which she does, though her tension and anxiety increase.  Several seconds pass.  ``Get dressed,'' Trenton orders.  Hayley dresses and waits warily to find out what he wants from her.



Trenton looks at Hayley intently.  ``It turns out I'm the smartest person here.  I've helped many people.  I've earned enough water credits to feed hundreds.  I could afford anything I want.''  His voice is getting more and more worked up.  Hayley thinks maybe he is angry?  He takes a deep breath and says in a measured voice, full of emotion that Hayley can't read, ``But she's the only one I've ever truly healed.''



Hayley looks at him blankly, not understanding what he means, and also preparing herself mentally for him to take out his anger on her, as Citizens do.  Trenton looks at her for a long moment and then leaves abruptly.



Hayley waits for him to return, but as time passes, she starts looking around the lab.  She's very aware of the body on the cart and skirts around it carefully.   She's glad the body is covered with a sheet so she doesn't have to look at a yucky dead thing.



She looks up at the monitors and then realizes that they are images of scars.  Specifically \textit{her} scars.  But it's not her skin.  The color is different and the shapes are off.  She is fascinated by them until she realizes that the ID in the corner is labeled ``corpse''.



Worried, she pages Dr. Gerhauser (who is busy) and then Swan.  ``What can I do for you?'' he asks.

``I'm in Lab 4.  I'm not dead, am I?'' asks Hayley.

``Stay there!  I'll be right over,'' instructs Swan, alarmed.

Within minutes, he comes running.  He is relieved that Hayley is standing there, looking no more injured than she was earlier.  She points to the monitors.  ``Those scars are mine.  I know each one and where they came from.  But the ID says 'corpse.'   I don't understand.''

Swan, hesitates, clearly uncomfortable, then explains, ``Someone wanted to kill you, but when they couldn't get you, they wanted to be clear that they knew a lot about you.  So they chose someone close to you and did this to them.''  He looks at her significantly, but Hayley clearly has no idea what he's talking about.

``You remember how we had to pull Signe and that guy from the Warehouse District -'' he tries again.

``Signe!''  Hayley interrupts, ``Is she okay?''

Swan pauses and seems to reconsider what he was going to say.  ``Er, I don't think I can talk about that now.''

``But is she here?'' Hayley persists.

Swan leads Hayley back to MedBay, with Hayley attempting to ask again where Signe is (part of her is beginning to suspect something is wrong so she is more persistent than usual) and Swan fending her off with non-committal answers.  He leaves Hayley with Jaya and tells them both to eat heartily.  And makes his escape.


\sceneHeadline{Hayley, Jaya and Jonah}

Hayley and Jaya go to the mess hall to eat.  Jonah arrives soon after and helps them get some food.  Jaya has trouble adjusting to her one-armed state and makes a mess of her food.  Hayley assists her as best she can, clearly having experience feeding someone, or eating one handed.  



As they are eating, over the loudspeaker comes the announcement, ``Incoming casualties, all hands report to the platform.''



Jaya runs for the platform. Hayley runs after her, picking up Jaya when she falls or collides with a wall.  Jonah, still exhausted from the surgery, follows at a less frantic pace.  Rook and Swan are at the platform, with Dr. Gerhauser coming up behind Jonah.  She tells Jaya that she should try to stay out of the way if she can, so of course Jaya immediately gets in the way.  Dr. Gerhauser orders Hayley to pick up a stretcher, which Hayley does (of course) and trails after Dr. Gerhauser.



The train is just pulling in.  The doors open.  There are two bodies propped against the wall.  Morgan is one of them, and Javier is trying to hold her guts in.  Davis is the other one and he looks dead.  Micah is passed out and Karil is trying to patch him up, clumsily.  There is burnt hexagonal object covered in blood.



Dr. Gerhauser asks who is the most in need of medical attention.  She looks at Davis and Javier shakes his head.  Hayley helps load Morgan onto a stretcher and she and Rook carry her to MedBay.  Dr. Gerhauser starts stabilizing Micah for transport.



Dr. Gerhauser asks Jonah if he's able to help with the surgery again.  He says yes and ends up helping Dr. Gerhauser patch up Morgan.   During the surgery Jonah doesn't notice anything particularly odd about Morgan except that all her organs are very healthy looking, almost like the organs of a much younger person.  There are some parts of her skin that Dr. Gerhauser uses different tools on.  Morgan has a bullet wound, abdominal trauma, and a cauterized wound on her shoulder.  Dr. Gerhauser actually spends more time on the shoulder than the bullet wound.  They insert a lot of tubes into Morgan's shoulder and pump her full of drugs.  Enough that even Larissa notes it with surprise.



Jaya eventually managed to make her way down to medbay in an attempt to follow Morgan, and ends up in the observational room.  She spends the entirety of Morgan's operation with her nose pressed to the class, watching intently.  



Hayley returns to the platform after dropping off Morgan and finds Rook there alone, cleaning up.  She offers to help.  He doesn't seem in a chatty mood so they clean in relative silence.  After a while, Rook tells Hayley, ``Someone is looking for you at your bunk.''

``Thank you.  Do you need more help cleaning up or may I leave now?''

``Yes I need help, but you should go.''

``Okay.  I will return after I meet with this person,'' promises Hayley.


\sceneHeadline{Hayley and Signe (!)}

Hayley walks into their bunk to find Signe waiting for her.  Hayley is so overjoyed that \hl{she actually hugs Signe briefly}\footnote{\textbf{Suko T }Part of her was beginning to suspect that something terrible had happened to Signe, so she needed the reassurance of physical contact.  Her subsequent bubbly excitement was partly due to the euphoria of being wrong. \textsubscript{05/02/14 2:07am}}.  It surprises Signe as neither of them are the hugging sort.  It's an awkward unpracticed hug that Signe returns just as awkwardly.  Hayley chatters excitedly that she is so happy to see Signe unhurt.



Signe tells Hayley, ``I'm not supposed to be here.  Trenton said that you can't come see me.  But he didn't say I couldn't come see \textit{you}.''  Signe looks pleased at that loophole and Hayley looks proud of her for figuring that out.  

Signe looks sympathetic, ``I'm sorry about your boy.''

``My boy?'' Hayley looks confused.  ``Who?  I don't have a - do you mean...Operator Gemayel?''  

``No, I'm sorry, I meant Tim, the one you met when you came to visit me...''

``Oh yes!  I remember him.''

``He's dead.  They killed him.  They came for me.  When they couldn't find me, they found him and killed him.'' 

``Oh no, that's sad!  He was nice,'' says Hayley.  Signe and Hayley make their sad faces.

``But \textit{you're} okay, aren't you?  You seem unharmed.'' says Hayley.

\hl{``I'm -'' Signe pauses.  ``I'm here now.  Morgan warned me to get out so I did.'' 

``I'm so happy that you did,'' says Hayley sincerely.

Signe glances at the door.  ``But I should go, I really can't stay long.}''\footnote{\textbf{Nathaniel Ford }It's possible it didn't come through, but Signe should have implied (naively, of course) that she had been in the facility for a while, staying with Trenton, but that she should go back and hang with him since, presumably, someone didn't want her gone long. \textsubscript{05/10/14 1:11am}}\footnote{$\rightarrow$\textbf{Suko T }I think I was picking that up but then got confused when she said she hasn't seen Trenton.  Was she saying hasn't seen him yet *that day*? \textsubscript{05/10/14 2:08am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It was more that 'over the entire course of history she hadn't seen him much', even if recently it was more often than it had been. \textsubscript{05/12/14 12:45pm}}\footnote{$\rightarrow$\textbf{Suko T }Ah, that makes sense.  Not that Hayley would ask for clarification but good for me to know how the subtext was going. \textsubscript{05/13/14 2:54pm}}\footnote{$\rightarrow$\textbf{Suko T }I just added ``yet today'' to make it clearer for posterity. \textsubscript{05/23/14 5:17pm}}

``Do you want to stay?  I think you could stay with me.''  Hayley gestures to her bunk.

``I should go see Trenton, I miss him. I haven't seen him yet today.  Is that okay?''

``Oh of course!  But I would like to see you again.''

``I would too.  I'll be in Trenton's Lab, but you can't come see me there...  Hayley, you should stay away from Trenton for a while, he's pretty mad.''

Hayley nods at the information and then thinks hard for a bit.  She quickly sketches out a map of SAC-09.  ``Here is the cistern.  Not many people go there.  Operator Langdon taught me to swim there.  It's very quiet and private.  Let's meet there sometime.''

``Okay!''  Signe and Hayley look at each other and smile happily.  Signe leaves and Hayley returns to help Rook finish cleaning up.


\sceneHeadline{Jonah, Jaya and Victor}

Jonah and Jaya meetup in the elevator after the operation.  They don't speak to each other.  The elevator stops and the doors open.  Victor is there and looks surprised to see them.  ``Oh good, I wanted to speak with you both.  Your officer... he's still lost isn't he?''

``He's dead,'' says Jaya.

``But the equipment is still active!  And the scan on Agent Hayley shows that the connection is still active also,'' protests Victor.

``Maybe you should speak to her then,'' says Jonah.

``Langdon is dead,'' insists Jaya again.

``He's not dead!''  Victor is even more vehement.  ``I even have an idea how to find him.  Trenton doesn't think it will work but I think it will work!  Just some basic telemetry...'' says Victor, full of stutters and the occasional twitch.

``What's telemetry?'' asks Jonah.  Jaya pushes the ``door close'' button but Victor's standing in the way, blocking the doors from closing.

``Oh ah, it's very complicated, I don't know if I could -'' says Victor, flustered.

``Pretend we are your students, explain it that way,'' says Jonah.

``It's been a long time since I had students....''

``Try,'' says Jonah.  It's not a suggestion.

``Well, first you need to take the signal and triangulate -''

``I know triangulation,'' interjects Jonah.

``Ah good, so you understand that you need three points, that's why we would need all three of you.  Then we could use the...'' and Victor launches into a stream of increasingly complicated and esoteric techno-math-speak.

``Wait, wait,'' says Jaya, ``if we can do this to find Oliver, can't they use this to find us?''

``No, because they only have one point!'' says Victor triumphantly.  He's a little deflated that the other two don't seem to appreciate this advantage as much as he does.

``Yeah, well what if they can do this \textit{telemetry} stuff with one point!?'' Jaya counters smugly. Jaya starts pushing the elevator ``door close'' button again and Victor steps into the elevator to let the doors close. Jaya looks annoyed at this.

``You do want to find him don't you?'' asks Victor.

``We're not going to leave him there,'' says Jonah.

``Trenton thinks that it won't work because of the bomb -''

``Bomb?'' Jonah retorts sharply.  ``\textit{What} bomb!?''

``The timespace bomb.  But it will work!  It rewrote you!  Here, take these to him at his lab.  Which is actually my lab!  I was there first.'' Victor shoves a sheaf of papers at Jonah.

``Why don't you take them yourself?'' asks Jonah.

``He won't listen to me any more, you tell him.  Maybe you can make him listen.''


\sceneHeadline{Jaya and Rook}

Jaya finds Rook and he tells her that if she wants to visit her family, she will need to go now.  She might not get another opportunity to do so for a while.  Jaya says she'd like to see them, but she's not too worried about them.  She figures no one's going to want to blow up the Bucket, they're going to go for richer places like Cardoza.  

``Can I have my arm?''

``Are you ready?  You seem... to be blunt, very eager.''

``I really feel capable of handling this,'' assures Jaya.

``While physically I think it would be best to get you accustomed to it as soon as possible, psychologically I don't know that it's good to give you a dangerous weapon and send you out there...''

\hl{``You do that all the time!''}\footnote{\textbf{q.google }Hear, hear!  Seriously, do they not pay \_any\_ attention? \textsubscript{05/11/14 11:05am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }That's bigotry for ya. \textsubscript{05/12/14 12:46pm}} says Jaya.

``Good point,'' Rook concedes.


\sceneHeadline{Hayley and Jaya}

\hl{Hayley is discharged from the Medbay (they need the room for someone else).  She returns to the bunk and runs into Jaya who is getting ready to visit her family.  Hayley greets her and helps her get dressed and pack a bag.

Hayley ask Jaya, ``Is it okay to have an overnight guest?''

``As long as it's not Trenton, sure.  Just, you know, let us know so we can clear out,'' says Jaya with a wink.

``Oh it wouldn't be Mr. Hadef, he's mad at me right now.''  Hayley looks puzzled.  ``And why would you want to clear out?  Won't you need to sleep also?''

``Who are you going to have over?''

``Signe,'' Hayley says with a happy smile.

Jaya looks a bit surprised and then looks Hayley up and down again, a little intrigued.  ``Huh.  I didn't see that coming.''  She grins.  ``No \textit{wonder} Trenton is mad.''

Hayley smiles back uncertainly, but clearly has no idea what she's talking about.}\footnote{\textbf{Nathaniel Ford }I totally missed this conversation. Delightful! \textsubscript{05/10/14 1:16am}}\footnote{$\rightarrow$\textbf{Suko T }Yeah, that's why I missed the Trenton-Jonah stuff, this was too good to skip :)  I loved the direction it went. \textsubscript{05/10/14 2:15am}}


\sceneHeadline{Jonah and Trenton}

Jonah goes to speak to Trenton in his lab.  He reads that something is wrong with Trenton, but not what, so despite his own urgency he tries to tone things down.  He tells Trenton that he wouldn't ask in a rush, but he needs to know some things very quickly, and they are getting (what he thinks, but doesn't say, may be their last) shore leave very shortly.  Trenton tells him to go ahead.

Jonah has two questions.  One is about using Victor's triangulation to recover Oliver.  Jonah says he knows Victor doesn't think it will work, but wanted Trenton's opinion.  Trenton admits that it \textit{is} possible, but notes that it is complex, plus that it is dangerous to link up multiple people at once.  Jonah presses the point, saying that the Orc was clearly an Operator on several Agents.  Trenton says yes, but this is where the danger is.

``We don't want to be too much like our enemy,'' says Trenton.

``So our enemy connects many people at once, not just as Agents and Operators?  What is the problem with that?''

``Psychological bleed.  You know how when you're in a situation with someone and you get to know them and some of their traits rub off on you and you start to understand how they think...''

``But that could be a good thing,'' says Jonah.

``Yes, to a degree, which is why we think that doing this one on one connection will be okay.  But it can be dangerous.''

Jonah considers this, and decides he doesn't have time to figure it out.  He asks about his second question.

``Victor mentioned something about a bomb.  What was he talking about?'' asks Jonah.

``It wasn't really a bomb like you know them.  It changed a fundamental constant of the universe.''

``But it seems the same, why does that matter?''

``Well I'm rather attached to the universe, aren't you?''

``What did it actually do?''

``You don't have the math to understand it, but let me try to explain it in a simplistic way.  Picture a piece of cloth and you're here in this spot.  Imagine the cloth gets wrinkled up right around that spot.  To you, things will look mostly the same but everything is changed with relation to each other.''

Jonah tries to move Trenton past the explanation.  The how doesn't matter at this point only the what -- and the when.

``When did Victor say it happened?''

``During your last mission.''

``But when, the beginning or the end?'' persists Jonah.  He explains that if it happened at the end it might have well affected the outcome of the battle.  He doesn't say that if it happened in the beginning he can't imagine how it could matter.

``The beginning,'' confirms Trenton.

They are both quiet for a moment and then Trenton says, ``Look, I have to get going...''

Jonah.  ``Me too.  I need to go see my family.''.  As he's walking out he adds ``Feel better.''  \hl{His demeanor implies that he knows what Trenton is going through}\footnote{\textbf{q.google }He doesn't.  He can tell Trenton is upset and not his usual self.  If he knew what had happened, he would be quite rattled.  His presentation is such as to make it seem like he must already know the details, but that's actually just his own stress showing through, which happens to have similar causes. \textsubscript{05/11/14 11:14am}}\footnote{$\rightarrow$\textbf{Suko T }aaand that would be the Social Chameleon 5 kicking in :) \textsubscript{05/11/14 2:25pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1

(And in other news, gDocs makes it REALLY HARD to type +1 without it autocompleting/jumping all over the document. May need a new +1 shorthand.) \textsubscript{05/12/14 12:47pm}}.

\hl{Trenton}\footnote{\textbf{Nathaniel Ford }Not entirely sure if I made this clear, but Trenton had a moment, and actually did straighten/seem better. \textsubscript{05/10/14 1:19am}}stands, smiles and replies, ``That's good advice.''


\sceneHeadline{Jaya and Jonah leave for home}

Jonah meets up with Jaya on the train platform.  Rook walks up carrying a case.  He addresses Jaya, \hl{``It's standard protocol not to arm you on base but... eh.''}\footnote{\textbf{q.google }This actually got quite a reaction out of everyone present.  Hayley was taken aback that protocol could be put aside.  Jaya and Jonah were surprised by \_Rook\_ putting aside protocol. \textsubscript{05/11/14 11:21am}}\footnote{$\rightarrow$\textbf{Suko T }Actually that was just me laughing.   Hayley didn't care- she just noted it as a protocol exception for future use.  

She was more taken aback by the mechanical arm.  She's a snob that way- organic replacements are the best.  It's a matter of professional pride. :) \textsubscript{05/11/14 2:27pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Organic replacements are comparatively expensive, and they tend to be snobby. ;-) \textsubscript{05/12/14 12:48pm}}\footnote{$\rightarrow$\textbf{Suko T }It's all about having high standards.  Which the TA clearly does not. ;-) \textsubscript{05/13/14 2:57pm}} Rook shrugs and opens the case.  He takes out Jaya's mechanical arm and they hook it up.  Jaya starts flexing and moving it around.  Jonah, quite unusually, is openly fascinated and horrified.  He thought Rook was just trying to talk Jaya down about having a replacement arm.  He asks Hayley about it, but her response is even more stunning, that she's seen replacement arms before but never a mechanical one.  The complex of emotions is too much and Jonah pushes it aside.


\sceneHeadline{Jonah's visit home}

Jonah uses his contacts to gather information and gets his family moved to an area in one of the National areas.  He sends his sister a note warning her that if the contact comes she needs to go where he says without asking any questions.  He is deeply divided on whether to try and bring her with him back to base.  For some reason he is much more worried about her than the rest of his family.


\sceneHeadline{Jaya's visit home}

Jaya starts getting a feeling that something is wrong as she approaches LA Ink.  The closer she gets, the stronger the feeling gets.  She walks up the block to LA Ink and sees that the shop is a smoldering ruin.  It is completely destroyed and has been for \hl{a while}\footnote{\textbf{Nathaniel Ford }A while, but not a very long while. It is definitely smoldering. \textsubscript{05/10/14 1:20am}} because the fire has long since been extinguished.  The chairs are hunks of charred and twisted metal.  There is a burned body in one corner.



There's a glint of metal in one shadowy corner and Jaya turns to face a cloaked figure with a sword.  The cloak sorta looks like a miner's cloak and the sword (a katana) is lifted to point at Jaya's neck.  Jaya retreats slowly, and the figure advances a few steps after her and then stops.  Jaya scoops up a chunk of metal to use as a truncheon.



Another person approaches and puts out his hand to stay the cloaked figure.  ``Douglas, no.''  It's Jayce!  His gun is in his holster.

``What the fuck did you do?'' asks Jaya angrily.``This wasn't us!'' protests Jayce.

``Where's my sister?'' demands Jaya. ``Is that her?'' she points to the burned body.

``No, your sister isn't here.  That's one of them.  We were looking for you.  Your sister has gone to ground somewhere, we don't know where.''

``Why are you here?''

``Like I said, we were looking for you.  He,'' Jayce indicates the Douglas, ``needs to talk to your people.  He thinks you have his friend.  I'm just trying to help him out.''

``Let me see his face then,'' says Jaya.

Douglas makes hand gestures but doesn't speak.  Jayce replies verbally and with clumsy signals.  Douglas pulls back his hood.  It's the guy from SAC-01.

Jaya smiles smugly, ``We do have her.  She's locked up.  With Trenton.  So I wouldn't know what state she's in now...''

Douglas raises his sword again and Jaya lifts her truncheon in response.  Douglas easily slices her truncheon in half with his sword.  Jaya is nonplussed but raises the remaining half of her truncheon threateningly.

``Why doesn't he talk?'' Jaya asks Jayce.

``We can't understand his language, I can sort of communicate with military hand signals.  He says that he can show you... 3, 4 and 7.  And he came from 1.  I don't know what that means.  Does it mean anything to you?''

``No.  Why would they mean anything to me?''  Jaya looks at Douglas and Jayce suspiciously. 

``I don't know, he just says that the TA would be interested in this.''

``I suppose I could bring you in, but you better not be lying.  You know what happens when you fuck with the TA!''  Jaya glares at both Jayce and Douglas.  Jaya points at his sword.  ``But if he's coming in he can't have his sword. Give it to me.''

Douglas refuses.

``Fine, then he has to be cuffed.''

Douglas refuses.  Jaya clenches her fist angrily around the end of her shortened truncheon.

``No deal then,'' she says and starts walking away.

``Look he just wants to talk!'' says Jayce loudly.

\hl{Jaya thinks fast}\footnote{\textbf{q.google }So much of this game is us trying to outmaneuver our characters efforts to try as hard as they can to miss the point. That was a nice save . \textsubscript{05/11/14 11:25am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{05/12/14 12:49pm}}.  She pulls out some cuffs.  ``Okay here, cuff the sword to his belt.''

Jayce and Douglas look confused.

``It's a \textit{compromise}.  It's how we do things in the TA.  It's in the manual,'' explains Jaya.

Douglas cuffs the sword to his belt (which apparently doesn't significantly impair Douglas from drawing it).

They head back to the train.  As they walk, Jaya asks Jayce, ``How did he find you?''

``Well he seems to have been watching me for a while.  I guess he saw that I was the coolest guy around.  Er - for my area!'' Jayce amends hastily when it looks like Jaya may take offense to that claim.  ``I mean, you know where I come from.''``Yeah,'' says Jaya, mollified.



They arrive at the train station and the train pulls up.  Jonah is already on board and sees Jaya with Jayce and a stranger.  He hides his surprise by welcoming Jayce and joking with him that it's nice to see him and Jaya getting along.  Rook talks with Jayce, Jaya and the stranger and all of them board the train.


\sceneHeadline{\hl{Jaya, Jonah, Hayley and the Gerhauser Sisters}}\footnote{\textbf{Suko T }Gonna need some help with this one.  Dialog and info missing due to sparse notes and massive amounts of info-dump and being a part of the conversations. :)  Please add in what you remember. \textsubscript{05/07/14 11:15pm}}\footnote{$\rightarrow$\textbf{Suko T }Yay!  Danke danke!!  I love collaborative documentation like this :)  Especially for info-intensive scenes like this when we just *know* it's going to come up later :) \textsubscript{05/11/14 2:28pm}}

Jaya, Jonah and Hayley report to the Ops room.  Jaya enters with a happy air, safe in the knowledge that Morgan was just laid up in Ops and there's no way there she can be laying in wait to debrief/interrigate/threaten/intimidate them.  Morgan is there, bandaged up, hair pulled back severely.  Jaya is floored and rather shook up- she can tell Morgan's on some serious drugs.  Morgan says, ``Agents, Operator, have a seat.  \hl{Do you have any questions?}\footnote{\textbf{q.google }Questions?  Why yes, yes we do.

Jonah is careful here, respectful but persistent.  He's particularly mindful of the pain, both because it can help get past a person's usual guards, but also out of long habit of having to work with people where all one can do is try to minimize it. \textsubscript{05/11/14 11:35am}}''

``You know who the Orc was, didn't you?  Why didn't you tell us?'' asks Jonah.

``It wasn't necessary.''

``\hl{But, she was your sister, correct}\footnote{\textbf{q.google }''It wasn't necessary for \_you\_.  But you are pretending you don't care, and you \_do\_, which affects your judgment on missions we risk our lives on.'' \textsubscript{05/11/14 11:37am}}?''.  He pauses. ``Why was she working for the enemy?''

``It was never clear what \hl{Esther}\footnote{\textbf{Nathaniel Ford }On an approximately 2:1 basis, Gerhauser interchanged ``Esther'' with ``Astarte''. Which is a fairly esoteric point, but for the sake of the audience at home... \textsubscript{05/10/14 1:38am}}\footnote{$\rightarrow$\textbf{q.google }I didn't notice the ratio, but I definitely noticed the switch.  ``Esther'' didn't seem to fit the motif -- but then ``Kate'' isn't just ``Kate'' either. \textsubscript{05/11/14 11:30am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I thought about having Morgan occasionally referred to as 'Morgue' but that seemed a little bleak. \textsubscript{05/12/14 1:04pm}}would do from moment to moment.''

She explains that their sister was the leader of the fight against their enemy.  She chose to sacrifice herself to try and save them all.  The nature of this sacrifice, and its complexities become apparent shortly.  It's implied that her unpredictability was one of the things that made her effective.

Jonah asks about the war.  He's expecting bombs to be falling immediately.  But Morgan explains that it's not actually as immediate as that. 

\hl{``We disabled Transit Minor.  Burroughs is lost.  But we sealed that off so they are having to find other ways in.''}\footnote{\textbf{Nathaniel Ford }This was in response to what Morgen was up to with Patrol group 2. \textsubscript{05/10/14 1:26am}}\footnote{$\rightarrow$\textbf{q.google }Ha.  I didn't put that together.  Literal ``we''. \textsubscript{05/11/14 11:41am}}  Jonah asks if they can't just ``portal'' their way in, but Morgan explains that portals need equipment in place to work, and they can't put it in place without taking the trains in.

``Who, exactly is this 'they'?  Who is our enemy?'' asks Jonah.``Octavius,'' replies Morgan.

``Is Operator Langdon dead?'' 

``No.''

``Can we ... is it possible to rescue him?''.

``Possibly, but it's not easy, and it's not necessarily going to be an option.''

``He fell through a hole.  How are we supposed to find him?''  asks Jaya.

``Victor had some ideas on what to do about that,'' says Jonah. Jaya glares at Jonah, muttering, ``I thought we weren't going to tell her about that.''

``That guy I brought in says he can show us SAC 2,3 and 4,'' says Jaya.

\hl{Morgan seems interested}\footnote{\textbf{q.google }Not as much as one might expect, but there are drugs involved, and this \_is\_ Morgan we are talking about. \textsubscript{05/11/14 11:44am}} and says they will follow up on it.

``Get some rest.  You may not get a chance to do so again for a while.  We have crossed the Rubicon,'' says Morgan.

\hl{``No we didn't,'' says Hayley, confused.}\footnote{\textbf{Adam Kenney }+1 \textsubscript{06/08/14 10:05pm}}

``Is there anything else?'' Morgan asks.

``I'd like to ask the doctor some questions,'' says Jonah, nodding to Dr. Gerhauser who has been sitting in a dark corner this whole time, saying nothing.

Morgan nods pushes herself slowly to her feet.  She walks to the doorway and then pauses.  She looks over the three of us and says, ``Good work.''

\hl{We are all suitably stunned.}\footnote{\textbf{q.google }Rook saying protocol doesn't matter?  Morgan giving praise?  The world \_is\_ ending. \textsubscript{05/11/14 11:45am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{05/11/14 2:31pm}}  And on that bombshell, she leaves.



\hl{Sensing that there is some ``talking'' about to be done, Jaya quickly slips out of the room after Morgan and soon runs into Jayce.}\footnote{\textbf{Suko T }\textless 3 this scene.  Jayce has sure had an interesting day... \textsubscript{05/23/14 1:13am}}They raid Jari's stash of ``the good stuff'' and escape to a secluded broom closet to drink.  Few words are exchanged and after downing enough to build up some liquid courage, Jaya jumps Jayce for a roll in the hay- no doubt an awkward situation with her new arm.  Luckily Jayce is good at handling unexpected situations.  \hl{They are saved from any awkward pillow talk afterwards}\footnote{\textbf{Suko T }A pity, this could have been a comedy goldmine... what *does* Jaya consider pillow talk??? \textsubscript{05/23/14 1:11am}} by the sudden appearance of Jari who hauls off Jaya to the Requisition cage without much comment.



Meanwhile, back in the Ops room, Dr. Gerhauser stands up and moves to sit down at the table.  Jonah asks Dr. Gerhauser, ``Are you alright?''

``Don't worry about my emotional state,'' says Dr. Gerhauser.

``I have to ask because I want to talk about Oliver.  Can we rescue him?'' asks Jonah.

``Do you want my honest opinion?''

``Yes. Your sister died but she took him with her.  Is that what she wanted?''

``My sister wouldn't go down without exacting \textit{exactly} the price she wanted.''

``Was she captured by Octavius?  What happened?''

\hl{``}\footnote{\textbf{Nathaniel Ford }Part of the conversation was skipped here, bridging these topics. \textsubscript{06/08/14 12:22pm}}Octavius is our enemy.  Morgan and myself.  You are Octavius' Harvest.''

``\hl{What does that mean}\footnote{\textbf{q.google }OOG, the question came up of even we even really knew the word ``harvest'', given how food works.  The answer was yes, but that it wasn't entirely clear how it worked, since working on the harvest is one of the jobs people most try and avoid having to do. \textsubscript{05/11/14 11:48am}}?''

Dr. Gerhauser sighs a little and looks tired.  ``Octavius sees you as parts to feed itself.  It needs workers.  We are its enemy because we are making it difficult for them to complete their process.''

``What process?''

\hl{``}\footnote{\textbf{Nathaniel Ford }Again, something was skipped about Octavius's plans and Hekate's only vague notion of what they are. \textsubscript{06/08/14 12:23pm}}Your social structure is already ideally set up for Octavius to takeover.  A few Citizens controlling the masses.  If Octavius controls the Citizens then....''

\hl{``Why haven't they taken over us already?''

``That is its goal.  It hasn't wanted to do it in a rush because it wants to make use of you.  If it would prefer not to damage what it wants to control.''

``They invaded you too didn't they?''

``Yes.  And we fought back.  But it isn't the same.  We are not the same as you.''}\footnote{\textbf{q.google }\_Rough\_ reconstruction.  There is questioning about what they want and why they don't just take it, which leads to discussion about the invasion of the Gerhausers' homeland (though not where that actually was!), and an explanation that Octavius treated them differently.  But the details may be wrong.

I'm also confused by the pronouns.  I don't remember if Dr. G used ``they'', ``it'', or just ``Octavius'' to refer to Octavius. \textsubscript{05/11/14 12:02pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Gerhauser is fairly fluid with her use of pronouns; there is an internal logic, but I probably mess it up from time to time.

Essentially, if you're talking about Octavius-who-invades, it's 'They'. If you're talking about Octavius-the-entity it is 'It', if you're talking about Octavius-the-specific-constituents it is *probably* 'Octavius', though 'Octavian' and 'Octavia', 'The Orc' and possibly others have come up. \textsubscript{05/12/14 12:53pm}}

``How are you different from us?''

``We're different, \hl{but very closely related, species}\footnote{\textbf{q.google }Despite her attempts this goes over Jonah's head.  The notion of different kinds of people being different biologically isn't one he really has experience with.  (I don't think he ever saw the prisoner from SAC-01...) \textsubscript{05/11/14 11:51am}}.  We're smarter and stronger than you.  We heal faster.''  She makes some statements to the effect of it \hl{not being a value judgment}\footnote{\textbf{q.google }As discussed afterwards, from a modern point of view, it most certainly is a value judgment.  Dr. G believes she is \_better\_.  Her being willing to be friendly (or even intimate) with the lesser folk doesn't change her seeing a fundamental distinction.

Whether Dr. G's racial superiority is balanced out by her \_noblesse oblige\_ is a sticky point for the audience to debate.  But from the point of view of someone living in the Directorate, this just comes of as ``Citizens think they are better than everyone else''. \textsubscript{05/11/14 11:55am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Perspicacious analysis. There are more underlying points here, but they are probably post-show discussions and don't actually impact this quite-appropriate understanding. \textsubscript{05/12/14 12:54pm}}, just that it is what it is.

\hl{``Tertius was different,'' says Dr. Gerhauser.  ``Tertius is similar to Octavius but was very vain.  Some parts of it were obsessed with eternal life.  Some of its constituents were very long lived- they go all the way back to Primus}\footnote{\textbf{q.google }At this point it's still not clear what Tertius, Octavius or Primus are, or what ``constitutents'' means in this context.  In particular the numerical order is an OOG convenience: the fact these names are numbers isn't known IG. \textsubscript{05/11/14 12:05pm}}.''  She explains that Tertius behaved differently than Octavius choosing to have only constituents that are healthy and strong to preserve its life.  \hl{She glances meaningfully at Hayley}\footnote{\textbf{q.google }An important point I don't remember is whether the relationship between Tertius and the Directorate, and whether is stated explicitly.  I don't think it was, but Dr. G \_did\_ look at Hayley when discussing it.

We did discuss it later OOG, but I think it was \_just\_ OOG. \textsubscript{05/11/14 12:07pm}}\footnote{$\rightarrow$\textbf{Suko T }It might be but the connection between Hayley and Tertius was drawn. I can't remember how Tertius came up in the first place though.  In this dialog it is just dropped in with no lead. \textsubscript{05/11/14 2:35pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I forget exactly how it came up as well, but I think it had to do with a reference to Tertius having had more control of the Directorate in the past, but Octavius moved in on the situation. And then the PCs asking about how they differed. \textsubscript{05/12/14 1:33pm}}\footnote{$\rightarrow$\textbf{Suko T }That sounds very likely.  I had forgotten that it was mentioned that Tertius had been in the Directorate for a while. \textsubscript{05/13/14 2:59pm}}.

``I'm confused.  What is Octavius?  Is it a person?  You speak of it as if it's not.  Is it an organism?''

``Octavius is an amalgamation of people.  There is no 'leader' as you understand it.  Their minds are all shared throughout their bodies.''

``It appeared that the Orc was an Operator over many Agents.''

``It's not quite like that.  There is no explicit Operator or Agent.  The various personalities are mixed.  Some personalities are stronger than others.''

``So a little like cells in a brain making a decision for a body?''

``It would be unwise to make too many analogies to biology as you understand it''.

``So what do they want from us?''

``They want to take you over to use you as stock.  \hl{To take the bodies of the ones they want to keep to add to themselves, and to use the rest as hard labor.}\footnote{\textbf{q.google }This \_should\_ be horrifying.  It is horrifying.  But to Jonah's ears it doesn't sound very different from how life already is.  He hasn't quite made the leap to the idea of having your personality submerged in other people's.  Even his experience as an Operator is only able to get him to not out of hand dismissing the idea as the ramblings of lunatics. \textsubscript{05/11/14 12:17pm}}''

``How is that different from how it is now?  That's what Citizens already do.''  His tone is a little acerbic, and the Doctor can hear it.

``There are similarities but it's not the same.  We don't have time to debate all the finer points of political anthropology but the Citizens are simply a group of people who arrange the rules to their advantage. \hl{{[}...{]}}\footnote{\textbf{q.google }I really don't remember how she made the distinction, and I don't want to guess because I'm finding that I'm putting my own spin on it. \textsubscript{05/11/14 12:21pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm pretty sure she referenced that Octavius does this... to a much larger degree. The acerbic tone came from ``How can you not see it's bigger than your little province? And more than a political-economic structure?'' \textsubscript{05/12/14 1:36pm}}.''

``It was a mistake to absorb Esther.''  She explains that their sister's sacrifice was to allow herself to become part of Octavius in an attempt to work around it from within.

``Because she has a strong personality?''

``Yes.''

``\hl{So even though she's dead}\footnote{\textbf{q.google }This was stated as a question of its own.  It's not clear if she's actually dead or not.  Both her own words, and Dr. G's reaction to those words seem to imply otherwise.  (This is a bit of a stretch for the questioner here, but it's too interesting OOG not to ask IG.) \textsubscript{05/11/14 12:15pm}}, she's still part of it?  What does or did Esther want?''

``We were fighting the war against Octavius.  Esther was strategic enough to trick Octavius into integrating her.  Whether that will \hl{kill}\footnote{\textbf{Nathaniel Ford }The word 'destabilize' came up, too. \textsubscript{06/08/14 12:25pm}} Octavius is unknown.''

``Did we kill her?  The body we saw looked like it could be her.''

``I looked at the constituent closely for a long time, she resembled you and Agent Morgan very much,'' chimes in Hayley.

``She's been \hl{dead}\footnote{\textbf{Nathaniel Ford }The implication here was clearly, ``She's been dead \_to us\_.'' \textsubscript{05/10/14 1:31am}}a long time.  A long time ago, she sacrificed herself to save Morgan and me.''

``So is she not dead?'' asks Jonah.

``She is dead.  Octavius would not have reacted the way it did if she didn't die. Though the impression of her personality will likely remain.  Her strategic mind and \hl{cunning}\footnote{\textbf{Nathaniel Ford }It was only mentioned once, but the word ``sadism'' was connect to her as well. \textsubscript{05/10/14 1:41am}}.''

``May I ask why you are here? Why are you fighting?'' asks Jonah.

``Our people are dead.  \hl{Morgan wants to destroy Octavius. And I want to defeat Octavius}\footnote{\textbf{q.google }Somewhere in all this the surprising information is gained that the sister who wants to save the Orc is Morgan \_not\_ Dr. G.  The latter believes the Orc's identity or self is gone and irrecoverable. \textsubscript{05/11/14 12:24pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Um. There may have been a miscommunication around this, but that is probably natural given the different perspectives different parties have on what it means to 'save' someone, and the hard facts of events that had occurred up until this point, and how that closes certain options. \textsubscript{05/12/14 1:00pm}}\footnote{$\rightarrow$\textbf{Suko T }Interesting.  I actually didn't think the roles necessarily swapped (i.e. that Morgan wanted to save the Orc and that Dr. G didn't) I just thought, as Nate mentioned, that how to ``save the Orc'' had been redefined to a level that was probably outside of our character's understanding.  Well maybe Hayley would get it, but you know, she's got a pretty messed up idea of what basic terms like ``living'' and ``dying'' mean. :) \textsubscript{05/13/14 3:30pm}}.''

{[}...{]}

Jonah's parting words are to the effect of ``Now that we understand what is going on things are different.  We respect your skill and your experience in fighting this war but we are no longer here because we are being told to. We know they are coming for us, so we are fighting for ourselves not just for orders.''

``I will have to talk to Morgan, It may be time to \hl{renegotiate our agreement}\footnote{\textbf{q.google }Strongly implying ``the agreement between Morgan and Dr.G'', but it could also mean ``the agreement between the sisters and the patrol.'' \textsubscript{05/11/14 12:26pm}},'' says Dr. Gerhauser.

{[}...{]}


\sceneHeadline{Jari and our new toys}

Jari gathers Jonah, Jaya and Hayley and shows them the new stuff they have in the Requisition cage.  Jari looks pretty rough- very tired and not in the best of shape.


\sceneHeadline{Jaya and Lackovich}

Jari tells Jaya she's been requested to go to Medbay.  Lackovich is there, looking pretty messed up and most of her body is in traction.

Lackovich asks groggily, ``Did Langdon make it?''

``No, he fell through a hole.''

``What about Jonah?''

``He's fine.  So's Hayley.''

``Did we kill him?'' asks Lackovich.

``The Orc?  Actually, that was a her.  No big surprise actually.  Big badass... of course she was a her,'' says Jaya with a touch of admiration.  ``She attacked Langdon and pushed him over the railing.''

Lackovich is quiet for a moment and then looks at Jaya seriously, almost earnestly, ``Jaya, I wanted to say - ''

Jaya interrupts her and says, \hl{``You don't look so good- let me turn those drugs up.''}\footnote{\textbf{Nathaniel Ford }There was fumbling here over the drug button. \textsubscript{05/10/14 1:42am}}

``-Thank you,'' finishes Lackovich.

``No.''

``I mean it.''

``No.  You're on drugs!'' says Jaya loudly.

``Sorry for blaming you -'' says Lackovich with the tone of \hl{someone making a confession.}\footnote{\textbf{Nathaniel Ford }But also the tone of someone fairly emotional and on drugs. \textsubscript{05/10/14 1:34am}}

``Shut up! You're on drugs!'' says Jaya somewhat desperately.

``Yeah.  Ok.  Fuck you then.'' says Lackovich.

``Fuck you too,'' says Jaya, relieved.  And she leaves quickly.


\sceneHeadline{\hl{Hayley and Carruthers}}\footnote{\textbf{Rebecca S. }Saddest \& most touching in scene in the game to date.  The feels, they hurt me even now. \textsubscript{05/10/14 9:49am}}\footnote{$\rightarrow$\textbf{q.google }Yeah.  And this in a session with a larger than usual share of touching scenes.  This one was tragic. \textsubscript{05/11/14 12:29pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{05/11/14 2:43pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 I'm glad it came off. \textsubscript{05/12/14 1:00pm}}

Hayley is walking back to her Bunk and runs into Carruthers in the hallway outside of the Bunks.  Carruthers is leaning against the wall, bouncing a ball against the floor, bouncing it off the far wall and catching it.  Hayley apologizes for bumping into her and tries to back away.  Carruthers seems to be barely holding it together and does not have her usual shy or stammering demeanor.  Hayley is about to walk past her when Carruthers asks suddenly, ``Your Operator - he's dead isn't he?  How did it feel when he died?''

``Oh, he's not dead!  He's just somewhere else,'' says Hayley with a smile, not noticing how Carruther's face shuts down at this news.  ``He fell through a hole.  I hope we'll find him soon.  Why do you ask?''

Carruthers goes back to bouncing the ball against the wall and doesn't answer.  Hayley senses that she must have given the wrong answer somehow and attempts to make polite small talk but quickly gives up.  She walks past Carruthers to the bunk, puzzled but chalks it up yet another failed conversation attempt.


\sceneHeadline{Jonah, Agent Morgan and the Self-Destruct Key}

Jonah is summoned to Morgan's office.  She hands him a key and then tells him to sit at her desk and tells him to open a particular drawer on the left side.  A panel appears with keyhole and a button.  She tells him not to use the key but to remember where this panel is.

Morgan tells Jonah, ``Keep the key with you at all times.  At some point, it may be strategically necessary to destroy SAC-09.  Once you press the button, you will have approximately 5 minutes to get on the train and get out.''

``That's not much time.''

``You can probably get to Platform 1 okay, but probably not Platform 2.  This office is remote.  If you think you can't get to the train, try a \hl{window}\footnote{\textbf{Nathaniel Ford }Note that no one in SAC-09 has actually seen a window, besides in her office, and those have always been closed. \textsubscript{05/24/14 10:50pm}}.'' Morgan gestures to one of the closed recesses in the office. 

``Why are you giving me this?'' asks Jonah.

``I was going to give it to Operator Langdon, but as he is unavailable, I'm giving it to you.''





\textbf{{[}4 Backlash Tokens left{]}}






\jumpHeadline{Quotes }

\quotedDialog{
Jonah: Have you ever operated on a friend?

Jaya: We're friends??\\[4mm]
}

\quotedDialog{
Rook: Take a deep breath and tell me you love me

Jaya: What the fuck?!

Rook: Just repeat the words.

Jaya: The FUCK you say!!\\[4mm]
}


Rook: The ink road is fine.  I'm quite jealous.


\quotedDialog{
Swan: What can I do for you?

Hayley: I'm in Lab 4.  I'm not dead, am I?

Swan (alarmed): Stay there!  I'll be right over.\\[4mm]
}


Jaya: It's a \textit{compromise}.  It's how we do things in the TA.  \hl{It's in the manual.}\footnote{\textbf{Suko T }Quote made particularly funny by who is saying it. :) \textsubscript{05/07/14 11:14pm}}


\quotedDialog{
Morgan: We have crossed the Rubicon

Hayley: No we didn't.\\[4mm]
}

\quotedDialog{
Lackovich: Sorry for blaming you-

Jaya: Shut up! You're on drugs!
}



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 11:07am
\end{flushright}

