\setcounter{chapter}{ 24 }
\chapter{\textbf{The Analysis of Oliver Langdon} }



\subChapterTitle{}

\deets{Rebecca \& Suko}{May 27th, 2014}

\hl{Disclaimer}\footnote{\textbf{Suko T }Aww I kinda liked ``Oliver is flucked''... I always misread it as ``flocked'' and pictured Oliver looking all stoic and hero-tragic staring out into the distance....while covered in fake xmas tree 'snow'. \textsubscript{05/28/14 1:21pm}}: I type phonetically when I type fast so forgive the typos/nonsense.  I also was trying to focus on the ``Jaya'' brain so some of the phrasing or word choice for non-dialog text is less than idea. \footnote{\textbf{Suko T }Also, super-big thank you for taking notes!  Really let me stay more in Hayley's head, which was great for this session.  Much appreciated! \textsubscript{05/28/14 2:07am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 I really appreciate this, actually. It's good to have these when you're in your room alone, crying, later. \textsubscript{05/28/14 12:04pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Yes, I'm just getting some decompression time now and it's amazing to have these notes to help me re-experience the session. Agh! Emotions! \textsubscript{06/08/14 11:55am}}



Missing big chunks, am glad Suko took notes as well (as usual).  Formatted content haphazardly.



A lot of intro text to scenes was scripted, perhaps Nate would be kind enough to grace us with some copy \& paste powers. 

 

My Adam has an honorary good quote for the night with, ``Wait, so \underline{  {\color[RGB]{17,85,204}they killed Kenney}  }\hl{?}\footnote{\textbf{Suko T }Ha! :) \textsubscript{05/28/14 12:20am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }OMG LULZ. :D \textsubscript{05/28/14 12:04pm}}``  

\jumpHeadline{}

\jumpHeadline{At the start}

We're in the Ops room, Dr. Gerhauser, Morgan, Rook, Swan and Larissa are there.  Carruthers is at the door, standing guard.  We're in the tanks, carts with our shit on are right next to our tanks, ready to grab

``Flooding all concourses, \hl{Alpha Zed to November Victor}\footnote{\textbf{Suko T }OMG I just got this.  Wow and I'd even guessed (happily correctly!) about SAC-09's location but missed this big clue.  

LOL, such a nice touch :) \textsubscript{07/10/15 12:30am}}.''

After about a minute Rook says Sac 9 is now isolated, setting time to track re-engagement to 10 minutes from go-signal. 

Because of the interference they're not really sure if Oliver will realize what's really happening. 

``We'll be monitoring the whole process.''

Jonah asks what happens if we fail.  Rook explains that if we fail, nothing will happen.  Partial failure is going to be confusing images, much like a bad drug trip.

During the operation \hl{Hayley}\footnote{\textbf{Rebecca S. }I'm sorry I didn't know how to spell your character's name :)  Next time! \textsubscript{05/28/14 8:53am}}\footnote{$\rightarrow$\textbf{Suko T }No worries, easy fix and goodness knows we have plenty of names with unusual spellings :) \textsubscript{05/28/14 1:22pm}} and Jaya should be able to maintain contact with Jonah- Hayley and Jaya will be entirely under while Jonah was only half under and able to communicate with the rest of the people in the Ops room.

In order to get in sync we should think about the same thing. Everyone agrees to use ``Oliver's gun'' as the syncing mental image (it'll help if Oliver is thinking the same thing)



Only Hayley will see the 1st scene

Hayley and Jaya can see the 2nd scene

Everyone can see the 3rd scene

After that everyone can see but only those in the scene can interact



We go under and everyone mentally ``sees'' themselves in a train car, blurred images speeding past the windows.



\jumpHeadline{ Scene 1 : The Burning}

Oliver is in a wheelchair.  When she speaks he fails to recognize Octavia's voice...  Pushing down a corridor.  They enter a room with high ceilings.  Through the window is a view of sea and the red setting sun, a sight that Oliver has not seen before.



Kneeling in front of a brazier is a tall beautiful man.  ``\hl{Astarte}\footnote{\textbf{Adam Kenney }So out of curiosity, do we think this is the name of Sister \#3? \textsubscript{06/08/14 11:58am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }The other PCs were privy to certain information, including her name, before you were. Which is why they freaked when you called your sister Ester. I think Suko gave you access to the session notes - let me know if not! \textsubscript{06/08/14 12:15pm}} taught us a great deal about memory, about it's beauty and it's terror. I have brought you here to witness an act of memory, an act of willpower.''  The man pours hot oil shit on his face and it fucking melts.  Creepy. Still alive but really really gross.  Familiar raspy voice asks Oliver, ``Are you sure?''

 {\LARGE \textit{ {\color[RGB]{102,102,102}this was mostly scripted} } } 

\jumpHeadline{Scene 2 : The Forum}

Octavia pushes him to another room.  Romanesque, see outside to the night.  Tall beautiful other peoples (30 of them). are seated in the forum area.  At the top colonnade area, 6 people are watching (they look different, more diverse racially, with varying skintones.  One even has a greenish tint to their face.  They are shorter and broader but still very good looking with symmetrical features.)

Man with the burned face takes a seat in the front row.

Octavia wheels Oliver to the center of the forum and puts a small rod on his lap, and then wanders over to sit down somewhere.

When they talk, they do a creepy chain talking thing.  Creepy hive behavior with speech and gaze. 

``You have hurt us very badly. We wonder that we should not hurt you equally so. But then, how could you, the small thing that you are, know such hurt? While inflicting physical pain upon you may be delightful indeed, we still have use for you.

``And yet, fool me once, shame on you, Astarte. Shame on you indeed. We have learned our lesson, Oliver Langdon. We have learned it very well. And so we shall analyze you completely. In that state of nothingness, you will have the means to decide to join us,'' Octavia will indicate the rod, ``or pass, forgotten, in a void larger than any single \hl{human}\footnote{\textbf{Nathaniel Ford }I probably left out the dripping disdain that should have accompanied this word. \textsubscript{06/01/14 11:22am}}mind has been able to encompass.''

``Since we shall take away all that is you, it is customary to give you first a gift, a royal gift. And so we have healed your leg, something our wretched sisters never would have done, however much you worshipped them. Astarte taught us much about memory, though, and so to remind you, the pain will remain, forever, until you die. Stand now, and'' the rest is said by all, save the six to the side, ``Accept our judgement.''

Oliver stands up and realizes his leg is whole again. ``What are you going to do to me exactly?''

``Best not to tell you, just show you,'' Octavia says


\jumpHeadline{Scene 3: Falling}

The ground opens up under him and he falls.  He presses the button on the rod but nothing happens.  He falls down a shaft.  There's a white light at the bottom... big bubble forms around him as he falls.  There is darkness and a wrenching \hl{nausea}\footnote{\textbf{Nathaniel Ford }This is exactly like, but about an order of magnitude worse, than the nausea sometimes experienced in the subway tunnels. \textsubscript{06/01/14 11:23am}}.


\jumpHeadline{Memory : DX Platform}

Oliver \& Jonah -- the doors of the train open up and shit gets real.  

There's a girl going amongst the corpses, they disappear after she visits them.... 

After the first wave of machine gun fire, Oliver darts forward to join Jonah behind a column, laying down some cover fire. 

``Lets get some covering fire in here,'' a frantic Oliver shouts.

Jonah is rather calm. ``Lets wait for some covering fire.''

``They got us trapped like rats in a hole!''

``The people up ahead are more trapped than us-- hey Oliver, do you know where you are?''

``What do you mean?''

``Where are you?''

``DX Station of course''

``I mean where you are when you're not here. -- where were you 10 minutes ago?''

``I remember taking the train from... from.. the Bucket. ``

``All right, lead the way.... `` says Jonah resignedly as they re-engage in the battle.

``So where do you think you are now?''

``I was at DX station, I joined the front, we're heading towards that sniper tower... ``

Oliver's memories clear up...

``Yeah... I don't really remember you from the war,'' says Oliver.

``I don't think you met me. ``

``Do you think I'll still get shot at?''

``Well it depends... are we still here?''

Oliver kicks at the dust...  (the train has left!  On the opposite platform, there's a dude in a heavily armored suit..\hl{looks like dudes they've seen before from Nickelpan}\footnote{\textbf{Nathaniel Ford }Similar to, though not exactly like the soldiers (which Hayley, at least, may now attach the Octavius-used term 'Legionnaires' to) seen at Nickelpan. As though they have similar level of equipment but different uniforms. Not unlike the difference between modern British and US soldiers, say. \textsubscript{06/01/14 11:25am}}) 

Oliver jumps behind a column and shouts for Jonah to take cover.  He looks around the column.

``Do you remember being captured?''

``Ah... yeah, right, they said something about analyzing me.  Taking me apart, I don't really remember.''

Explosions are approaching. ``Shit! Get down!'' says Oliver

Jonah starts to lecturing about the nature of the villains.  He asks if they've talked to him.

The little girl turns to Oliver and says ``Of course we talk to you''.  Jonah is ejected via closing train doors. 



\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ }  (Jonah) Apparently they are going to analyze him

\ding{228} {\color[RGB]{68,68,68}▶ } (people in Ops, usually Rook) You need to make him try harder.  

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } What do I need to try?

\ding{228} {\color[RGB]{68,68,68}▶ } We're not really sure. Make him open up. 



\jumpHeadline{ Memory : Guns Out} 



Train doors open.  Hayley is kneeling next to Oliver as he shows her how to assemble and disassemble a rifle.  There's a girl near by picking pieces up off the railing and tossing them over the side. 



``I miss you, are you coming back?'' Hayley opens with a smile.

``I miss you too''

``You look better''

``Well... It's not the easiest thing putting these guns together''

``It's not...  there's a lot of little parts... but I'm good at doing things over and over again'' Oh Hayley.

``I feel you can only do things so many times.''

``True, because eventually you die.''

``It's a very precision instrument- see how these parts fit together like this?  If you do it wrong, it will jam.''

``These things seem to jam a lot,'' says Hayley

``Yeah, there's been a lot of misfires lately''

``Are you going to come back now?  I miss this, I miss working with you.''

``Well I'm here now.''

``You are?''

REBECCAxxBEGINxxHIGHLIGHTxx``Lets talk more about disassembly,'' he walks through the disassembly of it. They keep removing pieces till there's nothing left of the gun.  ``You see how each part can be removed.''

``Yeah, they do that to people too''. xxENDxxHIGHLIGHT\footnote{\textbf{Nathaniel Ford }Prescient \textsubscript{09/22/14 10:19pm}}\footnote{$\rightarrow$\textbf{Suko T }The layers of metaphor and analogy in this scene are (and were) so cool. \textsubscript{09/23/14 4:04pm}}

``Yeah...''

``You can't do that to people, they just die''

``Yeah, well you can't reassemble a gun if you don't have pieces... ``



\textgreater \textgreater \textgreater \textgreater   OOG Kenney is handed 2 green cards, chooses one and spends a token

\ding{227} \ding{227}  (what Hayley sees) visceral flash of a man going down to one knee, wincing in pain with blood coming out of his nose


Little girl turns around with a pipe and advances on Hayley.  Hayley attempts to step in front of Oliver.  \hl{The train doors close}\footnote{\textbf{Nathaniel Ford }Visually, this is the camera moving in on the character's face, until the background is unclear, tunnel-wind blowing their hair, and then doors shutting in front of them, even though the train never really 'arrives'. \textsubscript{05/07/15 5:33pm}}



{[}Hayley gets a Yellow card: The Cold Water{]}



\jumpHeadline{ Memory : The Handshake} 



Jaya and Oliver are in the bunk.  Hayley and Jonah have just left.  The little girl is wandering around the bunk, touching things.

\memoryScene{
\textit{OLIVER: ``You don't forget the person who shoots you.''}

\textit{JAYA: ``Really?''}

\textit{OLIVER: ``What if I see someone that I need to deal with while we're in Nicklepan?''}

\textit{JAYA: (pause) ``You can't go hunting him down, but if you find that person, we'll help you deal with him.  We're a team and team members back each other up. And avenge each other!''}

\textit{OLIVER: ``Really?  Even if we have to resort to unconventional methods?''}

\textit{JAYA: (shrugs)  ``Whatever.  Do we have an agreement?''  (Both shake)}

}

Jaya then holds up a  finger in that classic ``One moment'' gesture and turns to suddenly punches the little girl in the face.  Oliver doesn't really notice.  She follows up with some kicks to the gut and turns to him to ask,  ``Who IS this?''

``Oh, that's my sister.''

Jonah tells Jaya to make Oliver mad.

Jaya punches Oliver, with the offhand disclaimer that it was \hl{orders}\footnote{\textbf{Nathaniel Ford }Didn't she say Jonah told her? Because it seems to me that Jaya doesn't take orders from Jonah per se... ;-) \textsubscript{06/01/14 11:28am}}.  ``What was that for?'' asks Oliver.

Jaya picks up the little girl by the scruff of her neck and shoves her at Oliver.  ``Why is this in your head?''

Oliver seems to remember more and asks Jaya, ``What do I need to do?''

Jonah relays Rook's caution, ``He's analyzing too much.''

``Well you can start by completing the mission.''``I thought I did, wasn't that the mission objective?  It was a success.''``Fuck no it wasn't!  I'm down a team member!  Meaning you!''



\ding{227}\ding{227}\hl{``Legionnaires, start bringing me hearts`` -- the thought flashes through Hayley and Oliver's minds.  Flashes of visions as well... People standing on the train platform, tall dudes from before, with big knives they start fucking up the weakling peoples (in Franchise clothing)... Mostly gutted and stabbed ... not dying outright, long painful bleeding out process.  

Hayley has an emotional reaction to the scene.  First indignation- ``You don't remove hearts like that!'' and then sadness at the waste.}\footnote{\textbf{Nathaniel Ford }Hayley may, with her nose for breadcrumbs, eventually pick up that they were very deliberate in how they mortally wounded the victims. Each blow was as efficient as possible while ensuring death and maximizing time until death. Most people bled out, conscious. The fighters were hamstrung or otherwise disabled before being mortally wounded. \textsubscript{06/01/14 11:31am}}

Oliver feels sharp rage.

Hayley wonders if that's what happened to the bodies at Nicklepan?  



\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } Was that getting emotional?

\ding{228} {\color[RGB]{68,68,68}▶} That was better.  I need to talk to Trenton.... Trenton and Victor agree, we need him more emotional but more analytical of the emotions... wait... one moment.   ..... (stuttered start) .... we need more readings. 

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } Figure out what you want and get back to me



\textgreater \textgreater \textgreater \textgreater  We on the train see things flashing by at a high rate. Fragments of memories ``first kiss'', ``when I wet my bed'', ``When I decided not to go to the academy'', etc



\jumpHeadline{Memory : Dinner} 

Oliver is at dinner with Mother, Father, Roger, plus SCARY SMALL GIRL.  She puts things in her mouth.  Food, napkins, silverware. They all disappear without her chewing.



Roger opens with, ``Hey chap, did I see you at Cardoza the other day when that scandal went down''

Snarky comment by Father leads him to be dismissed by Mother to fetch some wine. 

``I'm sorry dear''

``No, it's fine... Thank you''

``Are you alright, you see a bit distracted,'' Mother probes

``No, it's nice to be back home''

Father comes back ``Is it?'' Snarky mc snark.  Drops off a bottle of wine

``He seems alright to me dear.''

``You know I always try to do my best. ``

``Oliver, will you pass the klipchops please.  ``

He stands up and looks around, somewhat aimless... ``Father, I have to know, would you miss me if I was gone?''

The little girl shakes her head and picks up a salt shaker and puts it in her mouth. Oliver ignores her.

``Father... `` Oliver shakes him slightly, Father is staring off into space.  

``Of course I would, you fool!'' Father says suddenly (after Jonah spends a token to jump in and control the scene) 

``Well...it's just you wouldn't know it given how things are.''

The little girl looks at Oliver's dad, eyes narrowing in suspicion and approaches all creepy like ... 

Jaya jumps into the scene into the form of Roger and grabs a steak knife from the table and stabs the little girl in the back.  She falls to the ground and ``Father'' and Oliver continue to talk, barely noticing.

Oliver looks at Roger, ``Who are you, and why are you in my father's house?''



\ding{228} {\color[RGB]{68,68,68}▶ } We got a lock!  You guys are doing really well



\ding{227}\ding{227}Hayley feels a sense of frustration coming from outside of herself.  Many orders are being given, though she can't really understand what they are saying.   Then she is seeing a room through Octavia's eyes.  There are 2 Legionnaires holding holding Gillian down on her knees, there's a man (Lord Stanislav) objecting loudly.  When Octavia enters he comes at her, yet she ignores him.  When he gets close enough she stabs him in the eye with a dagger.   Hayley is freaking out and the boys get a sense of this.  

Octavia takes the knife and cuts Gillian's clothes off.  (( Hayley sends the feeling of OUTRAGE )) ``Now, how did this go?''  Octavia muses outside, and starts cutting into Gillian's flesh.  Hayley knows exactly what patterns Octavia is carving and feels the marks on her own skin.



\jumpHeadline{ Memory: Arresting Victor} 

Now we're all in the ``Arresting Victor'' scene!!



We're all REALLY FUCKING CONFUSED... 



Hayley's in hysterics, saying that she has to go help Ms. Vorrutyer.  She's hurt, she needs Hayley to help her.  Oliver gets confused too and agrees, though he doesn't seem to know who Hayley is talking about.



\ding{228} {\color[RGB]{68,68,68}▶ } Your readings are WAY off, you're losing him.  What is going on?



Jonah tells Jaya that they have to stop Hayley.  Jaya pulls Hayley aside and tells her to pull her shit together and start helping Oliver.  Hayley eventually calms down.  Jonah works his \hl{Social Chameleon}\footnote{\textbf{Rebecca S. }So much Social Chameleon, used so well everywhere.  Jonah should manipulate people's memories more often, he's really good at it! \textsubscript{05/28/14 11:25pm}} to calm down Oliver.  Oliver calls the little girl, ``My sister Esther'' and there's a brief moment of freaking out by those in the tanks. 



Jaya and the little girl make angry eyes at each other.... and the girl starts advancing on the group.  Jaya positions herself between Oliver and the little girl but Hayley walks right past Jaya and backhands the little girl across the face.  When the girl falls to the ground Hayley sits on her.  She clamps a hand over the little girl's face and hisses at her, ``You leave him alone.''  Hayley tightens her grip over the girl's nose and mouth and watches as the girls suffocates to death, attempting to fight Hayley at first, then flailing around, and then going limp.  Hayley then stands up.  The little girl vanishes. Hayley turns around, smiling, looking much more cheerful and the rage that Jonah had felt earlier is gone.



While \hl{Hayley's all homicidal}\footnote{\textbf{Nathaniel Ford }This is what we call 'character development'. \textsubscript{05/28/14 12:09pm}}\footnote{$\rightarrow$\textbf{Suko T }Somehow I don't think Padme's going to let Hayley babysit her kids anymore... \textsubscript{05/28/14 1:26pm}}, Jonah and Jaya attempt to get Oliver to remember some childhood memories and Oliver gets distressed that he can't.  Hayley can feel that Oliver is distressed and tries to get Jonah and Jaya to stop.



Oliver ramblingly suggests we go to the basement because...wasn't Victor hoarding water rations...?  Jonah humors him till Jaya tries to pressure them towards a bar. There's much conflicted feelings on whether humoring Oliver or getting him to follow the way the event went down would be the best course of action.  Jaya eventually heads into the bar and pops out of the scene. 



``What is going on?''

Jonah and Hayley do their best to convince Oliver that everything is normal.

``And Jaya will be drunk soon, so that will be normal.''

``So then you'll be able to beat her at cards.''

Oliver laughs.



\ding{228} {\color[RGB]{68,68,68}▶}  The analogy Trenton is using is... These aren't his words... It's like his sphincter was clenched and he let go.  I apologize he couldn't come up with a less colorful analogy.  

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } He's not dying, is he?

\ding{228} {\color[RGB]{68,68,68}▶ } We have no way to monitor his lifesigns. 



\ding{227}\ding{227} Hayley gets the sense there is some frustration.  There is a debate that goes over very very fast if they should kill Gillian.  Then they decide to just torture her... and then they'll reconstitute Signe. 



\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶  } Jonah, what does reconstitute mean'' wonders Hayley.  ``Isn't that for soup?''

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } Jonah replies, ``What is the context?''

\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶ } At hearing his voice in her head, Hayley just says a delighted, ``Hi!'' and fails to answer his question.





\jumpHeadline{ Memory : First Aid} 

Jonah is in the scene.  Jonah has been shot, he's in a hallway.  Oliver is first-aiding him. Jonah is compelled to say ``Oh Fuck'' on all levels.  Jonah is on the ground... there's a small girl wandering the hallways, where she trails her fingers along the hallway, the wallpaper peels back. 

``Looks like you're bleeding, a chest wound on your shoulder.  Talk me through it,'' Oliver says

``Pressure''

``I'll put tape on it... I always wish they'd put more tape in these kits... always so many bandages, bandages, bandages...''

``It's funny that I'm finally getting shot instead of you...I'm really sorry about that, your leg I mean''

``It's no fault of yours, it was stupid rushing out like that... ``

``But we couldn't help you.''

``Where were we exactly?''

``Transit minor, the last battle...  ``

``Oh yeah... well anyway, it was a long time ago ``

``Look, um, it is a change... shitty as this whole situation is,'' Oliver pulls the tape tighter, ``it's nice to do something nice for you for a change... feels like you pulled me out of a lot of scrapes''

``I tried... seems like we get into a lot of them without having any control over then... all four of us running in different directions''

``When did we ever have any control over anything?''

``Don't you have some control over things being a citizen?''

Oliver bitterly laughs. 

``You have to understand, when we were young, we always looked up to citizens''

``Yeah, you have all the water you can drink, a nice house, you can find a way to step on some people...''---- he makes some creepy foot analogy--- ``...Anyway, we're all just people''

``Well it wasn't clear from the trenches all the time.''

``I'm sorry, we saw you but there was no dashing back.''

---- voice fades out----

Oliver finds that he was applying first aid to the little girl.

\ding{227}\ding{227} \hl{There is a disturbance in the Force}\footnote{\textbf{Nathaniel Ford }I probably should have elaborated at the time, but if you think of the connection between the four of you being a boat, it's like someone really heavy jumped into the boat and then jumped out.

Or, more precisely, if you're an upside down four-sided die, with Oliver as the downward point upon which the die is being spun, the die is suddenly spun the other direction, and the reversed again. \textsubscript{06/01/14 11:34am}}.

{[}{[}{[} Nate spent one of his GM tokens and got a yellow sheet of paper --- WTF IS GOING ON?!? {]}{]}



\ding{228} {\color[RGB]{68,68,68}▶}  We may have a problem... it seems as though to quote Victor they are ``Riding his wavelength.''

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶} They're following him?

\ding{228} {\color[RGB]{68,68,68}▶} No, they're piggybacking him.  We can disambiguate... ??? The word he used is they ``Juked Us''

\ding{228} {\color[RGB]{68,68,68}▶}  if you see the girl, take her down at all costs. 



\jumpHeadline{Memory : Scars} 

Hayley and Oliver are hanging out at the cistern.  Hayley undresses.  Oliver, for the record, looks away as she undresses.  There's something moving under the water, the water is draining from the cistern.

``Jump in!''

Hayley goes in and immediately starts to drown.  Oliver jumps in and pulls Hayley to the side. As he does, he can feel her scars beneath his hands.

``Are you okay?''

Hayley calms down a bit, ``Yes, thank you.  Is that swimming?  I don't like it.''

``I took you here that time.''

``Oh... you did... that's right.''  She's calming down a bit.  ``You always rescue me.''

``Kate got so pissed.''

``That I didn't die?''

``No! No... just... she... ``

``She's very sad...''

``She didn't want me to do that.  Guess I had to leave my mark.  Make a strong showing?''

``Strong showing of what?''

``You know... the Directorate against the big bad Anglians... maybe a few other things...''

``Ah, proving your manliness?'' says Hayley.

``How many times did we come here anyway?''

``Five,'' she answers promptly.

``You never did tell me what happened to you''

``Well I guess I can now... I guess she's not my contract holder... ``
\textbf{\hl{ADAM's FUCKING PHONE RINGS}}\footnote{\textbf{Nathaniel Ford }The real reason Oliver perished. The writers hate interruptions! ;-) \textsubscript{06/01/14 11:35am}}

``... yes, I guess I don't think that's a problem.  I trust you... when my contract was purchased from Redemarrer, I was in a brothel, I didn't do very well... Guys don't like being told that they're stupid or fat or old.''

``Yeah''

``Yeah, women don't like that very much either.... So they just gave me to patrons who didn't care what I said much.  Mr. Vorrutyer purchased my contract.  When I was leased by the brothel you couldn't do anything permanent.  But once he had my contract he could do whatever he wanted to me.  Which was this.''

``How did you get out of it and into the TA?''

``He died and my contract passed to his daughter, Ms. Vorrutyer.  Somehow the TA got my contract.  I think it was because of medical reasons?''



\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶}  Hayley, wherever you are, keep your eye out for the girl.  PROJECTS JONAH



The water is now at waist level and dropping rapidly.  Hayley blinks and looks around... 

``You know, in a way... despite all the fucked up things that happened I'm kinda' happy you're in our squad.''

``I'm very happy too,'' she smiles at Oliver.  ``I think I understand what family means.''

``I don't think you do.''

THE DOORS SHUT



{[}Hayley gets Yellow card- ``The Things We Carry, The Pain We Walk With''{]}



\ding{228} {\color[RGB]{68,68,68}▶}  This is going very well, we just got a second lock

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶}  That's good, this is kind of hard to watch

\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶ (Hayley) } \hl{I didn't see the girl, perhaps because I killed her last time}\footnote{\textbf{Nathaniel Ford }For posterity: the girl was in the scene. \textsubscript{09/22/14 10:40pm}}\footnote{$\rightarrow$\textbf{Suko T }At the time, I assumed she was underwater consuming the water in the Cistern.  When Hayley blinked and looked around, that was her realizing that the little girl may be in the water with them. \textsubscript{09/23/14 4:08pm}}

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶}  She'll be back

\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶}  They seem to be getting very frustrated, I can feel it. And they haven't said anything recently...

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶} What have they said?

\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶} They've been arguing about whether or not to kill Ms Vorrutyer but they decided not. They're just going to torture her.... Then they wanted to get hearts... Told the Legionnaires to get lots of hearts, but they did it very poorly.

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶} Tell me next time they say anything

\ding{228}\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶▶} Jaya says it's not true, but I think I'm seeing through Octavia's eyes. 

so many wooooooords





\jumpHeadline{ Scene : Grenade!!} 

Jaya and Oliver and are in horrendous slow-mo to forever, talking.   The lights in the corridor are slowly being extinguished.



Jaya stands up from beating up naked chick and throws herself toward the grenade, as does Oliver.  ``You don't need to do this!'' says Jaya.

``Yes I do, it was an order!  But I can't remember who ordered it!  Why the fuck am I throwing myself on a grenade for an order I can't remember?''

``It was no order, you just did it.  That's why I'm jumping on the grenade this time.''

``What?''

``You got our back, so we have yours.''

``Who's we?''

``You got us 'cause we're in your brain''



Hayley steps into the scene as the naked chick.  Jaya and Oliver can see the naked chick stand up and start walking toward the darkness.  She's moving in creepy fits and spurts that average out to normal speed, unlike Jaya and Oliver's slo-mo falls.  The naked chick says something- the words don't make sense but the subtitles say, ``I will save you like you saved me so many times.'' and she draws a sword (from where??) and disappears into the darkness.  The severed head of the little girl comes rolling out of the darkness, bounces along the corridor and disappears into the darkness on the far side. It slows down once, dramatically, mid-bounce, so the half-angry, all-dead visage of the face is clear to the viewer.



Oliver can't remember what happened.  Jaya points out that Oliver survived the first time, just jump on the grenade and save her life like he did the last time. 



Eventually he lands on the grenade, and at the last moment his mouth ticks up with a smile.  



{[}Jaya gets Yellow card- ``Without Pity. Without Remorse''{]}



\ding{227}\ding{227} In Hayley's brain:  The face of a man, intensely concentrating.  Blood is running down the side of his head and dripping on the ground.  There's anger and thinking and decision making.  Graves would be a suitable target since it does not have any important resources.  The order is given: INITIATE GLASS ROAD. (Graves is a subway stop in the directorate) 



 \ding{228}\ding{228}\ding{228}{\color[RGB]{68,68,68}▶▶▶ } Hayley reports this to Jonah.  The folks in Ops ask for a confirmation that they said ``Glass Road''. 

\ding{228}\ding{228} {\color[RGB]{68,68,68}▶▶ } Jonah reports that Oliver appears to be forgetting things.

\ding{228} {\color[RGB]{68,68,68}▶ } Rook says that the memories he's dwelling on are important to him.  We have to find the locus of that memory.





\jumpHeadline{ Memory : Kate in the rain} 

\memoryScene{
\textit{Oliver is walking down the street in Cardoza, and cloaked figure steps out to meet him.}

\textit{OLIVER: ``Give me some warning next time!''}

\textit{GERHAUSER: ``I'm not supposed to be off base,'' (steps close) ``I have a favor to ask.  We've all lost pieces of ourselves along the way.  Everyone is somebody's daughter or sister.  I just need you to think twice about....''}

\textit{OLIVER: ``You're talking about the meeting we just had?''}

\textit{GERHAUSER: ``Not exactly no.  I can't stay.  It's important for you to know that Morgan is extremely driven.  But she doesn't always make the best choices.  You know what this means,'' (Looks at backpack)}

\textit{OLIVER: ``I'm touched by your concern, but especially after everything you've gone through, I'm surprised that you of all people...''}

\textit{GERHAUSER: (reaches out a hand and gently touches his face) }
}


The bitchy little girl is there... and a shadowy figure.  Boxes knocked over. After much balking and cowering, the girls nominate Jonah to be the one to jump into Kate.

HE/SHE SAYS ALL THE RIGHT THINGS

``I never could figure out the right thing to say,'' Oliver says.

``Just say it.  Don't think about it,'' says Kate/Jonah.

``I will miss you when I'm gone.''

``Don't go.''

``I must.  I'm all missing pieces''

``They try to take who you are, they took our sister away as well too.''

``yeah.... who was that?''

``Our sister or them?  No wait, Oliver, Oliver, just think about who you are.  Who we are is more than memories or words.''

``No matter how many times they put me back together, they never fixed my leg.  They never fixed my leg.... You never took that away from me.  Just... me...''

``Your leg is who you are?''

``No, but take it back.''

``Take your leg then.'' 



{[}Jonah gets a Yellow Card: ``The Keeper of Ways and Hearts''{]}



\jumpHeadline{ Memory : Babe in Arms} 



A bunch of scenes of Oliver saving Hayley.



\memoryScene{\textit{In one smooth motion, Oliver raises his gun, points it over Hayley's shoulder and pulls the trigger. A would-be attacker falls dead. Just as smoothly he slings the rifle and dives to grab Hayley's hand as she starts to fall down a shaft (that appears from no where). Even as he hauls her to her feet, he pulls her to one side and out of an explosion of gunfire launched by a tall, naked woman with ferocity in her eyes. The two of them land in a pile of corpses, where Jaya and Lackovich are also taking cover. A mortar is announced by it's signature whine, and an explosion goes off, sending everyone flying through the air. Oliver holds on to Hayley. Everyone lands against a wall and amidst shattered, dusty brown masonry. There is a small girl there, splayed against the wall just like the Patrol Group.}}



``Are you okay?'' asks Oliver

``Yes, thank you.'' says Hayley.

``That was a close one.  We should get going.''

``The train will be here soon, we will be okay for a moment.  We are safe.''

``We are never safe, not around here.''

Hayley laughs.  ``Safe for \textit{right now} then.''

``I suppose that's the best we can hope for.''

``I'm not worried.''

``I'm going to be sad to lose you.''

``Why would you lose me?''

``Well, I'm losing a lot....''

``I'll be here.  I'll always be here.  Because you always save me.''

...

Jaya snaps at the girl to leave and then makes the poor choice of trying to kick her (without the backing of a token).  Creepy girl lays hands on Jaya who then immediately dissolves from the memory.   Lackovich does nothing the entire time except lay down covering fire, ignoring everyone. 

...

``When you're gone, who am I going to protect?'' says Oliver as the train doors slide shut.



{[}Hayley gets Yellow card- ``The Farthest Arm''{]}



\jumpHeadline{ Memory : Baseline} 



Oliver and Gerhauser are in the lab.  Oh, there's also the little girl... touching all the lab equipment. 

\memoryScene{
\textit{GERHAUSER: ``Did you ever keep a pet?''}

\textit{OLIVER: ``Yes, a cat named Grey, I wasn't very creative.''}

\textit{GERHAUSER: ``Where were you when you suffered your injury?''}

\textit{OLIVER: ``DX station.''}

\textit{GERHAUSER: ``How do you feel about Hayley?''}

\textit{OLIVER: ``She's a nice girl}\sout{ \textit{,} }\textit{ but pretty messed up.'' (Oliver looks at G, G smirks)}

\textit{GERHAUSER: ``What is your biggest dream?''}

\textit{OLIVER: ``To do something that matters.''}

\textit{GERHAUSER: ``How do you calculate the area of a triangle?''}

\textit{OLIVER: ``Isn't it something like half the height times the width?''}

\textit{GERHAUSER: ``How many pieces in your sniper rifle?''}

\textit{OLIVER: ``57,'' replies Oliver instantly, and then adds, ``but really it's part of 5 modules.''}

\textit{GERHAUSER: ``And how do they fit together?''}

\textit{OLIVER: ``It would be easier for me to show you but...'' and Oliver describes the process as best he can.}

\textit{GERHAUSER: ``Do you trust Agent Morgan?''}

\textit{OLIVER: ``About as far as I can throw her.''}

\textit{GERHAUSER: ``Have you had sex recently?''}

\textit{OLIVER: ``No.''}

\textit{GERHAUSER: ``Do you suffer from headaches?''}

\textit{OLIVER: ``No.  Say, can I ask you questions?''}

\textit{GERHAUSER: ``I suppose.  Depends on the question.''}

\textit{OLIVER: ``How do you feel about me?'' asks Oliver.}

\textit{GERHAUSER: ``It's complicated.''}



\textit{OLIVER: ``Can I change my answer?''}

\textit{GERHAUSER: ``Which answer?''}

\textit{OLIVER: ``Morgan.  It's complicated.''}

\textit{GERHAUSER: ``Ah.''}

\textit{OLIVER: ``So why complicated?'' asks Oliver.}

\textit{GERHAUSER: ``I think you're liable to get yourself killed.''}

\textit{OLIVER: ``I agree, I'm trying to do something that matters, and I only have one thing to give.''}

\textit{GERHAUSER: ``That is where I disagree with you.''}
}
Again there's balking, and Hayley is thrown into Kate.  Jonah tries to walk Hayley through it and she mentally shushes him.  

``Well, what else do I have to give anyway... well, you were right probably...'' says Oliver

``... you have a lot to give, I know that.'' says Kate/Hayley.

``You know, everyone... was laying out a path for me. which is why I came back to the TA.  When everything was ruins around me''

``But you're not alone on it, isn't that what's important?''

``I'm sick of walking the straight line. ``



Little girl picks up a scalpel and starts playing with it. Fuck. 



``Everyone has their own ideas about what we're supposed to do. I never thought any of them were right... and... but there was a comfort in letting go and letting Jaya leave making stupid decisions so I could criticize her.  Morgan giving stupid orders so I could give her shit later when everything fucked up.''

``It's easier that way...'' says Kate/Hayley.

``But why... I think I asked this... I think... I think..''

``Just ask me again''

Aaaaand creepy girl uses the scalpel to cut ``Kate'''s throat



\jumpHeadline{ Memory : A Study of Langdon} 

Oliver is in a scene with his father, who is cleaning a gun. 

``When did you start lying to me? ``

``I don't know... never? I'm not sure... sorry''

``Sorry!? Phfff... Sorry is what what people say when they fail... You've gotten quite used to that word, 'aven't you?``

``I didn't fail, I did something important!''

``Oh? what did you do that was so important?  Certainly not something so important that you'd say anything about it''

``I... can, I can still... I can still help the Directorate! I can still help you somehow!''

``Why do you sound so... mealy mouth when you say these things?''

``You never saw the good in me!  ... Fine!''

``Do you have good for me to see?  Was there any good in you to see?''



THE GIRL IS SMILING VERY EVILLY --- Jonah cuts in as Father



``What, revenge? killing people I've never met from a distance?''

``So you grasp at what you have,'' Father counters more kindly than he has the entire scene

The girl stands up.

``I tried... wish I could do what you could do. That's why I was so angry.  You need to decide what to try?''

She seems to be selecting from some revolvers.

``Remember what matters to you.  What was it?'' asks Mr. Langdon/Jonah.

``You know, the further away you sent me, the more I cared about what you thought of me... but... I don't think I would have done anything worthwhile if you didn't think I was a useless sack of shit''

Girl blows off Father's head



{[}Jonah gets Yellow card- ``Sins of the Father upon the Son''{]}



\jumpHeadline{ Memory : The Orc of Anglia} 

``What do you want?'' asks the Orc.

``I want to make a difference,'' replies Oliver.



Hayley tries to jump into the Orc and gets violently rejected.  IT FUCKING HURTS.  She can feel the attention of Octavian bearing down on her.

....

``Why can't I kill them all?''

``It's like committing genocide, it never works''

``Isn't that your game?''

``Our game is much larger than that. If committing genocide is like frying an ant on the sidewalk, we intend to burn down the whole city.''

...

``You can't scare me'' says Oliver

...

``We want you to join us'' says the Orc.

``Why would I do that?''

``We want to get to know you.  It is the one way you will see her again.'' ``I was fascinated with you, the way you fight.  I could see how good of a fight it would be.''

``She'll be happy to know you are back,'' says Oliver

``We can heal you.  We can heal her too.''

``I don't want that.  She doesn't want that either.''

``You'd be surprised.''

``Shit happens,'' says Oliver.

``Is that what you really mean?  'Shit happens?'''  The Orc starts backing away, still talking. ``I'll tell her you say hi.''

Oliver runs after the Orc.



\jumpHeadline{ Memory : Jaya in the Rain} 


\memoryScene{
\textit{Jaya kicks over some boxes to get Oliver's attention. A small girl continues to kick over boxes, and then other things, all which fade as they fall to the ground.}

\textit{JAYA: ``Sorry I slugged you.'' (Pause) ``Not really.  We cool?''}

\textit{OLIVER: ``Sorry I gave you an order.  We cool?''}

\textit{JAYA: ``No, but, uh, I'm the Senior Constable and I want the team to be cohesive.''}

\textit{OLIVER: ``I'm not the one to talk to.''}

\textit{JAYA: ``Yeah... yours was the only address I could find.  Say you know of any good place to drink around here?''}

\textit{OLIVER: ``No, I don't drink around here.''}

\textit{(Jaya offers Oliver a bottle)}

\textit{OLIVER:  ``Where did you get this?'' (chokes)}

\textit{JAYA: ``Not at a Citizen's bar!'' (grins)}
}


``Now don't freak out, ok?'' Jaya pulls out her gun.  ``I'm going to shoot you.  In the leg.  For the good of the team.''

``Why?''

``The team needs you.  You're a...valuable asset for the team.''

``Who are they?''

``What?  The team?  You mean Jonah and Hayley?''

``Who's Jonah?''``Eh...Jonah's easy to forget.  But Hayley!  You must remember Hayley.''  Jaya makes a gesture of a woman's curvy silhouette.  Oliver shakes his head.



With approval from the voice in her head, Jaya goes ahead and shoots Oliver in the leg but it doesn't hurt or bleed.



The little girl puts a hand on Oliver.  ``Any last words?'' she asks.

...

``Go on then, punch me, right here,'' Jaya taps her jaw.  Oliver punches her.   She pulls back and swings as if in retaliation but instead aims at the girl next to him who manages to lean back, well out of the way.  Jaya tumbles forward and lands in the dirt, on her back.   She bemoans the fact that she's spent and can't do anything else.  Sitting up, she rubs her jaw and bitches, ``Ow!  You didn't have to punch that hard.'' 

``Stop whining,'' Oliver says, but he's smiling and shaking his hand.  ``That was pretty satisfying, actually.  How did you get to be our leader?''

``I'm really good at...good at...'' Jaya can't think of anything and the train doors close.



{[}Jaya gets Yellow card- ``Conformist, Last''{]}



\jumpHeadline{ Memory : The House} 

Oliver is sitting on a balcony waiting for Hekate Gerhauser, with a bottle of wine and his back to the wall, scoping out sniper positions. Kate is there, seamlessly, sitting across from him. They have just had a long conversation. There is a book on the table. She seems to have forgotten about it. Oliver has an unlit cigarette in his hand. There is a palpable energy in the air, but everything seems very still.  The water beyond the balcony is dark, with the sense of something beneath it. It is slowly rising as it gently laps against ancient stone.



``This... kept me going for a while,'' says Oliver.

``I'm glad'' says Kate.

``I'm sorry,'' apologizes Oliver.  ``...about all this.''

``Me too.''

(it's very anime, long shot, nothing moves-- except the birds)

``I wish I could see you again, but I know I won't, because this is the last time.''

She starts to cry

``I don't even remember your name.'' Oliver starts to cry too.  ``It's my fault...''

``No.''

``I don't even remember what happened, but it's definitely my fault because that always how it is.  But think of me sometimes.''

``Always,'' she says.



And just before it goes to black, Kate says quietly, ``I love you''



\textgreater \textgreater \textgreater  Hayley comes out of the pain.  The attention of Octavius has ``blinked'' and is distracted.  She can see the image of a man, blood gushing to the ground.  But the voices around him say ``We have him!''



\jumpHeadline{ Memory : The Battle of DX Station} \footnote{\textbf{Rebecca (as editor) }This was a link to Deus Ex-Human Revolution: Icarus Main Theme on Rdio}

shit gets real



``I'm proud of you,'' says Hayley.



``You have to go out there,'' says Jaya.

``Why?  Why did I do it?'' asks Oliver.

``You did it because you were trying to do something important.'' says Jonah.  ``Because that is what you do.''

``But it is the end,'' says Oliver.

``Or the beginning,'' says Jaya.



``It is okay to be afraid,'' says Hayley.  ``It is scary to do something knowing that it will hurt.''



``Remember me,'' says Oliver.

``Of course.  Of course I will,'' says Hayley.

``Remember... I don't even remember what you are supposed to remember,'' says Oliver, his voice full of emotion.

\hl{``It's okay,''}\footnote{\textbf{Suko T }I was trying so hard to keep my voice steady even though I was totally about to cry.  Hayley wasn't sad though, she was actually happy in her bizarre way.  So any voice wobbling was me, not her. \textsubscript{05/28/14 7:05pm}} says Hayley as gently and lovingly as you have ever heard her speak.  ``I'll remember that too.  I'll remember everything for you.''

``I'll miss you, I think''



\textgreater \textgreater  he ``releases''

Not limping, but grimacing, he charges out into the street... momentarily blends with the rush of the crowd. A glint of metal. 

Someone, not him, shouts ``Sniper!''

THERE IS A BRIGHT LIGHT

Oliver is shot through the chest, falls face first into a puddle of water, with one eye in the mud and one eye open staring outward, completely lifeless.



There's complete blackness, Oliver has feelings, but he can't even describe them to himself

Blinking blue light in front of him.  Everything he feels towards Octavius and the Directorate... A strand of hope... he know it means enslavement. He feels his breath becoming short as if he's running out of air...

Oliver holds fast onto his own IDENTITY, going toward the pain and hope. 

He gets a sudden urge -- there is someone waiting for him, someone he wants to see again. Possibly multiple somebodies, but he feels it's on the other side of that...



Hayley can see this, but gets no thoughts and only echoes of feelings.



He can't decide if he's dead or before life. Everything has to die and be asked into the world again.  That concept of ending recently is there, but he doesn't have words like death or life or being shot.



Oliver clings to the inherent urge to bite the hand that's trying to offer him something. 



He gets one last impression, and it's a threat, that the thing he wants will be destroyed as well. 



He leans into the feeling of nothing.  The air gets thin and he eventually goes to sleep. 



Many years later, the cylinder with the blinking light's battery runs out. 



\jumpHeadline{Quotes}

Hayley: This isn't me from then, this is me from now?\\[4mm]


\quotedDialog{
\hl{Nate: Note the tiara.

Adam: You know that 10x10 is 100 right?

Nate: But 9x9 is }\textit{not}.\footnote{\textbf{Nathaniel Ford }This is hilarious misquoted! Not deleting it because of Reasons. \textsubscript{05/28/14 12:13pm}}\footnote{$\rightarrow$\textbf{Suko T }Where Reasons = Tiara \textsubscript{05/28/14 1:27pm}}\\[4mm]
}

\quotedDialog{
Nate: Note the T.R. It's multiplicative not additive.

Adam: You know that 10x10 is 100, right?

Nate: But point nine by point nine is \textit{not}.\\[4mm]
}

\quotedDialog{
Rebecca: I do the thing that my people tell me to do

?: As Jaya always does\\[4mm]
}



\sceneHeadline{Yellow Cards}

\textbf{Hayley}



 ``The Cold Water''

 SAC-09 Cistern: This is a place of solace and healing for you, and when upset you long to return there.



 ``The Things We Carry, The Pain We Walk With''

 Leg Pain: There is a persistent pain in your leg, making moving quickly uncomfortable at best and often impossible.



 ``The Farthest Arm''

 Oliver Langdon's Sniper Rifle: It is a part of you, like another arm. You feel lost with it.




\sceneHeadline{Jaya}

 ``Conformist, Last''

 Anti-Authoritarian: You bristle at control, and want to prove those in charge they're wrong and can't dominate you.



 ``Without Pity. Without Remorse''

 Hardened: The pain others suffer is little compared to what you've gone through. You just can't be bothered to care as much for them.




\sceneHeadline{Jonah}

 ``The Keeper of Ways''

 Hekate: You want her, care for her, want to protect her, and are emotionally confused when at odds with her.



 ``Sins of the Father upon the Son''

 Daddy Issues: You really just want your father to be proud of you, to know you made a difference and accept you for who you are. And yet, even if he showed that he was proud of you or accepted you, you'd never entirely trust it.




\sceneHeadline{GM}

 ``There is Only the SHOT''

 Focused: Once you have decided something is important, other things fall away and are hard to consider seriously.



 \hl{``Citizen, First''

 Proud: You are better than most, and are frustrated when they don't see it.}\footnote{\textbf{Rebecca S. }Damnit, I should have intercepted this one... \textsubscript{05/28/14 11:07pm}}



\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 07/10/15 12:30am}
% Exported @ 08/24/15 11:09am
\end{flushright}

