\setcounter{chapter}{ 25 }
\chapter{\textbf{``Bottle it up''} }




\begin{center}
 {\LARGE \textbf{(SAC-09 Interlude)} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} June 19th, 2014



Coping.  TA-style.



\noindent\hrulefill




\sceneHeadline{Ops}

Jonah comes to full awareness first, having been half-aware of what was going on in SAC-09 already.  He lies still for several minutes, not opening his eyes.  Jaya does likewise.



Jonah surreptitiously scans the faces of the people in the room.  Micah is standing to one side.  Rook is looking impassive.  Morgan is poised as if waiting to pounce.  Carruthers is by the doorway, staring at Hayley.  Trenton and Victor are arguing- loudly enough to be heard through the tank walls but their actual words aren't intelligible.  Larissa is sitting at a monitor.  Dr. Gerhauser is also sitting at a monitor but is just staring into space.



Swan approaches Jonah and asks him some basic medical questions, although when he asks what Jonah needs, Jonah is silent.  Jonah starts feeling a sense of panic, someone else's panic.  Hayley is still in her closed tank.



Jaya opens her eyes and glares at everyone.  Swan asks if she wants to get out of the tank.  Moving with intimidating suddenness, Jaya flips Swan off.  Swan jumps back and looks nervous.  Morgan doesn't move but her attention is clearly drawn to Jaya.



Jonah grabs Swan's arm, which scares Swan even more.  ``What happens to an Operator when an Agent dies?'' Jonah asks, although he speaks loudly enough that everyone can hear the question.

``She'll live,'' says Carruthers flatly.   Jonah can see that Carruthers is armed and that she is really not doing very well, emotionally.



Jaya starts toweling off some of the goo and then grabs the third towel (probably Hayley's) and starts toweling off her hair.  She walks over to Dr. Gerhauser and slaps her hand down next to her.  ``WHAT THE FUCK WAS THAT?  What the fuck was supposed to happen???''

Dr. Gerhauser's focus was not on Jaya, and slowly rotates to look at her. But she doesn't reply, she just raises an eyebrow.

``That was so messed up!  You and Oliver... and.... and all that.  I didn't want to see that!!  Now it's all in my head.''  Jaya turns and jabs an accusatory finger at Morgan.   ``What the FUCK do you think you were doing?''



Rook says calmly, ``We were identifying Operator Langdon's location, which was successful.''



The sense of panic that Jonah was feeling earlier is growing stronger and stronger.  Suddenly it breaks and there is a flood of nonsense emotions and Hayley's tank pops open.



Jonah says to Swan, ``Get me out.'' and Swan assists him in getting out of the tank.  Jaya orders Swan, ``Get her out of there!'' pointing to Hayley.



Before Swan can reach her, Hayley crawls out of the tank.  She is moving very oddly.  She is covered in goo like Jonah and Jaya but it seems to cling to her in a creepy fashion.  She makes no effort to wipe it out of her eyes or hair so it drips unpleasantly down her face.  She vaults out of the tank to drop lightly to the ground, and starts walking across the room.



Jaya realizes that she has Hayley's towel and walks up to Hayley and attempts to drape the towel around her.  Hayley smoothly pivots out of the way and keeps walking.  Hayley leans toward Oliver's cart briefly and then continues to move toward her own cart.



\hl{Morgan and Micah stand up.}\footnote{\textbf{Nathaniel Ford }There is something I find pleasingly creepy about this sentence. \textsubscript{06/22/14 10:56pm}}  



Jaya stubbornly pursues after Hayley with the towel, and Hayley dodges each time until she reaches her cart.  Hayley's hands feel their way over the cart, as if she is learning the objects by touch, not sight.  Her hands land on the assault rifle and her body goes tense.



Micah steps forward, one hand on his sidearm.  Morgan looks even more alert and ready to move.



Hayley picks up the rifle.  Jaya can see that it is unloaded.  Jaya reaches around Hayley and grabs the stock of the rifle in one hand and the barrel in the other and pulls it toward the two of them in a subdual hold.



Hayley's body relaxes against Jaya's for a moment, seeming to give in, and then she savagely punches Jaya in the ribs, unerringly aiming for one of the barely healed broken ribs from the last mission.  With Jaya's grip loosened, Hayley drops and spins, grabbing a magazine and loading it into the rifle in one smooth motion.  She doesn't aim the rifle at anyone and Jaya can see that Hayley's eyes look unfocused and confused.



Jonah has hidden himself behind the Tanks with Swan.  Micah draws down and starts approaching Hayley and Jaya.  Rook stands.  Dr. Gerhauser has resumed staring into space.



Morgan says, ``Enough.''

With impressive speed and accuracy, Rook draws his gun and shoots Hayley full of flechettes.

Hayley looks even more puzzled and then drops to the floor unconscious.



Jaya demands, ``WHAT THE FUCK IS GOING ON?''

Morgan replies, ``You are going to have to be more specific.''

Jaya just points at Hayley.

``I suspect her Operator just died,'' says Morgan, looking over at Jonah.

Jaya leaves.

Carruthers stares at Hayley and then looks at Jonah with an expression of either anger or self-satisfaction.

Swan starts fussing over Hayley and gets her ready to move her to Medbay.  Rook also assists, but without the fussing.




\sceneHeadline{Bunk- Jaya and Jonah}

Jaya showers and then sits on her bunk and does a bunch of drugs (downers).  Jonah walks back slowly.  When he gets to the bunk he doesn't bother to shower off the goo or get dressed, he lies down and covers his face.  Jonah is exhausted but sleeps badly.  Jaya is mostly catatonic from the drugs and lies the whole night staring at Oliver's empty bunk.




\sceneHeadline{Medbay- Hayley and Carruthers}

Hayley comes to in Medbay.  It is dim and there is a needle in her arm.  There is an odd rhythmic noise that takes a moment to identify as a ball bouncing against the wall.  Hayley doesn't move, or open her eyes, but at her changed breathing pattern, the bouncing pauses for a moment.  When Hayley doesn't open her eyes, the bouncing resumes.  Hayley lies there for a very long time.  She's not sure how long she wanders, deep in her thoughts and memories.  At some point she falls asleep.



When she wakes up again, she can feel the unpleasant sensation of pain medication making her body feel numb and distant but doing nothing for the terrible emotional pain she is feeling.  Hayley tries to remove the IV and realizes that she has been strapped down, five-point immobilization.  She opens her eyes.



Carruthers is in the room, but says nothing.

``Did I die?'' asks Hayley.

``No.''  \textless pause\textgreater   ``Do you want to?'' asks Carruthers.

``I thought I did.  But no.  I don't.''  

Carruthers says nothing.

``I'd like the drugs to stop now, please,'' says Hayley politely.

Carruthers catches the ball and leaves.



Hayley closes her eyes again.  A few hours later, Swan appears and removes the IV.  ``How are you?'' he asks.

``I hurt a lot, but the drugs were just making me feel strange.  They weren't helping.''

``Where does it hurt?''

Hayley attempts to indicate but can't move enough to gesture.

``We will do a full evaluation,'' says Swan.

``Including a Theta3 Scan?''

Swan pauses for a long time before replying, ``Yes  That will be one of the scans performed.''

``What does it do?''

``It measures the disbursement of certain technology in your bloodstream.''

``I don't know all of those words,'' says Hayley, a bit distressed.

``That's okay, just rest,'' says Swan and leaves.

Hayley cries quietly.




\sceneHeadline{Bunk- Oliver's stuff}

While Jaya was tripping out, Jonah cleared out Oliver's bunk, tidying it so that it looks like no one has ever slept there.  He gathered up Oliver's things neatly in a pile.



When Jaya wakes up, she goes through all of Oliver's stuff, making a mess of Oliver's bunk and Jonah's tidy piles.  She takes Oliver's medals, money, cigarettes, alcohol and commission papers, and shoves them under her mattress.

``Maybe Hayley will want them,'' she says to Jonah.

``Anything personal we should send to his family,'' says Jonah.

Jaya just gives him a look.  ``You saw it.  His family doesn't give a fuck.  Only Hayley cares now.''  She leaves and heads to the mess hall.



Jonah takes the medals back and sees the other treasures that Jaya has stashed under her mattress (he leaves them there).




\sceneHeadline{Mess Hall- Jaya}

Davis is eating some roasted klipspringer.  It would look really delicious except the smell of food is making Jaya feel nauseous.  However the red liquid that he's drinking looks good.  Jayce is also there, eating well, though not as well as Davis.



Jari comes out of the galley and greets Jaya, ``What would you like?  Open galley.''

``Now that there are fewer mouths to feed, it's 'Open Galley'?'' sneers Jaya.

\hl{Jari does not reply.}\footnote{\textbf{Nathaniel Ford }Jari goes from fairly warm to cold here, which lasts the rest of the scene. Not sure how to best describe that inline. \textsubscript{06/22/14 11:00pm}}\footnote{$\rightarrow$\textbf{Suko T }It was certainly clear from your tone and body language that Jari was not ``Happy Fun Jari'' anymore. \textsubscript{06/22/14 11:28pm}}

``I want that,'' Jaya says, pointing at Davis' drink.

Jari heads into the galley and returns with another glass of red liquid.

Jaya drains it and hands the glass back to Jari.  It is very tasty and potent.

Jari goes into the galley again and returns with a bottle.  He sets it down on the table and says, ``I'll be in the galley.'' and leaves.



Jayce tries to catch Jaya's eye and she scowls at him.



Jaya grabs the bottle and leaves.  She passes Carruthers in the hall and they say nothing to each other.





\textbf{\hl{Medbay}}\footnote{\textbf{Suko T }Best.  Grief.  Counseling.  Ever.  
....By TA standards anyway. :D

Loved this scene. \textsubscript{06/19/14 1:47am}}\textbf{- Jaya and Hayley}



Jaya heads down to Medbay and asks Swan, ``Where's my team member?  The living one?''

Swan points to Hayley's room and then registers what Jaya said and asks in alarm, ``Wait- what do you mean?  Has something happened to Jonah?''



Jaya ignores him and heads to Hayley's room.  Swan leaves to go look for Jonah.



Jaya sits next to Hayley, a bit unsteadily as the alcohol already starting to kick in.  Hayley is awake.  ``I brought some medicine for you,'' Jaya says, offering the bottle.``No thank you.  It's poison,'' says Hayley.

``Yeah I know, but it's the good kind.''

Hayley says nothing.

``You almost shot me today,'' says Jaya.

``I'm sorry.  I don't remember.''  Hayley tries to shift but can't and looks a little distressed.

``You want me to loosen you up?  These guys are assholes.''

``I'd like to be able to move my neck.''

With the Predator-style knife built into her new arm, Jaya slashes the strap holding Hayley's head immobile.  She looks at Hayley suspiciously to see if she's still moving weirdly.

Hayley rolls her head and neck to loosen them and looks at Jaya curiously, ``Is everyone alive?''

``Everybody?  Well there's you.  Jonah.  Me.   That's it.  You should hurry up and get better.  They're going to want to send us on more missions.''

``It hurts a lot.  Drugs don't help.''

``Where does it hurt?''

Hayley tries to indicate again but can't, as her arms and legs are still strapped down.  ``My chest,'' she says.

Jaya examines Hayley's chest, and even takes a peek under the neck of the hospital gown and sees some of Hayley's scars.  She hurriedly covers them back up again.  ``I heard what you told Oliver.  In our heads.''

``What do you mean?  I told him lots of things,'' says Hayley, confused.

``Whatever- it doesn't matter.''

Hayley closes her eyes briefly and then looks up at Jaya.  ``Do you mean what I told him about my scars?''

``Yeah.  That was pretty messed up.''

``I didn't enjoy it,'' says Hayley quietly.

``Good.  Don't enjoy that.''

``If I had, I probably would have died sooner.''

They both fall silent for a moment.

``We found Oliver's stuff, do you want any of it?'' asks Jaya.

``Can I have his gun?''

``Sure, you can have his gun.  I'll tell Jari.  I'll make sure you get his cleaning kit too.'' Jaya punches Hayley in the shoulder companionably.

Hayley starts crying.

Jaya freaks out a bit.  ``Hey stop that.  Stop crying.  Just uh, contain the tears.  Hold them inside.''

``But I have to feel the pain, otherwise it gets worse,''

``No no, it doesn't work that way.  Just- just- don't be sad.''

``I'm not.  I'm happy,'' sniffles Hayley, still crying.

``Wait, what?  No- don't be happy!''

``What?''

``Don't cry either!  Be like me!  I'm not sad.  I'm angry!''  Jaya starts blotting some of Hayley's tears away with gauze pads.

``Why?  I'm not angry.  I'm not sad for him.  I'm sad for me.'' says Hayley, blinking furiously at Jaya's ministrations.  ``Um, I think you got some lint in my eye.  There's saline in the second cabinet on the upper right.''

``I'm angry at them!'' says Jaya as she fetches the saline and flushes Hayley's eyes, soaking her pillow.

``Thank you.  Them?''

``Morgan!!  They shot you!''

``They did?  Who did?''

``Rook!  Stone cold killer, man.  Fucking Morgan sent us in!  They knew.  Why did they do that?  They're just fucking with us!'' rants Jaya.

``No, it worked!  We found him.''

``What??  No!  Where's his body? He's gone.  Oliver's gone.'' Jaya repeats.

``I know he's dead,'' says Hayley, oddly calm.

``Okay good. He's gone.''

``...I brought him back with me,'' continues Hayley with a smile.

``No you \textit{didn't}.  He's completely gone and you are just going to have to accept that.  He's GONE.  He's not here.  Only crazy people would say that.''  Jaya continues on for a while in this vein.

Hayley eventually just nods and says, ``Okay.  But I would really like my rifle please.''  Jaya doesn't notice Hayley referring to Oliver's rifle as 'hers'.

``Okay.  Good.  I'll get it for you.  But no crying, okay?''

``I can't promise that.''

``Well no crying until after I get back.''

``I'm sorry, I will cry, but I won't tell you and you can pretend I didn't.''

Jaya drapes the cut strap back over Hayley's forehead so it kinda looks like she's still strapped down, and hastily leaves before Hayley starts crying.

Hayley smiles.




\sceneHeadline{Hallway- Jonah and Carruthers}

Jonah runs into Carruthers in the hallway.  They pause an awkward and uncomfortable distance away from each other and stare for a moment.   Carruthers starts to walk away when Jonah says ``You \hl{were}\footnote{\textbf{Suko T }Aww... way to rub it in Jonah. :P  This whole scene seemed so brutal to poor Carruthers.  Good stuff, but yeeouch. \textsubscript{06/21/14 4:23am}}an Operator, right?''

``Yes,'' she replies.

``Wasn't long ago either, right?  Sorry...time is confusing right now.  You said some things when we got out of the Tank.  Something about how 'she'd be okay'''

``I said 'she'd live','' corrects Carruthers.  There is a pause.  ``You \textit{were }asking about Hayley...?''

``No.  I wasn't.  I- This is very confusing.  I'm sorry.''

``No it's fine. \hl{I'm happy to help you get through your grief.}\footnote{\textbf{Nathaniel Ford }This sentence was very pointed. *I'm* happy to help *you* get through *your* gried. It, perhaps obviously, wasn't entirely sincere. \textsubscript{06/22/14 11:04pm}}''

``You were connected?'' asks Jonah.

``Yes.''

``What did they do to help you?''``They?''

``Swan.  Gerhauser.''

``They haven't been through it.  They didn't do anything.  They didn't \textit{know }to do anything,'' says Carruthers.

``Figures.''  Jonah thinks for a moment.  ``Can I ask you about it later?''

Carruthers nods.   Jonah thinks some more.

``I thought you were connected to the bitch,'' says Carruthers.

``No.''

``Did you feel him die?'' she asks.

``It was worse than that.''

``You would know if you did.''

``Ever see someone die?'' asks Jonah.

``Yes, but n-not violently,'' replies Carruthers, her stutter coming back.

``You're not a medic.''

``I'm trained in first aid...'' offers Carruthers.

``In the war, I saw many die,'' says Jonah.  ``It wasn't like that at all.  Did you feel pain? His pain?''

Carruthers doesn't speak.

``I'm sorry.  It's not the same.''  Jonah is quiet a moment.  ``Did you stay?  To the end?''

``He- he told me n-n-not to.  B-but I did anyway,'' says Carruthers, her stutter getting even worse.

``You don't feel his pain any longer?''

``No.  I don't feel his pain,'' she says, not stuttering.  She looks angry (maybe, she's hard to read).  She starts to say something else and then just leaves.

Jonah stands in the hallway for a long time.




\sceneHeadline{Hallway- Jaya and Rook}

Jaya searches for Jonah for three hours.  She runs into Rook.

``Agent Rook, I'd like to requisition Oliver's gun.''

``May I ask why?''

``It is my opinion that it is necessary for mental health.  My trainee- um- Agent- um Operator Hayley... It would help her to have Oliver's gun.''

``Operator Langdon's weapon was destroyed,'' says Rook.

``Oh.  Er.  Hm.''``Is Agent Hayley in emotional distress?''

``Yes, she was crying.''

``Noted.''

``But, uh, don't spread that around,'' says Jaya.  ``Special circumstances, you understand.''

``How very empathetic of you.''

``Well she's my only team member at the moment.  The only one I can find.  I can't find the other one.''

``He hasn't left the base.''

Jaya thinks and then looks a little alarmed- ``Do you think he-'' and she mimes someone hanging themselves.

``I don't know.  Did you look everywhere?''

``Yes I did!  For THREE HOURS.''``What about areas like the men's room-''

``I checked there.''

``Agent Parvadi, I would ask that you respect the sanctity of gendered areas of this base.''

Jaya protests, ``Hey I knocked first!''

``Perhaps a more salient question then. Are you not his Agent?  You should be able to contact him at will.''

``With my \textit{mind}?''

``Yes.''

``We haven't.''

They don't say anything for a moment.

``\hl{Well I'll get the gun}\footnote{\textbf{Nathaniel Ford }At some point he said something along the lines having another of a similar model. \textsubscript{06/22/14 11:06pm}},'' says Rook and turns to leave.  Jaya follows him to the Requisition Cage.  Rook takes a rifle, makes sure it isn't loaded and hands it to Jaya.  ``Hayley will be released in 6 hours,'' he informs Jaya.




\sceneHeadline{Medbay- Jaya and Hayley}

Jaya takes the gun and heads down to Medbay.  She passes by Swan and catches his eye but walks past him with the rifle.  Swan looks alarmed when he sees the rifle.



Jaya heads into Hayley's room.  Hayley doesn't look like she was crying more, but it is hard to tell from all the saline and gauze blotting that was done earlier.

Jaya holds up the rifle, ``Look!  I got your gun for you.''

Hayley frowns.  ``It is not my gun.''

``Well it's mostly the same.''

``Just a base model, it will need a lot of modification.... But thank you.''

Jaya puts it on the bed next to Hayley's hand so she can rest her fingers on it.  Hayley looks calmer.  

``It's not loaded,'' cautions Jaya.

``That's okay.  I could tell.   I could still probably crack someone's head open with it,'' says Hayley.

Jaya slugs Hayley in the shoulder again in approval.

Hayley frowns and asks, ``Why do you do that?''

``It's a camaraderie thing.''

``So it's a good thing?  Not punishment then?''

``No, not punishment!''

``Oh okay.  Good.''

``Okay so you have your rifle now.  You just concentrate on getting better.''

``Yes I know, I have to be ready, ready to protect you.''

``Right!  Yes, yes you do.''

``Because you're family.''

``Hell no we're not family!''

``You're like family- not blood related, but I feel responsible for you,'' says Hayley earnestly.

``Um, whatever.  You just keep it together okay?  No crying.  Keep it inside.''

Jaya leaves.




\sceneHeadline{Hallway- Jaya, Swan and Micah}

Jaya runs into Swan in the hallway.  ``Agent, may I ask you a question?'' he asks.

``What?''

``Did you just arm my patient?'' 

``Oh, it's not loaded.''

Swan looks a bit relieved. ``I'll inform Micah.''



Jaya finds a private spot in a hallway in Medbay and looks around before thinking  {\color[RGB]{255,0,0}::Jonah::}  really hard.

 {\color[RGB]{0,0,255}::Chief?::}  responds Jonah.

 {\color[RGB]{255,0,0}::Where are you?::} 

 {\color[RGB]{0,0,255}::I'm not sure.::} 

 {\color[RGB]{255,0,0}::Are you captured by the enemy?::} 

 {\color[RGB]{0,0,255}::There isn't anyone...I don't know.....I can't find Oliver.::}  thinks Jonah, confusingly.

 {\color[RGB]{255,0,0}::I'm going to find Morgan:: } thinks Jaya.

 {\color[RGB]{0,0,255}::Don't trust her.  It might not be her.::} 



Jaya heads to the elevator and runs into Micah.  ``I heard a report of unauthorized weaponry in Medbay?'' he asks.

``It was medicinal weaponry,'' replies Jaya.

``A rifle is not a tranq gun.''

``Hayley is in a bad place.  You know when kids cry and they need a doll.... she only needed the rifle for comfort.''

Micah seems to relax a little. ``I wasn't aware she had one.''

``I cleared it with Rook,'' explains Jaya.  ``Say, have you seen Jonah?''

``I think he is in Engineering.''

``Oh.  Uh, do you know where Morgan is?''

``I think she's in her office.



Jaya goes to Engineering but can't bring herself to go into Trenton's lab.  She tries to go to Morgan's office but the elevator won't accept it as a valid floor entry.  Jaya screams in frustration and punches the elevator wall with her mechanical hand- denting the wall.




\sceneHeadline{Hallway \& Bunk- Jaya and Jonah}

Jaya goes into the hallway again and thinks  {\color[RGB]{255,0,0}::Jonah?::} 

The elevator doors open and Jonah steps out.

Jaya punches Jonah in the face.

``Don't you EVER do that again!  We just lost Oliver.  Don't ever fucking disappear like that again!!'' yells Jaya.  Through their connection, Jaya can feel a jumble of battle panic and sympathy from Jonah.

``I was in my bunk,'' says Jonah.

``No, I looked there.''

``Hmm... that would explain why I am so confused...''

``Did you touch my stuff?  'Cause some of it can really mess with your mind...''

``I would never touch your stuff.''



Jaya tells Jonah that they have a debrief coming up soon.  ``They will want to ask us some questions.''

``No, we are going to be asking the questions,'' says Jonah.

``Has that ever worked?'' asks Jaya skeptically.

``Yeah...oh right.  You walked out the last time we asked questions.''

``We thought we were going to get him out.  That was so fucked up!  I don't want those memories.  They can't do that to us!  We're not brain tank people!''



They head back to the bunk.  Jonah's bunk has indeed been thoroughly tossed by Jaya.

``We tell them to go fuck themselves,'' she continues.

``I want to know what the hell they thought they were doing.''

``I think we tell them to go fuck themselves,'' Jaya repeats.

``Can you tell what I am feeling?'' asks Jonah.

``Are you angry?  You should be,'' says Jaya.

Jonah pushes his anger to Jaya- it's a different anger than hers.



``What did they think sending us in there would do if we weren't getting Oliver out?'' asks Jaya.

``Or at least why,'' says Jonah.

``We should ask for more pay.  When you're angry, you ask for something.''

``We can ask why.''

``No, you need to ask for a thing, that's just a question.''

``What do you want?'' asks Jonah.

``I want revenge. For Oliver.  And for us.  And all the bullshit.''

``The ones who did this to Oliver are far away.''

``Then Morgan.  Morgan works too.''



They start discussing how they want to approach questioning Rook and Morgan, probably some variant of ``good cop, bad cop''




\sceneHeadline{Medbay- Hayley and Morgan}

Morgan enters Hayley's room.  Hayley has managed to patiently wiggle and contort her way out of the arm restraints, though she left the leg restraints.  

``I was going to see if you were ready to be released from the restraints but I see you are already taking care of that,'' Morgan says.

``I was practicing,'' replies Hayley.

``What is your status?'' 

``I hurt a lot,'' replies Hayley.

``Do you need more medication?''

``No, it doesn't help.  And I think better without it.  It makes things too far away.''

``Do you feel you will be ready for another mission?''

``Depends on the kind of mission.''

``This would be a more political one.''

``Possibly, I would need some time to fully evaluate my condition.''

``Debrief will be in 5 hours.  Report to Agent Rook with your decision before then.''

\hl{``Understood.''}\footnote{\textbf{Nathaniel Ford }Morgan, importantly, mentioned that anger was useful - implicitly referencing Hayley's conversation with Jaya earlier. I don't remember the specifics, but something like,

``You know, Jaya was right about one thing. Anger is useful. It creates focus.'' \textsubscript{06/22/14 11:11pm}}\footnote{$\rightarrow$\textbf{Suko T }Ah yes, I remember that now!  A moment of Morgan agreeing with Jaya should be recorded for posterity. \textsubscript{06/22/14 11:31pm}}



Morgan leaves.  Hayley sits there thinking and Swan enters.  He releases her from the rest of her restraints.  She smiles at him and hops out of the bed.  She cries out when her leg collapses unexpectedly under her and she falls.

Swan is alarmed.  Hayley says that her leg hurts but neither of them can find any obvious injury.

``I can do a scan, a CAT scan if you like, but it will take some time to get that ready.... do you want to lie down?''

``No, I am used to this kind of pain.  I can handle it.  Can I go now?''

``Er- what?''

``Do I need to stay?  Can I go now?''

``I suppose so.  If you're feeling up to it.''

``My physical state is recovered enough that I can be discharged.  Please inform anyone who asks that I will be in the Cistern.  Oh- is Signe here?''

``She just left.''

``Oh.  Well please tell her that I would like to see her.  I miss her.''

``Okay.''

Hayley gets dressed in a jumpsuit and limps away, her rifle slung over her shoulder.




\sceneHeadline{Cistern- Hayley, Larissa and Rook}

She heads to the Cistern but finds the door to it locked.



She pages Swan who tells her to talk to Agent Rook.  Hayley calls Ops and reaches Larissa.  Hayley requests access to the Cistern.  Rook is not available to grant access and Larissa can't do it herself.  

``Please pass my request on to Agent Rook then,'' Hayley requests politely.

``I will but he's not here.''

``Then as soon as possible, please.''

``It's- It's against protocol to let you in without permission.  I can't-''

``It's okay.''  Hayley thinks for a moment and then pages Larissa again.  ``I would like to request access to the Requisition Cage please.''

``What?  Um, may I ask why?''

``I'm going to get the tools I need to access the Cistern.  That way you do not have to get in trouble.''

``Um, please hold.  I will pass your request along right away.''

``Thank you,'' says Hayley politely.

``Um, will you be returning to your bunk?''

``No I'm fine here, next to the Cistern.  Thank you.''



Hayley sits outside the Cistern for three hours.  She spends the time studying the door for weaknesses and working on a plan to open it.  Sometimes she just sits there, leaning against the Cistern door, with her eyes closed, rifle lying across her lap.



Rook steps out of the elevator and greets Hayley, ``Agent''

``Agent,'' she nods back and stands.

``I received a confused request.  Are you in distress?''

``Yes,'' says Hayley.

``Why here?  Why would access to the Cistern make you feel better?''

``It's safe in there.''

Rook thinks about it for several moments and then asks Hayley, ``I can give you temporary access.  The debrief is in one hour.  I expect you to report to the Ops room for the debrief.  Is that understood?  Can you do that?''

``Yes.''

Rook opens the door and Hayley steps inside.




\sceneHeadline{Bunk- Jaya and Hayley}

A few minutes before the debrief, Hayley shows up at the bunk.  She helps Jaya get dressed, and gets dressed herself in a TA uniform (and shoulders her rifle again).  They don't talk much.




\sceneHeadline{Ops}

Morgan and Dr. Gerhauser are not there.  Larissa, Micah, Rook, Victor and Trenton are there.  On the screen is a dossier with an ID picture of Oliver.  Lots of information on Oliver is scrolling by on the screen.



Jaya sits down next to Rook and tries to ignore Trenton.



Hayley comes to a complete stop when she sees the screen.  She smiles when she sees the commendations.  She mostly ignores everyone in the room and does not sit down until Jaya motions to her to sit down.  Instead of sitting with her team like usual, Hayley just sits down in the chair closest to her, all of her attention seeming to be drawn to the screen.



Rook begins the debrief by saying that they had identified the location of Operator Langdon.  

Rook addresses Jaya, ``As the commanding officer, please give the report.'' 

``The hell I will!  We need a debrief.  Where the hell were you sending us?''``Do you want this on the record?'' asks Rook.

``Yes!''

Hayley laughs suddenly at something she reads on the screen, not even noticing that she interrupted the conversation.

``Would you repeat the question?'' asks Rook.

``Where the hell did you think you were sending us?''

``It was a Search and Rescue mission.  The Search phase of the mission-''

``Where is he?  Where is his body?'' demands Jaya.

``Perhaps it would be best if Trenton explained,'' says Rook.

``Bear with me a moment while I try to find a way to explain it so that you will understand.  So everything you see, the world around you, looks basically flat.  Now imagine a circle.  The Directorate is on the surface of a large ball.  This ball orbits around a sun.  This sun is part of a collection of more stars...and there are even more places beyond that.  \hl{Now imagine a place with fewer stars.}\footnote{\textbf{Suko T }This sounds odd here, so I know I'm missing some astro-babble but I wanted to include the bit about ``fewer stars'' because it leaped out to me as something interesting when Nate said it. \textsubscript{06/22/14 2:42am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }You did a pretty good job transcribing the astro-babble. :) But yes, he said there was a place with very little indeed, that was a very large volume. \textsubscript{06/22/14 11:14pm}}  It is really really far away.''

``How can he be there?  We just saw him a few days ago,'' asks Jaya.

``It is possible to open a tunnel between the places,'' says Trenton.

``Why don't we do that?'' asks Jonah.

``The holes are like....bullets traveling from one place to another and we don't have a big enough gun.''

``Why don't we have a big enough gun?''

``Forget the gun analogy.  We don't have the resources to-

``Let's get back on track,'' interrupts Rook.

``Yeah, I still don't know where he was. Where was he?  Why was it so weird?'' asks Jaya.

``In order to do what they were doing, they put him somewhere with less stimulus,'' replies Rook.  ``It needed to be a place with no external stimulus.  Drugs wouldn't work because they don't stop you from thinking.''

Jaya nods in agreement on that point.

``But why would that do that?'' asks Jonah.

``We believe they were erasing him.''

``Yes.  They were taking his memories,'' says Hayley, speaking up for the first time. 

``What do you mean by that?'' asks Rook.

``Wait.  Do you mean you couldn't see what we were seeing?'' asks Jonah.

``Well in a sense we could,'' says Victor.  ``It was coming through the scan filter, but we couldn't see exactly what you were seeing, no.  By the way I just wanted to say you did a brilliant job.  Brilliant.''

``My colleague is correct,'' says Trenton.  ``We know where the body is.''

``You never thought we would get him out,'' says Jonah.

``We thought we could. But he is too far away.''

``Well you fucking better well try!  We don't leave him out there, we're bringing him back.  We don't leave our team members behind,'' says Jaya.

``We have the energy and resources to open a portal to where he was, but we could not get you back.'' says Rook calmly.

Jaya has no reply.

``Why couldn't we just wait until they come with their portals and simply jump through them?'' asks Hayley.

``No, that's a suicide move,'' says Jaya.  ``We'd be going straight to them.  They'd just kill us.''

``They didn't kill him.  Not right away,'' argues Hayley.

``We wouldn't know where the portal was headed,'' says Rook.  ``And we suspect that he was moved from the place he first arrived at through the portal.''

``Where did they move him?  And why?'' asks Jonah.

``There are places that are entirely empty of everything.  Even air.'' says Rook.

``You can't breathe?'' asks Jonah.

``Well they likely left him with something to allow him to breathe, but once that ran out-'' says Rook.

``He suffocated,'' Hayley finishes, quietly.

``Why?  Why did they do this?'' asks Jonah.

``We think this is what they did to Astarte,'' replies Rook.  ``Something to break them down so they can be absorbed into the rest.''

``So we all lose,'' says Jaya.

``Well when they reconstituted-''

``Reconstituted!'' interrupts Hayley.  ``Signe was reconstituted. What does that mean?''

``Signe?  Are you sure?'' Rook looks over at Micah and Micah leaves immediately.

\hl{Trenton has been trying to avoid acknowledging that Hayley is in the room but at this he glares at her with a look dripping with hatred.}\footnote{\textbf{Nathaniel Ford }Slight retcon here, because Trenton should have reacted even more strongly but I was in too many headspaces at once:

Trenton actually moved to get up from the table, but Rook made a calming/sitting motion and he begrudingly sat down again. \textsubscript{06/22/14 11:17pm}}\footnote{$\rightarrow$\textbf{Suko T }I am utterly fascinated to see how Trenton's going to resolve this, since I know that Hayley's just going to keep naively doing stupid shit like this. \textsubscript{06/22/14 11:34pm}}  

Hayley doesn't notice as she abruptly stands and says, ``please excuse me'' and leaves the room.



Jaya runs after her and finds Hayley crying loudly in the hallway.  Jaya tries to get her to calm down.  She orders Hayley to stop crying, and Hayley regretfully tells her that she can't obey that order.

``Sorry.  There's just too much.... stimulation here. It's so hard to think clearly,'' sobs Hayley.

``Hey, I have some drugs that will help with that,'' offers Jaya.

``No thank you.''

``But if it's too much stimulation, this will take the edge off.''

``But I have to feel it.  I have to feel everything.''

``No you don't.''

``Yes I do, otherwise it stays inside and poisons everything and I can't move forward.''

``No it doesn't, it gives you strength.  Anger is good, it makes you strong.''

``I don't like being angry.  Angry is confusing.''

``Well you can't be sad.  Just look at you, Hayley.  \hl{You can't shoot a rifle if you're crying}\footnote{\textbf{Nathaniel Ford }This really makes me want to have a scene where Hayley is despondently firing a rifle while weeping. \textsubscript{06/22/14 11:18pm}}\footnote{$\rightarrow$\textbf{Suko T }Ha!  The likelihood of this happening is higher than it should be :D \textsubscript{06/22/14 11:35pm}}, right?''

``No.''

``Maybe just pretend that you're not sad,'' says Jaya.

``I can't, I'm not good at hiding my emotions,'' sniffles Hayley.

``Really?'' says Jaya, sounding surprised.  ``Well then you just need to bottle it up and deal okay?  I need you to pull yourself together.  We're going to go on a mission.  You just do what you need to do to make that happen, okay?''

Hayley pauses and thinks, and then nods.  She wipes the tears away, tidies herself as best she can and limps back to the Ops room, with Jaya trailing after.



She sits down.  To Jaya's apparent dismay, she asks Rook ``I would like to request access to the Cistern.''

``You would need to clear that with medical,'' he replies.

``Understood,'' says Hayley and then sits back, closes her eyes and almost seems to go to sleep.

{[}...{]}

``Remember when we said that they had juked us?'' says Victor.  ``I was able to figure out what they did.  We know the frequency, we just need the equipment.''

``Where do we find this equipment?'' asks Jonah.

``We know somebody who knows where it is.'' says Rook

``Who?'' asks Jaya.

``Your 'friend' that you brought with you from SAC-01'' 

{[}...{]}

``What is the purpose of these places anyway?'' asks Jonah.

``The purpose of the Stand Alone Complexes is to guard against catastrophic failure of civilization.''

``And this counts?''``Well in some ways, actually, no.  If you look at it one way, this is the pinnacle of your civilization. If you look at it another way, you are quite destitute.''

{[}....{]}

``Oliver was further away than expected.  We think they took him somewhere and then moved him somewhere else.''

``What did we do to find him?''

``You accessed emotional cores that then sent information back to us.''

``What was your objective?  It wasn't to get him back.''``To thwart Octavian.  Their sister has destabilized their decision making ability, so it is a good time to strike.''

``What happens to someone that joins Octavian?  Can they be pulled out?''

``Dr. Gerhauser believes that it is possible to rehabilitate someone separated from Octavian.  Agent Gerhauser believes it is inhumane to do so.  That the person would just be pieces.''

``I was in pieces.  I put myself back together,'' says Hayley, opening her eyes.

``But are you the same as before?'' asks Rook.

``No.''

{[}....{]}

Jaya slams her hand down on the table.  ``I have lost a team member and several are severely damaged.  THIS IS NOT ACCEPTABLE.''

Jonah also yells a bit and then abruptly calms down.



Rook waits them out and then asks, ``Is there anything else to add?''

``Yes,'' says Hayley.  ``I know that Agent Parvadi thinks that I was imagining it, but I think that I may have been seeing through Octavia's eyes occasionally.''

``Octavia?  Are you certain?''

``Yes.  I have seen her.  She has met with Citizen Vorrutyer.  And I talked with her the last time.  Octavia was supposed to give Citizen Vorrutyer passage to Anglia to meet Lord Stanislav.''

``Do you remember what she said?''

``They discussed whether or not they were going to kill Citizen Vorrutyer.  They decided to torture her instead.  And I saw her kill Lord Stanislav.''

``You are certain that she killed him?''

``I believe so.  And I saw- I saw her start to cut into her-'' Hayley looks distressed and stops talking. 

``Interesting, especially considering the mission you would be going on.''

``What is this mission?'' asks Jonah.

``We believe it could be possible to tip the Directorate into opposing Octavian.  There is much discussion on that topic going on in Terminus.  But perhaps we will leave the mission briefing for later.''



As they stand to leave, the dossier has stopped scrolling.  Rook types something into one of the computers and the status ``K.I.A.'' appears on Oliver's dossier.









\underline{ \textbf{Quotes:} }



Rebecca: How many drugs will it take to get you to shut up?



Ion: Is Jonah feeling anything from Jaya?

Rebecca: You don't feel very happy.

Ion: Is that different from how\textit{ I} am feeling?

Rebecca: You want to hit someone.



Rebecca: There's a whole table between Morgan and Hayley

Suko: Won't make a difference.



Jaya: Rook!  Stone cold killer, man.  Fucking Morgan sent us in!  They knew.  Why did they do that?  They're just fucking with us!

Hayley: No, it worked!  We found him.

Jaya: What??  No!  Where's his body? He's gone.  Oliver's gone.

Hayley: I know he's dead.

Jaya: Okay good. He's gone.

Hayley: I brought him back with me.



Rook: Is Agent Hayley in emotional distress?

Jaya: Yes, she was crying.

Rook: Noted.

Jaya: But, uh, don't spread that around.  Special circumstances, you understand.

Rook: How very empathetic of you.



Swan: Agent, may I ask you a question?

Jaya: What?

Swan: Did you just arm my patient?''

Jaya: Oh, it's not loaded.



Micah: I heard a report of unauthorized weaponry in Medbay?

Jaya: It was medicinal weaponry

Micah: A rifle is not a tranq gun.




\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 3:36pm
\end{flushright}

