\setcounter{chapter}{ 28 }
\chapter{\textbf{``Terminus Rising'', part 3} }




\subChapterTitle{``Secret Agentman''}


\deets{Suko}{Aug 6th, 2014}



We meet the mysterious Agent Mohinder Lorentz!  Jonah decides to trust even more people.  Now that Lackovich is out of commission for a while, Jaya makes a new enemy, Agent Drake Malak. \hl{Hayley thinks he's hot}\footnote{\textbf{Nathaniel Ford }Really, Jaya's smartest course of action is to get Drake and Hayley on a date. Then Drake is dooooomed. \textsubscript{11/07/14 2:30pm}}\footnote{$\rightarrow$\textbf{Suko T }Absolutely.  One of the major reasons I believe Jonah will survive SAC-04 is that he refused to make out with Hayley. \textsubscript{11/08/14 10:55pm}}.



\jumpHeadline{Terminus}



\textbf{{[}12 Tokens in the pool{]}}



Hayley informs Jonah that he wasn't on the arrest warrant.  Jaya leads us to the rooftop of a restaurant so we can talk in (relative) privacy.  {[}\textit{Challenge 2: Convince people that we're on official TA business.  Concealment 1 (Jonah) + Agent 1 (Jaya) }\textit{) → Matched}{]}


\sceneHeadline{Rooftop}

There is a small garden on top of the building.  There are some chickens in a cage and a few klipspringers on chains.  There is a small Incorporated boy tending to the garden.



Jaya and Jonah radio Jari.  They tell him that Senator Bennett is compromised and that he has Station Chief Vargas issuing an arrest warrant for Jaya and Hayley.  Jonah tells Jari that Marechenko has an offer.  He will back us if he gets proof of SAC-09's location.  Jari laughs and says, ``That will never happen.  I've known her for some time now and Morgan will never agree to that.''   {[}\textit{Challenge 2: Convince Jari to plead our case, despite his doubts..  Flaw 2 Owe Jari a favor (Jonah) → Matched}{]}.  Jari grudgingly agrees to go back to SAC-09 and do his best to convince Morgan that the payoff (Marechenko's support) is worth the price.  He says it will take him at least an hour and half to get to SAC-09 and back, assuming they don't keep him there while they talk things over.



Hayley looks at Jonah and seems like she wants to ask something but doesn't.``What is it Hayley?'' he asks.

``Are you still angry at me?'' she asks.

``No.  I'm just frustrated.''

``I'm sorry.  I'm trying...''

``Well you need to try harder!'' snaps Jonah.

``Don't yell at me!'' yelps Hayley and she starts crying.

``Oh Jesus.  Hayley- focus!  Stop crying.  Remember?  Keep it inside,'' says Jaya.

Hayley sniffles and the tears slow a little but she keeps looking at Jonah sadly.



Jaya wanders around the roof and then kills a klipspringer {[}\textit{Refresh: Left Arm 3 (Jaya)}{]} who was totally trying to nibble on her uniform.  The animals go crazy and the little boy runs down the stairs.  Hayley attempts to clean Jaya's uniform with the rest of the water in her Canteen.  {[}\textit{Refresh: Dress Uniform 2 (Jaya)}{]}. And older man rushes out onto the roof and is upset over the dead klipspringer.   {[}\textit{Challenge 2: Get old man to chill.  Grim Visage 2 (Jaya) → Matched}{]}.  Jaya just glares at him intimidatingly and he backs down and goes away.


\sceneHeadline{Terminus Station}

Jonah says he will go to the TA station and try to find out if they've heard about Jaya and Hayley's arrest warrant yet, and suss out what's going on.  He heads to the TA Station and is waved through easily after showing his badge.  He asks ``Everything normal?''  The constable says that things are not normal- lots of Agents coming through.  A group earlier, then another one just now who went to go see the Station Chief.



Jonah goes to SC Ogleby's office.  The secretary stands up and says, ``They said you'd be back.  Please go right in.''  Jonah enters the office.  Ogleby is sitting at his desk.  Standing in front of the desk is a shortish guy in a plain uniform.  

Ogleby nods to Jonah.  ``Operator.  Glad you could join us.''

The man turns to Jonah.  ``Operator, Agent Lorentz has sent for you.''

``Where is the rest of your team?'' asks Ogleby.

``They are pursuing other avenues of inquiry but can be contacted if necessary,'' says Jonah.

``Agent in Training here is was going to take you over to HQ.''

``I can get in contact with them and arrange for a rendezvous,'' says Jonah.

``Very good,'' says Ogleby.

{[}\textit{Challenge 1 Notice. Sent back}{]}

{[}\textit{Refresh Vigilant 3 (Jonah)}{]}  Jonah notices an unusual level of weapons being readied and loaded and the two men in the room are very tense. 

``Let's get going.  Or do you want me to bring them here?'' Jonah asks.

``Would it be easier to pick them up along the way?'' asks the Agent in Training.

``It is somewhat up to you, but I can bring them back here.''

``Ah so I should wait here?''

``Yes.''

``I didn't quite understand.  Very good then.''

Jonah leaves and notices that neither Jaya nor Hayley's name are on the arrest warrants list posted in the main room.  The train scheduler seems very busy.


\sceneHeadline{Rooftop}

Jonah arrives back at the rooftop.  The rooftop is much noisier than when he left it, the chickens are calming down a little but the klipspringers are still upset about the dead body of their fellow herdmate.

``You came back!'' says Hayley, looking relieved.

``You're not on the warrants list,'' Jonah tells Jaya.  ``There was an Agent in training there who was going to take us to Lorentz.''

``Why didn't you go with him?'' demands Jaya.

``Because it could have been a trap and then I wouldn't have been able to report back to you about what I'd found out so far.''

``So what's the deal?''

``I was going to bring you to him but now I think it might be better to get him and bring him to you.''

``Yeah!'' says Jaya with relish, ``Then we can ask him...questions.''  She flexes her mechanical arm.

``How about we meet him part way between here and HQ?'' Jonah asks Jaya.

``Sure.''  They decide on a plaza area on the way to HQ.



Jonah leaves and gets the Agent in Training.  They walk to the agreed-upon meetup location.

``So you work under Agent Lorentz?'' Jonah asks Agent in Training.

\hl{``We all do}\footnote{\textbf{Nathaniel Ford }Ooh! Nice dodge, Nate! \textsubscript{11/07/14 2:34pm}}.  Well, apparently except you.''

``Yes we're in a group originally headed by Morgan.''

``Interesting phrasing.  You're a doctor, aren't you?''

``In a way.  What do you do?''

``Detective work mostly.  Looking into things.''  The Agent in Training points, ``Those your friends?''



Jaya is grinning at the children in the plaza and scaring them.  Hayley has her helmet on and is scanning the crowd with her Heads-up Display.  {[}\textit{Challenge 3 Notice.  Heads-up Display 4 (Hayley) → Overcome! }\textit{\textbf{3 VP (Hayley)}}{]}.  Hayley spots Jonah (of course) and scans the man next to him.  She notices that he is not wearing any armor or weapons.  And there is a bit of short grey hairs on the shoulder of his jacket (the man is not greyhaired).  Her understanding proper dress is put on high alert.



Before Hayley can tell Jaya what she sees, they are already within hearing distance.  

\hl{``Agent Parvadi,'' he says, ``I am an Agent in Training.  It's good to meet you.''}\footnote{\textbf{Nathaniel Ford }Somewhere in here AiT asked if Jaya had a medic look at something. I forget where it actually got mentioned. \textsubscript{09/02/14 4:01pm}}

Jaya nods.  Hayley moves to interpose herself protectively between the three of them and the crowds in the plaza.  She turns to the man.  ``Pardon me, but as you have no weapons or armor, I must try to protect you also.''

``That's very generous of you,'' he says.  Hayley just nods and turns back to survey the crowds.

``I don't think we are in any danger,'' Agent in Training says to Jonah and Jaya.

``Octavius is everywhere,'' says Jonah, watching carefully for a reaction.

``You mean Octavia?''

``I hope she dies,'' says Hayley clearly.

``Ah, that may be an opinion you wish to keep to yourself,'' says Agent in Training.

``I think she knows,'' says Hayley.

``She killed our teammate,'' says Jaya.

``And tortured Ms..... others,'' says Hayley.

``As you can see there are some things we need to talk to the Agent about.  We need to speak to him,'' says Jaya

``I'm surprised that Morgan didn't come herself,'' says Agent in Training.  ``I heard you just lost a teammate.  I'm sorry.  Are you okay?'' asks Agent in Training kindly.

``Yes,'' says Jaya.

``No,'' says Hayley.


\sceneHeadline{Transit Authority HQ}

We approach the \hl{TA Agent HQ}\footnote{\textbf{Nathaniel Ford }Note that this is the TA Agent HQ, not the TA HQ, which is a bit more decentralized or more accurately places as the Security Triumvirate. \textsubscript{08/11/14 9:58am}} building.  It has been riot-proofed and somewhat upgraded.  Jonah is very nervous and some of it is leaking through to Jaya.  {[}\textit{Challenge 1 Notice.  Streetwise 1 (Jonah) → Matched}{]}.  Jonah notices that there are people up on the\hl{roofs of nearby buildings}\footnote{\textbf{Nathaniel Ford }Important to note the people in question were in nearby buildings, not TA HQ. \textsubscript{08/11/14 9:57am}}.



{[}\textit{Refresh Ladies' Maid 2 (Hayley)}{]} Hayley suddenly moves toward the Agent in Training.  She raises a hand to brush at his uniform and says, ``I'm sorry I just-''  Before she can even touch him, he grabs her arm and smoothly flips her to the ground.  Hayley goes down without any resistance.  He holds her arm and neck at an uncomfortable angle, immobilizing her.  Hayley doesn't try move or resist and is very still. 



{[}\textit{Refresh Social Chameleon 4 (Jonah)}{]} Jonah draws on Agent in Training, ``Let her go!'' he demands.  ``What the fuck?'' says Jaya.  

Agent in Training looks at Jonah.  ``Lower your weapon.''

``Let her go,'' repeats Jonah.

``Lower your weapon.''

``On the count of three, I'll lower my weapon if you let her go.''

They count slowly and Jonah lowers his gun when Agent in Training lets Hayley go.

Hayley says, ``My apologies.  It's just that you had some hair on your uniform and I was tidying it.''  

``What the fuck Hayley!'' says Jaya.

``Let me go in and calm them down,'' says the Agent in Training and steps into the building.

``What the fuck was that?'' Jaya asks Hayley.

``It was bothering me.  It was so....unkempt..'' Hayley.  ``I wouldn't have let you enter into an official building looking like that.''

``But that's me!  On someone else, you just leave it there.  I mean seriously Hayley!  What the fuck were you thinking?  That could have been really bad.''

``This is why I reported myself unfit for duty,'' says Hayley, looking like she's going to cry again.

``Well just pull yourself together okay?  Don't do that kind of shit again,'' says Jaya.



\textbf{{[}7 Tokens in the pool{]}}



\textbf{{[}Agent Mohinder Lorentz Activated.  20 Tokens enter the pool{]}}



We enter the building.  An Agent at a desk, Agent Frederick, asks to see our badges.  ``You're Agent Parvadi?  Your reputation precedes you,'' he says to Jaya.   Agent Frederick explains that there is a locker where we can leave our weapons.  We don't relinquish any of our gear or weapons.  Jaya struts down the hall to the next floor.



We reach a Fili at a desk.  ``We're here to see Agent Lorentz.  Can you point the way?''

``May I see your Badges please?'' asks the Fili.  She checks them and then says, ``Room 301 in the main conference area.''  She points down the hall.



We go down the hall and enter a large space. There is a stairway leading up to the next floor.  In the middle of the room, between us and the staircase, is a tall, broad shouldered man.  He is square jawed, clean shaven and has a truncheon and sidearm.  He's extremely good \hl{looking}\footnote{\textbf{Nathaniel Ford }Despite evidence of scarring on his face. \textsubscript{08/11/14 9:59am}}\footnote{$\rightarrow$\textbf{Suko T }Hayley's learning to accept some (small) level of imperfection. :)  And he's still better looking than most of the people she's around, especially since she's not supposed to see Signe or Trenton anymore and Octavia's evil.  Life is so hard for an asthete in the Directorate. ;D \textsubscript{08/11/14 11:09am}} and Hayley finds him very attractive.  His Agent badge says Malak.  He looks us over and his gaze settles on Jaya.

``Good to finally meet you,'' he says.

``Uh, okay sure,'' says Jaya and starts walking past him.

``I heard you were in a fight.''

``I got put back together okay,'' says Jaya, pushing up the sleeve on her mechanical arm a little.

Malak sneers as Jaya passes him and seems a little disappointed that Jaya won't throwdown with him.

``She's a rude one,'' he says to Jonah.

``She's direct.''

``I'm surprised she's not dead yet.  You must do really good work.''``No, she's just that good,'' says Jonah.

``Agent Lorentz said you would be in a rush.''

``Yes.  But let's talk about why later, maybe over drinks.''  Jonah walks past Malak.

Hayley waits until Jonah passes Malak and then starts walking forward.  She nods to Malak politely but passes by without saying anything.  When she is almost past him, he says, ``Your strap is too short.''

Hayley stops and checks her straps.

``Your rifle strap.  It's half an inch too short.''

``Ah, thank you,'' says Hayley, adjusting it.  ``I haven't fully compensated for wearing it with the combat armor yet.''

``They said you were weird.''

Hayley pauses, thinks for a moment and says, ``Thank you.  I have been called much worse.''

Malak lets her pass without further comment but starts climbing the stairs after her.



On the next floor, there is another desk with a Fili seated at it.  Leaning against the desk is a woman. Her badge says Agent Vogel.  She is armed and her sidearm is definitely bigger than Jaya's.  The Fili requests to see our badges.  Jaya grumbles but complies.  Jonah also complies but only lets the Fili see it briefly, which surprises her a little.  Hayley obediently shows her Agent badge again.

``I have standing instructions to inform offenders of breaches of protocol,'' says the Fili.  ``You are required to salute superior officers.''

Jaya frowns and looks at Agent Vogel's badge.  ``How are we supposed to know who the superior officers are?''

\hl{``Agent Vogel outranks you by 3T levels,'' replies the Fili.}\footnote{\textbf{Nathaniel Ford }I forget if the squad actually saluted here? \textsubscript{08/11/14 10:21am}}\footnote{$\rightarrow$\textbf{Suko T }I don't know if Jaya did.  I think Jonah did?  Hayley probably did, especially once the Fili explained about Vogel's Agent ranking.  First to Vogel and then to Malak when Vogel called him Sir. \textsubscript{08/11/14 11:05am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Jaya saluted to Vogel but never Malak \textsubscript{08/11/14 11:31pm}}

Malak approaches and Vogel straightens and nods ``Sir''



Vogel starts walking away.  Jaya looks at the Fili and the Fili indicates that we are to follow Vogel.  She leads us to a set of double doors.  There is a guard armed with a pistol and a truncheon to one side of the doors.  To the other side of the doors is Agent in Training.



Vogel opens the doors with flair and walks right in.  Jaya, Jonah and Hayley follow her inside.  Malak also walks into the room, followed by Agent in Training.  Inside the room is a round table surrounded by comfy chairs.  Vogel and Malak sit, leaving an empty chair between them.  Jaya sits down next to Vogel.  



Jaya starts regaling Vogel with some of her war stories {[}\textit{Challenge 2: Make Vogel think Jaya is a badass.  Truncheon 2 (Jaya) → Matched}{]}.  Jaya waves her truncheon around for emphasis and demonstration.  Vogel listens and seems interested in the stories.  Malak seems to be mostly watching the truncheon.



Jonah waits to sit to see what Hayley does but she is watching Agent in Training.  When he stands next to the door, she takes a position next to the door as well and gestures politely for him to sit.  He gives her a curious look and doesn't sit down.  They both stand at the door, Hayley settling into a bodyguard stance.  Jonah eventually sits down next to Jaya, nodding to Malak and Vogel, ``Sir.  Sir.''  They nod in response.



``So where is Agent Lorentz?'' asks Jaya.

``You understand if we must take certain precautions,'' replies Vogel.

``We do understand.  Go ahead and ask us your questions, that's why we're here,'' says Jonah.

``Is Agent Morgan dead?'' asks Vogel.

``We don't know,'' replies Jonah.

Hayley coughs softly.

``We had reports that she was shot,'' says Vogel.

``We were not there.  We don't know,'' repeats Jonah.

``So Agent Morgan is in unknown condition.''

``Our superior officer ordered-'' says Jaya.

``Not Agent Rook?'' interrupts Vogel.

{[}\textit{Challenge 1: Notice.  Sent back to pool.}{]}

``Oh Rook is okay,'' says Jaya.

``We cannot verify the condition of Morgan and Rook,'' says Jonah.

Hayley coughs again, more loudly.  Jonah looks annoyed.

``Look, we cannot proceed without more assurances,'' says Vogel.

``We're not here to kill your commanding officer,'' says Jaya.

``We need to find out if you are not a part of the same threat that we suspect you are here to speak of,'' says Malak.

``Let's just talk then,'' says Jonah.

\jonahBrain{We need to do things that the enemy would find difficult, like caring about an individual}  thinks Jonah to Jaya.

``Well I'd like to haul Octavia out and shoot her in the head,'' says Jaya.  ``She killed Oliver.''

``Ah...Langdon,'' says Vogel.

``Officer Oliver Langdon,'' \hl{corrects Jaya.}\footnote{\textbf{Suko T }!!!  She really does care :) \textsubscript{08/10/14 1:07am}}\footnote{$\rightarrow$\textbf{Adam Kenney }Yes, she said his name correctly - wow! \textsubscript{12/02/14 6:13pm}}

``Operator,'' prompts Hayley from over by the door.

``Have you ever met one?'' Jonah asks Vogel and Malak.

``If, as you allege, that Octavia is one of these....things that we don't have a name for yet... then yes.  We have,'' says Vogel.

``Well they act funny.  Like a group.   All creepy finishing each other's sentences and shit.  Oh and when they die their faces get all melty and crap,'' says Jaya.

{[}\textit{Challenge 1 Notice.  Ladies' Maid (Hayley) → Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}  Hayley notices that Vogel looks over at the Agent in Training when Jaya says this and Malak looks at Vogel.

``Can you tell us what they look like?'' asks Vogel.

``Not really, I mean they look like regular people at first.''

``This is a waste of time,'' says Malak.

Jaya glares at him.  ``This is fucking important!''

``I can take you, little girl,'' taunts Malak.



Jaya rises to the challenge and they armwrestle.  {[}\textit{Challenge 4: Beat Drake Malak at Armwrestling.  Left Arm 3 (Jaya) + Flaw 3: Rivalry with Drake Malak (Jaya) → Matched}{]}.  Jaya puts up more of a fight than Malak expects and then she starts winning. He strains but she inexorably pushes his hand toward the table. Just before it touches the table he \hl{ragequits}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{08/11/14 11:34pm}}.  He pulls his hand away and pushes away from the table violently, breaking his chair.  He storms over to the window and does several rage man poses \hl{to express his feelings}\footnote{\textbf{Suko T }\textless 3 \textsubscript{08/11/14 11:53pm}}.  Hayley unslings her rifle and holds it at the ready, not pointed at anyone but watching Malak carefully.  Malak takes a few deep breaths and then returns to the table, a bit calmer but still angry.  He says to Jaya grudgingly, ``Impressive, Agent.''  He pulls up another chair to sit in.   ``I concede.''

``Most people do,'' says Jaya smugly.

Jonah is watching Vogel and Malak carefully.  Vogel's attitude is mostly indulgent, she seems impatient with the headbutting, but accepts that this is part of his process.  Malak is pissed that he lost.



``Speaking of impressive,'' Jonah says to Vogel and Malak, ``that was sufficient proof to me that you are not the enemy.  So I would like to explain some things.``

``Please do,'' says Vogel.

``Our experience is not so much in fighting with the enemy directly but in our insight into the way they think.  They don't do things like that, with individuals striving against each other.  They just don't have any interest in what we do.  We are like children to them.''

``So they look down on us.'' says Vogel.

``Yes.''

``Why do they even bother with us then?''

``Resources,'' says Hayley , still standing by the door, although she re-slung her rifle when Malak sat down and conceded the match.

``Do you mean as food or for services?'' asks Vogel.

``Both.  Anything they need,'' says Jonah.

``But what is it about us specifically that they are interested in?''

``Our structure,'' says Hayley again.

``Explain,'' says Vogel to Hayley.

Hayley takes off her helmet.  Malak notes her pretty face with surprised interest.  ``Our social structure is set up so that much of the population is controlled by a few, making it easy for them to control everything,'' says Hayley.

``And we are completely outgunned,'' says Vogel.



``Are you comfortable with us meeting Agent Lorentz now?'' asks Jonah.

``Yes,'' says Vogel.

``We want to meet him, is he here?  Can we speak to him? Or are we speaking to him now?'' asks Jonah.  Jaya glares at Malak.

Agent Lorentz (aka Agent in Training) sits down at the table.  Hayley smiles and sits down also (next to Jonah), though only after Lorentz has seated himself.

``So, either we go toe to toe and get our asses kicked,'' says Vogel and she looks at Malak who glares. ``Or we wait it out like herd animals.''

``Terminus is already compromised, Octavius has agents here,'' says Jonah.

``Like who?''

``Senator Bennett.  Agent Parvadi and Hayley have established that he is an Agent of Octavius.''

``And that leads us to our second problem,'' says Vogel.  ``Say we go toe to toe and win by some miracle.  What happens then?  How many of us will actually survive?''

``Sometimes sacrifices are necessary,'' says Jaya.

``What kind of numbers are you talking?  50\%?'' asks Vogel.

``More like 60\%'' says Jaya.

``Alright say that we lose 60\% of all active Agents.  We will have a highly weakened TA.  We have Compromised Senators.  What happens afterward?''

``I'd like to talk about Oliver,'' says Jonah.  ``In Nicklepan, a) there was no one left and b) they didn't fight.  Two, what happened to Oliver was-''

``Hayley can describe it best,'' says Jaya.

``If she can,'' says Jonah.  ``Can I summarize?''  Hayley sniffles but says nothing.  Jonah continues.  ``Anything they don't need, they kill.  Those are the lucky ones.  Everyone else is sliced and dissected, pulled apart, dissolved, their memories erased and-''  Hayley is looking increasingly distressed and seems to be having trouble breathing or speaking.  

Jaya interrupts Jonah, ``The important thing is that even the ones that live are fucked up.''

``And what can we do against something like that?'' asks Vogel.

``We have a lot of tech advancements at SAC-09,'' says Jaya.

``They're not enough.  And beyond that, we'll still get hit when we are weakest afterward,'' says Vogel.

``I don't know much about politics, but we don't have to let them know how weakened we are,'' says Jonah.

``So you mean to bluff?'' asks Vogel.

``They don't want to fight because it costs them resources, but they'll do it if they need to,'' says Jonah.

``You know how the TA works, correct?  You have your beat cops who keep the populace in line. They distribute the water so that people don't riot.  The stations are a chokepoint.  Without them, no one gets fed.  Morgan fucked us on that.  Transit Minor was a major chokehold and it's gone now.''

``But that did keep the enemy from using that station to get to us,'' says Jonah.

``I'm not disagreeing with the strategy, I'm just saying that she should have checked with us first so we weren't caught unaware,'' says Vogel.  ``Anyhow, if you control the stations, you control the flow of water.  Then there is the space between the stations.  That space is information.  The control of information is what Agents do.  The Senate does nothing without us. If we're fucked, this \textbf{all} goes down.  HQ is a huge magnet for attention.''

``Can't you go somewhere else?''

``We need a location where we can work from and strategize.''

``Excuse me, may I ask a question?'' says Hayley.  Vogel nods.  Hayley asks Jaya and Jonah, \hl{``What about the other SACs?  Could we use them instead?  Put people there and hide them?''}\footnote{\textbf{Rebecca S. }poor Hayley.  All the brain power and no one is listening (or at least giving her credit) \textsubscript{08/11/14 11:37pm}}\footnote{$\rightarrow$\textbf{Suko T }Nobody listens to Zathras. \textsubscript{08/11/14 11:54pm}}

Agent Lorentz speaks, ``Hmm... so you're saying we underplay our hand and maybe siphon off Agents secretly to another location?  Claim they were killed in battle and reassign them?''

``I don't know about that but I do know that if you seem vulnerable and weak they will often hurt you less,'' says Hayley.

``Do you know about Tertius?'' asks Jonah.

``No, what does that have to do with this?'' says Lorentz.

``Hayley can explain it best.  Tell them about Tertius, in one or two sentences, Hayley.''

Hayley looks alarmed and starts thinking hard.

Jaya sighs and says, ``Hayley, use as many words as you need to, okay?''

Hayley looks relieved.  ``Tertius is an entity like Octavius,'' she begins.

``Another one?  There are more?''

``Yes, there are actually hundreds, maybe thousands of them.''

``What??''

``How many named ones, Hayley?'' asks Jonah.

``Oh. There are only two named entities like them that I know of.  They are each made up of many...constituents.''

``Ah.  Continue.''

``Tertius was here in the Directorate.  Probably for some time.  Redemarrer was responsible for making constituents for Tertius.''   Lorentz seems to be familiar with the name Redemarrer.

``Sir, do you know anything about Redemarrer?'' asks Jonah.

``It was primarily import/export.  They didn't do well after the war and it was broken down and sold off,'' says Lorentz.

``Do you know if Redemarrer was part of the Directorate?'' Jonah asks Hayley.

``I don't know.  I didn't know about the Directorate until after I left the Island.''

``When did you leave the Island?''

``When I was sold.''

``Do you think Tertius is still there?''

``I don't think so, everything seemed to be removed.  I watched them carting off equipment and we were all sold off.''

``What is the point of discussing all of this?'' asks Lorentz.

``Because Octavius killed Tertius, or at least we think so,'' replies Hayley.

``It shows that these things can be killed.  We don't know how yet, but we know it is possible,'' says Jonah.

``What do you suggest we do next then?''

``Sir, may I ask a question?'' Hayley asks Lorentz.  Lorentz looks amused and gives permission.  Hayley asks him, ``If the Agents have control of the Senate, can you get them to delay this upcoming vote?  It would give you time to set up the bluff.  They wouldn't have to decide to resist, they just cannot be allowed to vote to ally with Anglia.''

``Yeah, what about some sort of legal attack?'' asks Jaya.

``Let me think about that,'' says Lorentz.

``We could get you access to SAC-09,'' says Jaya.

``That would be...\hl{contentious}\footnote{\textbf{Nathaniel Ford }He strongly indicated he considers SAC-09 Morgan's turf, and therefore not entirely safe for him. \textsubscript{08/11/14 10:32am}}.''

``Well we do have the resources that know the locations of more places like SAC-09,'' says Jaya, \hl{rather smug with herself and obviously believing she has just come up with the idea despite the fact that Hayley just suggested it about five minutes beforehand.}\footnote{\textbf{Suko T }Which means that Hayley is doing her job correctly, so it is all as it should be :D \textsubscript{08/11/14 11:54pm}} 

``So you're saying we go reclaim some of these locations together and set up our base of operations there?''

``Well we did just lose a team member, it would be good to have a larger group to get that done.  How soon can you get us the resources?'' asks Jaya, looking excited.  She makes repeated references to forming an\hl{elite fighting force-}\footnote{\textbf{Suko T }Yes!  How could I forget this?  The best part of this discussion...after the arm wrestling. \textsubscript{08/11/14 11:55pm}} the stars in her eyes clearly conveying that she would expect to lead such a team.  Jonah's brain whispers are not helping dissuade her of the idea. 

``You're hilarious,'' says Vogel.

``What about your Praetor?'' asks Lorentz.  We look at each other, not knowing the term.  

Jonah attempts to bluff, ``They are fine with it.''

``What does Rook say?'' asks Lorentz.

``They have given us the authority to complete our mission,'' says Jaya.

``Well this answers a lot of questions,'' says Lorentz.  He nods to Vogel and Malak.  ``Agents.''  They nod to him and get up to leave.  Drake Malak glares at Jaya and says, ``Later.''  He smiles at Hayley, who smiles back happily.



Once they leave, Lorentz leans forward.  ``I would like to clarify some personnel matters.  If you prefer, we can do this individually.''

``Anything you have to say, can be said in front of the whole team,'' says Jaya.

``Very well,'' says Lorentz.  ``I take care of my Agents and I haven't had a chance to talk with any of you yet.  I would like to know what you see as your position after the war?''

``What do you mean by that?'' asks Jonah.

``If you are not in this for more than the immediate fight, you are worthless to me.  I wish to know what you intend to do in the future.''

``I don't know sir but my main concern is my family.''

``Ah.  Give me their names and I will get them somewhere safe.''

Lorentz turns to Hayley, ``And what do you want to do in the future?''

``Whatever I am ordered to do.''

``That is not answering the question- what do you want to do in the future?''

``Whatever my contract holder tells me to do.''

``Your contract holder may be dead.''

Hayley is distressed at the thought but answers, ``My contract should pass to the next person who-''

``And if it doesn't?''

``Then it is sold-''

``And that's still not answering the question.  Have you considered becoming Franchise?''

``No, I don't know what that would mean,'' Hayley looks at Jaya and Jonah for help.  ``Is that the wrong answer?  I don't- I've never-I never thought about the future like that.  I don't know what the answer is.''

``Maybe you should think about that.''

``Okay but I'm not very-''

``Hey, stop questioning the girl.  She doesn't know, okay?'' interrupts Jaya.

``My apologies,'' says Lorentz.  He then queries Jaya on her hopes and dreams and gets back a rather dry response about serving the TA while also embracing the chance to perhaps ``fuck shit up''.  \hl{He claims this reminds him of Malak, which of course Jaya pulls a face at.}\footnote{\textbf{Suko T }HA!  Awesome. \textsubscript{08/11/14 11:55pm}}

``Do you have any messages that we can take back to Morgan?'' asks Jonah.

``Yes.  Tell her-''



And there is a large explosion.





\textbf{{[}20 Tokens remaining{]}}




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 12
\item Challenge 2: Convince people that we're on official TA business.  Concealment 1 (Jonah) + Agent 1 (Jaya) ) → Matched
\item Challenge 2: Convince Jari to plead our case, despite his doubts..  Flaw 2 Owe Jari a favor (Jonah) → Matched
\item Refresh: Left Arm 3 (Jaya)
\item Refresh: Dress Uniform 2 (Jaya)
\item Challenge 2: Get old man to chill.  Grim Visage 2 (Jaya) → Matched
\item Challenge 1 Notice. Sent back
\item Refresh Vigilant 3 (Jonah)
\item Challenge 3 Notice.  Heads-up Display 4 (Hayley) → Overcome! \textbf{3 VP (Hayley)}
\item Challenge 1 Notice.  Streetwise 1 (Jonah) → Matched
\item Refresh Ladies' Maid 2 (Hayley)
\item Refresh Social Chameleon 4 (Jonah)
\item Pool: 7+20 (Lorentz)
\item Challenge 2: Make Vogel think Jaya is a badass.  Truncheon 2 (Jaya) → Matched
\item Challenge 1: Notice.  Sent back to pool.
\item Challenge 1 Notice.  Ladies' Maid (Hayley) → Overcome! \textbf{1 VP (Hayley)}
\item Challenge 4: Beat Drake Malak at Armwrestling.  Left Arm 3 (Jaya) + Flaw 3: Rivalry with Drake Malak (Jaya) → Matched
\item Pool: 20
\end{itemize}




\jumpHeadline{VP Totals }

Hayley 4

Jonah 0

Jaya 0




\jumpHeadline{Quotes: }

\quotedDialog{
Jaya: ``I hate Octavius.  They killed Oliver.''

Nate: ``Whom you didn't like until that moment.'' \\[4mm]
}

\quotedDialog{

Suko: ``Her ego precedes her down the hall.''

Nate: ``Jaya is not one to let her ego get too far ahead of herself.''
}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 3:50pm
\end{flushright}

