\setcounter{chapter}{ 29 }
\chapter{\textbf{``Terminus Rising'', part 4} }


\subChapterTitle{``Sissorkicking Grenades''}

\deets{Suko}{Aug 13th, 2014}



Big \underline{  {\color[RGB]{17,85,204}Badaboom}  }.  \hl{Temporary detour into an episode of ER}\footnote{\textbf{Suko T }Gotta say Nate, I just love all these ``Tank'' scenes.  So wonderfully detailed and intriguing. \textsubscript{08/14/14 5:51pm}}.  Then the ladies kick ass and rack up a respectable bodycount.   Jaya kills someone through a wall and takes possession of a cool device.  Hayley scissor kicks a grenade out of the air and unintentionally flirts with Drake Malak.  Jonah asks lots of questions and makes an important decision.  Rook becomes even more awesome.  I didn't know that was possible.



\noindent\hrulefill





\textit{\textless start scene\textgreater }



\textit{There is an explosion, a feeling of vertigo and our vision goes...weird.  Everything's in high contrast and there's a staticky white noise buzzing in the background.  Jaya and Hayley are the most disoriented.  Someone is yelling at Jonah.  ``There's been an explosion in the plaza, wounded coming in to surgery room 3!''  We are in a modern hospital room, with nurses and people in scrubs.}



\textit{Jonah feels odd, a little distant, though any reflexive actions, particularly treating people, is relatively easy.  He is dressed as a doctor, his tag says Dr. Timon Natekar of George Washington Hospital, Ward 4.  He sees a woman in uniform, she looks like Jaya.  In the bed next to her is a teenager covered in }\textit{\hl{black markings}}\footnote{\textbf{Nathaniel Ford }This is more like soot and grime, and less like tattoos or someone took a sharpie to her. \textsubscript{08/15/14 5:23am}}\textit{ and bandages, but no other clothing, whom he doesn't recognize.  Next to her is an unconscious man in a marine's uniform with what looks like fiber optic cable shrapnel protruding from him.  The last bed is occupied by a absolutely stunning woman dressed in a very cute and more-than-a-little revealing business suit, with some burn markings and abrasions on her face who looks like Hayley.}



\textit{Jaya comes to, there is a buzzing weight on her chest.  She picks it up- it's a cellphone.  The cellphone has a picture of her (}\textit{no scars, no facial tattoos, with her ear back}\textit{) and a young girl.  Jaya stares at the phone in dumb confusion, letting the call just ring and ring.  Jaya's left arm is whole and hale.  She tries to get up and the nurse tries to get her to lie back down.  A nurse says, ``They were just at }\underline{ \textit{ {\color[RGB]{17,85,204}\hl{L'Enfant} } }\underline{ \textit{ {\color[RGB]{17,85,204} } } }\underline{ \textit{ {\color[RGB]{17,85,204}Plaza}} } }\footnote{\textbf{Nathaniel Ford }Hey! Jaya doesn't have Google! ;-) \textsubscript{08/15/14 10:57am}}\textit{, just brought in a few minutes ago.''}



\textit{The noise gets a bit louder.  }



\textit{Hayley comes to, she feels mostly okay, in fact even better than usual as her right leg seems fine now.  But she has this strong sense that she's lost something.  She feels around for the thing and can't find it. }



\textit{Jaya starts getting out bed, muttering and then eventually shouting ``No, no, no'' over and over again.  A big man who looks sorta familiar (can't make out his nametag) restrains her.  Jaya feels like yes she does still have some ink but there's another thought that maybe people might take it amiss...she has a position of responsibility after all (what?).  As soon as the caller gives up and the phone stops ringing Jaya tries to call them back, the man asks Jonah if he can sedate her.}



\textit{Hayley struggles to get up but the nurses say, ``You have to stay here, please lie back.''  Hayley obediently lies back and the nurses and interns relax their holds on her.  The moment they do, Hayley rolls off the bed and lands lightly on her feet.  Ignoring the alarmed reaction of the nurses, she goes toward a bag that she knows is hers and starts digging through it.  There are files in it with a university name on it and other names she recognizes.  She pulls out a book-sized device, looks a bit like a GPS but with a lot of modifications made to it.  On the side is a blue stick-on label that says }\textit{\hl{Dr. Hadef.}}\footnote{\textbf{Rebecca S. }mother fucking Trenton's last name. Noted because I'll forget that fact again \textsubscript{08/15/14 9:07am}}\textit{  Hayley feels that this is the thing she had lost and she's relieved to see it is okay. }



\textit{The nurses are demanding that ``Dr. Timon'' (Jonah) tell them what to do.  He tries to get them to lead the way but they make him choose who to start treating.  He yells in his head ``hey!  wake up!'' and feels a pull toward the marine.  He does his best to fake it and they start intubating the marine.  He says in his head ``Say the words!'' and does his best to repeat out loud the orders that appear in his mind.}



\textit{Jaya's really struggling now and Jonah gives permission for a mild sedative to be given, so long as she doesn't need to go into surgery.}



\textit{Hayley tries to power up the device to make sure it is still functioning.  She sees a bunch of numbers and graphs and appear, more than she has ever seen when the device isn't in test mode.}



\textit{The marine's uniform badge says Major Langdon, there are several ribbons pinned to his chest and a purple heart that somehow means something to you.  Jonah tries to remember what Mr. Langdon or even Oliver looks like and his body stops moving.  Jonah backs off and his body starts treating the patient again, although both Jonah and the person he is sharing the space with both think that the marine is terminal.}



\textit{A nurse approaches Jaya with a syringe of sedative.  The phone picks up, ``Mom? Is that you?''  Jaya frantically shouts into her cell ``Who are you? }\textit{\hl{Where are you}}\footnote{\textbf{Rebecca S. }This was meant in a ``where are you in the world, tell mommie so she can find you'' way and not in a ``I don't understand this device'' way. \textsubscript{08/15/14 9:48am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Noted! \textsubscript{08/15/14 10:58am}}\textit{?'' just before it gets taken away by a nurse.  The big guy holding down Jaya says ``Calm down!''  Both Jaya and the other Jaya in her head start freaking out (but for different reasons).  Jaya spits at the guy and thrashes around, knocking the sedative out of the nurse's hand.  The nurse curses.  Jaya may possible be foaming at the mouth at this point, and she is continues to shout and scream. }



\textit{Jaya looks over at the teenager next to her and the girl is looking at her, her eyes very centered and scary.  Jaya tries to remember what Morgan looks like and feels a sharp pain in her head.  }



\textit{The nurses are trying to get Hayley to get back in the bed and she insists that she's okay and she can discharge herself.  A resident corners her and gets her to sit down.  Hayley clutches the device to her chest and won't let anyone take it from her.  She tries to convince the resident she's okay but he keeps repeating that she's not allowed to leave.  He examines her and she also does a quick check on herself.  }





\textit{Jonah feels someone behind him.}



\textit{\hl{The girl gets up and starts booking it out of the room.}}\footnote{\textbf{Rebecca S. }I would like to say at this point I changed my prediction from ``Is that Morgan?'' to ``Of fuck, she's Octavius!'' out of game. \textsubscript{08/15/14 9:51am}}\footnote{$\rightarrow$\textbf{Suko T }I'd been thinking she was Signe up to this point (her being a teenager and all), but yeah, money on Octavius at this point. :) \textsubscript{08/15/14 11:21am}}



\textit{Jonah feels himself being pulled away and Jaya is very far away which distresses him.}



\textit{The white noise gets louder.}



\textit{Jonah tries to get away, but there is no ``away'' to go to.}



\textit{Hayley doesn't see the girl leave.  Remembering Dr. Gerhauser's instructions, Hayley asks the resident, ``What is your name?'' He replies, ``Doctor-'' but the rest is drowned out by the whining noise and Hayley's vision goes to white again.}



\textit{Jaya's vision whites out as she hears one of the nurses speaking to her daughter on the phone.}



\textit{\textless end scene\textgreater }



\textbf{{[}20 Tokens in the pool{]}}


\sceneHeadline{TA Agent HQ}

Our vision returns and we are back in the HQ conference room.  The scene in the hospital room seems \hl{hazy}\footnote{\textbf{Nathaniel Ford }Even more than hazy and dreamlike, it seems fragmented and disassociative - to the point where piecing it together is a struggle and feels like you're filling in arbitrary details. \textsubscript{08/15/14 5:26am}}, distant, and dreamlike.  The details are hard to recall.  It seems like only a few seconds have passed.



The explosion (which came from the wall behind Lorentz) has flung him over the table and he's unmoving on the floor.  There's debris, shattered glass, and dust everywhere and the wall of the conference room has slagged away.  



Jonah comes to and feels Jaya in his mind \textit{right there}, which is strangely comforting.



Jaya, not wearing combat armor other than her light vest, is not doing so well. {[}\textit{Challenge 2: Not be injured.  }\textit{Flaw 2: Injured right arm (Jaya)}\textit{ → Matched}{]}.  Her right arm is a really messed up- badly sprained but not broken- and she takes some time to repair her left arm as well {[}\textit{Refresh: Left Arm 3 (Jaya)}{]}.



Hayley stands up immediately, trusting that if she's too injured to stand, she'll find out soon enough.  She surveys the room, notes that Jaya's moving (fixing her arm), Jonah's getting up slowly and Lorentz is just starting to move.  She takes a protective stance over Jonah and Agent Lorentz.



Jonah moves over to Agent Lorentz, ``Agent Lorentz, how badly are you hurt?''

``Still assessing,'' he replies.

Jonah checks Lorentz over, who is doing his own self-check at the same time.

``My arm's messed up,'' yells Jaya. ``Jonah, get over here!'' 



Someone starts kicking the door down.  Hayley checks her rifle, makes sure her bag and extra ammo is in easy reach, and covers the door.  The door opens and the guard stationed outside \hl{rushes in}\footnote{\textbf{Nathaniel Ford }I was probably unclear; he didn't enter the room, instead using the doorway as partial cover to survey the scene. \textsubscript{08/15/14 5:27am}}\footnote{$\rightarrow$\textbf{Suko T }Because he's smart and has had training.  And actually paid attention during said training. \textsubscript{08/15/14 11:28am}}.  His rifle is ready but pointed down as he does a quick survey of the room.  Hayley watches him, ready to fire at him if needed.  The guard is followed shortly by Drake.  

``Drake.  Weapon.'' says Lorentz and Drake throws him a truncheon.

Hayley asks (in the general direction of Drake and Lorentz), ``Sir, do we dig in here or will we evacuate?''

``Secure the room,'' says Drake.  Hayley nods and starts looking around the room for which areas are the most defensible.



Jaya moves over to the new opening in the wall and looks outside.  {[}\textit{Challenge 2: Notice.  Binoculars 2 (Jaya) → Matched}{]}



Drake and Hayley join Jaya at the hole in the wall, taking up positions to either side of it.  ``What is in the second building on the right?'' asks Drake.  Jaya sees a guy in the building taking cover and some other people behind him.  She points them out to Hayley with an order of ``Shoot to kill'', and Hayley drops at least one of them before they find cover. There are also unarmed people in the street, oddly just standing there, dressed in Franchise clothing, looking really nervous.  But Jaya mostly ignores them for now.  Jaya continues to survey the rest of the building, relaying the info to Hayley.



{[}\textit{Challenge 3: Bandage Mohinder Lorentz.  Surgical Kit 2 (Jonah) + Street Medic 2 (Jonah) → Matched}{]}  Jonah bandages up Lorentz.



There is more shooting coming from elsewhere.  Jaya leans out to see where the shooting is coming from, exposing herself.  {[}\textit{Refresh: Adrenaline Junkie 2 (Jaya)}{]}.  {[}\textit{Challenge 2: Shoot guy aiming at Jaya. Rifle 2 (Hayley) → Matched}{]}  Hayley can see a guy aiming a rifle toward Jaya, but she shoots him before he can take his shot and he falls.



One of the guys in the building sees them too and aims a grenade launcher at them.  Jaya points him out to Hayley.  Jaya decides to jump down to the floor below to get more cover.  {[}\textit{Challenge 1: Jump down to second floor.  Adrenaline Junkie 2 (Jaya)  → Overcome! }\textit{\textbf{1 VP (Jaya)}}{]}



{[}\textit{Challenge 4: Shoot guy with grenade launcher before he can fire on us.  Saltaremachy 3 (Hayley) + Bodyguard 2 (Hayley) + Memory for Details 1 (Hayley) + Small Unit Tactics 1 (Hayley) → Matched}{]}.  Hayley does some quick calculations on how much cover is available for the people in the room, weighed against her memories of grenade blast radii from Nicklepan, and decides to try to take the guy out before he can fire.  She flicks her flashlight on and off which distracts him and causes him to pause for a crucial moment.  She fires at him and hits him, but he still gets the shot off.  Somehow exactly in the right place at the right time, as if she could track its trajectory exactly, Hayley spins, leaps and gracefully \underline{  {\color[RGB]{17,85,204}\hl{scissor kicks}}  }\footnote{\textbf{Nathaniel Ford }lulz \textsubscript{08/18/14 9:06pm}}, the grenade out of the air so that it explodes outside of the building.  Hayley and Drake absorb some concussive pushback, but there is negligible other damage from the blast.  Jonah, attending to Lorentz, misses what Hayley did entirely, but Drake sees the whole thing.



Lorentz reflexively raises the truncheon to protect himself.  {[}\textit{Challenge 1: Notice. Sent back to pool.}{]}  Jonah starts rebuckling on his combat armor which he had taken partially off so that he could attend to Lorentz {[}\textit{Refresh: Combat Armor 3 (Jonah)}{]}



Jaya disappears into the second floor and starts heading downstairs.  Hayley surveys the opposite building and then pings Jaya on the hush radio, ``Agent Parvadi, what is your current location?''

``Uh heading down to the exit on the ground floor.''

``What is the situation there, Sir?''

``Looks pretty good, I think we're about to head out and go around to that building.  I'll keep you updated.''

\hl{``Please do. Thank you, Sir.''}\footnote{\textbf{Suko T }I don't know how obvious it was, but after the explosion, Hayley's demeanor changed from the weepy mess she's been the last few sessions.  Her movements are confident and assured, her voice calm and professional.  There is not a moment of hesitation when she shoots the guys.  All that Small Unit Tactics training that Rook drilled into the team is coming into fruition now.  Also, she doesn't limp at all. \textsubscript{08/14/14 6:22pm}}



Jonah uses Operator to see through Jaya's eyes.  Vogel is by the main entrance, speaking into a hush radio.  There are many agents milling around, a few of them wearing armor.  Jaya asks for armor.  Vogel overhears it and says, ``There's no time for this shit.  Kick it.'' and the door flies open.  The group exits in precise military fashion.  Outside are other TA agents and several corpses.  Jaya pauses to root around under some of the corpses for a new truncheon.  {[}\textit{Refresh: Truncheon 2 (Jaya)}{]}



Back in the conference room, Jonah asks Lorentz if he has contact with the outside.  Lorentz says no, but Drake says yes.  ``I have contact with Parvadi,'' says Jonah.  

``Tell her to stay behind Vogel,'' says Drake.   Jonah nods but does not pass the message along.



Jaya and Vogel head down the street.  Jaya glories in feeling like part of an elite fighting squad.  One that she will soon be leading, of course. {[}\textit{Challenge 2: Notice.  Vigilant 3 (Jonah, through Jaya) → Overcome! }\textit{\textbf{2 VP (Jaya and Jonah)}}{]}.  Jaya and Jonah can see that the people standing in the streets are all Filis.  They are scared and it is taking a clear act of willpower to stay in place.  There's something \hl{Hayley-like}\footnote{\textbf{Nathaniel Ford }Strictly speaking, there is something Fili-like in the way Hayley follows orders, though she is perhaps an extreme case. \textsubscript{08/15/14 5:30am}}\footnote{$\rightarrow$\textbf{Suko T }''perhaps'' an extreme case?? :D \textsubscript{08/15/14 11:23am}} about them.   {\color[RGB]{74,134,232}::They're a distraction::}  Jonah thinks at Jaya.



Jaya and Vogel approach the building.  They breach the door.  Jaya says that the people were on the second floor.  ``We're in the building Hayley, What're they doing up there?'' Jaya asks Hayley over the radio.   {[}\textit{Challenge 1: Notice.  Sent back to pool.}{]}  ``I can't see anything through all the dust from the explosion.  Sorry, Sir,'' says Hayley.   Vogel indicates the stairs.  ``Would you like the honor?'' she asks Jaya.  Jaya heads up the stairs first.



Not realizing they are about to bust onto the second floor right now, Hayley starts reloading her rifle, readying herself to cover them.  {[}\textit{Refresh Rifle 2 (Hayley)}{]}



Jaya reaches the second floor.  She punches the door down and charges through.  There are two guys in the room, one of them has a device in his hands.  The other one is covering the door and opens fire.  {[}\textit{Challenge 2:  Avoid being shot.  Left Arm 3 (Jaya)→ Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}.  Anime-style, Jaya uses her mechanical arm to deflect the bullets and rolls into open door of bathroom in the room.  Jaya hears the sound of a \hl{single very loud gunshot}\footnote{\textbf{Suko T }Ah yes, Vogel's superior sidearm. \textsubscript{08/15/14 11:29am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Jaya would recognize the sound as being a gauss pistol, since she's used one of those before. \textsubscript{08/18/14 9:03pm}} and a body hitting the floor.



{[}\textit{Challenge 3: Kill guy through the wall.  Sidearm 3 (Jaya) + Small Unit Tactics 3 (Jonah)  → Overcome! }\textit{\textbf{3 VP (Jaya and Jonah)}}{]}.  Remembering where the other guy was and getting a bit of targeting assist from Jonah, Jaya shoots through the bathroom wall and unerringly hits the guy holding the device.  She hears a slumping sound.



Vogel says, ``Clear!''  Jaya comes out of the bathroom, offering her own non-committal ``Clear''.  The guy who was covering the door is missing half of his face.  Vogel tells her to check the other guy.  Jaya approaches the guy she shot.  She kicks away the device.  He didn't die immediately but he has several gunshot holes in him and pretty much bleeds out right in front of her.  Jaya picks up the device.  It's a small cylinder device, similar to the ones she has seen before, wrapped in fiber optic cables.  ``Motherfucker!'' she says loudly.  A soldier reports to Vogel that the rest of the building is clear.  Jaya lights up a cigarette and smokes.



Jonah tells Lorentz that he has a visual on the scene in the building across the way and describes the device to Lorentz.  Lorentz says it doesn't sound familiar but he'd have to see it to be certain.  ``This doesn't make any sense,'' says Lorentz.  ``Why would they attack here \textit{now}?''

``Could be a distraction.  What other areas might they have hit while we were dealing with this?'' asks Jonah.

Lorentz immediately tells Drake to go investigate that.

Jonah, Lorentz and Hayley then try to figure out how the attackers knew that they were in the conference room.  Lorentz has been using it quite a bit lately, it's true, but it was still not widely known.   Perhaps they were after us.  Hayley suggests that it would have been easy to follow us to HQ from the plaza, but then how did they know which conference room to hit?  They didn't get all of them, it was a precise hit to just this conference room.  Jonah wonders if the Filis have been compromised.



Jaya arrives and shows off the device ``she retrieved''.   ``\textit{You} retrieved?'' asks Vogel as she enters the room, sounding a little amused, but she doesn't contradict Jaya when Jaya says yes.  Jaya shakes it and both Jonah and Hayley reach out to stop her.  ``Those things are possibly impact sensitive, I would really avoid shaking it,'' says Hayley.  Jaya doesn't seem to acknowledge this but she does put it down more carefully.  Lorentz asks to see it and Jaya says he can see it but not touch it.  Lorentz carefully puts his hands behind his back and studies it. 



Jaya announces that we are going to take it back to SAC-09 with us.  Lorentz challenges her, saying it should stay here.  

``This is a dangerous device, possibly more dangerous than anything else here,'' says Jaya.

``All the more reason we shouldn't try to transport it.''

``But back at SAC-09 we have the resources to handle it.  We have Trenton and he's good at these things even if he is an asshole.  He can study it and figure out where they're coming from so we can go there and fuck them up.''

Lorentz nods, ``Assholes are often the most effective ones at their job.  Very well, you have convinced me you should take it with you.''  He turns to Vogel.  ``Get a Fili.''

Something about this situation bothers Hayley but she can't think of what (nominal Nose for Breadcrumbs spidey sense tingling).

``We'll need an armed escort back to the station.  There's probably still that arrest warrant out for us,'' says Jaya.

``Are you requesting any particular escorts?'' asks Lorentz.

``Uh, your best!  Of course, we should have your best agents with us,'' says Jaya

``Sir, before we were interrupted, you said you had a message for us to pass along to Agent Morgan?'' asks Jonah.

``Yes, tell Morgan thank you for handling the Transit Minor situation.  I look forward to showing her my appreciation.  I also request a conference with the Praetor.''



At Jaya's prompting, Jonah tries to radio Jari but Jari does not respond.  It has been about two hours since Jari left.  Jonah treats Jaya's arm. {[}\textit{Flaw 2: Injured right arm (Jaya)}\textit{ + Surgical Kit 2 (Jonah) → }\textit{ {\color[RGB]{255,0,0}Flaw 1: Injured right arm (Jaya)} }{]}



Jonah addresses \hl{Vogel}\footnote{\textbf{Nathaniel Ford }http://www.arizonatheatre.org/atc-resources/dynamic/yr\_2011-12\_show\_headshots/GOD\_aResnick.jpg

A younger shot of her, but of the actress who I have in mind for Vogel. \textsubscript{08/18/14 9:45pm}}\footnote{$\rightarrow$\textbf{Suko T }Nice.  Hayley was probably checking her out a little too.  Gender almost totally irrelevant to the pretty-worship. :) \textsubscript{08/19/14 12:42am}}, ``Have you worked with any of the members of the Security Triumvirate?''

``Yes.''

``How much do you trust them?''

``I don't.''

``No I mean how \textit{much} do you trust them?  Do you trust that they have the best interests of the Directorate at heart?  Is there any one of them that you trust more than the others?''

\hl{``They're all snakes and vipers but I trust that they won't disrupt the ship too much.  I trust them not to sink the ship.  But I also trust that they will turn on each other at any opportunity.''}\footnote{\textbf{Nathaniel Ford }Culturally, this analogy is all off. They wouldn't really being using ship/boat analogies, but, argh. I'll think of a better one they would have used. \textsubscript{08/15/14 5:34am}}

Vogel briefly talks into her hush radio and says, ``Drake wants to walk you home.''

``Awww....'' frowns Jaya.

``Well you did ask for the best...'' says Vogel, raising an eyebrow.

REBECCAxxBEGINxxHIGHLIGHTxx``Yeah well I was expecting....'' says Jaya and she looks Vogel up and down with a smile.

``That's flattering,'' says Vogel.  ``But I have a lot of matters to attend to right now.''  

Jaya offers her a cigarette.  Vogel takes it and says ``I quit'' while tucking it into her pocket.

``Yeah I quit every day too,'' says Jaya nodding in understanding.xxENDxxHIGHLIGHT\footnote{\textbf{Suko T }I really loved this bit. \textsubscript{08/15/14 2:57am}}
Vogel and Lorentz leave.



``What is a Praetor, Sir?'' Hayley asks Jaya.

``I have no fucking clue,'' says Jaya.

``I don't know either,'' says Jonah.

``Oh.  I thought it was just me.  How do we find out?''

``Lorentz seems to know.'' says Jonah.

``Why don't we ask him?'' asks Hayley

``Let's wait and ask our superior officers later, okay?'' says Jaya.

``Okay.''



Drake arrives with two other officers.  ``Let's get going,'' he says.

``Excuse me sir, may I ask a question?'' Hayley asks Drake

``Sure.''

``Because we may be attracting attention, shouldn't we approach the station obliquely?'' 

``What?'' asks Jaya.

``At an angle,'' explains Jonah.

``Not directly,'' adds Hayley.

``Don't worry, I've already taken that into consideration,'' Drake says with a tone of condescension that of course irritates Jaya.  He winks at Hayley and slaps her companionably on the shoulder.  Hayley jumps a little and frowns before she remembers something and then she relaxes and smiles.  Jaya sees this (dammit, that's \textit{her} thing!) and puts another mark in the ``reasons to hate Drake Malak'' column.  




\sceneHeadline{On the streets of Terminus}

We walk away from HQ, past the Filis who are still on the street.  Hayley calls out to one quietly, ``Fili, can you tell me your current orders?''

``No sir.  Please consult with my employer \_\_\_\_\_ (a Fili rental agency)'' says the Fili politely.  Hayley nods with equal politeness and walks on.

``May I state something?'' asks Jonah of Drake.

``Anything you like, boy,'' says Drake.

``The Filis are likely reporting on us.''

``I don't understand.  Why Filis?'' says Drake.

``Filis give accurate and detailed reports,'' says Jonah.



About a third of the way back to the Terminus Station, we run into a six man Patrol Group.  They salute Drake and the leader says that they heard there was a disturbance and they have been ordered to check the badges of all officers in the area.   Jonah asks under what authority, and they say that Station Chief \hl{Herrera}\footnote{\textbf{Suko T }randomly picked a name \textsubscript{08/14/14 1:10am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{08/15/14 10:59am}} of \hl{Ward 4}\footnote{\textbf{Nathaniel Ford }Coincidence? Or SPOOKY COINCIDENCE? \textsubscript{11/07/14 4:30pm}} issued the order.



Drake shrugs and shows his badge and the other two officers with us show theirs.  Jonah says to Drake \textit{sotto voce}, ``Given our previous conversation, this is probably not a good idea.''  Drake doesn't look interested in helping out.  



{[}\textit{Challenge 1: Convince Drake to intervene.  Unashamed 1 (Hayley) → Matched}{]}.  Hayley is getting increasingly anxious at the delay.  She gives Drake a wide-eyed ``helpless girl'' look and asks him prettily, ``This delay is leaving us exposed for too long.  Is there \textit{anything} you could do to help expedite this situation, Sir?''



Drake smirks and says, ``You're right, this \textit{is} taking too long.''  He walks up to the Patrol group leader and plucks the orders out of his hands.  He crumples them up and tosses them aside and then just walks right through the patrol.  The rest of us follow him. 



Nervously, the PG leader clears his throat and says, ``Uh, but Sir, I need to-''

Drake turns around and puts his hands on his hips intimidatingly.  ``You need to \textit{what}, Son?''  The PG leader wilts and mumbles, ``Err....''

``Go right ahead and file a complaint if you want.  We're done here,'' says Drake and he turns and leaves.

``Thank you, Sir,'' says Hayley.

``No problem,'' says Drake.  ``Sometimes you gotta remind these street rats of their place,'' he continues, and rests his hand on Hayley's back.  Hayley tenses at first and almost pulls away, but the warmth of his hand is comforting and reassuring so instead she starts leaning toward him a little.

``Sir, may I ask you a question?'' Hayley asks Drake.

``Sure.''

``What is a Praetor?''

Drake turns to throw a taunting look at Jaya as he says, ``What, your commanding officer didn't tell you?''

``If she did, I don't remember,'' says Hayley.  Jaya appreciates Hayley covering for her.

``Really?  That seems like a problem, if you're not remembering things.''

``Oh no, that's normal for me.  I get hurt a lot and have a lot of memory gaps.''

``Really.  Huh.  Well you know that the stations are really old, right?  And stuff can break down and stop working.''

Hayley thinks for a moment and then smiles in understanding, ``Oh yes of course, it takes a lot of work to keep my equipment in working order.''

``Yeah, it is important to keep \textit{all} your equipment well-oiled and in excellent working order.'' says Drake, hooking his thumbs into his belt, his innuendo clear to everyone but Hayley.  ``And  these stations, for that reason, need someone to take care of things,'' he continues

``Ah, like a housekeeper?''

``Or like a guard dog too. That person tends to the stations, keeps things in order.  That's a Praetor.''

``I understand now.  Thank you for telling me,'' says Hayley.

Drake continues to \hl{shamelessly come onto Hayley}\footnote{\textbf{Suko T }I have to wonder what the two officers that Drake brought with him are thinking about all this. \textsubscript{08/14/14 5:49pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }For most people... level 1 notice challenge. For Hayley, lets say level 4. \textsubscript{08/15/14 5:38am}}\footnote{$\rightarrow$\textbf{Suko T }LOL!  Isn't this true for just about everything except whether or not you're wearing last season's fashions or are using the wrong spoon for your soup? :) \textsubscript{08/15/14 1:41pm}} who fails to notice any of the rampant innuendo/subtext.  But she looks genuinely interested in Drake's offers and is \hl{obviously attracted to him}\footnote{\textbf{Suko T }She acts like a girl with a blossoming crush.  She walks closer to him than SOP, she smiles a lot, her attention is on him (not on the immediate environs, I'm sorry to say), and she seems to find whatever he says very interesting.  

I'm sure it makes Jaya quite nauseous to watch it. \textsubscript{08/14/14 3:23pm}}.

``You should come see me the next time you're in town.  I'll get you a better rack.''

Hayley is confused.  ``In an armory?  For my rifle?''

``Nah, I mean a bunk.  Don't stand in the requisition line with the regulars, those things are infested with fleas.  Come see me, I'll get you set up.''

``Oh that's very nice of you.  I'll keep that in mind if I need to stay overnight.  Also I want to say thank you for your advice earlier, it was helpful.''

``No problem.''

``I'm still getting used to my rifle.''

``Really?  Because you looked pretty good back there.  I mean, \textless cough\textgreater  not that I was watching you specifically or anything but sometimes it's just habit to evaluate a soldier's performance.''

``Hayley \textit{could }use more training,'' chimes in Jonah 'innocently'

``Yeah?  Well, I teach marksmanship and hand to hand combat.''

Hayley looks very interested at that.  ``What style?''

``Of combat?  Whatever takes someone down the fastest.''

``I need to learn to do that. Would you teach me?''

``Sure, I teach on Tuesdays and Thursdays. I'd be happy to show you what I can do.''

``I would like that very much,'' says Hayley, delightedly.

Jonah is relieved to see Hayley acting like a normal(ish) girl for once.  Jaya is fuming but takes note of Drake's schedule in case she needs to find him to kick his ass later.




\sceneHeadline{Terminus Station}

We arrive at the station.  Hayley waits until Jonah and Jaya enter the station, scanning the area around the station until they are safely inside.  Jaya's face is red and her hair is a mess as if she had been pulling at it in silent rage.  She mutters a tight, terse ``thank you'' rant in Drake's direction before stomping past him and into the station. Drake takes his leave and Hayley watches him go wistfully, being unashamedly obvious about it.  He looks back to see if she's watching and she smiles at him when he does.  



``Hayley, what the hell was that?'' snarls Jaya.  ``Get the fuck in here.''  Hayley is confused but steps into the station.  Jaya checks and Hayley and Jaya are still not on the arrest warrants list.



Jonah looks around the station and then asks Hayley, ``Hayley, do you see anything out of place?''

{[}\textit{Challenge 2: Notice.  Ladies' Maid 2 (Hayley) → Matched}{]}.  Hayley looks around the room, her eyes pausing on the Filis who are moving in an odd pattern.  ``Yes, there are Filis here, they may be watching us.''

``Was there anyone watching us outside?'' asks Jaya.

Hayley shakes her head.  ``No, I didn't see anyone while I was watching Agent Malak walk away.''

Jaya rolls her eyes and makes a disgusted noise.

Jonah watches one of the Filis closely, they seem nervous and overwhelmed.  They do not appear to be acting in concert or that they are paying attention to \textit{only} Jaya, Jonah and Hayley.



Jonah reaches Jari.  ``Sorry that took so long,'' says Jari.

``Do you have any answer to my question?  Because that will really affect what we do next,'' says Jonah.  

``Perhaps that's something better discussed once you're onboard.  Is this going to be a hot drop?''

``No, just do a normal arrival, try not to attract any attention.''

``Well this isn't a regular cargo train so...''

``Just do your best.''



Jari pulls into the station and we get on the train.  Rook is there.

Hayley salutes.  Rook salutes back.  Hayley turns around back to watch the platform through the train door windows, her rifle at the ready.

Jaya hands the device over to Rook.  Jonah explains that Jaya retrieved it from a man who was attacking the Agent HQ.  Rook confirms that it's not active.  ``Agent Parvadi caught him unaware, presumably before he could activate it.''

``Sir, we have a decision to make,'' says Jonah.  ``Marechenko will support us but he wants to be able to track us to where we are.''  Jonah pulls out the device that Marechenko gave him.

Rook pulls out a nearly identical device.  ``If he detects that this is forgery he may be upset.  It is actually valid, but if he attempts to use it, he will know immediately that it is a fake.  Morgan says the choice of which to give to him is yours.''

``To see where my loyalties lie?'' says Jonah.   

Rook asks, ``Do you trust him?''

``I trust Marachenko and I do not like \hl{starting a relationship with a lie}\footnote{\textbf{Suko T }So ironic, TIMON. \textsubscript{08/15/14 1:56am}}.''

``The decision is in your hands,'' says Rook.

``What do you think?'' Jonah asks Jaya.

``Don't do it.  Don't fucking give away our location,'' says Jaya.

``Hayley?'' Jonah asks.

``If we make more enemies, we will lose Terminus for certain.  Wasn't getting Terminus on our side our mission?  Citizens are often extremely vicious when they feel they have been insulted or betrayed and they will actively work against us,'' says Hayley, and then she turns back to scanning the platform.

``Whatever. All the Senators are assholes,'' says Jaya.  ``Aren't they?'' she asks Rook.

``I don't usually classify people by their bodily vacancies,'' says Rook, totally deadpan.

``What do you think, Sir?'' asks Jonah.

``I think in the short term, you are correct.  However in the long term, if he's been compromised once, he can be compromised again.  We can't afford to be betrayed.''

``Sir, may I ask a question?'' Hayley asks Rook.  Rook nods.  ``What do you mean that Senator Marechenko has been compromised before?  When was he compromised?''

``Perhaps I misspoke, I merely meant that he could be compromised and once he does it once, there is no telling how many other times it might happen.''

Jonah asks Jaya and Hayley and Rook what they think, again.

``Don't give him the real one,'' says Jaya firmly.  ``This is a direct fucking order.  Don't do it.''

``You know I hate lying.  Don't give him the fake one.  If he finds out, it will be very bad for us.  He's powerful here,'' says Hayley. 

``You could always just not give him either device and avoid lying or betraying our location,'' says Rook.

Jonah thinks hard.  ``Give me the real one,'' he says to Rook.  Jaya lunges to stop him, but Rook holds up a hand to stop her.  ``This is his choice,'' says Rook.  Jaya glares at Jonah as he leaves the train to drop the device in the maildrop.  Hayley covers him until he returns.  Jaya is furious but \hl{Rook calmly hands her back her badge}\footnote{\textbf{Suko T }Rook is so badass. \textsubscript{08/15/14 2:20am}} and says with a little smile, ``Trust me. It will be fine.''  Jaya can't figure out when Rook got ahold of her badge.



Jonah gets back onboard and the train pulls out of Terminus Station.



\textbf{{[}2 Tokens remaining{]}}






\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 20
\item Challenge 2: Not be injured.  Flaw 2: Injured right arm (Jaya) → Matched
\item Refresh: Left Arm 3 (Jaya)
\item Challenge 2: Notice.  Binoculars 2 (Jaya) → Matched
\item Challenge 3: Bandage Mohinder Lorentz.  Surgical Kit 2 (Jonah) + Street Medic 2 (Jonah) → Matched
\item Refresh: Adrenaline Junkie 2 (Jaya)
\item Challenge 2: Shoot guy aiming at Jaya. Rifle 2 (Hayley) → Matched
\item Challenge 1: Jump down to second floor.  Adrenaline Junkie 2 (Jaya)  → Overcome! \textbf{1 VP (Jaya)}
\item Challenge 4: Shoot guy with grenade launcher before he can fire on us.  Saltaremachy 3 (Hayley) + Bodyguard 2 (Hayley) + Memory for Details 1 (Hayley) + Small Unit Tactics 1 (Hayley) → Matched
\item Challenge 1: Notice. Sent back to pool.
\item Refresh: Combat Armor 3 (Jonah)
\item Refresh: Truncheon 2 (Jaya)
\item Challenge 2: Notice.  Vigilant 3 (Jonah, through Jaya) → Overcome! \textbf{2 VP (Jaya 1 and Jonah 1)}
\item Challenge 1: Notice.  Sent back to pool.
\item Refresh Rifle 2 (Hayley)
\item Challenge 2:  Avoid being shot.  Left Arm 3 (Jaya) → Overcome! \textbf{2 VP (Jaya)}
\item Challenge 3: Kill guy through the wall.  Sidearm 3 (Jaya) + Small Unit Tactics 3 (Jonah)  → Overcome! \textbf{3 VP (Jaya 2 and Jonah 1)}
\item Flaw 2: Injured right arm (Jaya) + Surgical Kit 2 (Jonah) →  {\color[RGB]{255,0,0}Flaw 1: Injured right arm (Jaya)} 
\item Challenge 1: Convince Drake to intervene.  Unashamed 1 (Hayley) → Matched
\item Challenge 2: Notice.  Ladies' Maid 2 (Hayley) → Matched
\item Pool: \hl{2}\footnote{\textbf{Suko T }I missed a refresh somewhere, because otherwise this should just be 1 token left. \textsubscript{08/15/14 2:09am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }There was one token on the table at some point that we decided was still in the pool. It's possible it should have been taken off instead. \textsubscript{08/15/14 5:40am}}
\end{itemize}


\jumpHeadline{Accumulated Flaws over last four sessions in Terminus }

 {\color[RGB]{255,0,0}Flaw 2: Trust Marechenko (Jonah)} 

 {\color[RGB]{255,0,0}Flaw 1: Injured right arm (Jaya)} 

 {\color[RGB]{255,0,0}Flaw 3: Rivalry with Malak (Jaya)} 


\jumpHeadline{VP Totals }

Hayley 0

Jaya 6

Jonah 2


\jumpHeadline{Quotes: }
\quotedDialog{
Jaya: We do have Trenton and he's good at these things even if he is an asshole.

Lorentz: Assholes are often the most effective ones at their job.\\[4mm]
}

\quotedDialog{
Jaya: Whatever. All the Senators are assholes.  Aren't they?

Rook: I don't usually classify people by their bodily vacancies
}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 3:56pm
\end{flushright}

