\setcounter{chapter}{ 31 }
\chapter{\textbf{``Shore Leave''} }


\subChapterTitle{``Alacritous Response''} 



\textit{Notes:} Suko and Rebecca

\textit{Date:} Sept 10th, 2014



Personal Backstory Trauma reared its ugly head for all three PCs.  Padme confronted Jaya over the destruction of L.A. Ink and now Jaya has to ask Morgan for money.  Jonah spilled his Big Secret to his family and is moving them all to SAC-09.  Hayley finally found someone (other than Signe) who speaks her language and learned some very fucked up information about the history behind her scars. 





\jumpHeadline{SAC-09}


\textbf{{[}3 Tokens in Pool from PC-initiated Scenes in previous session{]}}

The next morning, Jaya, Jonah and Hayley head to breakfast.  Javier and Carruthers are in the mess hall too.  Hayley smiles at Carruthers but Carruthers is lost in thought and Hayley leaves her alone.



Jonah and Hayley get normal meals, Jaya gets a bowl of gruel.  There is an envelope on Hayley's tray.  It has been redirected from Morgan's office and there is a handwritten note on it that says, ``Handle this.''  Hayley gets up immediately, leaving her meal untouched and leaves the cafeteria.  Jari swoops in out of nowhere and gathers up Hayley's tray before Jaya can steal anything off of it.



Rook enters and addresses Jonah, ``I received your request for Shore Leave, is there anything that we need to discuss?  Do we need to make accommodations at the base and if so, how many?''

Jonah thinks about it, ``One.  Or three.''

``So potentially three.  Are they comfortable in close quarters?''

``No one's going to be comfortable.''

``Any dietary restrictions?'' asks Rook.

Jonah pauses for a long while and then says, ``All of this is going to be totally out of their experience.''

``I'm sorry, I'm not sure how that's pertinent to dietary restrictions.''

``\hl{There's none that I'm aware of}\footnote{\textbf{q.google }''How would I know what their dietary restrictions are?  People on the street don't eat what you eat in Citizen-land.'' \textsubscript{09/25/14 3:12pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Or Rook-land, as the case may be. \textsubscript{09/25/14 5:35pm}}\footnote{$\rightarrow$\textbf{q.google }Indeed.  And the case appears to be just that. \textsubscript{10/05/14 1:15pm}},'' says Jonah.

``Very well then.  I'll see to it.  You should be ready to leave in 2 hours,'' says Rook and looks around the room.  His gaze pauses briefly on Jaya.  Jaya is staring down at her bowl.

Jonah turns back to his breakfast and half of it has already been eaten (by Jaya) while he was talking to Rook.  She takes another sausage off of his tray and he doesn't protest.  He looks distracted, stands and leaves the room.  Jaya puts her hands on Jonah's tray and watches warily for Jari but he doesn't appear.  Jaya finishes off Jonah's abandoned breakfast.



Hayley sits down on her bunk and reads the letter.  It is from the Vorrutyer lawyer and is full of legalese.  Various things for Gillian Vorrutyer's entire private estate (all her holdings) need to be signed, countersigned, etc. and they need the holder of the estate or an assigned proxy to come to deal with it.  There is a list of proxies at the bottom.  The first five names are crossed off and Hayley is sixth.  There are a few names listed after hers.  The meeting location is in DX Station.



Hayley finds Rook to request her Shore Leave to DX Station.  Rook tells her that Jaya needs to be on the same train, so Hayley goes trotting off to find Jaya.  Jaya is in the bunk, smoking.  Hayley tells her that the train is leaving soon and packs her bag and Jaya's.



Jaya goes to find Jayce.  He's sleeping in the one of the other barracks room down the hall from the two Patrol Groups.  Jaya kicks the bed and Jayce wakes up, a little twitchy, reaching for his knife under the pillow.  She tells him, ``Hey we talked about this.  The train's leaving and you're going to help me find my sister.   Ten minutes.'' and she leaves.



We all arrive at the Ready Line on time.  Jayce is asleep on a bench.  Hayley and Jaya are in their regular TA Agent uniforms.  Hayley has her rifle with her and neatly packed bags for herself and Jaya.  Jonah is in his old constable uniform (not Operator/Agent uniform).  



Rook walks out and addresses everyone.  ``Due to recent complaints, it is my duty to inform you of two key regulations from the TA handbook.  I'm certain you are familiar with these but as per protocol, I must remind you.  The first is that one does not fraternize across ranks.  Nor does one engage in the sale or purchase of sexual favors of any kind.  This is necessary to maintain the discipline of the TA. Secondly, it is my duty to inform you of the regulation that prohibits the unnecessary slander of senior officers and or lying about their actions, etc. etc.  I am sure you all understand these two regulations as I have stated them to you?''

Hayley asks, ``Could you please define, 'fraternize', Sir?''

``Have relations with,'' says Rook

``Of what level? Social?  Physical?  Politi-'' asks Hayley

``She's asking is it like first base, third base...you know, the level of breaking the rules,'' interrupts Jaya, glaring at Rook.

``I don't know what base means in that context,'' says Hayley, confused.

``I would recommend avoiding any 'base''' says Rook.  Jaya smirks.  Rook continues, ``\hl{Unfortunately this sort of behavior has the tendency to create emotions and feelings in the associated parties that can interfere with duties}\footnote{\textbf{q.google }Ya think?  I'm surprised fraternization is allowed even \_within\_ ranks.  (\_Is\_ it allowed OOG?) \textsubscript{09/25/14 4:29pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I think it's discouraged, especially if you're in the same order of battle/org chart. But I don't think it'll get you a dishonorable discharge like cross-rank fraternization. \textsubscript{09/25/14 5:35pm}}.''

``Ah!  Workplace relationships,'' says Hayley.

``Yes,'' says Rook

``He's just reminding you not to sleep with Trenton,'' says Jaya.  ``Remember, we've already had this discussion.''

``Technically, Trenton is not within the TA,'' says Rook.  Jaya glares daggers at Rook again.

``I still don't-'' Hayley looks even more confused and turns to Jaya. ``Um, may I ask for more clarification later, on the train, sir?''

``Yes!  On the train. Later.  Excellent initiative, Hayley,'' says Jaya, approvingly.

``I just need to get verbal confirmation from each of you that you all understand these regulations,'' says Rook.

Jaya blows a puff of smoke in Rook's face in blatant disregard to the ``no smoking'' signs and says, ``Understood.''

Hayley re-settles her rifle and nods, ``I understand, Sir.  Mostly.''

Rook starts speaking again and Jaya points out that Jonah didn't confirm his understanding.  Rook replies that Jonah gave his confirmation earlier.  

``Very good.  I'm just, uh, looking out for my team,'' says Jaya and she grabs Jayce and boards the train.  ``What was that about?'' asks Jayce but Jaya just shakes her head. Hayley picks up her bag and Jaya's and boards the train.

\hl{As Jonah boards the train, Rook says to him discreetly, ``My apologies for that lie.''}\footnote{\textbf{Rebecca S. }ugh, men! \textsubscript{09/18/14 9:26am}}\footnote{$\rightarrow$\textbf{Suko T }I know right?  I think they're starting to feel outnumbered and are clustering together for safety  :D \textsubscript{09/18/14 1:05pm}}

``No apologies necessary,'' says Jonah.

The train leaves.



Hayley turns to Jaya, ``Sir, can you please explain this to me?  Clearly base means something else.''

``Mouth, tits, ass,'' says Jayce.

``Stop being helpful,'' Jaya scowls at Jayce and then turns to Hayley.  ``It's like a different protocol that you don't execute.  No base.  Okay?'' says Jaya.

``Yeah no kissing anyone,'' drawls Jayce.  Jaya slaps his arm.

``Even when it's required by social protocol, I should still refuse?'' asks Hayley.

``There is no social protocol-'' starts Jaya but she's interrupted by Jayce.  

``Wait- where the fuck is kissing a social protocol?  \hl{I want to go there}\footnote{\textbf{q.google }He would find himself in hell. \textsubscript{09/25/14 4:31pm}},'' he says.

``As a greeting between old friends or to seal a social contract,'' says Hayley, as if reciting something she memorized.

Jayce tries to ask more about this but Jaya interrupts to say, ``Hayley, we're in the TA. The only kiss we give is with a fucking fist, ok?''

Hayley asks a few more clarification questions but eventually gives up and just gazes at Jonah.  Both Jonah and Jaya are smoking.  The smoke makes Hayley cough a lot and she seems to be trying to breathe as little as possible.



Hayley is dropped off first at DX Station, then Jonah at the Bucket, and last is Jaya and Jayce at the Annex.




\sceneHeadline{Jaya's Shore Leave- the Annex}

Rook motions for Jayce to get off the train, but stops Jaya when she tries to follow.  

Jaya braces herself in a combat-ready stance and says, ``Agent Sir Rook Sir.''

``Agent Parvadi.  \hl{You've made the mistake of messing with the cook, which I'm sure you will deal with the consequences of}\footnote{\textbf{q.google }Primordial wisdom.
QooC. \textsubscript{09/25/14 3:19pm}}.  But I assure you I had, in no way, any part to do with whatever message he wanted to transmit to you.  However, if you should choose to mess with me in the future, the consequences will be much greater.''

Jaya fumes for a bit and then crosses her arms.  ``Understood...Sir\textit{.}''

``Thank you.  I hope that we can continue to have a clear working relationship.''``I hope you keep that in mind the next time you order me to meet with someone.  \textit{Sir,}`` says Jaya and she leaves the train.

``Acknowledged,'' says Rook and the train departs.



When Jaya rejoins Jayce, he asks her, ``So... were you sleeping with \textit{Rook}?''

Jaya makes an annoyed sound.  ``He \textit{wishes}.  No, there was a misunderstanding.  Ugh.''  Jaya grabs Jayce's arm and drags him to L.A. Ink (where it used to be anyway).

Along the way, she quizzes him about what he saw during the attack on L.A. Ink.  Jayce said that he and Douglas arrived as some people were attacking the place.  

``Douglas took care of most of them. He seemed...\hl{you know when you haven't gotten laid in a while?  Yeah, like that but with a sword}\footnote{\textbf{q.google }QooC \textsubscript{09/25/14 4:33pm}}.  They were not normal street thugs.''

``Mining clothes and weird faces?''

``Yeah I guess...They had your sister pinned against the wall- alive- and we walked in and they tried to kill us.  We backed out and there was a fire fight.  Well my part was a firefight, Douglas was less fire-y, more sword.''

\hl{``He brought a fucking sword to a gunfight?'' says Jaya scornfully.

``Guy's fast,'' says Jayce.

``Fucking weirdo.''

``Says the girl with the arm.''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{09/18/14 1:04am}}

``Did you see any little ones?'' asks Jaya.``Kids?  I didn't see much of anything.  I literally walked in, they attacked us, I ducked, there was an explosion.  Douglas was shouting something, I don't know what.  When I came back in, the place was on fire and your sister was gone.  Two of them escaped out a back window and a third was already dead,'' says Jayce.

``So you...somehow...found my house.  I mean, my sister's house, which is pretty close.  Could you just...work that magic to find her again?''

``Oh sure.  Well, I was tracking you the first time.''

``She and I are so alike, you would not believe it.  Finding me is like finding her.  She's got some different tats, but...''

``Alright, follow me,'' says Jayce.



Jayce leads her to a bar and Jaya straight up asks the barkeep, ``Hey you seen my sister?''

Jayce is bemused, ``Guess you don't need me here.''

``Sorry, with my team, I'm just used to taking point.  You can ask the questions,'' says Jaya.  Jayce shakes his head and tells Jaya she's free to continue interrogating the guy.

Jaya starts tapping the bar with her mechanical arm (which alarms the bartender) and repeats her question to the bartender.  He starts reaching slowly under the bar.  He hands Jaya a slip of paper.  ``Your sister, she ran around with Ricco, right?''

``Yeah him and five other guys.''

``Well he's the one who showed up and said if you showed up, to go there.''

The paper has a bunch of symbols and directions on it.  They leave.  Jayce leaves a few coins on the bar, and Jaya almost takes them.  Jayce explains that the coins should encourage the bartender to remember him and be friendlier next time.  Jaya thinks that it's enough that the bartender remember that she didn't break anything this time.



They head to the street corner indicated by the address.  Jayce is a bit on edge.  Jaya sticks out in her TA uniform and people are giving Jaya a wide berth.  Jaya's not sure which guy is Ricco, she can't remember what he really looks like, so she just yells, ``Yo Ricco!''  One of guys starts and other people start looking at him.

``I got nothin' on me!'' the guy protests.

Jaya claps her hand over her badge and says, ``I'm not here for the fucking TA. I'm Jaya Parvadi, Padme's sister.  Where is she?''

``Of course I know who you are!  Everyone knows who you are.  Can we go somewhere less....?'' and he nods to a side alley.

Jaya grabs him by the collar with her mechanical arm and drags him into the alley.  She drops him and he looks warily at her arm, ``Jesus! What the fuck is that thing?''

``It's awesome.  It's \textit{my} awesome.  And it's going to be your fucking sadness\footnote{\textbf{Suko T }A thing of beauty, this. \textsubscript{09/17/14 4:07am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 Love this line. \textsubscript{09/19/14 4:28pm}} if you don't fucking take me to my sister.''

``I can take you there but she left very specific instructions...'' says Ricco.

Jaya glares at him.

\hl{``Look, I'm just doing what my baby mama told me!}\footnote{\textbf{Suko T }I love this line so much. \textsubscript{09/16/14 2:48am}}\footnote{$\rightarrow$\textbf{q.google }QooC \textsubscript{09/25/14 4:33pm}}  Okay?  Just come back here after dark.''

``I've got a train to catch-'' says Jaya.

``Hey you want me to cross her?  \hl{Even with that...thing \textless he gestures to her mechanical arm\textgreater  she's still twice as scary as you}\footnote{\textbf{q.google }The sum of the scene :) \textsubscript{09/25/14 3:22pm}}.''

``Fine,'' says Jaya and drags Jayce into a bar across the street.  Jaya drinks and does a bit of coke.  Jayce sticks with just alcohol.



Jaya staggers to the meeting point with Ricco (Jayce is somewhat less chemically impaired) and Ricco leads them along a labyrinthine path through various areas and buildings in the area.  Eventually they end at some stairs that go below street level and into some curtained off areas and a hallway.  In the hallway is another dude, whom Jaya remembers vaguely.  She thinks Padme had two kids with him and she remembers approving of him a bit more because he was a big guy and could hold his own. Not much of a talker, which was another point in his favor.

The guy looks at Ricco and says, ``Damn you're slow.''

Ricco glares at him, ``Fuck you.''

Jaya marches up to the second guy, ``Where's my sister?''

``She's down the hall.  Asshole stays here,'' says the guy, indicating Jayce.  The guy is alarmed by Jaya's arm but isn't a quick enough thinker to stop Jaya before she starts marching down the hallway to her sister.  \hl{Jaya tells Jayce to shoot anyone who does anything stupid}\footnote{\textbf{Nathaniel Ford }For the record, I think this is the point when Jaya transcended some boundary. \textsubscript{09/19/14 7:54pm}}\_Marked as resolved\_\_Re-opened\_\footnote{$\rightarrow$\textbf{Adam Kenney }It's probably a good thing that Jaya didn't have this policy in our early days. \textsubscript{12/03/14 11:05pm}} and she leaves him there with Ricco.



At the end of the hallway is a room.  A young boy (Micah), is playing in a corner and Padme is there.  Jaya rushes in and gives Padme an enthusiastic hug.  Padme is a bit taken aback by Jaya's arm.  She sorta hugs Jaya back but then pushes her away saying angrily, ``Get off me!  What is going on??''

``I'm just so happy you're not dead-'' says Jaya.

``Yeah, my fucking place was burned to the ground!  What \textit{was }that?  They were looking for you.''

Padme shoos Micah out of the room and then turns to Jaya and demands, ``The fuck happened to your arm?''

``Uh....I lost it...but I got it back.  It's better now.... I am really sad that I lost all the ink you did though, it was some really great work you did.  And I really appreciate it.  And I'm looking into maybe-''

``Are you fucking high?'' interrupts Padme.

Jaya pauses.  ``Obviously.  But the important thing is that you're alive-''

Padme slaps Jaya.  Jaya rolls with it.   Padme says angrily, ``I'm living in a fucking \textit{hovel}.  What the fuck is going on?  They tried to kill me and my boy.''

``Well, they were trying to kill \textit{me}, actually-''

``Oh right.  They were trying to kill me and my boy because of YOU.  What the FUCK is going on??'' yells Padme.

``Shit's getting intense!'' says Jaya defensively.  ``There's a war...''

``And you've been gone for-fucking-ever!''

``I'm getting you water chits!''

``And where are those going right now?  I'm fucking hiding out down here.  I've got every guy I've banged since I was thirteen making sure nothing happens to us...'' says Padme.  Jaya mutters something under her breath and Padme glares. ``Don't even start that.  You know how I run.  Speaking of which, this guy you have with you...''

``Which guy?'' says Jaya blankly.

``The one Ricco picked up with you.''

``Oh right, he was just helping me find you-''

``Oh, so he's not banging you?''

``What?  No!  Welllll...uh.  No.'' sputters Jaya.

``So you're telling me that someone's out to assassinate you and you're \textit{still} not getting laid.''

``I've been working really hard...''

``YOU'VE been working hard???  How many children do I have?''

``Uh....well it goes up and down...''

Padme slaps Jaya again.  ``You're my fucking sister.  \hl{How many kids do I have}\footnote{\textbf{q.google }Discussed below under Riva: Padme is an example of someone deliberately having children as a good economic choice. \textsubscript{09/25/14 3:36pm}}?''

``I think you have six...maybe down to five.  Have you heard from the ones on the Plantation?''

``No.  Have you?  Big TA girl?'' Padme sneers.

``No... Don't hit me again!  Uh, I've been really busy...I'm just happy you're alive...''

``I'm really happy I'm alive too.  Now are you going to tell me what the fuck is up? Why are people trying to kill you?  Why are they coming after me?''

``Well I'm a really important person now.  I've got all this information in my head and this arm...They're trying to get at me through you.  'Cause you're my fucking sister and\hl{I love you}\footnote{\textbf{Rebecca S. }Oh shit, somebody call the retcon police! Shouldn't Jaya's arm have fallen off at this point? \textsubscript{09/24/14 8:52am}}\footnote{$\rightarrow$\textbf{Suko T }Ooo... that would have been funny! :D \textsubscript{09/24/14 10:10am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }OH SHIT!!!! \textsubscript{09/24/14 3:20pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It really should have fallen off. I totally spaced it in the moment. We should discuss at session. \textsubscript{09/24/14 3:22pm}}\footnote{$\rightarrow$\textbf{Suko T }Amended, at least somewhat, although Rebecca is free to write it up more completely. \textsubscript{10/01/14 12:09am}}\footnote{\textbf{Rebecca S. }A vital key for insight into Jaya brain \textsubscript{09/18/14 9:34am}}\footnote{$\rightarrow$\textbf{Suko T }And the fact that she is willing to brave asking Morgan for money says a lot about the strength of Jaya's commitment to her sister. :) \textsubscript{09/18/14 1:06pm}}-''

With a small noise, Jaya's mechanical arm disengages and falls off.  Fumbling, she just barely manages to catch it before it hits the floor.  Luckily Padme had turned away at that point to pour them a drink.  Jaya manages to reattach the arm before Padme returns with the drinks, and repeats,  ``\textit{I love you}. \textless and the arm reactivates\textgreater .  And I want you to be okay.  The important thing is that you need to not get caught because that would compromise my position.''\footnote{\textbf{Rebecca S. }A vital key for insight into Jaya brain \textsubscript{09/18/14 9:34am}}\footnote{$\rightarrow$\textbf{Suko T }And the fact that she is willing to brave asking Morgan for money says a lot about the strength of Jaya's commitment to her sister. :) \textsubscript{09/18/14 1:06pm}}

After turning back Padme gives Jaya a look, along the lines of, 'why are you looking strangely panicked? Did something just happen?' But she shrugs it off and says, ``So I should stay here?  What am I supposed to do?  I can't work, I can't find new guys...''

``What about the tall one?''

``He only gives me fucking brats.  I need a bitch.  You know that!''

``Look I'll do what I can to keep you safe.  I'll....I'll ask...'' Jaya goes pale, her voice wobbles and she clears her throat a few times before she can continue. ``\hl{I'll ask my superior officer for an advancement.  I've got you covered}\footnote{\textbf{q.google }I think asking Morgan for money may be \_the\_ most overt expression of Jaya's commitment that we've seen. \textsubscript{09/25/14 3:28pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:33pm}}, I just need you to stay low.  It would really interfere with my ability to-''

``Have kids?''

``\hl{What?  NO!  You're making the family, I'm making the water chits}\footnote{\textbf{q.google }It's telling how in modern Western society this \_isn't\_ seen as an example of ``traditional family''.  Women, especially sisters, splitting the work and the child-rearing is older than history.

Here is to the Parvadi sisters and the many millions like them, doing a ton of work for very little credit. \textsubscript{09/25/14 3:39pm}}.''

``How about we both do both?  You know, I was making water chits too.''

``Welllll... clearly that didn't work out well for you.''

``Clearly you being the TA isn't working out well for \textit{either} of us.''

Jaya brings up her mechanical arm and looks at it, ``Well... it's not so-''

``Pay attention!  \textit{It's not working out for either of us}.  Put that fucking thing down and focus.''

Jaya starts rotating the wrist.  ``Isn't it awesome?''

``Girl, I am going to slap you...''

``No wait look, just one last thing...look at this,'' says Jaya and she triggers her Predator style knife. ``You gotta admit that's pretty fucking awesome.''

Padme says grudgingly, ``I admit it's awesome.  But they're trying to kill you.  And they're trying to kill me because you work for the fucking TA.  I don't care how fucking important you are.  Sorry- did your goals change?''

``No...''

``\hl{Because if you die out there...well, you just better get that fucking advancement, or I am going to come haunt your goddamn ghost ass}\footnote{\textbf{q.google }QooC \textsubscript{09/25/14 4:35pm}}.''

``I'll get you the money, I'll send lackey boy to bring it to you.''

``I don't trust your lackey boy.  Clearly he doesn't have anything...down there.''

Jaya makes an exasperated noise and punches the wall a few times.  ``Look, I'm trying to help you here!  Can you just rein in the bitch just a little?  I'm really dealing with a lot of bitchiness at work, there's a lot of crazy-''

``Aww... I'm so sorry,'' drawls Padme sarcastically.``You don't understand!  My superior officer, \hl{she's like- she's like Mom.}\footnote{\textbf{Nathaniel Ford }Out of total, innocent, can-not-be-questioned curiosity... did we ever define what happened to Jaya's mother? \textsubscript{09/19/14 7:59pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Nope nope nope.  An open field of possibilities.  No siblings have been mentioned (nor their existence denied), no word on the father(s) (obviously), and it's not even clear if mother dearest is alive or dead. \textsubscript{09/21/14 9:37am}}''\footnote{\textbf{q.google }That is \_awesome\_.  Years of RP interaction summed up in just three words.  Grendel move over.

Jaya's scene endings are always the Best Television Ever. \textsubscript{09/25/14 3:31pm}}

An awed silence falls.  










\sceneHeadline{Jonah's Shore Leave- the Bucket}

Jonah gets off of the train and spends some time dealing with paperwork and administrative matters, mostly to give himself time to calm down.  Jonah finds out that the boy who may have gotten his sister Riva pregnant got involved with another girl and there was some sort of huge fallout from that.  \hl{Small bit of good news is that Riva is probably not actually pregnant}\footnote{\textbf{q.google }We talked about this a bit OOG.  In a world with a high infant mortality rate and physical labor is literally currency, being pregnant isn't necessarily going to be viewed as a negative.  The main issue is making sure the guy can be relied on to support the kid.

Jonah is still relieved, since he hasn't been around to vet the guy, and still hopes he can give Riva a better deal in terms of choices. \textsubscript{09/25/14 3:35pm}}.  



Jonah sends Riva a series of notes to (eventually) meet up with him at his ``Jonah'' apartment, a location he's never revealed to her before.

``This is new,'' says Riva when he opens the door.

``Not really,'' says Jonah and motions her to come inside.

``Wait, you live here?'' says Riva, looking around.

``Sometimes.  Come in.  Want something to drink?  Besides water?'' offers Jonah.

``No, water's good.''

Jonah brings her water and food.  She starts chowing down. She watches Jonah warily and looks around the room, clearly casing the place.

Jonah waits for her to stop eating but she never really does.  Eventually she slows down enough to start speaking.  ``So, Mom's got the cough,'' she says conversationally.

``How long?''

``For a while.  She says she didn't drink nothing shitty but she hasn't stopped coughing.  Dad's not sleeping anymore, keeps him up at night.''

``\hl{And you, how are you}\footnote{\textbf{q.google }Don'tthinkaboutheguiltdon'tthinkabouttheguiltdon'tthinkabouttheguilt.

Just a little longer and this can all be fixed. Really.

Don'tthinkabouttheguilt... \textsubscript{09/25/14 3:44pm}}?'' asks Jonah.

Riva tilts her head and her hair falls forward to hide her face.  ``Fine.  I don't wanna talk about it.''

``That's good.''

``This is good food. Where'd you get it?  How much did it cost?'' asks Riva.

``\hl{I..... bought it}\footnote{\textbf{q.google }Such a struggle not to make something up!  Can't you see the poor guy is suffering? \textsubscript{09/25/14 3:46pm}}.''

Riva eyes his satchel. ``With what?  They don't pay beat cops that much.  Not enough for apartments that you don't live in.''

``\hl{Good, keep going}\footnote{\textbf{q.google }OOG at this point it suddenly becomes clear that Jonah thinks his sister is very bright, and that this is part of his connection to her. \textsubscript{09/25/14 3:41pm}},'' encourages Jonah.

``You haven't been laid recently,'' says Riva matter-of-factly, still eating.  Jonah gives her a look.  ``Yeah I found out about sex,'' says Riva.  ``\hl{Why didn't you tell me about that shit}\footnote{\textbf{q.google }Kid, there are \_books\_ written about this stuff.

In Jonah's defense he's been gone for two years in kind of a critical period. \textsubscript{09/25/14 3:46pm}}??'' she demands.

``What would you done if I had told you about it?'' asks Jonah.``Probably freaked out.''

``See, typically if you're an older brother and they're doing their job, they'd keep you away from that stuff.  You should be glad I didn't get in your way,'' says Jonah.

``Either that, or you're not doing your job,'' counters Riva.

Jonah looks very serious and kind of sad for a moment.

Riva continues, ``Anyway I don't think I'm pregnant.''

``What?''

``I don't think I'm pregnant.  That's why that guy was watching me, right?''

``Yeah mostly.''

``He was a little creepy.''

``Yeah well I needed someone to make sure you were okay.  I haven't been able to check in as much as I have wanted to.''

``Why not?''

``Work is not what it used to be,'' says Jonah.

``Is that why they are letting people get away with all kinds of shit these days?''

``Yeah, that's part of it.  I don't know where to start.  Sure you don't want something stronger than water?''

``Nah, it makes me sleepy and then I make bad decisions,'' says Riva.  Jonah pours himself a strong drink.

``Okay listen,'' Jonah says.  ``I have some hard things to tell you, and no good way to do it.  Like, you haven't seen this place before, right?''

``No,'' says Riva and then she looks at Jonah. ``Have \textit{you}?''

``Yeah.  Well....not recently.  But it's one of the ways I have been able to get more water and food.''

``\hl{An empty apartment}\footnote{\textbf{q.google }Jonah \_did\_ actually live in the apartment before SAC-09. \textsubscript{09/25/14 3:49pm}}?'' says Riva, dubiously.

``See you have to fit in, look like they do. Live like they do.  Then they give you the money they got.''\footnote{\textbf{Suko T }Rebecca and I were giggling at this because the natural conclusion from this line of reasoning was that Jonah was a prostitute or kept ``mister'' for some sugar mama (or sugar papa, no judging). \textsubscript{09/17/14 3:00pm}}\footnote{$\rightarrow$\textbf{q.google }Yes.  Though it's also a natural conclusion that this is what you do when you have a mark and you are trying to make a hard sell of any other kind. \textsubscript{09/25/14 3:48pm}}

Riva looks like she almost is catching onto Jonah's hints but not quite.

``Anyway,'' Jonah continues, ``This apartment came from a friend who didn't need it anymore.''

``A friend?  Just gave it to you?''

``In a manner of speaking, yeah.''

\hl{Riva narrows her eyes, ``When someone says 'in a manner of speaking' it means they did something wrong.  Did you murder somebody?''  Riva looks under the bed.}\footnote{\textbf{Suko T }And this is when I fell in love with Riva :D \textsubscript{09/16/14 1:21am}}

``No!  No.  \hl{I haven't murdered anyone}\footnote{\textbf{q.google }It's not ``murder'' if Greedo shoots first. \textsubscript{09/25/14 3:50pm}}. I killed some people but they were shooting at me.  But that's a fact of war.''

``Wait- I thought that was just a rumor.  There really is a war?  I thought that they just couldn't afford to pay the beat cops anymore.''

``No, the war is happening.  It hasn't started properly yet but it's just a question of when. Okay the bad news is this.  I don't think the war is staying away from home.  I think it's coming here.  Did you hear about Borroughs?''``Uh, just that they're having station problems, I dunno,'' Riva shrugs.  ``I heard that there were some problems, like the train tracks were broken.  Is that where you were fighting?''

``Yeah, actually.''

``But our station is safe- oh wait you said it wasn't anymore.''

``Uh...yeah, I don't think it's going to stay safe.  I....need to ask you something difficult.''

``You keep saying that,'' says Riva impatiently.

``It's difficult!''

``Well fucking man up and just ask me!''

``Look I didn't want to tell mom and dad about all this.''

``What is 'this'??  You keep dancing around the fucking topic.  Even Adriano didn't fucking beat around the bush this much,'' says Riva, sounding frustrated.  Jonah starts laughing.   She continues, ``I mean he was shy at first and shit, but seriously, you're scaring me!  What the fuck is going on?''

Jonah stops laughing and says intently, ``Yeah that's the thing.  I'm scaring you.  This is scary.''

``Then FUCKING SAY IT ALREADY.''

``There's a war coming and they're going to destroy everything and I don't want you here when it happens.''

``Why don't you stop them?''

Jonah's eyes go wide.  ``Because it's not \textit{easy}?  We're trying.  But you can't stop a war just by putting up your hands.  Bullets move faster than you can see.  Bombs destroy whole buildings.  You can't stop them just by saying 'hey stop!'''

``So what's the fucking point then?  If we're all going to die.''

``Because I want you to leave.''

``What are you talking about?  We can't leave.''

``I have a place you I can take you.''

``We're not allowed to leave.  Not without joining the TA or having some sort of special job.''

``Or knowing someone who can get you out.''

``Isn't that illegal?  Not the 'you shouldn't do it' illegal, but the fucking 'they will shoot you or beat you' kind of illegal.''

``Not if I tell them to let you through.  But I can only get you and mom and dad through.  No one else.''

``Where would we go?''

``There's a place that's safe for the moment,'' says Jonah slowly.  ``And...you'll see more of me....I don't know if that's a good thing or not.''

``Oh.  I get it.'' says Riva flatly.

``Do you?'' says Jonah, sounding skeptical.

``You want \textit{me} to tell mom and dad.  So the big scary thing is that you want me to convince them to come with you.''\textless 3

``No, the big scary thing is there are buildings that are going to be coming down around our ears,'' says Jonah.

``\hl{BULLSHIT}\footnote{\textbf{Suko T }\textless 3 \textsubscript{09/16/14 1:50am}}!'' exclaims Riva angrily.  ``\hl{How long have you been gone?  Why haven't you talked to them?  What did you do that you can take us out of here?}\footnote{\textbf{q.google }This is one savvy thirteen-year old.  Tremble in fear all you Caesars and Preceptors! \textsubscript{09/25/14 3:53pm}}  We're lucky the TA doesn't bother us.  We don't do anything.   We just raise klipspringers and starve except for the shit that you pull in that I'm not supposed to tell mom and dad about but they know it's coming from somewhere \hl{so they think I'm a whore}\footnote{\textbf{q.google }Dontthinkaboutheguiltdontthinkabouttheguilt---arrrrgh! \textsubscript{09/25/14 3:53pm}} or something...I mean, Dad nearly killed Adriano!  Which he fucking deserved but whatever.''

``What would you have done without that food and water?'' asks Jonah a little coldly.

``We would have died.''

``Okay so maybe, just maybe you should stop and think about that before you start accusing me of things,'' says Jonah angrily.

``I'm not accusing you of anything!!  I just want to know why all this is on me!''

``It's not all on you!'' denies Jonah.

``\hl{Yes it is!!}\footnote{\textbf{Nathaniel Ford }Not sure this entirely came through, but from an author's perspective I feel the need to say the intent was to prove Riva is a teenager and everything is about her even if it's not. \textsubscript{09/23/14 12:26am}}\footnote{$\rightarrow$\textbf{Suko T }Problem is that she made a pretty convincing case that it really IS all about her. :)  But yes, I certainly thought she acted like a teenage girl with equal parts bravado and sulking. \textsubscript{09/23/14 1:02am}}\footnote{$\rightarrow$\textbf{q.google }She's being a great lawyer but not a great diplomat.  Which is, yes, what you would expect from a sharp teenager. \textsubscript{09/25/14 3:55pm}} You want me to go tell mom and dad that you've been alive for three years and didn't want to talk to them.''

``No, I want you to tell mom and dad that you have a way out and then I'll talk to them.''

``How do you think I'm going to convince them?  They don't trust me about anything.''

Jonah sighs and gets up to pick up something.  He gives Riva his old medic's satchel.  ``Here.  Among other things, this will have meds for Mom's cough.  But see this patch?  Mom put that there.  She'll know what it is.''

Riva looks at the bag and then sighs and says grudgingly, ``Okay, what do you want me to do?''

``Tell them that you found me, and I'll explain everything, but I need for the three of you to come to me.  I'll get you on a train and get you out.  Take what you can carry, but not more than that.''

``So get them to a train station?  What if they don't want to come?'' asks Riva.

``What shape are they in?  Are they able to walk around?''

``Yeah, we gotta eat.''

``Then food will do it.  You need it anyway.  I have several boxes of food I want you to take back with you.  Better than the usual stuff.  And tell them there's more where that came from.''

``Okay.''

``And I'll explain everything when they come.''

``Okay.  But.....'' says Riva, sounding dubious.

``\hl{Mom I could talk to, but never Dad.  If I showed up at his door, after everything else, after we were through all the 'where have you been?' stuff, and I tried to convince him, he wouldn't come.  He never listened.}\footnote{\textbf{q.google }Didn't know any of that before this paragraph. \textsubscript{09/25/14 3:56pm}}  Which is fair.  He doesn't have to.  \hl{Fathers don't have to listen to their kids}\footnote{\textbf{q.google }Uh... not sure why he thinks that.  I think it's a combination of guilt and self-justification: He's leaving unsaid that kids don't have to listen to their fathers either.  That would take the conversation where he doesn't want it to go. \textsubscript{09/25/14 3:58pm}}.''

``Is there water where we're going?  And food?'' asks Riva.

``Yeah.  Here try some of this,'' Jonah gives Riva some fancy food like fresh fruit.

``That is pretty good,'' says Riva.  ``But there are two things, two parts of the deal.  The first part is that you owe me one thing.''

``What's the one thing?''

``No, I don't have to say.  You \textit{owe} me.  That's the deal.''

``You want \textit{me} to owe \textit{you} something for saving your life?''

``No!  I want you to owe me something for having to deal with mom and dad.''``That's fair,'' Jonah agrees, laughing wryly.

``The second, you have to answer a question,'' says Riva.  She takes a breath and looks at Jonah.  ``Did you want to leave?''

``You mean why I didn't show up?  Or wait- leave where? Now?  Before?''

``\textit{Before}, stupid.''

``A little bit yeah, but that's not why I didn't come back.''

``Okay.''

Jonah sighs.  ``So my answer is this, yes I owe you.  And I'll answer your question but I have to have your word that this is just between us.  I bring it up with mom and dad on my time.  \hl{You don't bring it up with anyone else}\footnote{\textbf{q.google }He actually means he doesn't want her to bring it up \_at SAC-09\_.  But the way to do that is to make her think he doesn't want her to tell their parents. \textsubscript{09/25/14 4:00pm}}.  Not a soul.''``You can trust me, I haven't told anyone about this \textless she gestures around the apartment and at Jonah\textgreater , not even Adriano.''

``I do trust you, that's why I will tell you this.''

``Okay well just spit it out already!''Jonah pours himself and Riva another drink.  She eyes the drink suspiciously.  Jonah is silent for a while and then starts speaking.  ``The good thing about being a medic is that you're not at the front lines.  You know how people can dodge a rock?  \hl{You can't dodge a bullet.}\footnote{\textbf{Suko T }Peanut gallery was whispering to each other that actually Jaya just dodged/deflected some bullets recently and Hayley kicked a grenade out of midair.... :D \textsubscript{09/16/14 2:22am}}\footnote{$\rightarrow$\textbf{q.google }The grenade kicking especially was \_hardcore\_ :).  The fans were all over the boards posting about that episode. \textsubscript{09/25/14 4:02pm}}  Being a medic means you can save people who are getting shot, though you don't get shot at as much.  There are all kinds of people there, not just Franchise, but Nationals, even Citizens.  One of the ones I made friends with was a National.''  Jonah pulls out his dogtags and shows them to her.  ``See those words there, there's two of them.''

``Wait a second, these are the tags you wear?  You only have one name.''

``Nationals have two names.  They have a personal name and a family name.  There's a guy named \textless Jonah takes a long drink and pauses again for a long time\textgreater  Jonah Gemayel.  He's a medic.''

``He's a friend of yours?''

``He was.''

``Oh.  So he's dead.''

``Yep.''

``How does he help you if he's dead?''

``Well a lot of people don't know he's dead....'' says Jonah trailing off and watching Riva.  Riva catches on almost immediately.

``Wait \textit{really}?  They haven't caught you yet???'' says Riva, her voice rising.  She slaps the table.  \hl{``NO \textit{WAY}!  You're not that smart!!''}\footnote{\textbf{Suko T }Spoken like a true sibling. \textsubscript{09/16/14 2:31am}}\footnote{$\rightarrow$\textbf{q.google }And the moment where Jonah knows he's persuaded her -- and that the hardest part is over. \textsubscript{09/25/14 4:04pm}}

``\hl{Maybe not, but no one else is either}\footnote{\textbf{q.google }''But \_you\_ are.  And I'm at least smart enough to get you \textgreater :).'' \textsubscript{09/25/14 4:07pm}}.''

``Wait, so you're pretending to be this Jonah guy?''

``These are his tags, his uniform.  Or it was his uniform.  Pretty much mine now.''

``So you're a National now?  You know they'll kill you for that.''

``Yeah.''

``They going to kill us too?''

``\hl{If they find out}\footnote{\textbf{q.google }Jaya really loves her sister in a really self-absorbed way, and Jonah really loves his sister in a really mercenary way.

He trusts you kid, and he'll give you the best deal he can, but he's leaving \_even\_ you as few angles as possible to take him down. \textsubscript{09/25/14 4:10pm}}.''

``So what do I tell mom and dad?  I...can't tell them that.  So I just get them to the train and you'll talk to them?''

``Yeah.  Look, if it had been up to me, three or four years from now, I would have shown you this place and asked if you wanted in.  You know why I didn't want to tell mom and dad?  For the same reason you don't want to tell them.  They can't keep a secret.  Mom's a terrible liar. ... Except that she's a \textit{little} smarter than that and we only \textit{think} she's a terrible liar\footnote{\textbf{q.google }This whole session is suddenly about what hidden dragons everyone's mothers are.... \textsubscript{09/25/14 4:11pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }You might replace 'session' with game and get the same result. \textsubscript{09/25/14 5:26pm}}\footnote{$\rightarrow$\textbf{q.google }You clearly know some things I don't know. ;)

(Tries not to wonder whether Rook even \_has\_ a mother....) \textsubscript{10/05/14 1:24pm}}.''  Jonah grins, one of the few happy grins he's had in a long time.  ``Have you figured that out yet?''  Riva smiles and nods.  Jonah is quiet for a moment and says, ``I've never told this to anyone else.'' Riva walks up to him and hugs him.  Jonah is shaking.  They hold each other for a while.  When Riva moves to leave, Jonah hands her some boxes of food, one for mom and dad and one for Riva.  Jonah tells her when and where to meet up with him and Riva leaves.  Jonah, still shaking, works his way through half the bottle and wonders how Jaya manages it.



The next morning, Jonah is at the station and sees his parents coming up the street in handcuffs, flanked by three TA constables and Riva trailing behind them.  Jonah lurks unseen as the lead constable reports to the front desk, ``\hl{I have arrest warrants for \_\_\_ and \_\_\_ (Timon's parents) and I'm to turn them into an Agent Gemayel}\footnote{\textbf{q.google }That was \_Kobayashi Maru\_ level brilliant.  It totally solves the problem and totally puts it on Jonah to deal with it.  His admiration actually exceeds his seething anger. \textsubscript{09/25/14 4:15pm}}.''  \hl{Riva is looking a bit smug.}\footnote{\textbf{Suko T }This is when the Peanut Gallery decided that Jaya really needs to adopt Riva. \textsubscript{09/16/14 10:49pm}}\footnote{$\rightarrow$\textbf{q.google }No, you know who needs to adopt Riva?  *Morgan*. \textsubscript{09/25/14 4:16pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Morgan *is* in the market for a new sister. After y'all killed her last one. \textsubscript{09/25/14 5:25pm}}\footnote{$\rightarrow$\textbf{Suko T }\textless 3 \textsubscript{10/01/14 12:13am}}  Jonah arranges for his parents to be taken to a private holding cell and pulls Riva aside.

``That was....interesting.  What exactly did you do?'' he asks her.

``You gave me some good shit so I traded it.  This guy who lives over the bar where I clean dishes- God I am not going to miss oil all over my hands- anyway he was a little behind on his payments so I made a deal with him.  I traded him the food and he put out an arrest warrant for our parents.  That way I didn't have to tell them much and \hl{I'm keeping our bargain- I'll tell them you're alive but I don't have to do it until right before you walk in is what I figure.''}\footnote{\textbf{Suko T }I am so on Team Riva right now. \textsubscript{09/17/14 2:13am}}

``Yeah I guess so.  They're going to be pissed anyway.''

``Yeah I figured, so better that they're in handcuffs,'' grins Riva.

``Okay...well this is going to be a real pain in the ass.  But that was impressive.''

``There's food where we're going, right?''

``Yeah.''

``Good.  That was really my only concern.  It was a reasonable risk.''

``Okay why don't you go in and talk to them, I'll be there in a few minutes.  You don't have to tell them anything, just tell them that I'm coming.''

``You...Jonah?  Or you...Timon?''

``Timon.''



Jonah makes sure that the interrogation room is private and no one will disturb him, and then he enters the room.  Timon's mom is lying on the bed in the room, and his dad is sitting next to her with his hand on her shoulder.  The handcuffs have been removed.  Riva is sitting in a corner with Timon's old satchel and their mom is staring at the satchel.  Timon's dad is staring off into the distance and \hl{looks stressed and upset}\footnote{\textbf{q.google }Jonah is worried about his father -- so that he doesn't have to stop and think about how much more worried he is about his mother. \textsubscript{09/25/14 4:17pm}}.



Jonah walks up to Riva, takes the satchel and sets it down between him and his parents.  His dad watches him. 

``I'm sorry about how you arrived here,'' says Jonah.  ``I don't have a lot of time and there was no simple way to do it.''

``I'm glad that you're alive.  Your mother was heartbroken,'' says Timon's dad with remarkable calm.  Timon's mom goes into a horrific coughing fit.

``\hl{There are some things that are easier to do dead than alive}\footnote{\textbf{q.google }QooC \textsubscript{09/25/14 4:18pm}}.  One of them is finally making sure we had enough food on the table.''

``Son, \hl{you know I don't approve of anything dodgy}\footnote{\textbf{q.google }He might know ... but we didn't.  A lifetime's of memories, created in an instant. \textsubscript{09/25/14 4:19pm}}.''

There is another coughing fit.  Jonah gets some medicine from the satchel and gives it to his mom.  She keeps coughing {[}and Rebecca flees the room{]}.

``I trust that you have your reasons, but this don't seem right,'' continues Timon's dad.

``\hl{No it's not right.  You know what else is not right?  Crossing the street and knowing it's even odds that someone's going to blow your head open.  It's not right watching people come back with injuries that make you want to vomit and still having to put people's guts back into them.  There's a lot of really really not right stuff, Dad}\footnote{\textbf{q.google }If there had been more time, and I'd been better prepared, this is a scene that could've used some Method. \textsubscript{09/25/14 4:20pm}}.''

``Forgive me son, but I'm a simple man.  I understand that you maybe saw some shit, excuse me Riva, but why you been gone so long if you ain't been dead?''

``I \textit{was }dead.  There's a guy out there that they buried with my name on him.  A friend of mine actually.''

``Now, you've always had your mother's brains and you're real smart and talk fancy, but I ain't dumb as bricks.  So if I understood you correctly, you sayin' that you ain't who you seem to be?''``Yes.''

``So you disavowed your name?''``No.''

Timon's dad looks at Jonah's uniform and says, ``I don't read too good but...\hl{that seems like a lie to me}\footnote{\textbf{q.google }Yeah, well you know they \_kill\_ you for the truth there right? \textsubscript{09/25/14 4:21pm}}.''

Jonah sighs.  ``Yeah.''

``And you think you have a good reason for that.''

``Yeah.  What food, medicine, and water I've managed to send to you for the last two years seems like a pretty good reason to me,'' says Jonah.

Timon's dad furrows his brow and then looks at Riva.  ``Well then.  I don't know if I should be relieved that my daughter ain't...well.  \hl{But my son's a liar}\footnote{\textbf{q.google }And a damned good one too.  This is why Jonah is closest to his sister.  She understands pride of \_craft\_. \textsubscript{09/25/14 4:23pm}}.''

``Your son's alive.''

``Sorry, I should have said- my \textit{children} are liars.  \hl{I don't think I raised you this way}\footnote{\textbf{q.google }What's \_wrong\_ with you man?! \textsubscript{09/25/14 4:23pm}}.  Where did I go wrong?''

``Simple,'' says Jonah.  ``You didn't prepare us for bombs being dropped on our heads every day for months.  What were you supposed to do about that, Dad?  Look.  You have damn good reasons to be really angry.  But I hid from you partially so that I could provide for you in a way that I couldn't do as just a street medic.  And I'm revealing myself to do more than that.  

There's a war coming, it's going to walk down the street and take down all the buildings and all your neighbors.''

``You come to save us from this?''``Yeah, I have a way out.  Which I've earned, for what it's worth.  No lies here.  The job I am doing is much more dangerous and difficult than I ever thought it would be.  Much more than I ever signed up for.''

``Danger don't justify lies.  But I understand.''

``Does it justify saving you?  Because that's what I want to do.''

Timon's dad frowns.  ``I ain't going to say that this is over.  I ain't going to say that I agree with your choices.  I ain't going to say that you leaving to go join up to be a street medic was a good choice.  I ain't going to agree to that.  But \hl{your mother is sick and I love her very much}\footnote{\textbf{q.google }That's actually his best reason for coming, though he probably doesn't know it yet. \textsubscript{09/25/14 4:25pm}} and bless my soul, despite everything else, I love you too.  So I'll trust you with this.  But we're going to talk about this.  This ain't an example to set for your sister.  And it's no way to honor me or your mother.  Look at at this place.  Look at the pain in this place.  Ain't no one been here who ain't been in pain.''\footnote{\textbf{Suko T }I really liked this monologue.  Says so much about Timon's dad, the life they've led, and their family relationships all at once.  Timon may have got his mother's brains, but he got his dad's sensitivity. \textsubscript{09/17/14 2:12am}}

``No.  No one who lives to be my age anyway.  Maybe Citizens, but even they...'' Jonah trails off.

``Tell me we don't got to stay here?'' Timon's dad asks.

``No, but we do have to leave on the next train.  So if you're coming, you have to come now.''

``So you saying we have to leave everyone behind?''

``For the time being anyway.''

``They goin' to die?''

``I hope not.  It's part of the job I'm doing-''

``But what do you think?''

``I don't think the odds are good.''

``Like I said, I will trust you, at least this far.  But I don't feel good about it.''

``The only thing you have to do, and you have to decide this before we go, is that this story, if we're all going to stay safe, has to stay between us.  I \textit{am }this man, at least until we decide otherwise.

``So you want me to say that you ain't my son?''

``No they know we're family.  They probably won't ask a lot of questions.  Just use the name.  You're going to have to decide if that's acceptable.   \hl{If you walk in without agreeing to that, then my taking you there to be safe is not going to help}\footnote{\textbf{q.google }That's a lot smoother than I expected.  I have some insight into how Jonah survives. \textsubscript{09/25/14 4:27pm}}.''

Timon's dad gently rubs Timon's mom's back and says evenly, ``Well, I suppose we all have our price.''




\sceneHeadline{\hl{Hayley's Shore Leave- DX Station}}\footnote{\textbf{Suko T }Rebecca's written commentary interlaced with her note-taking during this scene was hilarious to me.  So I changed up the format here to include it in the blue column alongside the transcript so you can enjoy it too :D \textsubscript{09/16/14 2:51am}}+1\footnote{$\rightarrow$\textbf{q.google }Also: Hayley + Fili is \_awesome\_.  It's like hooking up two copies of Eliza to each other only \_much\_ funnier. \textsubscript{09/25/14 4:54pm}}

\sceneHeadline{Shore Leave Epilogue}

After working out some payment arrangements with Padme, Jaya makes a weak excuse that she has to go ``'cause I, uh, owe someone money...'' and flees.  She and Jayce find a hotel and, with nobody else around, have really loud sex.  Afterward Jaya goes over the rules for Jayce to bring the money to Padme.  ``If you steal the money, I will hunt you down and kill you.  If you sleep with my sister, I will hunt you down and kill you.  Twice.''  Jayce is fine with the first one but mutters ``goddammit'' under his breath at the second.  Jaya makes sure he really really believes her on the second item.



Rook picks them up at the station the next morning.  Jaya is slightly high, slightly drunk, very hungover and ready to puke as she contemplates asking Morgan for money.  She would have asked Rook but even she realizes she kinda burned that bridge. For now anyway.



At the Bucket, Jonah boards the train with his family.  When Jaya sees the kid board the train, she stands up and goes, ``Whoa whoa whoa!  What the fuck is this?''

``Personal,'' says Jonah shortly.

``Yeah I can fucking see that,'' says Jaya.  She looks at Riva suspiciously.  ``Is she yours?''

``Excuse me!'' says Riva, sounding offended.  ``I'm fourteen!'' and then adds under her breath, ``\textit{almost}.''

``Chief!  PERSONAL.'' says Jonah very firmly.

``Ewww!'' exclaims Riva.  Timon's dad starts looking a little concerned.

``I'm your superior officer and I need to know what the fuck is going on,'' says Jaya to Jonah.

``\hl{No.  This is not a military situation Chief.  You want me to quote chapter and verse?  \textit{Personal}}\footnote{\textbf{q.google }Jonah's unstated contract with Jaya, is (apparently): I don't poke at your personal stuff, you don't poke at mine.  Whether Jaya sees is that way is of course story entirely, but if you look back it explains a lot of how Jonah tries to interact with Jaya. \textsubscript{09/25/14 4:57pm}},'' he replies.

``\hl{She's your superior officer?'' asks Riva, incredulously}\footnote{\textbf{q.google }I'm telling you kid: it's a very weird world out there! \textsubscript{09/25/14 5:00pm}}.

Rook says over the intercom, ``We got a problem back there?''

Jaya gets on the intercom and says, ``Uh, yeah, there appear to be some refugees...''

``Also, I made arrangements with Rook,'' says Jonah.

``Negative, Agent, arrangements have been made,'' says Rook at the same time.

Jaya holds down the talk button so Rook can't speak, but she doesn't say anything for a long moment as she fumes.  Finally she grumbles, ``Understood.''  She gives the Jaya FaceTM\footnote{\textbf{Nathaniel Ford }Beautiful \textsubscript{09/23/14 12:54am}} to Timon's family and then goes to sit with Jayce on the other end of the train.



Out of earshot of their parents, Riva leans over to Jonah and says, ``Soooo... I'm betting three months'' and she glances toward Jaya and Jayce.

``Okay, bet,'' says Jonah.  ``She's unpredictable.''

``Oh no no, that's how long- wait, you don't know??''

``She's unpredictable,'' Jonah repeats.

``So it's been less time that?  They seem very comfortable with each other.  Well... he seems comfortable with her.  She doesn't seem comfortable with anyone.''

``\hl{Hold your thoughts for when we get there.  Then tell me what you think when we arrive and I'll tell you what I think.''

``Alright,'' shrugs Riva}\footnote{\textbf{q.google }We should play that out at some point. \textsubscript{09/25/14 5:02pm}}.



At DX Station a stunningly gorgeous woman is waiting to board the train.  There's a bit of a commotion on the platform as people attempt not to stare at her.  She is walking confidently like a supermodel at Fashion Week, and there's someone walking next to her, carrying some luggage.  



The woman is Hayley but you've never seen her look like this before.  She's wearing a beautiful dress, 5 inch heels and is immaculately made up and styled. The slinky, \hl{revealing}\footnote{\textbf{Rebecca S. }query: how does revealing work with Hayley's scars? 
I REFUSE TO GIVE UP THE NOTION OF INDIA therefore I had been imagining something like the coral dress in this picture* but way more tailored on a way more busty lady and a mid-calf hem. 
Thoughts?

* http://akkidokie.files.wordpress.com/2012/10/manish-malhotra-at-wills-lifestyle-india-fashion-week-ss13\_11a.jpg \textsubscript{09/18/14 9:46am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Those dresses are gorgeous. \textsubscript{09/18/14 10:47am}}\footnote{$\rightarrow$\textbf{Suko T }Seconded, the fabrics are beautiful!

Actually you're pretty close to what I was thinking with that coral dress.  In my head, I was picturing something cheongsam-like:
like the green dress on the right but shorter
http://eterneljourney.files.wordpress.com/2012/01/1.jpg
or like this
http://media-cache-cd0.pinimg.com/236x/5e/0f/8d/5e0f8d444da53c471b41d460a7cdb59b.jpg

and a more clever neckline like this where the appliques hide some of the scars underneath butterflies and such, like this
http://modernqipao.com/wp-content/uploads/2014/03/17/Green-hand-beading-modern-qipao-Chinese-cheongsam-dress-005.jpg 
or this
http://www.beautifulhalo.com/transcendent-sheer-neckline-vback-evening-dress-featuring-tulle-overlay-and-exquisite-applique-p-97545.html \textsubscript{09/18/14 1:32pm}} dress is tailored to every curve and looks like it costs more than Jaya makes in a year.  It takes a moment to even notice she still has her rifle incongruously slung over her shoulder.  Her Agent badge is on display but \hl{neatly attached to a scarf}\footnote{\textbf{Rebecca S. }although reading the commentay I now wondering if something more like this*  (again more tailored and more busty with slightly shorter hem)

* http://fashionparo.com/wp-content/uploads/2014/04/Luxury-Indian-Girls-Georgeous-Stylish-Dresses-2014-Outfits-7.jpg \textsubscript{09/18/14 9:47am}}\footnote{$\rightarrow$\textbf{Suko T }I like that one too but I think it's too pretty and sweet with all the light flowy layers.  Hayley's dresses are definitely sexual, though juuust tasteful enough to avoid being skanky or tacky.  They are meant to display her like you'd show off a sports car or really expensive jewelry. \textsubscript{09/19/14 4:18pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Results: http://simply-sithel.tumblr.com/post/98152621044/wooden-pose-and-look-but-i-had-to-try-and-capture \textsubscript{09/22/14 9:36am}}\footnote{$\rightarrow$\textbf{Suko T }SO AWESOME.  I love it.  I adore the sparkles and the fact that she's in pink.  Gun came out great, I'm glad the bullpups use a shoulder strap like that, so we can see more of it.  Pose works just fine because she doesn't generally move seductively/flirtatiously, she poses more like a dancer.  The pose looks like she just went ``sashay step spin step step spin ta-DA!'' for Jonah :D \textsubscript{09/22/14 11:21am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Holy eff. I need to keep up with your blog, Rebecca. Those are some awesome sketches. \textsubscript{09/22/14 8:32pm}}like a broach so it becomes part of the ensemble.



As she boards the train, everyone's jaw drops, except Timon's father who grits his teeth not to gape at her, Timon's mother who is either too sick or too good at hiding her emotions to show a reaction, and Rook, whom no one can see.  Hayley barely notices the new arrivals and simply walks up to Jonah and smiles hugely. \hl{She says girlishly, ``Hi.''}\footnote{\textbf{Suko T }In heels she may be taller than Jonah.  I don't know how tall Jonah is, but Hayley's tall for a woman (good nutrition since infancy) so in her ridiculous heels she is possibly getting close to Agent Morgan-tall. \textsubscript{09/17/14 11:23pm}}\footnote{$\rightarrow$\textbf{q.google }I think she is taller even without heels.  Jonah is not tall: 5'6'' or 5'7''.  (Smaller targets are less likely to be hit by stray bullets.  Every little bit counts.)  Nutrition counts for a \_lot\_ in height.  No matter what else they did to Hayley I assume they fed her properly. \textsubscript{10/05/14 1:39pm}}

Jaya replies, ``Hi'' even though Hayley's not even looking at her.  ``Hello, Sir,'' says Hayley politely to Jaya and then turns her attention back to Jonah.  \hl{Jonah says nothing}\footnote{\textbf{q.google }Total traffic jam in Jonah's head.  No idea what to say or even how to say anything at all. \textsubscript{09/25/14 5:03pm}}.

Riva is starstruck and speechless.

Jaya starts snapping her fingers and saying loudly, ``Hayley, Hayley!  Come over here!  Leave the refugees alone.''

``Hey!  You don't get to talk to her like that,'' says Riva protectively.

``Oh but I was going to sit-'' Hayley gestures to the seat next to Jonah. 

``Shove it refugee!'' Jaya yells at Riva and then gestures to Hayley. ``Come sit next to me, Hayley.''  Jaya pats the seat next to her.

``I'm afraid she is my ranking officer, \hl{I do have to follow her orders when they are not unreasonable}\footnote{\textbf{q.google }Hey!  Where did the ``when they are not unreasonable'' come from?  More specifically, when did \_Hayley\_ figure it out? \textsubscript{09/25/14 5:04pm}}\footnote{$\rightarrow$\textbf{Suko T }Session 19 \textsubscript{09/25/14 5:29pm}},'' says Hayley apologetically to Riva.

Hayley walks over to Jaya but does so veeery slowly and shamelessly poses for Jonah like she's walking on a fashion catwalk the whole way.  Jonah still says nothing.



Riva follows Hayley, clearly fanboy-ing Hayley.  When Hayley sits down, Riva cocks one hand on her hip and challenges Jaya, ``Jealous?''

``Fuck off kid,'' says Jaya, making a shooing motion.  ``There's no room here-''

``Oh no, there's room, she can sit here,'' says Hayley, not understanding and gestures to the seat across from her.  Riva sits down.  

Jaya makes an exasperated noise and yells at Jayce that he was supposed to occupy all the seats so that there wouldn't be room for another.

``There are so many beautiful women around here, why does it have to be a competition?'' sighs Jayce.

``Really?'' asks Hayley, \hl{looking around curiously for the other beautiful women}\footnote{\textbf{q.google } \textsubscript{09/25/14 5:05pm}}.

``Don't look at the little kid when you say that,'' Jaya says menacingly to Jayce.

``No offense kid, you'll get there one day,'' Jayce says to Riva, and he gets up and goes to the front of the train, saying under his breath as he passes Hayley, ``I need a cold shower.''

``I know we're on shore leave-'' starts Jaya.

``Don't I look pretty?'' interrupts Hayley with a big smile, flipping her hair back expertly and posing for Jaya.

Jaya is speechless.

``You look \textit{gorgeous},'' says Riva.

``Thank you!'' preens Hayley.  ``I worked hard at it.''

``Can you show me how?''

``No!'' says Jaya.

``Yes!  It takes a little while but I have the cosmetics in my bag over there...'' says Hayley.

``Really?'' says \hl{Riva}\footnote{\textbf{Rebecca S. }so excited for Riva to be on base! Can she join Patrol Group 1 yet? We need a new Constable Trainee! \textsubscript{09/18/14 10:02am}}\footnote{$\rightarrow$\textbf{Suko T }Motion seconded! :D \textsubscript{09/19/14 4:18pm}} excitedly.

``No!  Hayley- we are officers of the law. We are supposed to- to-''

``Oh it's right here,'' says Hayley brightly, showing Jaya her Agent badge.  ``See, I coordinated it with my scarf.''

``Yeah, I see....it's \textless ahem\textgreater  right there...with your boobs... and um, hemline....and ...uh...boobs...'' Jaya trails off, gesturing vaguely at Hayley's exposed \hl{cleavage}\footnote{\textbf{Suko T }If Jaya looks closely enough, the scars on Hayley's chest that would have been visible in such a revealing dress have been expertly covered with makeup.  Also, the shape of the neckline seems to be precisely cut to discretely cover as many of the scars as possible, while cleverly appearing not to cover very much of anything at all. \textsubscript{09/18/14 12:05am}}and short hemline.

``Oh don't worry, it only looks like they will fall out,'' says Hayley cheerfully.  ``They won't really.  It's a very well tailored dress. See?'' and Hayley bows forward deeply to demonstrate, rendering Jaya speechless again.  And similar silly hijinks ensue.



\hl{Jonah eventually starts treating his mother's cough.}\footnote{\textbf{Nathaniel Ford }Hayley: so hot she makes grown men forget about their ailing mothers. \textsubscript{09/18/14 10:49am}}\footnote{$\rightarrow$\textbf{Suko T }Ha! :)  If only we had to deal with more ailing mothers, I could use Gorgeous all the time! \textsubscript{09/18/14 1:33pm}}  The train returns to SAC-09.


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: A thing of beauty, this., unable to correctly match (exceeded acceptable limit):ExpectedIts my awesome.  And its going to be your fucking sadness

	Unable to find a matching comment for footnote: _Marked as resolved_

	Unable to find a matching comment for footnote: _Re-opened_

	Unable to highlight for footnote: A vital key for insight into Jaya brain, unable to correctly match (exceeded acceptable limit):ExpectedWell Im a really important person now.  Ive got all this information in my head and this armTheyre trying to get at me through you.  Cause youre my fucking sister and I love you and I want you to be okay.  The important thing is that you need to not get caught because that would compromise my position.

	Unable to highlight for footnote: That is _awesome_.  Years of RP interaction summed up in just three words.  Grendel move over.

Jaya's scene endings are always the Best Television Ever., unable to correctly match (exceeded acceptable limit):Expectedshes like Mom.

	Unable to highlight for footnote: Rebecca and I were giggling at this because the natural conclusion from this line of reasoning was that Jonah was a prostitute or kept "mister" for some sugar mama (or sugar papa, no judging)., unable to correctly match (exceeded acceptable limit):ExpectedAn empty apartment? says Riva, dubiously.
See you have to fit in, look like they do. Live like they do.  Then they give you the money they got.

	Unable to understand footnote <3, too many options & none that matched to tell mom and dad. So the big scary thing is that you want me to convince them to come with you.. Optional comment markups: \footnote{\textbf{Suko T }<3 \textsubscript{09/18/14 1:12am}}\footnote{\textbf{Suko T }<3 \textsubscript{09/18/14 1:04am}}\footnote{$\rightarrow$\textbf{Suko T }<3 \textsubscript{10/01/14 12:13am}}\footnote{\textbf{Suko T }<3 \textsubscript{09/16/14 1:50am}} 

	Unable to highlight for footnote: This whole session is suddenly about what hidden dragons everyone's mothers are...., unable to correctly match (exceeded acceptable limit):ExpectedExcept that shes a little smarter than that and we only think shes a terrible liar

	Unable to highlight for footnote: I really liked this monologue.  Says so much about Timon's dad, the life they've led, and their family relationships all at once.  Timon may have got his mother's brains, but he got his dad's sensitivity., unable to correctly match (exceeded acceptable limit):ExpectedTimons dad frowns.  I aint going to say that this is over.  I aint going to say that I agree with your choices.  I aint going to say that you leaving to go join up to be a street medic was a good choice.  I aint going to agree to that.  But your mother is sick and I love her very much and bless my soul, despite everything else, I love you too.  So Ill trust you with this.  But were going to talk about this.  This aint an example to set for your sister.  And its no way to honor me or your mother.  Look at at this place.  Look at the pain in this place.  Aint no one been here who aint been in pain.

	Unable to understand footnote +1, too many options & none that matched \footnote{\textbf{Suko T }Rebecca's written commentary interlaced with her note-taking during this scene was hilarious to me. So I changed up the format here to include it in the blue column alongside the transcript so you can enjoy it too :D \textsubscript{09/16/14 2:51am}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{09/25/14 5:25pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:41pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:28pm}} 

	Unable to understand footnote +1, too many options & none that matched \footnote{\textbf{q.google }I am not a number! I am a ... carefully cultivated slave with a name and public image. And also a number. \textsubscript{09/25/14 4:40pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{09/25/14 5:25pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:41pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:28pm}} 

	Unable to highlight for footnote: The Hayley motto.  Be prepared and PROTECT EVERYONE, unable to correctly match (exceeded acceptable limit):ExpectedAre we likely to be attacked?
You, probably not.  But I may.
Here and now?
I hope not, but it is possible.
I am uneasy, say the Fili calmly.
I understand.  That is why I have it, says Hayley, with the same equanimity.  She adds, I will protect you also.

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }You may be under a misapprehension that praetors protect 'everyone'. \textsubscript{09/25/14 5:19pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{09/25/14 5:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{09/25/14 5:25pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:41pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{09/25/14 4:28pm}} 

No. I do not.
And you think there may be a possibility that you may die.
Yes.
Yes, says Hayley firmly.
Noted

	Unable to highlight for footnote: Beautiful, unable to correctly match (exceeded acceptable limit):ExpectedJaya FaceTM


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:04pm
\end{flushright}

