\setcounter{chapter}{ 32 }
\chapter{\textbf{``SAC-04'', part 1} }

\subChapterTitle{``Grave Rot'')} 

\deets{Suko}{Sept 24th, 2014}



Another nightmare session for Jaya- no drugs, no sex, and having to be on the same mission as Lackovich and Drake.  She also has additional KP duties under Jari.  Must be another Tank Session!   Jonah's session isn't so great either as he gets propositioned by Hayley, his family is bored and he has to contend with the terrifying sight of a river and jungle.  Hayley is pretty content, she gets swanky new custom-fitted uniforms from Morgan, a hug from Carruthers and makes Drake blow his cool.  



\noindent\hrulefill




\sceneHeadline{SAC-09}

The train pulls into the SAC-09 station and there is a welcoming party.  Morgan is there in her usual BDU.  Hekate is there in her labcoat with Swan at her side.  Micah is in full battle uniform.  Karil is in the gun platform, looking a bit bored.  Carruthers is there too.



When the train doors open, Micah barks an order for the constables to form up.  Jaya gives Riva a look and saunters off the train. Hayley, still in her dress and heels, follows Jaya and lines up with her.  She salutes Morgan and so does Jaya.  Jonah joins them eventually.  Micah points to Timon's family and tells them to wait to one side of the platform.  He tells Jayce to line up with the rest of PG1.  J\hl{aya gives Micah an annoyed look}\footnote{\textbf{Nathaniel Ford }Micah fails to notice. \textsubscript{10/01/14 12:12am}}.



Dr. Gerhauser is staring off into space.  Morgan looks down the line at each of us (Jaya, Jonah, Hayley and Jayce).  Swan is gaping at Hayley, \hl{the only one on the platform to overtly and visibly react to her new look}\footnote{\textbf{q.google }Which is sort of ridiculous.  Everyone is just \_too\_ cool. \textsubscript{10/05/14 1:41pm}}.  



Dr. Gerhauser steps up to Jaya and asks for her right arm.  She draws a blood sample and hands it to Swan.  ``I hope I'm getting something to replace that,'' says Jaya.  Dr. Gerhauser looks at her a bit blankly, ``What?''  ``Nevermind,'' says Jaya.  Dr. Gerhauser moves on to Jonah and Hayley, taking samples from them as well.  Rook exits the train at this point and stands near the train.  



Jonah is watching everyone else on the platform.  No one looks very anxious.  Karil even looks bored.  Morgan is watching all of us, but mostly Hayley, though Morgan has her usual stone-faced expression.  Carruthers is looking interested in the whole situation.  Micah looks surly, like he usually does.  Jaya looks bored.  



When Kate gets to Jayce, he asks if he has to, and Morgan says yes, so he lets Kate take a sample.  Kate then draws blood from Timon's family.  Timon's dad offers himself first but Kate takes blood samples from all of them.  Riva yelps a little.



Kate and Swan analyze the samples and confer quietly.  Hekate says to Morgan, ``Mohinder was correct. Also Jayce. The family is clean.''  



Morgan walks up to Jaya and says, ``Agent, report to Medbay.''  Jaya rolls her shoulders and heads off.

Morgan turns to Jonah. ``For the time being, your family will be restricted to Alpha Zed sector.  We'll arrange visits as your duty allows.  Dismissed.''  Jonah goes to his family and tells them to listen to Rook and that he'll come visit them the next day.

``Agent,'' says Morgan to Hayley. ``Feels good to be dressed for battle, doesn't it?''

Hayley smiles cheerfully, ``Yes, sir.''

``Welcome back.  Dismissed.''``Thank you.''  Hayley fetches her luggage from the train and goes trotting after Jonah.

Morgan tells Jayce, ``Medbay.''

``Really?'' says Jayce.

``Yes,'' says Morgan with tone that conveys that this is serious.  Jayce heads off to Medbay.

Morgan addresses Timon's family, ``Micah will escort you to your quarters.  Any orders he gives, you will follow absolutely.''

Finally Morgan turns to Rook, ``Agent.''  ``Agent,'' he replies.  They look at each other for a long moment, clearly communicating something unspoken.  Morgan continues, \hl{``You are cleared for your operation.}\footnote{\textbf{Rebecca S. }Am I just being dense again or do we not know what operation this was? \textsubscript{10/01/14 8:32am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }No one asked and it wasn't stated in the scene. \textsubscript{10/01/14 9:25am}}\footnote{$\rightarrow$\textbf{q.google }You are not being dense: when in doubt, they didn't explain.  If we Needed To Know they would've told us.  I'm sure of it ;). \textsubscript{10/05/14 1:46pm}}``  Rook gets back on the train.

Jonah tells Micah, ``Go easy on them, okay?''

``I'm not a monster,'' says Micah, sounding a little offended.

``I didn't say you were, it's just that this is all new to them,'' says Jonah placatingly.

Micah leads Timon's family away.

The train departs.




\sceneHeadline{Medbay- Jaya and Morgan}

Jaya is hanging out in Medbay.  Jayce comes in a few minutes later.  Swan takes their vitals and then walks Jayce to a separate room.  Morgan and Hekate walk into Medbay.  Jaya's got her feet up on a table and knocks some things over as she stands up. ``Agent Sir Ma'am,'' Jaya greets Morgan and then greets Dr. Gerhauser, ``Doctor Ma'am...Sir...'' Jaya trails off with a confused expression.  She regroups and asks, ``So am I cleared to return to my bunk?  I could use some rest, from my....rest, so I am rested for the upcoming mission...''

``So I have some bad news,'' says Morgan.  ``You seem to have become infected with a fairly virulent disease.  I'll let my sister go over the details.''

Dr. Gerhauser says, ``Colloquially it's called grave rot.  I don't know what you got into-''

\hl{``It was just a small pile of bodies!'' Jaya protests.  ``I was only in them for five, \textit{maybe} twenty minutes.}  \footnote{\textbf{Suko T }Jaya is so awesome. \textsubscript{09/30/14 11:30pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }She really is. \textsubscript{10/01/14 12:15am}}I didn't want to be there.''

``I make no judgement,'' says Dr. Gerhauser, ``but you need to take the antibiotics.  It's a five day course.''

``Can I have something to...you know... chase them down with?'' asks Jaya.  Morgan frowns.

Hekate replies, ``\hl{In fact you will need to avoid all other drugs while you are on the antibiotics, otherwise you may go into shock}\footnote{\textbf{q.google }Or, as Jaya might put it: ``Welcome to hell.'' \textsubscript{10/05/14 1:50pm}}.''

``Uh, it would be pretty shocking to go five days on just one... I don't know if I'll be fit for duty if I have to deal with this.  Perhaps we can deal with this later....after the next mission.''

``Let me see your hand,'' says Hekate.  Jaya extends her metal hand and Hekate frowns.  ``The \textit{other} hand.''

``That one is way cooler,'' mutters Jaya as she extends her regular hand.

``Do you see this here?'' says Dr. Gerhauser, pointing to some discolorations under Jaya's nails.

``Uh, my mom always said I needed to be cleaner than this,'' says Jaya.

``You will find that it will be difficult to clean this off.  It is becoming endemic in your tissue and if it spreads to major musculature or heart you will be in trouble.''

``But I can just get a new heart, right?'' asks Jaya, flexing her metal hand.

``We will not be resourcing you with a new heart when we can solve this problem with antibiotics.''

``But five days!  How about I do one day then skip a day....'' negotiates Jaya.

``You really don't understand how medicine works, do you?'' says Dr. Gerhauser.

``\textit{Kate},'' warns Morgan.

``I'm working with you here!'' says Jaya.  ``This is a compromise.  You need five days...How about I do five days.... every other day.  I'm working with you, Doc!''

``Unfortunately that's not how antibiotics work.  If you skip a day, the disease will come back in that day.  We need to kill it off.''

``Just give me stronger drugs so they last me through the day that I'm not taking it.''

``You would still need to abstain from all drugs and alcohol-''

``Alcohol is not a drug,'' says Jaya with authority.

``We can debate that later.  Do you understand what I'm telling you?''

``I understand what you're asking but-''

``Good,'' interrupts Dr. Gerhauser.  She places a bottle next to Jaya.  ``Take one of these daily in the morning.''  and she turns, gives Morgan a look, and leaves.

Morgan studiously ignores her sister's look and when Hekate's out of the room, says to Jaya, ``Sorry about that.''

``Yeah I don't think she really understands how one operates on a mission.  You gotta do what you gotta do to be top form.  I don't know if I can do this to top performance....''

``It will be a little while before you leave the base, we still have some mission details to work out,'' says Morgan.

Jaya gets a look of distant horror on her face and clears her throat. ``Yeah, speaking of details...I would like to uh...formally....uh...request.....um... You know how we got extra hazard pay for those missions where you put us in those big water tub things.  I feel that the severity, now that we're at war, has increased.  And an advanced, \textit{severely} advanced, hazard pay for our life threatening ongoing missions that we are engaging in-''

``You're asking for a pay raise.'' interrupts Morgan.

``Effective immediately...perhaps even before...'' Jaya is sweating profusely.

``Are you asking for a loan?''

``No!  It's like raise, but I get more of it...in the beginning...''

``You want to be paid for work you haven't done yet.''

``I'm very honorable!  \hl{I am an effective team member who has proven able to not die}\footnote{\textbf{q.google }Is that all it takes??  .  Can everyone else have raises too? \textsubscript{10/05/14 1:51pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I mean, not if you don't ask... \textsubscript{10/05/14 3:40pm}} and keep \textit{most} of my team from not dying....''

``Are you indebted to someone?  I can probably take care of them if that's the case.''

``I- I have a sister,'' says Jaya.

``Don't we all,'' says Morgan dryly.

``I've got a sister.  She's in a tough spot.  You know how the Orc tried to kill Oliver and all of his family...well she \textit{did} kill Oliver and all of his family...okay not \textit{all} of his family...well \textit{attempted} to-  Well someone is trying to fuck with my family and I'm pretty sure it's related to my work here and \hl{I think the SAC-09 owes it to me to protect my extended family...well at least my sister}\footnote{\textbf{q.google }Hear, hear! \textsubscript{10/05/14 1:52pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }reading this now (and having no memory of what brain was doing at the time) I wonder which extended family of hers doesn't warrant protection?  I guess I was just thinking the nephews... but it reads more suspicious than that in hindsight \textsubscript{10/06/14 9:15am}}\footnote{$\rightarrow$\textbf{Suko T }I don't know, Jaya's never been subtle about not being terribly interested in Padme's kids (except her favorite, Simon), and I think Jaya also doesn't get along with her Aunt (the one who told her about Padme losing the girl baby).  So she's got plenty of extended family to lose if need be... :) \textsubscript{10/08/14 4:02pm}}.  She's in a tough spot.  She really needs some money.''

``How many drugs are you on right now?'' asks Morgan.

Jaya holds up two fingers although a third sort of wobbles.

``Do you expect to experience withdrawal?  I recommend you be honest with me right now.''

``\hl{I'm always honest with you Agent Ma'am Sir}\footnote{\textbf{q.google }Whether she means to or not :). \textsubscript{10/05/14 1:52pm}}.  I just think I perform optimally in my current situation and if that situation changes, I might not perform as optimally.''

``I see.  I don't wish to lose you as an Agent,'' says Morgan.

Jaya looks surprised.  ``I don't want to be a lost Agent either.''

``So I need you to take the antibiotics, otherwise it will kill you.  Eventually.''

``This fucking job is going to kill me eventually.  But I haven't quit yet!'' Jaya laughs.  She bargains, ``How about this- what if I take the antibiotics and I get that hazard pay...advance.''

Morgan counters, ``How about this: you take the antibiotics, you stay off of all other drugs because I can't have you going into shock, I find you extra work to do around the base which will account for your pay raise and the advance you are requesting.  In addition to this, we can see about giving your sister additional resources for her safety.''

Jaya thinks about it for a long time, clearly desperately trying to think of any other solution.  ``You know...I think that maybe...that might...work out... for a short-''

``Great,'' says Morgan briskly.  ``One more thing.  I'm given to understand that this disease has the ability to transfer through contact with other people.  I request that you stay out of close contact with people to prevent any ping ponging.''``Is Hayley sick?  Is Jonah sick?'' Jaya says, almost sounding concerned.

``No but Jayce is.''

``Oh he probably got his own grave rot,'' says Jaya dismissively.

``\hl{Well}\footnote{\textbf{Nathaniel Ford }This should have probably been a slight drawl. \textsubscript{10/01/14 12:21am}}, on the off chance you got it from each other, please maintain your distance.''

\hl{``Yes Agent Ma'am Sir,'' grumbles Jaya}\footnote{\textbf{q.google }Background music: \_Turning Japanese\_? \textsubscript{10/05/14 1:54pm}}.

``Very good.  Now shall I send the advance to you or your sister?''

``Well I don't know how you'd find her...Jayce was going to deliver it.''

``Well then he has a good reason to leave the base.  Problem solved.'' Morgan turns and leaves.

Jaya calls out after her, ``Am I free to go?''  There's no reply.



Swan comes in a while later and looks surprised.  ``Uh, you know you're dismissed right?''

``Fucking A-'' curses Jaya and she sweeps a bunch of stuff onto the ground and stomps out, but then has to go back and pick up her bottle of antibiotics off the floor at Swan's reminder.




\sceneHeadline{Bunk- Hayley and Jonah}

Hayley follows Jonah into the Bunk and sets her luggage down and shuts the door.  She stands in front of the door, smoothing her hair and tugging at her dress anxiously.  Jonah puts his bags down and stands up with a resigned air.  ``So, you dressed for a party?'' asks Jonah.

``No I wore this for you.  I'm beautiful now.  Do you like me better?'' asks Hayley.

\hl{\textless long pause\textgreater }\footnote{\textbf{Rebecca S. }was it really a long pause in game?  Or were we delayed by everyone dying of laughter out of game?  Sooooo good. So good.  Hayley, she just... says it. Puts it out there. \textsubscript{10/01/14 8:40am}}\footnote{$\rightarrow$\textbf{Suko T }I think the long pause was filled with a long-suffering, ``lord give me patience'' sigh. :)  But yes, also lots of laughter from everyone else.  I always wanted Hayley to be the one who could do uncomfortable things or ask all the uncomfortable questions and I think I've finally reached that point.  Yay! :D \textsubscript{10/01/14 11:14am}}

``You look very nice.''

``I know,'' says Hayley.

``I need a drink.  You want a drink?''

``No thank you, it's poison,'' says Hayley \hl{politely}\footnote{\textbf{Nathaniel Ford }Well, ``politely'' in her eyes. ``pointed'' to the average person. \textsubscript{10/01/14 12:22am}}.

\textless another long pause as Jonah pours himself a drink\textgreater 

``If you like something else, I brought other outfits,'' offers Hayley.

``\hl{Why are you getting dressed up for me?}\footnote{\textbf{q.google }''I know why \_I\_ think you are getting dressed up for -- who knows what \_you\_ think you are getting dressed up for.'' \textsubscript{10/05/14 1:56pm}}''

``Do you not like looking at beautiful \hl{things}\footnote{\textbf{Rebecca S. }D: \textsubscript{10/01/14 8:40am}}\footnote{$\rightarrow$\textbf{q.google }Yeah.  Yeah, exactly. \textsubscript{10/05/14 1:56pm}}?'' asks Hayley, sounding puzzled.

``Yes.''

``That's why.''

``It's very nice of you.''``So do you like me now?'' persists Hayley.

``Did I not like you before?''

``You didn't seem to.  You were angry.  You yelled at me a lot.  I didn't like that.''

``I'm sorry.  There was a lot going on.  I was trying to figure out how not to get us all killed.  There were a lot of decisions to make.''  Jonah looks tired. ``I'm sorry I yelled at you.''

``That's okay.''

``Is it?  You didn't like it.''

``No, but I don't like a lot of things.  That doesn't stop them.''

``That's true.  That's true of everybody.''

``So can we kiss again?'' asks Hayley eagerly.  ``We can go to the gym if you like, since it's what you preferred.''

\textless another long pause\textgreater 

``Um.  \hl{Do you know what a rain check is}\footnote{\textbf{q.google }Jonah learned about these in his National School night classes!  Not sure if he knows what ``rain'' is though. \textsubscript{10/05/14 1:57pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I don't recall if we went over this, but it does rain on occasion. It's just not healthy to be out in it, for a variety of reasons. Much like you don't want to drink ocean water, rain water has the same negative medium to long term effects non-Directorate produced water does. \textsubscript{10/05/14 3:39pm}}?'' asks Jonah.

``No.''

``It means 'yes, but can we do it later'''

``Okay, so when?''

``I don't know, I need to sleep,'' says Jonah with a sigh.  ``Shore leave was not restful.''

``So tomorrow?'' says Hayley doggedly.

REBECCAxxBEGINxxHIGHLIGHTxx``Wow.  You really know how to make a girl feel good,'' says Jonah a little wryly.

``Yes I do.  And men also,'' says Hayley, matter of factly.xxENDxxHIGHLIGHT\footnote{\textbf{Nathaniel Ford }Too good. I couldn't write this dialogue. \textsubscript{10/01/14 12:24am}}\footnote{$\rightarrow$\textbf{Suko T }Thank you!  I was rather proud of this one. \textsubscript{10/01/14 1:37am}}\footnote{$\rightarrow$\textbf{q.google }Ditto. \textsubscript{10/05/14 1:58pm}}

``\hl{One day I'm going to understand}\footnote{\textbf{q.google }No, no you won't.  At least you'd better hope not. \textsubscript{10/05/14 1:59pm}} what in \hl{God's}\footnote{\textbf{q.google }What \_do\_ they say for this? \textsubscript{10/05/14 1:59pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }In the style of Urth of the New Sun, I assume that they have a phrase used for similar purposes and this is simply the closest translation our modern, English-speaking brains can understand. So we can ignore it. ;-) \textsubscript{10/05/14 3:37pm}} name they put you through there,'' says Jonah.  He says slowly, ``Where I grew up, it's usually the guys asking girls for kisses.''

``Oh, usually I'm asked,'' says Hayley.  ``Or told.  Ordered mostly.''

``Right.  Where I grew up, you can't be ordered.  You ask and the other person has to decide to say yes.  \hl{You ever been asked and said 'yes but not now'}\footnote{\textbf{q.google }''I can't \_believe\_ I'm saying this.'' \textsubscript{10/05/14 2:01pm}}?''

``No,'' says Hayley.

``It doesn't mean no, it means ask again later.''

``Perhaps after you've slept, I can ask then?'' asks Hayley.

``Okay.  All I can say is, the first girl I ever asked, I asked her several times before she said yes.''

``Why would I care about her?'' asks Hayley, confused.

``It's an example of what I'm used to.''

``Oh.  So am I supposed to wait for you to ask me?  I'm afraid I don't know how all this works...''

``No you can ask me, it just means that if someone says wait-''

``So I'm not supposed to take no for answer?'' says Hayley, enlightened.

``I didn't say no!  Er- I'm sorry, I'm just really tired.  I'm sorry I yelled at you.  Maybe when I've had some sleep...''

``Okay.  I'll ask you when you wake up,'' says Hayley, pleased, and settles in to wait.

Jonah takes some medication that insures he'll sleep for a looong time.



Once Jonah goes to sleep, Hayley starts putting things away, changes into her TA uniform and tidies up.  Jaya shows up eventually.




\sceneHeadline{KP Duty- Jaya}

Larissa drops by with orders for Jaya to report to Jari for her ``extra duties''.  It ends up being a lot of cleaning up of unused parts of the base.  There aren't a lot of witnesses to Jaya's work but Jari is always with her.  Jari also has her clean up during dinner but still only feeds her gruel.  Jaya is in a foul temper the next five days, yelling at Hayley a lot.  Hayley takes the abuse with good humor, seeming to barely notice, patiently cleaning up after Jaya and replacing her mattress after Jaya shreds it for the second or third time.  Jaya doesn't reveal her extra duties and Hayley and Jonah don't ask.  Jonah suspects that there's something up with the drugs Jaya is or (more saliently) is \textit{not} taking but doesn't confront her over them. He eventually can tell Jaya is going through withdrawal.



Jari's not particularly mean to Jaya but he does point out anytime she fucks up.  He lets her slack a little but if she skips out entirely, he finds out.  He's always present if there's food around.



Jayce disappears on the second day.  Jari has to prod Jaya more and more as the days pass to get her work done.  Jaya screams at him a lot.  Jari takes in stride, he's somewhat distant from her, treating her like a robot that's misbehaving.




\sceneHeadline{Bunk- Hayley and Jonah}

The next morning, when Jonah wakes up, Hayley asks, ``So can we kiss again?''

Jonah takes a moment to reply and asks her, ``You thought you were prettier in your dress?''

``Yes.''``Why?''

``Because I am told I am.''

``What do \textit{you} think?'' asks Jonah.

Hayley thinks about it.  ``I know it fits better.  And you can see more of me and I am very beautiful, so that's always a good thing.''

``And you're not beautiful when you're not wearing the dress?''

``Umm... less so.  I don't like being sloppy.  \hl{These uniforms are terrible.  They fit poorly}\footnote{\textbf{Rebecca S. }dear god, has Morgan mic'd the bunk rooms?? (she would, that bitch...) \textsubscript{10/01/14 8:44am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }To be fair, it isn't the first time Hayley's had that complaint. \textsubscript{10/01/14 9:24am}}\footnote{$\rightarrow$\textbf{Suko T }It's true, I think Hayley started complaining about it from the very first session. The timing is a bit interesting though.  Maybe Morgan *also* likes to look at beautiful things. :D \textsubscript{10/04/14 1:17am}}\footnote{$\rightarrow$\textbf{q.google }I'm sure all the rooms are mic'd.  I also assume they don't \_usually\_ listen in.  Privacy is a luxury in close quarters.

I'm guessing it \_is\_ a reaction to the uniform, and the fact that they heard the complaint a long time ago, and now care enough to fix it. \textsubscript{10/05/14 2:36pm}}and the color is all wrong for my skin.''

``Well we're not usually going on dates in our uniforms.''

``I did.''

``Yeah?''

``I didn't realize it was one,'' explains Hayley.

``With who?''

``Tim.  I think he's dead now,'' Hayley says.  

``\hl{So you went on a date with someone and now they're dead}\footnote{\textbf{q.google }Not the most politic thing to say.  If it were anyone but Hayley that would never have come out. \textsubscript{10/05/14 2:04pm}}?''

``Yes. It is sad.''  She frowns a little but doesn't sound terribly upset.

``That doesn't bode well.''

``For what?''

``Other dates.''

``\hl{Oh it was a very nice date.  He didn't die on the date.  Just afterward}\footnote{\textbf{q.google } \textsubscript{10/05/14 2:07pm}}.''

\textless more talking and awkward silences\textgreater 

``I don't really understand you,'' says Jonah.  ``\hl{You're going to want a straight answer and I'm not going to give you one because I don't know how you're going to react to my answer}\footnote{\textbf{q.google }It's almost as hard for Jonah to say this as it is easy for Hayley to understand why he's saying it.

Almost. \textsubscript{10/05/14 2:08pm}}.''

``Why don't you just ask me?''``If I say yes, will you be happy?''

``Yes.''

``If I say no, will you be unhappy?''

``Yes.''

``What will you do if you are unhappy?''

``I'll- I'll be unhappy,'' says Hayley, clearly confused by the question.

``And?''

``And what?''

``When the Chief is unhappy she yells at people.  When I'm unhappy I go off in the corner I drink and smoke. What do you do?''

``Nothing,'' says Hayley, then she stops and corrects herself, ``Sometimes I cry.  Mostly I cry.''

The conversation continues on in this vein for some time, punctuated by very \textit{very }long uncomfortable silences.   

``You ever kiss another soldier?'' Jonah asks Hayley.

``Possibly.  I assume you mean other than you?  They don't always tell me what their professions are.''

``Yeah, so... someone you were working with.''

``Well...until now I didn't work with soldiers,'' says Hayley, starting to sound very confused again. ``And I've kissed lots of other people.''

``Okay let me try this.  You saw what happened to Carruthers when Davis died?''

``I wasn't there for that,'' says Hayley.

``No but you've seen how she is, though?''

``I've seen her around but....''

Jonah realizes this line of reasoning isn't working and tries again.  ``When Oliver died you could feel it right?  It wasn't a good feeling right?''

``Most of it wasn't.  Some of it was.'' says Hayley.

``This doesn't seem to be happening to you the same way it happens to everyone else I know, but one thing that happens is that when you kiss someone, who might die, and they don't come back, it feels like it felt when Oliver died.''

``Hmmm...'' says Hayley thoughtfully.  \hl{``Then there will be a lot of unhappy people in Terminus.''}\footnote{\textbf{Nathaniel Ford }And all the Johns cried out in agony before being silenced... \textsubscript{10/01/14 12:28am}}\footnote{$\rightarrow$\textbf{Suko T }Ha!  Totally misread your comment the first time thinking it was Pimps not Johns.  And now I'm going to hear Imperial March music every time I think of Octavius. \textsubscript{10/01/14 12:53am}}\footnote{$\rightarrow$\textbf{q.google }QooC. \textsubscript{10/05/14 2:38pm}}

``When you're done kissing me and maybe you'd want to do it again...right?''``Maybe.  If you're good at it,'' says Hayley honestly.

``Well that's you, but what's going to happen to \textit{me} is that I'm going to start worrying about you more than I do.''

``I would like that!'' says Hayley, sounding pleased.

And more talking and long pauses and pacing.   \hl{In the end Jonah essentially tells Hayley to ask him again after the next mission}\footnote{\textbf{Rebecca S. }Jaya would applaud Jonah's clever thinking.  I just want to throttle him. \textsubscript{10/01/14 8:46am}}\footnote{$\rightarrow$\textbf{Suko T }Hey now, guys are sensitive creatures. You have to give them time and let them get used to the idea.  And she did just torture him not that long ago.  Might take a while for him to get past that (giant, attraction-killing, she be cray cray) issue. \textsubscript{10/04/14 1:23am}}\footnote{$\rightarrow$\textbf{q.google }I want to throttle most of these characters fairly often.  (PCs and NPCs both.)  It's a not nice place they all live in. \textsubscript{10/05/14 2:38pm}}\footnote{$\rightarrow$\textbf{q.google }''Might take a while for him to get past that (giant, attraction-killing, she be cray cray) issue.''

.  That might in fact take a while. \textsubscript{10/05/14 2:40pm}} and she agrees.




\sceneHeadline{Timon's Family}

Micah takes Jonah to see his family.  They are past a door we don't usually go through, and there are other barracks rooms there.  Swan and Hekate have already seen his mom and are treating her cough.  Riva complains that Micah made her run around the gym and stretch and exercise.  \hl{There's not much to do there, so Jonah tries to see them at least once a day and gives them as much information as he can.}\footnote{\textbf{q.google }To be elaborated at the next available SAC-09 session.  If there is one (doesn't pay to jump to conclusions). \textsubscript{10/05/14 2:41pm}}  Micah is with him the entire time anytime he's in that area.


\sceneHeadline{The Gym}

To pass the time until she can ask Jonah again, Hayley exercises a lot.  She is almost always in the gym or the shooting range, if she's not cleaning up the bunk after Jaya had another tantrum.  Sometimes she just sits outside the Cistern door.  One day she enters the gym as Morgan is leaving and Morgan gives Hayley an odd look.  Later that day, Jari comes by and measures Hayley.  Hayley doesn't ask why, she barely even notices.




\sceneHeadline{Ops Room}

Day 5.  We are summoned to Ops Room early in the morning.  Hayley makes sure to leave her rifle in the Req Cage so Rook doesn't scold her again.  Jaya looks like a mess. Hayley attempted to tidy her and Jaya snarled at her and punched the wall (again). 



Rook, Morgan, Larissa, Trenton and Douglas are there.  The tanks are there, burbling, but there is no one in them.  Trenton seems a little reined in.  He's not lounging around as much as he usually does, and seems somewhat in his own world.  He watches us enter.  He nods at Jaya but says nothing.  He greets Jonah by name.   \hl{With an oddly reserved tone that has less vitriol than before}\footnote{\textbf{q.google }I really want to know what's shifted him.  I can think of at least three interesting things he might have learned, and I'm sure there are others. \textsubscript{10/05/14 2:43pm}}, he says ``Agent Hayley'' to her and averts his eyes.  She nods to him politely, ``Mr. Hadef'' and doesn't look at him either.  She does stare at Douglas with a puzzled air, trying to place why he looks vaguely familiar.  At least he's nice to look at.



Hayley salutes Morgan and Rook.  Morgan says, ``Have a seat.''  We sit.  Morgan begins, ``There are four possible targets.  One is the station known as BonVenture.  We believe that with a stealth insertion and rapid deployment, we can secure the factory facilities needed by Marechenko.  Secondly we have need to secure the location codenamed the Beacon for future operations against Octavius.  The Beacon will allow us to.... make transit to Transit,'' she smiles.  ``Third, we have a Tank mission to actually unlock the doors of Transit.  That will be critical.  And fourth, and I believe this to be the most pressing, we have agreed to provide Mohinder with operational territory outside of the Directorate.  We believe,'' she glances at Douglas, ``the best target is SAC-04.  We are prepared to hand it over to him, however we would need a joint operation to secure it.''

``The second and the third don't have to happen in that order?'' asks Jonah.

``No,'' says Morgan.  

``So... the issue is that Transit has these doors-'' begins Trenton.

``\hl{Nobody fucking cares}\footnote{\textbf{q.google }And all the setting nerds in the audience pull their hair and gnash their teeth. ;) \textsubscript{10/05/14 2:44pm}}!'' interrupts Jaya loudly in a more crazed tone than usual.  ``We already told Mohinder we would do the mission so it doesn't fucking matter.''  After this sharp outburst she goes back to tugging at her hair and rocking slightly.

Trenton just looks at Morgan and shrugs.  

``No, they don't have to be done in that order,'' says Morgan.  ``But it sounds like your team also feels SAC-04 would be a priority.''

``What are we giving up by not pursuing the other missions?'' asks Jonah.

``Putting off Marechenko is possible, but it will keep the Directorate weaker as they will be limited to the resources that they currently have.  In terms of Directorate long term security, Mohinder will have the most long term benefit.  As for destroying Octavius, the middle two are important, though the order is not important so long as they get done.''  Morgan taps a button on her datapad.  ``We will be sending in four teams.  Two will be provided by Mohinder, and two by us.''

The door opens and Lackovich walks in.  Jaya is still rocking in her chair, head ducked, and doesn't notice at first.  Lackovich salutes Morgan.  Morgan nods, ``Operator.''   Lackovich sits right across from Jaya.  Jonah nods to her.  Hayley gives her a little salute and Jonah follows suit.  Lackovich looks at Jaya very evenly and a little distantly, and then quirks her mouth up in a hint of a smile.

Jaya glares at Lackovich, ``How are you fit for duty?  I thought you were broken!'' she demands.  She continues with rising volume and a frantic tone, ``I thought- I thought you were fucking wrecked.  Never fit for duty again.  We need this mission to succeed.  What the fuck you doing on this mission?  We need capable members on this team!''

``Are you done, Agent?'' ask Morgan.  Jaya gives an annoyed sigh and settles again into a slump.  Morgan says, ``Lackovich has been returned to operational capacity, much like you were.  Now, Mohinder's going to have two teams and we \textit{believe }they are going to have the same objective, but we are not necessarily all on the same page.  The stated objective is to capture SAC-04.''

``From?'' asks Jonah.

Rook says, ``So it turns out all known SACs, save for SAC-01, all have a Praetor.  Which means they are capable of defending themselves.  We believe that Douglas can help provide certain security countermeasures.  However we have to get him close enough to effectively take over that system.''

``Can you explain what a Praetor is, Sir?'' asks Jonah.

Rook looks surprised.  ``\hl{I thought we went over this}\footnote{\textbf{q.google } \textsubscript{10/05/14 2:50pm}}.''  Both Jaya and Hayley also give Jonah 'uh, we already asked this' looks.  Rook explains, ``It is a guardian.  A particular entity who is assigned to that complex to protect it against all comers.  It's a particular type of defensive system, different from a gate or gun nest.  It's a Praetor.''

``But it's a person?''

``\hl{Sometimes}\footnote{\textbf{q.google }See, Rook has a different defintion of ``going over this'' than we might have. \textsubscript{10/05/14 2:50pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }The answer Rook would have wanted to give probably would have blown Jonah's mind, so it didn't get past his 'lets be sensitive' filter. \textsubscript{10/05/14 3:44pm}}\footnote{$\rightarrow$\textbf{Suko T }The amount of stuff that gets caught by that filter must be truly prodigious. \textsubscript{10/05/14 5:14pm}}.''

``If something happens to Douglas, will the mission be terminated?  Will we be able to proceed without him?'' asks Jaya.  ``Because he brings that sword with him and things can go wrong really fucking fast and shit might happen something might go wrong and willwebeabletorecover...''  Jaya is forced to breathe and Morgan steps in smoothly, ``It is a key part of your mission objective to protect Douglas.''

``Understood,'' say Hayley and Jonah nearly simultaneously.  Hayley even reaches instinctively for her gun that isn't there and seems mildly distressed to find it gone.

``What is the purpose of sending four teams?'' asks Jonah.

``We are sending two teams because Mohinder is sending two teams.''

Jaya looks at Douglas, who has been watching the conversation but not saying a word.  ``So what about retard here?  Are we going to be able to communicate with him?  Because last time we needed Jayce to talk to him and I just sent Jayce to my sister and I don't know if he'll return-''

``Jayce will be returning shortly.''``He's going on this fucking mission?  This mission isn't safe.  This is like going into a danger zone!  He can't takecareofhimselfthisisnotgoingtowork!  Douglas can't even communicate with anyone!  What if something happens to Jayce?''

Trenton says under his breath ``Nice to see you actually care about someone.''  

Jaya ignores him.  ``What if something happens to Jayce?  Then we're totally fuckedandthe missionistotallyfucked because we can't talk to fucking Douglas!''

Morgan says, ``I'm sure you'll figure it out.''

Jaya glares angrily at Douglas.

``Douglas is fully briefed on what we need to have happen.  We translated that information through Jayce,'' says Morgan.

``He can be useful,'' says Jaya grudgingly under her breath.

``Jayce does actually seem to know what he's doing, in my experience,'' says Jonah.

``Mine too,'' mutters Jaya.  Jonah grins.

Morgan says, ``Your operational objective is to get Douglas to SAC-04.  Once he has unlocked the base for them, it's their problem.''

``With four teams, if there is any disagreement between us and Mohinder's teams-'' asks Jonah

``You will follow Directorate chain of command, as per usual,'' says Morgan.

``So if they send their senior Agents, that means they are in charge, correct?''``Yes,'' says Morgan.

``What about internally?'' asks Jaya, staring straight at Lackovich.

``I will make that assessment when you launch the operation,'' says Morgan.  Jaya looks displeased.

Morgan turns to Lackovich.  ``Lackovich, I will be sending Javier with you, as well as two additional constables.''  Morgan looks at Jaya, ``Unfortunately we don't have any spares for your team.''

``We are perfectly fine at three. We're at top operational form with three,'' boasts Jaya.

``May I ask a question?'' asks Hayley.

``Hayley,'' says Morgan with a small sigh.  ``Two things.  One, we have discussed this matter before, about you asking to ask questions.  And what was the conclusion from that?''

Hayley thinks and says carefully, ``I'm sorry, you didn't ask if we had any questions this time.  I didn't know if it was implied-''

``Ah well let's broaden the definition then. This is an open discussion.  You are free to ask questions.''

``Thank you,'' says Hayley.

``Secondly, see Jari after this.''

``Understood,'' says Hayley.  ``I was wondering if Operator Carruthers would be joining one of the teams, Sir.''

``Technically yes, however she will not be \hl{boots on the ground}\footnote{\textbf{Nathaniel Ford }Or boobs on the ground. Fuck you, Fox ``News''. \textsubscript{10/01/14 12:36am}}\footnote{$\rightarrow$\textbf{Suko T }Seconded!  Blegh. \textsubscript{10/01/14 1:38am}}.''``Ah.  Thank you,'' says Hayley.

``Oh, it can be done from a distance?'' asks Jonah.

``Yes,'' says Morgan.  

\hl{Trenton smirks and mutters disdainfully, ``\textit{distance}``}\footnote{\textbf{q.google }Says the guy who never has to travel anywhere. \textsubscript{10/05/14 2:53pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm pretty sure Trenton sees the extended hospitality of SAC-09 *slightly* differently. ;-) \textsubscript{10/05/14 3:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{10/05/14 5:12pm}}

Silence falls.  ``Well if you don't have any more questions, you are all dismissed,'' says Morgan.  ``Be at the ready line in 24 hours.''

``One more question,'' says Jonah.  ``What sort of equipment will we need for the area?''

Morgan replies, ``The rumors from Nicklepan indicate that it was an area that was avoided by them almost out of tradition.  \hl{But there is some indication that they explored it several times, failing every single time}\footnote{\textbf{q.google }Oh \_goodie\_. \textsubscript{10/05/14 2:53pm}}.'' 

``Do we know who their Praetor is, Sir?'' asks Hayley.

``SAC-04's?  No.''

``Do we know anything about these Praetors?'' asks Jonah.

``They all vary in personality,'' says Rook. ``And type.  They are specific to the facility that they are meant to guard.''

``Who is our Praetor, Sir?'' asks Hayley.  The room goes still. There is a pregnant pause.

\hl{``I am,'' says Rook.}\footnote{\textbf{Rebecca S. }!!!

ya'll may have figured it out before this, but this was a big reveal for me.... \textsubscript{10/01/14 8:54am}}\footnote{$\rightarrow$\textbf{q.google }I figured \_that\_ out.  But I'm batting 0.200 at best I think.

Besides, I don't know about you, but for me most of the fun of a story is getting to go ``!!!'' when something cool is revealed. \textsubscript{10/05/14 2:55pm}}

Hayley nods.

\hl{``So they can be reasoned with?'' asks Jonah''}\footnote{\textbf{q.google }That's not a hint.  Nope.  Not a hint at all.  Really. \textsubscript{10/05/14 2:56pm}}.  

``Possibly,'' says Rook.

``Their objective is to defend the SAC over all other objectives?'' asks Jonah.

``A better, more precise term is to \textit{protect},`` clarifies Rook.

``Do you have any tips on lines of negotiation we might use with the Praetor of SAC-04?''

Rook pauses and thinks for a moment.  ``I would attempt to make contact or to determine its personality before proceeding.  However, it is likely to be a single entity and if you find the core of that entity and destroy it, it will no longer be a threat.  Or if you reach some kind of negotiation with it and think you are are successful, it is unlikely to be a threat.  Different Praetors have different personalities and different implementations.  It could take any form.''

\hl{``So don't kick any fucking klipspringers!'' says Jaya, and laughs to herself}\footnote{\textbf{Nathaniel Ford }Jaya, Klipspringer Bane \textsubscript{10/01/14 12:38am}}

``I'm sorry to press the point, but what does that mean 'take any form'?'' asks Jonah.

``It means we do not know who built SAC-04 and installed the Praetor or what their concerns were at that time.''

REBECCAxxBEGINxxHIGHLIGHTxx``And they would still be around, after all that time?''

``Yes,'' says Rook.xxENDxxHIGHLIGHT\footnote{\textbf{q.google }Jonah is now just a teeny bit \_freaked out\_ about Rook. \textsubscript{10/05/14 2:58pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Aww. Rook is so adorable, though. It seems like just yesterday y'all were comparing him to Agent Coulson. \textsubscript{10/05/14 3:31pm}}\footnote{$\rightarrow$\textbf{Suko T }He's still adorable.  ETERNALLY adorable.  And even more like Agent Coulson (given the reveals in Marvel Agents of SHIELD) than we knew :D \textsubscript{10/05/14 5:12pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I haven't actually been watching said show, so I don't really know. :P Should I? \textsubscript{10/05/14 6:08pm}}\footnote{$\rightarrow$\textbf{Suko T }If you're asking about watching it, probably not. It has some okay episodes but episodes 2-15 of first season are kinda...awful.  And I love superhero shows and am a shameless Clark Gregg fan so they really have to be pretty bad for me to say that.  The only episode I can endorse as genuinely good is the season 1 finale.  But there's some stuff they did with Coulson (to explain why he's still around after the Avengers movie) that echo in amusing ways with what I know/guess about Rook. \textsubscript{10/05/14 11:26pm}}

``Thank you.  How long do you think this will take?''

``A few days.  You are authorized to pull out as soon as the mission is complete or if there is extreme danger to your teams.  \hl{We don't want to lose you on this, it's not worth getting yourselves killed over it}\footnote{\textbf{q.google }Awwwww!  Morgan is being all \_cuddly\_.  For Morgan. \textsubscript{10/05/14 2:59pm}},'' says Morgan.

``Thank you.  I have no further questions,'' says Jonah.

``Very well, Jari will be driving the train.  You have 24 hours.  Dismissed,'' says Morgan.  Jaya gets up and leaves before Morgan even officially dismisses them.



Rook catches Jonah before leaves and pulls him aside.  Everyone has left except Larissa.  Rook asks, ``Have you thought any more about the Hayley matter?''

``This is even more complicated than the last time we spoke.''

``\hl{Can I ask what the complication is}\footnote{\textbf{q.google }You can, but you won't get a straight answer. \textsubscript{10/05/14 2:59pm}}?''

``Yes, but can we do so in private?''

Without even looking away from Jonah, Rook says, ``Larissa, dismissed.''  Larissa gives a startled, ``Yes sir'' and leaves.

``So are you willing to be Hayley's Operator?'' asks Rook.

``Not at this time no.''

``You said there were complications?''

``Yes.  Hayley has expressed...the closest....what I can only call...a romantic interest.  But that would assume it was anyone but Hayley.''

``That happens sometimes between people who work together closely, under stress.''

``Yes.... it does.''

``Do you not return her feelings?''

Jonah doesn't answer.

``\hl{I have no dog in this race}\footnote{\textbf{q.google }Not a great topic to bring dogs into.  Even if there were any dogs. \textsubscript{10/05/14 3:01pm}} so it doesn't matter to me whether or not you do,'' says Rook.

``It would make being an Operator more difficult than it already is.''

``Also perhaps more effective.  If you have an intimate bond with them.  But I can see how that would be stressful...potentially.... scary.''

``To quote the Chief...I don't believe I would be Operating optimally if that happens.''

``\hl{An interesting quote}\footnote{\textbf{q.google }Freshly picked off the cherry tree. \textsubscript{10/05/14 3:01pm}}\footnote{$\rightarrow$\textbf{Suko T }I forgot to note that this is the second time Jaya has been quoted in game, first by Morgan and now by Jonah.  Even our characters find her eminently quote-able! :D \textsubscript{10/05/14 5:14pm}}.  Very well then.  How about we table this discussion for now.''

``One more question.  It appears that the Chief is going through some sort of withdrawal.  I assume you are aware of this?''``Yes. She was suffering from-''``I don't need the details, I just want to know if she will be okay for the mission.''

``If she stays off the drugs, she won't go into shock, and her system should be clean by the end of it.  But on the mission, she'll be a little rough.''

``\hl{That's going to make things...harder}\footnote{\textbf{q.google }''Do you all even \_think\_ about these things when you do them?  Is it really a good idea to make this \_more\_ dangerous than it is?''

He doesn't have the context of course. \textsubscript{10/05/14 3:03pm}}.''

``Good luck,'' says Rook and he turns and leaves.




\sceneHeadline{Req Cage- Hayley and Jari}

Hayley finds Jari.  He hands her two bundles and says, ``These are for you, sorry they took so long.  Compliments of Agent Gerhauser.''  Hayley clumsily signs for them and takes them back to her bunk.  Inside is clothing, tailored to Hayley's size and made of high quality fabrics (though still strictly protocol colors).  There are uniforms, a battle dress uniform, several skintight uniforms for wearing under combat armor, and even some workout clothing.  Hayley changes into one of the uniforms right away and carefully puts the rest away.



\textit{Req Cage updates:}

Req Cage 3 → 4

Radio Network 2 →  3

Armory 4 →  5

Workshop 5 →  6

Closet 2 →  3

Forensics 1 →  3




\sceneHeadline{Gym- Jaya and Morgan}

At 1100, there's a knock at the door.  Jaya is lying in her bunk and yells for Hayley to get the door.  Hayley comes out of the washroom where she was changing into her new workout clothing and answers the door.  It's Morgan.

``Sir,'' says Hayley.

``Agent,'' replies Morgan.

``Fuck!'' yells Jaya as she sits up at the sound of Morgan's voice and bashes her head into the ceiling.

Morgan looks Hayley up and down and smiles slightly.  ``Is Agent Parvadi available?''

Hayley says, ``Excuse me a moment while I check.''  She peers around the door and asks Jaya, ``Sir?''

Jaya is rubbing her head and rolls off her bunk.  Hayley leaps away from the door and catches Jaya just enough keep her from injuring herself further.  Jaya heads to the door as Hayley tries to tug Jaya's shirt at least into a semblance of order but Jaya pushes her away. 

``Agent, Ma'am. Sir,'' says Jaya to Morgan.

``Are you available for training?'' asks Morgan.

``I, uh, uh..... er.....what?'' says Jaya.

``Would I also be able to train with you at some point?'' Hayley asks Morgan.

``What?  Hayley- no!  This is- this is- NO!   I'm ready.  Let's- Let's fucking go!'' and Jaya starts heading out the door and down the hallway.

While Jaya's back is turned, Morgan winks at Hayley and gives her the slightest nod.  Hayley looks very pleased.



Jaya and Morgan spar.  Jaya is definitely not at her best but Morgan takes it a bit easy on her.  At their first break Morgan says, ``I believe you're on your last day, yes?  Are you going to stay off the drugs?''

``I'm never taking fucking antibiotics again,'' says Jaya fervently.  ``I am fucking done with these.''``I meant the recreational drugs,'' clarifies Morgan.

``I, um, what? No.  What?'' says Jaya cleverly.

``I find it's easier to keep a clear head when one is not addicted to certain substances.''

``Have you tried \_\_\_\_ (Jaya names her favorite drug)''

``I usually go for things that are more cultivated.''

Jaya names something else more expensive.

Morgan says, ``Regardless, I need to know what state you'll be in.''

``I'm gonna be- I'm gonna be....''

``Optimal?  Like you were before?''

``More than optimal!''

Morgan walks over to her bag and pulls out a small satchel and tosses it on Jaya's bag.  ``I recommend you go slowly at first.  I can't have you going into shock.  My sister would be upset.  As would I.''

``Yeah no shock.  Lackovich would just fuck everything up.  I'm on top of my game.  I'm definitely going to ease back into the game.''``But I would ask you to seriously consider....not.''``Yeah yeah,'' says Jaya.  ``Let's continue.''And they spar some more.  This time Morgan doesn't take it easy on Jaya and Jaya ends up with many new bruises.



On her way back from the gym, Jaya looks in the satchel. There are two hyposprays and a note on it saying ``not until 12 hours after the last pill.  Lasts for 4 hours.''   A scream of rage echoes down the hallway, followed by a ``thunk'' as if something metal had hit a wall.



While Jaya's sparring with Morgan, Jonah tells his family that he'll be gone for a few days and if they have questions they can talk to Rook or Micah.



\hl{Jonah also tries to find Jayce and get to know him a bit before the mission.}\footnote{\textbf{Rebecca S. }Noooooooope. Nope nope. Bad idea.  I missed this during the game. \textsubscript{10/01/14 8:59am}}\footnote{$\rightarrow$\textbf{q.google }I think this is slight mis-transcription.  Jonah wants to find Jayce to find out more about \_Douglas\_.  He's not going near Jaya's personal life: he has enough trouble already.

I'm assuming he didn't find him, because we didn't elaborate on that. \textsubscript{10/05/14 3:05pm}}\footnote{$\rightarrow$\textbf{Suko T }Perhaps the reason was Douglas but I think what was said was that Jonah wanted to get to know Jayce because he needs to know who will be at his back in a dangerous situation. \textsubscript{10/05/14 5:16pm}}




\sceneHeadline{Mess- Jaya, Jonah and Hayley}

The next morning, we head to breakfast.  Jaya still gets gruel but Jari says in an affectless voice, ``Good work this week.''  Jaya replies, ``Go fuck yourself.''  Jari shrugs.



Lackovich, Carruthers, Javier and two unfamiliar constables (Morley, a guy, and Breccan, a girl) are seated at a table.  Javier and Carruthers are on opposite ends of the table and not looking at eachother.  Hayley smiles at Carruthers and she smiles back.  

After mealtime as we get ready to leave the messhall, \hl{Carruthers flings her arms around Hayley in a big hug and says ``Good luck.  Don't die.''}\footnote{\textbf{q.google }Awwwww.  She even speaks the same language. \textsubscript{10/05/14 3:06pm}}\footnote{$\rightarrow$\textbf{Suko T }Not really.  Speaking Hayley's language would have been something more like:''I encourage you to make every effort to avoid being in a fatal situation, but I understand if such a thing is unavoidable.  I would be saddened by your death.''  But it's sweet nonetheless. \textsubscript{10/05/14 5:19pm}}

Hayley is startled and looks uncomfortable at first but then relaxes and awkwardly returns the hug, patting Carruthers on the back like someone unused to hugs.  ``You too,'' says Hayley, sincerely.

``I'll be watching,'' says Carruthers.

Jaya glares at the two of them and her vision goes a little funny.  She sees their hair start to move oddly, like it was wet or viscous.

``So you two are \hl{friends}\footnote{\textbf{q.google }See?  See?  Like \_that\_.  \_That's\_ what it means. \textsubscript{10/05/14 3:07pm}} now?'' Jonah asks Hayley.

``Who?''

``You and Carruthers.''

``Are we?'' Hayley looks surprised but not displeased.  ``Hmm.''

Lackovich walks up to Jaya, who is eating her gruel, studiously ignoring her and just watching Carruthers and Hayley.  ``You ready to nail this?'' asks Lackovich.

``Fuck off Lackovich.  Yeah I'm ready to nail this.  I'm a \textit{nailer}.  It's gonna happen-''

``Good, 'cause if you're off your game....''

``Yeah you're going to fuck everything up if I'm not on top of my game,'' says Jaya.

``I imagine she would step in-'' says Hayley.

``Shut the fuck up Hayley!  Stay out of this.  Just go make out with Carruthers some more.  I don't even care.  Just get out of my hair!''

Lackovich raises a brow at this rant.  Hayley's not upset by Jaya's tone but asks carefully, ``Is that an order?''``No!  Fucking goddammit!''  Jaya flips her gruel bowl over and rage quits the room. The gruel puddles and oozes just like she'd seen Hayley and Carruther's hair move earlier.

Jonah does his best to smooth things over a bit and welcomes Lackovich to the Operator Cadre.  Jonah notices Lackovich rolls her shoulder in a markedly odd way.




\sceneHeadline{Ready Line}

We go get suited up and then go to the ready line.  We're in full armor \hl{with all our gear.}\footnote{\textbf{Suko T }I took the liberty of divving up our gear, but feel free to suggest alternates and check my math.  I *did* give the AMP to Jaya which may be a bad idea :D  It requires AGENT to use so I don't know that Jonah can use it?  I assume Hayley would put Jaya's resurrection as a priority over her own.

We are really geared up to the teeth this time around! \textsubscript{09/29/14 10:37pm}}\footnote{$\rightarrow$\textbf{q.google }Unless it's tied directly to the special status of Agent vs Operator I assume it's just a rank \& access issue no? \textsubscript{10/05/14 3:12pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }You do actually need the skill. Speaking of which, if Jonah wants to buy 'Agent', he can do so, though that won't affect the in-game rank situation. \textsubscript{10/05/14 3:27pm}}  Carruthers is not there but Jayce and Douglas are there.



\textit{Jaya}

Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

AMP 3

Hush Radio 1

Gauss Pistol 2

HE Grenades 2

Binoculars 2

Heads-up Display 4

Letter of Marquee 2

Forensics Bag 1



\textit{Jonah}

Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

Field Surgical Kit 2

Medkit 1

HESP Radio 2

Gauss Pistol 2

HE Grenades 2

Electronic Bypass Kit 3

Heads-up Display 4

Operator Integration 2

Forensics Bag 1



\textit{Hayley}

Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

MedKit 1

Hush Radio 1

Heavy Pulse Rifle 3

HE Grenades 2

Binoculars 2

Heads-up Display 4



Morgan actually does a full inspection this time.  She gives everyone a few notes, ``fix this, tighten that.'' Even Hayley is not exempt, as \hl{Morgan has her adjust the fit of her weapon straps}\footnote{\textbf{Rebecca S. }I assume it's just that massive bosom of hers interfering with things again- that's why her straps are always wrong. Such a hinderance! \textsubscript{10/01/14 9:03am}}\footnote{$\rightarrow$\textbf{Suko T }Correct fit is so difficult when you can't see your feet.... \textsubscript{10/01/14 11:06am}}\footnote{$\rightarrow$\textbf{q.google }http://en.wikipedia.org/wiki/Amazons\#Etymology \textsubscript{10/05/14 3:13pm}}, though Morgan compliments her on the cleanliness of her rifle.  She tells Jonah to clean his weapons better.   Morgan addresses Jaya, ``Do you feel capable of taking command?''

``Fuck yeah,'' says Jaya in a low voice, and then leans in close to Morgan, her eyes intense, ``I can fucking \textit{do} this.''

With a big wolfish grin, Morgan leans in even closer and says, ``Don't fuck it up.''  Raising her voice to be heard by everyone, Morgan says, ``Operator Lackovich, as long as Agent Parvadi is in operational condition, she is in charge. Is this understood?''

``Yes, Ma'am,'' says Lackovich.

Morgan turns to Jonah.  ``Make sure she stays in operational capacity.  You understand?''

``Yes, Sir,'' says Jonah.

Jaya is looking around to see who's noticed that she was put in charge.  Jayce gives her a thumbs up.

``Get to the platform, Rook will meet you there,'' orders Morgan.



We assemble on the platform.  Micah is on the gun platform, Karil is at the door and both are in full combat armor.  After we are all on the train platform, the door closes behind us and we can hear heavy locks and seals being engaged. Jonah notices Hayley flinch at the noise.  Jari is on the platform in BDU.  ``You ready?'' he asks Jaya.  ``Fuck yeah,'' says Jaya, avoiding looking at him directly.

``Designate your radio operator,'' says Jari.  Jaya waits for a volunteer and ends up picking Agent Javier.   ``Very well, I'll wait for his signal for pickup,'' says Jari.  ``You will have a roughly 20 min window should you request emergency extraction.''

Jari addresses the group, ``Hope you are all ready\hl{and well fed}\footnote{\textbf{Rebecca S. }fuck you, Jari! \textsubscript{10/01/14 9:04am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Fuck you right back, Jaya! -Love, Jari \textsubscript{10/01/14 9:22am}}.  Lackovich, good to see you operational again.''  Jaya flushes at the reminder of food.  Jonah compliments Jari on the recent meal, deliberately needling Jaya a little.

The train starts pulling into the station, we notice that Karil and Micah come to attention and ready the gun. They are clearly following the procedure for train station defense.  Hayley brings her gun to ready position as well.  Jonah tries to stand out of the path of immediate danger.

Jari whispers to Jaya, ``Attention,'' and then a little louder, more firmly, when she fails to respond.  Confused, Jaya repeats the order, half disguised in a cough and then comes to attention herself and that ripples down the line as we all come to attention.  When it gets to Lackovich, she barks out, ``Atten-HUT!'' and her team snaps to attention.



The train doors open and out walks Drake.  He's wearing a vest of some sort, with a several grenades and pistols strapped to it and a rifle slung over his back, with a combat knife at his side.  He's bare armed, exposing a tattoo sleeve on his left arm and lots of rippling muscles.



Hayley salutes crisply.  Jonah and everyone else follows suit except Jaya (who salutes lazily with a noticeable delay) and Douglas and Jayce.  Drake returns the salute.  He looks down the line, notes the soldiers in the gun nest and addresses Jaya.  ``Agent.  You've looked better.''

``Agent, I've seen-''

``Who's in command here?'' he asks impatiently, interrupting her witty retort.

``I am.''

``Well it will be a pleasure working with you,'' he says, perhaps a little insincerely.

Jaya leans around him and looks onto the train.  ``Is Agent Vogel on this mission?''

``No, unfortunately we could only send a few Agents on this mission.  Who watches the watchers, right?  I'm sure she would send her regards.  Shall we be about it?''

Jaya walks right onto the train and deliberately brushes past him provokingly.  Drake raises an eyebrow at that.  Jonah greets Drake much more civilly and gets a civil response.

Hayley smiles at Drake as she walks onto the train, ``Agent.''

\hl{``Agent,'' he replies.  ``Good to see you again. I do look forward to looking with with you,'' he fumbles unexpectedly and then just blusters past it, saying loudly, ``Alright everybody aboard!''}\footnote{\textbf{Suko T }Thanks for letting this go through, I thought it was so adorable. :) \textsubscript{10/01/14 11:15am}}

Hayley doesn't seem to notice the fumble and smiles pleasantly, ``Me too.''




\sceneHeadline{On the Train}

Rook comes out of the cockpit and does a formal handoff with Jari and Rook leaves the train.  On the train there are eleven other people, roughly separated into two groups.  One of the groups is clustered loosely around Drake and the other group is clustered around this short really ugly guy with an Agent badge.  His eye has clearly been knocked out at least once, he's got rotting teeth, he looks like a mean SOB.   He's chewing something.  His team is very rough around the edges, though Drake's team isn't pristine either.



Jaya glides up to the unknown Agent smiling really big with her own yellowed teeth.  She salutes, ``Agent, interesting meeting you.''  He spits a gob of something black and disgusting on the floor.  Hayley cringes and pointedly looks away from the area where he is.  Undeterred, Jaya continues, ``I'm Agent Parvadi, you may have heard of me from...Nicklepan.  Very excited to be working with you on this mission.''

When he doesn't reply immediately, she just waits and takes up a stance, arms crossed, right next to him.  He looks up at one of his team members and that guy says, ``'K.''

Jaya calls loudly, ``Hayley!  Come here.''Hayley walks over, focusing very closely on Jaya so she doesn't have to look at the really ugly person.  ``Yes, sir?''

``I think we should get to know the rest of the team that we are going to be on this mission with.''

Hayley looks visibly unhappy at this instruction, and with noticeable reluctance turns to the Agent with a practiced smile and says, ``My name is Agent Hayley, it is a pleasure to meet you.''

``Rust,'' he says shortly and spits again.  Hayley looks a bit green at this disgusting display but she tries to keep smiling.  ``Adorable,'' he says.  Hayley then introduces herself to the rest of Agent Rust's team.

``Commanders?'' asks Jonah.  ``I wanted to ask a question about what happens when we arrive.  The SAC-04 may have a Praetor who \textit{may} be willing to negotiate, but we don't know.''

``Yeah, neither did Nicklepan.  Not one seems to know.''

``What is the protocol you wish us to follow when we get there?'' asks Jonah, trying to divide his attention equally between Drake and Jaya, which makes Jaya scowl at him.

Drake replies, ``Well I don't really wish to see anyone dead, so I'd like defensive deployments right out of the gate.  Then I figure we'll do some recon of the area and then proceed onto SAC-04 and once we meet the Praetor, we go from there.''

``And how should we approach the Praetor?  Straightforward or-''

``I like straightforward,'' says Drake.  'But aggressive if we need to be.''  He calls out to Jaya, ``What do you say, Agent?  You want to take point?''

``We have to protect our asset,'' says Jaya, waving in Douglas' direction.  ``But yes, we take the fucking point.''

Rust says, ``Fodder,'' and watches Jaya's reaction.  She doesn't seem to be twitching any more than she already was (which was a lot).

``Alright, I guess we settle in,'' says Drake.

Hayley continues through the train, introducing herself to all of Drake's team as well.  

 {\color[RGB]{74,134,232}::I need to tell you something in private.  Hold still and listen.  I was told to ask you if I need to administer any kind of first aid.  I assume you'll let me know.  Okay?  Nod if you understand and I won't have to ask you in front of all these damn people.::} 

Jaya just keeps scratching a scab on her cheek and looks out the window, giving no indication she even heard Jonah's thoughts.  

 {\color[RGB]{74,134,232}::Alright, so be it.::   } 

Jayce goes to sleep.  Jonah clarifies with Hayley that she needs to protect Douglas and Jayce over everyone else.  Some time passes.  Drake makes small talk with Hayley about guns and knives.  Hayley is very interested and sits as close to him as possible without violating any social protocol rules.




\sceneHeadline{SAC-04- The Mount of the Old Man}

\jumpHeadline{THE CARDS }

The Omen- Green

Children of the Corn- Green

Near Dark- Yellow

Poltergeist- Red

Let the Right One In- Red

Misery- Orange



Jaya stands at the door, Hayley positions herself to step out first in front of Jaya.  The doors open and a wave of cool wet air rushes in.  The air is damper than we've ever felt.  Once we're on the small train platform we are greeted by a sight we have never seen before.  Everything is green.  Vegetation is everywhere, there's even moss and other greenery on the platform itself.  Jaya draws her gun, Jonah drops to one knee defensively.  Hayley continues to move forward in a defensive posture.



Beyond the platform are trees, fucking enormous trees.  More trees than any of us, including Hayley, have seen before.  They are densely packed such that anything could be hiding in their foliage.  Beyond the trees, there are huge rocks that seem bigger than any building we've seen (we have no concept of mountains).  There's the sound of rushing water, like an enormous shower or tap has been left on.  



In a clearing near the platform (100 yards away) is a large boulder and pinned to it is a naked man with a long scraggly beard.  There is a large piece of black metal (like a pylon) driven through his sternum and he appears to be hanging from it. There are stains on the rock below him.  He has no hands (it looks like they have been amputated) and his feet are mangled.  He is not moving.



\textbf{{[}The Omen is triggered, 10 tokens enter the pool for a total of 20 in the pool{]}}



Hayley continues to look around.  The sky is very blue, a color which is very disconcerting.

Jaya says, ``I think we should investigate.''

Drake's teams are still on the train, Lackovich's squad is spread out over the platform.  Drake calls out, ``Is the area secure?''

``Hard to say,'' says Jaya.  

Hayley sees small movements in the trees (birds and small creatures) and reports it.  

Jaya calls back to Drake, ``There's a fucked up guy out here, we're going to check him out.''

Jonah instructs Lackovich's team to protect Douglas and Jayce while we walk up to the guy pinned to the rock.



{[}\textit{Challenge 1: Notice to Scan for Life.  Ladies' Maid 2 (Hayley) → Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}  Hayley looks at the guy and thinks that he's not dead, or if he died, it is very recent.  The spike does not appear to be piercing his heart.  The guy is naked.

Jaya calls out to the guy, ``Hey!  What the fuck happened here?''

The guy's eyes are closed one moment and then, creepily, open the next moment. He raises his head.  Hayley steps in front of Jaya and raises her rifle to point at the guy.  Jaya has her gun at the ready as well.

``If you cross the Rubicon, you will awaken Supay,'' he says.

``Have we crossed the Rubicon?'' asks Jaya.

``Agent Morgan said we did,'' says Hayley. 

\hl{``Water,'' whispers the guy hoarsely.}\footnote{\textbf{Rebecca S. }OoOoooOooooooh.  I just got this \textsubscript{10/01/14 9:11am}}

``Are you the Praetor?'' Hayley asks him.

``If you cross the Rubicon-'' and the guy stops and looks at Douglas.

``Give him some fucking water, Hayley,'' says Jaya.

Jonah is trying to figure out how this guy is still alive.  {[}\textit{Challenge 2:  How is he still alive?  Forensics 2 (Jonah) → Matched }{]}. There is a white silvery discoloration, like a mold on the stumps of his hands and around the stake.  He's extremely emaciated and appears to be starving.  One eye is occluded with white shit.  He should be dead already.  His skin is a little darker than ours, and his forehead is a little flatter than ours.

``The Harbinger comes in this world-moment,'' says the guy.

Jaya slaps the guy's leg (which is very broken), ``Hey!  What's a Rubicon?''

``Why are you here? Why was this done to you?'' asks Jonah.

``I am here to warn you,'' the guy whispers.

``I can put you out of your fucking misery,'' says Jaya, raising her gun.``No.  No you can't,'' he says.  ``All you can do is leave.''

Jonah offers medicine for the pain.

Jaya calls over Jayce and Douglas.  Lackovich sends Morley with them.  Jaya asks what Douglas knows about this. There's a lot of complex hand signals.  Neither of them seem to know what's up with the guy.  Douglas has never seen this before.

Hayley is examining the metal spike and trying to calculate what angle or force was required to do this to the guy.  



{[}\textit{Challenge 1: Notice.  Sixth Sense 1 (Jaya) → Matched }{]}.  Jaya notices that there's someone coming through the woods.  Jaya yells, ``\hl{En garde!}\footnote{\textbf{Rebecca S. }we desperately need a better phrase for this \textsubscript{10/01/14 9:12am}}\footnote{$\rightarrow$\textbf{Suko T }Can we just say ``Heads up?''  Or ``Incoming?'' \textsubscript{10/01/14 11:16am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'll throw out ``Echo up!'' or ``E-up!'' as totally made up terminology to mean ``Eye's up!'' or ``Head's up!''. \textsubscript{10/01/14 9:51pm}}`` and spins and points her gun at the the approaching person.

Out of the trees comes a guy with dark skin like the guy who is pinned to the rock.  He's naked except for a loincloth and is moving with a very odd cadence.  He has an strange bowl in his hands (made from a gourd but none of us know what that is).

Hayley jumps down from the boulder and steps between Jaya and the loincloth guy, her rifle at the ready.

``Fucking halt!'' Jaya yells at the loincloth guy.

``HA!'' he says loudly, almost like the sound is startled out of him.  ``Comingcomingwhat?  HA!''

He keeps moving forward.  Jaya says intimidatingly, ``I said fucking HALT.''

The loincloth guy steps back a few paces.  ``Halt!  Halt!  Halthalthalt!'' he mimics.  There's a certain look to his face that makes him look stupid.

``Do you need assistance?'' asks Hayley.

``Assistance?  Food!'' says the loincloth guy and he points to the pinned guy.  There is some sort of gruel in the bowl.

``Just let him fucking die,'' says Jaya.

``Fucking die!'' says the loincloth guy gleefully.  ``Nonononono....Newcomers!  Newcomers!  Listen to the warning.  Yes?  No?''

``No,'' says Jaya and Jonah.

``No listen to the warning?  No?  Oh.  I cry,'' says the loincloth guy.

``Who is the warning coming from?'' asks Jonah.

``I cry.  I cry.  HA!''

``Stop that.  You're freaking me out,'' says Jaya.

``I listened to the warning,'' says Hayley. ``Would you like assistance?''

``Warning for you, warning for you,'' says the loincloth guy.

``Oh jesus, we're here on a mission!  Not a fucking humanitarian mission!'' says Jaya impatiently (and also surprisingly multi-syllabically).

``Feed the Omen!'' says the loincloth guy.

``We are taking the Omen down.  He has Omened his last. Okay?'' says Jaya.

``Would you like him to come down?'' Hayley asks the guy.

The guy's eyes widen and he looks anxious and shakes his head.  ``That would be bad?'' Hayley asks.  Jaya ignores all this and waves over Morley.  She orders \hl{Morley}\footnote{\textbf{Rebecca S. }my new favorite cannon fodder! \textsubscript{10/01/14 9:14am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Just cus he's a dude... \textsubscript{10/01/14 9:51pm}} to help her and they take the Omen down.

``Nooooo,'' moans the loincloth guy, clearly distressed.

When Jonah looks back at the rest of the team, he can see Drake has oversight on the situation and is covering the area.  Lackovich is looking a little disturbed.  Javier has an abstracted expression on his face, like he's communicating with someone mentally.

As Jaya and Morley lift the Omen down, there's a stretching tugging snapping sensation and something breaks free from his body.  Around the spike are tendrils that have broken off and are leaking a thick white powdery substance, somewhat like blood if blood were made of ashes

Hayley offers the Omen the gruel, and he eats slowly, without enthusiasm.

``Okay good, see we're doing some good here.  Liberating the locals from their fucked up environment.  We should feel really good about ourselves and I'm sure this will endear them to us in the future,'' says Jaya confidently.

``Listen, listen,'' says loincloth guy. ``Listen. No one listens.''

\hl{``Where are we \textit{not} supposed to go?'' asks Jaya.}\footnote{\textbf{Suko T }So clever! \textsubscript{09/30/14 11:59pm}}  The guy points down the path.

``Okay, we're moving out!'' and Jaya points in the direction that the guy pointed.

``I'm sorry, I'm sorry, I'm sorry,'' the guy says to the Omen.

``Don't be sorry, it will be fine.  You can just show us the way!'' and Jaya firmly shoves the guy in the direction she wants to go.

``Agent,'' Drake calls out, ``is the train clear to leave?''

``Hell yeah!  Let's get this started!'' replies Jaya.  ``The locals really assure us that we should not go in this direction.  So let's head off!''

In a wrecked voice, the Omen says loudly, ``Do.  Not.  Wake.  Supay.''  Jonah gives him some analgesics and the Omen looks at Jonah and says, ``Fools.  Go.''



The train leaves.





We move out down the path, pushing the loincloth guy in front of us.  We hear a roaring, rushing sound that gets louder and louder.  Suddenly there is a break in the trees and before us is a huge rushing river.  There's a narrow decaying wooden rope bridge stretched out over it. We see remains of more secure older bridges and the moss covered remnants of what look like streets along the banks.  



On the other side of the bridge is more jungle, and rising out of that is a decent sized mountain (not that we know what one looks like).  It looks like there's a stairway cut into it, and there is vegetation and green stuff all over it.  There are other mountains next to it, some of them larger and at the top they have some white stuff.  We are feeling a little short of breath and the humidity is clinging to our skin.



The guy approaches the bridge and looks upset.  ``No.  We should not go.  HA!  No stay away from the food.  The place of food.  Noooo.''

``What IS that?'' says Jonah staring at the river in horror.

``Sir, shall we approach this like we did the Shaft?'' Hayley asks Jaya.

``Actually I'm a little freaked out.  Have you seen anything like this before?'' asks Jaya.

``No, but there are many things I haven't seen before,'' says Hayley calmly (though Jonah may note that her breathing is shallow and fast, and her skin paler than usual).  She sets down her backpack, pulls out a rope and knots it around her waist.  She secures her rifle over her shoulder and then walks up to Jaya with the other end of the rope.  ``Shall I proceed, Sir?''

``Ah, let's establish a solid base here first and then proceed. But good initiative, Hayley.''

Jaya waves over Javier and hands him the end of the rope.  ``Javier, I need you to be strong.  Hayley's going to go across and I need you to be solid anchor point to retrieve her, should anything go awry.''

In a voice that sounds almost feminine and certainly not his usual cadence, Javier says, ``I will keep her safe.'' He grips the rope firmly.



Jaya calls back to everyone else, ``We're going to send Hayley over, I want you guys to defend and observe the other side of the river and, you know, shoot the shit out of anything that might approach.''Drake confirms and his teams spread out to cover either side.  Jonah can tell that everyone on Drake and Rust's teams also think this river thing is a little freaky or at least weird.  Drake shows his discomfort by looking like he wants to punch something.



Jaya turns to Hayley, ``You're going to go over, establish the rope, then we send the others over, one at a time.  Fall back if anything gets fucked up.''

``Yes sir,'' says Hayley.  Jaya gives her a good luck slug to the shoulder.  Hayley, \hl{used to this by now}\footnote{\textbf{Rebecca S. }only took 30 or so sessions... \textsubscript{10/01/14 9:17am}}\footnote{$\rightarrow$\textbf{Suko T }Hayley is a slow learner. \textsubscript{10/01/14 11:17am}}, smiles and nods at her.

Hayley sets foot on the bridge and realizes immediately how incredibly fragile and about to disintegrate the bridge is.  {[}\textit{Challenge 2: Cross the Terrifyingly Precarious Bridge.  Athletics 3 (Hayley) → Overcome! }\textit{\textbf{2 VP (Hayley)}}{]}  Hayley takes a deep breath and then sprints easily and unhesitatingly across the bridge, not pausing as slats crack and fall away under her feet as she goes.  The guy is covering his eyes and moaning and yelping as Hayley crosses the bridge.

As Hayley reaches the halfway point, the guy tugs at Jaya's metal hand and says in an anguished sounding voice- ``No!  No!  Waking...''

Jaya pushes him down to the ground, ``Look why don't you just sit down, okay?''  He kneels subserviently to the ground, clinging to Jaya's metal hand as if for dear life.

When Hayley reaches the far side of the bridge, the guy screams and in the distance we hear a roar that echoes through the mountains.



\textbf{{[}14 Tokens remaining{]}}




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 3
\item Pool: 3 + 3 (3rd PC-initiated Scene)
\item Pool: 6 + 4 (4th PC-initiated Scene)
\item Pool: 10 + 10 (The Omen)
\item Challenge 1: Notice to Scan for Life.  Ladies' Maid 2 (Hayley) → Overcome! \textbf{1 VP (Hayley)}
\item Challenge 2:  How is he still alive?  Forensics 2 (Jonah)→ Matched
\item Challenge 1: Notice.  Sixth Sense 1 (Jaya) → Matched 
\item Challenge 2: Cross the Terrifyingly Precarious Bridge.  Athletics 3 (Hayley) → Overcome! \textbf{2 VP (Hayley)}
\item Pool: 14
\end{itemize}




\jumpHeadline{VP Totals }

\hl{Hayley 3}\footnote{\textbf{Rebecca S. }high five! \textsubscript{10/01/14 9:19am}}

Jaya 0

Jonah 0




\jumpHeadline{Quotes: }

``Petting the cupcake with a knife.'' - Suko (referring to Rebecca)



``He used to be muscle-y until our world expanded to include...Drake.'' \hl{-Rebecca}\footnote{\textbf{Rebecca S. }you have the audio of the session so I guess you have to be right-- I thought Nate said that though \textsubscript{10/01/14 9:18am}}\footnote{$\rightarrow$\textbf{Suko T }*technically* you just made a very clear ``Drake'' gesture and I said his actual name, but I didn't think the fine point of that was worth spelling out.  But yes, you really did say this. :) Nate had the lead-in line about how we went from most muscles to not muscle-y at all and back to second-most muscles. :D \textsubscript{10/01/14 11:04am}} (referring to Javier)


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:10pm
\end{flushright}

