\setcounter{chapter}{ 33 }
\chapter{\textbf{``SAC-04'', part 2} }

\subChapterTitle{``Red Shirts in the Mist''} 

\deets{Suko}{Oct 8th, 2014}



Lost some redshirts already.  Not looking good for having any left by the end of the mission. \hl{Crossed the river, hiked up a mountain}\footnote{\textbf{Nathaniel Ford }''Patrol Group One Goes For A Nice Hike'' would be an appropriate name for this session. \textsubscript{10/10/14 12:51pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{10/10/14 2:26pm}} chased by (allegedly) deadly mist.  There were tears.  And vomiting.  And creeeeepy people.  And a giant pile of bones. 


\jumpHeadline{Our gear:}


\textit{Jaya}

{\parskip=0pt
Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3 (with one arm modified to accommodate her awesome mechanical arm)

AMP 3

Hush Radio 1

Gauss Pistol 2

HE Grenades 2

Binoculars 2

Heads-up Display 4

Letter of Marque 2

Forensics Bag 1
}


\textit{Jonah}

{\parskip=0pt
Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

Field Surgical Kit 2

Medkit 1

HESP Radio 2

Gauss Pistol 2

HE Grenades 2

Electronic Bypass Kit 3

Heads-up Display 4

Operator Integration 2

Forensics Bag 1
}


\textit{Hayley}

{\parskip=0pt
Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

MedKit 1

Hush Radio 1

Heavy Pulse Rifle 3

HE Grenades 2

Binoculars 2

Heads-up Display 4
}

\jumpHeadline{THE CARDS }

{\parskip=0pt
\hl{The Omen- Green (triggered)}\footnote{\textbf{Rebecca S. }Ugh, so depressing to remember/realize that we've only triggered greens so far. \textsubscript{10/10/14 7:09pm}}

Children of the Corn- Green

Near Dark- Yellow

Poltergeist- Red

Let the Right One In- Red

Misery- Orange
}

\jumpHeadline{The River}

\textbf{{[}14 Tokens in the pool{]}}



We are at the edge of the ``river'', the water is turbulent and fast moving.  When Hayley runs across the bridge and sets foot on the other side, there is a roar that echoes through the mountain.  It sounds sorta like a human roar but we've never heard anything exactly like it before. 

``What the fuck was that?'' yells Jaya, addressing her crew.  No one answers except the skinny guy and he squeaks, ``Supay.''

``Hayley!  Anchor the rope, we need to get across NOW,'' orders Jaya.

Hayley had kneeled down, head bowed and breathing hard, to recover from the terror of running across the bridge.  At Jaya's order, she stands and with shaky hands, ties off the rope to the remaining concrete pillars of the old bridge.  Jaya tosses more ropes across and we take time to construct a more secure rope bridge. 



{[}\textit{Challenge 1: Notice.  Secret Truth 1 (Jaya) $\rightarrow$ Matched }{]}.  Jaya looks down at the river and sees it start to glow and swirl and rise up.  She starts feeling a dull headache.  Jaya yells at people to get moving and then calls Jayce over and asks him in a whisper if he sees anything going on with the river.  He looks upriver and looks surprised.  There is a thick mist pouring down river and overflowing the banks. 

``We're fucking moving!'' yells Jaya.  Jaya sends Jonah over the bridge, followed by Jayce and Douglas.   Hayley watches the people cross carefully, holding onto the rope on her end in case they break and she has to hold onto them.

Jaya notices the mist getting closer.  She sends Lackovich, Javier, Morley and Breccan next.  Once he crosses, Javier helps Hayley monitor the people crossing the bridge.  

Drake steps up and Jaya says ``Eyes up the river'' and she crosses ahead of him.  When she looks back, Drake and Rust are conferring.  Everyone seems a little nervous except Douglas who seems pretty at ease.  Drake sends his team over.  

The mist is now definitely overflowing the riverbanks and spilling into the forest.  While we don't have much experience with mist, it certainly is approaching alarmingly fast.  Jaya shouts ``Douglas, what the fuck is this?'' and points to the mist.



Jonah notices the old road goes to the mountain and to a big metal door, and heads toward it with Lackovich and \hl{Morley}\footnote{\textbf{Nathaniel Ford }I have only much belatedly realized we named a red shirt after Jules. \textsubscript{10/10/14 12:54pm}}\footnote{$\rightarrow$\textbf{Suko T }Hee!  I realized that as I was typing this up and it made me giggle every time I typed his name.  We really should stop naming npcs after people we know.  It really doesn't end well for them.  Not looking good for Javier, although he may get a pass since his other half (Davis) bit it. \textsubscript{10/10/14 2:24pm}}.  The door is set into the mountain and seems to be made of solid metal.  It looks a bit like the one in SAC-09 (though this one says SAC-04).  There is a mangled track that goes up to the door but it is buried in dirt and vegetation just a few yards away from the door.  There is mold and condensation on the door.  Jonah can't find any kind of control panel or opening mechanism.  As he searches through the vegetation around the door and finds the decomposed remains of a body.

Jonah says over the radio, ``Found a door.  No obvious way to open it.  Should get Douglas here.''

Jaya sends Jayce and Douglas to Jonah and then calls out over the river for them to bring over the skinny guy.  Only Rust's team is on the other side at this point.  Rust cocks his head and looks at Drake.  Drake grunts at Rust and Rust grunts back and they appear to have communicated something.  Drake orders Grabber to take the guy across.

Hayley pays extra attention to this transition as Grabber doesn't have both his hands as free as everyone else and he's carrying extra weight.  The skinny guy isn't trying to get away, but he does seem unhappy and moaning no.

Douglas and Jayce show up at the door and they start signing to each other.  

``Does he know how to get in?'' asks Jonah.

``He says it's a back door.  It's not our way in,'' says Jayce.

``Where is the way he does know?'' asks Jonah.

Jayce starts to reply but Douglas just points at path that goes up the mountain.

Jonah radios Jaya, ``Status?''

``We're still crossing the fucking bridge!''  Jaya turns away from the radio a bit to yell at people to move faster.  She turns back to the radio, ``Is the goddamn door open yet?''

``Apparently it's not our door,'' says Jonah.  Jaya is pissed about this.

Almost everyone has crossed at this point.  Just Rust and two others are still on the other side.  Jaya calls in her squads and starts marching up the hill, making Hayley and Javier abandon their posts at the rope bridge.  Jaya doesn't see Drake's reaction to this.




\sceneHeadline{The Mountain (Hill)}

The road goes up the mountain, wide enough to march two across comfortably. 

{[}\textit{Challenge 1: Notice (individual challenges).  Thrown back (Jaya).  Thrown back (Hayley).  Forensics 2 (Jonah) $\rightarrow$ Overcome! }\textit{\textbf{2 VP (Jonah)}}{]}.  Jonah notices that Hayley, who is usually quite crisp, is limping more noticeably than usual.  She is swaying and staggering a bit, almost like she is drunk.  Jonah starts noticing that everyone is moving or behaving a little oddly.  Jayce's nose is bleeding.

``Are you okay?'' Jonah asks Jayce.

Jaya looks at Jayce and accuses him of being on drugs.  They squabble a bit.  Jonah asks them to calm down.  ``Are you in pain?'' he asks Jayce.

``A little headache but...''

``Anyone else have a headache or feeling sick?'' Jonah asks the whole group.

``I've had a headache this past fucking week!'' says Jaya loudly.

``No headache but it feels a little like when I'm suffocated,'' says Hayley.

``Uh...suffocated??'' asks Jayce sounding alarmed.

``Don't ask,'' says Jaya flatly.

The mist is definitely creeping up the mountain.  {[}\textit{Challenge 2: Get Up the Hill Faster.  Air of Command 2 (Jaya) $\rightarrow$ Matched }{]}. Jaya drives her two squads up the hill doubletime.  This is really hard on most of us.  Douglas is doing mostly okay.  The skinny guy is having a hard time keeping up and Breccan is not doing a very good job forcemarching him.  Drake's group are falling behind as they are not doubletiming it.



We reach a switchback in the road.  Breccan now also has a nosebleed.  Jaya pauses to say over the radio to Drake and Rust, ``Agent, do you have any bloody noses down there?''

``Are you in a fight?'' asks Drake.

Jaya growls and clicks her radio on and off a few times before she says, ``NO.  We are not fucking fighting, we are fucking doubletiming it because we have to get up this fucking mountain-''

``Agent!'' barks Drake, ``Verbal discipline!''

``Several of our team have experienced non-combative bloody noses,'' says Jaya, remarkably calmly for how furious she is.  ``I think the fucking mist is fucking with us.''

``Standby,'' says Drake.

``Agent?'' says Jonah over the radio (after asking Jaya for permission).  ``Your medical personnel should keep an eye out.  It's possible there's an illness in the air.  People are starting to bleed but they claim no injuries.  Something is wrong''

``I concur, we have two nosebleeds and a bunch of headaches down here.  However our medics say we haven't come into contact with anything other than the air.  It doesn't seem right,'' says Drake.

``This place is strange,'' says Jonah.

``I concur,'' says Drake. 

And we hear two gunshots go off down the hill from us.



Jaya and Jonah attempt to get a status report, but all we hear from Drake is ``Combat positions!'' before going radio silent.  Hayley goes full defense around Douglas, trying to maneuver him into a more defensive position where she can guard him more easily.  It's a little awkward as he tries to get to a position where he can swing his sword without chopping her head off, but they manage.

Jaya peers through her binoculars to see what is going on.

Drake's team is taking up defensive positions in partial cover.  Drake says over the radio, ``Rust come in.''  

Rust replies, ``Reporting.  Hold on sir.  Drake, channel 3''  

Jaya frantically starts fiddling with her radio to get it to receive channel 3.

Jonah asks Jayce, ``Does Douglas know what this is?  How familiar is he with this place?''

``Not much.  He knows the codes to get into the SAC.  So more familiarity with just the facility, not any of this,'' says Jayce.

``Sir, will we be joining them down there?'' asks Hayley.

Jaya just managed to tune to Channel 3.  ``Hayley, shut up!''

``-an assessment.'' comes Drake's voice over Jaya's radio.  And then we hear a grunt.  ``Alright, pull back to my position,'' says Drake.

Jonah advises Jaya to offer reinforcements.  Jaya just mutters, ``Fuck them'' and doesn't offer.

``Is your position secure?'' asks Drake over the radio on the general channel.Jaya dials through the various channels before she finds the right one and says, ``Yes.  Why did you fire?  What did you see?  What the fuck is going on?''

``AGENT,'' says Drake repressively.

``AGENT,'' says Jaya, mimicking him.  ``Give me some goddamn answers!''

``Agent, we will conference when we get up there. Notify me if there is any danger.  Hold your position.''

``There's a danger to your fucking face,'' mutters Jaya (not over the radio).

Lackovich walks over to Jaya and says quietly, ``Agent, is everything okay?''

``He won't tell us what's going on!'' says Jaya agitatedly.

``Alright, maybe you should just calm the fuck down,'' says Lackovich.

Jaya's eyes go wide and she says in a stage whisper, ``Maybe they're going to fucking turn on us!''

``Chief, if they're shooting at someone they won't have time to explain,'' says Jonah.

``They're not shooting now!'' Jaya says loudly.

``Agent, keep your fucking cool,'' hisses Lackovich.

 

Watching through her binoculars, Jaya can see Drake's team slowly making their way up to us.  Rust's team comes out of the forest, down one person (Carlos).  Rust's team rejoins Drake's team and they confer.  Drake and one of his constables head up to us.  As they approach, Jaya leans over to Lackovich and mutters, ``Be on the ready....''

``Agent, report.'' Drake says to Jaya.

``Nothing to report except nosebleeds and headaches which we fucking told you about already.  We're just standing around like- like- fucking klipspringers.  Just standing on this fucking hill, like a klipspringer pack-'' says Jaya angrily.  Lackovich is trying to silently signal to Jaya to shut up.

``Calm down Agent,'' interrupts Drake.  ``I realize this may be your first field experience.''

Jaya gasps in outrage,  ``Have you been in a fucking field-'' she gesticulates wildly with her gun.

``CALM.  The. Fuck. Down.'' says Drake loudly.

``What the fuck were you shooting at?'' demands Jaya.

``Rust lost contact with Constable Carlos.  Two shots went off and he disappeared off the trail. They moved to the position they last saw him at and he was not there.''

``Do you think he's the one who fired the shots?'' asks Jonah.

``It seems likely based on what I heard,'' says Drake.

``So whatever's coming, probably doesn't have guns,'' says Jonah.

``Whatever!  We don't know that.  He probably turned coward and ran back to the train,'' says Jaya scornfully.

Drake seems to ignore her and says to Jonah, ``Suffice to say, whatever it is, it is coming up from the river and moving up the trail.''

``Which is why we were fucking doubletiming it!'' says Jaya angrily.  ``Thanks for making us fucking wait here.''

``Do we need to revisit who's in charge of this operation?'' growls Drake.

``Fuck no!'' says Jaya loudly.

Drake gets up close to her and says, ``Good.  Now take point.  Do \textit{not} double time it''

``Oh sorry, can't keep up?'' says Jaya nastily.

Drake says with quiet menace, ``Give me one reason not to throw you off this fucking mountain.  \textit{Agent}.''

Jaya doesn't back down and says confidently, ``Because you need me to complete this goddamn mission.'' and she turns and starts hiking back up the mountain (not doubletime tho).

Drake rolls his shoulders and turns to Lackovich, who looks at him nervously.  ``Sir?'' she asks.

``You better watch her,'' he bites out.  He turns to walk back down the mountain to the rest of his team, muttering, ``This better be fucking worth it.''

Jonah says to Lackovich, ``We better head out, yeah?''

``Yeah,'' she says and grumbles, \hl{``Worst.  Fucking.  Nightmare.''}\footnote{\textbf{Suko T }I feel like we're going to get to the point where Lackovich is going to look back at Octavius' torture with wistful fondness. \textsubscript{10/10/14 11:50am}}

``Hayley is watching her,'' says Jonah.  ``Let's watch out for other things.''

Javier says, ``Um, this may be a bad time to mention this but-'' and his voice drops to a whisper. ``Morgan's not happy.  Can we get her to calm down?''

``Given her current.... state I'm not sure.  Do I have permission to offer some way to get her out of this thing?''

``Standby,'' says Javier.  After a moment he continues, ``So Ops realizes she's still under the effects of withdrawal, but ideally she has to stay in command of this mission.  Lackovich is not known to Mohinder.''

``Can I offer her anything?'' repeats Jonah.

``Not if you don't want her going into shock, she still has a few hours to go before she's clear.''

``Ah, so we just have to survive for a few more hours.  We've been through worse,'' says Jonah to Lackovich and Javier.  ``We just need to be extra on top of things until she's done.''  Lackovich nods.



Jaya marches along, complaining vehemently to Hayley about Drake.  Hayley nods and makes noncommittal noises.  Douglas, Jayce and Morley are with them.  Everyone else is lagging behind a bit.  Jaya walks fast at first to make a point and then slows down to a reasonable ``I feel like shit and can hardly breathe'' pace.

As we head up the mountain, Hayley is trying to instruct Morley on how to coordinate with her to defend Douglas, \hl{basic bodyguarding stuff.}\footnote{\textbf{Rebecca S. }such lost potential... or is this why Morley hung back, trying to help Jaya and Jace? \textsubscript{10/10/14 7:18pm}}\footnote{$\rightarrow$\textbf{Suko T }We should have known he'd be the one to go, he had too many lines and sudden personality/character development in this episode.  Just a set up by the writers to make us care more when he dies. \textsubscript{10/10/14 10:07pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I mean, I suppose I'm not surprised Jaya can't spell her boyfriend's name...

Oh, but yeah! Morley. You totally brought that on yourself. \textsubscript{10/12/14 12:44pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Woah, woah, woah! What is this? High School?  Jace (:P) is certainly not a boyfriend. I can think of several terms that might be used, but none of them involve the world ``friend''.  

Also, picking on my spelling is a low blow :P  I can't even spell the name Hayley right half the time... \textsubscript{10/12/14 8:27pm}}  He tries to listen but is having a hard enough time just hiking up the mountain.

Jaya gets to the next switchback and calls a break.  Hayley checks out the area and gives it a cautious thumbs up.  It's not great but it's slightly more defensible than just being out in the open on the path.  Hayley sets up in a guard position, watching down the road.  

The other two groups join us as we rest and Jaya can see the mist coming up behind them at a steady pace.  She points and says loudly, ``Why didn't you say it was fucking right behind you??  We wouldn't have rested.''

Drake sets a few of his team to guard positions.  Drake and Rust appear to be in the best condition, several of their team members have bloody noses.  One guy upon stopping, vomits.  \hl{Jaya is feeling pinpricks up her arm.  Hayley is feeling very nauseous.}\footnote{\textbf{Nathaniel Ford }Jonah was also not feeling great. Sorry to not distribute symptoms around enough. :) \textsubscript{10/10/14 1:15pm}}\footnote{$\rightarrow$\textbf{Suko T }Maybe not at this moment but you did mention that Jonah wasn't feeling well.  Plus Jonah got the fun of constantly noticing how increasingly impaired everyone was getting (including himself)... I'm sure that went well with his paranoia. :) \textsubscript{10/10/14 4:11pm}}



Jaya can tell that if the mist continues to approach at this rate we won't make it up the mountain before it envelopes us.  She heads to Jonah, ``I've got an experiment idea I want to try.''  She looks over at the skinny guy and then back at Jonah. ``We gotta put him here, like tied to a stake in the ground, and then see what happens to him when the mist gets here.''  Her voice starts sounding a little crazed as she speaks faster and faster, ``Is he going to bleed out his eyes?  Is he going to fall over?  Is he gonna- gonna- and then we would know before it gets to us,''  She takes a deep breath and says more calmly, almost casually, ``So...what do you think?''

``So if it's bad, it'll kill him,'' says Jonah slowly.

``Something's gonna kill him.  Look at him, he's probably not going to make it to the next switchback.  He's gonna fall over.  I just want to make sure he does it while on the road so we can see him.  'Cause I've got my binoculars.''

Jaya takes Jonah's lack of dissent as approval and goes into the woods and finds a piece of wood to use as a stake and cuts up some rope.  She ties it to the guy who yelps ``HA!'' and looks worried.  Jaya has Javier drive the stake into the ground.  The guy moans, ``No.  Supay...''

``Rest!  Just rest here,'' says Jaya encouragingly and pours some water on him.

Jonah goes to talk to the guy, ``What happens when that comes?'' pointing to the mist.

``Supay comes,'' says the guy.  ``Go.  You- No.''

``What happens when Supay comes?'' asks Jonah.

{[}\textit{Challenge 3: Get useful info out of guy.  Social Chameleon 4 (Jonah) $\rightarrow$ Overcome! }\textit{\textbf{3 VP (Jonah)}}{]}.  Jonah offers him some food.

``Yes!  Offering.  Yes.  Yes.  Sacrifice of Offering.  HA! \hl{Offering of sacrifice,}\footnote{\textbf{Rebecca S. }wait, wait, what?? While Jaya and Hayley were playing the vomit game apparently useful info was pouring forth.  Why didn't Jonah mention we needed to offer a sacrifice? Jaya would have cut Guy's throat on the spot! 
Squandered opportunities... \textsubscript{10/10/14 7:21pm}}\footnote{$\rightarrow$\textbf{Suko T }Yup, I wonder if Jonah will tell us any of this because Ion seemed to treat it like Jonah felt it was senseless babbling.  Totally good info here tho.  ``Supay all around'' also very useful to know.

Oh and it also puts a spin on Guy's earlier mention of ``Place of Food'' \textsubscript{10/10/14 10:09pm}}`` says the guy, accepting the food.

``Food?  Food will do it?'' asks Jonah.   ``What is that coming up the hill?  Is that Supay?''

``No.  Supay all around,'' says the guy.  ``This \hl{world-moment}\footnote{\textbf{Rebecca S. }I feel like I'm getting the vibe of what ``world-moment'' means... \textsubscript{10/10/14 7:22pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm pretty sure that sentence is wrong somehow. Either I misspoke it or garbled it somehow. \textsubscript{10/12/14 12:45pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }No! No backsies! I so rarely feel like I get what's going on, you can't take this from me! Cruelty! \textsubscript{10/12/14 8:25pm}}\footnote{$\rightarrow$\textbf{Suko T }There are likely transcription errors for the Jonah/Guy scene.  Rebecca and I were talking rather loudly about vomiting and you and Ion were talking rather quietly so some words are very likely mis-transcribed.  Feel free to amend!  It's for posterity, after all. :) \textsubscript{10/12/14 10:14pm}} is not for me.''

``What are you afraid of?'' asks Jonah.

``For you.  HA!  You will leave this world-moment.  This world moment is to others.  Is the price of betrayal.  HA!  Even just he lived?  He stayed in this world moment.  Stay!   Go!   Supay is always watching.  Stay here.''

``We can't, we have to go up.  Do you want to stay?''

``Don't go up.  Stay in this world moment...HA!''

While this is going on, Hayley goes to vomit in the bushes somewhere, as politely as possible.  She feels a little better.  Jaya tries to do the same but can't make herself do it on command, despite Hayley's helpful coaching.

``Okay let's go!'' says Jaya to Jonah.  Jaya looks at the guy staked to the ground and then at Drake and shrugs, ``Let's see what happens. We're going up.''  Drake looks at Rust.  Rust half raises an eyebrow and spits.  Drake grunts at him.



The skinny guy wails and moans, ``Remember.  I'll remember.....HA!  Stay in the world-moment.  Noooo.....'' as we leave.  Jaya watches him through her binoculars.  The mist is definitely gaining on us.  \hl{The guy wanders around the stake, he doesn't seem to be trying to escape.  The mist envelops the guy and we hear the occasional lonely ``HA!'' echo up the path.}\footnote{\textbf{Suko T }Awww.... \textsubscript{10/10/14 11:54am}}  Jaya switches to the thermal sensors on her helmet and watches what happens to the guy.

The guy is kneeling on the ground with his arms above him and then his arms drop.  His body seems to float up into the air and then it just...fades away.

``I'd like to inform all members of this party,'' says Jaya loudly and broadcasting through her radio, ``That when the mist gets you, you are fucking gone.  So let's stay ahead of this cloud, people!''

``What do you mean?  You can't see him,'' says Jonah.

``He doesn't register on the thermal sensors anymore,'' says Jaya.

Jonah turns to Javier, ``Javier, I hope you got all that.  Has anyone been here before?''

``That's an unequivocal no.  Rook is awaiting more information,'' says Javier.

``Please have him let us know when he recognizes anything because we don't know what we're looking for out here,'' requests Jonah.

Drake says to Jaya, looking up the mountain and at the mist, ``We are not going to outrun this thing.''

``Fucking cloud can't get us. It's time to get moving.  We have to go faster.  End of fucking story.  We need to double time it,'' says Jaya with authority.



{[}\textit{Challenge 5: Get Most of the Team up the Mountain Ahead of the Mist.  Bad Cop 3 (Jaya) + Left Hand 3 (Jaya) + Stash 2 (Jaya) + Grim Visage 2 (Jaya) + Small Unit Tactics 3 (Jonah) $\rightarrow$ Matched}{]}.  \hl{Through a combination of yelling, intimidation, screaming, careful dispensation of drugs (mostly to Breccan and Morley), and just physically dragging people, Jaya hauls most of the team up the mountain}\footnote{\textbf{Suko T }Drake's gotta give Jaya at least little credit for this one, this is pretty damn impressive. \textsubscript{10/10/14 11:55am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Oh, credit is given. Maybe not by Drake \_per se\_, but it was an impressive performance. \textsubscript{10/10/14 1:19pm}}, assisted by Jonah's more orderly tactics of getting people to help each other.  Even some of Rust's people are a little intimidated by Jaya FaceTM.



Jayce stumbles and his nosebleed is getting worse.  Jaya is pretty much hauling him up the mountain at this point.   At some point Zengada just loses it and charges down the hill into the mist, firing his gun wildly.  We hear a heavy thump and we hear his gun go off again and some bullets spray past us. Then silence.  

The mist is swirling gently around our feet.  Morley stops and tries to cover Jaya as she is slowed by dragging Jayce behind her.  Jayce gets his feet under him and starts to move. 

Naveen turns around and looks at Jaya and then looks down the hill and then looks at Jaya again and just falls over.  He's bleeding heavily and his eyes roll back in his head.  Jaya leaves him where he lies and keeps going.

The mist is now up to her thighs.  

Morley, bringing up the rear behind Jaya, stumbles.  Jaya screams at him to keep moving and she can hear him trying to get up again but she can't see him in the mist anymore.  

Jayce is burbling incoherently at Jaya. Some of it is kind of emotional stuff but Jaya blocks it out.  After a while she can't hear Morley behind her anymore.



We continue to stagger up the mountain (all except Carlos, Zengada, Naveen, and Morley).  Jaya and Jayce are bringing up the rear.  Jaya's headache is getting worse until there is a moment of intense stabbing pain and she falls to her knees.  She realizes vaguely that the mist is no longer swirling around her.  Jayce collapses to the ground next to her and pants, ``Okay....so...we shouldn't....sleep together.''  And his eyes roll back and he passes out.

Hayley and Douglas are in the lead, Douglas suffering the least from elevation sickness and Hayley determined not to leave him unguarded.  Eventually Drake yells, ``Agent, halt!''  Hayley doesn't notice, completely focused on keeping one foot in front of the other.  Drake yells louder, ``Hayley!  AGENT!  \textit{HALT}!''

That gets through and Hayley comes to an abrupt, swaying halt, and weakly tries to get Douglas' attention to tell him to stop.  He does.



{[}\textit{Challenge 1: Maintain Mental Stability.  Unashamed 1 (Hayley) $\rightarrow$ Matched}{]}.  Hayley turns to look back at Drake but is distracted by the phenomenal view of this gorgeous valley that stretches out below her.  The mist seeping through the trees is creepy but also atmospheric and beautiful.  There are rainbows shimmering in the mist and the mountains... the lush trees....  Hayley is overcome by the unprecedented level of natural beauty before her and takes off her helmet and starts sobbing, unashamedly.

In stark contrast to the valley, Hayley can see the trail below her is littered with bodies, gasping for air and barely moving, some of them reduced to crawling.  Drake is standing in one place looking he's using every last bit of willpower just to stay upright.  Jonah is staggering up the hill looking super drunk.  Hayley doesn't see Jaya or Jayce.  Once she sees that Jonah is alive, Hayley mostly ignores the people and looks out again over the valley, soaking in the view and letting the tears fall. 

Javier stumbles up to Hayley.  Hayley smiles at him through her tears.  ``Isn't it beautiful?'' she asks, gesturing to the valley.  

Javier turns, looks and falls to his knees and starts weeping openly.  He's babbling something, Hayley doesn't think he's talking to her.  He says brokenly, ``I'm sorry... I'm sorry... I didn't mean for it to happen that way....I went back for him...''  

Hayley steps close and hesitantly, gently, places her hand on his shoulder.  He reaches up and takes her hand and grips it as he starts bawling.  They stand there, crying together.



Jaya is having a hard time moving but she's awake.  Jayce comes to and says, ``I'm pretty sure I'm not dead yet.''

``I'm pretty sure I am,'' Jaya fumbles for her pistol. ``But if I'm not, I'm going to make it so.''

``Aww... we're dead together,'' says Jayce, a little dreamily.

``I was going to shoot myself, but I swear to god I will shoot you.  Just shut the fuck up.  I swear my headache is bad enough.''  Jaya attempts to yell, ``Hayley!'' but it comes out as more of an asthmatic wheeze.

``Chief, don't- don't yell,'' says Jonah weakly over the radio.

``Fuck you Jonah,'' says Jaya out loud (not over the radio).

``What about me?'' says Jayce.  ``I suppose I wouldn't have lasted...but... Jonah?  \textit{And Hayley}?  Okay.  I guess I understand that one.''

Jaya replies by turning her head and throwing up.

A shadow falls over her face.  It's Drake.  He's backlit by the blazing sun.  She's never seen the sun burn so brightly before (because it's usually shrouded in haze).   He says through gritted teeth, ``Agent, on your feet or I swear to god I'm going to put you down right here.''

\hl{Jaya flails weakly, ``Go ahead and fucking shoot me.  I'd fucking do it myself if I could move.''}\footnote{\textbf{Suko T }I \textless 3 Jaya \textsubscript{10/10/14 12:01pm}}

Drake leans down and hauls Jaya to her feet.  She feels shitty and dizzy.  He holds her upright until she gets her feet under her.  ``We can't stop.''

``I fucking \textit{know} that!'' says Jaya and tries to wave him off.  ``I fucking got us up this fucking mountain.  Fucking-!''  She starts trying to walk in the wrong direction and he doesn't let go until she is facing the right direction again.  She points at Jayce.  ``Can you? Uh...''

Drake picks up Jayce in a fireman's carry.  Jayce is pretty much incoherent and his face is smeared with blood.  



At the next switchback we rest.   We don't have much choice.  The mist doesn't look like it's coming up the trail any further.  Drake picks the two most awake people- Hayley and Rust- and has them stand watch and tells everyone else to rest.  He even has his medic sedate a few people.  The sun starts to set while we sleep (we arrived here mid-morning and we reached this resting point mid-afternoon).  Hayley is disconcerted by watching the sun set behind the mountain, she's not used to how the elevation makes the sky still light but we're in shadow.  



After a few hours, Rust grunts at Hayley and gestures to Drake.   Hayley looks at him blankly and he grunts again.  ``Kick 'im'' he says, and spits.

``I'm afraid protocol states I cannot assault a superior officer,'' says Hayley.  ``I could get discharged.''

Rust gets up and walks over to Hayley.  He pokes her in the chest with his finger, right over her breast.  ``How you fit in that thing?''

``It fits okay.  It's not custom,'' says Hayley.

``It's not comfortable?'' says Rust, poking her other boob.

``I'm getting used to it,'' replies Hayley not resisting, but not stepping back either and watching him warily.

``Who's in charge here?''

``Agent Parvadi,'' says Hayley promptly.

``I'm sorry \textit{Agent},'' Rust says and spits.  Hayley wrinkles her nose in distaste and looks away.  ``Does that disgust you?'' he asks.

``Yes.''

Rust sneers and slowly wipes his face with the back of his hand and then smears it all over the front of Hayley's armor.  Hayley leans back a little but doesn't yield ground or say anything.  \hl{She frowns.}\footnote{\textbf{Suko T }Please add another to the ``dislike'' list. :) \textsubscript{10/10/14 12:03pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Rust lives to get people to dislike him. \textsubscript{10/10/14 5:20pm}}\footnote{$\rightarrow$\textbf{Suko T }It occurred to me that if Rust hadn't been so good at being an asshole, Hayley may have actually followed his order. \textsubscript{10/13/14 3:56am}}

``Soo...'' he drawls ``You outrank me now?''

Hayley looks puzzled, ``Not that I'm aware of.''

``Then kick 'im.  Not hard.  I don't think he'd like that.  Though...''  he waves and spits again.

``What rank of Agent are you?'' asks Hayley.

``Higher than you, sweet thang.''

``Really?  Oh.  Alright.''  Hayley walks over to Jaya.  Hayley lightly taps Jaya on the shoulder and says Sir?  She repeats it a few times.  At the third soft ``Sir?'' Jaya wakes up abruptly and lashes out.  Hayley gracefully leans out of the way with the ease of long practice.  Jaya rolls over, dry heaves a little and then looks up at Hayley.

Hayley whispers softly, ``Sorry Sir, I just wanted to inform you that I may be dishonorably discharged after I assault a superior officer under orders.''

\hl{``Do not assault-  Do not assault an officer.  Orders.  That's orders.  What time is it?'' asks Jaya.

Hayley says ``Thank you'' and reports the time.}\footnote{\textbf{Nathaniel Ford }This is such an interesting manipulation of the system. And by the system I'm not sure where `TA Handbook' ends and `Hayley' begins. \textsubscript{10/12/14 12:47pm}}\footnote{$\rightarrow$\textbf{Suko T }LOL!  I was wondering if Rust would call Hayley on it, since it was a pretty weak evasion (though she was loopy from altitude sickness so creativity was not going to be her strong suit).  But yes, Hayley totally cherry picks the TA Handbook bits that she wants to ``apply''. :)  She's learning to bend system to get what she wants.  Politely, of course!  She's already tested this out by going around Dr. G and Rook by using Swan and Larissa respectively.  

If Jaya didn't wake up (or Rust pointed out the chain of command issues) I had some other backup plans, so Hayley would have tried something else. \textsubscript{10/12/14 10:42pm}}  There's a sound of velcro ripping as Jaya opens the satchel and pulls out the syringe that Morgan gave her and injects it into her thigh. 

There's a phlegmy, ``Classy.'' from Rust.

Jaya feels an amazing rush.  She runs her hands through her hair and breathes deeply.  She feels like her vision has sharpened, gone catlike.  All of her senses are improved.  She rolls to her feet and looks at Hayley and asks belatedly, ``Who's giving you those orders?''

Hayley has already walked over to Drake and looks at him consideringly.  She then taps him lightly on the foot with her hand.

Drake wakes up immediately and sits up, using nothing but ab strength.  ``Couldn't have woken up to a better sight,'' he says to Hayley.  Hayley smiles back, pleased.

Jaya's head snaps around and she focuses on Hayley, ``Who gave you that order?'' Jaya repeats.  There's a low, phlegmy chuckle from Rust.

Hayley looks a bit alarmed at Jaya's intensity.  ``Are you...feeling better sir?''

``\textit{Excellent},'' whispers Jaya, with a big smile.

``It was-'' Hayley starts to reply to Jaya but then Drake rolls over and gets up.  He heads over to a tree and does 20 pull ups.  Hayley blatantly loses her train of thought and just gapes appreciatively at Drake showing off.  She tries to refocus on Jaya but it's obviously a struggle for her to look away from Drake and all those muscles.  Drake drops lightly to the ground and says expansively,\hl{``I love the TA!  Everyone up!''}\footnote{\textbf{Rebecca S. }The delivery of this made it one of my favorite lines of the night. \textsubscript{10/10/14 7:32pm}}\footnote{$\rightarrow$\textbf{Suko T }Agreed. \textsubscript{10/10/14 10:11pm}}

He walks over to Hayley.  ``Agent, you ready to go?  Rested?''

``Rested, still a bit tired though,'' says Hayley.

He chucks her on the shoulder,  ``Thank you for taking watch. I won't forget it.''

``Good.  Thank you,'' says Hayley with a smile.

``Also, tell Rust to fuck off,'' and he walks away and starts putting his gear on.

Hayley looks very conflicted.  She watches Rust walk around, kicking his people awake.  She has a considering expression on her face.

``Oh to answer your question sir, it was Agent Rust,'' Hayley says to Jaya.  She pauses and looks at Jaya.  ``Do you remember the question, sir?''

``Yeeessss,'' whispers Jaya with really wide eyes.  She's getting a great secondary wave of not just alertness but virility.  She feels completely alive.



Jonah wakes up groggily.  Javier sits up next to him.  ``I couldn't sleep,'' he says.  ``Carruthers is worried.''

``You should have taken something,'' says Jonah.  ``And she should take something.  She needs to let you sleep.''

``Yeah, she's apologetic,'' says Javier.

Jaya is buzzing around everywhere and prodding everyone to get a move on.

Jonah and Javier watch her.  ``The Chief has already taken some, so you better take yours fast,'' says Jonah.

``No shit,'' says Javier.  

Jonah tries to get Jaya to calm down a little and stands up.

``I'm glad you're feeling better Sir,'' says Hayley to Jaya.

``Thank you Hayley. Thank you for, uh, apparently taking watch.  That's very appreciated.  I will note that on the record...that you get commended.''

``Agent Malak already noted it, Sir,'' says Hayley.

``I wouldn't trust that bastard,'' says Jaya.

``Why-''

They are interrupted by Jayce snoring loudly.  Jaya walks over to Jayce, cursing under her breath, ``Layabout men.'' and kicks him.  ``Get the fuck up!'' she yells.

``Shut up woman!'' and he tries to roll over and go back to sleep.

Jaya grabs him by the scruff of his neck and lifts him up and tosses him toward Douglas.  Douglas neatly sidesteps out of the way.  Jayce goes sprawling to the ground.  He gets up and his nose is bleeding again, this time from being bruised by his fall.  Douglas signs something at Jayce and Jayce flips him off.  Jayce wipes the blood from his face and mutters under his breath.  ``\textit{Women}.''



Jaya goes to Lackovich, who is helping Breccan.  ``So...Morley didn't make it?'' asks Jaya, a question in her voice since her memory of that last push is a little hazy.

Lackovich glares at Jaya, ``Jaya?  Shut the fuck up.''

Jaya replies, ``Jesus fucking Christ!  You had a nap!  Just get over it.'' and she walks off.

Lackovich has a moment, looking like she's barely restraining herself from doing something violent to Jaya.  




\sceneHeadline{Top of the Hill}

We get organized and continue up the mountain, even though darkness is falling.  The vegetation starts thinning.  There is a surprising amount of light, for nighttime.  There are two moons hanging in the sky.  One of the moons seems almost like it has a face.  The other one is smaller and is really bright, a pure flawless white.   The stars are unexpectedly bright, a thick band of stars stretches across the middle of the sky and then they spread out across the rest of the sky.



Jonah has trouble looking up because if he looks up too long he feels like he will lose his grip on the ground and fall up into nothingness.  Jonah tries not to look up so much and starts walking closer to the edges of the path, nearer to the trees or the mountain wall.



Jaya feels like the faceless moon is watching her.  If she doesn't look at it straight there's an eye in it.  Looking at her.  Jaya pulls her gun.  Drake says, ``Agent?'' and Jaya hears a gun being pulled.  ``Are there hostiles?''

``Moon is kinda fucking hostile,'' says Jaya.

\hl{Lackovich says to Drake, ``She's fucking with you.'' and walks up to Jaya.  When she's close to Jaya she says under her breath, ``Put. The.  Fucking.  Gun.  Away.  Making us look bad.''

``Ha!  Don't you know a- a fucking joke?  Ha!  Fucking moon...'' says Jaya loudly and unconvincingly, and puts her gun away.}\footnote{\textbf{Suko T }hee! \textsubscript{10/10/14 12:12pm}}

Rust puts his gun away.  Drake glares at Jaya.



After one last switchback, we can see the top of the mountain.  There is an arch there, with a tunnel through it, made of concrete and metal.  There seems to be some sort of sign but we can't read it, the moons are backlighting the whole scene.  It is still and peaceful.

``Fuck yeah!  We're there!'' says Jaya loudly.

``Chief, get it together,'' says Jonah over the radio.

``Sorry sorry,'' says Jaya apologetically to Hayley.

``Rust, rear guard,'' says Drake.

Hayley heads out to the arch, approaching slowly but making sure she's between the arch and Jaya.  Hayley's using her HUD and isn't seeing much.  Jaya takes out her flashlight and looks at the sign.  It says ``TESCO''.  

Jonah asks if Douglas knows if this is the entry.   Jayce says it isn't, it's probably a checkpoint of some kind.  

Jaya is looking around the arch.  She doesn't see any skeletons.  Nothing thermal (besides us) shows up on the HUD.

Jaya says to Hayley, ``Let's go in to get away from the moon'' and she attempts to enter the tunnel.

Hayley interposes herself in the way and blocks Jaya from entering.  Jaya looks surprised.  Hayley explains, ``Sir, we need to check for security measures.''

``There aren't any guards.''  Jaya looks around again and sees a sign that says ``Private property of TESCO''

``There could be automated security measures,'' says Hayley.  ``Either allow me to evaluate the area or wait for the rest of team to arrive so they may learn from what happens to us.''

Jaya waves to the rest of the team in a nonstandard gesture that could possibly be interpreted as a ``come over here'' gesture.  She eventually says ``get over here'' over the radio.

``Hey Javier,'' says Jonah.  ``What's Tesco?''

``Standby,'' says Javier.  After a moment he says, ``Rook says that they were nice people.  You know, teachers and stuff.  And scientists I guess?''

``Like Trenton?''

``Uh... no more like um... Sandals?''

``That's not being clearer.''

``Oh, so yeah, kinda like Trenton...I guess.  Scientist-y,'' says Javier.

``Are they likely to have been armed?''

``Rook thinks you shouldn't assume that they are not without defenses.''

Jonah says over the radio to the team.  ``Apparently Tesco was originally for scientists but don't assume that there's nothing there.  Don't assume there won't be guns or traps.''

``That's why we have guns!'' says Jaya.  ``Get your ass over here.''

Hayley is investigating the arch and tunnel.  {[}\textit{Challenge 1: Notice.  Bodyguard 2 (Hayley) $\rightarrow$ Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}.   Hayley notices bloodstains.  They are old and difficult to decipher what caused them.  Looking in the vegetation nearby she sees a few bones.  She sees a few bits of black glass.  No scorchmarks.

\hl{Jonah heads over and tries to look around but doesn't actually look at anything.}\footnote{\textbf{Nathaniel Ford }For the record, I think I technically mishandled this: I should have given you some piece of misinformation or misconclusion, or something else adverse happening. (I'm not going to retcon it, though, just a slipup on my part.) \textsubscript{10/10/14 2:15pm}}\footnote{$\rightarrow$\textbf{Suko T }I think Ion said that the refresh was more that Jonah doesn't actually use his Forensics in any useful way despite the bloodstains, bones, etc.  So less a misconclusion than a deliberate miss of an opportunity for more information. \textsubscript{10/10/14 2:25pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Right, but simply not doing anything would have yielded that same result. Narratively, skill refreshes should put you in a more awkward situation. \textsubscript{10/10/14 2:58pm}}\footnote{$\rightarrow$\textbf{Suko T }Ah, right, that makes sense. Well you'll just have to be extra mean to Jonah on his next Refresh :D \textsubscript{10/10/14 4:14pm}} {[}\textit{Refresh Forensics 2 (Jonah)}{]}

Hayley reports over the radio, ``There are some bloodstains and bones surrounding the entrance to the tunnel.  They are older, I'm afraid I'm not capable of analysing how old.  But we should proceed with great caution.''

Jaya waits for her team (meaning PG 1\&2 and the VIPs).  She shines the flashlight around.

``Chief!  Stop that.  If anyone was there, now they know where we are,'' says Jonah.

Jaya shines the flashlight at her (admittedly scary) face and says with a predatory smile, ``I want them to know where we are.  So we can find them.'' She clicks the flashlight off.



Jaya heads into the tunnel and Hayley barely manages to get in front of her.  



\textbf{{[}Children of the Corn is triggered, 10 tokens enter the pool for a total of 11 in the pool{]}}



They walk through the tunnel out onto a gently rolling hillock.  On one side we see stretched before us, low buildings made of stone and metal roofs. The moon is hanging over them.  It is sort of magical.  



It flows into another hillock, over which hangs the other moon.  At the top of that hillock are two people, backlit by the moon, sitting and holding hands.  



And to the left, starting slowly at first but then growing to a veritable mound, nay, a hill, nay a mount...of bones.  Bleached white and gleaming in the moonlight.  Skulls.  Femurs.  Ribcages.



Jaya pulls out her binoculars and looks at the people on the hill.  They are wearing loose fitting tunics, pants and sandals.  Their hair is dark and their faces are dark.  They show up on on the heat sensors.  Jaya looks through the thermal scanner at the pile of bones.  It is as cold as death.

Hayley scans the buildings.  It is a veritable city and there are terraces among the buildings.  {[}\textit{Challenge 1: Notice.  Binoculars 2 (Hayley) $\rightarrow$ Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}  Hayley spots a couple of people on one of the terraces, they seem to be doing something, futzing with something and moving around.  There are some terraces that go up to the edge of the mountain and on top of that there are some structures.  Beyond that is rocky grass.

Jaya whispers to Hayley, ``How many do you see?''

``There are at least three,'' Hayley points.  ``They don't seem to be reacting to our presence.  I don't see any heavy arms immediately.''



Jaya radios to Drake and Rust, `` We see some locals...they look really fucking weird...they don't appear to be hostile....but there's a \textit{pile of fucking bones}.''

``Come again?  Bones?'' says Drake over the radio.

``Big ass pile of bones.  Very \textit{clean }bones. There are a couple of people here.  They aren't armed...but I think you should proceed with caution and join us at this end of the tunnel in case things get intense.  But I can't really claim that it's clear right now.''

``Acknowledged,'' says Drake. Rust grunts.

``Come through slowly,'' Jonah advises.  ``It's a little bit disturbing.''

``No shit,'' says Lackovich quietly with a sarcastic laugh.



Jonah looks at our team.  Lackovich is a little disturbed.  Javier is wide eyed and doing a slow scan of the area.  Breccan is looking around with wild eyes in a ``WTF is going on here?  Guys???'' sort of way.  Douglas is looking around cautiously, his sword out again, his shoulders tense.  Jayce is muttering to himself ``OMG I had a good life.... I didn't get laid that often but...jesus...''



Drake exits the tunnel with his rifle out and says, ``This is fucked up.''

Jaya leans toward Drake.  ``I think we should just mosey on through... and shoot anyone that approaches us.''  She presents that like a solid plan of action.

``You want to go over that one more time Agent?  Shoot anyone that approaches us?'' says Drake.

Jaya replies in a hushed voice, ``I think that would be the appropriate response given \textless she casts a significant glance at the giant pile of bones\textgreater  the circumstances.''

``What do you make of them?'' Drake says, gesturing toward the couple on the hill.  As he does so, one of the couple leans over and kisses the other one on the cheek.

``Looks like they are having a real good time, we should avert our eyes and let them do their thing,'' says Jaya.

``You know why we're here, right?''

``I think we should establish a stronger position before we wipe out the locals,'' says Jaya reasonably, her eyes a little glassy.

Drake sighs and mutters under his breath, ``Damn Mohinder.''  He looks at Jaya.  ``We are not wiping out the locals if we don't have to.  I have \textit{clear} orders.''

``That's what I meant-''

``We are here to occupy SAC-04,'' interrupts Drake.

``Which will probably have to result in wiping out the locals-''

``I don't wish for you to jump to that conclusion,'' interrupts Drake again.  ``You understand, Agent?''

Jaya grumbles.  Drake continues grudgingly, ``Much as I might agree with it.''  Jaya smirks at that.

``If we want to engage with the locals without shooting them, we should send him in first,'' Jaya gestures to Jonah.

``May I ask a question?'' says Jonah, approaching them.  ``The Praetor....we don't know what form they will take.  Will Praetors have people that work for them?

``You tell us,'' says Drake.

``Lots of people worked for Rook,'' says Jaya.

``So then, yes,'' says Drake.

``So they \textit{could} be working for the Praetor?'' asks Jonah.

``Our best intel of the area is there ain't been no patrol that's come here and come back,'' says Drake.

``If we can figure out what it wants, that's our best chance of making it through without having to shoot anybody,'' says Jonah. 

``So you're advising avoidance?'' Drake asks Jaya.

``Avoidance, followed by-'' starts Jaya.

``And \textit{you're} advising...what exactly?'' Drake asks Jonah.

``Avoidance, in this case.  I don't know that they work for it. We've seen how viciously it defends itself.  We're assuming that this is part of the defense...Rook suggested that they might be negotiable....'' 

``What do you think?'' Drake asks Hayley.  Hayley doesn't realize he's talking to her.

``Don't confuse the Agent, she's focused on-'' says Jaya.

``I asked for her opinion, how is that confusing?''  He repeats the question to Hayley.  ``Agent, what is your opinion on how to proceed?''

Jaya attempts to give Hayley complicated instructions with just her eyes.``My apologies, I didn't realize you were addressing me,'' says Hayley.  She pauses before answering Drake and looks with concern at Jaya.  ``Sir, are you okay?''

``Yeah, I'm fine,'' says Jaya, annoyed.

Hayley continues.  ``They are not immediately hostile, however there are lots of areas for them to hide.  Lots of cover for them as well in those buildings.  Unfamiliar territory for us, bad angles, very exposed for us to to proceed through.  If we were to-''

Drake looks at Lackovich, ``What about you?''

\hl{Lackovich looks put on the spot and says tightly, ``I concur with Agent Parvadi.''}\footnote{\textbf{Nathaniel Ford }Probably wouldn't be super clear to anyone there, but, for posterity, this was as much Lackovich following chain of command as anything else. \textsubscript{10/10/14 2:32pm}}\footnote{$\rightarrow$\textbf{Suko T }It was plenty clear OOG at least! :) I imagine Jonah picked up on it, since he is often doing something similar for Jaya. \textsubscript{10/10/14 2:40pm}}

Jaya looks surprised.  Lackovich does not meet her eyes.

Drake grunts and Rust, who has somehow approached without us noticing, grunts as well. 

Drake says, ``Alright.  Hayley, you and the Assets are with me.  You-'' he points at Jaya, ``take point.  Lackovich go with her.''

``Uh, I think I should have a medic..'' scowls Jaya.

``Is he in your squad?  Have I requisitioned him?''

Jaya looks confused.

``Then take your medic,'' says Drake patronizingly.

Jaya stomps away and looks annoyed, confused and a little lost.

``Keep moving Chief, try not to get shot.  It makes my day much harder,'' says Jonah with a drawl.

``But without Hayley here-'' says Jaya in a whisper.

``What?  You can't defend yourself?''

``No!  It's just...\hl{she's tactically useful}\footnote{\textbf{Suko T }Aww...Jaya says the sweetest things. :D \textsubscript{10/10/14 12:23pm}}.''

``You know why he took her off, right?'' asks Jonah.

``Because he's going to molest her while we're crossing this field?'' grumbles Jaya.

``There's a little bit of that yes, but mostly he wants to see what you're going to do without her,'' says Jonah.

``Well, then, you're going to have to back me up then.  You better do as good a job as Hayley!''

``Greeeeat,'' says Jonah sarcastically.  ``So if we both get shot, who's going to patch us up?  Hayley?  You ever seen her use a Medkit?''

``No, 'cause you've done a great job.  So don't fuck up!'' says Jaya bracingly and moves on.




\sceneHeadline{The Village People}

We start heading toward the city.  There is a long low wall with a door in it.  Jaya approaches the door, it is open and behind it is another tunnel.

``Chief, what do you see?'' asks Jonah.

``The fucking door in the wall!'' Jaya pauses and blinks.  \hl{``I mean, there \textit{is} a door, right?''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{10/10/14 12:25pm}}

``Yes, just look through the door when you get a chance.''``Don't tell me how to do my job!'' Jaya snaps at Jonah.  

She and Lackovich coordinate and Jaya gets through the tunnel.  Jaya goes to the nearest building and peeks inside.

{[}\textit{Challenge 2: Don't Flip the Fuck Out.  Gauss Pistol 2 (Jaya) $\rightarrow$ Matched}{]}.   Her gauss pistol is comforting as Jaya confronts some weird shit.  Jaya looks through the window and feels her reflexes take over.  Almost without thought, Jaya finds herself with her gun pointed at a woman, the trigger almost fully depressed, just an iota away from launching a bullet through the woman's brain.  But Jaya manages to ease her finger off the trigger and takes stock of what is going on in the building.  The woman is middle-aged with white hair pulled back into a bun.  She is casting a shuttlecock back and forth on a loom.  \hl{Her eyes are entirely glazed over with white}\footnote{\textbf{Nathaniel Ford }http://content9.flixster.com/question/51/99/14/5199147\_std.jpg \textsubscript{10/10/14 2:35pm}}\footnote{$\rightarrow$\textbf{Suko T }If we get infected by the white stuff, do we get wings 'cause we're girls? \textsubscript{10/10/14 4:17pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }There is only one person... er... entity... in the game thus far remotely both interested and capable of getting wings. \textsubscript{10/10/14 5:22pm}}\footnote{$\rightarrow$\textbf{Suko T }Augh!  \textsubscript{10/10/14 5:40pm}} and she is staring right at Jaya (not at her work).  She doesn't appear to be alarmed and her fingers are moving of their own accord.



Jaya eases back away from the window.  Jonah can see she had drawn her pistol and thumbed the safety off.  Jonah radios her, ``Chief?''

Jaya radios back, ``It's cool.  You know how there was that dead guy who wasn't dead?  There's this lady...probably a lady.... who was just looking at me.  Looking at me...'' Jaya peeks back into the room, ``Still looking at me...''

``Is this another thing like the moon?''

``The moon wouldn't look at me.  This lady just kept looking...''

``What is she doing, Chief?''

``She's doing that fabric thing... yunno.  Fuck if I know.  I'm a fucking TA agent.  Not a fucking \hl{workhorse}\footnote{\textbf{Nathaniel Ford }Ah, classism! Love it. \textsubscript{10/10/14 2:38pm}}.''

Jaya looks through another window.  That building is empty.

{[}\textit{Challenge 1: Notice (sound).  Thrown back}{]}



We head into the village.  It is a maze of streets.  Jaya confidently strides forward like she knows where she is going.  Lackovich, Javier, Jonah and Breccan follow her.  The other two teams (Drake's and Rust's) lag behind.



Hayley quickly realizes that Drake isn't moving quickly enough to keep up with Jaya.  Hayley is trying to map out the streets with her Memory for Details and doing her best to keep a mental note on where Jaya should be (approximately), while still guarding Douglas.



Jaya \& Co turn a corner and are surprised at how suddenly they hear a loud, steady, thumping noise.  There is a girl about Riva's age, tossing a large ball against a wall.  The girl has shoulder length white hair.  Jaya peers closer at the girl- the girl's eyes are filmed over in white.  There are no white filaments connecting her to the ground though.  She continues to bounce and catch the ball.



Jaya doesn't notice but Javier immediately takes a step back and fumbles with his rifle.  ``What's up?'' asks Jonah.  

Javier is twitching, ``Make her stop!  Make her stop!'' His voice gets louder and louder and he switches off the safety on his rifle.  ``Make her stop!!!''

``Calm down!'' says Jonah.

Jaya snatches the ball away from the girl.

{[}\textit{Challenge 2: Get Javier Under Control.  Trigger Reflex 2 (Jonah) $\rightarrow$ Matched}{]}. Before Javier can fire his gun, Jonah grabs it, switches the safety back on and pushes it down. 

The girl looks at Jaya and her eyes get sadder and sadder.  ``Javier, I'm going to give her back the ball.  I need you not to flip out, okay?'' says Jaya.

``Ow!'' cries out Javier and he drops to his knees, clutching his head.

``Close your eyes,'' says Jonah.

``No shit!'' says Javier, grimacing.

``Lackovich, subdue your Agent!'' orders Jaya.

``Chief, this is an Operator thing,'' says Jonah to Jaya.

He turns back to Javier.  ``Calm down back there.  Everything's fine.  Close your eyes.  If you need to take a break, close your eyes.  Not you.  \textit{Her.}``  

Jaya hands the ball back to the girl and she starts bouncing it again.

``What is the problem?'' Jonah asks Javier.``The noise-'' says Javier, his breathing labored, having a hard time focusing.  Javier starts fumbling for his rifle again. ``Augh!''

Jonah pulls Javier around the corner and says quietly, ``Carruthers.  \textit{Get it under control}.''

Suddenly Javier blinks and looks very confused.  ``What?  Whoa.  WHOA!''

Jaya looks back at Javier to see how he's doing, taking her eyes off of the girl.



And somewhere in the streets, there comes the strangled gurgling cry of someone dying.





\textbf{{[}6 Tokens remaining{]}}








\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 14
\item Challenge 1: Notice.  Secret Truth 1 (Jaya) $\rightarrow$ Matched
\item Challenge 1: Notice (individual challenges).  Thrown back (Jaya).  Thrown back (Hayley).  Forensics 2 (Jonah) $\rightarrow$ Overcome! \textbf{1 VP (Jonah)}
\item Challenge 2: Get Up the Hill Faster.  Air of Command 2 (Jaya) $\rightarrow$ Matched 
\item Challenge 3: Get useful info out of guy.  Social Chameleon 4 (Jonah) $\rightarrow$ Overcome! \textbf{3 VP (Jonah)}
\item Challenge 5: Get (Most) of the Team up the Mountain Ahead of the Mist.  Bad Cop 3 (Jaya) + Left Hand 3 (Jaya) + Stash 2 (Jaya) + Grim Visage 2 (Jaya) + Small Unit Tactics 3 (Jonah) $\rightarrow$ Matched
\item Challenge 1: Maintain Mental Stability.  Unashamed 1 (Hayley) $\rightarrow$ Matched
\item Challenge 1: Notice.  Bodyguard 2 (Hayley) $\rightarrow$ Overcome! \textbf{1 VP (Hayley)}
\item Refresh Forensics 2 (Jonah)
\item Pool: 1 + 10 (The Children of the Corn)
\item Challenge 1: Notice.  Binoculars 2 (Hayley) $\rightarrow$ Overcome! \textbf{1 VP (Hayley)}
\item Challenge 2: Don't Flip the Fuck Out.  Gauss Pistol 2 (Jaya) $\rightarrow$ Matched
\item Challenge 1: Notice (sound).  Thrown back
\item Challenge 2: Get Javier Under Control.  Trigger Reflex 2 (Jonah) $\rightarrow$ Matched
\item Pool: 6
\end{itemize}


\jumpHeadline{Dead Red Shirts: }

{\parskip=0pt
Carlos

Naveen

Zengada

Morley
}

\jumpHeadline{VP Totals }

{\parskip=0pt
Hayley 2

Jaya 0

Jonah 4
}

\jumpHeadline{Quotes: }

Ion:\hl{``We got taken out by...elevation.''}\footnote{\textbf{Nathaniel Ford }\textless 3 \textsubscript{10/10/14 2:41pm}}\\[4mm]


\quotedDialog{
Suko: ``See we could have gotten everyone up the mountain!  Just take a 5 point Flaw 'Saved by Drake''' 

Rebecca: ``No.  NO.  I'd rather shoot them in the head.''\\[4mm]
}

\quotedDialog{
Rebecca: ``Does she feel better?''

\hl{Nate: ``Imagine that there was a great injustice.  A force oppressing many people.  Innocent people dying. And a monsoon of fire washes over it...surrounding it...drowning....collapsing into a perfect waveform of nougat-y goodness...why nougat-y?  fuck it.  Which you then swallow.  And your body just feels like...\textit{Yeah} motherfuckers.  Let's rock.''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{10/10/14 12:25pm}}\\[4mm]
}

\quotedDialog{
Ion: We don't even know if the fog stopped.

Suko: Drake said it did, so it did.

Rebecca: Yeeaaah....there's going to be some re-education camp when we get back home...\\[4mm]
}

\quotedDialog{
Rebecca: Basically we don't have to worry about anything but what's in front of us.

Ion: I think you're misunderstanding the use of red shirts here.  'Keep them back there where it's safe'?

Suko: Well we already lost \hl{three}\footnote{\textbf{Suko T }Actually four at that point but I can't count. \textsubscript{10/10/14 12:32pm}} of them, we don't have many left.

Rebecca: I'm so sad about Morley.\\[4mm]
}

\quotedDialog{
Ion: I will make sure they don't get instantly immolated.

Suko: How are you doing that?

Ion: By keeping back and watching.

Nate: That's science!\\[4mm]
}

\quotedDialog{
Suko: See??  Pistols are comforting.  Rifles are comforting...

Rebecca: Yeah.

Suko: \hl{You understand.  It's a girl thing.}\footnote{\textbf{Nathaniel Ford }Lulz! I didn't hear this. That's awesome. \textsubscript{10/10/14 2:43pm}}
}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:14pm
\end{flushright}

