\setcounter{chapter}{ 34 }
\chapter{\textbf{``SAC-04'', part 3} }


\subChapterTitle{ ``Jaya vs. the Kabuki Zombie''}




\deets{Suko}{Oct 22nd, 2014}



Surprisingly, only one Red Shirt (Das) died this session.  Jaya took on one of the crazy bad guys by herself and beat it into submission...with her face.  Jonah has vision of himself in another place with his sister grown up into a lawyer.  Hayley gets Carruthers in her head as her new Operator.  Hayley and Jaya end up on a rooftop with lots of Red Shirts, facing a horde of zombies.  Jonah is alone inside the SAC-04 facility with just Drake, Douglas and Jayce.  We have successfully split the party, which I imagine will go very well for everyone.



Once again I color coded the Operator/Agent thoughts.

 {\color[RGB]{74,134,232}Jonah to Jaya} 

 {\color[RGB]{255,0,0}Jaya to Jonah} 

 {\color[RGB]{230,145,56}Hayley to Carruthers} 

 {\color[RGB]{153,0,255}Carruthers to Hayley}  {\color[RGB]{153,0,255} } \footnote{\textbf{Suko T }I color coded Carruthers' mental communication purple since green (Oliver), blue (Jonah), red (Jaya), orange (Hayley) were already claimed.  I wanted to make her a less saturated color to represent the connection distance but it was such a pain to read that I switched it to this. \textsubscript{11/02/14 12:01am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Ok, can I just say I love how much thought you put into this? \textless 3 \textsubscript{11/02/14 1:52am}}\footnote{$\rightarrow$\textbf{Suko T }Thanks!  It was this or go slowly insane by typing ``\_\_\_ thought to \_\_\_'' over and over. :) \textsubscript{11/03/14 12:36am}}



\jumpHeadline{The Village}



\textbf{{[}6 Tokens in the pool{]}}

{[}\textit{Challenge 1: Notice.  Thrown back}{]} Jaya, Jonah, Lackovich, Javier, and Breccan hear the scream but can't tell where it's coming from.  It could be coming from where they think Drake's group is, or it could be coming from in front of them... none of them are sure.  The little girl keeps bouncing the ball against the wall.  Javier staggers to one knee and drops his rifle.  He seems unsteady.  Faintly in the distance they hear Hayley yell Jonah's name.



Back with Drake's group and the VIPs, Hayley hears the scream and cries out ``Jonah!'' sounding panicky.   She stops walking and her voice is shaky as she stammers into her Hush Radio to Jonah and Jaya, ``Op-Oper- I mean Agent Parvadi, Operator Gemayel, please.  Please please report in.''

``Confirmed,'' says Jonah.

``What?  What??'' yells Jaya, almost drowning out Jonah.  Hayley's shoulders relax.

``All Squads report in,'' Drake orders over the radio.

``Patrol Group 2 reporting in,'' says Lackovich.  Neither Jaya nor Jonah report in.



There's a pause and then there is the pop-pop of gunfire in the distance.

Over the radio, we hear Rust say, ``We've got trouble.''

Jaya and Jonah take a moment to get their bearings as they realize they don't actually really know where Drake and Rust's teams are, though they can make a good guess.

Jonah turns to Javier, ``Getting it together?''

Javier stutters out, ``Lost.  Carruthers.'' and he grimaces.  His eyes are super dilated.

``Focus,'' says Jonah sternly.

{[}\textit{Challenge 1: Notice.  Agent 1 (Jaya) → Matched}{]}

Jaya feels some weird Jonah-paranoia in the back of her mind, and for some reason it makes her look up.  She sees that the stars in the sky overhead are disappearing.  The sky looks like it is being painted black as a churning darkness draws like a curtain across the sky. \footnote{\textbf{Suko T }The Nothing is coming. \textsubscript{10/23/14 4:43pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }+1 \textsubscript{11/02/14 1:26am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 many times. \textsubscript{11/02/14 1:59am}}

{[}\textit{Refresh: Air of Command 2 (Jaya)}{]}  Jaya freaks out and starts shaking Javier and slapping him (with her flesh hand).  ``Get your shit together!  We gotta get out of here!   Get it together!'' yells Jaya, clearly losing her shit herself. The two squads are in complete disarray.

{[}\textit{Refresh: Small Unit Tactics 3 (Jonah)}{]}  Jonah tries to take control of the situation and gathers up both squads and leads them off. Very decisively.  In the wrong direction.

Lackovich is trying to get her squad together.  She can't really get to Javier as Jaya's in the way, and Breccan's freaking out and keeps saying in a panicky voice, ``Wait!  Did we come from that direction?  Or that one?  Where's that gunfire coming from?'' as she tries to look in 14 different directions at once.

PG1\&2 get a little spread out.

Jaya, helmet-less, feels a noticeable chill in the air.



Meanwhile, Drake has efficiently organized his people into a standard defensive position, staking out the four corners of the intersection, using crossfire to protect each other and the Assets (Douglas and Jayce).  The Assets have been stashed into an alcove.

Drake orders Hayley to cover a corner and then starts to discuss something subvocally over the radio.



\textbf{{[}Darkness Falls is Triggered.  15 tokens enter the Pool.{]}}



``Hayley! What are you seeing?'' asks Jonah over the radio.  Jaya demands that Jonah help boost her up onto the roof.  

``Are you sure that's a good idea?  You'll be a huge target up there,'' says Lackovich.

``Just fucking do it!'' orders Jaya, commandeering Breccan to help boost her up, which Lackovich allows with a grumble.  



Hayley can see flashes of gunfire down the street she's covering.  Hayley \hl{replies to Jonah}\footnote{\textbf{Suko T }she mentions seeing the gunfire and this is a Code Yellow, possibly a Code Red.  She also asks how far away PG1\&2 are. \textsubscript{10/23/14 4:32pm}} but he's distracted by Jaya and ignores/misses her response.



Jaya notices that the roof of the building is very smooth and flat black glass.  As she hoists herself onto the roof, she sees a drop of something wet splatter next to her.  Her first instinct is that it's a huge drop of blood, but it's rain. She looks around and sees a maze of streets stretching out around her. She sees flashes of light and the distant pops of gunfire in between some buildings, some distance away.

{[}\textit{Challenge 2: Keep Her Balance.  Adrenaline Junkie 2 (Jaya) → Matched}{]}  In the other direction she sees a terrifying plunge into nothingness just one building away from her.  Jaya staggers and almost falls at the sight.  The houses in this section abut a very steep, very tall cliff.  There are a few terraces and then nothing but clouds below.  But Jaya's hopped up on adrenaline, ready to take on anything crazy- portals, Octavius, whatevs- so this doesn't faze her for long.



Everything gets noticeably darker as one of the moons disappears behind the Nothing.  Jonah freaks out a little.  Jaya describes (to Jonah) seeing gunfire, the ``giant pit'' and the darkness.  She can't quite describe the location of the gunfire precisely but knows the general direction of it.  {[}\textit{Challenge 1: Notice.  Thrown back}{]}



Hayley watches the gunfire approach and can see Rust's team crisscrossing the street, retreating toward their position.  Four of them, including Rust, are mobile, but the fifth is being dragged by Grabber.  Drake's team reconfigures their positions slightly to cover the incoming squad.  Hayley says quietly over the Hush Radio, ``Agent Parvadi, what is your ETA?''

``Fuck if I know, give me a sec,'' says Jaya.  She yells down to PG1\&2, ``You guys should get the fuck up here.  There's no way we're making it through this maze down there.  Way too complicated.''

{[}\textit{Challenge 1: Notice.  Thrown back}{]}  

``Can we get there on the roofs?'' asks Jonah.

``Get up here and find out!  It's a fucking order!'' Jaya says.

``Got it!'' says Jonah.  He turns his radio off and turns to Lackovich, ``Agent Parvadi wants us to go along the roof.  Truth is, from what she describes, that's the only way we're going to get there because the streets are completely tangled.''

``That's completely illogical,'' says Lackovich, sounding annoyed.

Jaya leans over the edge of the roof and yells, ``Are you questioning my fucking order?''

``You didn't hear that.  \textit{Sir.}`` says Lackovich loudly.

Breccan climbs onto the roof.

{[}\textit{Challenge 1: Notice.  Street Medic 2 (Jonah) → Overcome! }\textit{\textbf{1 VP (Jonah)}}{]}

Jonah can tell that Javier is not going to make it up.  Javier is unsteady and not coordinated enough to climb around on rooftops and jump from building to building.  ``Chief, we have a problem.  Javier is offline and he's not going to be able to do this.''

``Fuck!'' snarls Jaya, letting loose a stream of expletives.

The rain is getting heavier.  For us in the Directorate, this is making us a bit nervous because rain in the Directorate is mildly corrosive and unsafe to drink so usually you get out of the rain as soon as you can.

Up on the roof, Breccan says nervously, ``Uh, Sir, what is that?''

Jaya snaps at Breccan, ``What?  WHAT??''

``THAT,'' says Breccan, pointing with her gun at something behind Jaya.

Jaya doesn't see anything and turns on her flashlight.  On the street below, Lackovich, Jonah and Javier can see Jaya's flashlight sweep across the rooftops.

{[}\textit{Challenge 2: Dodge Shards.  VAC Infantry Light Armor 3 (Jaya) → Overcome! }\textit{\textbf{2 VP (Jaya)}}{]} There's an odd noise, muffled by Jaya's armor's helmet, like the fwip! fwip! sound of a sniper bullet but without the usual pop preceding it.  Something embeds itself in Jaya's armor and she looks down to see a black shard of something sticking out of her armor.  Then one of the shards hits her flashlight and it shatters.  More shards hit her and Jaya can feel the pinprick of one of them as it pierces completely through her armor.  Jaya's helmet indicators start informing her that containment and vacuum have been compromised.  Jaya looks around and sees that Breccan is okay.  Breccan has dropped prone to provide a minimal target to the attacker.



{[}\textit{Challenge 1: Notice.  Small Unit Tactics 1 (Hayley) → Matched}{]}   Rust, Misha, and Arjoon are covering Grabber as he hauls the injured teammate (Das).  One of the soldiers covering Grabber fires at something behind them and in the muzzleflash Hayley sees a dark shape with a reddish face and a strange helmet that seems sort of demonic.  The figure darts across the street and swings something at Grabber and Grabber falls down.



{[}\textit{Refresh: Bodyguard 2 (Hayley)}{]} Hayley broadcasts over the radio general frequency, ``Breaking formation to assist.''  Hayley actually doesn't wait for confirmation before running toward Rust's team, charging straight at where she last saw the figure to try to draw its attention/fire.



{[}\textit{Refresh: Bad Cop 3 (Jaya)}{]} Jaya hears this and curses, ``Fucking Hayley!''  Jaya grabs one of her grenades and chucks it in the general direction of the thing that was shooting at her.



Drake yells at Hayley, ``Agent, get down!''  and someone else on his team yells ``Get out of the line of fire!''  One of Rust's guys starts firing up at the roof.  There's a cha-thunk noise slightly behind Hayley and then an explosion goes off and Hayley is thrown into a wall.



``Who the fuck threw a grenade?'' Drake shouts over the radio.  ``You better be the next person dead or I'm going to fucking KILL YOU.  WHO THREW THAT?''

Rust says over the radio, ``Wasn't my squad!'' and there are negatory responses from Drake's team.  Lackovich reports, ``No idea sir!''  Jaya and Jonah are once again radio-silent.



Jaya ignores Drake as so much background noise and looks around to see if she got anything with the grenade.  The rain is getting increasingly heavy.  {[}\textit{Challenge 1: Notice.  HE Grenade 2 (Jaya) → Overcome! }\textit{\textbf{1 VP (Jaya)}}{]}.  In the flash of the grenade Jaya sees something very strange.  A figure has climbed over the edge of the roof with a red face with deep hollows where eyes would be. \hl{The face seems plastic and mask-like, with a grimace and horns}\footnote{\textbf{Suko T }Like this?
https://www.etsy.com/listing/158402178/hannya-kabuki-mask-airsoft-mask?ref=market \textsubscript{10/27/14 1:53am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }More like this but with black for the eyes:
http://1.bp.blogspot.com/\_vp3tA9fhYl4/SnrUFYZHxXI/AAAAAAAAADY/pggsh2mfc8A/s320/diablada5.jpg \textsubscript{11/02/14 1:05am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Shit, those are some big ass horns... \textsubscript{11/02/14 1:21am}}\footnote{$\rightarrow$\textbf{Suko T }Sweet! \textsubscript{11/02/14 10:22am}}.  The figure's body seems to disappear and reappear or shift color (from black to white and back again).  It is carrying a long black blade of some sort.  In its other hand it has something that looks like a gun (since that's the closest analog she knows of).  It raises the gun and there's that fwip! fwip! noise again and Jaya's armor starts getting shredded.



Jaya charges the figure.  She can track it a bit through her helmet sensors.  It doesn't show up on thermal, but it shows up briefly on some of the other sensor modalities.  Jaya is making sure not to run off the edge of the roof into the pit. The roofs are different heights and it is difficult to run across in the rain.



Jonah turns to Lackovich and says, ``Please keep an eye on Javier, I'm going to go follow Agent Parvadi and see what she's doing.''

``Of course,'' says Lackovich, a little confused.   Jonah leans against the wall and engages Operator.



Hayley reaches Grabber who appears to be hamstrung.  Das is lying on the ground, bleeding severely.  He appears to be missing part of an arm and a leg.  In one hand, Das is clutching a grenade.  {[}\textit{Challenge 1: Notice.  HE Grenade 2 (Hayley) → Overcome! }\textit{\textbf{1 VP (Hayley)}}\textit{{]}}.  The pin is out and the only thing keeping it from exploding is Das' grip on it.  Hayley can tell that if the grenade goes off, it will catch pretty much herself and all of Rust's team.

She turns to Arjoon and points to Grabber.  \hl{``Constable Arjoon, get him out of here,'' she orders.}\footnote{\textbf{Suko T }I think this is the first instance (recorded) of Hayley giving an actual order to someone.  She's passed along orders from other people before but this is all her own. \textsubscript{11/03/14 12:07am}}Once Rust, Misha, Arjoon and Grabber have started clearing out of the immediate blast radius, Hayley grabs the haul loop on the back of Das' uniform and starts following them slowly.  As she drags Das, the grenade falls out of Das' hand. 



Back on the rooftops, Jaya is trying to track the figure.  The grenade flies up in the air and the figure swings at it and bats the grenade toward Breccan.  Breccan is shouting ``Sir!  Sir!  Get down!!''

Jonah, seeing through Jaya's eyes, sees the figure and says aloud, ``What the \textit{Hell}??''  Lackovich responds but he can't hear her.

The figure has stopped running, the ``gun'' it was holding appears to be gone.  It is half circling and dodging.  Jaya pulls out her truncheon in one hand, her sidearm in the other and goes in low, engaging the figure ``street brawler''-style.  The creature goes into a broadsword fighting stance swinging its sword at her, trying to keep its distance from Jaya.

Right in the middle of this, Jaya gets this slightly distracting sense that something weird is happening to someone, somewhere.



Back down on the streets, {[}\textit{Refresh: Athletics 3 (Hayley)}{]} Hayley drops Das and \hl{expertly kicks the grenade up into the air}\footnote{\textbf{Suko T }I should take this as a Skill.  She's getting a surprising amount of practice at it. \textsubscript{10/24/14 2:09am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }''Footballer'' \textsubscript{11/02/14 1:23pm}}+1.  It explodes.  Hayley feels a nauseating sense of intense disorientation like when she first connected to Oliver as Agent-Operator.  Hayley says (or thinks she says), ``Oliver!'' with confused delight.  The world goes funny and she loses all sense of up and down.  

Hayley sees a series of images that repeat somewhat haphazardly although the bar scene comes up the most often.

\textit{...She's in a bar, staring at someone and there's a sense of deep longing, stronger than Hayley has ever felt before.  The other person's identity...she almost knows it but the more she tries to remember, the more it slips away... }

\textit{...She's on a train, a particular train...}

\textit{...She's at a TA constabulary swearing-in ceremony...}

\textit{...a blurry fractured distorted-perspective Picasso-like image of Transit Minor but there are flames everywhere and }\textit{\hl{Legionnaires}}\footnote{\textbf{Nathaniel Ford }The incoming sense was more ``unknown enemy shooting'' but as Hayley perceived it her mind almost seamlessly replaced that with ``Legionnaires shooting''. \textsubscript{11/02/14 1:23pm}}\textit{ are shooting at her.  She has a weird echo-ey alien (to Hayley) feeling of wanting her...mother?...}

\textit{...She sees herself in a hospital bed in SAC-09 Medbay, beat up and unconscious but somehow still incredibly good-looking.  There's an overwhelming sense of sadness and empathy for herself (which Hayley also finds extremely strange and unfamiliar)...}

\textit{...and then she's back in the bar again...}



Jonah is watching Jaya's fight through her eyes.  There is an explosion over his head and he is suddenly somewhere else.  There's a moment of disorientation like he felt back in Terminus at Agent HQ.  Suddenly he is sitting at a table in a room somewhere else.  

Riva is sitting next to him, she's older than he last saw her, and she's wearing a nice, professional suit with a badge.  She looks all grown up, with her hair pulled back and nice makeup.

In front of them on the other side of the table \hl{are two people in suits, a man and a woman}\footnote{\textbf{Rebecca S. }in my mind's eye they are Mulder and Scully \textsubscript{11/02/14 1:39am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Then I did my job well... \textsubscript{11/02/14 1:09am}}.  They both have badges, made of plastic, full of words and pictures, including face-ID photos of the wearer. There are piles of documents on the table, including a folder that's right in front of Jonah with a pen next to it.  

The woman is talking, ``... Dr. Hadef has a tendency to flaunt federal authority in these matters.  If he contacts you or you come across any additional documents from that day, we request that you contact us immediately, per the Patriot Act.  If you sign this court order here as an acknowledgement, that will be all and you will be free to go.''

Jonah slaps himself.  The two people lean back in surprise and Riva asks, concerned, ``Timon?''

The man asks, ``Dr. Natekar?  Are you alright?''

The woman follows up, ``Why did you do that?''

Jonah hears a whistling sound, like he'd been boxed in the ears.  Behind the two people is a huge mirror that takes up the whole wall.  In the mirror Jonah sees himself and Riva (who puts her hand on his shoulder). He looks the same, but cleaner, more tidy, with a nice dress shirt and tie.

Jonah closes his eyes and concentrates really hard on trying to synced up to whatever he was looking at before.

Someone stands up and asks again, ``Are you alright?''  Riva sounds a little alarmed as she says, ``I don't know.  Timon??''

Jonah opens his eyes and the mirror has gone black and through the mirror Jonah can see the following scene....



Jaya is going in low- using her mechanical hand to deal with the sword and her other hand to fire a lot of bullets into its torso.  {[}\textit{Challenge 5: Subdue the creature.  Sidearm 3 (Jaya) +Truncheon 2 (Jaya) + Small Arms 2 (Jonah) + Vigilant 3 (Jonah) + Battle Dress Uniform 2 (Jaya) + }\textit{\textbf{ {\color[RGB]{255,0,0}FLAW 2: Shoulder \& Neck wound (Jaya)} }}\textit{ → Matched}{]}.  The creature slices down with its sword.  Jaya jerks back out of the way but the blade still cuts through part of her helmet and through her armor with disturbing ease.  The tip of the sword slices into her neck, right through her ``loyalty'' tattoo and into her shoulder.  Jaya brings up her cybernetic arm and the blade hits it and shatters into pieces.  



Jonah is watching all this unfold.  Because he's in sync with Jaya, he gets up out of his chair and moves to dodge when she does.  Because he's Vigilant, he occasionally moves before she does and she follows him instead, avoiding grievous harm.

The man asks Riva, ``Is he okay?  What is going on?  I thought he was fit.''

Riva glares at the guy, ``I'm his lawyer, he's \textit{fine}.  Can we just have a minute?''  She looks at Jonah and then turns to the agents, ``I need to speak to my client.  You need to leave.''  When they don't move immediately, she repeats firmly, ``You \textit{have }to leave.''

The whistling is getting louder.



Hayley sees the grenade arc up into the air and it explodes high up in the air.  She hears the sound of something shattering but can't tell what.  The visions keep coming back to the scene in the bar.  Hayley starts hearing a rhythmic noise, faintly.  She sees the vision of herself in the Medbay bed again and is again filled with the feeling of sadness, a feeling of: ``I'm so sorry for you. I can't believe the pain you are going through. \hl{I am willing to end it for you.}\footnote{\textbf{Nathaniel Ford }To clarify this slighty, the particular feeling was a mix of ``This is a terrible thing, I know for certain, and I wouldn't wish it on anyone.'' and ``This is a thing that shouldn't exist and should be stopped.'' and ``I don't want to make a decision for (someone else) but don't want to be a coward for not making a decision.'' All of which resolved into, ``I am willing to end this for you if you give me the barest nod.'' \textsubscript{11/02/14 1:14am}}\footnote{$\rightarrow$\textbf{Suko T }Yay Carruthers! \textsubscript{11/02/14 10:24am}}``  Hayley hears the rhythmic noise again, more loudly, and she's back on the street again.

She has this incredible rush of energy, she feels alert and awake.  She grabs Das by the uniform loop and actually hoists him onto her back and runs down the street with him.  Her pace is weirdly \hl{syncopated}\footnote{\textbf{Nathaniel Ford }Great word! \textsubscript{11/02/14 1:15am}}, following a rhythm that only she seems to hear.



Jonah is still in the room.  The agents leave and Riva turns to him.  ``What is wrong?  We were almost out of here.''

The whistling is getting very loud and the action in the mirror is getting very intense.  The mirror seems to be getting even larger, the black reflective surface slowly overflowing the frame.\footnote{\textbf{Rebecca S. }the way this was described made me happy \textsubscript{11/02/14 1:41am}}

``Why are we here?'' asks Jonah.

Riva is confused and says hesitantly, ``They brought you in for questioning over the ER incident.  T-Timon?  What is going on?''

``That's a good question,'' says Jonah slowly.  ``How long have you been a lawyer?''

Riva takes a step back and says, ``Since you put me through \textit{law school}.''

``Oh good!'' says Jonah and then the whistling gets incredibly loud and he's back in Jaya's head.



The creature facing Jaya goes reeling back.  Jaya looks down at the splattered pools of blood from their combat dance, blood red mixed with the same gooey white shit that leaked out of the Omen.  The creature is very messed up but is trying to get away.

``Chief!  Grab it and come back!'' orders Jonah.

{[}\textit{Challenge 2: Catch the guy.  AMP 3 (Jaya) → Overcome! }\textit{\textbf{1 VP (Jaya) + 1 VP (Jonah)}}{]}  The AMP sends a surge of drugs into Jaya's bloodstream to compensate for her new injuries and Jaya feels awesome.  She lunges at the creature and tackles it from behind before it gets away.   She grapples it and feels the sharp pinpricks of more shards piercing her armor.  

Jonah can tell that Jaya has a gushing head wound that she appears to be ignoring.

\hl{The creature 's head creepily rotates around and faces Jaya.}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{11/02/14 1:42am}}

Jonah lurches back and bumps up against the wall.  Lackovich has her hand on his shoulder and is demanding, ``What the fuck is going on?''

Jonah does not answer and just says over the radio, ``What the \textit{hell} is that thing?''

{[}\textit{Challenge 2: Headbutt the guy into submission.  Heads up Display 4 (Jaya) → Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}

Jaya smashes her helmeted head repeatedly into the creature's face.  The helmet starts protesting the abuse and then it cracks and breaks completely. The body eventually goes limp beneath her.  Jaya eventually finds the button for her radio and broadcasts over the general frequency, ``Unnnnnghhh.... I subdued one of them.  Get your asses over here, right now.''

``Chief, you're going to have to come to us, there's still gunfire.''

``I repeat, get your fucking asses over here, NOW.  That's a fucking order Jonah,'' says Jaya.

Jonah says over the general frequency, ``We have a prisoner.  We think.''

Jonah and Lackovich get ready to join Jaya on the roof.  Javier's a bit out of it but doesn't seem in as much pain as before.

The rain is getting very heavy.



Hayley brings Das to the medics and they try to help him but it's not looking good.  Drake puts a hand on Hayley's shoulder and asks, ``Are you alright?  You went down out there.''

Hayley smiles, \hl{so pleased that he's touching her and the rush of comfort that brings, and also that he seems to care that she was possibly injured.}\footnote{\textbf{Suko T }Because Carruthers has front row seats to the Hayley brain, I'm annotating with Hayley's thoughts and feelings more, especially if it might cause problems later :D  I'll try to keep it to a minimum in game so I don't slow down the session, but will be more explicit in the notes.  Hope you find it entertaining! \textsubscript{11/01/14 11:59pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }+5 \textsubscript{11/02/14 1:43am}} But she doesn't want him to worry so she says earnestly, ``It's happened before.  I should be fine.''

Rust mutters contemptuously, ``Fainting spells.''



{[}\textit{Challenge 1: Notice.  Binoculars 2 (Jaya) → Overcome! }\textit{\textbf{1 VP (Jaya)}}{]}.  Jaya is lying on top of the guy and is all tangled up in her equipment.  She starts detangling herself, removing her binoculars and tossing them aside.  As she does, she hears a sizzle and pop as they start melting as they lie in a puddle of white goo.  The same goo that's splattered all over her armor.  Jaya rolls away and starts stripping off her armor off rapidly, including her sidearm and other weapons.   {[}\textit{Refresh Sidearm 3 (Jaya)}{]}

Breccan comes running up and start trying to help Jaya.

Jaya pushes her away and orders, ``Shoot it some more.''

``Yes Sir!'' says Breccan and starts firing at the creature.

At the sound of gunfire, Drake barks over the radio: ``All squads report!''

Jaya looks over at the creature and the whole thing seems to be melting into the roof.  The head appears to detach and starts inflating and begins to slither off.  {[}\textit{Challenge 2: Don't freak out. Air of Command 2 (Jaya) → Matched}{]}.   Breccan freaks out a bit and Jaya orders her to shoot it more.  We all hear the sound of a gun going full auto.

At the sight of the creature through Jaya's eyes, Jonah freaks out and drops to the ground, yelling ``Get down!''  {[}\textit{Refresh Vigilant 3 (Jonah)}{]}



With the full weight of his authority behind it, Drake orders over the comm, ``ALL SQUADS REPORT IN.  \textit{NOW}''



Jaya tries to grab the creature again, even as wounded as she is.  {[}\textit{Challenge 2: Not fall and crack open her head.  }\textit{\textbf{ {\color[RGB]{255,0,0}Flaw 1: Hit head on the roof (Jaya) } }}\textit{→ Sent back to pool}{]}  Jaya slips and hits her unhelmeted head and the creature slithers off.  The remains of the creature's spiky glass outfit are still in a deflated heap on the rooftop.



Lackovich reports in to Drake eventually.  Jonah, Lackovich and Javier are prone.  Jonah hears Javier say, sounding puzzled/worried, ``The bouncing has gone away.''  Jonah looks up and sees figures approaching along the streets around them.

Jonah takes a deep breath and says over the radio over the general frequency, ``Status report. Agent Parvadi is on the roof and has subdued a hostile.  There are incoming, I don't know if they are hostile but they don't look friendly.''

``Copy that,'' says Drake.  ``Can you hold your position?''

``Tentatively, it depends on how fast they are coming,'' replies Jonah.



\carBrain{Report in.} says Carruthers in Hayley's head.

Hayley is confused at first, looking around for Carruthers and then says softly (but aloud), ``Hello?  Operator Carruthers?''

\carBrain{Agent } says Carruthers.

``Hi!'' says Hayley cheerfully, outloud (albeit quietly).

\carBrain{Hi.  Agent Morgan wants to know what is happening} Carruthers feels much more ``distant'' than Oliver did.  It is harder to ``hear'' her.

Hayley switches to speaking just in her head  \hayleyBrain{Apparently Agent Parvadi has subdued a hostile.  They are being approached by others who do not seem as hostile.  Agent Rust's team has lost one member, Constable Carlos.  Agent Drake's team has lost two members, Constables Naveen and Zengada.  Operator Lackovich has lost one member, Constable Morley.  Constable Das is not doing well and almost dead.  Patrol Groups 1 and 2 are together, but not with me.  I have been requisitioned to Agent Malak's team and assigned to help guard the Assets.  Agent Malak and Agent Rust's teams are nearby, Agent Rust's team just rejoined us.  We are holding our position, looking for enemy combatants and protecting the Assets.} 

Hayley gets the faintest impression of a nod.  \carBrain{Is Javier okay?} 

Hayley frowns a little in thought and Carruthers can tell Hayley's thinking through all the Constables to remember which one is Javier.   \hayleyBrain{I have not seen him, but they haven't reported any injuries to their squad yet.} 

There is no verbal response but a strong sense of disappointment from Carruthers.



The figures are approaching Jonah, Lackovich and Javier's position slowly but steadily.  Jonah turns to Lackovich, ``We should get off the street.''

Lackovich turns to Javier, ``Are you up for it?''

``I guess I have to be,'' says Javier hesitantly. ``I- I can't reach Carruthers.''

``We can't worry about that right now,'' says Lackovich.

``She's fine.  The connection may be \hl{down}\footnote{\textbf{Suko T }Because SAC-09 has been destroyed along with Jonah's family... \textsubscript{10/27/14 3:01am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Ooh! Dark! \textsubscript{11/02/14 2:12am}}\footnote{$\rightarrow$\textbf{Suko T }I feel it's a natural conclusion.  In how many action films does communication between teams get lost because everyone's *fine*? :D  Especially with your note that we've never had a connection get lost randomly/unexpectedly before.  Except when Oliver died. \textsubscript{11/02/14 10:26am}}, but that's them, not us.'' says Jonah.  He can tell that Javier understands what he has to do intellectually but isn't sure he can actually do it.  ``Operator,'' says Jonah, indicating himself. ``That's why I'm telling you what I'm telling you.''  Javier nods.



The rooftop is quite a scene.  Jaya is stripped down to her tank top and skivvies with a bleeding headwound, a deep cut right through her loyalty tattoo on her neck, and various cuts and bruises all over her body.  She's lying on her back next to a puddle of corrosive goo and blood.  There are pieces of armor (mostly broken/damaged/half melted), equipment, shell casings, rope, and weapons strewn all around her.  Rain is drenching everything.  Breccan is still trying to get the release on her weapon to work, cursing as the rain and her shaking hands make it virtually impossible.



Drake points to a building and tells one of his team to secure it and stash Grabber and Das inside.  He orders, ``Rust, on roof.  Now.'' 

Rust nods and takes a running leap at a building and then does a strange spider climb up the wall.  Hayley watches him and notes the new technique with interest.

Drake turns to Hayley and asks, ``Do you want to back him up?''

``Not really,'' says Hayley honestly, ``But I will.''

``Alright, let's go.  Madelyn, you're with me,'' Drake says.  He easily assists Hayley and Madelyn onto the roof and then vaults onto the roof himself.



Lackovich and Jonah struggle to get Javier up on the roof.  Then they haul Lackovich up.  They manage but it's not graceful.  Jonah can see that there are about a dozen figures in the streets, closing in on their position.  Jonah starts heading in Jaya's direction but warns Lackovich and Javier, ``I want you to try to stay calm. What we're about to see is a little...weird.''



Hayley sees Jaya lying down near a puddle of blood and immediately runs straight to her and kneels down next to her.  ``Agent Parvadi?'' she says, sounding alarmed.

``Hayley,'' says Jonah over the radio. Hayley ignores him.  Drake starts sauntering over toward Jaya.

``Fuck.  Is Drake here?'' Jaya asks Hayley, not lifting her head or even opening her eyes.

``Of course I'm here!  This is where the action is.  Or so I hear,'' says Drake loudly.

Hayley is attempting to help Jaya sit up, but Jaya just flops back limply.  Hayley starts examining Jaya's wounds and tries to bandage and clean them with some of her supplies in her medkit.

``Where the fuck is my medic?!?'' Jaya screams from her prone position.

``I see you.  We're on our way,'' says Jonah with a sigh.

Jonah reaches everyone else and reports to Drake, ``Sir, I may be able to summarize what happened here but in the meantime what you need to know is that there are hostiles on the street.  And these roofs are extraordinarily slippery.''

Rust is poking at the body of the creature with his rifle.  Drake orders Rust and Madelyn to check out what Jonah reported and they go to the edge of the roof where Jonah climbed up.

``I don't think they are people,'' Jonah calls out to them.



Jaya's waving off Hayley's first aid attempts with increasing annoyance.  ``No, I need Jonah.  I need drugs....I'm not moving until I GET SOME FUCKING DRUGS!'' she yells as she remains prone.  {[}\textit{Refresh: Air of Command 2 (Jaya)}{]}.  Hayley nods, ``Yes sir,'' stands, and goes to fetch Jonah.  

Carruthers can feel a \hl{complicated rush of feelings from Hayley}\footnote{\textbf{Suko T }reference: her lists \textsubscript{10/30/14 2:01am}} when she sees Jonah but the primary one is strong relief that Jonah does not appear to be injured.  ``I'm so glad you're not hurt!'' she tells Jonah.  ``But Agent Parvadi really needs your medical attention right now.''  Hayley indicates Javier and Lackovich, ``I can help them.  You should go.''

\hl{Jonah looks over at Drake and flicks a glance questioningly at Jaya.  ``Do your work,'' says Drake, giving permission.}\footnote{\textbf{Rebecca S. }\textgreater :-/ \textsubscript{11/02/14 1:48am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Clearly Jaya should just trade Jonah away for Madelyn and have an all girl team PG1 \textsubscript{11/02/14 1:49am}}\footnote{$\rightarrow$\textbf{Suko T }Don't forget to leave a spot for Riva! \textsubscript{11/02/14 10:27am}}  Jonah looks down at Jaya's many wounds and sighs, ``Jesus.''  He starts trying to tend her injuries.

{[}\textit{Reduce Flaw: }\textit{ {\color[RGB]{255,0,0}FLAW 2: Shoulder \& Neck wound (Jaya). } }\textit{\textbf{ {\color[RGB]{255,0,0} } }}\textit{Surgical Field Kit 2 (Jonah)}\textit{ → }\textit{\textbf{ {\color[RGB]{255,0,0}FLAW 1: Shoulder \& Neck wound (Jaya)} }}{]} 

{[}\textit{Reduce Flaw: }\textit{ {\color[RGB]{255,0,0}Flaw 1: Hit head on the roof (Jaya).} }\textit{  Medkit 1 (Jonah) → Flaw 0}{]}

Jonah is worried about the constant rain, ``We need to get her out the rain.  If water gets into the wounds, it's going to be toxic.''



Hayley helps Javier navigate the slippery roof.  She feels really good about helping him.  He seems distracted, not feeling very well.  Hayley asks if he's okay with uncharacteristically sincere concern.  There's a distant wave of relief from Carruthers and a feeling of anxiety/guilt.

This puzzles Hayley so she asks, discreetly,  \hayleyBrain{Did something go wrong?}  {\color[RGB]{255,153,0} } 

\carBrain{Victor says there was a...feedback loop.  Because both of us were there. } 

Hayley gets a image flash of Transit Minor from Carruthers and shakes her head.   \hayleyBrain{Oh.  I don't understand that but I will think about it later. Thank you for the information.}  {\color[RGB]{255,153,0} } 

\carBrain{Morgan is glad the situation is secure. } 

 \hayleyBrain{Should I tell people that I'm talking to you?}  {\color[RGB]{255,153,0} } 

\carBrain{Uh...maybe not Drake.  I mean, I think you should just tell our commanding officer. } 



Jonah finishes bandaging up Jaya and repeats, ``We need to get out of this rain.''

``Yeah,'' agrees Drake.  ``A shame though.  Been a while since I've had a shower this good.''

Jaya start gathering up her shoes and weapons.

Jonah points to the white goo, ``Also, this is highly acidic.''  Jonah takes samples of the white goo.  He takes a while to gather it up, being very careful not to touch it {[}\textit{Refresh: Forensics 2 (Jonah)}{]}

Drake is listening to his radio, and says ``Got it, Rust.''  He addresses everyone, ``Okay we need to move.''  He turns to Jaya, all bandaged up and still in her skivvies and says scornfully, ``If you're done being naked, you ready to move?  Agent?''



Hayley makes sure Javier is stable and not in danger of falling off the roof and goes over to Jaya who is staring at her pile of heavily damaged armor.  Carruthers feels Hayley run through a very quick assessment of Jaya's armor, then a note that Jaya is essentially unprotected and Hayley comes to a swift conclusion.  ``Do you want my armor, Sir?'' she offers, already starting to unbuckle her helmet.

``Yes!'' says Jaya.

``Stop,'' says Jonah, too late.  They both ignore him.  ``Let's do this out of the rain,'' pleads Jonah.  They continue to ignore him.

Jaya looks at Hayley with a grin, ``Strip.''  Hayley nods and removes her armor without hesitation.

Jaya starts suiting up in Hayley's armor.  Hayley helps adjust it to fit, and they figure out how to modify it to accommodate Jaya's mechanical arm.  Carruthers cannot feel a single drop of resentment or concern from Hayley over this situation.  In fact Hayley's very content and pleased with this solution because a) she is protecting her team which is a priority b) she is protecting her superior officer which is also a priority and c) she's helping by giving up something of herself.  Hayley seems to find all these things very emotionally rewarding.  

``Chief, you're being an ass,'' says Jonah, sounding disgusted.



Hayley is completely unselfconscious as she moves around in her skintight BDUs that have quickly become completely soaked through by the rain.  Hayley starts rummaging through Jaya's damaged armor to see what parts are salvageable.  The lower torso is mostly okay but the upper torso is not and the helmet is cracked to pieces.  She puts on what she can.  Carruthers can tell that she's far less worried about the lack of sufficient armor than the fact that she's cold and wet and might catch a cold.  But both worries are pretty minor.



Drake starts to say something but when the armor switching starts to happen, he stops, says something over the radio and Rust and Madelyn return. 

Madelyn sees Hayley and wanders over to Lackovich.  Shaking her head, Madelyn murmurs under her breath to Lackovich, ``Luck of the fucking draw.''

Lackovich gives her a look and starts to agree but then snaps briskly, ``Eyes front, Constable.''

And both of them look the other direction pointedly.

Drake just watches the whole thing. Eventually he says over the radio, ``Rust, get the other team moving, we'll catch up.''



Once we're suited up, Drake says to Jaya, ``\hl{Constable}\footnote{\textbf{Suko T }Ooo!  Not even ``Senior Constable''!  he must be piiiiissssed. \textsubscript{10/28/14 5:15pm}}, a moment?''  Jaya nods and they walk over to the edge of the roof.  They stand side by side and gaze into the abyss.

Drake opens with, ``I recognize that Morgan runs things a little....\textit{differently}.  But do you think you can maintain any more discipline than I've seen thus far?''

``I don't see any problem with our discipline,'' says Jaya.  ``We fucking killed a combatant.  What did you do?  Spend some ammo?  Do you have any corpses of your own?  Oh, I'm sorry, did you lose some people?  'Cause my team's all here.''

``Tell that to Morley.''

Jaya says nothing.

Drake continues, ``I recommend keeping your eyes on the prize.  Much as I like going around killing things, that's not why we're here.''

``I was defending my team.  Maybe you should do the same thing when your team is fucking fired on.  You gotta do what it fucking takes!''  Jaya looks a little distracted and then points.  ``By the way, its head ran away down over there.''  She leans forward and peers over the edge.  She sees some terraces below with some tallish skinny grass-like plants growing there.  There are people on the terraces that are starting to move slowly toward our group.

Drake grips the scruff of Jaya's neck and there's the sensation of being pushed forward, but his grip keeps her from falling.  ``You know, I would hate for you to fall off right now,'' he says, almost conversationally.

\hl{``Yeah!  It would really demonstrate your ability to control a situation,'' Jaya says provokingly.}\footnote{\textbf{Rebecca S. }I just want to say I'm quite proud of myself for this.  Normally get tongue tied trying to come up with snarky/snappy retorts (that don't sound dumb) but I was really happy.  Drake just brings out the quality snark! \textsubscript{11/02/14 1:59am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 Actually threw him, too! \textsubscript{11/02/14 1:30am}}+1

Drake sighs in annoyance and says darkly,  ``I sincerely hope you make it out of this mission alive.''

Jaya rolls her eyes, jerks out of his grip, and just walks away.  ``Hayley!  With me,'' she orders and walks to the edge of the roof.

``Yes sir,'' says Hayley.

Jaya looks down and says, ``Oh shit!  What the fuck is this?'' pointing at the horde of zombies.



We climb down from the roof and rejoin the rest of the squads and the Assets.  Unfortunately Das has died.

We manage to maneuver through the zombies.  No shots have been fired yet and it is an uneasy truce for the moment.

Jayce sees Jaya and looks surprised and then sees Hayley and looks away.  Douglas takes note of Hayley's new lack of armor.



Drake stays with Douglas \& Jayce and tells Jaya to take the rearguard.  Which is fine since Jaya has put on a stoic expression but she's hurting.  In many of the intersections we find a bunch of people standing there.   Occasionally one of them will take a step forward.  Drake instructs Rust to find the best path to avoid them.

Not having any immediate orders for her position in the formation, Hayley drops back to where Jaya and Jonah are.  She says quietly to Jaya (not over the radio!).  ``Sir, if there is anything you would like to report to Agent Morgan, please just let me know.  Agent Morgan would like an update.''

``WHAT?'' says Jaya loudly.

``Shhh, I'm not supposed to tell the other Agents,'' says Hayley, worried.

``Who's Operating you?'' whispers Jonah.

``What?'' repeats Jaya in a confused whisper.

``Operator Carruthers,'' says Hayley

``Oh.  That explains it,'' says Jonah.

Jaya has a look of fear in her eyes as she leans away from Hayley and sputters a bit. ``Wait.  Uhhhhhh.  Ffffff.....What?  Uh.....''

\carBrain{Fascinating. } 

 \hayleyBrain{She does that sometimes.}  {\color[RGB]{255,153,0} } 

Jonah tells Jaya, ``You should tell her about what you were fighting. They might know what it is.''

``What the fuck is going on?'' says Jaya.

``Tell Hayley what you were fighting,'' clarifies Jonah.

``Please describe what you saw,'' asks Hayley.  ``I only saw it in flashes and there were other things I saw... I was somewhere else....I think I was in a bar...it was very confusing.''

``\textit{Chief}.  Tell her what you saw,'' repeats Jonah firmly.  ``In case we have to fight them again.''

Drake notices our lagging behind and calls out, ``Hey! What's going back there?  You going to keep up or not?  Agent.''  He practically spits the last word.

``Just completing a report, Sir,'' replies Hayley.

{[}\textit{Challenge 2.  Don't tip off Drake to what we're talking about.  Air of Command 2 (Jaya) → Matched}{]}

``I'm conferring with my fucking team!'' says Jaya with authority.

``Fine, just don't hold us up,'' says Drake.

Hayley glances over at Javier but he seems to be doing much better and is keeping pace with the rest of us.

``\textit{Is Morgan inside your head?}`` Jaya whispers to Hayley, her eyes wide.

``Not that I'm aware of, Sir,'' says Hayley.  \hl{In her head, Carruthers is laughing.  Hayley is startled into laughing a bit too.}\footnote{\textbf{Rebecca S. }No! No! Resist the corrupting influence of Carruthers! \textsubscript{11/02/14 1:02am}}

``Voices in your head, talking to you,'' says Jonah quietly to Jaya.   \jonahBrain{Like this. } ``\textit{Carruthers. } Not Morgan,'' stresses Jonah.

Jaya grumbles, not happy, but she ends up describing the creature in colorful terms, punctuated by many swear words.  She of course frames everything to make herself look great.  She includes the description of the head slithering off. 

Jonah adds that the white stuff is acidic and that the body of the creature melted when she fought it.  He notes that he has some of the white goo.

Jaya turns to Jonah, ``What the FUCK?  Keep that shit away from me.''

``Is there anything else you want to report, Sir?'' Hayley asks Jaya.

\carBrain{Rook wants me to confirm that it is white and slightly corrosive? } 

``Uh, Agent Rook wants me to confirm that it is white and....corrosive?'' asks Hayley uncertainly.

Jonah holds up the jar so Hayley can see it and says, ``it is VERY corrosive.  And animate.''

\carBrain{Please hold on a moment, they are conferring.} 

``Oh and show them these,'' says Jonah and holds up the black jagged things.

``What is that?'' asks Hayley.

``That's what got me there and there...'' Jaya points to the gashes and holes in her former armor.  Hayley makes sure to look at the damage so Carruthers can see it.

\carBrain{Rook says that is probably obsidian and this is strange because that Praetor shouldn't be here.} 

 \hayleyBrain{He is referring to the white stuff or the black things?}  {\color[RGB]{255,153,0} } 

\carBrain{The black things.} 

``Agent Rook says that the black things are probably obsidian. And that it is strange because that Praetor isn't supposed to be here.''

 \hayleyBrain{Does this mean there are two?}  {\color[RGB]{255,153,0} } 

``We are so fucking fucked!!  Do we abort the mission?'' asks Jaya.

\carBrain{I'm not going to ask that question, I'm pretty sure Morgan wants you to do the mission.} 

``Agent Morgan would like us to continue,'' says Hayley.

``Agent Morgan can go-'' Jaya bites back the rest of her sentence with a frustrated noise.

\carBrain{Should I tell Agent Morgan that?} 

\hayleyBrain{\hl{Uh, she didn't finish the sentence, so I don't know what you would tell her.}}\hl{  Hayley feels confused and is reviewing the last few sentences in her head to figure out what she missed.} \footnote{\textbf{Rebecca S. }Once again, Hayley being the best \textsubscript{11/02/14 1:03am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }THE BEST. \textsubscript{11/02/14 1:37am}}

``Ask them how is this other Praetor different?'' says Jonah.

\carBrain{That Praetor is supposed to be at the Canal.  SAC-08.} 

``This one is supposed to be at the Canal.  SAC-08,'' says Hayley.

``No, what is it \textit{like}?  I don't need to know where it is supposed to be,'' says Jonah.

There is some muddled confused mental conversation between Hayley and Carruthers but eventually they straighten out which Praetor they are talking about and what info is needed.

\carBrain{He's uncertain, because based on descriptions of its current activities thus far, it seems idiosyncratic with his experience.  He apologizes that he can't give a better description but he thinks this one is much less...mercantile than he's familiar with.} 

``Agent Rook says this one is behaving...um...idi-'' Hayley fumbles over the unfamiliar word.

\carBrain{idiosyncratic} 

``-idiosyncratic.  I don't know what that word means but maybe you do.  And it is less mercantile than he's...used to?'' Hayley says uncertainly.

\carBrain{would expect} 

``-would expect.'' Hayley repeats firmly.

``\textit{Mercantile}?'' says Jonah incredulously.

``Fucking Rook,'' mutters Jaya, loudly enough to be heard. 

Hayley whispers to Jaya, ``Sir, do recall that they can hear everything that I can hear.''

Jaya turns pale.

\carBrain{I won't tell that to Morgan.  You can tell her that.  She can owe me a favor.} 

Hayley says softly to Jaya, ``Operator Carruthers says she won't report that.''  Jaya breathes a sigh of relief and starts to smile, but Hayley continues, ``And you will owe her a favor.''

Jaya glares.  Hayley feels a wave of anxiety from Carruthers.

``I think you should go man the Assets.  \textit{Now}.'' says Jaya, her tone pleasant but her eyes furious.

Hayley nods briskly and rejoins Drake's Squad.

 \hayleyBrain{I think that went well!}  {\color[RGB]{255,153,0}  } Hayley thinks cheerfully.  Carruthers gets the impression that Hayley's not telling Carruthers so much as patting herself on the back for doing something that didn't appear to end in disaster.

\carBrain{I think you might be wrong.} 

Hayley feels disappointed.  Clearly she missed something somewhere, but she has no idea what.



Drake orders Hayley to join the center of the formation since she is unarmored.  Ignoring the fact that most of his team is unarmored also.

The rain is soaking everything.  We have water in our boots.  We get the feeling that this rain is different somehow.

``Why is there so much rain here? How has everything not been destroyed already by it?'' complains Jonah.

\carBrain{Rook believes that's unlikely, given the Praetor.  Praetors wouldn't allow their SACs to be destroyed.} 

Hayley says quietly over the Hush Radio to Jaya and Jonah, ``Agent Rook is fairly certain this rain won't destroy.  Praetors wouldn't let something like that destroy their.... place?  Area...?  I think?''

``Thank you,'' says Jonah over the radio.

Drake has Rust scout out the best path out to avoid the most number of people.  At one point Rust's group forcibly removes some of the zombies out of our path by throwing them through a window.  






\sceneHeadline{The Cave}

We get to a more open area in front of a cave opening in the side of the mountain.  It appears to be the highest point in the area.  In front of the cave is a large, strangely shaped rock.

Jayce and Douglas confer and then Jayce says something to Drake.  Drake says loudly to everyone. ``Alright!  We're going in.  Who wants point?''  He looks at Jaya.

Jaya looks at Jonah.   Hayley looks at Jaya, and starts preparing to head out in front of Jaya.  But Jaya doesn't move.

``No one?  Alright!  Rust, you're up!'' says Drake.

Hayley is confused and looks in greater concern at Jaya, trying to assess if the damage was worse than she thought.  Jaya looks off into the distance and massages her arm.  It appears that she may not have even heard Drake and may not be paying any attention to what is going on. {[}\textit{Refresh: Left Arm 3 (Jaya)}{]}

Jonah says over the radio general frequency, ``Sir, a general question?''

``Go ahead,'' says Drake.

``So far the hostiles...well the one we fought anyway, were not the same as these people on the street.  Would you agree?'' asks Jonah.

``That does seem the situation, Agent,'' says Drake.

Jaya mutters to Jonah, ``He doesn't fucking know.  He didn't manage to do shit.  He doesn't even fucking know what he was shooting at.''

``Thank you, sir,'' says Jonah more loudly, ignoring Jaya.



Over the Hush Radio, Jonah tells Hayley, ``Don't tell Javier about Carruthers.  I think he's disoriented by losing the connection and it will distress him.  Let them tell him when we get back to SAC-09.''

``Okay,'' replies Hayley, uncertainly.  Carruthers can tell that Hayley has almost no idea what Jonah is talking about and doesn't understand why this would distress Javier.  She's agreeing simply out of habit and because she wants to please Jonah and if doing this thing for him would please him, she's happy to do it.



Rust's team gives the all-clear and we head into the cave.   Drake orders PG1\&2 to hold the entrance and says, ``Hayley with me.''

Drake's team heads to the back of the cave with Douglas and Jayce.  There is a circular door there.  It's a smaller door than the one we saw lower on the mountain but there is a panel next to it and Douglas starts messing around with it.  After a while, the door rolls open.  Inside there is a very small room and on the far side of that there is another door.

Jayce and Douglas confer for a while and Drake gets impatient.  ``Alright, what is it?''

``Uh, he says this is basically an airlock.  But there's a security system in place and it's currently in some kind of lockdown mode.  Which means we only have a limited amount of time to turn off the security system before extreme measures are taken.  The difficulty is that it has sensors so probably only four people can go in.''

``Not a problem!'' says Drake.  He points to Jayce and Douglas.  ``You. Tall guy.  Me.''  He looks around.  ``And....Rust''

``Me,'' says Jaya at the same moment, stepping up.  ``I believe the two senior people should look out for the rest of us.''

Drake looks at her and drawls, ``Funny, I would have expected you to want to have command of the top.''

Jaya ignores Drake.  ``How certain are you that we will get in?'' Jaya asks Douglas.  Jayce interprets for her and Douglas signs back.

``Uh, getting in is easy,'' says Jayce.  ``Turning off the security system may be harder.  He's not sure of the exact layout inside.  If he can get to a command panel it should be fine.''

``So he knows how to turn it off if we can get him there?'' asks Jonah.

``Let's say 'yes','' says Jayce.  ``I mean...'no' is a  loose word, right?  He can do it.''

``Let's do it then!'' says Jaya.

There's another slow, deliberate exchange.  Jayce adds, ``He says there's something 'biometric'?''

None of us seem to know what he's talking about.

Drake looks at Jaya.  ``You're already injured.  We may need to move fast.  Make quick decisions.  Good ones.  Sure you're the right one?''

Jaya realizes with regret that she shouldn't have taken Hayley's armor since she would totally send Hayley if she hadn't.

Jaya says to Drake, ``How many SACs have \textit{you} investigated?''  She waves Jonah over. ``Jonah, you take point. Make your team proud.''

She turns back to Drake, ``You've never been in a SAC, you need someone with experience and you probably will need a medic.  So I'm sending Jonah.''  She then tries to whisper/gesture to Jonah to keep her updated via the mental link.  Jonah sighs and tells her she could just ask that over the link and she frowns at him.

``Very well,'' says Drake, ignoring their gesturing and whispering.  ``Rust, you have command.''

{[}\textit{Refresh: Air of Command 2 (Jaya)}{]} Jaya turns to Hayley in confusion and says in a loud whisper (that everyone can hear in the echoing cave), ``Can he \textit{do} that??''

Everyone turns and looks at her.  Hayley looks appalled.

Jayce laughs a little too heartily and says, ``Ha ha HA!  You're hilarious.  \textit{Everyone }knows how chain of command works.'' and he pulls Jaya aside.

\hl{Jayce leans close and whispers, ``Just to be clear...I'm going down there with a psychopath, some guy who doesn't speak our language and... Jonah.''}\footnote{\textbf{Suko T }\textless 3.  Though I love the whole hilariously ill-timed conversation, I really love this opening line. \textsubscript{11/02/14 12:06am}}

Jaya pats him on the back.  ``I tried to help you out.  Good luck.''

``Alright, well just because I have a bad feeling about this...\hl{I just feel}\footnote{\textbf{Suko T }Just guessing here, what he actually said that alarmed Jaya was unintelligible through the snickering.  Please amend if you know what was said. \textsubscript{10/29/14 5:41pm}}...''

Jaya leans back and says loudly, ``Protect the medic.''

``I- I just gotta know...'' stammers Jayce.

Jaya looks around to see who is watching, a couple of people are glancing their way but most people are doing other things.  Jonah orders Hayley to give him her Medkit, and she loses track of the rest of Jaya and Jayce' conversation.

``You're right, this is probably a stupid conversation to have right now, right?'' Jayce whispers apologetically to Jaya.

Jaya pats him firmly on the back again and kinda pushes him away at the same time.  ``Just stick close to the medic.''

``OK ok, I get it. It's cool,'' says Jayce.

``You'll be fine,'' says Jaya bracingly.




\sceneHeadline{SAC-04}

Jonah, Drake, Jayce and Douglas step into the airlock.  Drake and Douglas are looking straight ahead.  Jayce is looking back with a concerned look.  He and Jaya actually make eye contact.  Jaya salutes Jayce as the door closes behind him.

``You have so much to look forward to when you get back,'' says Jonah in a quiet aside to Jayce.

``Yeah, I don't know what the fuck is wrong with me,'' Jayce whispers back as he turns back around to face front.



\textbf{\hl{{[}Let the Right One In is Triggered.  30 tokens enter the Pool.{]}}}\footnote{\textbf{Rebecca S. }soooooooo fuck.
we are so fucked \textsubscript{11/02/14 1:10am}}\footnote{$\rightarrow$\textbf{Suko T }I'd also like to note that those of us on the rooftop have no medic (since Drake and Rust's medics are back in the Cave with Rust) and Jonah took Hayley's Medkit.  But I'm sure we'll be fine.... \textsubscript{11/03/14 12:31am}}




\sceneHeadline{The Killing }\footnote{\textbf{Nathaniel Ford }To stay in-theme, which is to say 'Horror Film', this should probably be ``The Killing Fields'' \textsubscript{11/02/14 1:57am}}\footnote{$\rightarrow$\textbf{Suko T }Done! \textsubscript{11/02/14 10:30am}}\textbf{Fields}

Once the door closes behind the boys, Jaya turns and says, ``Hayley, to me.''

``Eyes up!'' says Rust.  We can see a mass of people starting to move forward toward the cave.

Jaya gives a nod to Hayley, Breccan, and Lackovich (forgetting momentarily about Javier) and indicates that we should stand so the redshirts are between us and the horde of zombies.

``I think we still have time,'' he points to Jaya and then points to a building outside and orders,  ``Take your team, occupy the top of that building.  You should have good fire suppression from up there.  GO.''

``We're not going fire on them!  That's just going to fucking enrage them,'' protests Jaya.

Rust spits something disgusting on the floor.  ``I didn't say fire on them.  You fire when I give you the order to fire.  \textit{Agent.}''

Hayley is already heading out and making sure Javier is able to keep up with everyone.

Jaya sighs and looks at Hayley's boobs, which have no armor protection, and says to Rust, ``You're right, Hayley can't handle close combat.  Let's go.''  She laughs and says to Hayley with a conspiratorial smirk and a glance down at Hayley's chest, \hl{``Gotta protect the 'assets'.''}\footnote{\textbf{Suko T }HA!  So good. Even better that Carruthers sees this whole exchange too. \textsubscript{11/02/14 12:07am}}

{[}\textit{Challenge 2.  Get to the rooftop before it gets overrun by zombies.  Air of Command 2 (Jaya) → Matched}{]}

We climb up onto the building and it seems like a large portion of the people sense us and start turning in our direction.  It's still raining.  It's miserable.




\sceneHeadline{SAC-04}

The door opens.  There is a hallway ahead of them that seems to curve to the right.  Douglas signs something to Jayce and Jayce says, ``Douglas wants to know if he should take point?''

Douglas slowly unsheathes his katana.

Drake says, ``Let's do this!'' and takes point.




\sceneHeadline{The Killing Fields}

The people slowly start approaching.  About 2/3rds of them seem to cluster around our building, while the remaining ⅓rd heads to the cave.  

Jaya is bitching about Drake to Hayley.  Hayley is trying to tune it out a bit as she scans the area and evaluates its defensiveness.  Mostly she learns that this building is crap for defense.  There are no chokepoints, no alternative exit routes.  Pretty much all it has is advantage of ground.  She's not seeing any ranged weapons in the approaching horde so that's good.

\hl{Hayley sets about coordinating a defense with PG2, giving quiet instructions to Breccan, Javier and Lackovich, if they need it, for optimal defense}\footnote{\textbf{Rebecca S. }she should pick Air of Command as a skill \textsubscript{11/02/14 1:14am}}.  Stuff like laying out their ammo so it's at hand for fastest loading, positioning themselves for maximal coverage of the streets below while presenting minimal targets, and agreed upon signals to allow us to stagger our shooting during reloads and to take breaks.




\sceneHeadline{\hl{SAC-04}}\footnote{\textbf{Nathaniel Ford }Somewhere in here Jonah picked up that Douglas may understand their language. Wanted to note it for posterity. \textsubscript{11/02/14 2:50pm}}

The corridor is curved and slopes downward.  It is less curved than the spiraling corridors of SAC-01.  Jonah notes there are tracks in the floor.  Presumably there is some mechanism for hauling things up from lower levels.  They walk for a while.  They reach a large room with branching corridors off it with sealed doors.

{[}\textit{Challenge 2: Notice.  Vigilant 3 (Jonah) → Overcome! }\textit{\textbf{2 VP (Jonah)}}{]}  This place is quiet but not deathly quiet.  Jonah gets a sense that something is tracking us.  Things may be shifting when he looks away from them.  There is a sense that some\textit{thing} is watching them.

``Be advised that I believe we are being monitored,'' says Jonah.

Douglas points to a door with his katana and Drake opens it.  Behind it is a long corridor.  There are words written on the corridor walls saying, ``TESCO''.  Underneath that it says ``Operation Executive, Terran Educational, Scientific and Cultural Organization''\footnote{\textbf{Rebecca S. }OMG
Such plot reveal! \textsubscript{11/02/14 1:15am}}

In the corridor there are various doors with lights above them in red, green, and blue. Douglas points toward the end of the hallway.  Drake has his gun ready and heads down toward that door.

As Drake passes the threshold of this door, Jonah gets a sense that something has changed.

``I think it knows we're here,'' says Jonah.




\sceneHeadline{The Killing Fields}

At that moment, outside, the 100 or so vacant-looking people out in the square suddenly pick someone from PG1, PG2 or the folks in the Cave and focus on them suddenly.



\hl{Jaya smiles.}\footnote{\textbf{Nathaniel Ford }Such an important cinematic note! Still sends chills up my spine. \textsubscript{11/02/14 1:49am}}



There is a surge in the massed horde toward the building.  Hayley notes that some of the group is rushing the Cave but her focus is on protecting her people here.

The attackers aren't mindless, they are helping throw each other up onto the roof and climbing up to get at us.

{[}\textit{Challenge 4. Kill as many people near us as possible without completely compromising the safety of our position.  Sidearm 3 (Jaya) + Snap Reflexes 2 (Hayley) + Bodyguard 2 (Hayley) → Matched}{]}  Jaya pulls out a grenade and goes to drop it on the zombies right below her.  Hayley notices this and realizes that this would just create a pile of dead bodies that would provide a ramp right up to their position.  Before Jaya can even let go of the grenade, Hayley yells at Jaya, ``No! Further!''  Jaya's so surprised, she does as Hayley instructs.  There's an explosion, knocking some of the people back away from the building and \hl{Jaya starts unloading on the crowd, laughing as she does.}\footnote{\textbf{Rebecca S. }It just feels so good when what you're shooting at STAYS DOWN ONCE SHOT.  The relief just makes you giddy. And giggly. And the laughter just flows from there.... and being more powerful than everyone else... and winning \textsubscript{11/02/14 1:32am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Wait for it... \textsubscript{11/02/14 1:50am}}+1  She mows down the people nearest to us, especially the ones that were looking at her.  The crowd is mixed: adults, elderly people, small children.  We shoot them all.

{[}\textit{Challenge 3.  Don't hesitate in killing civilians.  Bad Cop 3 (Jaya) → Matched}{]}

Hayley starts firing with Jaya, being slightly more selective in picking off targets.  Carruthers assists Hayley when she can but they do have some moments of conflict.  Most particularly when Hayley calmly shoots small children in the head as easily as she drops adults.  No emotional distress, no thought of prioritizing adults as targets over children.  Just a dispassionate calculation of how far the enemy combatant could get before they make the situation worse, and then she kills them precisely before they reached that point.  No matter who or what they were.  Carruthers may not be certain Hayley even recognized them as children, beyond compensating for their shorter stature and smaller torso (thus making headshots more viable than through the heart) when aiming them.

Hayley \hl{feels a growing sense of nausea that distresses her}\footnote{\textbf{Suko T }Carruthers is Hayley's compassion module upgrade \textsubscript{11/01/14 11:46pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }I feel like our asset is being compromised \textsubscript{11/02/14 1:17am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Upgrades always increase security attack vectors. \textsubscript{11/02/14 1:52am}} until she realizes it's not coming from her and then she tries to ignore it.




\sceneHeadline{SAC-04}

They enter the corridor and the moment the last person (Jayce) steps into the corridor, the door rolls shuts behind them.

``Yeah, it knows we're here.  This is the timer that Douglas was talking about,'' says Jonah.

They pick up their pace and pass by a glass wall in the corridor.  Through it they can see what looks like a lab.  There is a slight dusty film over the glass and there are some desiccated, almost mummified bodies leaning against the wall.  The lights in the room bathe everything in lurid red light.  \hl{One of the bodies has its hand resting on the glass.}\footnote{\textbf{Rebecca S. }I feel compelled to watch the first Resident Evil film again \textsubscript{11/02/14 1:17am}}

They pass by another room with a red light over the door and they see a bunch of tall cylinders filled with a grey substance.  They don't look familiar.

This is a long corridor.

At the next room, Drake brings his gun up and then steps slowly to one side.   ``So Operator, what do you think of that one?'' he asks Jonah.

\hl{Inside are several Tanks, similar to the ones in SAC-09 and SAC-01}\footnote{\textbf{Rebecca S. }wait. wait. wait
So... I was thinking about this.
Remember in SAC-01 that lady got out of the tank? And then tried to kill us?  And than Jaya (and Oliver) subdued her?
DID WE BRING ANOTHER PRAETOR BACK TO SAC-09 BY ACCIDENT??!
WHAT DOES ROOK THINK!?
IS THERE A ROOM FULL OF ROOKS IN TANKS SOMEWHERE IN SAC-09?!?!

THE PEOPLE DEMAND ANSWERS! \textsubscript{11/02/14 1:19am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }The ``People'' have been awfully quiet about getting answers. Just saying... \textsubscript{11/02/14 2:04am}}\footnote{$\rightarrow$\textbf{Suko T }Our policy of ``beat senseless first, ask questions at some point much much later'' is really starting to bite us in the ass I think.  At least we did finally ask who our Praetor is!  At this rate we'll know answers to this particular situation in about three years.

It would be awesome if the lady (the one Victor has a crush on!) is the SAC-01 Praetor, although didn't they say that SAC-01's Praetor was removed? \textsubscript{11/02/14 10:40am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Without saying anything about the nature of Naked Chick, it was stated that SAC-01 had no Praetor, though of course no one asked why. ;-) \textsubscript{11/02/14 1:16pm}}.  There four tanks.  One is empty.  In two of them there are bodies, strange bodies that are oddly bloated and weirdly long with horned masks for heads.  The fourth one has just a head, bobbing, but Jonah can see a body slowly starting to regenerate below it. The tanks are filled with a milky white fluid. 

\hl{``Yeah... I think we've met him,'' says Jonah.}\footnote{\textbf{Rebecca S. }High five for an excellent closing line \textsubscript{11/02/14 1:20am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{11/02/14 2:03am}}



\textbf{{[}28 Tokens remain{]}}




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 6
\item Challenge 1: Notice.  Thrown back
\item Challenge 1: Notice.  Agent 1 (Jaya) → Matched
\item Refresh: Air of Command 2 (Jaya)
\item Refresh: Small Unit Tactics 3 (Jonah)
\item Pool: 7 + 15 (Darkness Falls)
\item Challenge 2: Keep Her Balance.  Adrenaline Junkie 2 (Jaya) → Matched
\item Challenge 1: Notice.  Thrown back
\item Challenge 1: Notice.  Thrown back
\item Challenge 1: Notice.  Street Medic 2 (Jonah) → Overcome! \textbf{1 VP (Jonah)}
\item Challenge 2: Dodge Shards.  VAC Infantry Light Armor 3 (Jaya) → Overcome! \textbf{2 VP (Jaya)}
\item Challenge 1: Notice.  Small Unit Tactics 1 (Hayley) → Matched
\item Refresh: Bodyguard 2 (Hayley)
\item Refresh: Bad Cop 3 (Jaya)
\item Challenge 1: Notice.  HE Grenade 2 (Jaya) → Overcome! \textbf{1 VP (Jaya)}
\item Challenge 1: Notice.  HE Grenade 2 (Hayley) → Overcome! \textbf{1 VP (Hayley)}
\item Refresh: Athletics 3 (Hayley)
\item Challenge 5: Subdue the guy.  Sidearm 3 (Jaya) +Truncheon 2 (Jaya) + Small Arms 2 (Jonah) + Vigilant 3 (Jonah) + Battle Dress Uniform 2 (Jaya) + FLAW 2: Shoulder \& Neck wound (Jaya) → Matched
\item Challenge 2: Catch the guy.  AMP 3 (Jaya) → Overcome! \textbf{1 VP (Jaya) + } \textbf{1 VP (Jonah)}
\item Challenge 2: Headbutt the guy into submission.  Heads up Display 4 (Jaya) → Overcome! \textbf{2 VP (Jaya)}
\item Challenge 1: Notice.  Binoculars 2 (Jaya) → Overcome! \textbf{1 VP (Jaya)}
\item Refresh Sidearm 3 (Jaya)
\item Challenge 2: Don't freak out. Air of Command 2 (Jaya) → Matched
\item Refresh Vigilant 3 (Jonah)
\item Challenge 2: Not fall and crack open her head.  Flaw 1: Hit head on the roof (Jaya)\textbf{ }→ Sent back to pool
\item Refresh: Air of Command 2 (Jaya)
\item Reduce Flaw: FLAW 2: Shoulder \& Neck wound (Jaya). {\color[RGB]{255,0,0}  } Surgical Field Kit 2 (Jonah) → \textbf{ {\color[RGB]{255,0,0}FLAW 1: Shoulder \& Neck wound (Jaya)} }
\item Reduce Flaw: Flaw 1: Hit head on the roof (Jaya).  Medkit 1 (Jonah) → Flaw 0
\item Refresh: Forensics 2 (Jonah)
\item Challenge 2.  Don't tip off Drake to what we're talking about.  Air of Command 2 (Jaya) → Matched
\item Refresh: Left Arm 3 (Jaya)
\item Refresh: Air of Command 2 (Jaya)
\item Pool: 9 + 30 (Let the Right One In)
\item Challenge 2.  Get to the rooftop before it gets overrun by zombies.  Air of Command 2 (Jaya) → Matched
\item Challenge 2: Notice.  Vigilant 3 (Jonah) → Overcome! \textbf{2 VP (Jonah)}
\item Challenge 4. Kill as many people near us as possible \textit{without} completely compromising the safety of our position.  Sidearm 3 (Jaya) + Snap Reflexes 2 (Hayley) + Bodyguard 2 (Hayley) → Matched
\item Challenge 3.  Don't hesitate in killing civilians.  Bad Cop 3 (Jaya) → Matched
\item Pool 28
\end{itemize}




\jumpHeadline{UPDATED Gear }

\textit{Jaya}

{\parskip=0pt
Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3 (from Hayley)

AMP 3

Hush Radio 1

Gauss Pistol 2

\sout{ HE Grenades 2 }

\sout{ Binoculars 2 }

Heads-up Display 4

Letter of Marque 2

Forensics Bag 1
}


\textit{Jonah}

{\parskip=0pt
Battle Dress Uniform 2

Vacuum-sealed Infantry Light Combat Armor 3

Field Surgical Kit 2

Medkit 1

MedKit 1 (Hayley's)

HESP Radio 2

Gauss Pistol 2

HE Grenades 2

Electronic Bypass Kit 3

Heads-up Display 4

Operator Integration 2

Forensics Bag 1
}


\textit{Hayley}

{\parskip=0pt
Battle Dress Uniform 2

\sout{ Vacuum-sealed Infantry Light Combat Armor 0 } (Jaya's messed up armor)

\sout{ MedKit 1 }

Hush Radio 1

Heavy Pulse Rifle 3

HE Grenades 2

Binoculars 2

Heads-up Display 4
}

\jumpHeadline{THE CARDS }

The Omen- Green (triggered)

Children of the Corn- Green (triggered)

Darkness Falls- Yellow (triggered)

Poltergeist- Red

Let the Right One In- Red (triggered)

Misery- Orange


\jumpHeadline{Flaws left at end of session }

\textbf{ {\color[RGB]{255,0,0}FLAW 1: Shoulder \& Neck wound (Jaya)} }


\jumpHeadline{Dead Red Shirts }

{\parskip=0pt
Rust's team: Carlos, Das

Drake's team: Naveen, Zengada

PG2: Morley
}

\jumpHeadline{Live Red Shirts }

{\parskip=0pt
Rust's team: Grabber, Misha, Arjoon

Drake's team: Takashiri, Madelyn, Pipes 

PG2: Breccan
}

\jumpHeadline{VP Totals }

{\parskip=0pt
Hayley 1

Jaya \hl{7}\footnote{\textbf{Suko T }Woo hoo!!!  High five! \textsubscript{10/23/14 5:59pm}}

Jonah 4
}

\jumpHeadline{Quotes: }

I pull out my gun and shoot the Darkness.
\extraIndent{Rebecca}

\quotedDialog{
Nate: For Hayley, dead people rank lower than ugly people

Suko: Only sometimes.\\[4mm]
}

\quotedDialog{
Hayley: I think that went well!

Carruthers: I think you might be wrong.
}


Question is, would I send in Hayley?  I just took all her armor...
\extraIndent{Rebecca}

\quotedDialog{
Rebecca (to Ion): Good thing you brought your sister into the base, now you can just roll up her character when you die.

Ion: All I can say is that if I go down, I'm going to blast everything he actually thinks about Jaya into her psyche.

Rebecca: No no no...

Suko: It's okay- it'll just be a really bad trip..Jaya will take some drugs and it'll be..

Rebecca: ...It'll be over.

Ion (to Suko): That's not how it works.  \textit{You} lost an Operator.  You know what it's like.

Suko: But Hayley be \textit{crazy}.

Ion: So will Jaya be when we're done with this. \\[4mm]
}


Rebecca: We just put all the boys in the meatgrinder.






\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: The Nothing is coming. because:GivenExpectedThe sky looks like it is being painted black as a churning darkness draws like a curtain across the sky.The sky looks like it is being painted black with a churning darkness drawing like a curtain across the sky.

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }"Footballer" \textsubscript{11/02/14 1:23pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:31am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{11/02/14 2:03am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:27am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/03/14 12:07am}}\footnote{$\rightarrow$\textbf{Rebecca S. }+1 \textsubscript{11/02/14 1:26am}} 

	Unable to highlight for footnote: the way this was described made me happy because:GivenExpectedThe mirror seems to be getting even larger, the black reflective surface slowly overflowing the frame.The mirror seems to be getting even larger.

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 Actually threw him, too! \textsubscript{11/02/14 1:30am}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:31am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{11/02/14 2:03am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:27am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/03/14 12:07am}}\footnote{$\rightarrow$\textbf{Rebecca S. }+1 \textsubscript{11/02/14 1:26am}} 

	Unable to highlight for footnote: To stay in-theme, which is to say 'Horror Film', this should probably be "The Killing Fields", unable to correctly match (exceeded acceptable limit):ExpectedThe Killing Zone

	Unable to highlight for footnote: OMG
Such plot reveal!, unable to correctly match (exceeded acceptable limit):Expected“Operation Executive, Terran Education Science Culture Organization”

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }Wait for it... \textsubscript{11/02/14 1:50am}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:31am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{11/02/14 2:03am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/02/14 10:27am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/03/14 12:07am}}\footnote{$\rightarrow$\textbf{Rebecca S. }+1 \textsubscript{11/02/14 1:26am}} 


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:24pm
\end{flushright}

