\setcounter{chapter}{ 35 }
\chapter{\textbf{``SAC-04'', part 4} }


\subChapterTitle{ ``Code Gold''}

\deets{Suko}{Nov 12th, 2014}



Drake becomes Praetor of SAC-04 (but Jaya and Hayley don't know that yet).  Jonah learns how to turn the Operator/Agent connection on and off.  Douglas is reunited with his friend from SAC-01 and Victor gets a kiss from a gorgeous redhead.  Morgan gives Jaya a special mission involving gruel and politeness.  Hayley still doesn't get any real sleep, but she gets an awkward hug from Carruthers and forgiveness from Douglas, so she's ok.  There is a Code Gold initiated. Jonah is prepped to become Signe's Operator.



Once again I color coded the Operator/Agent thoughts.

\jonahBrain{Jonah to Jaya} 

\jayaBrain{Jaya to Jonah} 

\hayleyBrain{Hayley to Carruthers} 

\carBrain{Carruthers to Hayley} 


\jumpHeadline{SAC-04}



\textbf{{[}28 Tokens in the pool{]}}


Jonah is still looking into the glassed in room with the tanks.  There is some writing in one corner that he can't read.  He asks Jayce to ask Douglas if he can read what it says.  Douglas is looking down the corridor and Drake is looking in multiple directions at once (but in a manly way).  Seeing them being so vigilant and on alert, Jonah relaxes, feeling like someone finally has his back for the first time. Jayce catches Douglas' attention and Douglas signs back, somewhat offhand.



Jayce says, ``He says it says Lab One?  He doesn't seem to think it's important.''  He gestures at Douglas, ``He basically says that we shouldn't dick around.''




\sceneHeadline{The Killing Fields}

Hayley tries to shoot as many of the people approaching the cave as she can before the angles make it unsafe.  Not having a sniper rifle, she aims for center of mass.

Jaya screams, ``Shoot the motherfuckers!  Shoot them in the damn head!'' and she fires until her magazine is emptied.  {[}\textit{Refresh: Sidearm 3 (Jaya)}{]}

{[}\textit{Challenge 2: Notice.  Nose for Breadcrumbs 2 (Hayley) → Matched}{]}

{[}\textit{Challenge 1: Notice. Agent 1 (Hayley) → Matched}{]}  As Hayley shoots them, she notes that they appear to be operating in groups of roughly 10 and they are organized around a single person.  Additionally, two tiles have dropped down and from one of them something shiny, black and vaguely circular is emerging.

The zombies start swarming the building.  {[}\textit{Challenge 4: Stop the zombies from getting up the building.  Left hand 3 (Jaya) + Vacuum-sealed Armor 3 (Jaya) → Matched}{]}  Jaya goes to town and starts tossing people off the building (not her team).  She tears off limbs and breaks bones.  The sprays of red arterial blood, showers of bone fragments and gobs of flesh coat her in a layer of horrifying awesome.  From Jaya to Jonah there is a sense of intense joy.  She cackles with glee and is grinning madly as she digs her fingers into eyesockets and rips out eyeballs or crushes them.  Lackovich, Breccan and Javier are taken a bit aback {[}\textit{Refresh: Bad Cop 3 (Jaya)}{]}.  Hayley isn't bothered by this quite so much but she gets an increasing sense of nausea from Carruthers until she's overcome with a sensation of vomiting that is hard to ignore.



The people attacking look like civilians.  Other than their milky white eyes they look just like any other mob of people.  Hayley is unable to pass along the information she noticed earlier as she is trying to control her reaction to Carruther's nausea and she loses track of the immediate situation {[}\textit{Refresh: Bodyguard 2 (Hayley)}{]}




\sceneHeadline{SAC-04}

Jonah gets distracted by the white goo in the tanks {[}\textit{Refresh: Vigilant 3 (Jonah)}{]}.  Jonah eventually realizes that the others are agreeing that they need move now.  Drake says loudly, ``Soldier!  NOW.''  {[}\textit{Challenge 2: Notice. Trigger Reflex 2 (Jonah) → Matched}{]}  Jonah realizes that the glass of the lab is starting to fog over and his Heads-up Display notes a drop in temperature.

``Something's changing.  Incoming!,'' says Jonah backing away from the glass.

Drake and Jayce go on high alert.  ``Where??''

``This room,'' Jonah pointing.  ``The glass is changing.  Sir, if it's anything like what Agent Parvadi was fighting, \hl{we have to get out of here \textit{now},'' says Jonah. }\footnote{\textbf{Rebecca S. }so helpful! :-/ \textsubscript{11/18/14 7:51am}} 

Drake grunts and then says, ``Douglas, go.''

Douglas lopes down the hallway. They come to a doorway with a panel on it.  Douglas sheaths his sword and starts working on the panel.  The temp in the corridor is continuing to drop.  Back near the door they came in through, a spigot of some kind starts spraying a liquid.  Jonah talks to Jayce about telling Douglas to go faster.  Jayce says he doesn't want to stop Douglas from working on the panel.  Another spigot turns on.  {[}\textit{Refresh: Small Arms 2 (Jonah)}{]}  Jonah shoots at it and the nozzle explodes and a dark liquid starts gushing out.  The liquid puddles but instead of just spreading like a normal liquid it starts climbing the walls.



``Let's blow the door,'' says Jonah.  Drake starts slapping explosives on the door and Jonah tries to figure out how to take some shelter from the explosion.  Jonah asks if Douglas can open Lab One  Douglas stabs his sword through the panel by the lab door.  The panel goes red around it.  Douglas pulls the door open and there's an exchange of air pressure.  The dark liquid is flowing aggressively along the floor toward them.  They rush toward the lab to wait for the door to be blown up.




\sceneHeadline{The Killing Fields}

A bright beam of red light (coming from the shiny round thing in the plaza) sweeps across the roof.  Jaya is happily gouging someone's eyes out and doesn't see it.  Hayley tackles her, yelling, ``Down!''  The beam passes over Jaya and Hayley.  Breccan says ``WTF?'' and topples off of the roof.  Lackovich goes prone.



Jaya jumps down after Breccan, abandoning her post. {[}\textit{Refresh: Air of Command 2 (Jaya)}{]}.  She pulls off the person who has jumped Breccan, but several of the people get ahold of Breccan and are trying to drag her to the plaza.  Jaya briefly considers attempting a tug of war to retrieve her constable, but restrains herself when she realizes she might not get her back in one piece.



{[}\textit{Challenge 4: Kill the zombies holding onto Breccan, but Breccan and Jaya get dragged to the Plaza.  Rifle 2 (Hayley) + Hush Radio 1 (Hayley) + Hush Radio 1 (Jaya) + Heavy Pulse Rifle 3 (Hayley) → Matched}{]}  Hayley starts picking off the zombies hanging onto Breccan.  Through the hush radio she gives clipped orders to Jaya, ``On your right.  Duck now.  Left.''  Jaya actually follows Hayley's orders.  Their coordination manages to keep Jaya and Breccan from being shot.  They shoot all the zombies off of Breccan but she and Jaya have been dragged to the Plaza.



The laser thing starts aiming at Hayley.  {[}\textit{Challenge 2: Dodge.  Athletics 3 (Hayley) →  Overcome! }\textit{\textbf{2 VP (Hayley)}}{]}  Hayley nimbly ducks out of the way.  

{[}\textit{Challenge 1: Notice.  Bodyguard 2 (Hayley) →  Overcome! }\textit{\textbf{1 VP (Hayley)}}{]}  It is a very slight shift now, but Hayley notices that the roof that they are on is beginning to slide and collapse.  The laser has sliced all the way through the building.



Jaya shoots at the laser thing and her gauss pistol does crack the casing a bit, but it's not breaking it entirely.  If she had a bit of time she could probably destroy it but once she started firing at it, it turns and aims at her. {[}\textit{Challenge 2. Dodge.   }\textit{\textbf{ {\color[RGB]{255,0,0}Flaw 1: Cauterized abdomen wound (Jaya)} }}\hl{\textit{.  Thrown back}{]}}\footnote{\textbf{Rebecca S. }Question for Nate: more details on where this wound was? It was repaired before the session ended so no lasting damage, right?  No impedance to baby making parts, right? Right??? \textsubscript{11/18/14 8:59am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }As Swan indicated, he'll let Gerhauser make the medical report... \textsubscript{11/18/14 9:59am}}  The laser fires a pulse that perfectly pierces Jaya's abdomen.  It's incredibly painful but doesn't bleed as much as Jaya would have expected.  She stumbles back and hands grab onto her and start dragging her across the Plaza.  The pain momentarily overtakes her and her arm starts going on the fritz, flailing around uselessly. {[}\textit{Refresh: Left Arm 3 (Jaya)}{]}




\sceneHeadline{SAC-04}

Jonah and Douglas enter the lab and run smack into a figure there, dripping in white goo, brandishing a black blade.  Two tanks are open and empty.  Douglas exclaims something that sounds like his equivalent of ``Oh shit!!'' and engages with the figure.  Drake yells, ``Ten seconds!''  The figure has some cloaking effect and is getting hard to see/track.



Jonah looks around for the second creature.  {[}\textit{Challenge 1: Notice.  Grace Under Fire 1 (Jonah) → Matched}{]}  He sees it disappearing into a hatch leading to another room.  Jonah tosses a grenade after it.  Jayce is in the doorway, his gun ready but he's hesitating, not wanting to shoot Douglas.  Drake is running toward them.  Jonah is aiming carefully at the creature, trying not to shoot Douglas.  Drake and Jayce enter the room.  Douglas is being backed into a corner.  Jonah's grenade goes off in another room.  Drake yells, ``WTF?''  {[}\textit{Challenge 2: Shoot the creature and not Douglas.  Small Arms 2 → Matched}{]}  Jonah finds his shot and shoots the creature and it staggers.  Jonah's attack gives Douglas an opening and he runs the guy through with his sword and slices through him.



At that moment there is a massive explosion and Jonah is knocked to the floor.  There's a wave of flames, smoke and debris that floods through the doorway.




\sceneHeadline{The Killing Fields}

Hayley shouts to Lackovich and Javier that the roof is collapsing.  Hayley thinks that they could jump to another building, but she doesn't think Javier would make it.  So clinging to the more stable spots on the roof might be the best bet.  {[}\textit{Refresh: Athletics 3 (Hayley)}{]}  Lackovich responds the fastest and jumps to a spot where she can hang on.  Javier's been swarmed by guys so Hayley runs over to help him, and gets him to a more stable spot.  But in doing so, sacrifices her time to find a stable handhold for herself.  The roof collapses and she falls, and is momentarily stunned.



Jaya is being dragged to a hole.  They seem to be ignoring Breccan for the moment, though Jaya quickly loses track of her.  {[}\textit{Challenge 2: Cinematically cling to edge of hole.  Side Arm 3 →  Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}.  Jaya plants the gauss pistol into someone's brain and lets go to grab onto a lip about one foot down the pit, deflecting attacks with her metal hand.



Jaya notices that there is flaky green residue around the edge, and one of the guys she shot is at the edge of the hole.  His red blood is trickling down the sides of the pit and is turning white.  Someone is fighting around the edge hole.  Jaya's proud of Breccan (she assumes it's Breccan).



Jaya starts climbing out of the hole through the white goo, though she tries to keep her flesh hand out of it.  A figure looms over the edge of the hole.  It's Agent Rust.  He looks down, is a little surprised.  He spits past her into the hole.  ``Need help?'' 

Jaya flips him off and then extends her hand and says, ``Help me the fuck out of here.''   She is \hl{braced for the possibility that he will drop her down the hole}\footnote{\textbf{Nathaniel Ford }It's probably good you didn't step prior to this point, but only after. \textsubscript{11/18/14 10:01am}}, since she would certainly do that in the same situation. He grins widely, exposing his awful teeth and grabs her wrist roughly.  He yanks her out of hole, and dumps her ungracefully onto the ground.  Breccan is a few feet away just swatting people away from her with her truncheon.



Jaya notices rivers of white spreading through the puddles of red blood on the ground, like a spreading infection.



Back at the building Hayley staggers to her feet, mostly unharmed but a little bruised and dizzy from the fall.  The ground underneath her is very unstable with the rubble.  She can't find her rifle and panics, spending some time searching for it {[}\textit{Refresh: Heavy Pulse Rifle 3 (Hayley)}{]}.  She sees, among the debris, blocks of gold colored things, a torn bag leaking circular gold colored disks.  Hayley has no idea what they are but part of her absently notices that the sheer volume of metallic colored things would certainly be a popular decorating trend in Terminus.



Lackovich is perched precariously on the wall and is attempting to provide cover for Hayley and Javier.  Carruthers is chirping to Hayley from very far away  \carBrain{Are you okay?? You need to wake up now!} 

Hayley cradles her rifle and says (to Carruthers as much as Lackovich and Javier) ``I just needed to catch my breath.  Let's move.''




\sceneHeadline{SAC-04}

The dust settles a bit from the explosion and Drake says, ``Everyone up!''  The liquid is still coming and it's crawling across the window.  It is dark grey/blackish in color.  Everyone hustles through the blown door.  The corridor branches into a T and the corridor curves away to either side.  The doors remind Jonah of SAC-01 architecturally but the central area is closed here.  There are doors with labels on them along each corridor.  They eventually find a door to the central column.



It is a large circular glass door, through which they can see a second clear glass door.  There are some designs etched onto the door.  The design has warped grid with splotches on it, and some leaves around the outside.  There are some triangles on the corners, between which it says TESCO.



Through the door, in the room, they can see a round table.  The walls are lined with bookshelves full of books.  Most of the chairs around the table are brown, but two are silver and one (on the far side) is gold.  The table is covered in food.  Gourds, bowls of berries, bread, plates and cups at every seat.  \hl{Every third place there is a pitcher of green liquid}\footnote{\textbf{Rebecca S. }we've still no idea what would have happened if someone drank the green liquid, right?  Nate, wanna' clue us in? \textsubscript{11/18/14 8:00am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'll think about it. I will say that one person on the squad almost became intimately familiar with it. \textsubscript{11/18/14 11:21am}}\footnote{$\rightarrow$\textbf{Suko T }Assuming that the green stuff was alcoholic, maybe Jaya wouldn't have minded falling into and drowning in a vat of hooch.  Corn has a lot of sugars for making booze....:)

That's it!  They weren't zombies, they were just drunk... \textsubscript{11/18/14 12:17pm}}.



There is a man in brown robes sitting in the chair to the immediate left of the gold chair.  He has greyish skin, and there are chevrons on the arm of his robes in two sets of colors (one set is black and gold, the other is blue and silver).  He doesn't seem to be dead, he's just sitting there.



As they scope out the room, they hear a muffled ``Ha!''





\textbf{\hl{The Killing Fields}}\footnote{\textbf{Rebecca S. }Thanks so much for this scene, Nate. :D  Rust has moved up my ladder of favorite people several rungs now. \textsubscript{11/18/14 9:07am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }IG or OOG? \textsubscript{11/18/14 11:26am}}\footnote{$\rightarrow$\textbf{Rebecca S. }OOG of course :P 
Jaya has no favorite people.  Only useful ones. \textsubscript{11/18/14 11:36am}}\footnote{$\rightarrow$\textbf{Suko T }But what about Padme!  Isn't she the only favorite?  And maybe Simon. \textsubscript{11/18/14 11:58am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Questionable...  also, according to Padme, she's the *only* useful one between the two of them. \textsubscript{11/18/14 12:08pm}}



Rust helps Jaya and Breccan fall back to the cave.  Rust's people are organized about it and coordinate well to cover each other when they need to reload.  Rust stops shooting for a moment, pulls something out of his pocket, shoves it in his mouth and then resumes firing.



Jaya sees the collapsed building and says, ``Where the fuck is the rest of my team?''  She stops falling back and demands, ``Where are my people?''

Rust grunts, ``Roof.  Dunno.''

``We're not fucking leaving them,'' says Jaya.  She realizes that her gun is gone and looks around for another.   She puts her hand on Rust's holstered second gun.  Rust's hand immediately closes over hers painfully and he says challengingly, ``Try it.''  

{[}\textit{Refresh: Side Arm 3 (Jaya)}{]}

Jaya says insincerely, ``Sorry.'' and uses her metal hand to peel back his fingers. ``I need to borrow your sidearm.''

Rust drops his gun and a knife appears in his hand and he presses it against her neck. ``Bad move, Lady.'' A line of blood appears where knife meets neck.

Jaya keeps her newly acquired gun low, but presses it up against Rust's sternum and snarls, ``That's not very cooperative of you, Agent.  I thought we were supposed to be a fucking team.''



Hayley has climbed out of the rubble and sees two uniformed figures in a strange standoff.  She can tell it's Jaya and Rust.  Jaya's pointing a gun at Rust and Rust has his hand near her throat.

 \carBrain{They're asking for a status report} 

\hayleyBrain{One moment please, I need to get the status.}  {\color[RGB]{255,153,0} } 

Hayley says over the hush radio, ``Agent Parvadi?  Do you need assistance?''

Jaya doesn't reply, she and Rust are staring each other down.  Leaning closer and closer to each other, neither wanting to back down.  Rust doesn't press the knife deeper but Jaya can feel the warm trickle of blood down her neck.  Rust's breath is horrible.  Rust takes a deep breath and exhales in a slobbery hiss, spraying her with spittle, and backs off saying ``Finish this later.''



Jaya's being eyed by the other members of the squad.  She checks out her new gun and then looks up at Rust and calmly says, ``While we're at it, can I have some of that chew?''  She holds out her metal hand as if expecting him to hand her some.  Rust rolls something around mouth and spits a big glob quite accurately onto the palm of her metal hand.  ``That enough?'' he sneers.  

Jaya flips him off and wipes it off.  ``I'm getting my fucking team.''



Through all this Hayley is repeating over hush radio, ``Sir?  Sir?''

Jaya finally replies, ``Hayley?  If you're still alive, I'm coming to get you.''

``Sir, we'll come to you.  This place is not safe. \hl{It is structurally deficient.}\footnote{\textbf{Nathaniel Ford }Lulz! \textsubscript{11/18/14 11:27am}}''

{[}\textit{Challenge 1: Notice.  Sent back.}{]}

In Jaya's head she hears \jonahBrain{Ha!} 



Hayley is coordinating with Lackovich and Javier to get to the Plaza.  She also reports to Jaya over the radio, but speaking loudly enough that Lackovich and Javier (and Carruthers) can hear.  ``Sir, you should also be aware that the enemy combatants are working in teams of approximately ten, with one person coordinating each group.''



\textit{{[}Challenge: Notice 1.  Streetwise 1 (Jonah) → Matched{]}  }Jaya notices that the people they're shooting are getting back up.  She shoots one and yells loudly, ``Motherfucker!''  She turns to Rust and says, ``\hl{Did you know they're getting back up?? FUCK!}\footnote{\textbf{Rebecca S. }And thus ends Jaya's good time. \textsubscript{11/18/14 8:06am}}''



Hayley, Lackovich and Javier fight their way to the Plaza and join up with Jaya \& Co.  Along the way Hayley gives a report to Carruthers.  \hayleyBrain{Status report.  No known additional casualties for the teams outside of SAC-04.  Some injuries, nothing incapacitating. I have noted that the combatants appear to be working in teams of 10, with a single organizer or leader for each group.  There is an object that has a bright beam of red light that slices through buildings and causes damage.  We have been killing the enemy combatants with predictable efficiency but their numbers are large.  I have no direct communication with the team inside.}  {\color[RGB]{255,153,0} } 

Carruthers can tell that this last item distresses Hayley a great deal.




\sceneHeadline{SAC-04}

Douglas is fiddling with the door.  Jonah can see the ``Ha!'' guy wandering around the table.  ``How the hell did he get here?'' asks Jonah.

``I guess there's a quicker way in,'' replies Jayce.  ``How much time did we have again?''

``This is where we need go right?'' asks Jonah.

``Douglas says yes, he says it's the Operational Control Center.''  Jayce and Douglas confer.

``But he thinks it's been modified.''

``Yeah.  It has.  We got a message from base,'' says Jonah.

``Of \textit{course} you did,'' says Drake dryly and checks his ammunition.

``Game plan sir?'' Jonah asks Drake.  ``Whatever this is, it isn't very friendly.  But I don't think we're getting out without \textit{some} kind of overture.''

``I'll back your lead.  You know the mission objective right?  We want control of this base.  And if he gets violent, I'll shoot 'im,'' says Drake, pragmatically.



Douglas opens the door and sheaths his weapon.  They step into the antechamber.   Jonah lowers his weapon, Drake and Jayce do not.  The door behind them shuts, the one in front of them opens.  The guy at the table looks up and squints at the visitors.  His eyes are covered by the white film.  ``Ha!'' guy appears to be wandering around, putting out food and moving things around.




\sceneHeadline{The Killing Fields}

Jaya and Hayley realize that there are more people coming out of the buildings.   The fight is getting more and more desperate.  We start running out of ammo and many are reduced to truncheons and knives.  The ones we kill are getting back up again, no matter how many limbs we hack off. 



Hayley has a bit more success by targeting the 1-in-10 for each cluster, because every time she drops one of those, the whole group becomes aimless and stop attacking.  But no one else seems able to spot them like she can, so it's of limited use.



We get backed up to the cave entrance.  Hayley looks around consideringly,  ``Agents, shall we use explosives to collapse the entrance and seal them out?''

``Fuck NO!'' yells Jaya.  ``Just shoot more of them!!''

Hayley sighs a little, not really talking to Carruthers but in her head she resigns herself to dying in the cave.  She has already calculated that they don't have enough ammo to hold out for very much longer.  But she obeys orders and does her best to protect Jaya and PG2.  She's not angry about it, she just hopes she can die protecting someone.  \hl{Someone important would be best.}\footnote{\textbf{Rebecca S. }$<$\textbackslash3 \textsubscript{11/18/14}}\footnote{\textbf{Suko T }She knows the value of her life, she doesn't want to martyr herself for some schmoe. \textsubscript{11/18/14 11:59am}}




\sceneHeadline{SAC-04}

There are bookshelves, many books.  Jonah almost thinks he can make out what some of the titles say.  There is a dome above the table has a vision of the night sky with two moons that look like our moons.  It is slowly rotating.



The ``Ha!'' guy walks up to them and offers them a gourd and cups of green liquid.  Jonah takes a cup but doesn't drink.  Jayce is offered a cup as well and then the guy seems to forget what he's doing and wanders off.



``Welcome,'' says the guy in the robes.

``It's good to be here.  You're the Praetor of this place?'' asks Jonah.

The guy blinks. ``Praetor....?  No.''

``What are you then?''

``I'm terribly sorry.  I seem to have forgotten my manners.  And my name.  Would you like to sit?''

Jonah politely refuses.

``It is difficult to live in this world moment.'' says the man.

``Forgive me, 'world moment'?''

The robed guy looks curiously at Jonah. ``Yes.  You wish to talk to the Praetor?  What about?''

``Ha!'' yelps the ``Ha!'' guy.  Jonah is watching the ``Ha!'' guy to see if he's like Mohinder (controlling things behind the scene), but no, the guy is just wandering around.  He seems to lose track of what he's doing all the time.

{[}\textit{Challenge 1: Notice.  Sent back}{]}

Jonah explains, ``We come from another 'world moment'.  A different Praetor.  There is a threat that is of significance to all Praetors.''

``What do you want?''

``Permission to use this place,'' says Jonah.

``Ha!''

``It has been long expected that this world moment would come.  It is unfortunate that it came with such fire,'' says the robed man.

``Which fire?'' asks Jonah.

``Many lives have been interrupted.  \hl{In time those too can be healed.  If you remember.}\footnote{\textbf{Suko T }Jonah asks so may questions but not about this intriguing tidbit! Argh!! \textsubscript{11/18/14 1:41am}} But, the Praetor is tired.  Do you wish the mantle?''

``The what? Sorry, I do not understand.''``Do you wish to become the Praetor?  As the one who came before?  You will have to negotiate with Supay of course,'' says the man quietly.

``Supay??''

``Yes the other one not of this place, who came before.''

``Is Supay another Praetor?'' says Jonah, playing dumb.

``Was. Praetors without a Complex are not Praetors.''

``How did he lose his place?'' asks Jonah.

``We asked him in another world moment, the one in which he came. But I do not remember.  Perhaps you can ask him.  I'm sorry, sometimes I forget things.''

``You are not the Praetor but you speak for him.''

``I..... live here.  As we all do.  Under the Praetor's watch,'' says the man slowly.

``Does the Praetor-''

``Ha!''

``-normally attack people who come to his door?'' continues Jonah.

``The Praetor protects this complex.  This world moment.  Supay is somewhat more....aggressive.  I apologize if that is what caused this senseless violence,''  the man says softly.

``Your guest attacked us,'' accuses Jonah.

``He is not a guest.  He is part of this complex now.  There is a Praetor.  And there is Supay.''

``Who is in charge?''

``Why does someone need to be in charge?  Why can't we just live together?''

``Because we're not!  Have you been outside? We walked in and Supay tried to kill us!!!'' says Jonah loudly and angrily, clearly losing his temper. {[}\textit{Refresh: Social Chameleon 2 (Jonah)}{]}

``I have not. It all happened so fast...I am sorry if you were offended,'' says the man placatingly.``I am not offended, I'm \textit{terrified}!  Do you know what that is like??'' demands Jonah.  He looks over at the ``Ha!'' guy who is just rocking in place.``I wish I could empathize, but I do not know if I can. Warnings were posted.''``\textit{Warnings}.'' says Jonah, still sounding upset.

``Yes so that those from other world moments would not come into conflict with ours.''

``You left a man in a state of agony on a wall.  That is a warning?''

``Ah... yes.  He did hurt many people.  So it was his punishment, for a time, in this world moment.''

``I see,'' says Jonah.  He sits down abruptly and puts the drink down.  ``Would you give me a moment?''

``Take all the time you need.  Would you like some food?'' says the man graciously.

``This man came, do you know what he wanted?'' ask Jonah.

``Supay?''

``Supay came?'' asks Jonah.

``I don't understand....''

``Do you know the name 'Octavius'?'' asks Jonah.

``HA!  Ha!'' yelps the ``Ha!'' guy.

``I do not remember Octavius. Perhaps there are others here that do.  If they are not... interrupted.''

``Others?''

``Many live here.  Nearly a thousand.  Few are in this world moment though.''

``You said the Praetor is tired?

``He has been damaged.  It is beyond repair.  We are very good at repair.  \hl{At memory.}\footnote{\textbf{Suko T }ORLY?  Hmmm... seems to be a lot of not remembering going on... \textsubscript{11/18/14 1:44am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford} Well, there is memory and then there is world-moment memory. \textsubscript{11/18/14 11:31am}}  Very good.''``I'm sorry,'' says Jonah.

``Did you cause this damage?'' ask the robed man curiously.

``No.''

``Then why did you apologize?''

``It is sympathy,'' says Jonah.  ``We are in a similar danger where I come from. Which is why I came to speak to your Praetor.''

``Ha!'' says the 'Ha!' guy.  Jonah looks at him very closely.  He has stopped moving around and seems to be unable to remember if he should go to a bookshelf or to go sit in the chair.

``You need another Praetor, correct?'' asks Jonah. ``What if we can give you one?''

The robed man says, ``Yes.  If you wish to take up the mantle, we can allow it.  \hl{I must advise that you will have to negotiate with Supay.  As he negotiated with us}\footnote{\textbf{Rebecca S. }ah, man... am sorry we missed watching this... I'd love to see Drake ``negotiate'' with Supay... \textsubscript{11/18/14 8:13am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }As it turns out, they get along famously. \textsubscript{11/18/14 11:34am}}.''

``Does he wish to be a Praetor?  Here?''

``Supay is not capable of being a Praetor here.  Not in the full sense of it.''

``How would we know if someone is capable?''

The robed man gestures to a cup in front of the gold chair which seems to have gold liquid in it.

Drake asks, ``Is he saying what I think he's saying?'' pointing to the cup.

``I wouldn't think it's that simple,'' says Jonah

``Douglas says that he thinks it is,'' says Jayce.

Jonah asks for another minute to ask more questions.

Drake nods and circles around to stand by the cup.

Jonah addresses the robed man again. ``What sort of person do you need be your Praetor?  If Supay cannot do it, why?''

``Supay was damaged.  Supay was...unbalanced,'' says the man with his usual calm.

``Do you know the other Praetors?  Have you met them?''

``I have not.  The Praetor has.''

``Ha!''

``Would your Praetor be willing to speak to me as a representative?''

``We can advise you in this world moment on the knowledge that our Praetor has about your Praetor.  If that is what you are asking.''

``Do they trust each other?''

``We do not know who your Praetor is.''

``Do they work together or not?  Is it a group?  Or simply a post?''``It is a post. But also a family.  A collaboration.  A career,'' says the robed man.

``Our Praetor sent us because our complex is under threat by something that devours places alive.  Like a disease. We need all the help we can get.  If you think we can provide you with a Praetor, I suspect that our Praetor is willing to do this.  But we need to know what will be expected of such a person.''

``The post of Praetor is well defined.  This complex must be protected.  Those in it must be protected.  Our knowledge must be protected,'' says the robed man.

``Will Supay agree to work with a new Praetor this way?'' presses Jonah.  ``From what we have seen, we are not welcome here.''

``I do not know your interactions with Supay. They happened so fast.  If you wish to negotiate, if you wish to take up the Praetorship, then that can be arranged.  Supay is protective, as Supay should be.  But Supay is damaged and cannot enter this place.''

``Will you give me a moment?'' asks Jonah.  He addresses Drake, ``Sir, do you know what a Praetor is?''

``Yes,'' says Drake.

``I'm not entirely clear on the idea...'' says Jonah.

``It's in charge of the station,'' says Drake.  ``Used to be lots of them.''

``Do you think the person that is in charge of this place thinks like a normal human being?''

``Given what we've seen, I'll say no.  But do we have a choice?''

``We have to negotiate with it.  There are conflicting people in charge here and what we have been fighting may or may not be the original. That's the information we got from home,'' says Jonah. 



Jaya is feeding a sense of rising panic to Jonah as the group in the cave is pretty much pinned to the back wall of the cave, fighting for their lives.  Jonah is panicking as well but it has an anxiety edge to it where one wrong move will end in disaster.  They get a little panic-loop going.



``Essentially they are offering the place. But there is more than one judge.  And if they disagree, they may not only destroy the person they are talking to but everyone else too. ``

``But to do this we just have to drink that?'' asks Drake, pointing to the cup.``Yes but I don't know if you get interviewed or if you get the job or.... I don't know how this thing works,'' says Jonah, sounding tense and frazzled.

\hl{``Only one way to find out!'' says Drake and he picks up the cup}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{11/18/14 8:16am}} and is about to drink it when Jonah pleads with him to let him ask one more question.

Jonah asks the guy in robes, ``The one who drinks, does he speak to Supay?''

``Speak to Supay?  Supay does not....speak.'' says the guy, sounding a little puzzled.

``It's not an automatic thing?  Does he automatically become Praetor?''  Jonah is desperately trying to read the guy.  He wants to know if the position is automatic or if the person doing this will be evaluated and perhaps someone could speak for them.  Based on the guy's incomprehension of Jonah's questions, he thinks that at least the guy believes the process is automatic.

Jonah addresses Drake.  ``Sir, I believe you can proceed.  With the following to not-insignificant caveats.  If they don't accept it I don't know what they'll do to you.  If they \textit{do} accept, I don't know that you'll be able to leave.''

Throughout this, Douglas is calm and is watching what Drake is going to do.  Douglas is not moving forward toward the cup at all.



Jonah asks for another pause and asks Jayce, ``Can you ask Douglas if he knows what they are negotiating about?  \hl{What a Praetor is?}\footnote{\textbf{Nathaniel Ford }From a literary point of view, a Praetor is a bit like a Parent. They are defined by a particular role, but the characteristic behavior of individuals in that role varies so much as to be hard to describe. Are Langdon and Padme the same? Padme and Jonah? Jonah and Timon's father? Langdon and Hospitalized Jaya? What are these people? Are they more or less than their role-title? Does that role-title even define them well enough to qualify? Or does it define the user of the signifier more than it defines the signified? \textsubscript{11/18/14 11:39am}}\footnote{$\rightarrow$\textbf{Suko T }If this is so, then Rook deserves a  Nobel Parenting Prize or something for being the Praetor for SAC-09 and all of us. \textsubscript{11/18/14 12:01pm}}\footnote{\textbf{Suko T }I think this is now the fifth time Jonah has asked someone about this. :) \textsubscript{11/17/14 1:47am}}  Does he understand what this conversation is about?  There is someone in charge where he lived.  Does he know who they were and how that worked?''

``He says that's not actually true.  They didn't have a Praetor.  But he says he understands this.''

``Okay,'' says Jonah and pauses and thinks.

Drake says, ``Enough'' and drinks the contents of the cup.  He starts making odd faces like he's struggling with something and pulls out the chair and sits down.



The ``Ha!'' guy walks up to Jonah and puts hand on Jonah's shoulder.  He smiles and softly says, ``Coniecturalem artem esse medicinam''. Then, ``Ha!'' and dies.

Jonah replies, ''\hl{Medicus nihil aliud est quam animi consolatio.}\footnote{\textbf{Nathaniel Ford }+1 \textsubscript{11/18/14 11:41am}}''



In the cave, the attackers suddenly just...stop.  The mobile ones start wandering away.  Jaya continues to kill and maim a few more before Hayley patiently pulls her off of them and says, ``Sir, they're not resisting.  I think you may wish to stop.''



Back in the room below, Jonah confirms that the ``Ha!'' guy is dead.  The guy in robes is unchanged, just watching.  Drake is breathing shallowly and his eyes have a thousand yard stare.  Veins of gold are spreading over his eyes.



Jonah says to Jayce, ``One way or another, this is almost over.''

Douglas signs something and Jayce says, ``Yeah we're fucked either way.  If we have to get out of here, what are we doing here?  I'm never going down a hole with you people ever again.  I was right the first time...''

Jonah says, ``I hope you're wrong, because that means we're not going anywhere.  I think what's going on is the Agent is signing onto taking charge of....whatever the fuck this place is.''

Drake says with Rook-like calm, ``That is correct.  Give me a moment and I'll open the doors to the surface.  Tell Rust to proceed back to Terminus.  He's only to take one squad with him.  Leave the others with me.  Your job here is done.  Good work.''

``What message would you like him to take back?'' asks Jonah.

``Rust will know what to say.  Tell him: Coale Six.''

``Coale Six.  And what message would you like us to take back to our people?''

``Do they need a message?''

``Honestly sir, I don't know most of the time,'' says Jonah.

``Tell them that I believe the situation is now under control.''

``Should I tell them that you will be in contact again?''With a slow smile, Drake says, ``Certainly.  Tell Jaya I would love to have her over.''

``Understood,'' \hl{Jonah grins}\footnote{\textbf{Rebecca S. }insubordinate bastard... \textsubscript{11/18/14 8:18am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Yeah, but so was Oliver. Men are short, short-lived and insubordinate. \textsubscript{11/18/14 1:59pm}}\footnote{$\rightarrow$\textbf{Suko T }And women are tall, scary and psychotic? :) \textsubscript{11/18/14 3:35pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }And hella loyal! Don't forget that part, that's important... the ladies be loyal. \textsubscript{11/18/14 3:44pm}}.  He stands and salutes Drake.  Drake stands and salutes him back.



Jonah turns to Jayce, ``Good news!  You get to go down more holes with us.''

``No fucking way!  \textit{Nofuckingway}!!'' mutters Jayce.




\sceneHeadline{The Killing Fields}

Once Jaya has stopped killing, Hayley looks intently at Jaya. ``Operator Gemayel, is he alive? Does this mean they succeeded?''

Jaya, ``I don't know.''

Hayley taps her head, ``Can you ask him?''

Jaya gives a long suffering sigh but shouts in her head  \jayaBrain{Jonah!!} 

There's a long pause.  

\jonahBrain{Chief can you hear me?  I tried the radio but it didn't work.} 

``Augh!  Fuck!!'' says Jaya at the mental contact.

``What just happened?'' asks Hayley, alarmed.

``Not dead,'' says Jaya, looking irritated.  Hayley is flooded with relief.

\jonahBrain{I have good news and bad news...} 

``Bad news??'' repeats Jaya out loud.

Hayley's freaking out.  ``What?  What??  Bad news???''  Carruthers can tell that Hayley's more frantic now than she was when facing certain death by zombie.

\jonahBrain{The good news is the mission was a success.  We can go home.} 

``The mission was a fucking success!!'' says Jaya loudly.  ``Please tell me Drake bought it on the way down.  Please come on, I just need something to go right,'' says Jaya out loud.  Rust raises an eyebrow.

\jonahBrain{Take a deep breath Chief.} 

``Is there gas?'' says Jaya in panic.

\jonahBrain{Wait did the fighting stop?  It should have stopped.  Wait wait, are you alright?} 

There's another feedback loop of panic.

``What's going on?  Gas?'' asks Hayley in confusion.

``Jonah just said there's something bad gonna happen.''

\jonahBrain{No, no.  It's not bad for the team.  But.... you're all alive. Can you confirm please?} 

``Yes!  Please just fucking tell me!!'' yells Jaya, eyes wide as she stares about the cave, struggling with the concept of focusing inward.

``Are they alive?  Sir?''  Hayley is starting to hyperventilate.

Lackovich grips Jaya's shoulders and drags her a bit away, hissing through clenched teeth, ``You need to get your fucking shit together!''

\jonahBrain{Chief!  Calm down.  The mission was a success.  We have what we need.  The fighting should have stopped.  We're coming out.} 

``They're coming out,'' whispers Jaya.  ``Jonah's alive.''  Hayley lets out a huge breath of relief and sits down abruptly, almost fainting.  Jaya continues, ``Everyone's alive.''  she repeats it louder for everyone else, ``Everyone's alive!!''



Hayley sits on the ground, her arms wrapped around her legs, head resting on her knees, breathing shallowly and fast, her eyes closed.  Carruthers is subjected to an intense mix of emotions from Hayley.  Feelings, long deferred (terror, relief, panic, sadness, pride) sweep through Hayley in an undifferentiated stream.  Hayley simply bows her head and yields to it but at the same time seems to be stubbornly daring this storm to break her.  If Carruthers wasn't so used to strong emotion it would be overwhelming. 



Jaya walks up to Rust and hands him back his gun.  ``Thanks for the loan,'' she says.  Rust spits.  Jaya continues, ``No hard feelings, right?'' Rust says nothing.  They stare at each other.  When Rust blinks, Jaya rolls her shoulder, ``Pleasure working with ya.'' and she walks away.



Jaya goes to congratulate Breccan.  ``Great truncheon work...fell of a building but we recovered from that...''  Jaya ignores Javier and Lackovich.



Jonah, Jayce and Douglas walk back up to the surface. When they get back to the exploded door, the area is suspiciously clean.  They notice that the black liquid is gone.  Only a few dried flakes remain.  Jonah collects a few for forensic study later.  There is no sign of Supay, although in Lab One, the head is still regenerating.

``There's one more slight problem,'' Jonah says to Jayce.

``Problem?  What problem?'' asks Jayce, alarmed.

``The Chief and the Agent don't get along.  Let me break the news to her.''

``Drake?  Yeah, I knew they don't get along.  What am I, an idiot?''

``No you're not.  So don't tell her off the cuff.  Because we're going to have a really fun time when we tell her.''  Jonah smirks.




\sceneHeadline{In the Cave}

Jonah, Jayce and Douglas walk out.  Douglas looks pretty beat up.  Jayce is mostly okay.  Jaya cranes her head and doesn't see Drake and smiles widely.  When the door opens, Hayley looks up and sees Jonah.  Carruthers can feel that Hayley's emotional exhaustion vanishes at the sight and she is incandescently happy at seeing Jonah alive and hale.



Jonah walks up to Jaya, salutes, and says ``That was....interesting Sir.''

``That was fantastic!  We succeeded!'' says Jaya enthusiastically.

``Does anyone need medical attention?'' asks Jonah.

Jaya doesn't say anything but does poke a finger at her cauterized abdomen wound.  She asks Jonah, ``Where the fuck is Drake?  Did he not make it out?  Is he down there, incapacitated somewhere?''

``Drake is staying.''

``Is he injured? I mean, I understand...''

``Sir, I have to pass along a message to Agent Rust.  One moment.''

Jaya frowns at not getting her questions answered.  Hayley leans close to her and says quietly, ``It is true, Agent Parvadi, that we were to open the door and they were to take over from there.''



Jonah addresses Rust, ``Agent, one you should should return back with one of your teams, and leave the other one here.  They will be meeting up with Agent Malak.  And the other is Coale Six.''

Rust spits and Jonah thinks that Rust is pleased (though it doesn't show).  Rust wanders over to Grabber and they start conferring.



Hayley asks Jonah, ``Operator Gemayel, am I still requisitioned to Agent Malak's team?  Do I stay?''

``No.  We are going back to our previous commands.''

\hl{Carruthers can feel Hayley's a little unhappy about this, which prompts her to clarify ``And that is a direct order, from Agent Malak?''}\footnote{\textbf{Rebecca S. }Whaaaaaaaaat? 
I missed this somehow in the game \textsubscript{11/18/14 8:24am}}\footnote{$\rightarrow$\textbf{Suko T }You were talking with Jayce at the same time (whee for transcribing double-tracked conversations!).  Hayley liked being on Drake's team, hence the disappointment.  Jaya may indeed have to work on some deprogramming :D \textsubscript{11/18/14 12:03pm}}

``Yes.''

Hayley drops her gaze for a second and Carruthers can feel a sharp sense of disappointment and hurt from Hayley.  But Hayley just says, ``Oh.  Okay.'' and walks away.



Jaya walks up to Jayce, slaps him on the arm and says, ``See?  Fucking fine.  You're better off than fucking giant guy, y'know?  Good job standing next to the medic.''

``Good to see you, too,'' says Jayce.

Jaya winks at him and says in a loud whisper, ``Where the fuck is Drake?''

``I uh... he's downstairs.   He drank the juice.  I don't know, I only understand like half of this,'' says Jayce

``I'll explain on the train,'' says Jonah.

``We can't just leave him down there!'' says Jaya.

``He'll be fine,'' says Jayce.

``Yes we can, he stays,'' says Jonah.

``Quitter,'' mutters Jaya.



Jonah treats Jaya's wound, which has started bleeding at this point.  {[}\textit{Reduce Flaw: }\textit{ {\color[RGB]{255,0,0}Flaw 1: Cauterized abdomen wound (Jaya).} }\textit{  Medkit 1 (Jonah) → Flaw 0}{]}




\sceneHeadline{Down the Mountain}

We start heading down the Mountain.  The clouds have gone away and the sun is starting to come up.  Rust is taking Madelyn, Pipes, and Arjoon back with him. They strip down their equipment and leave a lot of stuff at the cave and start doubletiming it down the mountain.  Our group does not hurry down the mountain, due to injuries and Jonah saying that we don't need to hurry.



Jaya tells Javier to give a status report over the radio.  Hayley taps her temple lightly and says that she's already given a report (she doesn't know that Drake is Praetor but she reports everything else that she's been told or observed).  Jaya looks uncomfortable with the reminder.



Jaya waits until Rust's team is far enough ahead and then starts talking loudly about how Rust's team is probably setting up an ambush for them and that's what all the code stuff was about.  Hayley goes into bodyguard mode and starts scouting ahead and asking the group to pause while she checks out blind corners and other possible ambush sites.



At some point Jonah catches up to Hayley out of Jaya's hearing and says, ``Don't worry about it, we're fine.''

Hayley looks at him calmly and says, ``She's my superior officer, Operator Gemayel.'' and continues to play bodyguard and scout.



After an hour or so, Jonah can tell that we're all tired and particularly Hayley is starting to stagger a bit from exhaustion.  He calls a rest.  Jaya takes the second dose of Morgan's drugs and says she'll keep watch while everyone sleeps.  Jaya tries to put some moves on Jayce but he's exhausted and a bit standoffish.  Jonah tries anxiously to diffuse any tension in the group, unwittingly making Jayce a bit more cranky as Jonah keeps him from sleeping.  Douglas comes over and puts his hand on Jonah's shoulder and makes a ``calm down'' gesture.



After about 30 minutes of rest, Hayley has the odd sensation of being mentally shaken awake.

 \carBrain{Hey!  Hey!  Wake up } There is a feeling of barely suppressed panic from Carruthers.  \carBrain{I need   to } \textless brief signal loss\textgreater  \carBrain{  talk to you.  Can you guys get back any faster? } 

Hayley is still groggy and half asleep but she starts making some mental calculations

\hayleyBrain{Yes.}  {\color[RGB]{255,153,0} } 

 \carBrain{Really we just need Jonah.  They realize you are tired and everything.... Not if it's going to  compromise safety. } 

Hayley does a quick personal health check \hayleyBrain{No I can do it.  I'll probably collapse afterward though.}  {\color[RGB]{255,153,0} } 

 \carBrain{Um... okay.  Morgan says anytime you can make is good but don't hurt yourselves.  We need you all back. } 

\hayleyBrain{What if we collapse when we get to the train or SAC-09?  What state of unwellness is acceptable?}  {\color[RGB]{255,153,0} } 

 \carBrain{Uh, hold on... They're going to need Jonah awake... I guess....Um... } 

\hayleyBrain{But the rest of us don't?  Understood.  Oh, I haven't opened my eyes yet.}  {\color[RGB]{255,153,0} } 

Hayley's eyes pop open and she takes a deep breath and sits up.

Jaya swings around at the movement, ready to attack something, but sees it's Hayley.  ``Ah good. But you should really go back to sleep, we have another two and half hours...''

Hayley says, ``Sir we really have to leave now.  We have to get Jonah, er Operator Gemayel, back to SAC-09.''

``What??''

Hayley yawns, still trying to clear her head, ``They wish to have him back at SAC-09 as soon as possible.  I can carry him if he can't make it,'' says Hayley.

``So can I.  Okay cool.  EVERYBODY UP!'' exhorts Jaya.

Jonah sits up suddenly and pulls out his gun in alarm.

``Naptime is over!  Gotta go, gotta go!'' says Jaya with manic energy.

``Chief, we need our rest,'' says Jonah.

``Direct order from Agent Morgan, we are to return as soon as possible,'' says Hayley, sounding exhausted as she gets to her feet.  ``Some amount of damage is acceptable.  But not for you, Operator Gemayel.  You need to be awake and alert when we return.  I will carry you if I need to.  What is your physical status?''

``Need a lift?'' says Jaya, trying to grap the drag loop on the back of Jonah's uniform and haul him to his feet.  ``You got two ladies excited to carry you down the hill.  Let's fucking do it!   Fucking doubletime!!'' orders Jaya.

Jonah swats Jaya's hands away, crankily.   ``Is that part of the order?  Some amount of physical damage is acceptable?'' Jonah asks Hayley.

 \carBrain{Don't hurt yourselves. } 

``The advice is that we shouldn't hurt ourselves but that you were the priority.''

Jonah asks if some people can stay behind since some people are unwell.  Hayley confers with Carruthers and says it's okay but inadvisable.  Also Jonah realizes that there is only the one train so they'd be stranded until the train returns. Jaya refuses to leave anyone behind.



To that end she kicks Jayce awake, who curses at her and then when she tries to pull him to his feet, pulls a gun on her. ``Jaya!  Fucking put me down!''

``Jeez, you always get so fucking grumpy!'' complains Jaya and she walks off to check on Douglas.  Douglas is awake, looking tired, but is moving under his own power.



``Good.  Everyone's alive.  That's good,'' says Jonah almost dreamily.

Hayley and Jaya look over (more or less discreetly) at Lackovich at this comment.  Lackovich has a dark fuck you look on her face.

Jonah looks around at the uncomfortable silence and says, ``No I mean, from when I went in...I wasn't sure...'' (this doesn't help).  

Lackovich snaps, ``Javier, Breccan, with me!'' and she starts marching down the mountain.



``Hayley, make sure that Jonah gets down the mountain,'' orders Jaya.  Hayley nods and marches next to Jonah.  She sets a brutally fast pace.  Jonah starts lagging behind and Hayley tries to put an arm behind him to help him move faster.  He shies away and says angrily, ``Agent.  Hands to yourself.  I'll keep up.''

Carruthers can feel Hayley is very hurt and also frustrated by this, but all Hayley says is a clipped, ``You weren't.''



Everyone makes it down the hill.  Jayce is doing the worst, trailing behind everyone.  When Jaya attempts to ``help'' him he picks up the pace and stays out of arm's reach.  She uses that to sort of herd him down the hill.  She's still very paranoid that Rust's going to ambush them or Drake's going to shoot her from behind.



Jaya gets some jumbled images from Jonah, one in particular of Drake with golden eyes flashes past and she barks, ``Jonah!  Rein it fucking in!!''

``What?'' says Jonah, confused.

Jaya points at her head and says, ``Keep it under fucking control!  \hl{I don't want any of that shit in my head.}\footnote{\textbf{Rebecca S. }because clearly in Jaya train of thinking Jonah's vision of Drake with golden eyes is just some fanciful day dreams on his part she doesn't want in on.  She's seen the way he sides with him in every argument. \textsubscript{11/18/14 8:31am}}\footnote{$\rightarrow$\textbf{Suko T }And asks for Drake's permission before treating Jaya's wounds... such a kiss-up. :D \textsubscript{11/18/14 3:36pm}}  C'mon don't ruin my fucking high!''

Jonah actually picks up some of Jaya's drug rush and says softly, ``oooo that's good.''



We get to the bottom and the large metal door is open.  Grabber (whom they had left at the top of the hill) is sitting there, eating something.  He nods as we march by.  We don't see Rust's team.  It's a bit of struggle to get across the river but we manage.



Javier calls the train.  It takes a while to arrive.  Jari is driving the train and says, ``You guys look like shit.  Sorry this took so long, I had to drop off Agent Rust's team.''

We board the train.   Hayley makes sure that everyone (who is supposed to) gets on the train.  Lackovich reports quietly to Jari, ``Morley didn't make it.''

Jaya's eye twitches at hearing that but she says nothing and just strides onto the train and starts doing some pull ups.



As the train starts off, Jonah thinks at Jaya \jonahBrain{Chief, before we give the status report, do you want to know what happened?  Yes or no?} 

``Fuck!  FUCK!!'' She walks up to Jonah and puts her hands on his shoulders.  ``Okay.  When we're in the same fucking space, surrounded by our fucking dudes, \textit{use your mouth}.''

\jonahBrain{You may not want everyone to hear this.} 

Jaya slaps Jonah, ``Fucking cut it out!  Jesus.'' she stalks off to pace around the train.

\jonahBrain{I'll take that as a no.} 



Lackovich gets up and walks over to Jaya.  She pulls out a cigarette and hands it to Jaya and says firmly, ``Smoke it.  Don't say anything else until it's done.''

Jaya sighs, ``Thanks.'' She rolls her eyes in a ``can you believe this shit?'' commiseration look with Lackovich, who doesn't take the bait.  The cigarette calms her down a bit but she's still hyped on Morgan's drugs.  Lackovich keeps feeding Jaya cigarettes, half of which Jaya palms for later, and keeps her attention most of the trip.

At all the fumes and smoke, Hayley moans a bit and turns a bit green like she's going to be sick. She is trying to breath as shallowly and as little as she can, which is not working well with her exhaustion.



\textbf{{[}13 Tokens remain{]}}




\sceneHeadline{SAC-09}

We pull into the SAC-09 station.  There is red lighting and once the door opens we hear a repeating message, ``Please be advised, Code Blue is in effect.  Medical emergency.''

On the platform are Swan, Dr. Gerhauser, Micah in full combat gear, and Morgan.



Morgan steps forward.  Jaya salutes.  Morgan salutes back and says, ``Report.  Casualties?''

``Uh, one?''

``Dead or wounded?''

``Dead.''

``Is anyone else in immediate need of medical attention?''

``No,'' says Jaya.

``Several people,'' says Jonah.

Morgan raises an eyebrow and looks Jaya up and down, taking in her gore-spattered armor and the slice through the midriff.

``Do you want to reassess that?'' asks Morgan.

``It's not mine,'' says Jaya with a shrug.  ``Is there an emergency?  We are prepared to assist.''

Morgan takes a finger and pokes at Jaya's gut wound.

Jaya yelps and steps back. ``Fuck!  Okay maybe we can use a little medical stuff, but we are ready to help!''

At Jaya's cry, Hayley forces herself to her feet to come stand next to Jaya and salutes Morgan as soon as she's able.  But she's clearly is barely keeping herself from falling over.  Jaya looks at her and says, ``Okay well..maybe Hayley could use something...''

Morgan turns to Jonah, ``Operator, please proceed with Dr. Gerhauser.''  Jonah follows but looks tired and unhappy.  He does note that Douglas seems very on edge.



Morgan looks at the rest of us, ``Anyone else who is in need of medical attention should see Dr. Swan.''  She addresses Jaya.  ``Once you're patched up, I need you to resupply and report to the Ops room.''  Morgan looks at Jayce and Douglas and says, ``you two stay here.''



Jaya puts an arm around Hayley and says, ``I'm going to take Agent Hayley to Medbay, and then we'll be right back, Agent Ma'am Sir Agent.''




\sceneHeadline{In the MedLab- Jonah and Dr. Gerhauser (and Rook and Signe) }\textbf{\hl{*}}\footnote{\textbf{Nathaniel Ford }Indicates counts towards backlash. \textsubscript{11/18/14 4:12pm}}

As Jonah is walking with Dr. Gerhauser, he says, ``There's one thing you should know, the only people present at the final event were myself, Jayce and Douglas.  I don't know if Jayce understands what happened and \hl{I didn't get a chance to update everyone.}\footnote{\textbf{Suko T }Not true!  Jonah was just being pissy.  Understandably, of course. :) \textsubscript{11/17/14 5:24pm}}''

``I understand,'' says Dr. Gerhauser and she hands him a packet.  ``These are a variety of stimulants, if you have any questions, feel free to ask me.  We have some time before the procedure, so I can instruct you, as per your request.  Do you understand?''

``Yes.''

``Do you feel capable of learning right now?''

``Do I have a choice, really?'' says Jonah.

She stops and looks at him, ``Yes, of course.  Our deal was that I showed you how it worked, then you'd do this.  If you don't want to proceed...then we'll proceed with the other option.''

``No!  It's not- It's just that I need to sleep.  I'd like two days to sleep, but I'm assuming that's not an option.''

``The situation is pretty critical,'' says Dr. Gerhauser calmly.

``Alright then.  Yes.''

Dr. Gerhauser starts walking again and says, ``In regards to the the situation around SAC-04, I suppose you can write down your notes before we begin.''

Jonah jots down the notes: more than one Praetor, he mentions the name Supay and the white goo and notes that he has samples.  He says one of them negotiated with us and wanted to give up the Praetorship and Drake took it.  As a postscript Jonah notes, ``Agent Parvadi was not informed of the final point.''



Dr. Gerhauser walks Jonah to a lab room.  \hl{Rook is there, hooked up to electrodes again}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{11/18/14 8:36am}}\footnote{$\rightarrow$\textbf{Suko T }More shirtless Rook.  Never a bad thing.  Even better that he's being stoic and grim. \textsubscript{11/18/14 12:04pm}} but this time they look like needle-type connectors that have burrowed into his skin.  He has the grimmest look that Jonah has ever seen on him.  Rook half smiles and nods at Jonah.  Signe is also there, naked and in a tank.  She is twitching.  Jonah looks at her with a mixture of fear and anger.



Dr. Gerhauser escorts Jonah to a terminal and asks if he needs some water.  ``I'm going to give you a basic rundown and then leave you with the technical manuals.''

``That's fine, although I don't expect to understand all of this so I may need to go over this again,'' says Jonah.

``Certainly, I would expect nothing less,'' says Dr. Gerhauser briskly.  She starts drawing on the screen.  ``You wanted to know how to turn this on and off.  Imagine a circle with a hole in it.  Inside of another one, like so.  Now imagine that these are like wheels that can turn independently on their own axis.  Actually they are spheres, but let's keep this simple for now.  In one orientation,'' she draws the circles with the gaps aligned. ``they look like this.''  She draws another set with the gaps misaligned, ``and in another orientation they look like this. Now, if we were to put something here, like so,'' and she draws a bar through the aligned gaps ``they would turn together.  The way this works is the internal one is attached to the Agent.  And as it turns in the Agent, it will also turn in you.  The outer one turns relatively independently.  By inserting the locking mechanism, we can insure that these two turn the same way. The difficulty is that if we're in this position (misaligned) we need to move it in this position (aligned) in order to engage the lock.

``The other thing you need to know is that there are many of these and in order to align them we need to coerce them using an electromagnetic field.  What we use are tools that lets us visualize this on a large scale, and the alignments.  And what we need to do bring those fields into alignment.  That takes a lot of power because you don't have just one of these, you have on the order of a hundred thousand.''

``What do I actually experience?'' asks Jonah.

``Oh,'' says Dr. Gerhauser and punches some keys on the terminal.  Three images appear.  She points to the first, ``This is the baseline reading of your brain that I took some time ago.  Do you recall?  This is a baseline of Signe's brain.  And here is an abstraction of the lack of synchronicity between the two of you.''

``You're trying to get our brains fit together.''

``This is the field being generated by the Tank you're in and if we can bring those fields together, we can see the alignment occur and at that moment we can send the interlock signal to the device in your head.''

``But you don't know what I'm going to experience.''

``But you've already experienced this with Agent Parvadi.....I'm sorry.  When you made this request my understanding was that you wanted to know how to turn this machine on and off.''

``No I want to know how to turn on and off this \textit{adjustment}.''

Dr. Gerhauser looks puzzled.  ``This \textit{adjustment}?''

``When you make an Operator and Agent, their minds are in sync.  Their brains are in sync.''

``Well parts of them.''

``You change things about both people to make this happen, I want to know how to change it back.''

``You turn off the interlock,'' says Dr. Gerhauser.  

``Oh okay,'' says Jonah.

Dr. Gerhauser pulls out a device and hands it to Jonah. ``Here is your interlock signal.  It's encrypted. Certain machines can read it.  It should keep any random person from turning off your interlock.''

``Similar things exist for all Operator-Agent connections?''

``Yes of course.''  She pauses and asks, ``Do you have any more questions on a broad scale?  There are other matters I need to attend to.''

``How long does this take?''

``Effectively a couple of minutes once we were powered up to engage the synchronicity and engage the lock.''``Should I expect a similar sense of disorientation?''

``Yes.''``Is there anything I should know about Signe's mental state?'

Dr. Gerhauser looks at Signe and Rook looks up.  She says, ``We are uncertain as to what Signe's mental state is going to be.''

``Is it possible that she will be in such a state that I cannot communicate with her?  Is it contagious?''

``I expect that similar to operating on a badly wounded patient who would be happy to have the relief but has to go through some degree pain to get there.  You may feel some empathic response to this situation but I don't expect it to directly damage you any more than when Agent Parvadi damages you when she takes drugs.''

Jonah laughs.  

Rook starts pulling out electrodes.

\hl{``One other question,'' says Jonah.  ``Does Trenton know about this?''}\footnote{\textbf{Rebecca S. }Insert here all the snickering and side comments Suko and I were having.  Note that he asks about Trenton's state before making pass at Gerhauser.  Just saying. \textsubscript{11/18/14 8:38am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }In case you hadn't 'connected the dots' yet, Jaya is in imminent danger of sleeping with Trenton. Or at least having direct-ish access to exactly what that experience is. \textsubscript{11/18/14 11:50am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Whaaaaat?  What what what what?  No.  I think you meant to type *Jonah* in that comment. \textsubscript{11/18/14 11:52am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I forget... who is Jonah's Agent again? \textsubscript{11/18/14 12:04pm}}\footnote{$\rightarrow$\textbf{Suko T }+10  That would be the best Shore Leave ever. \textsubscript{11/18/14 12:05pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }no no no. Jaya and Jonah discussed this. He has to keep that shit in his head.  In HIS head. 

Suko \& I were discussing (cackling with glee?) about the Trenton/Jonah situation on Sunday but... we didn't really... extrapolate it all the way .... \textsubscript{11/18/14 12:05pm}}\footnote{$\rightarrow$\textbf{Suko T }Definitely there was cackling with glee.  And speculations about a Trenton/Jonah/Signe/Hayley quadrangle of doom. \textsubscript{11/18/14 12:13pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I think you're leaving out Jaya, Carruthers and Gerhauser. Quite a party! \textsubscript{11/18/14 12:55pm}}

Dr. Gerhauser says carefully, ``We have not spoken to Trenton directly about what is going on here with Signe.  He knows that she is compromised and that we are keeping her sedated to keep her from being further compromised.  He does not know the details of how far this is proceeding.''

``What am I allowed to tell him?''``We expect that once you're in position, she will become safe and she will be allowed to see him.  It will be some hours before we are ready to do this so you should spend the time to satisfy that you can turn the connection on and off.  I can show you demo and training modes to practice.''

``If I turn it off, does that mean she's again vulnerable?''

``Yes.''

Jonah sighs.

Rook leaves, and when it's just the two of them (and Signe) Dr. Gerhauser says, ``Thank you.''

``You can thank me after it's done.  We can have a drink,'' says Jonah.

Dr. Gerhauser cocks her head and looks at Jonah for a moment and then turns and leaves.




\sceneHeadline{Ops- Jaya, Hayley and Morgan (with a bit of Jari too) *}

Jaya takes Hayley to Medbay.  Swan takes a bit of time with Jaya's abdomen wound and patches her up.  As he's cleaning it, Jaya asks, ``I didn't get Grave Rot in there, did I?  Because I really cannot go through another.....''

``Uh, I'll let Dr. Gerhauser go over your medical condition with you once she's signed off on your readings-''

``And I'll need some more pain medication.'' interrupts Jaya.  Swan gives her something light.



They go to the RecCage and ring for Jari.  Jari arrives as Jaya is trying to open the cage with an improvised lock pick.  

``Can I help you?'' he asks.

``Um...yeah!  Morgan told us to uh....'' stalls Jaya.

``Re-gear,'' says Hayley.  Jari frowns at the pile of damaged VAC armor.

Jari hands a clipboard to Jaya and she frowns at it.   As diplomatically as possible, Hayley takes the clipboard, ``Sir, with your hand, perhaps it would easier for me to fill this out for you'' and she proceeds to fill out the requisition form quickly.  Unfortunately the only armor available is some combat vests, but we can resupply other items, especially ammunition and medkits.

``Best not to keep Morgan waiting,'' says Jari, pointedly.

Hayley attempts to tidy Jaya somewhat and we head to Ops.



Morgan stands as we arrive.  We exchange salutes.  She walks past us and says, ``Fall in.''  Hayley sees Carruthers in one of the tanks in Ops and she waves at her.  Carruthers smiles back.  Unfazed by seeing Carruthers naked while Carruthers is in her head, Hayley evaluates Carruther's naked body curiously and decides she looks pretty good out of the those ugly uniforms. There's a warm fuzzy feeling from Carruthers, along the lines of: \hl{``The pretty girl thinks I look good!  That's \textit{amazing}.''}\footnote{\textbf{Rebecca S. }So good! \textsubscript{11/18/14 8:40am}}\footnote{$\rightarrow$\textbf{Suko T }I agree, Carruthers is all kinds of adorable. \textsubscript{11/18/14 12:06pm}}



We head back to the train platform.  On the platform is Micah, Jayce and Douglas. Jayce is asleep on a bench.  Micah and Douglas are sort of facing each other, arms crossed, but their shoulders are relaxed.



Morgan says to Hayley and Jaya, ``Thank you for not taking too long.''

Jaya looks panicked.  She thinks she may have upset Morgan.  Morgan walks up to Micah and says, ``Sergeant, we're ready.''  Micah nods, Douglas nods...everyone turns to look at Jayce except Hayley (who is looking at Agent Morgan).



Douglas puts a hand on Jayce's shoulder and Jayce wakes up and stretches.  He looks around and has a moment of panic as he realizes everyone's looking at him, including all the scary women.  Then Douglas signs something to him and he relaxes.  ``Oh it's time?  Okay.  Shall we?''



Morgan walks off, and we fall in line behind her, Micah taking up the rear.  We all get in the elevator.  Jaya's very confused and looking around, trying to figure out what's going on.  As we travel down to the lab level, she thinks that maybe we're going to shoot Trenton and a happy smile spreads across her face.



They enter Trenton and Victor's lab.  The door opens and Victor is inside, clutching a wad of papers, and it's clear he's been clutching them for some time.  He's pacing back and forth.  Trenton is sitting in his section of the lab, his feet up, staring off into space.  Karil is there in full combat armor standing next to an interior door.



Jaya is looking at Douglas suspiciously.  Douglas is a little tense, and he seems to have a sidearm and grenade that we hadn't noticed before.



Morgan addresses Karil.  ``We are here to turn over Subject Gamma Alpha One.''

Karil nods and replies formally, ``I understand I am to release Subject Gamma Alpha One.''

Victor is still shuffling around nervously.



Karil turns and opens the door.   A woman walks out. She's tall, roughly Douglas' height (he's 6'3'' and she's around 6'), with long red hair in a braid.  She's very pretty, with light colored skin.  She looks much healthier than she did the last time we saw her.  She looks around the room.  Jaya smirks at her.  She smirks too and then smiles at Douglas. They salute each other, a salute that is different than ours, and start talking to each other.  Their language is still incomprehensible to us.



After a short exchange, she walks up to Douglas.  Jaya tenses.  Douglas hands her a short knife.  She tucks the knife into her belt and asks something of Douglas.  Douglas points to Jayce and she signs to him.  Jayce says, ``She wants to know where the 'Brave One''' is.''



Silence until Jaya says outloud, ``Is she talking 'bout Oliver?  He's fucking dead.  \hl{Too fucking brave for his own good.}\footnote{\textbf{Suko T }Awwww.... Jaya is so nice about Oliver... now that he's dead... \textsubscript{11/18/14 2:15am}}``  Hayley looks wistful at the mention of Oliver.

Jayce signs something to the woman and she frowns at Jaya.  She looks around the room again and pulls her knife out.

Jaya unholsters her gun and says, ``What is fucking going on?''  Hayley immediately steps in front of Jaya, between her and the woman.  Jaya looks peeved.



The woman grins evilly at Jaya and cuts off a lock of her red hair.  She plays with the hair a bit and then ties it together and tucks the knife away again.  Jaya hesitates and then holsters her gun. The woman walks over to Victor and leans down.  And leans down some more...and a little more (Victor is considerably shorter than her).  She kisses him softly on the lips, hands him the lock of hair, says something and then straightens and says something to Douglas.



Douglas turns to Morgan with challenging, ``You going to fuck this up?'' look.  Morgan is impassive.  Douglas and the woman leave.  As they pass, the woman gives Jaya a ``whatever'' look and smiles.  Hayley smiles back, a nearly-reflexive ``you're pretty'' response.  Jaya sneers and pulls a face behind the woman's back.  Jayce turns and follows them out and so does Micah.

Jaya throws a questioning look at Morgan, who instructs, ``Escort them off the base.''

Jaya shrugs and follows them, with Hayley behind her.  

As we leave, we hear the sound of a very crumpled wad of paper hitting the ground.  If we turned around we would see that Victor is bright red.




\sceneHeadline{Train Platform- Jaya, Hayley, Jayce, Rook, Douglas, Gamma Alpha One *}

We reach the train platform and Rook is waiting there.  Rook looks at everyone (Hayley salutes) and Rook nods to Douglas. Douglas and the woman board the train.  Jayce follows them onto the train.



Jaya's eye twitches a little but she says nothing and remains at parade rest with Hayley and Micah.  Jayce stands in the doorway of the train and looks back at Jaya.  She raises an eyebrow.  He raises one right back.  ``You know where to find me,'' says Jaya.



Hayley turns to Rook, ``Agent Rook Sir, should we be boarding the train?  It was not clear how far we needed to escort them off the base.''

``I've got it from here, Agent,'' replies Rook.

``Good.  Thank you, Sir,'' says Hayley and relaxes.



Jayce rolls his shoulders a bit and says, ``Say, uh, 'Hi' to your sister for me.''

Jaya smiles and then narrows her eyes suspiciously with a ``waitaminute'' look.



Rook says to Micah, ``I have them Sergeant, you are free to go.'' He nods at Jaya and Hayley in turn. ``Agent.  Agent.''  And Rook boards the train and enters the cockpit.



Jaya looks more grumpy than before and is giving Jayce the stink eye.  Jayce is looking a bit uncomfortable.  Jaya leans forward and asks, ``Where you guys headed?''

``Dunno, they wouldn't tell us where they were dropping us off.''

``Don't fuck up again,'' Jaya smirks.  She keeps staring at Jayce.

``Okay, I'll try not to,'' says Jayce.  He has a pained, ``I don't know what to say'' expression.



Hayley's been looking puzzled at Douglas and the woman since they left the lab.  She suddenly remembers what has been tickling her memory since she saw the two of them together.  Hayley looks straight at Douglas and says sincerely, ``I apologize for shooting you.''

The doors start to slide shut and just before they close,\hl{Douglas says clearly, ``You are forgiven.''}\footnote{\textbf{Suko T }OMG I just realized- is Jayce totally pissed at Douglas now?  If Douglas could speak our language this whole time, Jayce didn't need to risk life and limb and be forcemarched up and down a mountain... \textsubscript{11/19/14 10:46am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Someone should go ask him! \textsubscript{11/19/14 11:33am}}

Hayley is touched and pleased.  

After the doors close, Jaya suggestively licks her lips and winks at Jayce through the window.

The train pulls out of the station.



Micah leaves.

Jaya doesn't move from that spot and lights up one of the cigarettes she got from Lackovich. Hayley waits for a moment and then asks quietly, ``Do you want me to stay, Sir?''

``No.  You go pass out.  Do Carruthers.  I don't care.  I'm going to stay here.  It's cool.''

``Do what?'' says Hayley, confused. There's a wave of embarrassment from Carruthers and Hayley finds herself blushing, which confuses her even more since she rarely blushes.  She wonders if she's feverish.

``Just get out of here, Hayley.  Fuck off.'' says Jaya.

``Yes, Sir.'' says Hayley.



Hayley is exhausted.  She checks in on Javier briefly to assure herself/Carruthers that he's okay.  Carruthers is out of the tank and finds her there.  Carruthers hugs Hayley.  Hayley is surprised but hugs Carruthers back awkwardly.  There's a weird feedback loop where they can both sense that this act is not natural for either of them, but they are forcing themselves participate to please/comfort/assure/connect with the other person.  Their mutual discomfort actually makes it more reassuring.



Hayley showers, stows away her gear and passes out on her bunk.




\sceneHeadline{Training Room- Jaya and Morgan *}

Jaya has been working through several smokes, still not budging.  About 45 minutes have passed when Jaya looks around and sees Morgan standing at the top of the ramp.  She's in workout gear.   Morgan asks, ``Everything alright, Agent?'' 

Jaya stubs out her cigarette and clears her throat. ``Fuckin' fine.  Um, sorry, I know I'm not supposed to smoke-''

``Thank you for keeping it outside the base,'' says Morgan.

``Happy to oblige,'' says Jaya.

``Up for training?''

``Fuck yeah,'' says Jaya.  They start walking to the training room.  

``Could you just,'' Jaya gestures to a \hl{spot vaguely between her actual ab wound and her hear}\footnote{\textbf{Suko T }\textless 3 \textless 3  Awwww.... Jaya doesn't know what heartache feels like... \textsubscript{11/18/14 2:20am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It's *like* getting punched... \textsubscript{11/18/14 12:06pm}}t, ``uh, avoid this uh, spot.  I mean, fuck up everything else, but just try to avoid here..''

``That's fine.  If you feel it start to bleed again, you should let me know.  I don't want to damage you permanently.''

Jaya laughs and moves to slap Morgan on the arm and thinks the better of it just in time.  Jaya changes the gesture to run her fingers through her (own) hair casually.

``So the mission was a success?'' asks Morgan.

``Well other than our one casualty, there was really fucking optimal performance from all team members.  I would really like to commend even the new, uh, uh....'' Jaya makes a gesture about Breccan's height.  

``Constables?'' suggests Morgan.

``Uh, just the one, since we lost the other.  But anyway, she did an excellent job, we should consider her for filling a team member position member role...there is an opening....''

``I look forward to your report.  If she did perform particularly admirably, it would not be remiss for you to write her a commendation.''

Jaya pauses and then says confidently, ``Yeah!  Someone will write her a commendation.  It will be fucking awesome.'' 



They get to the training room and start wrapping their fists.

Morgan says conversationally, ``It's good to see you take up more of a leadership role.''

``I'm a born leader! Just getting into my prime,'' brags Jaya.  She tries to take off her shirt but it's stuck to her with dried blood and bandages.  She decides to leave it on.  

Morgan starts throwing a few jabs at Jaya.

``I just really feel like- uh- whoa!'' Jaya's still on the tail end of the drugs so she's feeling pretty good but she's having a hard time both sparring and speaking at the same time.

``You really should think about writing the occasional commendation,'' says Morgan.

``Yeah!  A commendation will be written for- for- uh... fuck!  Um, the fucking awesome Constable that assisted us.  I will see that something, `` Jaya ducks a punch, ``is written.  Uh, where do I turn it in?''

``You can submit them to myself, Larissa or Agent Rook.''

``I'll get it to Larissa, ASAP, tomorrow.''

Morgan picks up the pace and Jaya struggles to keep up.  Jaya can tell that Morgan's taking it a bit easy on her.  Jaya gets angry and goes at Morgan harder.

Morgan says, ``There is one matter that I'd like to bring to you if you are intent on the path to become a better leader.''

``Yeah!  Fucking bring it.''

``Well, as I'm sure you know, team discipline is important.''

Jaya actually disengages and steps back, ``You know, I've been talking to Jonah.  I've had this conversation with him lots of times.  He just will not fall in line-''

``This is not about Jonah.'' Morgan interrupts.  ``You have to take care of your team.  Just like you take care of your rifle, your truncheon, your arm...your base.  So when something stops working you fix it.  Good leaders fix that.''

``Yeah!  I'll fix everything!'' Jaya disengages again so she can think.  ``Uh, is this about Hayley?  Because she's really been progressing well-''

``This isn't about Hayley,'' interrupts Morgan again.  Jaya is at a loss.  ``So I'm going to ask you to complete a mission for me. Which I think you will find useful to you as a leader.''``Yeah!  Is there extra hazard pay?''

``I'm going to outline this mission for you.  It's very simple, you only have to do three things.  But I understands woman of our nature can become passionate-''  

Jaya looks a little surprised and disturbed.

Morgan starts sparring again and says, ``So feel free not to hold back.  If you feel the need.''  

Jaya nods a little.

Morgan continues, ``So we have a bit of an issue amongst base personnel that I'd like resolved and I'd like you to resolve it.''

Jaya is barely deflecting Morgan's blows, looking very confused.

``You only have to do three things for me.''

``What!  What!  Just fucking say it!'' yells Jaya.

Morgan is clearly trying to assess if she should even ask this but then seems to shrug and says, ``Okay. The first thing is you have to do is ask for a second bowl of gruel.''

Jaya swings at Morgan with the metal arm. 

``Just eat all of it. Eat all of the first bowl and the second bowl.  Say please when you ask for the second bowl.''

Jaya swings at Morgan's face.  Morgan is clearly on the defense.

``And the third thing is that when you are done with those two things, is to say thank you.''

Jaya throws up her hands and backs away. ``What the fuck is this?  Rook tried to set me up with fucking Jari.  I'm not into that.  Jari freaked the fuck out.  He's taking it out on me!  I don't understand.  This is fucking bullshit!''

``I agree,'' says Morgan.  Jaya gapes at her, her momentum temporarily lost in surprise.  Morgan continues, ``Which is why you're going to fix it.  Because you have two choices here.  Either fix it, or run away from it.  And I don't take you for a coward.''

``I'm not a fucking coward but I'm not sleeping with fucking Jari!!''

``I didn't \textit{say} sleep with Jari.''

\hl{``But he's going to get all fucking weird again when I'm all 'please' and 'I love your fucking gruel'  Fuck that, man!  He's going to think I'm fucking into gruel or something!  No!!''}\footnote{\textbf{Suko T }\textless 3 Jaya \textsubscript{11/18/14 12:18am}}

``I don't care if you don't like his gruel.  I don't care if you think he was coming onto you.  \textit{I don't care about any of this}.  But what you \textit{will} do is ask for more, say please and say thank you.  Because he's on your team, whether you like it or not.  If it actually becomes a problem, if \textit{he} becomes a problem, then we'll fix it.  But right now the issue is with \textit{you}.''

Jaya curses and lunges forward and swings at Morgan.  Morgan is a little caught off guard.  Jaya spits, ``Fine'' and then re-engages and they spar full out this time.  Morgan starts even provoking Jaya to step it up even more, saying things like ``I know you can punch harder than that!''

Jaya works herself to exhaustion.  



Morgan hands her a water and says, ``I have to go take care of some matters, we may have a potential security situation.  Go get cleaned up, get plenty of rest.  I expect that issue to be taken care of by morning mess tomorrow.  Is that understood?''

``Understood,'' grumbles Jaya, not looking at Morgan.

``Good job today, soldier,'' says Morgan and she leaves.




\sceneHeadline{Bunk}

Jaya comes in after sparring with Morgan and wakes Hayley up and has her start writing some commendations.  Between Jaya not being able to remember Breccan's name and Hayley's exhaustion, it takes a while to figure out that needs to be done but Hayley eventually starts writing, yawning constantly.  Jaya has Hayley write commendation letters for Breccan and Javier.

She asks Hayley, ``Should we write one for Lackovich?  Do you think that would go to her head?  I don't want her getting any fucking ideas...''

``Well she showed a lot of leadership when we-'' says Hayley.

``No no.  Just say she followed orders really well.  She had our back.  Yeah. Write that down,'' says Jaya, tapping the paper.

Jaya falls asleep before Hayley finishes.



Dr. Gerhauser finds Jonah and tells him, ``If you have nothing else to do, you should get some sleep.  We are experiencing some power issues.  So it's going to be a little while before we can do this.''



Jonah heads back to the bunk to find Hayley still awake, slowly writing the letters.  She looks up as he enters and looks a little dopey as she smiles sleepily at him and says ``Hi'' softly.  Jonah says shortly, ``Hi'' and he goes to sleep.



Hayley finishes the letters and stacks them neatly for Jaya and goes to bed.  She's barely asleep when the alarm goes off.  ``Warning. Warning.  Code Gold initiated.  Operator Gemayel, report to Lab \_\_\_.  All other personnel commence lock down.''



We all get up.  Jonah gets up immediately and is mostly ignoring Jaya's questions/exhortations, ``What the fuck did you do?  Jonah?  Go!  Go!''  He doesn't reply.  \hl{Hayley is moving very slowly but she helps Jaya get dressed and geared up.}\footnote{\textbf{Rebecca S. }clearly you should bump Lady's Maid. Such skill! \textsubscript{11/18/14 8:53am}}




\sceneHeadline{MedLab *}

Jonah arrives to find several people in MedLab standing in front of the tank.  Morgan, Rook and Dr. Gerhauser.  Signe is in the tank, but she is awake and looking at Jonah.  Then she looks back at Morgan and smiles creepily in a Octavian/Octavia way.  She twitches oddly and then smiles again.  

Dr. Gerhauser asks Jonah, ``Are you ready?''

``Yes,'' says Jonah.

Morgan says to Rook, \hl{``This may be our last time to talk face to face.''}\footnote{\textbf{Suko T }Ooooh I get what this meant now.  I was so confused at the time!  I thought she was talking about her and Rook. \textsubscript{11/18/14 2:28am}}\footnote{$\rightarrow$\textbf{Rebecca S. }I *think* I know what you're saying, but could you lay it out for me? \textsubscript{11/18/14 8:54am}}\footnote{$\rightarrow$\textbf{Suko T }I thought that Morgan was saying she'd never talk to Rook face to face again. But she was, I presume, talking about us and Octavius.  I could be wrong about the later conclusion but at least it makes wayyyy more sense for the subsequent conversations!  

Ion had the same misunderstanding as I did, which is why some of Jonah's questions to Rook sound odd.  When he talked about not getting a chance to talk to Rook later, it's because he/Ion thought Rook was going away somehow during this process. \textsubscript{11/18/14 12:11pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Ahhh! I'm sorry. That's my bad. \textsubscript{11/18/14 12:56pm}}

``That is true.  Is it worth it?'' asks Rook thoughtfully.  They stand there side by side and contemplate the tank for a while.

``Sirs?  Do whatever you have to do to keep this place safe,'' says Jonah.



Signe's hand reaches up and taps on the glass of the tank, pointing at Jonah.

Morgan says, without turning around, ``Operator, what do you think?  Should we talk to her?''

``What are the odds of this succeeding?'' asks Jonah.

``I think we can succeed but we should act now.''

``Is there any benefit to talking to her?'' asks Jonah.``It's always good to know your enemy,'' Morgan smiles.

``Does it increase their odds of finding us?'' asks Jonah.

Jonah sees Rook's mouth quirk up in a half smile.

Morgan takes a deep breath and sighs.  ``I suppose you're right.  Report to Ops.''  She looks at Rook and says, ``Do it.''



Rook says, ``Follow me. Do you have any last minute questions?''

``Just one.  If there's a chance I don't get to ask you afterward, if my understanding is correct.''

``I think we're safe on that front but if it will make you feel better, go ahead,'' says Rook.

They step into the elevator.``The other Praetors, they are nothing like you,'' says Jonah.

\hl{``We're all different,'' says Rook calmly.  ``Everyone's different.''}\footnote{\textbf{Rebecca S. }for some reason, my favorite line of the night. \textsubscript{11/18/14 8:55am}}

``Apparently,''  says Jonah and then he lapses into thought and doesn't speak for a while.

Rook says, ``That not really a question, that was a statement.''

``Did you know them?'' asks Jonah

``Some of them.''

``The two we met?''

``Based on the report Carruthers was given, the one named, inaccurately I believe, Supay, was assigned to another SAC that I was familiar with.  Also,'' says Rook cheerfully, ``the samples you brought back were fascinating!''

``I hope you'll have a chance to explain them.''

``So do I!''

The elevator doors open.




\sceneHeadline{Ops }\textbf{\hl{*}}\footnote{\textbf{Nathaniel Ford }Though, technically this would also include the 'first' scene of the next session. \textsubscript{11/18/14 4:14pm}}

Once she's dressed, Jaya starts marching off confidently and then pauses and looks at Hayley.

``We should report to Ops for assignment,'' says Hayley quietly.

``Exactly!'' says Jaya and turns around smartly and starts heading to Ops.



In Ops, there is a lot of activity, no one's really talking to Jaya and Hayley.  Swan and Larissa are there.  There is the sound of things powering up.  Carruthers is there, but she's in uniform.  In the absence of other orders, Hayley guards the door.  Jaya is unsure what to do but too proud to ask for direction.



Jonah and Rook walk in.   Rook points and says to Jonah, ``You should probably use Tank 1.''



Rook says to Jaya, ``Agent, may I speak with you outside?''  He says to Hayley, ``Agent, stay here. Guard Operator Gemayel.''  Hayley nods and goes to stand by Tank 1.



Rook pulls Jaya into the hall. ``Agent, you will need to report to Lab \_\_\_.  There is a subject in a Tank there.  Should that subject escape, it is to be constrained with extreme prejudice.''

``Terminated?'' asks Jaya.

``Only if absolutely necessary but use every single precaution you have.  Micah will meet you there.''

Jaya nods.

``Do not inform Agent Hayley,'' says Rook.

``But Hayley's going to be in that room,'' Jaya points to Ops.

``If you should come into contact with Agent Hayley, I do not wish you to tell her of these orders.  Do you understand?''

``Sir!  Yeah,'' says Jaya, half salutes and saunters off.



Rook comes back into the room.  They put \hl{Jonah in the tank}\footnote{\textbf{Suko T }Hayley certainly doesn't look away from Jonah's nakedness.  Just sayin'. \textsubscript{11/18/14 12:56am}}\footnote{$\rightarrow$\textbf{Rebecca S. }oh Hayley.... \textsubscript{11/18/14 8:56am}} and power up.  




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 28
\item Refresh: Sidearm 3 (Jaya)
\item Challenge 2: Notice.  Nose for Breadcrumbs 2 (Hayley) → Matched
\item Challenge 1: Notice. Agent 1 (Hayley) → Matched
\item Challenge 4: Stop the zombies from getting up the building.  Left hand 3 (Jaya) + Vacuum-sealed Armor 3 (Jaya) → Matched
\item Refresh: Bad Cop 3 (Jaya)
\item Refresh: Bodyguard 2 (Hayley)
\item Refresh: Vigilant 3 (Jonah)
\item Challenge 2: Notice. Trigger Reflex 2 (Jonah) → Matched
\item Refresh: Air of Command 2 (Jaya)
\item Challenge 4: Kill the zombies holding onto Breccan, but Breccan and Jaya get dragged to the Plaza.  Rifle 2 (Hayley) + Hush Radio 1 (Hayley) + Hush Radio 1 (Jaya) + Heavy Pulse Rifle 3 (Hayley) → Matched
\item Refresh: Small Arms 2 (Jonah)
\item Challenge 2: Dodge.  Athletics 3 (Hayley) →  Overcome! \textbf{2 VP (Hayley)}
\item Challenge 1: Notice.  Bodyguard 2 (Hayley) →  Overcome! \textbf{1 VP (Hayley)}
\item Challenge 2. Dodge.   Flaw 1: Cauterized abdomen wound (Jaya).  Thrown back
\item Refresh: Left Arm 3 (Jaya)
\item Challenge 1: Notice.  Grace Under Fire 1 (Jonah) → Matched
\item 14 tokens
\item Challenge 2: Shoot the creature and not Douglas.  Small Arms 2 → Matched
\item Refresh: Athletics 3 (Hayley)
\item Challenge 2: Cinematically cling to edge of hole.  Side Arm 3 →  Overcome! \textbf{2 VP (Jaya)}
\item Refresh: Heavy Pulse Rifle 3 (Hayley)
\item Refresh: Side Arm 3 (Jaya)
\item Challenge 1: Notice.  Sent back.
\item Challenge: Notice 1.  Streetwise 1 (Jonah)
\item Challenge 1: Notice.  Sent back
\item Refresh: Social Chameleon 2 (Jonah)
\item Reduce Flaw:  {\color[RGB]{255,0,0}Flaw 1: Cauterized abdomen wound (Jaya).}   Medkit 1 (Jonah) → Flaw 0
\item Pool 16 (plus 1 flaw minus \_\underline{ 6 }\_ tokens for SAC-09 scenes) = 11 more backlash
\end{itemize}




\jumpHeadline{Flaws left at end of session }

\textbf{ {\color[RGB]{255,0,0}FLAW 1: Shoulder \& Neck wound (Jaya)} }




\jumpHeadline{VP Totals }

Hayley 3

Jaya 2

Jonah 0




\jumpHeadline{Quotes: }

\quotedDialog{
Ion: {[}Level 1 notice challenges{]} tend to be stuff that would be cool to know or we could take advantage of if we wanted to.  If it's actually threatening, it's not a one.

Rebecca: But I'm not worried about \textit{us} getting hurt.  I'm worried about the Red Shirts.  He'd totally kill a Red Shirt on a 1.

Nate: I'd kill a Red Shirt without even having a Challenge.\\[4mm]
}

\quotedDialog{
Ion: It's literally only a flesh wound.

Rebecca: Yeah but it's some important flesh there.  We'll wait until Rook fixes it.  He'll make it better.\\[4mm]
}


Guy in robes: I'm terribly sorry.  I seem to have forgotten my manners.  And my name.


\quotedDialog{
Suko: You're a boy so you get to be short and dead.

Rebecca: He's nice.  So he's short.\\[4mm]
}

\quotedDialog{
Nate: The alarm goes off.

Suko: Yay!  Hayley will never get more than 30 minutes of sleep. \hl{I'm aiming for 45 minutes next time.}\footnote{\textbf{Nathaniel Ford }Aim high, Hayley. Aim high. \textsubscript{11/18/14 12:03pm}}
}

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:26pm
\end{flushright}

