\setcounter{chapter}{ 36 }
\chapter{\textbf{``Backlash''} }




\begin{center}
 {\LARGE \textbf{(aka. ``Eating Crow'')} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} Nov 19th, 2014



Sex!  Angsty discussions of feelings!  Shame and guilt!  Fights in the hallways!  Tough choices!  Babies!   Was this the Monsterhearts episode of 4T?



Jonah successfully becomes Signe's Operator and has sex with Carruthers.  Who is still sharing brainspace with Hayley.  Awkward!  Jaya completes her special gruel mission.  She also learns that she's pregnant.  Trenton and Dr. G both apologize to Hayley, which mystifies her.  Hayley is told she's got the emotional development of a 9 year old.  This probably explains a lot for some people.



Operator/Agent thought code (reclaimed green for Signe)

 {\color[RGB]{74,134,232}Jonah to Jaya} 

 {\color[RGB]{255,0,0}Jaya to Jonah} 

 {\color[RGB]{230,145,56}Hayley to Carruthers} 

 {\color[RGB]{153,0,255}Carruthers to Hayley } 

 {\color[RGB]{194,123,160}Jonah to Signe} 

 {\color[RGB]{106,168,79}Signe to Jonah} 



\noindent\hrulefill





\textbf{{[}11 Tokens Backlash{]}}


\sceneHeadline{T-Lab- Jaya}

Jaya heads down to T-Lab.  Micah is there in full combat armor (no helmet) and a rifle.  In the lab is a Tank with a naked Signe inside.  The equipment looks cobbled together, not like the Tanks in Ops.



Signe is awake and locks eyes with Jaya when she enters.  Jaya looks Signe up and down, whistles and says, ``Ah!  So she's the one who's got Hayley hot and bothered.''  Jaya looks over at Micah with a conspiratorial wink.  Micah looks at Jaya, a bit disconcerted, and looks back at Signe.



Signe looks at Jaya with a menacing teeth-baring smile (not her usual expression at all) and then suddenly punches the side of the Tank.  The Tank doesn't crack but Micah jumps slightly and both he and Jaya go into a more combat ready stance with weapons pointed at Signe.  It doesn't seem possible but Signe's grin gets even wider.  It looks especially weird through the distortion of the glass.



Jaya edges toward Micah and says in a loud whisper, ``What the FUCK is going on?''

\hl{``I don't really 'science'}\footnote{\textbf{Suko T }So much personality showing for Micah this episode.  If this were a tv show, I'd be worried that he's gonna die soon.  If we start getting any of his backstory, I'll know for certain.  Writers always like fans to start caring before they break our hearts. \textsubscript{12/02/14 11:26am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Hey, Jari got some backstory out and doesn't seem to be in any immediate danger... \textsubscript{12/02/14 12:27pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }If he keeps messing with Jaya, he will be \textgreater :-/ \textsubscript{12/02/14 12:39pm}}...but we have a security situation,'' says Micah, still watching Signe warily.




\sceneHeadline{Ops}

Jonah climbs into Tank 1.  Rook returns to Ops and he and Larissa start going through the power up protocols.  They say, ``Flooding causeway 3 and 4.  Causeway 1 and 2 clear.  Flooding Causeway 1.'' There is a display that Hayley figures out corresponds with some of the protocols they are going through, tracking the progress.



To Jonah, this feels similar to when he was first connected with Jaya and the later the Operation to find Oliver.  Jonah is trying very hard \textit{not} to think about how similar this is to those two occasions.



For those in Ops, midway though, there is a strange 'bong' noise.  Larissa looks panicked and Rook goes very still.  It repeats twice and then Rook hits something on a console and it stops.



Hayley asks, ``I am not familiar with that alarm sound, what does it mean, Sir?''

Rook tells her, ``Hold your position.''  He turns to Dr. Gerhauser, ``Dr. Gerhauser, proceed.''

A few moments later, Morgan walks in and Rook walks up to her.

Jonah can feel things happening. 

As if continuing an interrupted conversation, without any preamble Rook says, ``We have only eight.''

``I don't see another option,'' replies Morgan.

``Neither do I.  Launching LRMs 1 and 2,'' says Rook.

At this point, Dr. Gerhauser says, ``We are prepared to engage interlocks.''

Almost in unison though Rook is slightly faster, he and Morgan say, ``Do it.''



Jonah falls down the rabbit hole.




\sceneHeadline{T-Lab- Jaya}

Jaya is watching Signe who is still staring her down.  Though Jaya can't hear her, Signe mouths something that Jaya is pretty sure is, ``I am going to eat your face'' and Signe punches the side of the tank again.  Then suddenly her aspect changes and she gets a weird panicked/contorted look on her face.  She begins to thrash around and convulse.  She claws at the top of the Tank.




\sceneHeadline{Ops }

Jonah gets a throbbing pain in his head, which is different from what happened with Jaya.  He gets the strange sensation of both falling and having something fall toward him at the same time.  There is a flood of confused emotions, mostly panic, but also an abiding sense of loneliness mixed with a fear of losing that again, but also wanting to be alone.  Contradictory feelings, very messy.  Lots of things that are directly pointed at each other.  



There's a sensation that his brain later tries to give a visual component to.  He sees a reflection of two Signes, one in a mirror, and they are each taking distinctly different actions.  The one in the mirror is incredibly pissed.  The one outside the mirror is begging for mercy and trying to get away but can't actually do so.  The mirror starts cracking.  He feels himself violently punching something \textit{hard}. He can't quite figure out if it's him, or himself imagining punching something, or if it's someone else (he decides it's the latter).



He comes to in the Tank and is now actively Operating Signe.  He can feel her flailing, punching and scrabbling at something, completely panicked.

 {\color[RGB]{194,123,160}::Calm down.  Take a deep breath.::} 

There is a long wailing cry of anguish in his head and  {\color[RGB]{106,168,79}::What the fuck is going on???::} 

 {\color[RGB]{194,123,160}::You're alive.  Concentrate on your hands and feet.  Do you know where they are?  Can you feel them?  Then you are alive.::} 

Jonah gets a strong flash of a younger, more manly, glowing Trenton, saying almost those exact same words.  There is an incredible wave of fatigue from Signe.

 {\color[RGB]{194,123,160}::You're doing great.::} 



In Ops, there is a distant thump, almost like thunderclap.



Signe starts falling asleep.  In the Tank her body starts going limp.  Jonah tries to reinforce that image of Trenton, telling Signe to hold onto it.  He attempts to slow/ease her descent into unconsciousness by talking to her more and more quietly.




\sceneHeadline{T-Lab- Jaya}

Micah has his rifle trained on the Tank and asks Jaya tightly, ``Do you think you can subdue her?''

Jaya rolls her eyes, ``Of course I can.''

``Because our orders were to subdue her-''

``I fucking know our fucking orders!''

Without taking his eyes off the Tank, Micah swallows and says through gritted teeth.  ``I know you know our orders.  I wanted to know which one of us was going to do it so I knew which one of us was going to lower our weapon.  \textit{Ma'am.}''

Jaya smiles and says, ``I got this.  I \hl{worked with}\footnote{\textbf{Rebecca S. }My brain and my mouth don't always work well together, but I distinctly remember *intending* to say ``I owe it to Hayley''  ... but this reads better, so leaving it ;) \textsubscript{12/02/14 7:43am}}\footnote{$\rightarrow$\textbf{Suko T }Aww, ``owe it to Hayley'' would be so sweet!   Jaya's a big softie inside, isn't she? ;) \textsubscript{12/03/14 3:16pm}} Hayley.''

Right about then, Signe slowly stops thrashing.  Bubbles escape her mouth and after a minute she goes limp.



Jaya can feel that Jonah is in a state of distress, enough that it's hard to suppress or push away.  Jaya sends back anger.  She can catch maybe a quarter of the exchanges between Jonah and Signe.  She somehow finds herself thinking of Trenton and idly wondering- ``\textit{Is} he sexy?''



\hl{Jaya lowers her gun and says in horrified realization, ``Oh fuck.''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{11/30/14 3:41am}}




\sceneHeadline{Ops }

Dr. Gerhauser reports, ``We established a connection.  All interlocks are engaged.  It looks like a success.''

Rook says, ``I concur.''  He turns to Morgan and reports, ``One hit.''

Morgan nods and asks Rook, ``I trust you can clean up here?''  Rook nods.  Morgan leaves.



Dr. Gerhauser turns on the Tank comm and asks Jonah, ``How are you doing in there?  Your signs look good.  Considering.''

``What happened?'' asks Jonah. 

``Rook confirms that at least for the time being they have lost the signal.''

``They need some number of connections?''

``They were about to get three, but now they are solidly in the 1-2 range.''

``Good.  Tired,'' says Jonah wearily.

``It will be a little weird, but we're going to transfer you to one of the MedTanks so that we can monitor you overnight.  But you can sleep in there.  If you like.''

Jonah isn't happy about that but agrees and gets out of the Tank slowly.  Carruthers brings him a robe.  Hayley watches but does not move to assist Jonah.  Though he is covered in goo, she is finding it less gross than she usually would.  Carruthers is not turned off by the slime.




\sceneHeadline{T-Lab- Jaya}

Morgan walks in.  Jaya is standing at ease...her version of it anyway, fidgeting with an unlit cigarette.  Morgan looks at Jaya, looks at Micah, salutes him and looks back at Jaya.  Jaya hides her cigarette.  Morgan studiously ignores the cigarette and asks, ``Situation report, Agent?''

Jaya salutes Morgan, ``Looks good.  She punched the Tank twice but it held.  Everything's just fine,''  reports Jaya.  One eyelid droops more than the other.

``Good.  When's the last time you got some sleep?'' asks Morgan.

``Right before this thing happened there was sleeping and....I don't know before then,'' Jaya can feel exhaustion from Jonah and Signe exacerbating her own fatigue and her eyelids twitch even more.

``Do you have another half hour in you?''

``Fuck yeah!'' says Jaya.  She nods and her whole body sways with it.

``Swan will be coming to take Signe to MedBay.  Just make sure she's secure in her bed.  I don't want her escaping.''

``Definitely secure,'' yawns Jaya.

``Agent,'' Morgan nods to Jaya and then nods to Micah, ``Soldier.''

Jaya nods at Micah and says, ``Soldier'' with a smirk.

Micah gives her a look and asks pointedly, ``\hl{What does three up and three down mean to you, Agent?}\footnote{\textbf{Rebecca S. }I still don't get it... \textsubscript{12/02/14 7:45am}}\footnote{$\rightarrow$\textbf{Suko T }https://www.youtube.com/watch?v=U034RLQov\_w \textsubscript{12/02/14 11:41am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Within context, it means he thinks you're a transit cop and he works for a living. ;-) \textsubscript{12/02/14 12:25pm}}''

Jaya looks at him blankly.

``I thought so,'' says Micah and turns back to the Tank.

Swan comes in about 30 minutes later.  Micah stands guard while Swan and Jaya help her out of the Tank.  She's asleep, even adorably snoring a little.  Jaya pats her on the head.  Swan cleans her up, bandages her hand (which is pretty fucked up) and straps her down.  Remembering what was effective in tying Hayley down, Jaya double checks the straps, tightens a few, and makes sure that Signe is secured.



They bring Signe down to one of the MedBay rooms (the one that Hayley was in last time).  Duty discharged, Jaya heads back to her bunk and goes to sleep.




\sceneHeadline{MedBay- Jonah, Hayley, Carruthers and Dr. Gerhauser}

Dr. Gerhauser escorts Jonah down to MedBay.  Carruthers and Hayley go with them.  These Tanks seem like an older version of the other Tanks.  



``Take Tank 1,'' directs Dr. Gerhauser.

Jonah says sleepily, loudly enough that everyone in the room can hear, ``That drink is going to have to be the good stuff.''

From Carruthers, Hayley catches a very analytical series of thoughts  {\color[RGB]{153,0,255}::What does it mean? What does he mean by that?::}    All Hayley is thinking is  {\color[RGB]{255,153,0}::Eww.  Drinking.::} 



The last thing Jonah sees before he passes out is a vision of three women: a tall gorgeous woman in a lab coat, a short cute woman in undress fatigues, and another tall gorgeous woman in a fitted BDUs, all watching him as he lies there naked in the Tank.



Carruthers is distracted by all this and there is a flash of embarrassment from Carruthers as she realizes that Dr. Gerhauser has turned to her and said, ``I told you.  You too.''

Carruthers starts disrobing.  Hayley steps forward and assists her with practiced ease, carefully folding Carruther's clothing and stacking it neatly on her cart.

Dr. Gerhauser watches for a moment, seems a little puzzled/surprised, and then says to Hayley, ``Can you make sure she gets into the Tank alright?  I just need her monitored overnight.''

``Yes,'' says Hayley.

``Thank you,'' says Dr. Gerhauser and leaves.

``Are you feeling alright?'' Carruthers asks Hayley.

``Very exhausted.  I really need sleep.''

``Oh, I'm sorry,'' says Carruthers and there is a flash of empathy.  

Hayley is puzzled by it but attempts to explain further, ``I'm not used to missing sleep.''

Hayley helps Carruthers climb into the Tank and once it is clear that she isn't needed in the MedBay anymore, she goes back to her bunk and goes to sleep.




\sceneHeadline{Bunk- Hayley and Rook}

Twenty minutes after she closed her eyes, Hayley is gently shaken awake.  A soft voice says, ``Agent Hayley?''  Hayley struggles to open her eyes.  The room is not as dark as it should be- there is a soft blue glow faintly illuminating the room.  

Rook says quietly, ``I'm very very sorry for waking you up but I thought you might want me to inform you- You don't need to get up- but I want to let you know that Signe is in MedBay One.  She's gone through some trauma.''

Hayley makes a sleepy distressed noise.

``We've confirmed that she's okay now.''

``Is she-?  Happened?'' says Hayley semi-incoherently.

``Trenton is there and Dr. Swan.  I do not wish to wake your commanding officer.  But if you wish to be there, you have permission to do so.  But you can continue to sleep if you wish.''

``No no, I want to see her,'' Hayley tries to get up and fails.

``Would you like help?'' asks Rook.

``Yes please.''

``How would you like help?

``I think... getting upright, please.''

Rook gently assists her to her feet.  Hayley staggers and almost falls over, all of her usual grace gone.  She eventually manages to keep herself upright, probably by leaning on a table.  \hl{Perhaps it's just the exhaustion but part of the room seems more blue and the other part more red}\footnote{\textbf{Rebecca S. }I just like the idea now of night-light Rook... \textsubscript{12/02/14 7:48am}}\footnote{$\rightarrow$\textbf{Suko T }http://www.youtube.com/watch?v=NhjSzjoU7OQ
(or if that doesn't work, TMBG's Birdhouse In Your Soul) \textsubscript{12/02/14 10:01am}}.  Maybe purplish?  Hayley notes it but puts the observation aside for puzzling over later.  Hayley starts moving toward the door and then stops and looks down at herself.  ``Oh.  \hl{Perhaps I should put on clothes.''}\footnote{\textbf{Suko T }For the record, she's not naked, she's just sleeping in the equivalent of a nightgown and underclothes.  Not indecent but of course entirely inappropriate for wearing outside of the bunk. \textsubscript{11/30/14 1:37am}}

``Stay there,'' says Rook.  He goes to her locker and opens it.  ``I admire how neat you are.''

``Thank you,'' says Hayley, stifling a yawn.

He pulls out a BDU.  Hayley starts trying to dress herself but keeps falling asleep midway through, even in the middle of buttoning her shirt.  After the third time, Rook asks, ``Are you sure you don't wish to sleep?  It's totally fine if you do.''``I really want to, but I'll sleep when I know she's okay.''  Hayley takes a deep breath and attempts to focus enough to finish getting dressed.  Once she starts stands and starts walking she wakes up a little, but her limbs feel leaden and she's dizzy and lightheaded.  



When they step into the hallway, the light returns to normal.

Rook says to Hayley, ``If you want to sleep down there, Swan should be able to provide you with a cot.  If you need anything further let me know.''

``Thank you.  I- I had something to tell you but I forget...'' Hayley says helplessly, clearly not able to think clearly.

Rook smiles at her, ``You'll remember later.'' he says reassuringly.




\sceneHeadline{MedBay- Hayley, Signe and Trenton}

They get to MedBay.  Trenton is sitting in a chair next to Signe's bed, looking distinctly unhappy.  He doesn't look up or acknowledge Hayley at all.  Other than noting that he's there, Hayley doesn't pay him any mind either.  All of her attention is on Signe.



She walks straight to Signe and hesitantly pats her hand, like a frightened little kid might when faced with someone sick in the hospital.

Trenton looks up, ``Oh.  Thought you were Swan.  What are you doing here?''

``Hmm?''

``Did they wake you up?  Wait- did they tell you?''

``That she- she- was in MedBay?'' Hayley replies absently, still mostly focused on Signe.  She strokes Signe's bandaged left hand and whimpers sadly.  She sounds bewildered as she asks Trenton, ``Do you know what happened?  Do you know?  Who hurt her?''

``If you ask Morgan, it was a security breach,'' says Trenton with a yawn.

``Somebody...hurt her?'' asks Hayley.

``Physiologically?  No.''

Hayley looks at the bandage and looks \textit{very} confused.

``Okay I guess that counts.  But it's just a fracture.  Not too bad.''  He looks at Hayley and states more than asks, ``So they didn't tell you.''

``Tell me what?''

Trenton stretches and says, ``Finally, we have something in common besides our good looks.''

Hayley mentally considers this and agrees absently.  Hayley shifts to stand near the head of Signe's bed and starts stroking Signe's hair awkwardly.  Trenton offers her a flask and Hayley declines politely.

Hayley contemplates crawling into the bed with Signe but the tie-down straps make it too hard to do so without risk of injuring Signe or falling out of the bed.  Not seeing a cot or chair and being too fatigue-stupid to figure out what to do next, Hayley just leans down to rest her head on the pillow next to Signe's and continues to gently comb her fingers through Signe's hair.  



Trenton does his best to take this in stride and clears his throat, ``So apparently our friend Octavius got a little too close.''

``I heard there was a hit,'' says Hayley.

``A 'hit'?  What do you mean?''

``I don't know, they just said one hit,'' says Hayley, obviously not very interested in this topic. She starts whispering softly, lovingly, to Signe, ``I'm glad you're okay.  I'm glad you're back.  I missed you.'' over and over.



``Soooo... this is an awkward time but she wanted me to do it, so- I'm sorry,'' Trenton says quickly like he's trying to get something unpleasant over with as fast as possible.

``For?''``Uh, for being a jerk.''

Hayley doesn't move her head but looks up at him and frowns slightly, ``Um, your apology is accepted, but not necessary.  Thank you.''  Her attention returns to Signe.

``That's where you're wrong, 'cause...apparently it was really necessary.  So.  Sorry.  Yeeeeaahh.  Aaaand.  Stuff.''  Trenton isn't even looking at Hayley as he says this, but Hayley only spares him the briefest of glances before returning her gaze to Signe.   He continues, ``Anyway she really cares for you so-''

``I care about her.  She's my friend,'' says Hayley without hesitation, interrupting him.

Trenton sighs.  ``I'm glad that she's got a friend.  It's actually been a really long time, now that I think about it.  Hm.  Anyway... do you want me to leave you here with her?''

``I was given permission to sleep here.  So she won't be alone.  I don't want her to be alone.''

``I mean, I can stay, if you have other things to do,'' offers Trenton, clearly not knowing how to interpret Hayley's response.

``She would be happy to see you.  But I can sleep here too,'' says Hayley unhelpfully.

Trenton has an unreadable (to Hayley) expression on his face, but she can at least tell he doesn't look happy.  She lifts her head slightly to look at him, ``Did I do something wrong?''``No, it's just-''

``Do you want me to leave?'' asks Hayley, looking worried.

``No!  No, it's just- do you want \textit{me} to leave?''

``I think she would like to see you when she wakes up.''

``Okay...''

Hayley rests her head back on Signe's pillow and looks at Signe even though she is still addressing Trenton.  She says with an affectionate smile, ``She cares about you a lot.  You are very important to her.  That is why I was helping you.  Because she asked me to.''

Sounding a bit desperate, Trenton asks, ``Look, can you stand up when you say that?  You have to realize it's a little weird, with your head, next to hers... like that.... conflicting messages and all....''

``Oh sorry!'' says Hayley.  She stands up obediently and turns to face him fully.

Trenton attempts to be discreet again and says, ``I'm going to go talk to Swan about her IVs... do you need anything?''

Hayley evaluates Signe's medical equipment and says, puzzled, ``Her IVs look fine.'' 

``I know.  \textit{I know.}`` He takes a deep breath. ``That was just an excuse to take a walk.'' 

``Oh.  OH!  You are being polite!'' Hayley very belatedly figures out what Trenton was trying to do and says, ``Thank you.''

``Trying.  Trying \textit{really hard},'' responds Trenton, sounding like he's gritting his teeth.

``That's very nice of you,'' says Hayley solemnly.

``Again.  \textit{Trying.}''

``I like that better.''

``Er- What?''

``You being nice.'' Hayley smiles at him.

``Uhhh....'' Trenton seems at a loss for words.  There is a lengthy pause.



When he doesn't say anything for a while, Hayley looks at him curiously.  ``Who was it in your lab?''

``What?''

``The pictures.  They never told me.''

``In my lab?  Wait- what?'' says Trenton, somewhat thrown by her change in topic.

``The scars that weren't mine but were.''

``Oh,'' Trenton realizes what she was talking about and says with more assurance, ``That wasn't my lab.   Yeeeah, that.  I totally overreacted.  That was my bad.  I was scared for Signe.... and... and that's all we need to say about that.  It was some guy named Tim.''

``Oh.  That is sad,'' says Hayley almost reflexively, not sounding particularly sad.

``Scary sad,'' says Trenton.

``It's a very unpleasant way to die,'' says Hayley calmly.

Trenton looks a little alarmed, ``Have you- Have you died?''

``Yes.  Twice,'' Hayley looks like she's thinking hard and corrects herself.  ``Maybe.  It's a little unclear.''

``....What??'' 

``Not from that though,'' Hayley rushes to reassure him.  ``I was able to tolerate more of the pain so it didn't kill me from shock.''

``Sorry I didn't mean to pry,'' says Trenton, backing away from the topic as quickly as he can.  At a loss, he offers her the flask again, ``Are you sure you don't want any?''

``Oh no.  It's poison.  I assume that's alcohol,'' says Hayley primly.

``Well there's poison and then there's poison that's easily regenerated from.  Technically speaking, oxygen is poison and you breathe that.''

``It is?  Hmm,'' says Hayley thoughtfully.  ``I was told that alcohol would damage my body so I don't partake.''

``But, you wear makeup?''

``Yes. So I can be more beautiful.''

``Uh, okay.'' Trenton takes a deep breath and tries again.  ``Look, I'm going to go talk to Swan.  Do you need anything?''

``I will need a cot-''

``Great!  I'll go get you a cot.''

``Thank you.''

``Holler if she wakes up.''  Trenton gives Hayley a long look and then leaves.



A few minutes later, Swan delivers a cot.  Hayley tells him, ``I wanted to say thank you.''

``For what?''

``For your assistance with the Cistern.  I'm sorry that you got in trouble.''

``Oh. Right.  It's fine, it's cool.''

Hayley smiles in relief.

As he helps her set up the cot, Swan asks, ``Can you definitely get some sleep?  I know that Morgan is kind of a taskmaster and Gerhauser... well.  You should really get some sleep.''  Swan mutters, almost to himself.  ``Why do people never listen to me?``

``Oh no, I want to sleep. I took your pills.  It is very hard for me to stay awake right now.''

``Oh!  Good.  Well I'll shut up then and let you sleep.''

He leaves.

Hayley strips down to her underwear, carefully folding her uniform and putting it to one side where it won't get wrinkled.  She moves the cot to be as close to Signe's bed as she can, then lies down and goes to sleep.  Some time later, Trenton returns to this scene.  He has a hard night of it.




\sceneHeadline{MedBay- Jonah and Carruthers}

Jonah wakes first.  His dreams had been intense and disjointed. There's a lot of images that don't make sense to him.  It's weird but not uncomfortable.  

Through the comm, Hekate says, ``Are you awake?  Your baselines are good.  You are free on your own recognizance.  If find yourself suffering from any medical symptoms that are abnormal, please contact me immediately.''\footnote{\textbf{Rebecca S. }I assumed through this whole scene that Dr. Gerhauser was watching everything on a security cam in her office, being mildly pissed off. \textsubscript{12/02/14 7:55am}}

Jonah is still a little bleary but eventually climbs out of the tank.  He moves slowly and is trying to get his bearings.

One of the other tanks pops open and Carruthers (naked) climbs out.  Jonah immediately looks over at her.  She looks in his direction nervously and greets him, ``Jonah.  Are you okay?''   Jonah just stares at her and she repeats the question. 

``I think so...'' he says slowly.  He asks uncertainly, ``Carruthers?''

``You can call me Brianna,'' says Carruthers.

``Everything is backwards here,'' says Jonah, still trying to make sense of his clothes.  Carruthers starts fidgeting with her clothes too. Jonah says, ``I feel like I've had too much to drink without getting to drink anything.'' 

``Hey so...I'm just going to ask this-'' Carruthers starts, stops and then says in an embarrassed rush, ``You know what nevermindbadidea.''

``Ask me what?''

``Doyouwantohavesex?'' Carruthers blurts out nervously.

Jonah looks at her in puzzlement, ``What?  Slower...''

Carruthers is half covering herself and says more clearly, ``Do you- do you want to have sex?''

Jonah sits down abruptly.

``I'm sorry, that was a stupid question because I think you're really into Hayley or something which would make sense because...'' Carruthers babbles and starts getting dressed.

``No....''

``No you don't want to have sex or no....?''

``No I'm not-''

Carruthers pauses and waits for Jonah to say anything further but when he doesn't she backpedals again, ``I'm sorry, that was a \textit{really} stupid thing to ask.  I'm really sorry.  Um.  I just sometimes...''

``...it's been a while?'' asks Jonah.

``Yeah!   And you seem nice...and I don't know....'' flounders Carruthers.

``Not right now, right?'' asks Jonah.``Well we're alone, no one's around...'' says Carruthers.

``I'm- I'm sorry.  Yes.  Can I take a shower first?'' asks Jonah.

``Er yeah, I think there's a shower down the hall...''

``Do you remember your first time?'' asks Jonah slowly.

Carruthers looks very uncomfortable.  ``Uh... like sexually?``



Elsewhere, Hayley gets a dream of having sex with a guy she's never met.  It doesn't bother her at all, it barely even registers among all of her other memories of sex with strangers.



``No!'' says Jonah and taps his temple.  ``As an Operator.''

``Oh yes, of course!'' 

``I've got that disoriented hangover thing going on.''

``Oh!  Oh right.  I'm so sorry,'' Carruthers says sympathetically and takes a step forward.  She puts her hand gently on his forehead.  ``I'm sorry, I forgot,'' she says consolingly.  ``I'll help you get cleaned up.  If Swan's not awake we can take a shower.  No one needs to know.''

Eventually Jonah lets Carruthers lead him to the shower.  Carruthers is gentle and conscientious.  She is slow and careful as she moves closer and closer to him.

Before things heat up too much, she asks hesitantly, ``Should I let Hayley know?''

``Let Hayley know what?'' ask Jonah, not cluing in.

``Uh,'' Carruthers indicates their nakedness and proximity.  ``About us...''

``No, she's not invited,'' says Jonah firmly.

``Just wanted to make sure,'' says Carruthers.  She then, awkwardly but determinedly, derails the conversation to non-verbal exchanges.


\sceneHeadline{Mess Hall- Jaya and Jari}

Jaya wakes up, she has a weird sense of emptiness.  She's still tired, her injuries hurt, and she's very hungry.  She also feels unexpectedly lonely because the room is empty.  Jonah's not there, Hayley's not there, Oliver's not there.  Jaya is also feeling a little horny.  Naturally, since Jayce isn't there either.



Jaya concentrates on her empty stomach, drops her head back, and yells at the top of her lungs, ``FUUUUCKKKKKKK!''

Eventually, just barely before breakfast is over, Jaya hauls herself out of bed, gets dressed, and slinks into the Mess Hall.

She looks around to see who is going to bear witness to her shame.  PG2 is there (Lackovich, Javier and Breccan), minus Carruthers.  Jaya sorta nods/acknowledges them.

Lackovich greets her, ``Where is Jayce?  I would have expected him to be here already.  Jeez that guy can pack it away.''

Jaya gives her a dirty look, ``You know.  Just....You know...'' 

``You okay?''

``I got a hangover. So I'm just going to...'' Jaya gestures vaguely toward the kitchen.

Jaya walks up to Jari and he says neutrally, ``You made it to breakfast.''  He slides a bowl of lukewarm gruel toward her.

Jaya's sleeves are rolled up and she glances down.  Jari can't really ready the words chickenscratched onto her arm but she reads it and with a pained sigh, says, ``Thanks.'' and takes the bowl of gruel. 

She goes to sit in one of the least occupied corners of the Mess Hall.  She feels like everyone is watching her (whether or not they actually are).  She eats slowly, belching occasionally and looking like she's going to vomit soon.

She works her way through the first bowl.  It goes slowly because she often just lifts the spoon up and then drops it back down again without any gruel actually making it to her mouth.  About halfway through her bowl, PG2 gets up to leave.  They can sense that something is up but can't figure out what.  They bus their trays and chat a bit with Jari.

Lackovich walks over to Jaya, ``Hey, when you get a chance later, can we chat?''

``Yeah, free.  Later.  Yeah.'' says Jaya more to her gruel than Lackovich.  ``You're dismissed.  It's cool.''

Lackovich pauses, rolls her shoulder and narrows her eyes at Jaya.  ``You must be having an interesting morning, \textit{Agent.}``  She turns and barks, ``Breccan, we're done here.'' 

Jaya lifts her head and looks at Lackovich.  She looks like shit.  Her eyes are red and puffy, she looks a pale and green from nausea.  This is the worst Lackovich has seen her look.  There's a momentary glimmer of ``dear god save me'' in Jaya's eyes but then she looks back down and keeps picking up her spoon and letting the gruel dribble off of it.

Lackovich has an odd expression as she herds her two PG2 members out the door.  She keeps looking back at Jaya, waiting for eye contact, but Jaya's attention is solely on her gruel again.  Lackovich leaves and the door shuts.

Jaya is alone in the Mess Hall.  After a very sour belch, Jaya decides she's eaten enough of the gruel and goes to find Jari.  She drops the bowl on the pass-through.

``Are you back on cleaning detail?'' he asks.

``No.  Um.''  Jaya clears her throat and mutters.  ``Can I have another one.  Please.''

``Sorry, what?  Another bowl?  Oka-''

``Just give me another fucking bowl!'' interrupts Jaya loudly.  She adds a muttered, ``Please.''

``Alright!  Jeez.''  He heads back into the kitchen and hands her another bowl.  ``Do you want me to heat it up?''

``It doesn't fucking matter,'' mutters Jaya again and she stomps off to her secluded corner of the Mess Hall again.

Jari watches Jaya for a while, a little suspiciously, but then eventually returns to the kitchen and continues cleaning up.

Jaya gets about 4/5ths through the bowl and can't bring herself to eat any more without gagging.  Her queasy watery burps foreshadow how poorly this is going to go later.

She walks back to Jari and drops the bowl on the counter. 

``Hungry today,'' comments Jari.

Jaya glares at him.  ``Thanks,'' she says almost venomously, and then turns and walks out.



She has barely made it outside the Mess Hall doors and Rook walks up to her.  ``Agent!  Please report to MedBay.''

``I, uh, left something in my bunk, I'm just going to back and get it...''

``Very well, Agent,'' says Rook pleasantly.

Jaya returns to her bunk and vomits up her humiliation.  She cleans herself up a little and heads off to MedBay.




\sceneHeadline{MedBay- Jonah and Carruthers}

Their liaison is fairly nice.  Afterward, Jonah checks with Carruthers, ``So just us, right?  Not the others?''

``Oh absolutely.  Because we could get in trouble and it could get complicated,'' says Carruthers fervently.  She smiles at him.  ``Thank you though.  That was really good.''

``Er.  Yeah.  Thank you too.  Ditto.''

``Do you want to leave first, or should I?'' asks Carruthers.

``You know what?  Tradition.  I'll go first,'' says Jonah.



As Jonah leaves MedBay he runs into Rook.  Rook greets him, ``Ah!  Operator.  Just the man I was looking for.  Do you have a minute?  I need to talk to you about your sister.''

``Okay, let's go,'' says Jonah.

As the elevator doors shut, Jonah sees Carruthers leave the MedBay room he was in.  He can tell that Rook has noticed this.  Rook cocks his head to one side and looks consideringly at Jonah but says nothing.



Rook asks Jonah, ``How are you feeling?''

``Disoriented.''

``I'm given to understand that the second Agent is somewhat more difficult than the first. If you feel it is unmanageable, we can always pull one of the Agents.  But we can discuss that later.''

``Signe is okay?'' asks Jonah.

``Yes.  The quantum interference we were experiencing in this region is dropped significantly.''

``Should I be looking for something?''

``Yes, but I shouldn't expect you to perceive anything more than a door that is trying to be opened would perceive.''

``Wonderful,'' says Jonah somewhat sarcastically.  ``So there is no way to tell if they are doing anything?''

``Oh there are ways to tell. We can measure how strong their lock is based on the number of signals we can detect.  Because the signals are weaker now and more diffuse we suspect they have lost much of their lock.''

``So it's not that they hammering at the door, they are trying to find the door.''

``Yes.  As I said before, it's more of a reflectance situation.  Since they don't have the technology Signe has, they are having to trying to connect through a different technology,'' explains Rook.

``And Signe is particularly prone to being locatable?'' asks Jonah.

``Well she used to be part of Tertius.''

``One day you will have to explain that more.  Do you know what was done to her to make her that way?''

``Signe? What do you mean?  \hl{Like a human?}\footnote{\textbf{Suko T }!! \textsubscript{12/01/14 12:40am}}`` asks Rook.

``Noooo... more vulnerable to Octavius.''

``Oh.  When Tertius was, for lack of a better word, dispersed, Signe was part of that dispersal.  Since Octavius did the dispersing, it had a pretty good idea of what was going on and who the constituents were.''

``So they acted in unison like Octavius?  They spoke with one voice and acted as one?'' asks Jonah.

``Tertius was a little different, but yes.''

``Is there something about the behavior of someone who was part of Tertius or Octavius?''

``Characteristic behavior?   Difficult to tell.  My understanding from Morgan and Hekate is that their characteristic behaviors are volatile with regard to their constituency.  Octavius in particular.  Astarte had a profound impact on their mentality.''

``But there are many of them, aren't there?'' asks Jonah.

``Hmm.  Consider the situation where someone is a talented medic in a demographic that mostly consists of farmers.  That medic may have a profound impact on the medical knowledge of that demographic.  Even if you remove the medic, that impact remains.  Similarly, someone with a certain personality types can have a profound impact on other personality types that they have been connected to.''

``Short answer is that I don't know what I'm looking for.  I don't know Signe so I don't know what to look for,'' says Jonah, sounding a bit dismayed/frustrated.

``Let me put you at ease this way then.  You are using equipment very similar to Tertius' thus you have a much better ability to interact with Signe than Octavius ever will.  There's a reason why Octavius took so long to interface as much as it did.''

``So there's only room for one person in the door?'' asks Jonah

``They were learning the shape of a door that you have drastically changed, and now they have to learn the shape of a whole new door.''

``How do I know if they are coming?  I don't want to wake up and find Octavius in my head.'' 

``Ah.  I don't think that will happen.  I think you will see plenty of signs.  I can't tell you what they are, but they will be obvious to you, based on all the literature.''

``I haven't read the literature.''

``I'll see if I can get you clearance,'' promises Rook.



They arrive at Rook's lab and they go inside and sit down.  Rook asks Jonah briskly, ``Now, about your sister.  You expressed a desire to have her be educated.''

``Yes.''

``There are several methods by which we can go about this.  Three of which I wish to present to you now.  One is the traditional method of tutoring and education.  We can cover a variety of subject matters.  This is largely verbal.  It is slower, but over time it is can lead to a higher level of social skills because it requires more social interaction and engagement.  While that would be effective it would be relatively slow.''

``Who would be teaching?  You?''

``For the large part, yes.  \hl{Though I may find other mentors for specific topics, I could school her in reading, writing, arithmetic, quantum mechanics, biology, and a variety of other topics.}\footnote{\textbf{Suko T }OMG.  So hot for teacher.  Blame Rebecca for suggesting Rook in tweed. \textsubscript{12/02/14 1:10am}}Alternatively there's a method by which we would attempt to push a large amount of information into her brain.  Some of it won't stick.  She would be out of activity for a time and it would be harder to diagnose the outcome.  But she may more quickly come to an understanding of certain complex topics that would otherwise take years or decades to teach.''

``What do you mean by 'push'?''

Rook pauses thoughtfully.  ``Ah.  Hmm.  You are not particularly familiar with writing, I take it?  Writing is a way to create signifiers that map a signifier to signified.  If you were able to write a glyph, such as the one on your medics bag, it indicates that it is a bag for medics.  What we are able to do is on a more more complex level, deliver symbols to her brain to signify knowledge.  If you want to take the analogy a bit further, it will be difficult to understand which symbols she will understand.''

``Is this like being in the tank?'' asks Jonah.

``No.''

``Explain exactly what you would do, physically.  What does this involve?'' asks Jonah.

``It involves hypnosis which is a\underline{  {\color[RGB]{17,85,204} series of visual stimuli to her visual cortex}  } through which we would push a large amount of information directly to her cortex.''

``Is this like Agents and Operators?  Have you done this before?''

``I have not done it myself but I have read all the literature.''

``Have you experienced this before?''

``I have not.''

``Do you know anyone who has?''

``Yes.''

REBECCAxxBEGINxxHIGHLIGHTxx``Are they here?''

Rook avoids the answering the question and continuesxxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }our guess was Trenton \textsubscript{12/02/14 8:07am}}, ``There is a third option.  An implant, similar to the one Agent Parvadi uses, but obviously with a very different purpose.  Utilizing that implant we can stimulate neural responses directly to her learning patterns.  \hl{It is a mechanical device with a biological interface.}\footnote{\textbf{Rebecca S. }I gotta get Jaya one of those! \textsubscript{12/02/14 8:07am}}``  



He opens a cannister and pulls out a small device with several wires and bits coming off of it.  ``It would be inserted at the base of her cranial cavity and these parts would be surgically implanted in her brain.  This part would be covered with a pseudo flesh flap so it is not obvious.  Through it we can alter the program to tailor the learning she is getting.  This is would be the safest option, given our time constraints.''

``Why would time be a constraint?''

``Learning has value.  Knowledge has value.  The sooner you get that knowledge the more value it has to you.  Presumably you wish for her taught for a reason.  To promote herself, to increase her own safety, to increase her ability to make choices. So the sooner she gets that knowledge the better.''

``Yes but- usually it takes time.''

``What this device would do is increase the rate at which she could assimilate information.  As well as providing some options access to reference materials.''

``What is this device called?''

Rook reels off a string of numbers.  ``Patent \#\_\_\_\_\_\_\_\_\_''

``That's the name of it? What does it mean?''

``It signifies the device,'' says Rook, puzzled.

``Why would you call it that?''

``There are many models,'' Rook gestures around the room to all of the other cannisters.  ``If I were to come up with a name for all of these, it would become confusing.''

``These are all like that?'' asks Jonah.

``Similar in that they are all mechanical devices that have biological interfaces.''

Jonah looks around and there is a gleam in his eye as he realizes the immense street value of the items around him.  He says, ``Let me think about it.  Let me talk to her and get a chance to recover from yesterday.  And eat something.''

Rook hands him a clipboard.  ``Certainly.  Here is the waiver that you need to sign if you want to do the implant.   Underneath that is the waiver if you want to do the hypnosis route though honestly the results from that are volatile and I wouldn't necessarily recommend it.''



Jonah asks for a day or two think about it and talk to Riva.   He pauses and then asks Rook, ``On a completely different matter, does Trenton know about Signe?''

``Yes.''

``Does he know she's alive?''

``Yes.''

``And being Operated on?''

``Yes.  He may not know who her Operator is.  He may have forgotten to ask.'' says Rook, deadpan.

``He \textit{may} not know?  This is important I think.  Would it be a problem if I told him?''

``I don't see why.  Do you think it will be a problem?'' asks Rook.

``I think it would be a problem if he were surprised by it.''

\hl{``It is my understanding that you two are close,'' says Rook, sounding a little surprised.}\footnote{\textbf{Rebecca S. }:) \textsubscript{12/02/14 8:09am}}\footnote{$\rightarrow$\textbf{Suko T }Everyone sees it but them... \textsubscript{12/02/14 11:28am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }HAHAHA!

lulz \textsubscript{12/02/14 12:26pm}}

``This is not a normal situation.''

``Ah. Well I do not wish to misjudge the degree of friendship you two have.  But I should hope the two of you can talk it out.  I was the one who told him of the nature of the security situation,'' says Rook.

``What else can I tell him?  Does he know about Octavius?''

``Yes.  I believe that is the reason he forgave me for my...opacity around the subject.  He realized I was acting in his best interest.  We did not tell him immediately because we knew his reaction would be strong and we were concerned he would take volatile action.''

``I understand that, that's why I'm asking these questions.  I don't want to surprise him unpleasantly.''

``He doesn't know but he may have surmised some of this by now.''

``Well I need to speak to him, and to Riva and I will come back to you with an answer,'' says Jonah.

``Very well,'' says Rook calmly.




\sceneHeadline{MedBay- Hayley}

Hayley has strange dreams.  There is a torrent of images, almost in fast forward, and Hayley feels a bit exhausted by the end of it.  There are many flashes of things from Hayley's past, including getting cut, her time at Redemarrer, Heaven, and other times.  There is no particular emphasis on anything and they seem to be in random order, with no real connection between the various dreams/memories.  They do always cycle back to the Cistern.  Perhaps because of this, there is a significant amount about Oliver, though it too is very disjointed.  Many memories of Jonah, a lot of them very sexual.  A little bit about Trenton, which are mostly just confusing.  Everyone makes an appearance eventually.  Jaya, Morgan, Dr. Gerhauser, Swan....even Tim.  There are are some dreams that Hayley can't contextualize, conversations with people she feels should be familiar but aren't.  Hayley feels unusually concerned/distressed that she doesn't know why these conversations are meaningful.  Usually that sort of thing doesn't bother her.



She wakes up feeling horny.  Trenton is sleeping on the floor on the other side of Signe's hospital bed, using his jacket as a pillow.  He's removed his shirt and shoes.  Signe appears to be sleeping peacefully.  



Hayley is only awake a few moments when she hears  {\color[RGB]{153,0,255}::Hayley?::}  in her head.  Hayley ignores Carruthers for a moment as she reassures herself that Signe is just asleep and didn't die while Hayley was sleeping.  Carruthers gets a lot of fretful anxiety from Hayley as Hayley lightly touches Signe and assesses her condition.  Somewhat reassured, Hayley says brightly,  {\color[RGB]{255,153,0}::Hello!::} 

 {\color[RGB]{153,0,255}::Hello.  I didn't wake you did I?:} :  There is a strange emotion (guilt) coming from Carruthers that Hayley isn't familiar with.  It sorta makes her stomach feel unsettled, like food is sitting heavily in her gut.

 {\color[RGB]{153,0,255}::How are you feeling?::} 

 {\color[RGB]{255,153,0}::Still tired, but I got some sleep.::} 

 {\color[RGB]{153,0,255}::Did you sleep alright?::} 

 {\color[RGB]{255,153,0}::I think so, I dreamt a lot.  That is not usual.::} 

 {\color[RGB]{153,0,255}::I could kinda tell.  Hey, um, do you swim?::} 

 {\color[RGB]{255,153,0}::Yes!:: }  Carruthers gets a wave of happy/safe/cared-for feelings from Hayley that seem to mean Oliver.   {\color[RGB]{255,153,0}::Oliver, I mean, } \textit{ {\color[RGB]{255,153,0}Operator Langdon} } {\color[RGB]{255,153,0}, taught me.::} 

 {\color[RGB]{153,0,255}::Is that safe?::} 

 {\color[RGB]{255,153,0}::I-  I don't know.  I didn't drown.  He wouldn't let me.::} 

 {\color[RGB]{153,0,255}::And you didn't burn either?::} 

 {\color[RGB]{255,153,0}::No.  Should I have?::} 

 {\color[RGB]{153,0,255}::Well the water where I grew up was pretty bad.  My brother drowned a squirrel in it once.  It looked really disgusting after four hours.  Like one of the the most disgusting things I've ever seen.  Smelled really bad too.  My mom was really upset because we could have used the meat.::} 

 {\color[RGB]{255,153,0}::Why didn't you just get another one?:: } asks Hayley naively.

There is a moment of complete lack of comprehension on both sides.

 {\color[RGB]{153,0,255}::So where do you swim?::} 

 {\color[RGB]{255,153,0}::The Cistern.  But I haven't- Oh.  I was supposed to think of a reason to go back there.  I need to go back there.::}  Carruthers can feel a rising sense of anxiety from Hayley as she realizes she still doesn't have access to the Cistern.

 {\color[RGB]{153,0,255}::Why can't you go back there?::} 

 {\color[RGB]{255,153,0}::I didn't give a sufficient excuse to Dr. Gerhauser.  She says it helps me hurt the people she cares about.  So I need a very good excuse.::} 

 {\color[RGB]{153,0,255}::} \textit{ {\color[RGB]{153,0,255}Gerhauser} } {\color[RGB]{153,0,255} won't let you go back?::} 

 {\color[RGB]{255,153,0}::Doctor Gerhauser. Yes.::} 

 {\color[RGB]{153,0,255}::} \textit{ {\color[RGB]{153,0,255}That} } {\color[RGB]{153,0,255} explains some things.::} 

: {\color[RGB]{255,153,0}:Does it?  Good.  I don't understand it.  She said she's not angry at me but she sounded angry.::} 

 {\color[RGB]{153,0,255}::Ohhhh Dr. Gerhauser is } \textit{ {\color[RGB]{153,0,255}very } } {\color[RGB]{153,0,255}angry at you.::} 

 {\color[RGB]{255,153,0}::Oh!  Oh good.  I'm getting better:: }  Hayley feels pleased.

 {\color[RGB]{153,0,255}::At what?::} 

 {\color[RGB]{255,153,0}::Understanding when people are angry at me.::} 

 {\color[RGB]{153,0,255}::Do you know } \textit{ {\color[RGB]{153,0,255}why} } {\color[RGB]{153,0,255} she is angry at you?::} 

 {\color[RGB]{255,153,0}::No.::} 

 {\color[RGB]{153,0,255}::So this is an indelicate question but....uh.... were you in love with Langdon?::} 

There is reflexive  {\color[RGB]{255,153,0}::No.::}  and then a pause and Hayley thinks hard.  Carruthers can tell this way of thinking about people is very new to her.  {\color[RGB]{255,153,0} ::Unless family counts.::}   Hayley continues more confidently.   {\color[RGB]{255,153,0}::Yes. }  {\color[RGB]{255,153,0}\hl{Like family.  Not blood family. The other family.}} \footnote{\textbf{Rebecca S. }another great Hayley motto! Funny, but then makes you feel ever so slightly sad/uncomfortable.. \textsubscript{12/02/14 8:13am}}\footnote{$\rightarrow$\textbf{Suko T }Yay!  It is usually my goal to leave people feeling that way after a conversation with Hayley :) \textsubscript{12/03/14 3:19pm}} {\color[RGB]{255,153,0}:: }   Hayley seems to feel this make sense.  {\color[RGB]{255,153,0} ::He took care of me.  Kept me safe.  Explained things to me.:: }  Again, Hayley projects those feelings of happy security at the thought of Oliver.

 {\color[RGB]{153,0,255}::That seems a weird thing for her to be jealous over.::} 

Hayley doesn't reply, seemingly waiting for Carruthers to say something else.  When she doesn't, Hayley asks, {\color[RGB]{255,153,0} ::So do you know why she's mad at me?::} 

 {\color[RGB]{153,0,255}::Well, I assumed she was jealous of you because you were in love with him or something.  It's not like she shares her thoughts with me but you can tell by the way she looks at people.::} 

 {\color[RGB]{255,153,0}::You can?  I mean, I can tell she looks at people, but I can't tell what she's thinking.::  } 

 {\color[RGB]{153,0,255}::It's not that hard, you just have to put yourself in their shoes.::} 

 {\color[RGB]{255,153,0}::Why would I do that?  They won't fit.:: }  Hayley isn't being facetious, she really doesn't understand what Carruthers is talking about.

 {\color[RGB]{153,0,255}::Hayley, it's an expression.::} 

 {\color[RGB]{255,153,0}::Sorry, I don't know all of them.::} 

 {\color[RGB]{153,0,255}::So, did Oliver love you?::} 

There is a big pause.  If thinking about if she loved someone was new, speculating on if someone loves her is even more foreign.  {\color[RGB]{255,153,0} ::I don't know.  How would I know that?  He never said it.::}   Hayley offers almost shyly, but with affection and pride  {\color[RGB]{255,153,0}::He said he would miss me.::} 

 {\color[RGB]{153,0,255}::Hmm.  That's kind of ironic because that must be how Gerhauser feels too.::} 

 {\color[RGB]{255,153,0}::That she misses me?:: }  Hayley is clearly starting to lose the thread of this conversation.

 {\color[RGB]{153,0,255}::No. No!  You know she was into him right?::} 

 {\color[RGB]{255,153,0}::No.   What do you mean 'into him'?  Like sex?:: } 

 {\color[RGB]{153,0,255}::Or romance and stuff.:} : Carruthers seems very uncomfortable.

 {\color[RGB]{255,153,0}::Oh.::} 

 {\color[RGB]{153,0,255}::Not everything's about sex.::}  and another wave of unfamiliar emotion from Carruthers.

 {\color[RGB]{255,153,0}::Oh.  I don't know about romance.  But he loved her.::} 

 {\color[RGB]{153,0,255}::Does she know that?::} 

 {\color[RGB]{255,153,0}::I don't know.  How would she tell?::}  Carruthers can feel Hayley floundering and that she's trying very hard to keep up with this conversation but it is somewhat incomprehensible to her..

 {\color[RGB]{153,0,255}::Sorry, I just got confused by some of the things you were dreaming last night.  I couldn't really sleep.  I didn't mean to pry.::} 

 {\color[RGB]{255,153,0}::That's okay.::}   There is no sense of violated privacy or embarrassment from Hayley, she is completely okay with sharing that with Carruthers.

 {\color[RGB]{153,0,255}::I saw stuff, stuff before everything happened.  You know, before stuff with the Chief (image of Lackovich) and Langdon went down.::} 

 {\color[RGB]{255,153,0}::Before Nicklepan?::} 

 {\color[RGB]{153,0,255}::Both I guess.  There's that one time that Gerhauser snuck off the base and told me not to say anything.  Which I probably shouldn't be telling you.  But I'm not actually saying it, so it's okay, right?::} 

 {\color[RGB]{255,153,0}::Oh is that a secret?  I can keep secrets.::} 

 {\color[RGB]{153,0,255}::Yeah...why don't we keep that a secret.::} 

 {\color[RGB]{255,153,0}::Alright.  Who is authorized to know?::}   Hayley is feeling on much firmer ground here.

Carruthers meanwhile, is taken aback by this  {\color[RGB]{153,0,255}::It's a secret.  So like, } \textit{ {\color[RGB]{153,0,255}nobody} } {\color[RGB]{153,0,255}::} 

 {\color[RGB]{255,153,0}::But I have to tell my contract holder.::} 

 {\color[RGB]{153,0,255}::Definitely don't tell Morgan!!:: }  There is a sense of panic from Carruthers \hl{and some mental ``ohshiitohshit''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{12/02/14 1:24am}}   {\color[RGB]{153,0,255}::Morgan didn't want Hekate to go but she snuck off the base anyway.  Probably to see Oliver.::} 

 {\color[RGB]{255,153,0}::Oh yes, I saw that.  He remembered that.  He liked that.  They said things.  I think.  Probably romantic things.::} 

 {\color[RGB]{153,0,255}::I hope so.::} 

 {\color[RGB]{255,153,0}::Probably their date was better though.::} 

Carruthers has no response to this, and after a pause says  {\color[RGB]{153,0,255}::Sorry.  I'm having a really weird morning.::} 

 {\color[RGB]{255,153,0}::I'm sorry::} 

 {\color[RGB]{153,0,255}::No it's my fault.  I got talky and it's nice to have someone around that I can talk to.  I can talk to you right?::} 

 {\color[RGB]{255,153,0}::Yes of course::} 

 {\color[RGB]{153,0,255}::How's Signe doing?::} 

 {\color[RGB]{255,153,0}::She seems to be recovering.:: } Carruthers is swamped with feelings of happiness, affection, warmth and devotion from Hayley at the thought of Signe.  In some ways it's deeper and stronger Hayley's feelings for Jonah because it is uncomplicated.  It is like how she feels about Oliver but instead of feeling protected, the roles are reversed and Hayley feels very protective of Signe.  Like a mother to child or older sister to baby sister.  There is a slight backwash of feelings from Carruthers- envy and a bit of disappointment.  Hayley doesn't really grok them.  

 {\color[RGB]{255,153,0}::She is better.  I don't like it when she's hurt.  It makes me sad.  And upset.::}  Hayley starts fussing over Signe again.  Carruthers can feel that Hayley is almost compelled to have some sort of physical contact with Signe, without her usual aversion to touching and being touched.  Carruthers helps feed into that.  Hayley was mostly just trying to make Signe look prettier (arranging her hair, smoothing the blanket just so).  Carruthers helps Hayley actually make Signe more comfortable by adjusting her pillow and fiddling with the tie down straps.  Hayley clearly has very little idea of how to make someone comfortable.

 {\color[RGB]{153,0,255}::Okay.  Sorry.  I just wanted to ask you some questions.  I feel better now.  I'll let you hang out with Signe. But if you need anything, you just ask, okay?::} 

 {\color[RGB]{255,153,0}::Okay.::}   Now that her anxiety over Signe is has calmed down, other emotions come to the fore.  Hayley starts contemplating Carruthers naked.  The evaluation is definitely sexual, not just aesthetic.  

Carruthers is embarrassed, which Hayley doesn't really understand, but she can sorta feel Carruthers blush.  The connection between them seems to draw into itself and grow more attenuated.   {\color[RGB]{153,0,255}::I'm being asked to- Something for the Chief...sorry, I'm going to be distracted in a moment...::}  

 {\color[RGB]{255,153,0}::Okay.::}   Hayley then pictures Jonah naked and contemplates this also.

This time Carruthers not only sends embarrassment and that mysterious other emotion, but inadvertently sends back pictures of Jonah in various positions and in the shower.  Carruthers thinks, somewhat frantically,  {\color[RGB]{153,0,255}::I really have to go.  Sorry.  Lackovich is asking me something.  Um.::  } Carruthers can tell that Hayley is feeling very turned on and that she is somewhat unfamiliar with the strength of the sensation. Hayley's not distressed by it, she's more curious than anything else. Carruthers shuts down the connection as fast as she can.




\sceneHeadline{MedBay- Jaya}

Jaya walks to MedBay.  She passes Carruthers in the hall.  Carruthers is bright red and Carruthers keeps her eyes fixed on the floor and passes Jaya quickly.  Jaya scowls and assumes that Carruthers has heard of the gruel incident this morning.



Jaya arrives at MedBay and Swan tells her that Dr. Gerhauser is waiting for her in her office.  Jaya stomps into the office and collapses into one of the chairs. ``You wanted to see me?''  She belches.

``One moment please.''  Dr. Gerhauser finishes typing something and then looks over at Jaya, ``We need to talk.''

``I'm in your office,'' grumbles Jaya.

Dr. Gerhauser leans forward and says, ``I need to put you on a 30 day antibiotics.''

``No.  NO!  Nonono.  I- I...I did the antibiotics-!!  I did the fucking antibiotics!!!''  Jaya stands up. ``I don't have grave rot anymore.  There were no dead bodies. On me.  For any amount of time.  This time.''

Dr. Gerhauser starts to smile.

Jaya looks around and then slams her hand forcibly onto the desk and shouts, ``\textit{You can't do this!}``   She picks up a mug from the desk and throws it on the floor.

``Calm down.  It's a joke.'' says Dr. Gerhauser with a smirk.

``What- really?''  Jaya looks at the broken mug and the dent she put in the desk.

``Yes, you are cured of the grave rot.''  

Jaya sinks back into her chair, a tinge of red in the bits of skin between her tattoos.

``Sorry to get your goat like that.  But it's been a long time since I've seen something funny.  I apologize.''

Jaya leans forward and glares daggers.

Dr. Gerhauser is unperturbed by this. ``I do have something serious to talk to you about. Your abdomen wound caused us to do a complete scan as I'm sure you know.''  Dr. Gerhauser pauses for a moment then continues, ``You have certain physical abnormalities that we discovered in the scan.  In some ways it is quite fortunate that you were injured in the way you were. Because otherwise we wouldn't have scanned in this particular manner and we wouldn't have had access without opening you up.''

``What?  Am I going to die?''

``No.''

``Well.  Great!'' says Jaya jovially, slapping the table. ``So we good here?''

Dr. Gerhauser frowns and says, ``I'm sorry.  There isn't a delicate way to put this, but... your baby might.''

Jaya stands and starts backing away, ``What?''  Then she looks around a little desperately and says ``Ha!  HA!!  Great fucking joke!'' She pulls open the door and shouts back into med bay ``Great fucking joke!'' before slamming the door closed.  ``You got me this time!'' Jaya grabs another mug and smashes it to the ground, her eyes a little wild.  ``Fucking HA!  Fucking hilarious!''

Dr. Gerhauser picks up another mug and sets it within Jaya's reach.  ``Let me be clear.  Your baby will die unless we do surgery.  It is probable that you have had multiple miscarriages without noticing.''

\hl{Jaya sits back down, grabs the third mug, and squeezes it with her metal hand until it explodes into shards of pottery and dust}\footnote{\textbf{Rebecca S. }http://simply-sithel.tumblr.com/image/105072732089 \textsubscript{12/12/14 11:46pm}}\footnote{$\rightarrow$\textbf{Suko T }So good!!!  Thinner neck was the right choice for proportion balance I think.  I love their expressions.  They capture so much. \textsubscript{12/12/14 11:53pm}}.  Dr. Gerhauser flinches out of the way of the flying debris and frowns a little.  

``I need a drink.''  Jaya pulls out a cigarette and immediately lights up.

``I don't know how much education you have about this, but a drink right now would not be advisable.''

``I need a fucking drink.  Right NOW.''  Jaya starts looking around to see if she can find one amid all the papers and books.

``Ms. Pavardi, please listen to me,'' says Dr. Gerhauser patiently.

``Oh fuck oh fuck,'' Jaya starts hyperventilating a little as she buries her face in her hands.

Dr. Gerhauser continues, ``If it were medically safe to give you a drink or drugs, I would.''

Jaya reaches into her pocket and before Dr. Gerhauser can do or say anything, flips open a little tin and takes a bit of something.  ``Fuck.  Just give me a sec, okay?''  Jaya's breathing starts leveling out.

Dr. Gerhauser looks very annoyed.  ``We can leave your situation as it is and the baby will pass without pain or even without you noticing.''

``You're fucking kidding me.''

``It's not uncommon for a woman to get pregnant and for some of them to fail.''

``Are you saying I'm a failure? What the fuck?'' demands Jaya.``No, I'm saying you had a very unfortunate luck of the draw, vis--vis your reproductive organs.''

``Ah....so is like Rook going to put something in...'' Jaya gestures with her metal hand and rotates her wrist.

``While we had \textit{in vivo} cannisters on \hl{Mars}\footnote{\textbf{Suko T }!!!! \textsubscript{12/01/14 5:35pm}}, we do not have access to those here.  I can do the surgery to make sure you do not lose the implantation.  But I'm not sure that's what you want \textit{professionally }right now. How much do you know about how pregnancy works?

``I dunno.  You put the thing in,'' Jaya makes a very specific gesture. ``And the thing comes out.''

Dr. Gerhauser looks unsurprised. ``So... essentially nothing.'' 

``It takes two, it takes some time.  You work on it and then....'' Jaya looks uncomfortable.  ``It was more Padme's thing.  She's got it down pat.  Excepts she fucks it up sometimes.  And I hear it hurts a lot.''

``We have drugs for that.''

``Really?''  Jaya's interest is piqued.

``Why endanger the life of the mother over something as silly as traditional pain?'' Dr. Gerhauser says reasonably.

``That's an excellent way of thinking!'' approves Jaya.

``My sister indicated that this might be a sensitive subject for you-''

``You told \textit{Morgan}?  You told \textit{Agent Morgan}?'' Jaya is horrified.

``Her title is Agent Gerhauser. And yes, I had to report on your wound.  She was very happy for you.''

``Really?'' Jaya is surprised and a little wary. ``She wasn't envious or something?''

``Why would she be envious of you?''

``I mean because it takes some effort and it's awesome. And I don't think she's getting any good odds....ya know?''

``No.  Please explain.'' Dr. Gerhauser asks, with the pleasant tone of someone watching someone else dig their own grave.

``You know how you gotta put something in to get something out?  I don't think she's getting anything put in, ya know?'' says Jaya, a little pityingly.

``You're making a lot of assumptions.  My sister's sex life is none of your business.

But your reproductive life \textit{is} my business and unfortunately somewhat hers also.  So you have a choice to make. I can fix the abnormality-''

``I'm not fucking abnormal!'' interrupts Jaya.

``-Or we can let nature run its course.  If we fix it, I have to advise you to stay off of drugs and alcohol.''

Jaya eyes Dr. Gerhauser suspiciously, ``For how long?''

``Unfortunately this joke is not as funny as the last one.  Nine months.''

Jaya recoils.  ``That's not fucking funny!  My sister fucking shoots up all the time and they come out... well mostly fine.  And she drinks!  The last time, okay well the other last time I saw her, she fucking drank me under the table.  Course, then she lost it, but It doesn't seem to affect her.  So why would I need to- Why couldn't I-''

``Let me put it this way: you can take my medical advice or-''

``How many kids you had?'' asks Jaya belligerently.

``Again, none of your business.''

``You haven't had any!  I mean my sister's had...uh....'' Jaya clearly can't quite remember how many kids Padme's had.  ``Uh...six.''

``Do you wish to have a viable baby or a non-viable baby?''

``I want a fucking awesome baby!  Of course!  Who doesn't want a baby... well...can you tell if it's...uh, \hl{good}\footnote{\textbf{Rebecca S. }botched this delivery (no need to amend the record) but in case it wasn't clear, when Jaya asks if the baby is ``good'' here she is asking if it's female. \textsubscript{12/02/14 8:23am}}\footnote{$\rightarrow$\textbf{Suko T }I like that the meaning of ``good'' is clear to Jaya but would be misinterpreted by most other people.  Who knows what Dr. G thinks it means, in this context. \textsubscript{12/02/14 11:30am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I actually loved that I knew exactly what Jaya meant and knew that wasn't what was being communicated. \textsubscript{12/02/14 12:26pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{12/03/14 3:19pm}}?

``It is probably fine now, I can do some tests if you like.  But if you're not going to keep the baby, then I'm not going to bother.''

``No!  Padme's going to fucking \textit{shit }herself!'' Jaya says gleefully.

``It is going to require that you stay off of drugs and alcohol for nine months-''

``Weellllll what if-'' Jaya starts.

Dr. Gerhauser cuts her off and says firmly, ``When I say requirement, it is not a negotiation.  It will require that you stay off of drugs and alcohol for nine months.  Well, eight at this point.  And it will require removing you from active duty in three months' time.''

``What???  My sister worked the whole time!'' protests Jaya.

``What does your sister do, pray tell?  How many times per day does she get shot at?''

``Oh. Uh.  Actually... I kinda fucked up there toward the end, they did burn down her place.  I think she got shot at too.''

``So you have three months of active duty until I will \textit{insist} that you are pulled off the line.  Or we can let nature take its course.''

Jaya attempts again, ``Can we like-''

Dr. Gerhauser sighs in frustration, ``\textit{Why} do you insist on trying to negotiate with the laws of physics?''

``What if- what if-...'' Jaya says desperately, ``Rook makes some armor....'' gesturing to her abdomen.

Dr. Gerhauser looks like she is at the end of her patience.  ``Look.  If you insist on continuing to fantasize, I will allow you to do so.  On your own time.  When you have made a decision, feel free to come back-''

``No!  I've made my decision!  Do the thing!  Let's fucking do it right now!'' Jaya puts out her cigarette on one of the mug shards on the desk.

``You \textit{will} stay off of drugs and alcohol for 8 months?'' asks Dr. Gerhauser, looking at Jaya pointedly. 

``You know, I gotta do what I gotta do,'' says Jaya, her eye twitching.

``Very well, I will prep it.  Go get some rest.''

Jaya walks out of the room.  Swan is looking back at her somewhat warily.  

``Wasn't a fucking joke,'' says Jaya, glaring at him and she stalks off.



During all of this, Jonah is having breakfast.  He drops two glasses, decides to get a drink and then in the middle of having that drink, decides to go have a smoke.  He is jittery.





\textbf{\hl{Dr. Gerhauser's Office- Hayley and Dr. Gerhauser}}\footnote{\textbf{Suko T }I loved the reveals in this SO MUCH.  Even if I wasn't able actually provoke Dr. G into strangling Hayley, I feel like I'm getting closer.  Someday....

Has Dr. G really thought through what a teenage Hayley is going to be like?  How could that possibly be less maddening? :D \textsubscript{12/02/14 1:52am}}\footnote{$\rightarrow$\textbf{Rebecca S. }I agree with every statement.
(re: ``Someday...'' is this what Morgan's hallway training is for? To prep Hayley for that moment when Dr. G finally flips out and attempts to murder her?) \textsubscript{12/02/14 9:15am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Please. Dr. Gerhauser would never stoop to hurting someone...

...physically. \textsubscript{12/02/14 12:30pm}}\footnote{$\rightarrow$\textbf{Suko T }+10

...I would say ``challenge accepted'' except I think it's a losing proposition.  Doesn't mean I won't keep trying tho. ;) \textsubscript{12/03/14 3:30pm}}



Hayley vaguely notes Jaya storming past the door but doesn't think much of it.  Swan comes in a few minutes later.  He realizes Trenton and Signe are still sleeping and he whispers, ``Do you have a minute?  Dr. Gerhauser wants to talk to you.''

``Okay,'' Hayley replies.  She leans down and whispers to Signe, ``Bye!  I'll be back.''

``I'll watch her,'' whispers Swan.  The cot has been neatly stowed away and Hayley is fully dressed.  Hayley smiles gratefully at him and leaves.



She knocks on Dr. Gerhauser's door. ``Enter,'' says Dr. Gerhauser.

Hayley walks in and waits (standing) for acknowledgement.  There are broken bits of coffee mugs all over the floor.

Dr. Gerhauser says, ``I apologize for the state of the office.  Please, have a seat.''

Hayley sits, her back ramrod straight and her hands folded neatly in her lap. 

``How are you feeling?'' asks Dr. Gerhauser.

``More rested.  Thank you.''

There is a very very long pause as Dr. Gerhauser says nothing.   Hayley waits patiently, not fidgeting, just watching Dr. Gerhauser steadily.  Dr. Gerhauser looks like she choking down something incredibly distasteful.  When she finally speaks, it's like each word is being dragged out of her kicking and screaming.  

``I.         May.             Have been.        Somewhat.                                Unfair.

                        And... irrational.  

                                                                                             With you\hl{.}\footnote{\textbf{Rebecca S. }It's a hard scene to capture, but I approve of your efforts.  Needs double the white-space though ;) maybe a couple page-breaks in there. \textsubscript{12/02/14 9:16am}}\footnote{$\rightarrow$\textbf{Suko T }Agreed.  A very early version of this had each word segment on a separate line and lots and lots of extra carriage returns.  But I thought that got a little hard to read (though it upped my page count considerably!).  So this was my compromise. :) \textsubscript{12/02/14 11:21am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It's a really awesome stab. This is why medium matters, I suppose. \textsubscript{12/02/14 12:28pm}}''

Hayley's expression is carefully blank.

Dr. Gerhauser takes a deep breath and says with great effort, ``I apologize.''

Hayley looks a little confused but says calmly, ``Your apology is accepted.   But not necessary.''

Dr. Gerhauser takes another deep breath and clears her throat. ``Your commanding officer recognizes that I have jurisdiction over certain areas of this base.  Do you understand this?''``Yes.''

``So you understand that I find it a breach of protocol that you used the Cistern without my express permission.''

``Ah.  You made that clear.  I apologize for that.''

``Thank you for that apology.''  Dr. Gerhauser pauses again and then forges on. ``In my medical opinion is not wise for you to continue to indulge in that particular psychosomatic craving.''

``I don't know all of those words.  Is that important?''

``Which words are you unfamiliar with?''

``The connection between psychoso...somatic craving and indulging it?''

``Are you familiar with cravings?''

``Yes.''

``Indulging a craving is giving into it and letting that craving take control. Knowing, for instance, that you shouldn't drink alcohol, but doing it anyway.  Or that you shouldn't have sexual relationships with a coworker but doing it anyway.  Or knowing that you shouldn't lose control but doing it anyway.  Becoming emotional when you shouldn't.''

``I see.  I am not very familiar with that circumstance,'' says Hayley honestly.

Dr. Gerhauser chuckles humorlessly.  ``Of course not.''  She pauses again before continuing. ``Your commanding officer wishes me to give you some leeway but I am not convinced that it is wise.  As I stated before.  So instead, I am going to give you choice.  But I will discuss the matter first so you can fully understand the implications thereof.''

``I appreciate that.''

``How familiar are you with what was being done with you at Redemarr?''

With confidence Hayley says, ``Very.  It's been a while, so I wouldn't know all of my medical charts perfectly.  Hmm... perhaps since I was twelve.  Before that would be more unclear.  I was much younger then.''

``Interesting terminology: 'younger'.  Part of your pathology is that you have an abnormally slow growth curve.   In particular in the emotional department.  This is due to a number of genetic locks that were placed on your genetic pathway.  They can only be unlocked at certain times with certain chemicals.  Which we proceeded to do because it was necessary for you to operate at a higher level.  If you'll consider for a moment the depth of experience you have had since joining Patrol Group One, versus all of the time before that.  I think that you would agree that it has been somewhat more vivid.''

``Yes. Except for certain other moments.''

``Yes.  Childhood can be quite affecting and in your case, has been abnormally long.  Part of the reason you look the way you do, part of the reason you heal as well as you do, and part of the reason why your mind is as flexible as it is, regarding VTXs.''

Hayley smiles proudly.

Dr. Gerhauser continues, ``However we believe that it is time for you to mature and-''

``Get older?'' Hayley looks very unhappy.

``-Proceed to the next stage of your development.  The increase in mental, emotional, sociological and performance capacity... we believe is important.''

``But I'll be \textit{old}?'' persists Hayley, frowning with great distaste at the thought.

Dr. Gerhauser clears her throat and says with equal disdain, ``I understand that your 'people', for lack of a better word, were vain.  But I did not realize they had bred it into you genetically.  Yes.  You will become older.  And depending on how you look at it, those in their mid 20's are far more attractive than those in their teens.''

``Really?'' Hayley is very dubious.

``And we believe, based on historical evidence, that there's a good chance you'll become....'' Dr. Gerhauser gets a very sour expression, ``...even \textit{more} physically attractive.''

``I would like that,'' says Hayley, pleased.  ``That would be nice.''

``You will have to maintain yourself more diligently.''

``More?  I suppose I could sleep a little less,'' offers Hayley, uncertainly.

``Sleep is part of maintenance.  I don't know why no one listens to me.  It is very important.''

``Oh no, sleep is very important.  I always try to get lots of sleep,'' says Hayley virtuously.

``Absolutely. For every hour of increased physical activity we expect a fifteen minute increase in your sleep cycle.''

Hayley nods.

``However...'' Dr. Gerhauser says slowly. ``And admittedly, the research on this is a little shaky.  I believe I do not wish to put you through this hormonal treatment unless you are willing to give up these childish notions.''

``What is a childish notion?''

``The quintessential notion is the favorite blanket or teddy bear that you do not wish to part with.''

``I don't know what these things are,'' says Hayley unenlightened.

``In your case it is a strange obsession with a particular room.''

``It's not shaped like a blanket,'' says Hayley, failing at her analogy roll.

Dr. Gerhauser excuses herself and types something into a terminal to regain her composure.

She turns back to Hayley.  ``I've had this conversation with you before-''

``Because... it is comforting?'' asks Hayley slowly, very uncertainly.

``Thank you for that...analogy leap.'' says Dr. Gerhauser in a tone dripping with sarcasm (which Hayley doesn't notice).  Dr. Gerhauser continues, ``You find it comforting for entirely psychological reasons.  There is nothing that distinguishes that room from any other room.''

``But Operator Langdon is there.''

``Operator-'' Dr. Gerhauser says, her jaw tight,  ``Operator Oliver Langdon is dead.''

``Yes.''

``Dead people cannot be in a room.''

``Oh.  Not his body.  I understand that.'' says Hayley earnestly.

``Not any part of him.  He's \textit{dead}.'' says Dr. Gerhauser somewhat viciously.

``No,'' says Hayley stubbornly.

``Yes,'' says Dr. Gerhauser flatly.

``No.  I mean, I keep him here,'' Hayley pats her chest.  ``I promised I would remember.  So I do.''

``And what \textit{I'm} saying is that you need to grow up.  Or you can choose to stay as you are now.''  Dr. Gerhauser leans forward and places her hands on her desk.  She looks at Hayley intently.  ``Door number one: we continue the the hormone treatment and continue down your development pathway.  Door number two: we wait for this psychological issue to resolve itself.  And I give you access to the Cistern until such time as that happens.  Your commanding officer is pleased enough with your performance, that \textit{you} get to make this choice.''  Dr. Gerhauser's tone makes it clear that she doesn't think this is a good idea. 

REBECCAxxBEGINxxHIGHLIGHTxxHayley is silent for a long time.  And then simply says, ``Okay.''

Dr. Gerhauser, ``Hayley?''

``Yes?''

``'Okay' is not a sufficient answer.''xxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{12/02/14 8:30am}}

``You wish me to pick now?'' asks Hayley, surprised.

``Not picking is also a choice.''

``So there are three choices,'' says Hayley vacuously.

Dr. Gerhauser narrows her eyes at Hayley and says, ``I believe you are more intelligent than that.  And I will not will not lay out for you why those three choices are effectively two.''

Hayley gives up trying to avoid making the scary choice and asks, ``The first door...I don't go to the Cistern again.''

``I believe that would be unwise.  You will be experiencing an increased level of emotional activity and we need you to be disciplined and focused.''

``But if I will be feeling things, I will need it,'' protests Hayley.

``The feelings you have will...change''

``Will they be less scary?'' asks Hayley anxiously.

Dr. Gerhauser gives a short laugh, ``Honey, feelings are always scary.  And whenever possible, you should avoid them.  That's just advice from me to you.''

``Oh I like to feel them. But they are still terrifying.  I don't have much else.  But that.''

``I believe that isn't true.  But that you are not nearly old enough or wise enough to understand why.  Your relationship with the Cistern, should we continue the treatment, is likely to change.  I do not wish for it to turn into an obsession.  I do not wish it to move down pathways which would cause dangerous interactions with the rest of your psyche.''

``May I ask a question?''

``Certainly, we're friends here,'' says Dr. Gerhauser, not sounding friendly at all.

``We are?''  Hayley is surprised, which throws her off for a moment before she says, ``You seem to know how this will turn out. What do you recommend?''

``I recommend that you grow up and face the challenges in front of you and you let go of the past.''

``Why?''

``Because where you are now, and where you go in the future is changeable.  The gates that are open to you, you can move through any one of them.  The gates that you went through in the past, the choices you made, the things that happened to you, they are \textit{not} changeable.  \hl{Living there is living in a static place.  You can let it dominate you, and that is comforting.  But is that living?}\footnote{\textbf{Rebecca S. }Yeah, Hayley.  Get with a new world moment, why don't you? Sheesh \textsubscript{12/02/14 8:32am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm glad that a character who had a hard time formulating cogent sentences had such a deep impact on the lexicon. \textsubscript{12/02/14 2:40pm}}''

``It is how I have lived,'' says Hayley, sounding puzzled.

``Right.  So the question is do you wish to live as you have lived, or do you wish to be more than that?''

Hayley asks, a little timidly, ``Will I understand things better?''

``I sure hope so,'' says Dr. Gerhauser, a little fervently.

``Will I be less scared?''

``Probably not.  You will probably be more scared.  But at the same time you may be better able to handle it.''  Dr. Gerhauser sighs.  ``It amazes me what they did actually.  The fact that you have the emotional response of a nine year old when you are clearly much older than that.''

``Twenty three!'' supplies Hayley.

``Physically I'd actually put you at 17, but as I said, emotionally much younger.  Mentally... you're all over the map.''

``I- I think that I need to think about it.'' says Hayley, hesitantly.

``Very well, dismissed.'' says Dr. Gerhauser briskly.

Hayley sits for a second, thinking, and then stands up and leaves quietly.

The door shuts behind her and Hayley can hear the sound of more breaking ceramic.



Hayley goes to Signe's room and looks at her for a while and then goes to look for Swan.  

``Hello.  Can I ask you a question?  Do you know what I was asked by Dr. Gerhauser?''

``No.''

``Oh.''

``Hayley, you don't need to ask me, to ask a question.''

``Aren't you a doctor now?'' Hayley asks, puzzled.  ``Isn't it polite?''

``It's politer amongst friends to just assume that you can ask.''

``We're friends?'' asks Hayley eagerly.

``Hayley...no offense but I know a lot about you physically...er not \textit{that }way but, um... there's a lot I know about you. Let's just be friends.  It will make it a lot easier.''

``Okay.  I like you,'' Hayley says with a happy smile.

``I like you too!'' says Swan.

``If I was more mature, would I be able to help Signe better?''

``What?  Uh...why do you not think you're mature?''

``Dr. Gerhauser.  Said I wasn't.  Not yet.'' says Hayley.

Swan says with careful diplomacy  ``Words...can have a lot of meanings.  So how do you mean 'mature'?''

``She said it meant 'older', 'wiser'.''

``We could all be wiser, right?  Wisdom is good!''

``Would that help her?  If I was wiser?'' persists Hayley.

Swan sighs.  ``Yes of course.  How could it not?''

``Okay!'' says Hayley brightly.  ``Thank you.''




\sceneHeadline{Hallway- Jaya and Lackovich}

Jaya heads back to the bunk and picks up the stack of commendations that Hayley wrote.  She goes prowling around the base, looking for Rook.  She runs into Lackovich.  Lackovich has a bag slung over her back and flags Jaya down before Jaya can escape.  Jaya (not so discreetly) hides the stack of letters behind her back.

``Uh, hey!  What's up?'' she greets Lackovich.

``Got a minute?  I'm going to the platform, heading out-'' starts Lackovich.

``Oh is Rook driving the train?'' asks Jaya.

``Uh... I think so?''

``Great, let's walk to the platform!'' says Jaya with surprising enthusiasm.

``So you okay?  Rough mission?'' asks Lackovich pleasantly.

``Oh yeah.  It was really intense.  Yeah... sorry.  Sorry about... you know.....um....'' Jaya clearly can't remember Morley's name. ``...your constable.   I lost an Agent so I know...uh...I'm sorry....''

``Can we not compete on that front? Because first of all, I'm still winning, and second of all-''

``What do you want to talk about?'' interrupts Jaya.

``So it's actually a weird question and I don't know if anyone's talked to you yet.  Rook asked me this thing....''

Jaya grabs Lackovich. ``What the fuck did Rook say?'' 

``They are looking at options to make Jonah's life a little easier and they wanted to know if I could be your Operator-''

``Wait!'' Jaya interrupts excitedly, ``Jonah wouldn't be my Operator anymore?''  An evil grin starts spreading across Jaya's face.

``Uh...but he's a good Operator, right?  He's got the best metrics and shit-''

``FUCK NO!'' exclaims Jaya loudly.  ``It's like- It's like- having \textit{Jonah} in your head!  I'm out there and focusing and he's like- 'Jaya! Why don't you think about this thing?' or 'Jaya!  What's going on?' and you know you're, like, in the fucking zone, you just don't want that fucking shit in your head.  Er- What were you saying?''

Lackovich looks around and says to Jaya quietly, ``You need to chill out!''

``I know!  Jonah's fucking stressing me out!!''

``Jonah.  \textit{Jonah's} stressing you out?'' asks Lackovich incredulously.

``Yeah!'' says Jaya confidently. Then a little less confidently, ``Yeah.  I...think so.  Pretty sure.''

``I think you're delusional.''

``I'm not fucking making it up!  He's in there!'' Jaya attempts to contact Jonah but he's ended the connection. ``Well, okay maybe not right now, but he's in my head all the other fucking times when it's \textit{not} useful.''

Lackovich is keeping a tight grip on her temper.  ``Look, all I need to know is if this a good idea or a bad idea.  Right now I'm kinda feeling like this is a bad idea-''

``Wait- what idea?'' asks Jaya.

``Would you rather have me in your head?'' asks Lackovich and at Jaya's horrified look, she says with satisfaction, ``that's what I thought!  Asked and answered.  I don't even know why I ask you these questions-''

``Nonono wait!  Save me!'' Jaya grips Lackovich's shoulder and looks desperate.  ``I don't know you but you gotta be better than Jonah.  Nothing could be worse.  You know when to fucking shut up!  You know, I really appreciated those times when you shut down and clammed up and I feel like I could work with you.''

``If we did this, we are going to have some fucking rules,'' says Lackovich.

``Yeah, you stay out of my fucking way-''

``We can't do this fucking shit.  I'm there to do a job.  You have to respect that.  You have to respect \textit{me}.''

``Yeah!  You gotta help me.  Help me fucking succeed!''

Lackovich hisses, ``\textit{Jaya}.  This isn't just fucking about \textit{you}.''

Jaya looks at her in surprise and Lackovich throws up her hands. ``FUCK!  This is a bad idea.''

``No!  No!  You gotta help me out!'' pleads Jaya.  

Lackovich says incredulously, ``I gotta help you out?  \textit{I} gotta help you out?  I'm the \textit{only} one who helps you out.''

``Hayley helps me out!  You ain't got nothing on Hayley!''``Maybe you should ask Agent Morgan how much I have on Hayley.''

``Wait- you got dirt on Hayley?'' asks Jaya, almost sounding awed.

``Oh my \textit{GOD}.'' swears Lackovich.  ``\textit{Jaya}.  I just need to know if this is a good idea, 'cause I can just tell Rook no and we can just leave it at-''

``This is Rook's idea?  The man is fucking brilliant.  I owe the man a fucking drink!  Yeah!  Let's do this!''  Jaya extends her hand for Lackovich to shake, realizes it's the metal hand with the letters in it and switches to her flesh hand.  ``'Cmon!  Let's do this!  You and me!  FUCK YEAH!!!'' she exhorts.

Lackovich grabs her hand and shakes it, but then keeps her grip and pulls Jaya in close and growls, ``Do not make me regret this, Bitch.''

Jaya looks uncomprehending and says with a grin, ``We're going to be fucking awesome!  We're going to be fucking unstoppable!''  She slaps Lackovich on the arm.  ``But I'm still going to be head of Patrol Group One, right?'' 

``Really??? You're going to pull fucking rank on me?  Right now? THERE'S NOBODY FUCKING HERE!'' Lackovich yells and it echoes down the hall.

``I just want it be FUCKING CLEAR!'' Jaya yells back.

Lackovich glares at Jaya.  ``Here's what's going to happen.  I'm going to go get my brains fucked out and then I'll tell Rook and we're going to do this thing.  But \textit{you're} going to keep it under fucking control.''

``I'm going to be good!  I'm going to be chill..''Jaya gets a horrified look as she remembers her earlier conversation with Dr. Gerhauser.  ``I'm... I'm going to cut out the shit...and go.....clean....''  Jaya's voice trails off.

Lackovich rolls her eyes.  ``Look, don't make any promises you can't keep.   Don't talk.  Just do.''

Jaya starts to walk off and then realizes that she needs to speak to Rook and awkwardly keeps walking with Lackovich to the train platform.



They get to the platform and Jari is there, looking a little impatient.  Lackovich and Jaya both mutter to each other in consternation.

``Uh yeah, sorry.  I guess something came up.  I'm driving today,'' says Jari.

Jaya immediately stubs out her cigarette and says to Lackovich, ``I'm fucking outta here.  Good luck'' and turns smartly on her heel to leave.

Before she can entirely get away, Jari calls out to her, ``By the way, Jaya?  You're welcome.''

Jaya pauses, visibly flinches and then just continues walking away.




\sceneHeadline{Hallway- Hayley, Micah and Karil (and Morgan)}

Hayley is sitting with Signe when Swan comes in again and whispers, ``You're needed in Ops.''

Hayley nods and gets up.  She whispers, ``Bye.  I'll be back'' to sleeping Signe.  Trenton wakes up groggily and groans, ``I need medicine...''



Hayley leaves.  She steps out of the elevator on the Ops floor.  Micah is standing in the middle of the hallway outside of the elevator.  He's wearing BDUs.  Hayley looks at him curiously and nods politely, ``Master Sergeant,'' and tries to skirt around him.



Right as she gets into arms' reach, he pulls his hand back to swing at her.  Hayley, not having any true sense of self-preservation, only barely manages to roll with the punch enough to not have him break her nose.  He lands a solid punch to her jaw and she goes down pretty hard.  She gets into a defensive crouch and looks very confused.  Micah approaches again and is clearly looking for an opening.  



Hayley is wary and asks again, ``Master Sergeant?''  Micah goes in low and sweeps her with his leg and sends her tumbling backwards.

Hayley gets back into a low crouch again and asks, very confused, ``Do I need to fight you to get to Ops?''  She can sense someone behind her.  Hayley turns slightly to try to put the wall at her back. The person behind her (Karil) grabs her and binds up one arm, while Micah again comes in low and punches her hard in the kidneys.  It \textit{hurts}.  Micah really knows how to punch.



Hayley suddenly goes on the attack.  She uses Karil's hold on her as leverage to lift herself up to kick Micah in the head.  He blocks it but she does land a blow.  Karil throws her against the wall.  Hayley rolls gracefully and comes up ready to attack again. She launches herself at Micah.  She doesn't pull any punches and every blow and kick is meant to knock him down or incapacitate.



Micah goes into a defensive position, blocking most of the blows and backpedalling a bit.  She almost misses Karil's attack, a calf stomp, and barely dodges out of the way.  As she turns to face Karil, Micah sees an opening and grabs her and pins her arms.  Karil punches her in the gut, definitely not as hard as Micah, and from previous sparring with him, Hayley thinks he pulled it a bit.



Morgan's voice says, ``Enough.''



Micah and Karil both immediately stop.  Hayley stops as well and struggles to catch her breath.

Morgan says, ``Pretty good but you need to be way \textit{way} more aware of ambushes.''

Hayley can't reply for a moment, trying to get enough air to speak.  ``Yes, Sir,'' she wheezes.

``Given your role, and given whom we're fighting, you understand that at any moment, anyone could be an enemy.  Correct?''

``No,'' Hayley gasps a little. ``But I do now.''

``Learn that lesson really really well.  When you can beat Karil  And when you can beat Micah.  And when you can beat both of them at together, then talk to me and we'll spar.''

Hayley smiles, very pleased. ``Thank you, Sir.''

Morgan adds, ``\hl{Also, I'm sending you off base for various training.  I'll give you more information later.}\footnote{\textbf{Rebecca S. }I think I missed this in the game.
And now I'm concerned. \textsubscript{12/02/14 8:39am}}''

``Okay.  Thank you sir,'' says Hayley.



Morgan leaves.  Karil looks at Hayley and makes sure that she's is able to stand okay, which she thanks him for.  She doesn't seem to be angry or upset at Micah and Karil, though she is clearly hurting.

Micah says kindly, ``You'll do better next time.''

``Yes.  I will,'' says Hayley matter-of-factly.

Micah gestures to Karil, and says to Hayley, ``Nice move.''

``Thank you,'' Hayley smiles at him.




\sceneHeadline{Annex- Jaya}

Jaya is sent a memo that if she wants to go on Shore Leave, now is good time but she needs to be back on base for medical tests by \_\_\_\_.  Jaya requests to go to where Padme is now and then goes searching for Rook.

She is told that Rook is dealing with SAC Security issues and is unavailable.  Jaya swears and leaves the now crumpled and sweaty letters of commendation on her bunk.



Jari takes Jaya to the Annex. The station is quiet at this hour. On her way out of the turnstiles, one of the Constables looks at her and asks hesitantly, ``Are you Agent Parvadi?''

``Yeah.  What is it?'' says Jaya, leaning against the turnstile. 

``The Chief said a message came in for you.  It's at the front desk.''

Jaya goes to the front desk and demands her message.

``You're supposed to go to room 382.  It's actually in the sub-basement, I don't know why they numbered things this way...''

``What the fuck is this about?'' snarls Jaya.  ``I'm a very busy individual.''

``I don't know, Agent Ma'am!'' yelps the Constable.

``Someone show me the way, I don't want to get lost in this fucking place.''

A Constable walks Jaya down to the sub basement.  At some point, Jaya's spidey sense starts tingling.  She sees dark figures at both ends of the corridor.

One of the figures hawks, spits something disgusting on the floor and growls, ``You.  Get.'' The guy escorting her takes off, leaving Jaya alone.






\jumpHeadline{Quotes: }

Ion: Being ``In the Tank'' in this game is a totally different thing to us.



Nate: It doesn't seem possible but Signe's grin gets even wider.  It looks especially weird through the distortion of the glass.

Suko: Hot.



Nate: Signe mouths,  ``I am going to eat your face.''  Well, maybe it's hard to tell exactly what she said, but you're pretty sure the words ``I am going to eat...something'' are directed at you and definitely-

\hl{Suko: Jaya knows smack talk and bitch-speak.  She knows.}\footnote{\textbf{Rebecca S. }:D  I'd forgotten this. So good! \textsubscript{12/02/14 8:41am}}

Rebecca: Very fluent.



Ion: I should have asked for a hazard bonus.

Nate: You aren't nearly as aggressive about that as Jaya.

Suko: Yeah you really needed to negotiate that before you said yes.  All you asked for was more training and schooling?  What is up with that, Jonah?



Nate: So there you are with three women.

Rebecca: Naked and in a bathrobe.

Ion: And passing out at the wrong end of things.



Suko: Cyber uterus!



Dr. Gerhauser: How much do you know about how pregnancy works?

Jaya: I dunno.  You put the thing in \textless Jaya makes a very specific gesture\textgreater  And the thing comes out.

Dr. Gerhauser: So... essentially nothing.



Dr. Gerhauser: Why do you insist on trying to negotiate with the laws of physics?



Dr. Gerhauser: Honey, feelings are always scary.  And whenever possible, you should avoid them.  That's just advice from me to you.


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: I assumed through this whole scene that Dr. Gerhauser was watching everything on a security cam in her office, being mildly pissed off. because:GivenExpectedThrough the comm, Hekate says, Are you awake?  Your baselines are good.  You are free on your own recognizance.  If find yourself suffering from any medical symptoms that are abnormal, please contact me immediately.Through the comm, Hecate says, Are you awake?  Your baselines are good.  You are free on your own recognizance.  If find yourself suffering from any medical symptoms that are abnormal, please contact me immediately.


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:41pm
\end{flushright}

