\setcounter{chapter}{ 37 }
\chapter{\textbf{``Shore Leave''} }




\begin{center}
 {\LARGE \textbf{(aka. ``Counselor Morgan'')} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} Dec 4th, 2014



Jaya gets ``taught a lesson'' by Rust (though he needed four other guys to help him do it. Pansy). Jonah signs his sister up for lessons with Professor Rook and confirms that Trenton is okay with Jonah being Signe's new Operator.  Morgan counsels Hayley on sex and not being a victim.  Hayley also has a lovely frolic with Drake.



Off we go to find a Beacon!



\noindent\hrulefill






\jumpHeadline{Shore Leave-  }\underline{ \hl{Jaya} }\footnote{\textbf{Rebecca S. }tweaked some stuff... mostly pulling out a lot of ``!''s and replacing them with ``...''s  Added in more gestures that (I hope?) happened around the dialog. \textsubscript{12/11/14 9:53am}}\footnote{$\rightarrow$\textbf{Suko T }Thanks!  Please feel free to always do this!!  I love having more character flavor there, especially for Jaya since she's so physical. Half the fun is her/your expression at the time. :D \textsubscript{12/12/14 12:28am}}
\sceneHeadline{Annex Station, Sub-basement- Jaya, Rust and the Brute Squad}

Jaya is surrounded by five shadowy figures in a darkened hallway of the TA sub basement.  She recognizes Rust's silhouette, but doesn't recognize anyone else- definitely no Drake or even Madelyn.  She puts her hand on her sidearm, but maintains a casual pose and asks, ``What the fuck do you want?''

Rust starts sauntering down the hallway toward Jaya.  The guy with him is a bruiser, no question, and follows a step behind.  ``Two things.''  He holds up an envelope.

Jaya leans back, but Rust keeps moving closer to her.  Jaya checks over her shoulder.  The other guys behind her are also closing in.  ``Why don't we do one thing at a time?'' she says to Rust and then addresses all of them, ``And you stop fucking moving.''  She glares at Rust.  ``I don't like this.''

``Not my problem,'' says Rust and hands her the envelope.

Sensing the guys behind her are very close, Jaya takes the envelope and takes a step back, turning so her back is to the wall.

``It's from Mohinder.  Point two, I need to borrow this,'' and Rust reaches for Jaya's sidearm.

Rather than resisting, Jaya actually unholsters her gun, flips it around and hands it to Rust, grip first.  ``What?'' she sneers, ``You think you need a fucking gun?''

Rust takes the gun and tries to clock Jaya in the head with it.  She was expecting this and blocks it with her metal hand.  Unfortunately Rust was expecting her to do that and counters by kneeing her in the groin.  They start brawling and she winds up on the floor in short order.  Rust says, ``We can make this easy or we can make this hard.''  

One of the other guys kicks Jaya.  

She rolls with the kick and pops her Predator-style knife.  Moving to a crouch, Jaya brandishes her knife and says defiantly, ``Hard for who?  You or me?''

Rust hawks, spits and says, ``Hard way then.''  Rust and the brute squad all pull out truncheons.



Jaya feints an attack at Rust but punches the guy to one side with her metal hand (no knifework yet- she doesn't want to escalate things).  There is a satisfying crunch of bone. 

Unfortunately a truncheon comes down on the back of her head.  A few more truncheon blows rain down as she staggers to one knee. Someone kicks her in the face and she starts losing track of where everyone is.  There is blood everywhere and she has definitely broken her nose again.



Jaya keeps fighting, slashing with her knife, getting in some solid blows and cuts, but they keep pummeling her until she gives out a bit.  \hl{At that point, two of them grab her and hold her upright (making sure  to incapacitate her metal hand)}\footnote{\textbf{Rebecca S. }at some point I hope to be able to deploy the mid-fight arm-detachment-for-surprise attack.  The arm stub has a nice metal cap, right? Could probably fuck up a face if she arm-stub-punched 'em, right?  Course, things would have to be pretty fucking dire... and am not sure how easy it would be to retrieve arm mid-brawl... \textsubscript{12/11/14 8:53am}}\footnote{$\rightarrow$\textbf{Suko T }Rocket fist!! \textsubscript{12/11/14 11:35am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Jaya/BAYMAX mashup? \textsubscript{12/11/14 11:53am}}\footnote{$\rightarrow$\textbf{Suko T }Hee!!  That would be cute/scary.  The tattoos would be so easy with a sharpie on vinyl.  

I could see Hayley being Honey Lemon.  The precision would appeal.

Is Jonah Wasabi? :D

Which means Riva is Fred, our mascot. \textsubscript{12/12/14 12:36am}}while someone starts punching her in the face.  She has a pretty good guess that it's Rust since they are coming from someone quite a bit shorter than her.  Jaya's words are a little slurred but she sneers clearly enough, ``You hit like a fucking \textit{girl}.''

Rust gets in one last blow that makes Jaya spit out a tooth.  Rust leans down and picks it up.  ``This'll do.''  He growls at Jaya, ``Next time, \textit{don't fuck with me}.  We clear?''

Jaya spits a glob of blood at him.``I'll take that as a yes,'' says Rust, and spits in Jaya's face.  ``Don't make me do this again.''

Rust leaves.  He takes Jaya's gun, unchambers the bullet, ejects the magazine and drops it all on the floor.  Three guys remain, the two holding her shove her down while the third clips Jaya over the back of the head again, hard enough to make her dizzy and disoriented for a few seconds.  Jaya struggles to stay conscious.  They all leave before she can do anything else.



Jaya swears and eventually staggers to her feet.  She manages to find her gun and ammo, and makes sure that she has a bullet chambered.  It takes some time for her to figure out how to get out of the sub basement.  She emerges in the middle of the main TA office, clearly looking like she just got the shit beat out of her.  The low level flunkies in the area look very alarmed by her.  Jaya looks around and recognizes the Constable who abandoned her downstairs. She pulls herself upright, walks up to him and punches him hard.  Even though it's just her flesh hand, there is a nasty wet crunching noise and he goes down.



Jaya cracks her neck intimidatingly and walks out of the TA Station.  People on the street stay the fuck away from her.  Normally people give her a bubble of space but now they seem to be actively leaving the streets when they see her.  There is a rumor of a rough Senior Constable (or maybe an Agent) who loves to beat people up over water stations.  And also she has a cybernetic arm.  And is covered in blood.  And looks pissy as hell.


\sceneHeadline{Padme's Hideout- Jaya, Padme, Micah (toddler) and Garren}

Jaya goes by LA Ink, it's still burned down.  She spits a glob of blood on the ruins and then goes to her sister's new place.  It takes her a while to find it, but she eventually does.  The entryway is being guarded by Garren (the big guy who Jaya likes better than Ricco).

``What the fuck happened to you?'' Garren asks.

``Forget about it.  Take me to my sister.''  Jaya works her jaw a little and growls, ``None of your fucking business,''  as he stands there, gawking at her state of fucked up-ness. 

``Okay.  Uh, do you want a cloth or something?'' Garren offers her a dirty bit of cloth, it has some grease stains on it.

Jaya flexes her wrist and pops her Predator knife.  She enunciates very clearly,``Take me to my fucking sister. Right.  Fucking.  Now.''

``Uh...Padme!  Your sister's here!'' yells the guy over his shoulder, keeping an eye on her knife.  He leads her down the hallway.  Jaya stumbles after him, lurching a bit from side to side, occasionally running into a wall.



Padme is headed toward the alcohol cabinet when she sees Jaya and stops in her tracks.  ``The fuck happened to you?''

``Uhhhhh....'' Jaya replies cleverly.

``Micah, bring me my bag,'' says Padme to her little boy playing in the corner.

Jaya points out a few bottles from the alcohol cabinet, ``Bring me that one and that one.''

Padme brings two bottles and sets one down, ``That one is for drinking.'' She opens up the other one, ``You want to sit down already?''  Jaya slumps into a chair.  Padme looks at her mechanical arm and says, ``Can you put that knife away?''

``Oh yeah, sorry,'' says Jaya. Jaya stares at her arm, struggling to focus.  ``Waitaminit...wait....'' The wrist spins one way, then the other but eventually the knife retracts.

Padme starts cleaning her wounds with the alcohol.  It burns.  Jaya shrieks.

``You need to stop doing this,'' admonishes Padme as she begins to clean up the mess that is her sister's face.

``They gotta learn respect.'' says Jaya.  She yelps and then asks, ``How you doing?''

``Fine.  Did you bring \hl{more money}\footnote{\textbf{Suko T }We sorted it in game but just to confirm, Session 33, page 5 Jaya tells Morgan to give the money to Jayce and Page 7 Jayce leaves the base before we head out to SAC-04. \textsubscript{12/07/14 5:41pm}}?  I haven't seen your boy in over a week.''

``But he gave you the money?''``Yeah, but it didn't last long.  Especially down here.  I have to pay people to bring me shit without giving away where the fuck I am!'' complains Padme.

Jaya lets out a long suffering sigh. ``They don't care about you!  Stop hiding. Stop being difficult! You need to just take what I'm giving you and be fucking thankful- OW!  That hurts!!  And just please stop being difficult.  I'm having a hard time here.  I'm doing all I can.''

``It's not that I'm not grateful,'' says Padme and she pours more alcohol over Jaya's open wounds pointedly.  Jaya whimpers.  Padme continues, ``It's just that I don't know what I'm supposed to be fucking doing!  I don't really like it down here.''

Jaya says, exasperated, ``Go to a new station, find new men, find a new set up, find new people to ink.... do I have to fucking do everything here??  Can't you just-''

``Is it safe for me to leave?''  interrupts Padme.  Jaya pauses for just a little too long and Padme says angrily, ``So....No.'' 

``Do you know how to shoot a gun?''

``You going to give me one?  You know how hard it is to get ammunition?''

``If I give you a gun will you sell it?'' asks Jaya.``Nooo....definitely not,'' says Padme, almost sincerely.

Jaya hands Padme her service pistol. ``I'll tell them I lost it in the fight.''

Padme chambers it slowly.  ``Do you have more ammunition?  One magazine isn't very much.''  The sisters exchange a look and Padme says sarcastically, ``Sorry, I'm being... 'difficult'.''  She sighs and says more sincerely, ``I'll make it up to you with a tattoo or something.''

Jaya's eyes light up, ``Do you have your supplies here?  I could use some new ink.''

``Not here but I can send Garren to get them.''

``That's why you have no money!  You should bring people here and make some-''

``If I bring people here, they'll know where I am,'' says Padme.

``Well- well...why not have whatshisface give you more money for ink or something?'' She gives her sister a significant look up and down, clearly suggesting 'something' in particular.  ``I mean, get some money!''

Padme glares, ``Last I heard, the money was \textit{your} job.''

``And I got you some fucking money!  It cost me....a lot.  I don't think you know how much that money cost me.''  Jaya slaps the table, her eyes a little wide with remembered horror, ``You don't \textit{understand how much that money cost me}.''

``You're right.  I don't,'' says Padme and pours more alcohol over Jaya's arm. ``But I lost everything in that fire.

``But you still got that thing-'' says Jaya pointing at Micah.  ``And those ones,'' she points back toward Garren.

Padme sighs.  ``Fine.  You're right.  I just need it to end, okay?  So when's it going to end?''

Jaya pauses, ``Ummm....It's just that...we're at war.  There's a lot of shit going on...'' she doesn't have a good answer and changes the topic, ``You going to get the ink?''

Padme rolls her eyes and heads out with Garren to get her supplies.  She points to Micah and tells Jaya, ``Play with him for a while.  And can you feed him?  I'll be right back.''

``What??  No!''  Jaya protests but Padme is already gone.  She looks at Micah and pours a shot of alcohol into the cap of the bottle and hands it to Micah.  He snatches it and knocks it back greedily.  He starts choking and wheezing.  Jaya finds this hysterical and attempts, possibly roughly, to get him to try another sip.  Eventually he asks to see her mechanical arm and Jaya picks him up and starts spinning him around.  With improved wrist action, the spinning never stops and he thinks this is great, laughing uproariously.



Eventually Padme returns, bag slung over her shoulder, and demands, ``The fuck are you doing??''

``I'm fucking watching the kid!'' Confused by Padme's tone, Jaya hoists him up high to demonstrate and he giggles.

``Let him go.  Why is there vomit all over his shirt? What did you feed him??''

``I didn't do it.  I didn't vomit on him,'' protests Jaya.  Looking down at her nephew she does spot some vomit, now that Padme mentions it... 

``I didn't say you did.  \textit{Did} you vomit on him?''

``No...'' says Jaya.  Her stomach does churn slightly at the question, from the stress of her sister yelling at her and possibly all those blows that rained down upon her not too long ago.  Also, watching Micah spin for so long and so fast does make her feel a little dizzy... 

\hl{``Are you \textit{sure}?''}\footnote{\textbf{Suko T }Padme knows her sister. \textsubscript{12/10/14 12:08pm}}

``He's fine.  He's gotta get a tougher stomach if he wants to survive out here,'' She drops the kid with casual disregard.  

Padme says sternly, ``Micah, how did you vomit?'' 

Micah's eyes bounce nervously from Jaya to Padme and back again.  Jaya stares at him with the promise of retribution in her eyes.   Micah stutters, ``J-J-J-''

Padme sends Micah to the corner for a time out.  She turns to Jaya and asks her what tattoo she wants as she starts setting out her tattoo equipment.

Jaya takes off her shirt and sits down with her back to Padme.  There is a twisted nest of names tattooed on her back, most with lines through them and a couple that have been fully blacked out.  She reaches back and vaguely gestures to the patch of skin, ``I got a new one to add.  \hl{I just gotta put this behind me.}\footnote{\textbf{q.google }Literally. \textsubscript{12/15/14 6:23pm}}  It'll really help things.  Can you put 'Oliver' back there?''

``Sure.  What's the story behind this one?''

``Nah.  Nothing.  Just make it look fancy...and put a line through it.  I think there's space there.''

``Alright. Big?  Small?'' asks Padme.

``On the smaller side,'' says Jaya \hl{and she drinks steadily through the tattooing process.  To cope with the pain.  All of the pain.}\footnote{\textbf{Rebecca S. }http://simply-sithel.tumblr.com/image/104478594439 \textsubscript{12/11/14 12:33am}}\footnote{$\rightarrow$\textbf{Suko T }\textless 3 \textless 3 \textsubscript{12/11/14 1:24am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }\textless 3 \textless 3 \textless 3 +1 \textsubscript{12/12/14 2:59pm}}

Jaya eventually remembers the envelope and pulls it out of her pocket.  It's rumpled and blood stained at this point, parts of her clothing having gotten soaked through.  She scowls at the knowledge that the blood's mostly hers.  The letter is on official letterhead from Agent Command (HQ).  Turns out to be a commendation for performing above and beyond the expectation of duty in the protection of squad members. At the bottom is Agent Mohinder Lorentz' signature and seal.  And it really does have Jaya's name and serial number at the top of the letter (Jaya double checks).

Jaya grins and a drop of blood falls on the page.  She folds it up, smearing the blood on the page, and tucks the letter away.

Jaya gets royally drunk.  Jaya and Padme continue to squabble and at least come to sisterly terms by the end of the evening.  


\sceneHeadline{Annex Station- Jaya and Rook}

\hl{The next morning}\footnote{\textbf{Rebecca S. }Am guessing at time line here... \textsubscript{12/11/14 9:13am}}, Jaya heads back to the station. She is pretty well bandaged up but she still looks like she's been through a fight.  They call for a train for her and the wait for it's arrival is long and awkward for everyone on the platform.  After a bit, the train shows up and Rook steps out of the cockpit. 

\hl{Jaya salutes}\footnote{\textbf{Nathaniel Ford }WUT \textsubscript{12/11/14 11:53am}}.

Rook returns the salute, ``Agent.  We didn't expect you back so soon.''

Jaya flinches. ``I think I've had enough Shore Leave.  It's good to see you.  I actually really needed to talk to you.''  She walks up to Rook and puts her hand on his shoulder and tries to guide him back onto the train as she talks.  His shoulder is pretty solid, but he relents after a second and follows her onto the train.

``Before we talk about that, do you want to tell me what happened?''

``Oh it's nothing.  I got jumped-'' says Jaya, trying to wave it off like it's of no consequence.

``By?''

``Hooligans.  Maybe Agents of Octavius...who the fuck knows.  I got a couple of 'em, and they got a couple of me... but yeah, when I came to they had dragged off the ones that I killed.  And I'd been disarmed.... it's just a big blur.''  Jaya pauses and looks at Rook a bit hopefully, and points out her missing tooth, ``Hey, do you happen to have a replacement one of these things?''

``Why don't you have a seat and we can talk about that?'' says Rook calmly.

Jaya sits and winces as she's reminded of all her bruises.

Rook turns on his heel and walks out into the TA Station, the train doors closing behind him.  Jaya tries to follow but finds that the train doors will not open for her.  She punches the door with her fleshy hand and then sits down and defiantly lights up a cigarette.  After a moment, she thinks better of that and puts it out, resigning herself to just slumping in her seat as she waits.



After about five minutes, Rook returns and says, ``Agent?  Ready to leave?''

``Yep!  I was ready to leave when I got on the train,'' she says dryly.

``I was just checking.  We have to make one pit stop,'' he says and goes into the cockpit.

Jaya tries to yell through the cockpit door.  ``Are we picking up Hayley from her Shore Leave?''

Rook says over the intercom, ``Hayley's not on Shore Leave yet.  Like I said, we weren't expecting you back so soon.''

Jaya looks at the intercom and frowns.  ``Hey, I feel really weird talking over the intercom, can we talk in person?''

\textbf{{[}PC-initiated Scene- 1 token enters the pool{]}}



Rook says, ``Why don't you come join me in the cockpit?''

Rook opens the door.  The cockpit is a bit fancier than the one that Jaya saw in Cordoza when she killed Cyril.  There are a few more screens and one of the screens has a complicated diagram on it that looks like a train map.  Rook has his hand resting on a metal plate.  There are two seats.  He gestures to the other seat.  ``Please sit down.  What do you want to talk about?''

Jaya attempts to ask casually, ``Uh...a  couple of things....'' She looks down at the briefly lit cigarette that she's still holding.  ``Uh....so....  where'd ya drop off those tall guys?  The blondies.  Uh....Douglas.  Where did Douglas and them go?''

``Oh, you mean Douglas and Charlie Gamma One?''

``Yeah the chick.  Bitchy McBitchface,'' says Jaya with a sneer.  She rolls the cigarette between her fingers and avoids making eye contact with Rook.

``I dropped them off at Ark Station. It's pretty far up the line.''

Jaya nods, her attempt at looking nonchalant spoiled by her fidgeting.  ``Ark Station... that's cool.  You, uh, know what Douglas is doing while he's there? What he's up to there?''

``Up to?''

``Yeah.  I don't know...like stormin' another SAC or-''

``You do realize they aren't Agents, right? Nor Constables?''

``Yeah!'' Jaya's gaze flicks up briefly and she scowls.  ``I knew that!  I know that....''

``I believe that his primary goal was to get out from under Morgan's area of influence,'' says Rook calmly.

``Can't blame him for that...'' Jaya mutters with a smirk.

``Are \textit{you} wanting to get out from under Morgan's area of influence?'' asks Rook curiously.

``What??? \hl{No!!}\footnote{\textbf{Rebecca S. }Really?? ``No'' was said? I thought I tried to dodge that...hmm.. \textsubscript{12/11/14 12:38am}}\footnote{$\rightarrow$\textbf{Suko T }I felt like it was more a reflexive, ``no!'' cover-your-ass kind of thing than a true, ``I love Morgan'' thing. \textsubscript{12/11/14 2:16am}}`` exclaims Jaya.  Again her head jerks up and she looks Rook in the eye.  She quickly looks away and beings to scan the cockpit.  ``Er...is he like, setting up a sword shop or something? What's his plan?''

``He did not discuss his plans for the immediate future with me.''

``Are you- are you worried that he's going to attack the Directorate?'' Jaya is still fidgeting with her cigarette.  The paper is getting seriously frayed.

``No,'' says Rook with a half smile.  ``Should I be?''

``No, no.  Just that maybe we should keep an eye on him,'' she rolls her shoulders ``Tall scary dangerous person, ya know.''

``I believe 'keeping an eye on him' would be an express violation of the agreement we came to with him.''

``There was an agreement?'' says Jaya in surprise.  ``What's it say?''

Rook replies, ``He'd let us into SAC-04 in exchange for his friend, and once they left we would no longer attempt to follow their movements and we leave them alone.  You have to understand that they probably feel relatively threatened by us.''

``Yeah...'' chuckles Jaya, nodding in agreement and smirking to herself.  In Jaya's opinion, everyone should feel threatened by the TA.

``May I ask why you are concerned about him?'' asks Rook.

``Just, uh, tying up loose ends at the end of the mission.''  The cigarette has disintegrated into tobacco flakes and she dusts her hands off, sprinkling the cockpit floor with shredded cigarette bits.  



Jaya looks at Rook and says with a smile,  ``Hey- I have a different question!  So we were just on this mission.... And uh, there was this... `` she rolls her head a bit and gazes out the window of the cockpit, which shows nothing but blackness, ``We found out later it was a Praetor...and I ripped its head off, which was \textit{really }hard to do...'' a smile flits across her face, ``and then its head got up and walked away.  So I was just wondering.'' She turns back to Rook and stares at him intently ``If something happened to your head, would it get up and walk away?''

He half turns and looks at Jaya with a quizzical look on his face.  ``I find that extremely unlikely.''

``That it would walk away?'' She continues to stare intently at him, possibly leaning in a bit.

``Well, for the first part, my head lacks feet.  But assuming you meant a broader definition of walk-''

``It would be \textit{mobile},'' clarifies Jaya, annoyed at Rook's pedantic nature.

``My head?  I assume it would only be mobile insofar as whatever kinetic energy it had left after its separation from my body.''

``So..... you're like a normal person then.''  She doesn't sound convinced, though the hopeful note in her voices suggests she might wish to be.

\hl{``I'd like to think so.''}\footnote{\textbf{Suko T }Rook is so much BETTER than normal. \textsubscript{12/09/14 12:17pm}}

Jaya leans further in and gazes at the back of Rook's neck.  ``So.. if we were to cut you, you'd just bleed...like a normal person?''  Her tone is optimistic.

Rook says calmly, ``I think I begin to see what your concern is.  You ran across a Praetor who was particularly dangerous and you are wondering if I might pose a similar danger to you.''

``Yeah!  I mean, how hard would it be to subdue you?''

``I'd like to think it would be fairly hard to subdue me, but I also know that I am of no threat to you.  I will not harm you.''

Jaya looks really creeped out and in no way reassured by his reassuring statement.   ``And you... bleed red?''

Rook chuckles a bit. \hl{``To be fair Jaya, in theory one can make you bleed in places where you wouldn't bleed red.}\footnote{\textbf{Suko T }Rook teasing Jaya!  Squee!! \textsubscript{12/09/14 12:18pm}}\footnote{$\rightarrow$\textbf{q.google }For the official record though, the witness did \_not\_ answer the question. \textsubscript{12/15/14 6:27pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Rook works hard to allow everyone to be as relaxed around him as he is around them. \textsubscript{12/15/14 8:14pm}} For instance, your bile duct carries different viscera than your blood vessels.  Your brain is a kind of white-greyish material.  Pancreatic fluid is another-''

Jaya cuts him off, raising her hands  ``Ooookay!  You know what, I should have asked Jonah.  Nevermind.  I'm sorry.  I'm just going to go sit back there...'' She begins to back out of the cockpit. ``Do you mind if I smoke back here?''``I prefer that you didn't.  For your own safety.''

``I just need something to calm my nerves,'' Jaya says in that wheedling tone Dr. Gerhauser knows so well.

``Oh!  Well put your hand there,'' Rook says, pointing to another metal plate.

``Is it drugs?'' asks Jaya hopefully, and goes ahead, placing her hand on it.  She gets a weird tingle, sort of Operator-y but there's no person attached to the feeling and she feels even more in control

``Close your eyes,'' instructs Rook.  Jaya is very suspicious but eventually closes her eyes.

She can't see Rook's face but he sounds pleased as he says, ``We've come a long way in terms of trust between us.  This is pleasing to me.''

Jaya yanks her hand off the plate and gives Rook a sharp, suspicious look.

``Put your hand back on the plate,'' says Rook patiently.

``I don't like talking about trust. It makes me feel untrusting.'' says Jaya grumpily\textless 3, as she returns her hand to the plate.

``Interesting.  Now, think 'Interface'.''

Jaya laboriously thinks ``interface.''  The sensation travelling up her arm is very weird.   She starts seeing odd things.  Rook says, ``Now think 'Focusing Agent'''

``Focusing Agent,'' she says, under her breath to help her think.

There is a burst of light that reminds Jaya a bit like drugs or like being high up on the mountain when the calming colors all come together.  Jaya feels good.  She stands there with a dopey grin on her face.



They pull into another station.

Rook gets up and tells Jaya, ``You may stay here if you wish, but please don't touch anything else.''

Jaya pulls her hand off the plate and looks around.  ``What?  What's going on?  What station are we at?''  She is much more mellow than earlier.

``Terminus.  I need to run an errand.''

Jaya, realizing Vogel is in Terminus, eagerly asks  ``Can I follow you?''

``No.  Please stay on the train. It's not that I don't trust you, Agent, but stay on the train.  That's an order.''  Rook leaves the train.  Jaya starts to pout but then puts her hand back on the plate and relaxes.



After a few minutes, Jaya can hear a Code Black announced throughout the station.  People start rushing around.   She can see some Constables trying to peer into the tinted windows of the train and debate if there is anyone on the train.  For her own amusement, Jaya flips off the unseeing masses out the window, but makes no real movement.  She keeps her hand on the plate and easily ignores the situation as it escalates.  People are yelling about trains and shipments needing to come in.  One of the displays on the cockpit console is displaying ``Station: Terminus.  Status: Code Black.''



After about 30 minutes, Rook comes back and says briskly, ``I think we should be leaving now.''

``Yeah there's a Code Black now,'' says Jaya in a lazy, partially amused tone.

``I hadn't noticed,'' Rook deadpans.  He puts his hand back on the plate and the train departs



Jaya keeps her hand on the plate the whole way back.  It's not as good as drugs but it's pretty cool and she thinks it won't (shouldn't) piss off Dr. Gerhauser.




\jumpHeadline{Shore Leave- Jonah }
\sceneHeadline{Guest Quarters- Jonah and his family}

Micah comes by the PG1 Bunk and finds Jonah.  He asks Jonah, ``I had a message from Agent Gerhauser indicating that you wanted to see your family?  Now would be a good time, if you are free.''

``Yes,'' says Jonah and he gets ready and follows Micah to another section of the base.  They head down a corridor to some large blast doors with two sigils on them.  Micah swipes a card and puts his hand to a panel.  He hands Jonah a badge and explains the rules of visitation.  ``In other words, just go there when you're visiting.  And don't derelict.''

It's a long featureless hallway.  After a few minutes of walking, they come to another set of blast doors, where Micah repeats the procedure from earlier.  This door also has the same two sigils on it.  On the other side of the door there are two different sigils.  They look \textit{almost} like letters.



Micah points to the third door on the left. ``Your family is therein.  Please constrain yourself to this area.  If you need anything, I'll be available over the comm.  I don't see any reason to stay here.''

``Understood.  Thank you.'' says Jonah.  He asks if his family knows he is coming but they do not.  Micah walks down the hallway into another part of this section.



Jonah knocks on the door.  The door is flung open by Riva.  She looks like she's worked herself up into a huff but sees that it's Jonah and deflates a bit.  ``Oh!  Timon!'' she exclaims.

``Who?'' teases Jonah and gives her a hug.

``Uh...Jonah!'' Riva corrects herself and hugs him back.  ``I'm so glad you came!  Can we leave??  It is \hl{booooooooring}\footnote{\textbf{q.google }If only it was.... \textsubscript{12/15/14 6:30pm}} here!''

Jonah can see his mom lying in a bed, she seems to be sleeping.  There is an unattached IV next to her.  Jonah had spoken to Swan and Dr. Gerhauser and they told him that his mother was suffering from borderline malnutrition and pneumonia.

His father is sitting at a table, his hands are resting on the table.  There is glass of water in front of him, almost filled to the top, and he is staring at it intently.

Jonah greets his father. 

``Hello son,'' says \hl{Timon's father}\footnote{\textbf{Suko T }Can we please give his parents names? I know Franchise from Timon's area usually only have one name but they have no names at all... \textsubscript{12/10/14 2:33pm}}\footnote{$\rightarrow$\textbf{q.google }Done. \textsubscript{12/15/14 6:34pm}}\footnote{$\rightarrow$\textbf{Suko T }thank you!!  Much easier to transcript with names \textsubscript{12/15/14 11:40pm}}, looking up from the glass.  

``How are you?''

``I'm fine and your mother is much better,'' says Timon's father.

``I'm BORED!'' says Riva loudly.

Jonah's glance keeps flickering over to his mother but he tells Riva, ``Good.''

``\textit{Good??}  How is it \textit{good}?''

``It means that you're safe.  It means that you haven't gotten into too much trouble.  And it's a problem that I can fix.  So I'll call that a win.''

``If boring means being safe and never getting into trouble then \hl{I never want to be safe again}\footnote{\textbf{q.google }The universe is working hard to oblige you. \textsubscript{12/15/14 6:35pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Teenagers. They don't get it yet. \textsubscript{12/15/14 8:13pm}},'' pouts Riva.

``I'd \textit{prefer} to be bored.  How is mom doing?''

Timon's dad replies, ``She seems to be doing better. She's not coughing as much and she seems to be sleeping more deeply.   I don't really want to wake her.''

``No don't wake her, I'll be back again later.  She should sleep as much as she can.  They have very impressive medicines here,'' says Jonah

``How much does it cost?'' asks Timon's dad.

``It's not going to cost anything,'' says Jonah.

``Everything costs something,'' says Timon's dad with a frown.

``Oh.  In that sense you can consider it part of my job privileges.  Believe me, we have \textit{more} than earned them.''

``Very well.  Just so long as it's being honestly paid for,'' Timon's dad gives the glass of water another dubious look.

Jonah looks at the glass too.  He can't see anything wrong with it.

Timon's dad explains, ``Riva found out that this came out of the wall and ceiling...and it's so.... clean.  Are you sure it's safe?''

Jonah laughs wryly.  ``It took me a while to believe it.... but yes it is safe.''

``See Dad??  \hl{Why can't I bathe like the soldier man said???}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{12/11/14 12:51am}}`` pipes up Riva.

Timon's dad frowns at Riva.  ``Hush.''

Riva gives an exasperated huff and flops onto the bed. She asks the ceiling, ``Can we get out of here anytime soon?''

Their dad looks at Jonah, ``Is there a plan for us to stay here?  I don't like being idle like this.''

``Yes.  First of all, I'm sorry I didn't come earlier.  I was literally was out working up until today.''

``Considering the privileges, I believe that,'' says his dad.

``Tell me what you'd like, and I'll see what I can get.  Our biggest restriction is this- home is not safe so you will have to stay here for the time being.  It's going to take some getting used to, Dad. A lot of what is here I never would have imagined existed,'' says Jonah.

Timon's dad doesn't seem to really comprehend the implications of what Jonah is saying, but nods in acknowledgement and says, ``I don't know what I can do here.  I can...herd animals.  Cook.  Clean.  Carry... I don't know if you need these things but I don't think I'm being of much use in this.... cell.''

``Who else has been to visit?'' ask Jonah.

``A nice doctor man.  A less-affable doctor lady, very tall.  And one man who brings food on occasion.''  He describes Jari. ``And the soldiers.''

``Jari is very pleasant and he cooks.  I will talk to him.  Very possibly he can use the help.''

Timon's dad nods and says, ``Perhaps Riva can help too.''

Riva rolls her eyes at her dad.  She turns to Jonah, ``Hey are there any kids here?''

``Yes.  You.''

``Ugh!!  This place gets worse and worse!''

``There are things you can do to not be bored,'' says Jonah a little smugly.

``Like not bathe?  'Cause \textit{that's} really interesting\footnote{\textbf{q.google }I very much doubt that she's ever bathed. \textsubscript{12/15/14 6:38pm}},'' says Riva snidely.  She suggests, ``What about that lady on the train? She promised to teach me stuff.''

``I don't think she will, but I did make arrangements for someone to teach you 'stuff'.''

``Like what?  Fighting?'' says Riva, interested.

``Potentially, but first \textit{other} stuff.''

``Like what?'' says Riva suspiciously.  ``This isn't boring bandage cleaning is it?

``It's a little hard to describe but everything they do here is a little...crazy.''

``Crazy is good!''

``I'll talk to my superior officer and have him present your choices to you, because I think he'll do a better job of it.''

``Okay.  Can we go now?'' asks Riva quickly.

``No, but probably in the next few days.''

``Okay....so what am I supposed to do until then?''

``Tell me what you think of this place,'' asks Jonah.

Riva complains, ``It's boring.  Seriously there are these four walls cut of some kind of rock. There is that annoying low level humming.''

``You're going to have bear with me,'' asks Jonah.

Riva says in an annoyed tone, ``Give me something!  \textit{Jonah}.  What about\hl{the girl}\footnote{\textbf{Rebecca S. }THE girl?  WHAT, there was only ONE girl?  FUCK YOU, RIVA! \textsubscript{12/11/14 12:53am}}\footnote{$\rightarrow$\textbf{Suko T }Jaya, there was only one girl.  And only one woman. :D \textsubscript{12/11/14 1:36am}}\footnote{$\rightarrow$\textbf{q.google }You did see the ``other girl'' part right?  She didn't mean Signy. \textsubscript{12/15/14 6:39pm}}then?  Is she busy?''

``Yes.''

Riva sighs in frustration.  ``What about that \textit{other} girl?''

``They are very busy.  In fact they are probably exhausted,'' lies Jonah.

``How can they be exhausted?  It is soooooo boring here!  What work are you doing that is not boring?''

Timon's dad actually raises an eyebrow and clearly also waits for Jonah's reply.

``You don't want not-boring because then you don't come home again,'' extemporizes Jonah.Timon's dad frowns.

``That's clearly not true.  'Cause you're here!  You always come back!'' protests Riva

``That's good!'' says Jonah all friendly and smiling all of a sudden.  ``So you expect me to come home?''

``Yeah but I didn't expect you to take so long, normally you return faster.''

Jonah promises again to talk to his SO and he teaches Riva some new card games.  She is placated for a while.

Jonah decides to tell Rook that he'd like to do the traditional teaching method first and then possibly do the other things later, once she has learned more.


\sceneHeadline{MedLab- Jonah and Trenton}

Jonah goes to see Jari and asks if his dad can help him. Jari is pleased with the offer, saying that he is very understaffed and he's been asking Morgan for help for a while now.  Jari's not bothered by Timon's dad's inexperience (with the tech and drinkable water on demand), he says it always takes a bit to get the staff up to speed on how things work here.



Jonah goes looking for Trenton. When he can't find him in the Lab, he goes down to MedLab to Signe's room.  Hayley is not there.   Trenton has set up a small makeshift table which is already covered in paper and datapads.  Signe is sleeping in the hospital bed, in a sedated state of unconsciousness.



Trenton looks up and greets Jonah, ``Oh hey, what's up?  How's it going?''

``Surviving...ish.  You know.''

Trenton looks around, ``Sorry, I don't have anything to offer you.''

``No that's okay, I brought something,'' says Jonah and pulls out a bottle of liquor.  

``Don't let Swan see us,'' stage whispers Trenton as he pours them each a glass, hands one to Jonah.  And keeps the bottle.

``How you been doing?'' asks Jonah, looking over at Signe meaningfully.

``Yeah.  I'm good!  Thank you.  I hear I have you to thank,'' says Trenton.

``Yeah.. I wanted to talk to you about that.  I don't know what they told you.  So how about you tell me what they told you and I'll fill in the rest,'' says Jonah cautiously.

``So the issue is that she has some hardware in her that they are attempting to use to take control again.  And you stopped them by effectively stopping the software,'' says Trenton

``Right.  Which means as long as it's happening, she's going to be on the other end of an Operator connection.''

\textit{``Yours} though, not theirs.  That's a win,'' says Trenton.

``Yes.''  Jonah isn't sure it's a win -- but if Trenton believes it then \textit{that} is a win on Jonah's end.  I don't know what they are doing to her.''

``I don't believe they are doing anything to her.''

``According to Rook, they can't.'' says Jonah slowly.

``Problem solved,'' says Trenton briskly.  ``I believe Rook when he says that and I haven't been introduced to the math that would make me feel otherwise.''

``Oh, okay,'' says Jonah sounding relieved.

``I think at this point it would be as easy to hijack her signal as it would be to hijack any of your signals.''

Jonah looks paranoid again, ``How easy is \textit{that}?''

``Astronomically hard.  More than astronomically hard, actually.''

Jonah asks Trenton to explain what that means.

``So you wouldn't be able to-'' says Jonah.

``Not unless I had all the computing power in the universe.''

``That's actually one of the most comforting things you've told me,'' says Jonah with a sigh.

Trenton nods.  ``That's why it was a good plan.  Actually, I came up with the plan, but didn't realize I came up with the plan.  So score one for Victor.  He got a bonus for that.  Not the one he wanted, but let's be honest, he had no chance.''

``As long as you're cool with it.  You'll let me know if you stop being cool with it?''

``Yeah.  Don't worry, if I cease being cool with it, you'll find out pretty fast,'' says Trenton, still smiling but definitely not joking.  ``And you, let me know if anything changes on your end.''

``Yes.  I'm still figuring things out. Everything else I have been taught is by people who knew it already.''

``That seems sad.  Haven't you ever wanted to figure something out that no one has figured out before?''

``Yeah....but not when it's in my head. There are things that you can learn that don't involve risk to life or sanity.  I prefer those,'' says Jonah a bit primly.

``Okay.  I get it.  \hl{But just as a heads up, all the funnest things require some risk to sanity. Just ask Victor!   He's \textit{great}.}\footnote{\textbf{Rebecca S. }favorite line of the night \textsubscript{12/11/14 12:59am}}\footnote{$\rightarrow$\textbf{Suko T }Trenton is a smart man. \textsubscript{12/12/14 12:37am}}\footnote{$\rightarrow$\textbf{q.google }Yes -- but also one who has never been hungry. \textsubscript{12/15/14 6:45pm}}`` Trenton laughs.

Jonah brings the convo back to Signe and \hl{reassures Trenton that stuff really only bleeds through during moments of high stress and usually there's not much}\footnote{\textbf{Rebecca S. }Lies! Lies! Lies! \textsubscript{12/11/14 1:02am}}.  Trenton seems okay with this.  Jonah reiterates that he wanted to make sure Trenton knew about him being Signe's Operator.



Jonah asks Trenton about what schooling is like.  ``None of it involves...hypnosis?''

``Have you been talking to Rook again?'' asks Trenton, almost, but not quite rolling his eyes.

Trenton says \hl{he's not allowed}\footnote{\textbf{Rebecca S. }whyyyyy? \textsubscript{12/11/14 1:03am}}to use the hypnosis learning technique but it should work.  There is a risk of neural burnout if you use it too much, like doing LSD too much. Jonah probably conceals his alarm.  Probably. 

``But you weren't taught that way?'' asks Jonah.   He has been waiting for this confirmation from someone other than Rook or Dr. Gerhauser.  He resolves to tell Rook to start Riva with ``regular'' teaching (already way beyond anything he ever had).

``Nope, I'm just brilliant naturally,'' says Trenton smugly.

``There are smart people and not so smart people.... are you way ahead of the pack?'' asks Jonah, trying to get a sense of scale.

``Yes,'' says Trenton without hesitation.

``Gerhauser seems to be relatively impressed,'' says Jonah.

``With me?'' says Trenton, surprised.``Not that she'd ever tell you.''

``Huh.  Interesting.  That little minx,'' smirks Trenton.

``Don't get the wrong idea of what 'impressed' means.  She thinks you're clever,'' says Jonah, also grinning.

Trenton drawls lazily, ``Ah, but that's how you get those kinds of girls.''

``Yeah.... don't do that,'' says Jonah.

``Why?  You want her?'' teases Trenton.

Jonah freezes and gets a very strange look on his face.  

``OOooookay....'' says Trenton, not expecting that reaction.

Jonah unfreezes and continues talking about something else, as if nothing happened.  ``Do you know what a Praetor really is?''

``I think I hear Swan,'' says Trenton, and he tucks the bottle away under Signe's blanket. ``Let's just say I think they are more than meets the eyes.  I will say they are very territorial.''  

``You could say that again!'' says Jonah fervently.  He lets out a big sigh of relief.  ``Okay.  Good.  Glad I could help.''

Dropping his habitual smirk, Trenton says, sincerely, ``Thank you, \hl{I owe you one}\footnote{\textbf{q.google }That phrase is better than gold in Jonah's world. \textsubscript{12/15/14 6:48pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }\textgreater \textgreater  insert sophomoric snort giggle here \textless REBECCAxxBEGINxxFOOTNOTExxREPLYxxSuko T xxHERExxISxxTHExxFOOTNOTExxHa!  I am snickering madly in the corner with you Rebecca. :) \textsubscript{12/15/14 11:52pm}}.  Seriously.  Just don't tell anyone.''

Jonah leaves MedBay.




\jumpHeadline{Shore Leave- Hayley }
\sceneHeadline{\hl{Morgan's Office- Hayley and Morgan}}\footnote{\textbf{Rebecca S. }Excellent scene, once again between Hayley \& a Gerhauser.  The hilarity mixes with sadness and gets all toxic... I think I like Dr. G's scenes better though, they hurt less... \textsubscript{12/11/14 8:42am}}

After the fight in the hallway (and after Hayley determines that she's not actually needed in Ops), she heads to MedBay and carefully tends to her bruised jaw.  Swan isn't there but Hayley helps herself to the supplies she needs without a thought.  Lavish application of cold compresses and anti-inflammatories.  She treats her other bruises too but with less care/concern since they are on her torso and not her pretty face.  She is limping more than usual.



Hayley gets summoned to Morgan's office.  She puts on one of her nice new uniforms and takes a bit of extra care to hide the jaw bruise with makeup (she's very good at it).  She has her rifle with her.  And the ammo she never returned to Jari.



Morgan's office is tidy and neat.  It is a circular room with various inset panels with murals in them.  To one side there is a cot made up with military precision, things neatly stowed in a footlocker, a faint whiff of weapon grease in the air.  Morgan is at her desk, a data pad to one side.



Hayley salutes.  Morgan looks up as Hayley enters, stands and returns the salute, asking, ``Are you planning to shoot me?''

Hayley looks confused and says hesitantly, ``No, sir?''

``Would you mind placing your weapon by the door?''

``Of course,'' Hayley leans her rifle by the door, carefully placed so that it can be grabbed and used quickly.  She says earnestly, ``You said I need to be ready.... for when people attack me.''

``Interesting.  So you find a rifle is useful for close personal protection?

``It can be.''

Morgan walks around to the front of her desk and leans against it.  ``Is that your weapon of choice?''

``Yes?'' Hayley's voice ends on a questioning note.

``Explain your reasoning.''

Hayley looks like she's at a loss for words.  ``It was- it was what I was taught to use?  This one I know the best.''

``Two things.  First, I don't think you really believe that.  So \hl{explore your feelings}\footnote{\textbf{q.google }This sentence must have come from someone else's dialog and wormed its way in here.  And now it's holding on with all of its tentacles and not letting go. \textsubscript{12/15/14 6:50pm}} on that more.  And secondly, if it \textit{is} the weapon you know best, you may not want to advertise this to your enemies.'' 

``Why?''

``Because then they know what to prepare for.''

Blank look from Hayley.  ``I don't really understand, but I'll think about it,'' she promises.



Morgan clears her throat and says to Hayley, ``I need to send you on a pseudo-diplomatic mission.''

``Yes,'' says Hayley obediently.

``Mohinder requires a sheaf of, for lack of a better term, documents that I am to provide to him.  However we don't wish you to be seen in the Directorate, so we will be sending you to SAC-04.  While you are there, I have a second mission for you.  I have arranged for you to undergo some training with other Agents that are there.''

``Thank you, Sir,'' says Hayley.

Morgan continues, ``While you are there, you are to take note of the entire layout, defenses, any items of note that you can.  If you can, without attracting any attention, gain access to any \hl{more sensitive areas}\footnote{\textbf{q.google }I can almost see the quotes, floating around the words. \textsubscript{12/15/14 6:51pm}}, I would appreciate details on those as well.''

``What is a sensitive area, Sir?''

``Command centers, medical bays, \hl{personal quarters}\footnote{\textbf{Suko T }Subtle Morgan.  Subtle. :) \textsubscript{12/10/14 1:40am}}\_Marked as resolved\_\_Re-opened\_\footnote{$\rightarrow$\textbf{Rebecca S. }(oops! wrong button click)
I think I actually flinched when she said this. So much ``NoOOooooOOooOOOO!'' was had. \textsubscript{12/11/14 1:09am}}, supply areas, areas where they may be doing any kind of research or development.  Any area that they have more security around,'' says Morgan.

``Places where there might be secrets?''

``Yes.  However I don't want you to take too much time, I want you there for the length of the training.  I do not wish for this to be noticed by them.  Do you think you can do that?'' asks Morgan.

``I am not very good at lying,'' says Hayley honestly.  ``But...I think I can at least look around.  I am good at looking,'' she offers.

``That's all I want you to do.  Take every opportunity that is presented to you to look around.''

``I will.''  Hayley pauses and when she's not immediately dismissed, she asks, ``I have a few things I would like to mention to you, Sir.  If there is time.''

Morgan gestures for her to continue.

Hayley says slowly, ``I....understand that it is very important that we have allies in Terminus.  I believe, although I cannot give you too many details without orders, that I may have aggravated Senator Emeritus Langdon during my last shore leave in DX Station.  I caused him to be denied something that he seemed to...want.''

\hl{Morgan is silent for a moment and then says neutrally, ``Tell me that this is of a business nature?''}\footnote{\textbf{Rebecca S. }\textless 3 \textsubscript{12/11/14 1:10am}}

``Yes,'' Hayley looks puzzled, her expression saying, 'what else could it be?'

Morgan lets out a long slow breath.  ``What did you deny him?''

``Are you ordering me, as my contract holder, to tell you, Sir?'' asks Hayley carefully.

``Are you uncomfortable discussing this with me for some reason?''

``I can only discuss the matter with my contract holders.''

``If that's true, why are you asking me for permission?'' Morgan stands up and walks back around to sit behind her desk.

``Because there are two of you and I need the order clear,'' says Hayley.

Morgan looks intently at Hayley.  ``You do understand that there is a very good possibility that if she's not already dead, Gillian will be.''

Hayley's expression goes blank and she says quickly, ``She's not dead.''

Morgan clears her throat and repeats, ``You understand that if she is not already, there is a good chance that Gillian will be.''

Pause.  ``But she's not dead \textit{yet},'' insists Hayley, her voice a little wobbly.  

``That is correct.'' says Morgan. ``As far as I know.''

Hayley clenches her hands together nervously and unconsciously reaches for her rifle where it should be at her side, and looks clearly distressed when it is not.

``I think I can surmise the general gist of what went on with Senator Langdon.  I think we have options to smooth it over.  If you have any particular ideas, let me know,'' says Morgan.

``I don't have ideas, but I do have other information.  Not just on him, but on others in the... Directorate.''

``Oh?'' Morgan sounds interested.  ``Such as?''

``Inappropriate liaisons, political and business deals...'' Hayley closes her eyes and walks through her memory palace, reviewing the documents she memorized.  ``Also, some... proclivities that would likely cause awkward social-''

``Can you provide these to me?  Write them down in your spare time,'' Morgan looks at Hayley and clarifies, ``\textit{Not} while you are at SAC-04.  Provide this to me at your earliest opportunity.''

``Yes sir.''

``Is there anything else that you wish to discuss?''

``Yes sir.''

Morgan's expression is unreadable (to Hayley) but she nods for Hayley to speak.

Hayley clears her throat nervously, her shoulders are a little tense, and she confesses solemnly, ``I was, um, extremely rude to Mr. Hadef and as my contract holder you may have to provide him with restitution.''

``Trenton Hadef?  So what did you do to Mr. Poseidon?'' asks Morgan with the hint of a smile.

``I didn't address him by name and he was being very polite and I was.... rude.  I asked him for something,'' says Hayley quickly.

``What did you ask him for?'' asks Morgan with admirable solemnity.

``A cot.''

``You asked Mr. Hadef for a cot, you failed to address him by name and you were rude at the time.'' summarizes Morgan.

``I didn't face him while speaking to him,'' says Hayley.  ``I know I'm not supposed to anyway because of my orders but I think those orders don't count anymore.''

``Take off your jacket,'' orders Morgan.

``Yes sir,'' says Hayley, unperturbed, and she removes her jacket.  Her shoulders have relaxed.

``\hl{Drop and give me 100}\footnote{\textbf{q.google }Morgan's ``Speak Hayley'' skill is at least a 2. \textsubscript{12/15/14 6:53pm}},'' says Morgan.

Hayley drops to the floor and does 100 pushups. They start out well but about midway they falter as her recent injuries make it hard to keep perfect form.  Morgan gives her pointers to clean up her form.  Hayley looks frustrated at her sub-par performance.

When Hayley has completed the 100, Morgan says, ``I consider you to be duly punished.  Do you understand?''

``Thank you sir,'' Hayley looks appreciative and a little relieved.  

Morgan gestures for her to sit, which she does.  ``However your form was slipping towards the end there.  I expect you to double whatever upper body regimen you are doing and increase your core work.''

``I'll- try,'' says Hayley hesitantly.

``I will speak to Hadef and make sure he is properly restituted,'' says Morgan with a straight face.

``Thank you sir.  I'm sorry that you were put in that position.'' Hayley says contritely.

``\hl{I don't want you to say sorry, I want you to never put me in that position again}\footnote{\textbf{q.google }Possibly a 2.5 \textsubscript{12/15/14 6:54pm}}.''

``Yes sir.''

``I don't care about screwups, just don't make them twice.''

``I try not to.''

Morgan frowns.  ``I don't ever want to hear the phrase, 'I try' to come out of your mouth again.  Just do.''

``Yes sir.''

``Even if you fail.  \textit{Do}.''

``Yes... sir.''

``Is \textit{that} all?'' asks Morgan.



``No, Sir.''  Hayley looks earnestly at Morgan.  ``I have read the handbook.  And I understand about fraternization rules.  But as my contract holder, do you have any additional restrictions on who I am allowed to have sex with?''

Morgan's gaze shifts to the side but she manages to keep her composure, though it's a moment before she speaks, ``Agent, are you asking me for permission to have sex with somebody?''

``Can I?'' asks Hayley with surprise.

``Do you believe that it would impact the execution of your duties?''

``I don't know, I've never done my duties while having sex with somebody.''  Hayley pauses and then adds, ``Actually that is incorrect.  Sometimes my duties \textit{were} to have sex.''

Morgan sighs.  ``I am aware of some of your background.  I am...not sure that if you have relationship questions, I am the appropriate person to ask.  My sister may be a better bet.''

``As my contract holder, you are the one who establishes the rules,'' says Hayley, a little anxiously.  ``Ms. Vorrutyer was \textit{very }clear on who I was allowed to have contact with.''

Another pause before Morgan says, ``Do you have any reason to believe that those guidelines should be changed?''

``Yes.  The TA Handbook fraternization rules are different from the social ones.''

``And under the social rules, who is included that is not included under the TA guidelines?''

``That it should be anyone who is of social advantage.  Or- not \textit{dis}advantage.  Certainly do not wish to bring any shame to the house.'' Hayley says this smoothly as if reciting something memorized and then stammers a bit, ``I- I don't know.... what that means for SAC-09.  That is why I am asking.''

Morgan sighs and asks, ``I suppose you're not familiar with the concept of a rabbit hole, are you?''

``No. Should I be?''

``Has my sister spoken to you about medication?''

``Do you mean the hormone therapy?  Yes, sir.''

``Did you make a decision on that?''

``Yes I have, Sir.''

``That you told my sister?''

``Not yet sir.''

``What is your decision?''

``Uh...door one.  Continuing the hormone treatment?''

``So I suppose we should address this now.'' says Morgan and then is silent for a bit.  ``You realize I am poorly equipped to handle the details of your sex life.''

``No.  W-why?''

``Because I am not \textit{you}.  Because the protocols under which I would make such a decision are almost certainly radically different from yours.''  She looks thoughtfully at Hayley.  ``But I suspect that you don't have much in the way of personal protocols, do you?''

``No,'' says Hayley, looking at Morgan hopefully.

``So.  Your first objective would be to perhaps consider what sort partner would be appropriate for \textit{you}, rather than for your contract holder.  I will explain this in as much detail as I am capable of without \textit{actually} having a PhD in psychiatry.  If you perform the...act... with a partner whom you are not emotionally....safe with, you are liable to experience emotional turmoil which will impact your ability to perform your duties and to generally be the best human being you can \textit{possibly }be.''

``And I want that!'' says Hayley eagerly.  She says more solemnly, ``And I know.... about about what you described.  That's how it usually is.  I hate it.''

``\hl{So I recommend not doing things that you \textit{hate}}\footnote{\textbf{q.google }Catching up on weeks of missed irony supplements. \textsubscript{12/15/14 6:57pm}}.  Or people for that matter.  Though that can be fun sometimes, or so I hear.''

Hayley looks revolted at the idea, ``I don't understand how.''

Morgan clears her throat again and says, ``I can perhaps help guide you on a case by case basis.  If you have someone that you wish to run by me...?  But I do not believe that is appropriate for me to lay down guidelines on this matter except to say that it is my desire and my intention and my \textit{order} for you to protect your mental and emotional health as much as you protect your physical health.''

Hayley looks very pleased.  ``Thank you!  I appreciate that.''  She pauses and asks, ``So....what do I do next?''

\hl{``Is there anyone that you wish to run by me?''}\footnote{\textbf{Suko T }Morbid curiosity got Morgan, didn't it? \textsubscript{12/09/14 7:01pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Is it morbid? Then Morgan is probably into it. \textsubscript{12/12/14 2:55pm}}

``There are a few I have considered.  This is very new so I am not certain that it will work.  I might hate it, also.'' says Hayley frankly.

``These are people you'd consider sleeping with?''

``I think so,'' says Hayley.

``Such as?''

``Uh...Operator Gemayel.''

``Anyone else?''

Hayley looks like she's thinking hard.  ``Ummm....I contemplated Operator Carruthers also. She's very nice.''

``That's a bit to be expected,'' says Morgan.

``It is?'' Hayley is surprised.

``Usually there's a bit of emotional backwash in these systems.''

``Oh.  I thought you meant it was expected that she was nice.'' 

\hl{Morgan says gravely, ``I expect all of my soldiers to be proper.  And nice.  Except when they are expected to kill.''}\footnote{\textbf{Rebecca S. }Second favorite line of the night.  Also, pairs well with pervious Eating Crow session. \textsubscript{12/11/14 1:17am}}

Hayley looks a little worried. ``Oh.  We may have to work on that, Sir.''

``You always do.''

``I- I do!'' Hayley clearly was about to say 'try' but catches herself in time.  She continues, ``I have not given this a lot of thought.'' she falls silent as she thinks this over.

Morgan cautions, ``I would be careful about sleeping with your squadmates because you are liable to be with them for some time.  That said, if it doesn't cause problems and you don't tell me about it, we're all good.''  Morgan clarifies, ``And by 'me' I mean your superior officer.  They almost \textit{never} need to know.''

``But what if they ask?'' wonders Hayley.

``Ah.  Then you have to determine if they are asking because they want or need to know, or if they are asking to get plausible deniability,'' says Morgan.

Hayley looks horrified at this prospect and clearly doesn't seem to understand what all these words mean.

Morgan clarifies, ``If someone asks for plausible deniability, what they want is for you to say 'no, I have not slept with anyone.' \textit{Even if you blatantly have}.  So now they can turn to \textit{their }superior officer and say there isn't any fraternization going on between ranks  Because it isn't a problem, they can say that and still follow their general orders.''

Hayley looks troubled, ``Fraternization \textit{between} ranks is a problem also?  I thought it was only across ranks.''

``Anything that would impact discipline is a problem.  For instance, if you were to sleep with Operator Gemayel.  And then sleep with Operator Carruthers, and Operator Gemayel was to become jealous of you sleeping with Operator Carruthers, it may pose a problem.  It may cause his concentration to waver when he is performing his duties.''

Hayley looks mostly befuddled by all this, but takes a desperate guess, ``Is this workplace romances?''

``Yes.''

``\textit{This} again,'' says Hayley, sounding a little frustrated and annoyed.  ``Is there someone I can talk to who can explain this to me?''

``My sister holds a PhD in Psychiatry.  \hl{Though you'd never know it.}\footnote{\textbf{Suko T }Totally believe they are sisters from this comment alone.  \textless 3 Morgan. \textsubscript{12/10/14 12:51am}}''

``Oh.  I'll ask her then.''  Hayley thinks for a bit and asks, ``If the rules are flexible-''

REBECCAxxBEGINxxHIGHLIGHTxx``The rules are \textit{not} flexible,'' interrupts Morgan. ``But your ability to move \textit{within} the rules is fairly flexible.''

``Oh!'' exclaims Hayley, actually sounding like she understands that.xxENDxxHIGHLIGHT\footnote{\textbf{q.google }Emotional level-up.  In one fell swoop. \textsubscript{12/15/14 7:00pm}}\footnote{$\rightarrow$\textbf{Suko T }Actually this is just ``rules clarification'' nothing newly emotional about that.  The emotional level up is in the next section. \textsubscript{12/16/14 12:08am}}  ``Hmmm.  May I assume that these rules apply also to across-ranks fraternization?''

Various emotions pass over Morgan's face.  Hayley can't read a single one of them. ``I will return to my previous answer.  If it's not going to impact your duty.  Satisfied?  Go to.''

``Thank you,'' says Hayley sincerely.  ``That was very helpful.  Thank you.''

``I would warn you about power dynamic.  But perhaps you can take that up with my sister.  Now, I hesitate to ask this question, but do you have anything \textit{else} to ask?''



``Just- a speculation?  Thought??'' says Hayley hesitantly.  ``When I-  When we- When I was with Operator Langdon, I think I saw through the eyes of Octavia.  I mentioned that, I think. She... began....''  Hayley takes a deep breath and reaches for her gun again, which is not there.  She instead twists her fingers together tightly.  ``She began...cutting into Ms. Vorrutyer in a way that I am....\textit{very} familiar with.  I- I wondered....It seems like...other women have suffered this also.''  Hayley's voice trails off until she is almost inaudible at the end.  She takes a few shaky breaths before continuing.  Morgan waits, utterly still.  The silence is very loud.  Hayley eventually starts speaking again ``I- I think that there are other people who have been killed that way.''  She closes her eyes briefly and corrects herself.  ``I know that they have.  I read- I read the reports.  I saw the pictures,'' she whispers.

``Official reports?'' asks Morgan intently.

``Some of them.  Some of them were just articles...obituaries.''

``Do you have these reports?'' asks Morgan.

``I don't have them physically.  Just in here,'' Hayley taps her forehead with her finger. ``I... memorized them also.''

``Do you believe that Octavius is connected to those murders?''

``I don't know.  I just thought that she had learned them from...someone.'' Hayley's voice is shaky.

``Who?''

Hayley looks even more distressed and shifts uncomfortably in her chair, ``I'm not allowed to say.''

``Why are you not allowed to say?''

Hayley takes a deep breath, and says in a small voice, ``Because I have been ordered not to.''

``Do you wish me to countermand that order?'' asks Morgan

Hayley doesn't look away from Morgan, and says very carefully, ``You can.  If you want. To know.''

``I want to know if \textit{you} want \textit{me} to countermand the order,'' says Morgan equally carefully.

Hayley looks away from Morgan and is silent a long time.  Finally she faces Morgan and says, ``I do.''

``Consider the order countermanded.''

A bit tremulously at first, her eyes darting around a bit, Hayley says, ``I do not have the direct proof, but I believe that Samson Vorrutyer is responsible for the torture and murder of at least 17 women between the ages of 21 and 23.  All members of the Directorate, a few Citizens and Franchise, but mostly Nationals and Incorporated.  No assailant was convicted or identified for the deaths.  Their deaths occurred over the last 40 years but they appear to have stopped after my contract was purchased by Mr. Vorrutyer three years ago.  The torture appeared to increase in intricacy and amount over the years.''  Though her words are dispassionate, Hayley is clearly barely holding it together through this recital.  Midway through she starts focusing on Morgan, using the eye contact like a lifeline to pull her through this.  Her whole body is trembling.

``You have good discipline, soldier,'' says Morgan, holding Hayley's gaze steadily.

``Thank you sir,'' whispers Hayley.

``I will need to think about that information.  And when you are able, perhaps we will speak of this again later.  You are dismissed.''

``Thank you sir,'' says Hayley, her voice almost breaking.  She gets up quickly and grabs her rifle and heads to the elevator door.

``Agent,'' says Morgan. 

Hayley turns around and swallows hard.

``If you are ever being violated in any way, you have my permission to kill the antagonist.  Do you understand?''

Hayley sighs softly and smiles tremulously, though her eyes are full of tears, ``Thank you sir.''

``With extreme prejudice.'' Morgan stresses.

``I understand sir,'' says Hayley, barely audible.

``You are very valuable to me and a number of other people.  It is absolutely imperative that you defend yourself against all comers.  Is that clear?''

``Very.  Sir.  Thank you.''  Hayley manages to say.

``Very good.  I will send your orders around for when you are to depart.  Dismissed.''

Hayley turns sharply and steps into the elevator, pressing the door close button almost blindly.  \hl{As the elevator doors close, Morgan can see Hayley's shoulders sag and hear her start crying.}\footnote{\textbf{Suko T }Holy crap this whole scene was a freaking amazing emotional rollercoaster.

Morgan wins the Hayley Experience(TM) game. \textsubscript{12/10/14 3:01pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I would love to have your player analysis of what is going on. I loved the scene as well, but I'm more in Morgan's head than Hayley's. \textsubscript{12/11/14 2:21pm}}\footnote{$\rightarrow$\textbf{Suko T }Sure!  Will try to send you something.  I am so curious to know what was going on in Morgan's head through this but I expect that I'll just have to speculate for now :)

Oh and unless she's learned how to put up better blocks, Carruthers probably got some emotional bleed from this scene and definitely the SAC-04 interlude. \textsubscript{12/12/14 12:43am}}\footnote{$\rightarrow$\textbf{q.google }''Holy crap this whole scene was a freaking amazing emotional rollercoaster.''

And a mindbender.  Both of them are speaking quite a bit outside of expected boundaries. \textsubscript{12/15/14 7:03pm}}


\sceneHeadline{SAC-04- Hayley and Drake}

Hayley arrives at SAC-04 and Drake greets her at the train station.  Hayley notices the gold veins in his eyes and thinks they are pretty.  She tells him so.  ``Thank you, they rather fit me,'' he says.  Hayley agrees.  



``Glad that you are here, you'll dine with the command staff tonight in Mess Hall 6,'' says Drake as he escorts her into the base (no need to hike up the mountain anymore).  A temporary bridge has been installed across the river.



There are other people there at SAC-04, not a ton, but certainly more than before.  There is a lot of training going on in the upper areas.  A gunnery range has been set up.  They are clearly forming an \hl{Elite Fighting Squad.}\footnote{\textbf{Suko T }Jaya, your team is being trained up for you... isn't that nice of Drake? :D \textsubscript{12/10/14 11:37pm}}



The people in the village are still there.  The couple sitting on the hill are still sitting on the hill.  When Hayley walks by a window, that same woman is inside, weaving.  All this doesn't bother Hayley because she's used to people standing around like robots.  There are some people in the village with their heads caved in or massive injuries and yet they seem... kind of alive.  Hayley looks away from that because it's unsightly and doesn't comment on it.  Someone seems to be clearing the giant hill of bones away.



Hayley is there for five days.  She always dines with the command staff or upper echelons of the staff at the base.  She notices that people are continually coming and going. Mohinder is there at dinner one night.  He congratulates Hayley on helping secure the base and asks her to give his best to Morgan.  Vogel comes through briefly and does not appear to stay the night.  While she is there she greets Drake as ``Praetor'' in front of Hayley.  On day 4, Rust shows up.  He has a large patch/bandage on the side of his neck.



Drake is friendly and flirty with Hayley, especially when no one is around.  Hayley asks him to show her around the base.  While she fails to notice the more subtle flirting, she is very obvious that she enjoys the attention.  She seeks out his company, she asks him lots of questions about everything (both SAC-04 stuff and trivial things about the plants and does he swim?).  She finds everything he says \textit{fascinating}.  By day 3 Drake seems quite taken with Hayley and expresses his interest more overtly.



Once Hayley realizes his interest, she is totally onboard with having sex with Drake.  Her only hesitation is if he finds her scars off-putting, but he thinks they're pretty cool, and he has scars of his own.  They sleep together for the remainder of her visit.  She is participates enthusiastically, perhaps even a little aggressively because she's so delighted that it feels good and she feels safe with him.  And she has no idea how to be coy or play cool, even if she wanted to.



Hayley notices that Drake doesn't sleep much and has a lot of energy.  Probably their first night together Hayley doesn't get quite as much sleep as she should, but after that point she's very careful to make sure she gets all her rest, meals and attend all of her training.  Well, she \textit{tries} to anyway.  Everything's a little timeless at SAC-04 and she's distracted by the novelty of everything and gets a little lost in it.  It is more than a little ridiculously idyllic- there's even a romantic/sexy romp in the rain, followed by \hl{breathtaking rainbows}\footnote{\textbf{q.google }Those are actually probably pretty mindblowing for any resident of the Directorate. \textsubscript{12/15/14 7:07pm}} that appear when the clouds clear.\footnote{\textbf{Suko T }I imagine that somewhere in SAC-09, Jaya is overcome with sudden, intense nausea. :D \textsubscript{12/12/14 12:54am}}\footnote{$\rightarrow$\textbf{Rebecca S. }No, she doesn't.  Because thankfully there's at least a two people left in this game who aren't linked directly (or by N degrees) \textsubscript{12/12/14 11:45am}}\footnote{$\rightarrow$\textbf{Suko T }Oh if they were actually connected Jaya would not be feeling nausea, not from Hayley anyway. ;)   I just figured this was Jaya's Secret Truth warning her that she better start deprogramming Hayley STAT.  :D \textsubscript{12/12/14 10:07pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Oh shit, I totally forgot about Secret Truth! D: \textsubscript{12/12/14 11:40pm}}\footnote{$\rightarrow$\textbf{q.google }''No, she doesn't. Because thankfully there's at least a two people left in this game who aren't linked directly (or by N degrees)''

That's what went through my head too.  (The damned in-game link must be bleeding through.)

I think it would be a \_very\_ different game if Hayley and Jaya had a link.  An explicit one anyway.  They communicate remarkably well. \textsubscript{12/15/14 7:06pm}}



It doesn't seem like anyone has noticed Hayley and Drake, or if they have, they don't say anything.  It may help that if anyone else hits on Hayley while she's there, she's equally pleasant and friendly to them (though she carefully stays out of arm's reach of everyone but Drake unless she's training or dining with them).  Also, during training, Hayley doesn't expect special treatment.  In fact she actually pushes herself even harder to do more difficult things and learn more faster, to impress Drake.  She loves the training too- especially as it is usually held outdoors with that incredible view of the valley in the background.



On the last day, Drake walks Hayley to the train station.  He hands her a small satchel.  ``You might need these.  Just a gift from me to you,'' he says.  ``The green vials should be one day's sustenance.  Give or take, depending on the size of the person.  I tend to like to down several myself.  But it should be all the nutrients you need in case you get stuck in a bad situation.  The blue vials... pour a drop onto uninjured skin and then pour the rest into a wound about three seconds later.  There's a priming thing,'' Drake demonstrates. ``Turn this here and a drop will come out.  Pour that onto uninjured skin, turn rest of the way and pour the rest out onto the injury.  Clear enough?''  Hayley nods her understanding.  Drake says, ``There are some edge cases where that could be a problem, but for most life threatening injuries, it could help a lot.''

``Should we remove all debris from the wound first?'' asks Hayley.

``Generally a great idea,'' says Drake. He smiles at Hayley, \hl{``I love how smart you are.''}\footnote{\textbf{Suko T }OMG I think he's serious.  He's so doomed.

Though in his defense, Hayley's intellect is pretty much directly correlated to how much she likes someone and also how happy and secure she is feeling.  So who knows- perhaps for Drake at SAC-04 she's a freakin' genius.  

Dr. Gerhauser, on the other hand, gets the 6 year old sulky moron. \textsubscript{12/10/14 4:27pm}}\footnote{$\rightarrow$\textbf{q.google } \textsubscript{12/15/14 7:08pm}}\footnote{$\rightarrow$\textbf{q.google }''Hayley's intellect is pretty much directly correlated to how much she likes someone and also how happy and secure she is feeling.''

I think that's true of almost everyone.  Intelligence is severely impacted by confidence.  But it's also of little use if no one has ever expected you to use it or cared if you have. \textsubscript{12/15/14 7:10pm}}\footnote{$\rightarrow$\textbf{Suko T }While this is true, it's very marked in Hayley.  And it's less confidence than just actually wanting to make an effort.  If she's unhappy, she's not going to make an effort and her IQ drops like a rock. \textsubscript{12/16/14 12:16am}}   Hayley lights up with a real smile at the compliment.  He continues, ``Finally, the black vials.  Same thing with the priming, but don't drop it on your skin.  Just turn it once, wait three seconds, turn it all the way and then throw it.  Stay clear of whatever it hits.   And take care of yourself.''

``I will.  What is the radius of effect of the black vials?  How far away should we be?''

``It's a splash.  You can practice with a vial of water.''  He chuckles, ``Isn't it wonderful to be able to say that?''  Hayley doesn't quite understand but she smiles anyway because he's amused.  Drake shakes his head.  ``I never thought I'd see the day when I could say something like 'practice with a vial of water.'''

``I like it here,'' says Hayley, wistfully.  ``It is beautiful here.''

``It \textit{is} beautiful here.  And \textit{you're} beautiful,'' says Drake and leans down and kisses her for a long time.  \hl{Hayley kisses him back with great enthusiasm.}\footnote{\textbf{Suko T }No sad angsty ``last kiss'' for Hayley. \textsubscript{12/10/14 4:05pm}}  



The train approaches and Drake backs off to an appropriate distance.  He says, ``I'll see you around, Agent?''

``I hope so,'' says Hayley sincerely.

``Me too.  Don't be a stranger,'' He salutes.

Hayley returns the salute and she smiles at him, a somewhat dopey besotted smile that screams, \hl{``you're really cool, I liiiiike you''.}\footnote{\textbf{Suko T }Cannot WAIT until Jaya finds out. \textsubscript{12/10/14 4:32pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }surely Hayley has enough sense not to mention this...? \textsubscript{12/11/14 1:35am}}\footnote{$\rightarrow$\textbf{Suko T }Of course she won't *say* anything, but seriously, Hayley's not exactly subtle about her feelings when they are of the socially-approved positive variety. \textsubscript{12/11/14 2:19am}}



The train pulls in and Rook disembarks.  Rook looks at Drake. Drake looks at Rook. Hayley salutes and Rook returns it.  Rook has a half smile on his face.  \footnote{\textbf{Suko T }Did Dad just approve of Hayley's boyfriend?? \textsubscript{12/10/14 4:31pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }The word ``territorial'' just keeps circling in my brain...
Maybe Rook will slip Jaya some Praetor elimination tips in that casual way of his before dropping her off at a train station...? \textsubscript{12/11/14 1:37am}}

Rook says to Hayley, ``Agent, you ready to go?''

``Yes sir,'' says Hayley, still all smiles.

Rook turns back to Drake and they exchange another look.  There is a palpable...tension? energy? something in the air\hl{but both of them are smiling.}\footnote{\textbf{Suko T }Sometimes I wonder if Rook's head will explode from all the secrets he keeps ever so discreetly. And then I remember, it's Rook and his capacity for awesome appears to be boundless. \textsubscript{12/10/14 4:32pm}}  Hayley is mostly oblivious and boards the train.  Rook boards the train after her and goes into the cockpit.  Hayley girlishly waves goodbye to Drake through the window and Drake waves back (in a manly way of course).  As the train pulls away Hayley leans into the window to keep him in view as long as possible, then settles into her seat with a happy sigh.




\sceneHeadline{SAC-09- Jaya}

Jaya spends a lot of time in MedBay getting her injures from the beating taken care of and also undergoing the correctional abdominal surgery with Dr. Gerhauser so Jaya can keep her baby.  Rook checks in on her often.  Jaya insists that she's fine but she wants that plate again.  Rook laughs it off, ``Funny joke, Jaya!''



Dr. Gerhauser admonishes Jaya not to get into more fights.  During the bed rest Jaya repeatedly replays how that corridor encounter would have gone down if it'd just been her and Rust.  She takes comfort in her absolute certainly that she would have been able to crush him if it were just the two of them.  Or even if he had just a couple fewer lackies.  Despite best efforts, she is unable to avoid dwelling on how unlikely it would be that she'd find as many- or any- individuals to aid in an authorized beat down these days. She fidgets constantly with her now quite scabby ``Loyalty'' tattoo/wound, to the point that Swan needs to rebandage it. 



Swan and Rook come in take some molds of Jaya's teeth and then she undergoes some dental surgery and gets a metal tooth to replace the one she lost, which was her left canine.  It's a little sharper than the original tooth.\footnote{\textbf{Rebecca S. }Is it shinny? Gold? Metallic? Super-powered? Can I take it as a lvl 1 asset?? \textsubscript{12/11/14 1:38am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Also... In game it was said to be an incisor (right?) but I'd much rather it be the left canine... that cool? \textsubscript{12/11/14 11:21am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Yup! I think that's actually what I meant, anyway. I'm not good at dentistry. \textsubscript{12/11/14 11:23am}}\footnote{$\rightarrow$\textbf{Rebecca S. }also, was that ``Yep'' for it being hella' bling? \textsubscript{12/11/14 11:29am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }'Yep' for canine. If by 'super power'... yes: if by 'yes' you mean 'you can de/reattach it with a fun code phrase I haven't come up with yet'. But 'no' if by 'no' you mean 'it doesn't have it's own tentacles to run around on, allowing it to return itself to your mouth'. Rook is happy to provide the following color options: bright, ceramic white, matte black and cyber-arm colored. Anything else you'd have to negotiate with him. \textsubscript{12/11/14 11:35am}}\footnote{$\rightarrow$\textbf{q.google }''I'm not good at dentistry.''

\_laughs\_ \textsubscript{12/15/14 7:12pm}}  Jaya is pleased.

Rook says to Jaya, ``I really don't wish to encourage you to headbutt any further opponents-''

``It wasn't headbutting!'' she starts to protest, mostly unintelligible around all the cotton wadding in her mouth.

``Stop moving your mouth,'' instructs Rook, but he smiles, ``But hopefully this should help you... if you should fall into that circumstance again.''




\sceneHeadline{SAC-09- Jonah}

Jonah confirms with Rook that he wants to start Riva with traditional lessons and then consider the other options once Riva knows more.  Jonah gets some reports at the end of the week.  One from Rook saying, ``She's a very bright girl, I'm having a lot of fun working with her.''

And another report from Riva which is full of exclamation points, ``\hl{ROOK IS AWESOME!!!!!}\footnote{\textbf{Suko T }So much fangirl screaming in the audio during this part. \textsubscript{12/10/14 4:47pm}}  He's shown me all kinds of really cool things!!!! Have you ever soldered before???''

Jonah goes to go see her to hear more about it. Mostly to see that she's okay but a little bit to check to see if Rook has told her something Jonah doesn't know.  Riva appears to be learning basic things like learning how electricity works.

Jonah says a little smugly, ``I told you that you wouldn't be bored.''

``This is SO much better!''

``And now you see why it was so hard to explain it to you.''

\hl{``Actually no!  It's very simple,'' and Riva starts explaining it all to him.}\footnote{\textbf{Suko T }Because Riva is also awesome.

How much longer before she can be a Constable Trainee and join PG1? \textsubscript{12/10/14 4:51pm}}



At some point during the week Micah delivers a package of books to Jonah.  They are books on prenatal care, a guide for delivering a baby and a book on taking care of small children.  Jonah quizzes Micah about them, but Micah just shrugs and says Dr. Gerhauser told him to deliver them, he doesn't know why.



Jonah gets a lot of book-time and reads up on how the Operator machine works.




\sceneHeadline{Ops}

Hayley steps onto the SAC-09 platform and is told to report to Ops a few minutes later.  Hayley only pauses long enough to stow her rifle securely somewhere, stash her gear, and then goes to Ops.



PG1 shows up in Ops to find the room empty except for Morgan, Lackovich and Carruthers.  Hayley salutes them.   Jaya slouches into a chair and salutes everyone from her sitting position.

``Sit down,'' says Morgan returning the salutes.  ``I apologize that we weren't able to do a proper debriefing after your last mission.  Which went spectacularly except for the loss of one team member.  I apologize that the funeral for that team member has been delayed until now.  It will happen at 1600 hours today if you wish to participate.  Is there anything else that you wish me to know that I don't already know, regarding that mission?''

\hl{Dead silence for several seconds}\footnote{\textbf{q.google }Noted out-of-band, that Jonah delivered information about the turnover of SAC-04 before Signy's attunement. \textsubscript{12/15/14 7:14pm}}\footnote{$\rightarrow$\textbf{Suko T }Yes that was in Session 37 notes during Jonah's talk with Dr. G before he learned how the Operator connection worked \textsubscript{12/16/14 12:17am}}.  Jaya is the first to break it with just a, ``No.''

``Alright,'' says Morgan.  ``One thing I would like to add is Mohinder has filed an official commendation for Agent Parvadi, in recognition of her extraordinary efforts in getting the team out of danger. I wish to second this commendation.''

\hl{Jaya looks extremely nervous and eases back in her chair. ``Thank- Thank you sir,'' she stammers.}\footnote{\textbf{q.google }Morgan is apparently scoring points by acting unexpectedly this session. \textsubscript{12/15/14 7:15pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }There is a fairly strong subtext here, which I wasn't entirely sure would come across except that Jaya reacted as expected. (That is, Morgan made sure Jaya knew everyone knew how well she is expected to perform.) \textsubscript{12/15/14 8:10pm}}\footnote{$\rightarrow$\textbf{q.google }Yes.  It's clear Morgan is being very very tactical in what she says.  But from a PC perspective it looks like she's turned over several new leaves... and is throwing them like shuriken. \textsubscript{12/15/14 9:37pm}}

``After the report of Operator Lackovich, I feel that you have really done honor to this team.''

``Uh, thanks!  Sir Ma'am,'' says Jaya.

``I have made sure that key senators in the Triumvirate, the ones we are allied with, are aware of this.  We all expect you to perform this well or better in the future.''

``I won't let you down, Sir,'' says Jaya, sounding like she might pass out.  She is clutching the edge of the table so tightly that the knuckles on her flesh hand turn white.  Hayley attempts to discreetly get Jaya to let go with her metal hand before she dents the table too noticeably. 

``Well done soldier,'' says Morgan to Jaya.  



``Moving on.''  Morgan looks at everyone at the table, ``There are two things that we need to discuss, then we will discuss what your next mission will be. \hl{First, you are to be engaging tomorrow morning in PST, which is to say, Portal Safety Training.  I wish for you all to be well rested.  Rook will be guiding it.}\footnote{\textbf{Rebecca S. }I have a vivid mental image now of a GLaDOS/Morgan mashup, and it's scary... And Rook is the Companion Cube. (Dr. G \& Trenton are turrets) \textsubscript{12/11/14 1:42am}}\footnote{$\rightarrow$\textbf{Suko T }Is Oliver the Cake? \textsubscript{12/11/14 1:44am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Someone analyzed all the cake. Did everyone get a piece? \textsubscript{12/11/14 11:32am}}\footnote{$\rightarrow$\textbf{Suko T }\textless 3 \textsubscript{12/11/14 11:56am}}\footnote{$\rightarrow$\textbf{q.google }''I have a vivid mental image now of a GLaDOS/Morgan mashup''

That was \_perfect\_. \textsubscript{12/15/14 7:16pm}} If you have any questions direct them to him.  It is imperative that that you take this training seriously.  Is that understood by everyone?''  

Hayley and Jonah agree, Jaya hesitates like she is going to ask something and then agrees.



``Secondly, it is necessary that PG1 is aware of certain strategic imperatives.  And for that reason I have asked you all here to discuss them.  I have also asked certain members of PG2 to attend because  there is no point in keeping a secret from them.  Octavius, as you may be aware, has long term plans concerning Transit Major.  It is our intention to go to Transit Major.  As you know, we intend to unlock Transit Major via the Tanks.  We believe we can do this with your help.  That is one possible mission we can send you on next.  I hesitate to \hl{suggest}\footnote{\textbf{q.google }In game I don't fully understand why Morgan is ``suggesting'' anything.  Even if she wants us to choose, why not just tell us?  (OOG, it's obvious.) \textsubscript{12/15/14 7:17pm}} doing this first, simply because once we do that, a timeline will be established.  It is almost certain Octavius will figure it out.  When we get to Transit Major we wish to deny Octavius not only the ability to use it, but to use Transit Major itself to shut down Octavius' VTX.''  Morgan looks around.  ``You all are noding which means you are absorbing the information, but I need to hear that you comprehend them.''

``Questions then sir?  Two.   How is it possible to physically go to Transit Major before unlocking it?'' asks Jonah.

``It is not actually physically possible to go there before we have unlocked it.  And we have to activate the Beacon in order to properly go there.  So we have two missions in front of us.  One is to unlock Transit Major.  The other is to get the map to get there, if you will.''  

Jonah asks, ``And you are saying that the former will start the timeline, but the Beacon will not?

Morgan cautions, ``I hesitate to- we are already racing against time. Octavius is on the move.  Once we unlock Transit Major, anyone will be able to enter it.''

``Second question, what is special about Transit Major?'' asks Jonah.``A great many things.  It has the most power and most number of transit nexuses anywhere in the known universe.  It has technology beyond the likes of which you, me or anyone on this station or \hl{even Octavius}\footnote{\textbf{q.google }!!! \textsubscript{12/15/14 7:19pm}} comprehends. Things that were built a long time ago and for various reasons have been forgotten. Octavius wishes to utilize this much like we are taking advantage of Tertius' VTX.''

``So I guess I've a third question.  What is a VTX?'' asks Jonah.

``Think of it as a model of the Agent/Operator connection.''

``So is it used to create one or used to mimic one?''

``It \textit{is} one. We are using Tertius' VTX to connect you.''

``I see.  Somewhat like a radio?''

``More akin to a radio \textit{frequency},'' corrects Morgan.

``Okay, thank you.  So it is the most significant Beacon you have and with it you could connect large numbers of people.  More than Octavius can already connect?''

``Transit Major has additional technology that has less to do with how the VTXs work and more to do with how space works.''

``Like the trains?'' says Jonah.

``Exactly.  \hl{In fact the majority of the trains go through Transit Major, they just don't stop there.}\footnote{\textbf{q.google }''I'm sorry Agent.  This information is above your tech level.'' \textsubscript{12/15/14 7:20pm}}''

``More traffic than we see?'' asks Jonah.

``Well sixty percent of the overall traffic.  I don't know how much traffic you have seen.''

``Well, SAC-04 was like nothing I'd seen before...'' Jonah asks a little uncertainly, ``I assume it \textit{is} part of the world?''

``Yes.'' Morgan chuckles a little.  ``I apologize for the limited horizon in your experience.  There is nothing I can do about that.''

``The explaining is helpful, thank you,'' says Jonah.

``When you say destroy or disable the VTX, does that mean we would destroy the...constituents?'' asks Hayley.

``The constituents would likely be greatly distressed, but whether or not this would destroy them is almost...philosophical.''  Morgan grins, wolfishly.

``Is this what Octavius is using?'' asks Jonah.

``Octavius has a VTX, it is the Octavius VTX, for lack of a better term.  They wish to use Transit Major for an operation or a purpose that we do not entirely understand. But none of the analogies that I can come up with would mean anything to you.''

``But it would give them an advantage over us?  A significant one.'' says Jonah.

Morgan laughs shortly, ``Let me put it this way, any advantage they seek over us is entirely to utilize us toward that end, the end that they wish to use Transit Major for.''

``\hl{Alright, good enough}\footnote{\textbf{q.google }No, no!  \_Not\_ good enough!  Want \_more\_ time behind the curtain!  More!

(Damn PCs.  No \_idea\_ what they just got handed to them.) \textsubscript{12/15/14 7:24pm}},'' says Jonah.



``\hl{Just want to bring this conversation back to a tactical, strategic level}\footnote{\textbf{q.google }Whoa. \textsubscript{12/15/14 7:27pm}},'' says Jaya. ``In one of them, someone is going to shoot at us.  And in the other we're going to go in the tank and....trip a little.  Am I understanding this correctly?''

``More or less,'' says Morgan.

``So if we go shoot the people, are there a lot of people?  How many forces are there?'' asks Jaya.

Morgan says, ``Rook informs me that the Beacon is.... stewarded by a very interesting set of entities.  He is.... \hl{abnormally opaque}\footnote{\textbf{Suko T }\textless 3 \textsubscript{12/10/14 10:19pm}}\footnote{$\rightarrow$\textbf{q.google }I think that may warrant more exclamation points than ``even Octavius''. \textsubscript{12/15/14 7:26pm}} on the subject.''

There is an awed silence (well except for from Hayley who is dealing with her own opacities).

``I recognize that statement may sound surprising, but it is entirely true, I assure you,'' says Morgan, totally not teasing us at all.

``This is not like the Praetors at SAC-04?'' asks Jonah.

``We do not believe there is a Standalone Complex there, no,'' says Morgan.

Jaya starts to speak but Jonah interrupts her to say, ``To clarify, the entity that we encountered at SAC-04 was not normal in any way.  It didn't even manifest as ... \hl{human}\footnote{\textbf{q.google }This an idea that's only slowly beginning to even mean anything. \textsubscript{12/15/14 7:29pm}}.  It didn't bleed.  The white material, that's not blood. I dont' know what it is.''

``Rook has a fair idea what it is.'' says Morgan calmly.

Hayley gets a little distracted at the thought of SAC-04 and smiles a bit to herself.  Carruthers can feel a happy buzz from Hayley.

``Are these entities similar? Or radically different?'' asks Jonah.

``He would not say.  And unfortunately that is outside of the purview of my agreement with him so I am unable to compel him,'' says Morgan

``\hl{An agreement!}\footnote{\textbf{q.google }Really.  Morgan is four for three now. \textsubscript{12/15/14 7:29pm}}`` exclaims Jaya with interest. ``I- I thought-''

Jonah interrupts again to explain, ``Chief, SAC is not part of the same Agent structure as the Directorate.  We are using the same ranks but Rook is not part of either and they have made some sort of arrangement for use of SAC-09.''  Jonah turns to Morgan and says apologetically, ``\hl{Forgive me if this is wrong, it is just speculation on my part.}\footnote{\textbf{q.google }What it is is him talking over a sudden rising panic about who Rook really is. \textsubscript{12/15/14 7:31pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }What's the worst case scenario, really? \textsubscript{12/26/14 8:26pm}}''

``Why don't we state it then?  Don't speculate.  What is the agreement?'' asks Jaya.

``Are you asking about my personal business, Jaya?'' asks Morgan sweetly.

Jaya looks alarmed.  ``What?? No no no...Sir Ma'am!  NO.  I'm just- just-  Nevermind.  You know?  Nevermind,'' Jaya drops the subject and runs her hand through her hair, clearly distressed.

\hl{``That's too bad.  Because I was entirely willing to tell you,'' says Morgan, a wicked gleam in her eyes.  Jaya is speechless.}\footnote{\textbf{Rebecca S. }let us never forget that Morgan is the most evil creature on the base. Eeeeeevil. \textsubscript{12/11/14 1:48am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }That... is probably true. For traditional senses of evil, anyway. \textsubscript{12/11/14 11:46am}}\footnote{$\rightarrow$\textbf{q.google }I wish Jaya hadn't backed down, even though it's completely reasonable that she did. \textsubscript{12/15/14 7:33pm}}

Jonah steps in and says to Morgan, ``Sir, what I think the Agent is actually asking, is what is the nature of the threat there?''

``The objective is to turn the Beacon on.  Who is protecting the Beacon, and whether they want it turned on, is unclear.  We expect them to be of advanced technology, but we don't necessarily expect them to be hostile. Certainly not in the way the \hl{so-called Supay}\footnote{\textbf{Suko T }I feel like you're trying to tell us something, Nate.. :) \textsubscript{12/10/14 10:36pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }That may be. But I'm not sure what message is being received. \textsubscript{12/11/14 11:46am}}\footnote{$\rightarrow$\textbf{q.google }Let me help you then: the \_so-called\_ Supay.  As in ``there might be another, more edifying name''.  Which you might tell us.  

Or not \textgreater :). \textsubscript{12/15/14 7:34pm}} was hostile.''

``Oh.  Not too bad then.'' says Jaya, almost sounding disappointed.  ``So this Beacon...we just push a big button and we'll know it when we see it?''

``Rook will be accompanying you.''

``Rook's coming on the mission with us?'' Jaya says, sounding dismayed.

``\hl{I don't see any way around it}\footnote{\textbf{q.google }\_That\_ too would be really neat to follow up on. \textsubscript{12/15/14 7:35pm}},'' says Morgan.

``But when we operate with with Patrol Group 2, the chain of command is clear.  But if Rook accompanies us on the mission, what is the chain of command?'' asks Jaya.

``Are you unclear on the chain of command, Agent Parvadi?'' asks Morgan ominously.

Jaya stares wide-eyed at Morgan. Her eyes say yes, but her mouth says ``No.'' and she lets the question drop.  Jonah says  {\color[RGB]{74,134,232}::Rook will be in charge::} 



``Now, turning back to strategic points that are important that you are crystal clear on,'' says Morgan.  ``When we finally gain access to Transit Major, \hl{Hekate is capable of disrupting/destroying Octavius' VTX}\footnote{\textbf{q.google }Actually \_that\_ I'm going to ask about in-game. \textsubscript{12/15/14 7:36pm}}.  She will require Victor and his equipment.  Should Victor not be available, Trenton would be an acceptable substitute.''

``Victor's better at it,'' points out Jaya.

``Victor possesses certain intuitions that Trenton does not, and likewise, Trenton possesses certain intuitions that Victor does not.  In \textit{this} case, Victor's broader understanding of physics means he is the better candidate.  However, in a pinch, Trenton's... frankly \textit{anomalous }understanding of mathematics could work.  I also believe Victor is the better choice because he is emotionally uncompromised.''

Jaya approves of this endorsement.

``I will provide you a list of equipment that Victor or Trenton will need.  As well as my sister.  For this reason, it is imperative that none of these personas are to be allowed off base and into harm's way.  I know this has happened in the past. It will not happen again. Are we clear?'' says Morgan with deadly seriousness.

``Sir, do you mean this base or that one?'' asks Jonah.

``Until such time as we are ready to strike, putting any of these people in harm's way will be problematic,'' says Morgan.

``These people....being your sister and the two brains?'' asks Jaya.

``Yes.''

``Which one are you most concerned about?'' asks Jonah.

``Frankly, my sister,'' says Morgan.

``Oliver's gone, so-'' mutters Jaya under her breath.

Morgan's face goes completely blank and she stares impassively at Jaya.  Jonah says to Jaya  {\color[RGB]{74,134,232}::Chief::}  Jaya starts fidgeting a bit nervously   {\color[RGB]{74,134,232}::Just look at the table::}  Jaya looks at the table, and looks a little panicked.

Attempting to distract/diffuse the situation, Jonah says, ``Sir, do we have your authority to stop her if she tries to leave?''

``You have my authority.  Is that \textit{clear}, Carruthers?'' says Morgan pointedly, without ever taking her eyes off Jaya.

Hayley had been feeling a sense of growing panic from Carruthers.  Carruthers is hunched into a little ball and she squeaks in terror, stuttering, ``Y-y-yes Sir.''

``Do you have any other questions on the strategic elements?''

``We are on a timeline,'' says Jonah.

``Octavius is attempting to do something. Trenton and Victor have been unable to figure out what.'' says Morgan.

``If we activate the Beacon, will we be leaving behind a force to guard it?'' asks Jaya.

``I believe that once the Beacon is activated, we will not need to defend it. However we may be able to enlist some of Mohinder's people to do that for us.''



Morgan says, finally letting her gaze drift off Jaya. ``There is a somewhat more esoteric concern.  Which is to say, Senator Marechenko.  We have made certain promises to him and if we wish to call upon him later, we may wish to deliver on these promises now.''

``Maybe Mohinder's people could help with that,'' suggests Jaya.

``Maybe, but then that would be Mohinder helping him, not us,'' says Morgan.



``So we have before us, three operational targets.  The Beacon, the locks on Transit Major, and Bonventure station,'' says Morgan.  ``Do you have any preferences?''

``I think we should do the easy thing first and go activate the Beacon,'' votes Jaya.

``The easiest thing is Bonventure,'' says Morgan

Jaya mutters to Jonah, annoyed, about his promises to Marechenko and then clears her throat and says loudly, ``I think we should cut to the chase and go activate the fucking Beacon.  How hard could it be?''

``Would Octavius care if we went to Bonventure?'' asks Hayley.  ``it would not necessarily alert Octavius to our plans to go there?

``That is correct.''

``Unless he sells us out,'' frowns Jaya, referring to Marechenko.

``It might be good to gain extra resources.  If we need to move quickly in the future we may not be able to do so afterwards,'' comments Hayley.

``Perspicacious,'' praises Morgan.  \hl{Hayley will be more flattered when she learns what that word means}\footnote{\textbf{Rebecca S. }''having a ready insight into and understanding of things.'' for all the Rebeccas \& Hayleys in the audience. \textsubscript{12/11/14 1:57am}}\footnote{$\rightarrow$\textbf{Suko T }Hayley's just never had that word applied to her before.  Unsurprisingly. :) \textsubscript{12/11/14 2:22am}}.

``Senator Marechenko is presumably going to use those resources to defend if Octavius actually manages to make it to the Directorate,'' says Jonah.

``True but if he is well disposed towards us, we may be able to convince him to use them in manners which are advantageous to us.  The greater concern is that if the Directorate becomes unfriendly to us... we run into a problem.'' says Morgan.

``How pressing is time?'' asks Jonah. ``Do we have time to go to Bonventure?''

``If so, then just.'' says Morgan.

``How long will Bonventure take?'' asks Jonah.

``We are merely securing this station for Marechenko.  We believe the population is under-resourced on the technology front,'' says Morgan.

Jaya looks annoyed.  ``I just spent a lot of bullets shooting at people who were 'under resourced'.  Let's not do that again.  It's too....It's not a good fight.  Let's go,  let's meet some.... entities and activate a Beacon.  Let's just move forward.  And if we have time, maybe we can circle back and do your little man a favor.'' she glares at Jonah again.

Hayley asks Morgan, ``Sir, is it necessary that the whole team go on all three?  With the connections with patrol group two...'' and Hayley gestures between herself and Carruthers (and gives Carruthers a quick smile).

``Interesting proposal,'' says Morgan and she looks thoughtful for a long moment.  She says slowly, ``I would feel better if your teams stayed together, because as a unit you are very useful.  And as dead people you are not useful at all.''

Jaya says strongly, ``I think we have proven that we can perform optimally in the field together, even with some'' Jaya gestures to PG2'' ...additions we can continue move forward to succeed and move forward our forward momentum to succeed at our missions.''

Morgan looks at Jaya and then looks at Lackovich. Lackovich is burning holes in the table with her eyes.   Morgan looks at Jonah and asks him,\hl{``So you would prefer not to split the team as well?''}\footnote{\textbf{Rebecca S. }Split the party? What could POSSIBLY go wrong? \textsubscript{12/11/14 2:00am}}\footnote{$\rightarrow$\textbf{q.google }Nothing ever went wrong when we split the party before.  Not once.

Twice maybe.

Or perhaps five or eight times.  Nothing to worry about! \textsubscript{12/15/14 8:57pm}}

``I think it would be ill advised.''

``Very well, we'll table that suggestion for now.  But good suggestion, Hayley.'' 

Hayley looks very gratified by the praise.

Jaya is looking pityingly at Hayley, not saying it, but thinking how sorry she is that Hayley has such terrible ideas.

Jonah asks, ``I am unclear on what Senator Marechenko needs from us there in Bonventure.  If he needs people to claim the space, there are only a few of us and he has lots more people at his disposal.  What are we providing that he doesn't have?''

``First of all, we provide him the actual means to get there. Secondly, the activation of the equipment he wants, along with the schematics he needs to utilize it.  Thirdly making it painless for him, which is to say, removing any obstacles in his way.''

``Obstacles,'' says Jaya, ``Civilians.  Current residents.  It's all the same thing''  

``How is it that 4-5 people doing this for him any advantage for him when he can get 40 people to do it for him?''

``The difference is handing him something on a golden platter versus saying 'here's this thing you can take on if you can find some constables to spare','' explains Morgan.

``Then my opinion is merely 'if we have time'.  If we don't have time, then we can't afford to do that.  If we do have time then we should make sure that the Directorate is able to withstand anything that is thrown at it while we finish off the more dangerous part of this,'' says Jonah.

``I thought we had just enough time,'' says Hayley, looking at Morgan for confirmation.

``We have time if we do it now, I believe,'' says Morgan.

``Fuck that!'' says Jaya loudly.  ``\hl{We've fucked up half the missions}\footnote{\textbf{q.google }But, we did so optimally ;). \textsubscript{12/15/14 8:58pm}}.  Last one went very well but we lost a team member a couple missions back... you know, we can't afford to be fucking around!  We gotta get in there, do the \textit{real} job, finish the \textit{real} problem, wrap this up, and then maybe go back to Marechenko and do whatever the hell he wants.'' Jaya gestures dismissively at that last part.

``But the Citizens will be at risk in Terminus,'' protests Hayley.

``So are the people on the ground,'' says Jonah.  ``If you have any family... they're at risk.''

``Everyone's at fucking risk.  \textit{We're} still at risk.  Everything's a fucking risk!  Take some fucking risks! Let's do the real objective,'' says Jaya, pounding the table for emphasis. ``Kick it off, let's get going!  We are at fucking war!  Now is not the time to pander to some fucking politician's wants.  Let's just get in there and do the real job.  Don't fuck around.''

Hayley looks a little horrified at Jaya's language but says nothing.

Jonah says hesitantly, ``I'm concerned that we have a home to get back to, as well as stopping-''

``\hl{Home is where you make it}\footnote{\textbf{Nathaniel Ford }Let us remember, in the future, that Jaya said this. \textsubscript{12/11/14 7:56am}},'' says Jaya dismissively. ``Let's do this!''

``The Beacon then?'' asks Morgan.

``Fuck yeah! The Beacon.  With this patrol group and patrol group 2 and Rook,'' says Jaya.

Morgan looks at Hayley who looks back unblinking, her expression carefully neutral.

``Do you have an opinion?'' Morgan asks Hayley.

``Yes.''

``Please share it.'' says Morgan.

``I think we should go to BonVenture,'' says Hayley confidently.

Jaya sighs loudly, ``Hayley gets very confused about protocols-''

``This is actually exactly what protocol dictates,'' interrupts Hayley.  Jaya doesn't notice and continues trying to excuse Hayley's behavior.

``Agent Parvadi, I'll ask for your opinion in a moment,'' says Morgan.  Jaya falls abruptly silent. Morgan asks Jonah, ``Operator?''

``Like I said, if there is time, I think we should go to BonVenture.  If there is not, we should go to the Beacon,'' says Jonah.

``Operator Lackovich?''

\hl{Lackovich has her 'I hate my life' look on her face and she mutters, sounding somewhat pained, ``I agree with Agent Parvadi.  We should strike now.''}\footnote{\textbf{Rebecca S. }This new pairing is going to go SO WELL!! \textsubscript{12/11/14 2:06am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{12/11/14 2:23am}}

``Operator Carruthers?''

Hayley can feel intense anxiety from Carruthers.  Caruther stammers, ``I- I- I....ab-abstain?''

``No,'' says Morgan says flatly.

Hayley can now feel terror from Carruthers.

``Bon-Bonventure?'' blurts Carruthers.

 {\color[RGB]{255,153,0}::That is the better choice::}  Hayley thinks approvingly.

 {\color[RGB]{153,0,255}::I knew it would be!::} 

``Agent Parvadi?''

Jaya says loudly and confidently, ``Clearly we should go to the Beacon.  Do it now while we still have time.  And not go dicking around.  Because there may not \textit{be} time.''

``Are you willing to accept the consequences of your choice?''

``Fuck yeah!'' exclaims Jaya.

``Excellent.'' says Morgan.

``I'm the fucking \hl{Senior Constable}\footnote{\textbf{Rebecca S. }Jaya, didn't you get the memo that we're all Agents now? (well, except for those Operators, but still...) \textsubscript{12/11/14 2:08am}}\footnote{$\rightarrow$\textbf{q.google }Yeah but \_everyone's\_ an Agent.  It's gotten so the title barely means anything.  Now Senior Constable, that's a rank with real \_weight\_ behind it.  Usually backing a truncheon. \textsubscript{12/15/14 9:01pm}} of this group and I say we should go to the fucking Beacon!'' Jaya slaps the table again for emphasis, this time with her metal hand and everything on the table jumps. Hayley winces.

Morgan is silent for a few moments and then says, ``Very well Agent Parvadi.  Beacon it is.  You have training tomorrow morning.''

Jaya sits back, looking very smug.

Hayley is expressionless but Carruthers can feel her flash of disappointment.  But soon it is buried under Hayley calculating what she needs to get done before they leave- several reports for Morgan, extra exercise, extra sleep.

Jonah leaks\footnote{\textbf{q.google }Not ``sends''.  It leaks through.

Jonah it turns out, doesn't actually want to go to Bonventure.  How interesting. \textsubscript{12/15/14 9:04pm}} a pleased feeling to Jaya but Jaya can't really feel it separately from her general sense of feeling pleased with herself.



Morgan says, ``You have training tomorrow morning.  Get there as soon as possible.  We will set up the operation for the Beacon.  If there is time later, we will see if Marechenko's needs can be met.  and if not, we will deal with those consequences.''  Jaya looks a little pale at that.  Morgan looks around the table, ``Again, I thank you all for your service.  If you need anything, let me know.  That is all.''  Morgan pauses and says, ``Oh, there's one more thing.  There is a reason I asked the five of you in this room.  It is not because I want this information spread around the base.  I am entrusting all of you with the knowledge so you can act should emergencies or contingencies arise.  Don't disappoint me.''

A chorus of ``yes sir.''  And we are dismissed.  We get up and leave. Jaya knocks her chair over as she leaves.






\jumpHeadline{Quotes: }

Suko: This is the smack talk stage of the fight

Rebecca: Yeah, she's letting him back the fuck down before she guts his platoon.



Rebecca: She's a lone lady in a hallway with some... they're all men?

Nate: Yeah

Rebecca: ...with some assholes.



Nate: You would also know from your streetfighting that he hasn't pulled a deadly weapon yet.  So there is a bit of a protocol there that you're familiar with.

Rebecca: And I'm escalating?

Nate: You are \textit{definitely} escalating.

Rebecca: What if I just chop someone's hand off?



Jaya (to Rook): And uh, there was this... we found out later was a Praetor... and I ripped its head off, which was \textit{really} hard to do...and then its head got up and walked away.  So I was just wondering.  If something happened to your head, would it get up and walk away?



Jaya: So..... you're like a normal person then.

Rook: I'd like to think so.



Suko: I have a medicinal rifle, you can have a medicinal train!



Jaya: I don't like talking about trust. It makes me feel untrusting.



Nate: Paper...tastes like dead trees.  Those trees had it coming....



Ion: I do have that camera...

Suko: That's just what we need, an Instagramming Riva.

Nate: Duckface!



Suko: I'm telling you- make up and fashion lessons.  Right here.

Rebecca: And sex tips...fighting....

Nate: How to be a nine year old.

Ion: Torture...

Suko: All that too!  Full service.



Suko: I think I have to say yes.  Look at Rebecca!  (to Rebecca) I could have little Drake babies!

Rebecca: NO!  Nononononono...



Rebecca: I'm taking the level one skill- ``Bitey''.



Suko: Hayley's smiling a bit.

Rebecca: I will stab you as soon as I find out what is going on.



Morgan:  I would feel better if your teams stayed together, because as a unit you are very useful.  And as dead people you are not.



Rebecca: Why wasn't Rook in the room?

Nate: His head was too busy running around the base.


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to understand footnote <3, too many options & none that matched I dont like talking about trust. It makes me feel untrusting. says Jaya grumpily. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }<3 \textsubscript{12/11/14 11:56am}}\footnote{\textbf{Rebecca S. }<3 \textsubscript{12/11/14 1:10am}}\footnote{\textbf{Rebecca S. }<3 \textsubscript{12/11/14 12:51am}}\footnote{\textbf{Suko T }<3 \textsubscript{12/10/14 10:19pm}}\footnote{\textbf{Suko T }<3 \textsubscript{12/09/14 12:16pm}} 

	Unable to highlight for footnote: I very much doubt that she's ever bathed., unable to correctly match (exceeded acceptable limit):ExpectedCause thats really interesting

	Unable to find a matching comment for footnote: _Marked as resolved_

	Unable to find a matching comment for footnote: _Re-opened_

	Unable to highlight for footnote: I imagine that somewhere in SAC-09, Jaya is overcome with sudden, intense nausea. :D, unable to correctly match (exceeded acceptable limit):Expectedfollowed by breathtaking rainbows that appear when the clouds clear.

	Unable to highlight for footnote: Did Dad just approve of Hayley's boyfriend?? because:GivenExpectedRook has a half smile on his face.He has a half smile on his face.

	Unable to highlight for footnote: Is it shinny? Gold? Metallic? Super-powered? Can I take it as a lvl 1 asset?? because:GivenExpectedIts a little sharper than the original tooth.Its a little sharper than a regular tooth.

	Unable to highlight for footnote: Not "sends".  It leaks through.

Jonah it turns out, doesn't actually want to go to Bonventure.  How interesting. because:GivenExpectedleakssends


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 07/11/15 3:02am}
% Exported @ 08/24/15 4:48pm
\end{flushright}

