\setcounter{chapter}{ 38 }
\chapter{\textbf{``SAC-09''} }
\footnote{\textbf{Nathaniel Ford }Best. Present. Ever. \textsubscript{12/25/14 10:25am}}



\begin{center}
 {\LARGE \textbf{(aka. ``Big Chicken'')} } 
\end{center}




\textit{Notes:} Suko

\textit{Date:} Dec 18th, 2014



We get Portal Safety Training!  Which involves a lot of running.  Jonah gets information from Dr. Gerhauser on implants.  Hayley apologizes to Dr. Gerhauser and tries to be nice.  It goes poorly.   Jaya gets Lackovich as her new Operator/Furnace of Fury and hallucinates about a giant chicken.  We head off to the Beacon.  There is an earth-shattering kaboom!





\noindent\hrulefill






\sceneHeadline{SAC-09}

Sakhander (Timon's dad) starts working for Jari in the mess hall.



Hayley spars a few rounds with Micah and Karil.  She doesn't win.  Yet.




\sceneHeadline{Bunk}

There's a knock at the door, and as usual, Hayley answers it. It's Rook.   He greets Hayley, ``Agent, will you come with me?''

``Yes sir,'' says Hayley and follows him down the hall and down to Level 3 where MedBay is.  Rook leads her to an area of the floor she hasn't been in before.  As they walk up to the door to one of the rooms, Rook asks, ``I understand that you spent some time at SAC-04.''  They walk into the room and he shuts the door.  The room has a monitor on one wall but is otherwise empty, with a MedBay-level sterile feeling.  There is a rubber mat on the floor, like some sort of training room.  Rather than nervous, Hayley feels somewhat at home in such a antiseptic lab-like environment.

``This is a bit of a delicate question,'' says Rook.  ``I hope you feel free to answer candidly.''

``Yes sir.''

``Did you have sexual relations with Agent Malak?''

Hayley looks down, her brow wrinkled in thought.  Something occurs to her and her expression clears.  She looks up again, meets Rook's eyes squarely and says confidently,\hl{``No sir.''}\footnote{\textbf{Suko T }Naaaaate how could you make me lie to Rook!!!??  :(  :(   Rip my heart out whydoncha? \textsubscript{12/22/14 1:05am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I didn't *make* you... \textsubscript{12/25/14 10:27am}}

\hl{Rook cocks his head to one side and looks at Hayley}\footnote{\textbf{q.google }Is this the first time Rook has actually looked surprised on camera? \textsubscript{02/25/15 4:36pm}}.   Hayley starts grinning.  ``Really?'' he asks her, sounding a little dubious/surprised.  ``At any time, were you injected with anything while you were on that base?''

``Not while I was awake sir.''

``Did you, ingest any particular food that was not natural?''

``I don't know what natural means.''

``Food that you are not used to.''

``Yes,'' says Hayley promptly, still smiling.

``Solid food?''

``Yes sir,'' says Hayley.  She adds, ``I liked it.  It was nice.''

\hl{Rook looks quite confused}\footnote{\textbf{q.google }A moment we shall always treasure. \textsubscript{02/25/15 4:38pm}}.  ``Oh.  And you drank water, I assume.''

``Yes!'' says Hayley, her smile getting even wider.  It's possible she may be trying not to giggle.

``Alcohol?''

``No sir.  At least, not so far as I am aware of.''

``Have you had alcohol before?''

``I have.''

``So you are aware of its effects on you?''

Hayley stops smiling and pauses for a while before she says, ``I was....very upset at the time that I had alcohol.''

``So you are \textit{not} aware if its effects on you?''

``No.  I mean, I know the medical effects of it.''

``But you would not be able to assess if you had similar symptoms.''

``No sir,'' says Hayley.  She asks hesitantly, ``Should I learn?''

``Are you asking me as your commanding officer, or as your friend?''

Hayley looks a little confounded by the question.  ``The answers would be different?''

``Yes,'' says Rook.

\hl{``Oh.  Then as my commanding officer.''}\footnote{\textbf{Nathaniel Ford }To be fair, Hayley kind of broke Rook's heart here... so even steven? \textsubscript{12/25/14 10:28am}}\footnote{$\rightarrow$\textbf{Suko T }Nooooooo!   :'( \textsubscript{12/25/14 4:20pm}}

``No comment.''

``Thank you,'' says Hayley.



``Well I guess I don't need to do a complete examination,'' says Rook and he turns the monitor on.  ``Would you close your eyes for a moment?''  Hayley closes her eyes.  Rook steps behind her.  Hayley doesn't tense but she's listening very hard to try to figure out if Rook is going to attack her while her eyes are closed.  She doesn't hear anything, but he seems to be doing something around her head.



After about 30 seconds he steps away and says, ``You may open your eyes now.  When was the last time you had a Theta 3 scan?''

\hl{Hayley opens her eyes.  ``I.....'' she hesitates.}\footnote{\textbf{Rebecca S. }I was really impressed you remembered Swan's warning... \textsubscript{12/25/14 9:13am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm not, really, as fun as it would have been if she had... \textsubscript{12/25/14 10:35am}}

``Nevermind, it will be in the records.  Why don't you report to MedBay?''

``Yes sir.''

``That will be all unless you have any questions?''

Hayley requests extra paper to write her reports for Morgan.  Rook promises to deliver them to her quarters.  He dismisses her and she leaves.



She heads to MedBay and asks to see Dr. Swan, but he's busy. She tells Larissa to please tell him that it's about Theta 3 scans.  She also asks to see Dr. Gerhauser, she has an answer for her.  Hayley briefly checks in on Signe.  Trenton is in Signe's room, surrounded by pages covered in math.  Hayley asks for a moment of his time and says, ``I need to apologize.''

Trenton laughs it off, ``Don't we all?''   He's clearly drinking.... 'coffee'.

``I was very rude and you were being nice,'' says Hayley.

Trenton grunts in acknowledgement and makes an offhand quip.  For anyone more socially aware than Hayley, he's clearly distracted, with his attention elsewhere.

``If you wish restitution, I cleared it with my contract holder,'' adds Hayley.

Trenton doesn't really engage with this comment and starts absently asking Hayley some math questions.  Hayley blinks in confusion and after a moment, leaves quietly.




\sceneHeadline{Training Room- Portal Training}

The next day, Hayley wakes up early. She's well rested and in a \textit{great} mood.  She makes sure that Jaya is up and dressed on time.  Jonah gets up on his own.  He notices that Hayley's practically glowing and is looking particularly pretty today.



PG1 reports to the Training Room on time.  Rook is standing there, holding an odd squarish-shaped gun.  He draws some lines on the floor.  There are sets of Vacuum-sealed Heavy Combat armor and some sacks off to one side.  Hayley salutes Rook. Jaya just stands there.  Rook looks at Hayley, ``Agent, could you go check on Patrol Group 2?''

``Yes sir,'' says Hayley and she trots off.

Jaya looks irritated, ``Lackovich can't get here on time?  Geez, slowing us all down.''

Rook smiles, ``Actually that's what we're here to talk about today.  Speed.  If any of you wish to warm up, please do so.''



Hayley doesn't get very far before she runs into PG2 on their way to the training room.  Lackovich is pretty much dragging her group along.  Carruthers and Javier seem really tired.

``Sorry we're late,'' says Lackovich.

``It's alright,'' says Hayley and she slips an arm around Carruthers to help her along.  Carruthers' thoughts are a little muddled but she says apologetically to Hayley  {\color[RGB]{153,0,255}::Sorry, didn't sleep well::}   Hayley can feel those strange emotions from Carruthers again.   Before they get to the doorway to the training room, Hayley makes sure to step away from Carruthers so that she is not seen leaning on her, and discreetly straightens Carruthers' collar and shirt.



They walk into the training room to the sight of Jaya doing one armed pushups with her mechanical arm. 

Rook points to one of the lines of chalk on the floor, ``Please line up.''

Jaya is first to line up, followed soon after by Jonah.  Lackovich lines up next, as does Hayley, who is keeping a watchful eye on Carruthers and Javier to make sure they line up too.

Rook clears his throat.  ``Alright, good you're all in training gear.  First, I'm going down to the other end of the room. There is a line there.  You can all see it, yes?  Very good.  One by one, you are to run across that line.  At the point that you cross that line, I want for you to be moving as fast as you can move.  You may start in any way you wish, so long as you are going as fast as you possibly can when you cross the line.''

``Got it!'' says Jaya.  ``Ready?  Let's go.''

Rook points the gun at her.  Jaya sprints as hard as she can, Lackovich is watching, so she pushes herself pretty hard.

When she crosses the line, Rook points to armor.  ``Suit up,'' he tells Jaya.  He calls out to the rest of us, ``Next!''

Hayley takes two deep breaths and then just starts running.  Jaya eggs her on.  Hayley's leg hurts, but she's able to ignore it for the most part though she definitely is limping afterward.   Rook tilts his head to one side a little at Hayley's performance.  But all he says is, ``Next!''  Hayley walks back, frowning.  Jaya encourages her, tells her she did well, but Hayley looks displeased, saying ``I can do better.  This psychosomatic thing is a problem.''  Hayley starts helping Jaya put on her armor.  And as she does so, Hayley starts smiling a little dreamily, as if she is remembering something pleasant.  Jaya ignores it.

Lackovich goes next and is told to suit up.   Jonah waits to see if Carruthers or Javier go.  Javier starts running.  He's surprisingly fast for such a big guy.  Rook tells him to suit up also.

Carruthers runs next, but she's pretty slow. She's trying hard though.

Jonah runs, but the fact that there's a gun pointed at him slows him down.  He's used to running away from guns, not toward them.  His focus is on Rook.

After Jonah crosses the line, Rook says, ``Agent Hayley, Operator Gemayel, Operator Carruthers, please return to the first line.''



Rook calls out to Hayley, Jonah and Brianna, ``Alright, you three.  Again. This time faster.''

Jonah ends up going first as Hayley has turned to whisper running tips to Carruthers (not very helpful, unfortunately).  There's a lot of anxiety coming off of Carruthers.

Jonah runs faster this time, though still not as fast as he knows he could.  Rook comments, ``That was better, once more at that speed.  Next!''

Hayley runs next.  She crouches a bit to get a better start and her pace is smoother, but the pain in her leg is getting worse.

``Agent Hayley, Operator Carruthers, again.''

Jonah runs one more time, and Rook nods, ``Good. Suit up.''

After Hayley's run, Rook says, ``Hmmm.   Well, suit up.''

Carruthers runs again and Rook says to her, ``Okay, wait here.''



Rook addresses the rest of us ``Agent Parvadi, you're first.''

In armor, Jaya runs again.  She's showing off a bit, though she definitely misses her drugs.  

``Good,'' says Rook.  ``Why don't you go one more time just to be sure?''  Jaya is crestfallen.

Lackovich runs and is a little awkward in the heavy armor but manages.

Javier does well enough that Rook says, ``You're clearly not having a problem with this, go pick up a sack and we'll do it again.''

When no one is looking, Jaya discreetly rubs something on her gums.  Just a little bit.

Jaya crushes her next run and Rook tells her to pick up a sack.

Lackovich runs a bit faster, fueled by rage, and is told to run more one time.

Carruthers is standing off to one side, shuffling her feet.

Jonah runs next. The armor slows him down a little and Rook tells him to run again.

While putting on her armor. Hayley is looking a little odd. She's doing a lot of moves and jumping with the armor to get used to the weight.  She looks a little goofy, but doesn't seem to care.  Javier gives her a quizzical look and wonders why she doesn't just run.

Hayley tries to do her best on her run in the armor.  But as she focuses more and more, her leg feels worse and worse.  She breaks out in a light sweat, trying not to let the pain interrupt her running form.  Right as she crosses the finish line, Hayley hears Oliver's voice in the back of her head  {\color[RGB]{106,168,79}::Remember::  } Hayley stumbles and goes down on one knee.

``Are you alright?'' asks Rook.

``I will be in one moment,'' says Hayley, breathing deeply.

``It's imperative that when you cross the line, that you not stumble.''

``I'll- I'll do better.''

``I'm sure you will.  If you need to take a moment to rest, do so,'' says Rook kindly.



Javier runs, the sack looks pretty heavy.  When he crosses the line Rook says, ``Almost, give it one more go.''  Javier looks a little disgruntled but heads back.

Jaya goes next, cutting in front of everyone else.  She's bouncing excitedly on the balls of her feet and then just takes off..  Rook looks at the results and says, ``Surprisingly good!  Go pick up a second sack.''  Jaya grabs a second sack, unfortunately having to pick up this one with her weaker fleshy arm.  Each sack weighs about the same as half of a person.

Jonah runs and Rook says he can try it with the sack if he wants.

Hayley is still trying to recover, her eyes shut.

Lackovich runs instead and does well.

Hayley runs again, and manages to keep herself from stumbling this time, but when she draws to a stop there is intense stabbing pain in her leg.  While she doesn't cry out or fall over, she grimaces, clearly in a lot of pain.

Rook asks her, ``Are you sure you're alright, Agent?''

Hayley takes a deep breath, ``It's psychosomatic.''

``\hl{I do not think it means what you think it means}\footnote{\textbf{q.google }I can see Rook as Inigo, but Hayley as Vizzini is hysterical. \textsubscript{02/25/15 4:42pm}}\footnote{$\rightarrow$\textbf{Suko T }Never get involved in a landwar in Anglia? \textsubscript{02/25/15 4:44pm}}.  Do you need to rest so you do not injure yourself?''

``No.  Thank you sir,'' gasps Hayley, but doubles over at the agony in her leg and has difficulty standing up straight again.  Carruthers can tell that Hayley is in a great deal of pain, but also that she is used to enduring it.



The testing continues for a while.   Eventually Lackovich passes with one sack, Jaya is able to carry two (maybe three, all Rook says is ``that was an impressive performance''), and Javier hauls three across the line.  Jonah manages to carry one sack, but Rook advises him to avoid weight if possible.  Hayley is never told to even try carrying a sack.



Once we're done, Rook tells us to take off the armor. ``Alright.  This is the learning portion of the training.  It is necessary to understand how fast all of you can move on your own-''

``Who's the fastest?'' interrupts Jaya.

Rook replies, ``I believe Agent Javier is clearly the fastest amongst your group.  But given his height, and natural strength advantages, that is not surprising.''  Jaya looks disgruntled about this.



``The one thing you must know about portals is that to properly utilize them, you must be going at a certain velocity based on the length of the object you wish to pass through the portal.   Failure to move fast enough will result in situations such as Agent Parvadi's arm,'' says Rook, gesturing to Jaya's mechanical arm.

``Wait...\textit{portals?}`` says Jaya slowly, just now connecting the dots.  She gets a look of dawning horror.

``Yes, portals.  As you know, our enemy uses them extensively.  But so does the train network.  That is why it is necessary for any train car traveling along the tracks to reach a certain velocity before it passes a certain point.''  Rook says this all with the brisk tone of repeating old news, \hl{but everyone is quite surprised by this info}\footnote{\textbf{q.google }Actual \_information\_.  .

(That was actually really cool.) \textsubscript{02/25/15 4:43pm}} (Jaya is still stuck on the portals thing).

``Trains use portals?'' asks Jonah.

``Yes, that is how they can go many places that aren't necessarily that close.''

``Such as SAC-04?''

``Yes.''

``Do they use them in the Directorate?'' asks Jonah.

``Yes.'' says Rook.

``Yes,'' chimes in Hayley.  ``The thing that Operator Langdon...fell through, and then the eight soldiers, and the three or four that other-''

``Those are ad-hoc portals.  If you run into those- well my recommendation is that you don't run into those unless you are going at a particular velocity, basically top sprinting speed.  Operator Carruthers, I wouldn't recommend you attempt to pass through a portal threshold unless you were dropping into it from a height where you could reach terminal velocity.  Let gravity do the work.''  

``What does ad-hoc mean?'' asks Jonah.

``Means that they will only be open for a short amount of time and then they will close again.''  

``Do you only have to be moving fast through ad hoc portals or all portals?'' 

Rook explains, ``It's true of all portals.  Effectively what it means is that you only have a short amount of time to get all the way through the portal.  And while it may seem like the portal has no width, it does. And if you don't pass through it at a particular speed, part of you may be stretched out or lost in between.''

Jaya looks at her arm.

``Happily, this relative velocity is quite low.  You can do it at a good clip running.  We wouldn't recommend it but we also didn't want you to attempt to do this unless you know the risks involved and had some idea of your ability to do so,'' says Rook.

``So this is not a requirement for the mission?'' asks Jonah.

``Absolutely not.  This is entirely for your own safety.  Hence Portal Safety Training!'' says Rook, somewhat cheerfully.  ``But it is also important, should you ever have to operate a train, that you make sure that the train is going at a particular velocity.''

Jaya's head snaps up, ``We're going to drive the trains?''

``I assume only in an emergency situation,'' says Rook.

``Would we be getting any training in..trains?'' asks Jonah.

``Potentially.  We do not yet have it scheduled but as the train schedules are a bit hard to work with right now.  Trains are a fairly complicated beast.  We'd like to train you on them but given the time constraints we'd like you to concentrate on other things first.''

``How fast do they need to go?  Presumably faster than a person can run.'' says Jonah.

``Yes, that is necessary because they are longer.  The longer the train, the faster it is required to go to pass through the portal.  \hl{All trains are equipped with safety devices around this because as you might imagine this is incredibly important}\footnote{\textbf{Rebecca S. }wonder if this is what caused our crash at end of session? \textsubscript{12/25/14 9:28am}}.''

``Is there a difference in speed requirement if you are carrying a gauss pistol versus a rifle?'' asks Hayley.

``For roughly the length that you might occupy if you are required to personally put yourself through a portal, the difference between a pistol and a rifle is not too bad.  However if you can keep it vertical, it would be less likely to damage your equipment.''

Hayley nods in understanding.

``So if you put something through a portal and left it there, it would be destroyed?'' asks Jonah.

Jaya's arm rotates.

``Technically it would be distended and the atoms would be pulled apart, but yes.  It is not like a doorway that you can pass back and forth through.  It is better that you are moving at speed.''

Rook pauses and surveys the students.  ``Do any of you have any questions?''

Jaya just looks at him sadly.

Jonah asks, ``What did we learn from how much we could carry?''

``Each of those sacks is roughly half a person, though obviously that varies.  If Carruthers was unarmored, she might weigh the same as a single sack.  I would say that-''

``Wait!  I want to try something,'' interrupts Jaya.  



She gets up, walks over to the line and points at Carruthers.  ``Carruthers!  Get over here.''

Carruthers looks at Lackovich in alarm.

``What exactly do you wish to do?'' asks Rook.

Jaya limbers up and says, ``I just want to practice!  Because she's going to be all squirmy and stuff.  Usually when I'm carrying someone, they're not moving.''

Rook leaves it up to Carruthers.  Carruthers asks Lackovich, ``Sir?''

Lackovich lets Carruthers decide.  Carruthers stands and slowly walks over to Jaya, with the look of a woman walking into her death.  Rook walks down to the finish line.

Jaya instructs, ``Now don't go limp, but don't punch me either-''

``I would never punch you!'' protests Carrithers nervously.

``Maybe act surprised?'' says Jaya and then just runs at Carruthers, scoops her up and keeps running.  Carruthers indeed looks very surprised.  And terrified.

REBECCAxxBEGINxxHIGHLIGHTxxWhen Jaya runs across the finish line, Rook says, ``That was... borderline.  I would only do that in an emergency situation.''

``Really?'' says Jaya, Carruthers still draped over one shoulder.  ``Should I do it again?''

``No please!'' says Carruthers a little desperately.  ``Please let me down.''xxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }needs more work, but: http://simply-sithel.tumblr.com/post/110710815564/omg-were-finally-going-to-have-another-4th \textsubscript{02/11/15 8:43am}}\footnote{$\rightarrow$\textbf{Suko T }\textless 3 \textsubscript{02/11/15 10:34am}}\textless 3

``In any event, I recommend that you keep practicing.  Operator Carruthers, I can show you how to use the radar gun if any of you wish to remain and practice.  If any of you have any further questions, I am happy to answer them.''



Jonah asks about the radar gun and Rook shows him how it works and tells him some average speeds for humans.

Hayley clarifies with Rook that it doesn't matter how many people pass through the portal at one time so long as they are all travelling at the same (correct) velocity.

Rook explains that yes, if you can somehow anticipate someone coming through a portal you could cause them serious harm by preventing them from passing through.  He also notes that using gravity could help.  When we first encountered Octavius, he/they attempted to drop through a portal to get up to the correct speed. 

Rook addresses everyone, ``That brings up a good point.  One thing that you should be aware of is that when you come out of the portal, you may not be in the same orientation either to the ground or to anything else that you were before.''

``What does that mean?'' ask Jonah and Jaya.

``Oh!   That would explain it,'' says Hayley, sounding like something just became clearer to her.

``For example, if the other end of the portal is pointed at the ground and you ran through it, you would be running as if you were running in mid air, straight toward the ground.''

``That doesn't make any sense,'' says Jaya.

``That's why they \textit{fell},`` says Hayley to no one in particular, nodding with satisfied understanding.

``Can you point portals in any direction?'' asks Jonah.

``In theory.  Most installed portals all follow certain gravitational orientations so as not to confuse travellers.''



Jonah asks about how portals are made.  Rook says it is complicated.  While they are talking, Jaya is attempting to run while carrying Hayley.  It doesn't go well.  Jonah points the radar gun at them and Rook murmurs to Jonah that they probably would have died.

Jonah asks how Octavius creates the ad hoc portals and what is keeping him from using them to invade already.

Rook explains, ``Octavius has a device that creates them.  The difficulty is that you can have the device here but where it opens up on the other side, unless it is \underline{  {\color[RGB]{17,85,204}localized in some way}  } it could end up anywhere within a very large margin.  For instance, if I had the device here and was attempting to open a portal, the other end could open on the other side of this room or a hundred miles away.  Unless I had a device that could 'zoom in' on the particular location.  For example the \hl{beacons}\footnote{\textbf{Suko T }batons?  It was a little unintelligible in the recording. \textsubscript{12/23/14 3:14pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }He said beacon, but referred to the batons, yes. \textsubscript{12/25/14 10:48am}} that they carry allows us to tell the device 'here I am'.''

``Interesting.  Why don't they send in more people through the train network to bring more beacons in?'' asks Jonah

``That is why Transit Minor was destroyed.  I believe they have been attempting to do so and have had more success in other areas.  The other thing to note is that opening a portal requires an immense amount of energy.''

``\hl{But we use the trains all the time.}\footnote{\textbf{q.google }From an IC perspective the notion that all trains are portal jumping devices is no weirder than that there are portals at all.

From an OOC point of view, there are multi-colored sparks flying all over the cerebral cortex. \textsubscript{02/25/15 4:49pm}}''

``Yes but those were installed.  Basically they are opened in perpetuity.''

We continue to practice and Rook leaves, reminding us that Mess is at 0800.  Jaya's eye twitches.  Jonah hands off the gun to Carruthers, showing her how to operate it.  At a certain point Javier starts throwing shit at the radar gun to see how fast he can throw stuff.  Jaya immediately joins in and it becomes a competition.  Carruthers doesn't like this new game, putting on one of the helmets from the Combat armor and hoping they don't hit her with the stuff they are throwing.  Hayley just keeps running.  Jonah gives her helpful feedback.




\sceneHeadline{Mess Hall}

We're having enough fun that most of us lose track of the time. Luckily Hayley reminds everyone when breakfast is near.  We all roll into the Mess Hall together in a very congenial mood.  It's the first time that PG1 and PG2 have ever done so.  Jari and Sakhander are there.



As Jaya passes through the line (she gets the same food as everyone else), Jari reaches up to a shelf and hands her a bottle, ``By the way....There's not much left but if you want it, it's yours.''



In an expansive mood, Jaya offers to share her booze, pouring a shot of it in people's coffee (though she keeps the bulk of it for herself of course).  She even pours one for Hayley, who, uncharacteristically, does not stop her.  Hayley then stares at the spiked drink with great suspicion and dubiousness.  Much like Sakhander staring at the glass of water.



Lackovich turns to Jaya and asks quietly, ``That thing we talked about, still think it's a good idea?''

``What, shore leave?'' asks Jaya, confused.  Then her eyes go wide and she exclaims, ``Yes!''  She grabs Lackovich's shoulder and whispers loudly, ``Let's do it now.''  Jaya looks over at Jonah and her voice gets even more vehement, ``Let's do it \textit{now}.''

``Calm down!'' says Lackovich, trying to pry Jaya's hands off her.  ``I have to tell Rook.  Jeez.''

Jonah is trying to listen in on Jaya's thoughts.  He gets a feeling of excitement from Jaya and the image of his face and Lackovich's face.

Lackovich addresses her squad, ``Javier, you have rifle practice, Carruthers, you are to report to MedBay.  I'm going to go take a shower.  Bye.''  Javier nods.  Carruthers looks downcast.  Lackovich leaves.

Jaya looks at her squad and asks with a touch of confusion, ``So... what're you guys doing?''\footnote{\textbf{Suko T }I love this contrast between Lackovich and Jaya's way of dealing with their squads :) \textsubscript{12/23/14 11:23pm}}

``Eating.  Drinking.  Cheers,'' says Jonah, lifting his glass.

``I have reports to write.  Lots of reports'' says Hayley.

``But you finished those reports, right?'' says Jaya looking around.

``Additional reports,'' clarifies Hayley.

``I didn't give you more reports to write,'' says Jaya looking at Hayley a little suspiciously.

``They're not for you, Sir.''

Jaya frowns.  ``Who's ordering you to write more reports?  If Trenton's telling you to write him love letters, you don't have to do it.''

``They're for Agent Morgan,'' says Hayley.

``What reports did Morgan ask for?'' asks Jaya with a touch of panic in her voice. Jonah gets a flash of an image from Jaya of Morgan's face spliced together with Supay's mask and horns and he shuts down the connection again.

``Information that she requested,'' says Hayley.  ``I had a pseudo-mission!''

``Are you reporting on us?  Are you \textit{spying} on us??'' demands Jaya.  ``You can't spy on us!  Don't tell Morgan what we talk about in our bunks!!  It's not her business.''  Jaya starts looking around, paranoid.

Hayley is confused, ``Why would she ask?''

``She didn't ask about that?''

``No sir.''

``Wait- So then what did she ask about?''``Actually she did not ask about very much.  I offered information,'' says Hayley looking a little proud of herself.

``You know, you keep trying to get ahead, and that's really good.  But you're going to make the rest of us look bad.  So why don't you rein it in.  Just...work on your running.  Less reports, more running.  Don't kiss ass to Morgan.''

Hayley gets a very odd look on her face.

Jari calls out, ``Okay unless you are helping with dishes, time to go!''

Jaya stops mid conversation, drops her mug and leaves.  Hayley cleans up her tray and Jaya's.

Jonah just shakes his head and leaves.  Hayley looks at him a bit curiously but lets him leave without comment. 




\sceneHeadline{Bunk- Jaya and Morgan}

We all go through various training: weapons and various lectures on medical procedures and such.



After some training, Jaya heads back to her bunk and opens the door.  There's someone sitting in the chair that Jonah usually sits in.  It's Morgan. She's leaning back a little in the chair and has a thoughtful expression on her face.  Jaya stumbles back a little and puts her hand on the door.  ``Ah, Agent!  Sir!  Ma'am!''  Jaya looks around to make sure she's in the right room.  ``Uh.  Hi!''



Morgan is mostly in BDU but wearing a dress-down/training shirt.  On the table in front of her is her badge, face down, and gun, in its holster.  Morgan gives a friendly smile to Jaya.  Jaya starts sweating and salutes.  ``No need to salute,'' says Morgan.

``No I, uh, prefer to salute, uh....'' and Jaya salutes again for good measure.  Morgan returns it and slowly stands up.

``Do you uh, need the room?'' asks Jaya.

``No, I just wanted to have a quick word with you.  As a friend,'' says Morgan and adds, ``I mean, I think of you as a friend.  Which is an odd thing to say.  A comrade even.''

``Really?  Wow.  I'm, um.  Flattered!  Flattered!'' Jaya stammers, looking far more horrified than flattered, and checks her pulse to make sure she's not on a drug hallucination trip.  Her eyes are darting about the room and she rubs her new tooth as she tries to regroup.  ``What- what do you want to talk about?  Hayley?  Jonah?  Um....''  She starts backing up until she bumps into Oliver's bunk and she stops in confusion.

Morgan clears her throat and says, ``I felt it necessary to visit you, not as an officer, but as a friend.''  She starts pacing slowly toward Jaya who immediately starts sidling sideways.  Morgan's posture is relaxed but she doesn't stop stalking Jaya as they start circling the table.  She says to Jaya, ``I just felt like I owed you an expla-''

``You don't owe me anything!'' says Jaya, alarmed and raising placating hands. ``We are-''

Morgan places her hand on Jaya's shoulder and Jaya freezes, mentally cursing Morgan's greater reach.  ``It's just that... as your friend...  Hekate.  I wanted to talk to you about Hekate.''

Jaya looks over Morgan's shoulder in the vain hope that someone will come through the partially open door to save her.  Surely Morgan won't kill her so blatantly if there was a witness.  She says, ``Yeah. Sisters, I understand sisters.  No need to say anything more.  Yeah....''

``She is my sister.  And as her sister...'' Morgan leans forward until her head is even with Jaya's and says quietly, with terrifying precision, ``As her sister, and as an \textit{unholy bitch}, if you \textit{ever} disrespect her again, publicly, privately.... or even in the dark recesses of your mind...my response is going to be... disproportionate.''

``Noted!'' squeaks Jaya, pale beneath her tattoos.  Her mind roils with panic and she attempts to internalize Morgan's 'advice' immediately.

``Am I making myself heard?''

``Very!'' Jaya says faintly.

``As a friend,'' reminds Morgan.

The word causes Jaya's stomach to flip, but the realization that Morgan isn't going to kill her- at least right now- is slowly settling in and she becomes nearly numb with relief. She reaches up and pats Morgan's hand gently and clears her throat.  ``I'm totally, uh, it won't happen again. Sir.  Ma'am.''

``I knew you'd understand,'' says Morgan with her customary smile and she pats Jaya on the shoulder.  ``I like your bunk,'' says Morgan, looking around.  ``A little messier than I would keep it, but...''

``Hayley's been busy these last couple days,'' wheezes Jaya, attempting to sound calm and casual, but spoiling the effect by needing to lean on the table for support and sounding very winded.

Morgan picks up her gun and badge, nods at Jaya and walks out.

As soon as the door closes behind her, Jaya dives for her flask.




\sceneHeadline{Dr. Gerhauser's Office- Jonah and Hekate}

At approximately the same time as Jaya's retreat to quarters, Jonah knocks on Gerhauser's door.  He's bringing the pregnancy book with him.  There's a metallic click and the door opens slightly.  She's seated at her desk, typing into a console.  

``He....y Doctor,'' says Jonah.

``You may have a seat,'' says Hekate, still typing.  ``One moment.''  She finishes and looks up, ``I wanted to talk to you about the operation schedule.  Rook had put your sister on it and then removed her. Is that correct?''

``The operation schedule?'' asks Jonah in confusion.

``Yes.  We try not to have too many operations on top of one another.  Makes doctors tired.''

``Wait- operation on \textit{what?}`` asks Jonah in alarm.

``Agent Rook informed me that she was in need of an implant?''

``Regarding her schooling?'' asks Jonah slowly.``Yes I believe it was a learning module.''

Jonah visibly relaxes.  ``Yes.''

``And why was the operation cancelled?''

``Because he left it up to my sister and myself to decide how far to go and how fast.''

``She is below reading level for her age, is she not?  She is 13 correct?'' Hekate turns and consults a datapad.

``Reading level?''

``Yes.  Reading comprehension, knowledge of words, symbols, ability to interpret-''

``What level are you measuring with?''

``Hmm. I suppose these are outdated metrics for your people.  We can use this as a rubric.  Age versus grade level.  See this chart?  I'd put her about here.  Smart, but uneducated.''

Jonah gets a slightly nasty look on his face and he says pointedly, ``Yes.  Well.  Education appears to be a luxury.''

Hekate looks at him, saying in a slightly puzzled voice, ``In this case it's a luxury we can afford.  So why are we denying it to her?''

``Because I am not clear on what the consequences are.''

``The consequences of more education?''

``The consequences of putting a \textit{module in her head},`` says Jonah with emphasis.

``Oh, you refer to the cybernetics?  I suppose that is to be expected.  Is that the agreement you came to with Rook then?''

``Yes for the time being, we'd like to see how she does.''

``Oh.  Disappointing,'' says Hekate.

``Have you used these modules?'' asks Jonah

``Well I certainly didn't require a remedial module-''

``Does anyone in your family have these modules?''

``We all have cybernetics of one sort or another,'' says Hekate easily, as if this is completely normal. 

Jonah looks at her askance and says dryly, ``Do you.''

``Of course.''

``For example?''

``That's a fairly personal question,'' says Hekate.

``Well you're asking about a fairly personal matter,'' Jonah says acerbically.

``But I'm her doctor.''

``And I'm her brother.''

``I fail to see why that entitles you to personal information about me.''

``You're asking why I don't want to jump the gun...'' says Jonah.

``Ah.''  Hekate sighs.  ``Well I have a standard monitoring system, a standard cardiovascular emergency assist system, and a direct neural interface, though I abstained from the more military implants of my sister's...''

Jonah interrupts, ``How many of these- you don't have answer this, but how many are in your head?''

``Depending on how you count systems, I have three main systems,'' says Hekate.

``I see.  To be frank, that is at least a little bit comforting.  There is a great deal of technology that I know nothing about.''

``It is not that you don't know anything about it, it's that \hl{your people}\footnote{\textbf{q.google }Dr. G's biggest blind spot isn't the racial superiority it's the inability to understand how little most non-Citizens have. \textsubscript{02/25/15 4:55pm}} chose to eschew it for religious reasons.''\footnote{\textbf{Rebecca S. }Iiiiiiiiinteresting! \textsubscript{12/25/14 9:46am}}

``Religious reasons?''

Hekate says dismissively, ``Superstitions.  You know.''

``No I don't.''

``Something about the sanctity of the human body being more important than the extensibility of human power.'' 

``I see.  Who told you this?'' asks Jonah.

``History....'' Hekate sighs.  ``I forget that you often are not-''

REBECCAxxBEGINxxHIGHLIGHTxxJonah interrupts, ``You talk about my people as if there's only one group of people here.''

``Well more or less, that's true.  I suppose you can mince words between this klipspringer and that klipspringer but they are all basically klipspringers.''xxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }One of the top quotes of the night... Dr. G comparing Jonah to cattle essentially... \textsubscript{12/25/14 9:47am}}

``Right, well I don't think we should put cybernetics in to Riva just yet.''

``Why is that?  Is it because you are afraid of it?  Your cybernetics have not treated you ill, have they?'' asks Hekate curiously.

``That's a matter of opinion!''

``And what is your opinion?''

Jonah sighs deeply.  ``Are we speaking frankly?

``You are protected by doctor-patient confidentiality, if that is your concern.''

``Oh.  That's good.  Is that another thing that you brought from where you came from?''

\hl{``Ethics?  Yes.''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{12/23/14 11:40pm}}

``Doctor patient confidentiality, \textit{lovely}.  And how does that work exactly?'' says Jonah, sounding a bit hostile.

``You seem sarcastic.  What do you mean?''

``How much money changes hands to make it work?''

``I don't understand.''

``No, I guess not,'' says Jonah, a little bitterly.  ``Doctors obviously work differently where you come from.''

``Yes, we are not allowed to talk about our patients' personal matters to others.  Is that different for you?  How do your patients feel safe with you?''

``\textit{My} patients?''

``Yes...'' Hekate looks a little bit taken aback at Jonah's incredulous tone, wondering briefly if she had read that info correctly in Jonah's file.  ``You \textit{were }a doctor weren't you?  It was in your file.''

``I don't think you use the word the same way we use it.  A doctor is something Citizens have.''

``Ah.  You were a low-class doctor.  That's the same thing, though.  Right?''



Jonah looks around her office.  ``Where do we start?  There are all these books.  You learned to be a doctor from books?  Books are useful for teaching.  I wouldn't have agreed three months ago, but I agree now.''

Hekate says slowly, ``It's all open to you..  I don't understand what-''

``There are no \textit{books} on the street.''

``Well that is something to remedy.  In your sister's case, we have plenty of books but her reading comprehension is quite low so her ability to utilize them-''

``She's never had a chance to read.''

``Be that as it may, why deny it to her?'' asks Hekate.

``Because... I've already had something implanted in my head and I didn't know anything about how it worked when it happened, and I'm not convinced that the rest of you do either,'' says Jonah, sounding like he's getting a little worked up.

``As a point of medical knowledge, you should know that it's not entirely in your head, it's attached to any part of your nervous system.''

``Well there you go!  Didn't know \textit{that},'' says Jonah aggressively, almost nastily.  ``What else is there?  There's a great deal that needs to be clarified.  You haven't tried it yourself.''

``I can't.''

``How many people you know who have tried it?''

``On this base?''

``No, other than the ones on this base.''

``Well there is Octavius, I have never encountered one directly before... well not if you don't count my sister.''

``Well.  There you go.''

``But it wasn't her choice, so I wouldn't say that she 'tried it'.''

``Speaking frankly-''

``You keep using that phrase,'' notes Hekate.

``How much choice did I have?''

``Well that's an interesting philosophical question. I will grant you.  You both had a lot of choice and basically no choice.''

``Right.  And you used something that, forgive me, the only person you know who had similar technology, or similar enough, that either you're playing with fire or it's \textit{different} enough that you didn't know what would happen.''

Hekate says calmly, ``I see your concern.  Hmm.  In my professional judgement, it was safe enough at the time.  And I trust in my judgement.\footnote{\textbf{Suko T }No confidence issues with this gal :D  Go Dr. G! \textsubscript{12/23/14 11:58pm}}''

``I'd like to-''

``I understand if you don't.  I don't require you to, but I understand if that makes you uncomfortable.''

Jonah says frustratedly, ``Do you understand \textit{why} I don't trust you?  On these issues anyway.''

``I can't say I do.''

``Right.  Because you're a doctor.''

``No, because I'm a very smart person who has never done wrong by you. That is why you should trust me.''

``I don't agree with you.''

``Have I wronged you in some fashion?''

``At least once, yes,'' says Jonah.

``Enlighten me.''

Jonah \hl{just gives her a look and grips the chair arms meaningfully}\footnote{\textbf{q.google }I particularly liked that bit. \textsubscript{02/25/15 5:01pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{02/26/15 11:16am}}.

``Ah.  My sister's...'' she sighs.

``I take it you haven't tried \textit{that} either,'' says Jonah belligerently.

``Yes.  Mea culpa.  I apologize that at the time our focus was on Hayley, not on you.  I believe... your assistance in that matter was....critical.  I don't necessarily agree my sister's choice to go ahead with that procedure-''

``Choice again.  Did \textit{I} have a choice?''\footnote{\textbf{Rebecca S. }It somewhat surprises me to say it, but Jonah is really making a pile o' valid remarks in this conversation. \textsubscript{12/25/14 9:51am}}\footnote{$\rightarrow$\textbf{Suko T }I definitely agree! \textsubscript{12/25/14 4:21pm}}

``It was within the strictures of your laws, I believe.''

``That's not answering the question.''

Hekate concedes, ``True, that's a bit of an ethical dodge.  Do you not want see Hayley better?''

``\textit{That} made Hayley better?''

``Hayley was operating under a large number of genetic and behavioral constraints that have been bred into her.''

``Oh.  Wonderful.'' says Jonah flatly.

``And yes, if you want to see the numbers, I believe it made her better.''

``Oh.  Wonderful,'' says Jonah with heavy sarcasm.

Hekate pauses.  ``I am sensing that this affected you more profoundly than was previously detected?''

Jonah says slowly, angrily,  ``Instead of me, I suggest you try it yourself and then try to see how much time you want to spend in the same room and on the same team as the person who did it.'' He punches the book he's holding for emphasis.

Hekate seems a little surprised, ``Your discipline is somewhat greater than I had assessed.  I apologize for underestimating you.''

``Perhaps you can...'' Jonah changes what he's about to say and sighs.  ``I need to ask you a different thing.  About my sister.''

``Obviously, I am in your debt.''



Jonah places the book on her desk. ``Can you please explain what this is about?''

``I would like to, but doctor-patient confidentiality prohibits me.  However, as you are your sister's legal guardian, at least within a certain interpretation of the law, I can tell you that it is not about your sister.''

Jonah looks even more bewildered.

Hekate continues, ``In my professional opinion, it is important that you be at least passingly familiar with female pregnancy in your species.  Such that should you be called upon to perform a successful birth...surgery....you are able to do so.''

``And in your professional opinion this was relevant to learn in the middle of missions that may results in our deaths in the next few weeks?  This is high enough importance?''

``There is a lot of pre-natal care that is necessary for a successful pregnancy.''

``Wait.  Roll back.'' says Jonah but doesn't seem to know what to ask next.

Hekate says, ``You are already a skilled field surgeon, I don't think you need any more training in that.  I wanted to make sure you had the information in case it came up.  I cannot break doctor-patient confidentiality but I might point out that you have a number of women on your team.

``Interesting.  Okay.  for the record....'' Jonah says slowly.

``Which is entirely sealed so far as I'm concerned''

``\textit{If} my sister has a similar condition-''

``You would be told, as her legal guardian.  At least until she comes of age.''

Jonah says, ``I would hope that she trusts me to tells me, but it is perfectly reasonable to tell her to tell me.''

``That is general practice.  We don't try to pass along information unless we absolutely have to.  For the safety of the patient.''

``That makes more sense.  I'm surprised that you would tell me that instead of giving me a book,'' says Jonah, pointedly.

``I apologize.  Sometimes I overestimate people's ability to deal with my brusqueness.  I have a lot to attend to and often\hl{I deprioritize people's need to know things}\footnote{\textbf{q.google }That's good.  It makes her fit in well with the SAC-09 senior officer core. \textsubscript{02/25/15 5:05pm}}.''



Jonah starts getting a flood of anxiety from Jaya and he falls back in his chair with a look of alarm.  It is about this time that Jaya has returned to her room and having her ``conversation'' with Morgan.

``Jonah?  Are you alright?'' asks Hekate.

 {\color[RGB]{255,0,0}::Gerhauser!  Gerhauser.  Morgan.  Dr. Gerhauser..... I'm going to die.  She's going to kill me.   Ohhhhh Jesus!  She's } \textit{ {\color[RGB]{255,0,0}touching} } {\color[RGB]{255,0,0} me.  I'm going to die.  I'm going to die... gonna die.....oh god oh god....gonna die........::} 

``Jonah, do you sense displacement?'' asks Hekate.

``What is displacement?''

``Are you seeing something other than what you expect to see?''

 {\color[RGB]{255,0,0}::Okay........okay.... ..........I'm not going to die....not going to die.  It's going to be okay::} 

``I'm feeling something... very strongly,'' says Jonah distractedly.

``Is it related to the VTX?''

 {\color[RGB]{255,0,0}::Be nice to Dr. Gerhauser.  Be nice to Dr. Gerhauser.  Be nice to Dr. Gerhauser. Good happy thoughts.  }  {\color[RGB]{255,0,0}\hl{Stab her in the face.  NO!  Happy thoughts.}} \footnote{\textbf{Suko T }I listened to this whole bit more times than I needed to for the transcript because it was just so hilarious.  Rebecca, you are SO good. :D \textsubscript{12/24/14 10:42pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 Is there a way to digitize clips for sharing? \textsubscript{12/25/14 11:02am}}\footnote{$\rightarrow$\textbf{Suko T }I imagine there is!  I shall look into it.  I will try to find a nice elementary school kid who can show this luddite how to do it, since I have very little idea of how to do video/sound editing on a computer.  If it were on a cassette tape, I'd be *all* over that.

(Or, much more likely, I will make Peter do it for me) \textsubscript{12/25/14 4:25pm}} {\color[RGB]{255,0,0} Be nice to  Dr. Gerhauser.   Not going to die.::} 

``Apparently it's related to you,'' says Jonah, sounding bemused.

``Is the Agent okay?'' asks Hekate.

``She doesn't think so.''

``Hmmm, where is she?'' Hekate looks up Jaya's location.

Jaya is calming down and Jonah is able to focus a bit better.  He asks Hekate, ``What do your books tell you about this?  You know that the signals don't always get blocked, right?''

``There is some emotional bleed depending on how close the Operators are.  You and Agent Parvadi have a \hl{particularly...acerbic reaction to one another.}\footnote{\textbf{q.google } \textsubscript{02/25/15 5:07pm}}  The rougher edges are...rougher.  The quieter times are quieter,'' says Hekate.

``Agent Parvadi doesn't keep her-''``Thoughts to herself?'' interjects Hekate.

``She prefers I try and respect that. I don't even know if she knows how-''

``Well, given her educational level I'm not surprised.''

``You keep saying that,'' says Jonah sharply.

``What do you mean?''

Jonah demands, his voice getting louder and louder, ``Where in \textit{hell} is one supposed to get an education like you're talking about?  Unless you are Trenton.  You know that most people in the directorate are \textit{not Trenton}, right?''

Hekate replies calmly, ``True.  But that is why giving your sister an implant would be a good idea.  I suppose we could give you one as well, but you seem relatively intelligent.''

Exasperated, Jonah points out, ``What does that have to do with anything?  My sister is smarter than I am.''

``Possibly....''

``Look, it may be a good idea, but let her try the other way first,'' says Jonah, calming down a little.

``If you insist.  I just don't see any reason for delay. And as I said, the operation schedule is a little difficult to move around.  I saw she had been removed and I was disappointed.''



Jonah changes the subject abruptly.  ``The thing Agent Parvadi is feeling apparently has to do with  you.  She's terrified.''

``Of me?  I don't see why.  I didn't hurt her.'' says Hekate.  She adds, with just a whisper of emphasis, ``\hl{Not \textit{physically}}\footnote{\textbf{q.google }I don't think I laughed at the time, but now its pretty funny. \textsubscript{02/25/15 5:15pm}}.''

``Why would she be suddenly terrified of you?'' asks Jonah.

``Perhaps you should ask her about it,'' advises Hekate.

``No.  That's a bad idea,'' says Jonah unhesitatingly.

Hekate asks, ``Is she taking drugs?  Is she having a hallucinatory trip?  Has she had alcohol recently?''



Jonah frowns and says somewhat frustratedly, ``You know what, we should talk about how this Operator-Agent thing works.  I know you \textit{think} you know how it works.''

``What questions do you have?''

Jonah says to Hekate, ``Maybe \textit{you }should ask some questions.  This is not alcohol and not drugs. That stuff is part of the Chief's \textit{diet}.'' Hekate looks like she wants to say something but doesn't.

Jonah continues, ``It is easy to block those things out.  This is something else.'' 

\hl{Hekate asks, ``Has she been spending a great deal of time with Rook?  He hasn't been training her to any extra capacity beyond weapon training?''}\footnote{\textbf{Rebecca S. }Really really wonder what this could have meant \textsubscript{12/25/14 9:57am}}

Jonah is a bit surprised by the question, ``No, not to my knowledge.   I just don't see why this would suddenly happen....unless it's because of the double connection?  That it's harder to filter out?''

``You and Signe and you and her?  I would not expect so, but if you want I can run a \hl{Theta Scan}\footnote{\textbf{q.google }Beware the \_Theta Scan\_ my son, the neutrinos that bite the quantum interference waves that catch. \textsubscript{02/25/15 5:18pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }*grin* Nice! \textsubscript{02/26/15 11:21am}}.''

Jonah tries to explain. ``Look, I've never felt her this scared, at least not on base.''

``She seems relatively intimidated by my sister,'' says Hekate.  She pauses.  \hl{``Ah.''}\footnote{\textbf{Suko T }\textless 3 \textsubscript{12/24/14 3:03am}}  She turns to her computer.  Jonah looks horrified.

Hekate says, ``Suffice to say that I think Agent Parvardi is out of the woods.  Are you continuing to feel something from her?''

``No... but sisters has something to do with it.''

``Let me explore a theory and I'll get back to you.''

``I have enough trouble with one sister, I don't know how you deal with two.''

``Well it helps to be smarter than either of them-''

``That helps somehow?''

``Yes.''

``Helps with most people, I'm not sure it helps with sisters,'' Jonah sighs.  ``Family is hard.''

Hekate pauses and then says, ``I should get back to work unless you have any further questions?''

``I think we should speak quite a bit more about Operator Agent actually works.  Because one or both of us doesn't know enough about it,'' says Jonah, sounding tired. 

``I have given you all the documentation.  It seems to be working within parameters.''

``Yes but every time we talk, you tell me something new I didn't know.  And you were surprised by some of the things I am telling you about it.  And since at this point it's not really personal but is also a matter of our survival, I think we should know as much as we can.''

``Well if you wish to prepare a list of questions, I am happy to answer them.''

``Okay we can start with that,'' Jonah says, and then adds almost teasingly, ``Oh and I think you owe me a drink.''

``I do?''

``We talked about it, didn't we?''

``Oh.  Yes.  Um.  I'll see if I can find something.''

``I know where to get the good stuff, if it comes to that.''

Hekate clears her throat, ``So.  A drink, then.  And I take your sister off the operation schedule.'' 

``Yeah.  There are other things but I think they go better with alcohol,'' says Jonah.

Hekate goes very still at that.  

Jonah picks up his book. ``I'll read this, thank you.''

As he gets up, Hekate says, ``One more thing, I apologize for my sister.  Dismissed.''

``Your sister doesn't owe me any apologies,'' says Jonah and he closes the door behind him.




\sceneHeadline{Dr Gerhauser's office- Hayley and }\textbf{\hl{Dr. Gerhauser}}\footnote{\textbf{Suko T }Particularly for the last part of this scene, I was so much in Hayley's head I really didn't want to write in too much interpretation of Hekate's emotional state because it would be heavily Hayley-biased.  So Nate, if you could add in any particular notes that you want to convey, that would be super awesome.  Let's fine tune the pain! :D \textsubscript{12/25/14 1:49am}}

\textbf{\hl{{[}3 Tokens enter the Pool{]}}}\footnote{\textbf{Rebecca S. }So worth it \textsubscript{12/25/14 9:59am}}\footnote{$\rightarrow$\textbf{Suko T }Yes.  Yes it was. \textsubscript{12/25/14 4:25pm}}



Hayley has been writing her reports in Signe's room.  Sometimes Trenton is there.  Hayley mostly ignores him, other than to greet him politely when he enters the room.



Swan ducks into the room and says she's been summoned to Dr. Gerhauser's office.  Hayley smiles at Swan, clearly pleased to see him. ``I wanted to speak with you!  You told me to tell you if anyone asked to do a Theta Scan?''

``Yes.  Did someone?''

``Yes, Agent Rook.''

Swan grows noticeably paler.  ``Uh, okay. Thanks for letting me know.  Did he actually do the scan?''

``I don't think so.  He didn't use that tool thing that you showed me.''

``Ah.  Good.''

Hayley realizes something and adds, ``But my eyes were closed, so actually maybe he did.''

Swan looks even paler at this\footnote{\textbf{Rebecca S. }New crazy fan theory!!! - sweet lovable Swan  is actually a deep cover Octavian spy who has been slowly working to alter Hayley's mind so she can be Operated like Signe by Octavious.  (which would make Morgan's recommendations that she train against our security staff a Very Bad Idea)  Luckily Rook will uncover the plot Just In Time and save us all!  (or not... in which case PG1 will have to put Hayley down like the lovable family pet that has contracted rabies and is trying to kill everyone....) \textsubscript{12/25/14 10:04am}}+1QUOTE: Nathaniel Ford        12/30/2014 11:52 PM
I can't comment. and Hayley continues, ``But he didn't mention it until afterward, so maybe he didn't?  I don't actually know.  I'm sorry, I didn't want to open my eyes.''

``No, no you did fine.  He didn't talk to Dr. Gerhauser afterward did he?''

``I don't know, it was last night,'' says Hayley.

``Uhhh...I have to go...'' and Swan leaves quickly.



Hayley passes Jonah leaving Gerhauser's office, but doesn't speak to him other than to nod politely.  Even though the door is open, Hayley knocks and waits.  There is a longish pause and then a quiet, ``Come in.''  Hayley walks in and stands at parade rest, although she is listing slightly, keeping her weight off of her right leg.  She doesn't sit down and Dr. Gerhauser doesn't invite her to.



When Dr. Gerhauser says nothing, Hayley asks, ``Do you have time to speak now?  I have both an answer and an apology.  For you.''

``Which do you wish to start with?'' asks Dr. Gerhauser.

``The answer.  It is more important,'' says Hayley promptly.

``I agree.''

``I would like to choose door one.''

``So you wish to continue the hormone treatment.  You understand that this will result in certain physical, emotional and mental changes in you?

Hayley nods.  ``You explained that.  Yes.''

Dr. Gerhauser sighs.  ``There are a fair number of protocols and procedures you will have to follow on a regular basis.  Your fertility will increase.''

``My what?  I don't know that word.''

``It will become possible for you to make babies.''

Hayley makes an ``ewww'' face.  ``How?''

Dr. Gerhauser gives her a look and says, ``You know, I believe I have just the doctor on staff to explain this to you.''

Hayley catches on a little belatedly, ``Oh, you mean sexual relations to procreate?''

``Yes.''

``Oh.  I thought you meant I would shape them.  Like the scientists did.''  Hayley looks a little relieved.

``I will not be granting you authorization for that sort of equipment.''

``I would not be very good at that,'' says Hayley solemnly.

``We will also be providing treatment to suppress your fertility.  It is something you should be aware of, if for some reason you no longer have access to drugs.  We don't wish you to become pregnant at this time.  I don't believe you do either.''

``I guess not.'' says Hayley, not really understanding the implications.

``Well you can take that up with your contract holder.''

``Alright.  I will.''

Dr. Gerhauser continues, ``You are liable to get bigger.''

Hayley looks puzzled.  ``I thought I already reached my maximum height?''

``Life is full of surprises.  And I didn't say height.''

Hayley looks distressed and sad.  ``I will get \textit{fat??}''

Dr. Gerhauser rolls her eyes.  ``You will also be hungrier and more physically active, I should hope.  Any and all of these changes we will provide guidance for management, but mostly it will be up to you.''

Hayley looks more confident with this.  ``I follow rules well.  If the instructions are clear.''

``Hmm.  Well then.  Out of completely morbid curiosity, why did you choose door one?''

Hayley is surprised but replies readily, ``O-oh!  Because I want to be wiser.  So I can help Signe.  And if I was wiser, I maybe would have been able to help Oliver- uh, I mean Operator Langdon.''



Dr. Gerhauser stands and walks over to a cabinet.  She pulls out a briefcase and removes a satchel from it. After clearing a space on her desk, she puts it down and opens it.  She goes over the various chemicals inside and the time of day and the order that she is to take them.  There are some syringes, most are oral in liquid form, there are some backups in pellet form to be taken with water.  There is a printed schedule included with all this.  It all folds up into a tidy smallish package.  Apparently Jari can provide something to allow it to be attached to her uniform.  She spends about half an hour going over everything and then 15 minutes quizzing Hayley to see if she really understands what to do and when.  Hayley is used to such regimens and recalls it all reasonably well.



``That is Phase 1.''  Dr. Gerhauser pulls out another packet.  ``This is Phase 2.  The instruction booklet is inside, and we can go over that some other time.''

``When should I start Phase 1?'' asks Hayley.

``It is up to you.  The power is all in your hands.  It's my gift to you.''

``Thank you, that is very nice of you,'' says Hayley sincerely, obviously missing the bitter edge to Dr. Gerhauser's voice.  ``Do you have any more questions, Doctor?''

``No.  Do you?''

``No.  But I did have the apology.''

Dr. Gerhauser stares at Hayley.

Hayley asks hesitantly, ``May I apologize now?''

``It's a singular thing to ask permission to give an apology.''

``Oh.  I wanted to make sure you were done giving instructions first.''

``I am.''

``Very well.  I would like to apologize for being...unhelpful.  In our last conversation.''

``Why do you think that warrants an apology?''

Hayley says slowly, ``Because I.... misunderstood something about what you were trying to do.''

``What did you misunderstand?''

``I thought you were being a very bad doctor,'' says Hayley frankly, looking directly at Dr. Gerhauser.  ``And you were not helping me be my best.  I dislike that very much.  So I disliked you very much.   So I was very unhelpful.  Now I understand you were trying.  So I was wrong.  So I apologize.''

Dr. Gerhauser is silent for a while.  Hayley waits patiently.  Dr. Gerhauser says quietly, ``I accept your apology.''

Hayley nods in acknowledgement, her shoulders relaxing a little.

Dr. Gerhauser says, ``I unfortunately cannot be your psychological doctor in the way that I think you perhaps require.  So let's leave it at that.''

Hayley furrows her brow in puzzlement.  ``My...imaginary doctor?''

Dr. Gerhauser clears her throat, ``The word \textit{psychosomatic }is different from the word \textit{psychological}.''

``Oh. Sorry, they sound very similar.''

``One is imaginary, the other has to do with the mind and/or emotions.''

Hayley looks at Dr. Gerhauser curiously. ``How would you be a doctor of that?''

Looking at Hayley intently, Dr. Gerhauser asks, ``When Oliver died, how did it make you feel?''

Hayley tilts her head thoughtfully, ``While he was dying or after?''

``Why are you parsing the difference?''

``\textit{While} he was dying I was very scared.  And unhappy and in a lot of.... pain.  \textit{After} I was scared. But I was also happy,'' and Hayley smiles a little wistfully at the memory.

``You have sustained physical injuries before?''

``Many,'' says Hayley without hesitation.

``Did they scare you?''

``Not afterwards. But during?  Usually.  Yes.''

``So before the fact, they scared you.''

``Before I knew they were going to happen. Yes.''

``And they hurt?''

``Yes.''

``So you were scared and hurt.  Did you ever feel happy after the fact?  That it was over?''

Hayley pauses to think and then says firmly, ``No.''

``Did you ever feel relieved?''

``Yes.''

``Is relief like happiness?''

``Oh.  I never thought about it.''

``Is it more positive than negative?''

``Yes.''

Dr. Gerhauser says clearly, ``So, you are describing two situations.  One physical, one emotional. Both of which involved you being scared and in pain.  And then a mixture of positive and negative emotions.''

``Yes.''

``And you wonder why there can be doctors of both the mind and the body?''

``Yes.''

``Hmm.''

Hayley asks, ``I don't know how you heal that. So how would a doctor help?''

Dr. Gerhauser pauses for a long moment and then asks Hayley, ``Do you know how we healed Jaya's arm?''

``Um....bandages, surgeries and medication?''

``Could you do that yourself? Build her a new arm?''

``If I had clear instructions...perhaps,'' says Hayley with naive confidence.

``So.  You \textit{concede} that there are things that can be done that you do not understand, but if you were instructed in them, you could.''

``Oh there are \textit{many} things.  Yes.'' says Hayley.

``So you also concede while there may be \textit{physical }operations you do not know how to perform, someone \textit{else} may know them and can tell you.''

``Oh.  I am certain.  Yes.'' says Hayley with confidence.

``Then why would you not concede that there are \textit{mental }operations that someone else could perform?''

Hayley says slowly, ``Because I have never seen or heard one done before-''

``Yes you have,'' says Dr. Gerhauser pointedly.

Hayley looks blank.  ``I have?  I missed it. When?''

``You were there.  Jonah was there as well.''

Hayley is thinking very hard and trying to remember.

Dr. Gerhauser adds, ``You were under a great deal of duress at the time.  Sometimes healing can be painful.''

``It usually itches,'' says Hayley, trying to hold onto the parts of the conversation she understands.

``I don't think Jonah really felt that it was just an itch,'' says Dr. Gerhauser, pointedly.

Hayley looks pleadingly at Dr. Gerhauser, she's trying really hard to follow this line of clues but she's not getting it at all.

Dr. Gerhauser sighs.  ``In any event, I'll let you roll that one around in your head for a little bit.  \hl{Is there anything else?}\footnote{\textbf{Suko T }I think, after these last few conversations, the Gerhauser Sisters will just stop asking Hayley if there is anything else. It always seems to end in trauma. \textsubscript{12/24/14 11:50pm}}''



Hayley looks down and clears her throat a few times. She uncharacteristically starts fidgeting, shifting her weight a bit, straightening her jacket unnecessarily.  She takes a deep breath and looks earnestly at Dr. Gerhauser. ``I would....I would like to do something nice for you.''

``Ah.''  Dr. Gerhauser is motionless, her face blank.

Hayley clears her throat again, nervously.  ``I was told that I need to... watch over my emotional health and well being.''

``I fail to see the connection.''

``There was something nice that I wanted to do for you, but I didn't because I disliked you.  And now I don't.''

``You are welcome to continue to dislike me, it doesn't bother me at all,'' says Dr. Gerhauser evenly.

Hayley is thrown off by this and asks confusedly, ``You- you would like me \textit{not} to be helpful?''

``I don't require your helpfulness or not.  I don't require you to like me.''

``Alright,'' says Hayley, clearly not really understanding but accepting the information regardless.  She seems at a loss as to what to do next.

``Feel free to continue to hate me, if that is what you wish,'' says Dr. Gerhauser.

``I don't,'' says Hayley.

``Very well then.''

``You're my doctor,'' says Hayley slowly. ``You're going to help me be my best.  Is that not correct?'' she asks uncertainly.

``Whether or not you are your best is entirely up to you.  If I can open the door for you, then I consider that within my mandate. It does not require you to be nice to me.  Nor, at times, does it require me to be nice to \textit{you}.''

``Of- of course not,'' says Hayley, with a 'duh, of course that's how things work' expression.  She adds cautiously, ``...but I would like to.''

``Why?'' asks Dr. Gerhauser, almost growling.

Hayley says slowly, ``Because...because you are important!  And I would like to try to please you.''  She smiles a little anxiously at Dr. Gerhauser.  ``It makes me feel better,'' Hayley adds.

Dr. Gerhauser takes a deep breath and she stares at Hayley for several heartbeats.  Her affect changes suddenly.  She smiles and says indulgently, ``Dear Hayley, what do you have for me today?''

Hayley takes a deep breath and closes her eyes.  When she opens them, she is smiling, her expression clear and a little eager.  ``I want to share with you that... the \textit{very} last, the very last memory that he held onto the longest-''

Dr. Gerhauser's face goes cold and she orders, ``Stop.  Absolutely stop.  \textit{Leave}.''

\hl{``-was the memory of...}\footnote{\textbf{Nathaniel Ford }What was Hayley going to say here? \textsubscript{12/26/14 10:40pm}}\footnote{$\rightarrow$\textbf{Suko T }''-was the memory of you, on the balcony by the lake, telling him that you loved him.  Even though they had taken away your name from him by then, I could feel how much he still loved you and wanted to see you again.  Isn't that nice?''

:D \textsubscript{12/27/14 1:45am}}Oh.  Alright.'' Hayley looks very confused and disconcerted, and she turns to leave.  She looks back at Dr. Gerhauser, her face very bewildered and distressed, wondering what went wrong.  This was not the reaction she had expected.

Dr. Gerhauser is visibly quivering a bit.

Hayley pauses and says uncertainly, ``I...I apologize.''  She clearly doesn't know what she's apologizing for.

Dr. Gerhauser says nothing.

Hayley turns away and walks to the door, her limping very pronounced.  She puts her hand on the door panel and stops, her back to Dr. Gerhauser.  She deliberately shifts her weight to her right leg and at the sharp intense pain this causes, her anxiety drains away.  She turns her head to look at Dr. Gerhauser and says quietly, ``He loved you.''  

Dr. Gerhauser does not look at Hayley and says nothing.  

Hayley adds, ``I thought you would have wanted-''

``That is where you were wrong.  Get out. Get out \textit{now},'' Dr. Gerhauser bites out.

Undeterred by her tone, Hayley frowns and says confidently, ``No.  I was there with him.  I'm \textit{not} wrong.''

``\textit{Get}.  \textit{Out}.'' hisses Dr. Gerhauser.

Hayley looks at Dr. Gerhauser curiously for a moment and then says quietly, ``Okay.''  She steps out of the office and closes the door gently behind her.  As soon as the door is shut she starts hearing the massive shattering of things.  Really large things.




\sceneHeadline{Ops}

The atmosphere on the base is awkward, people aren't really talking to each other.   



The next day, Hayley reports to Ops to give Morgan her completed reports.  As she walks in, Dr. Gerhauser is leaving.  Dr. Gerhauser blows right past Hayley, not acknowledging her existence in any way.  Hayley nods politely to her and doesn't think anything of it.



Morgan is sitting at the table, her wolfish grin just a bit more indulgent than usual.  Hayley salutes.  ``Agent,'' says Morgan.  ``Are those my reports?''

``Yes, sir.''

``Good. Go fetch Jaya.''

``Yes, sir.''  Hayley leaves the reports with Morgan and heads off to find Jaya.



Jaya is not in her bunk, so Hayley methodically visits the handful locations where she has found Jaya before.  She eventually finds Jaya on the train platform, smoking.

``Sir?'' calls out Hayley.

``What? Sir Ma'am...yes?'' Jaya turns around and relaxes a bit when she sees that it's Hayley.

``Sir, Agent Morgan has requested your presence in Ops.''

Jaya stubs out her cigarette.  ``Are we... going on the mission?  Are we going to the Beacon?''

``I don't know, she only requested you.''

``Only me?  Okay.  Yeah.''  Jaya gives Hayley a fatalistic look and starts walking toward Ops.  On the way she whispers to Hayley, ``Did she...did she look...angry?''

``She's smiling!'' says Hayley cheerfully.  ``I think she is happy.''

Jaya looks terrified and she starts patting herself down.  She removes several small vials and packets, handing them to Hayley.  ``Hold onto these for me and just go put them on my bunk, okay?  Just in case.''

Hayley nods and accepts them and puts them away carefully.



Inside Ops, there is Agent Morgan, Dr. Swan, Larissa, Rook, Lackovich and Carruthers.  Carruthers is already in the tank and Lackovich is getting undressed.   Hayley salutes Agent Morgan, Rook and Lackovich.  She smiles at Carruthers.

Morgan greets Jaya, ``Agent.  You ready?''

Jaya looks at her blankly for a moment and then says with increasing excitement as she realizes what's about to happen, ``Yeeeeesss?  Yes.  Yes!''

``There's my budding battle commander,'' says Morgan.

``I'm ready!  So ready.'' says Jaya as she start taking her shirt off.

Rook stops her, ``Ah, Agent, it is not necessary that you get undressed.''

``But don't I need to...?'' asks Jaya, waving at the tanks.

``No.  I will escort you to the couch,'' says Rook. 

Jaya starts buttoning her shirt back up again and says loudly, ``I'm ready!''

Morgan asks Jaya, ``I just I need to clarify one point.  You wish us to disengage Jonah?''

``YES,'' says Jaya very clearly and uncharacteristically meeting Morgan's gaze directly.

``Are you sure that is best for your optimal operational performance?''

Jaya pauses at that and says slightly less confidently, ``Yes.''  She adds with increasing enthusiasm, ``I believe it will be optimal performance for myself and my teammate and my team to function...optimally.  Really, it will just be better for everyone.'' Jaya taps her hand on the table emphatically.

``A lot of the literature indicates that a one-to-one connection is better than a larger network, so if you feel safer that way...''

``Safer?  What??'' Jaya is momentarily puzzled and then, realizing it's argument to back her position, says with conviction, ``Yes.  Yes I do.''

``Alrighty then,'' Morgan says and then turns to Hayley.  ``Agent, please fetch Operator Gemayel.''  Hayley leaves.


\sceneHeadline{Comfy Chair Room- Jaya}

Rook takes Jaya to the room she was in the last time the Operator-Agent connection was made, with the weapons in cages on the walls and the comfy chairs.

Rook has Jaya take a seat and then sits across from her and says.  ``I have to ask you an awkward question.''

``Sure...yeah! Go ahead,'' says Jaya a little warily.

\hl{``Will you please tell me that you love me?''}\footnote{\textbf{Suko T }I would!  I do! \textsubscript{12/25/14 2:47am}}

Immediately she scowls.  ``I don't want to give up the arm!  NO!'' Her tone is vehement and she cradles her arm protectively, hugging herself.

``You don't have to give up the arm, but I would prefer it is disengaged during the procedure.  For your own safety.''

Jaya looks sad.  ``Could I just- hold onto it?  Even if it's detached.  I just don't want to give it up.''

``I don't see a problem with that,'' says Rook.

After a pause, Jaya turns away slightly and whispers the key words to her arm.  There's a mechanical click and the device falls away, exposing the metal cap at the end of her stump.  She nestles the metallic limb it in the crook of her arm like a baby, petting it lovingly.  After Rook leaves, Jaya quickly grows bored and starts swinging her arm experimentally like a truncheon, getting used to the weight of it.




\sceneHeadline{Ops}

Hayley eventually finds Jonah in the MedLab library.  He's reading.  She tells Jonah that he's needed in Ops.  ``Do you know what for?'' he asks.

``I believe it has to do with the Tanks.  And dis-engagement, which I believe does not mean divorce in this case,'' says Hayley.

There's a loud ``bong!'' noise that reverberates throughout the base. 

``That noise again?'' says Hayley, frowning.

``No.  Oh \textit{no}.'' says Jonah, sounding alarmed.

Hayley and Jonah start running to Ops.



There is a bit of a kerfuffle in Ops when they get there.  Rook is sitting at the table, very still.  Victor and Trenton are in the room.  Morgan looks over at Jonah as he enters and says, ``Ah!  Operator.  We are going to be disconnecting you from Agent Pavardi, and connecting Operator Lackovich to her, as an extension of our base-to-field capabilities. Do you understand?  Any questions?''

``Is that the extent of what we are doing?'' asks Jonah.``Yes, although a separate situation has arisen,'' explains Morgan.

``Yes,'' says Rook.

``We wished to make sure you are comfortable, because there can be some disorientation,'' says Morgan.

``As long as it does not interfere with the separate situation, I am at your disposal,'' says Jonah.

``It should actually increase your capacity to deal with Signe,'' says Morgan. 

Hayley looks alert at that and then her eyes narrow in thought as if she's maybe connecting the dots at last.



REBECCAxxBEGINxxHIGHLIGHTxxMorgan invites him to sit down and offers him tea, which he accepts.

``Requesting clearance for four through seven,'' says Rook to Morgan.

Morgan frowns, ``\textit{Now?}''

``I'm afraid so.''

``Granted.''



Jari comes in and pours some tea.  He looks around and puts it down.  Morgan looks at him and he tightens his jaw and makes a thoughtful sound.  Jari turns and leaves.xxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }Poor poor sad Rebecca has no idea what's happening here. \textsubscript{12/25/14 10:16am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'd be surprised if anyone did, at this juncture. \textsubscript{12/25/14 11:20am}}\footnote{$\rightarrow$\textbf{Suko T }I have some guesses but the only ones I'll admit to publicly is that I was thinking Rook was referring to LRMs and maybe this particular situation has something to do with Jari's past in Anglia?  Probably totally wrong, but I often guess the wrong thing, which makes me crap at being a detective. :) \textsubscript{12/25/14 4:33pm}}



Larissa says, ``Flooding Concourses 3 and 4''




\sceneHeadline{Comfy Chair Room- Jaya}

Jaya hears a distant rumble.  Jonah feels a wave of excitement from Jaya, if there was a Christmas, it would be like Christmas!

Jaya starts feeling tired and she goes back to cradling her mechanical arm.

Jonah has the oddest feeling of relaxation, like getting a massage...in his head. There's a sensation of letting go, of muscles relaxing that he didn't even know were tense.  He feels tired.




\sceneHeadline{Ops}

Larissa says, ``We're clear.  Aligning interlocks.''

Morgan says, ``Proceed.''

Rook says, ``T minus 27''

Morgan frowns at this.  Hayley is paying close attention to all of this.

``Flooding Concourses 1 and 2,'' says Larissa.  Hayley notes the monitors tracking the progress again.  

From Carruthers Hayley gets a sense of excited ``Wheee!''



The lights flicker and multiple systems seem to loose power briefly and then comes back up.  Trenton and Victor are babbling intensely to Larissa.



Jonah is mostly back now, and he doesn't feel Jaya in his head anymore.  Signe is still there but quiescent. 




\sceneHeadline{Comfy Chair Room- Jaya}

Jaya a little tired and feels a slight sense of frustration, a ``when will this be over??'' feeling.  Then there is a blinding white light and she starts hearing a distant ringing in her ears.




\sceneHeadline{Elsewhere}

\textit{Jaya is seated at a table. She is at one end and there is an empty chair on the other end.  Her sister is seated to her side, looking a little heavier than Jaya remembers.  Padme is talking to one of her sons.  Garren is there.  Most of the table is occupied with Padme's kids, but there is a young girl there, whom Jaya recognizes.  From the photo.  On a phone.}



\textit{There is a ton of food on the table, and photos on the walls.  Light is streaming in through a window.  Jaya is feeling remarkably chill, and there's the familiar warmth of alcohol permeating her }\textit{\hl{body}}\footnote{\textbf{Nathaniel Ford }Jaya may not necessarily pick up on it, but her body doesn't feel strung-out, like her regular body does (from years of drug use). \textsubscript{12/25/14 11:22am}}\textit{.  Everyone is talking animatedly, and two small kids are running in circles around the table.  The doorbell rings.}



\textit{Jaya looks down at herself.  She can see her tattoos are different, she has both of her hands, and she's wearing a dress, not her uniform.  Jaya hears Padme say to the girl, ``I bet your mom flipped her shit when you got that.''  The girl's face turns red.}

\textit{Jaya looks up and has a feeling of ``yeah I did.''  Jaya nods and looks carefully at the girl.  She can't see anything obvious on the girl (like a nosering or anything), she's nicely dressed.  Seated next to the girl is a young man.  The girl looks like a teenager, maybe 13 or 14.}



\textit{The doorbell rings again.  Padme asks, ``Do you want me to get that?''}

\textit{``Yeah. Fucking go get the- yeah,'' says Jaya.}

\textit{``Language,'' says Padme disapprovingly as she gets up.}

\textit{Jaya picks up her glass and looks down the table. There is a giant cooked bird in the middle of the table that smells incredible.  Jaya picks up her knife, slices a chunk out of the turkey and leans over toward her daughter, grinning.}

\textit{``Mom!'' exclaims her daughter.  When Jaya says nothing and just starts chewing on the turkey meat, still smiling.  }

\textit{Her daughter looks at her funny and asks, ``Are you okay?''}



\textit{``Um, there are two officers here to see you,'' Padme announces to Jaya.  }

\textit{Jaya's grin disappears.  ``Is it Morgan?''}

\textit{The people at the table start paying attention to this.  ``Who's Morgan?'' asks her daughter.}

\textit{Jaya turns and tries to see who's at the door, but she can't see it from her seat at the table.}

\textit{She sits back down and shakes her head.  ``It's gonna be a good trip.  Send them away.   I'm just going to stay here...'' and she turns her attention back to her daugher.}

\textit{``Mom!  Stop being weird,'' mutters her daughter.  Jaya laughs and tousles her daughter's hair.}



\textit{Padme sits down, leans over and whispers to Jaya, ``It's the FBI.  They're asking for you.''}

\textit{``What?  No!  No!  I'm staying here!'' Jaya grabs the hand of her daughter, squeezing it a little bit  too hard.  ``What's your name?''}

\textit{``}\textit{\hl{Kali}}\footnote{\textbf{Suko T }Though she pronounces it like ``Callie'' \textsubscript{12/25/14 3:39am}}\textit{, mom.  Are you okay??''}

\textit{``Good.  Good name,'' says Jaya approvingly.  She is pleased to note that Kali looks like her.   Maybe a bit like Padme too.}

\textit{Jaya notices out of the corner of her eye that two people, a man and a woman, have entered the room but her attention remains on Kali.  The woman says, ``Ms. Parvadi?''}

\textit{The ringing noise is getting louder.}

\textit{Jaya asks Kali, ``You look really good.  Are you strong?  You gotta be able to defend yourself.'' }

\textit{``Mom!  Calm down.''}

\textit{``I know!  I just don't want to let go,'' says Jaya and grabs her daughter's other hand.}

\textit{Kali says, ``We had this conversation!  He's cool, okay??  Can you stop embarrassing me?''}

\textit{``Fuck off,'' Jaya tells the boy and turns back to her daughter.}

\textit{The woman FBI agent says, ``Ms. Pavardi..are you okay?''}

\textit{``Jaya?'' asks Padme, worried.}

\textit{\hl{The man says, ``Wait a moment...''}}\footnote{\textbf{Rebecca S. }:D \textsubscript{12/25/14 10:18am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{12/25/14 4:34pm}}



\textit{Jaya looks over at them. She gets a vague echoey hollow feeling, like she really should know who these people are, but she doesn't recognize them.   She says to them emphatically, ``Fuck off.'' and turns back to her daughter. She holds Kali's head between her hands and looks at her intensely, ``I just- I just want you to be good!  Make me proud!''}

\textit{``I am good!'' says Kali.}

\textit{Jaya pulls Kaili closer into a hug and pats her on the back.  She rests her head on Kali's shoulder.}



\textit{The man turns to Padme and asks, ``Is this.... normal?''}

\textit{Padme, though she looks alarmed, tries to cover for Jaya.  ``I'm sorry, you caught us at a bad time....''}

\textit{The ringing sound is getting very loud now.}

\textit{Even through that noise and all the commotion going on, Jaya's attention is caught by the tv in the other room.  There is an image of a hostage situation around a college campus, Reed College perhaps?  And scrolling across the bottom of the screen is a warning notice, ``The CDC has expanded its warning regarding-''}

\textit{The ringing gets very loud.  Jaya's vision gets very bright and her family, her daughter, all disappear.}




\sceneHeadline{Comfy Chair Room- Jaya}

And then Jaya feels incredibly \textit{incredibly} angry.  Not dynamically angry, statically angry.  She feels a seething core of hatred and anger.  Of everything.  It's so intense that even Jaya is a little taken aback and impressed by it.  She's a little ashamed to realize she is not this hardcore.  What she thought was fury before is nothing compared to this.



Jaya feels like she is in a small room with\hl{a furnace of anger}\footnote{\textbf{Rebecca S. }I am extremely amused by this, having used a similar phrase to describe myself.  So now to me it is like this:  There is a Rebecca that has a Jaya in her head, and that Jaya has a Rebecca in her head.  Madness abounds. \textsubscript{12/25/14 1:07pm}}\footnote{$\rightarrow$\textbf{Suko T }It's Anger Inception!  Is the top still spinning? :D \textsubscript{12/25/14 4:35pm}}.  Slowly the sensation tamps down until it is just a constant burning warmth at the back of her mind.  She can tell the identity associated with it is Agnes (Lackovich's given name).  She eventually senses that the anger has a target.  Jaya wonders if the target is her, but after a bit, she can feel that while she is not the target, she is \textit{not} a good person and definitely provides fuel for the fire.  



Jaya is feeling a surge of energy.




\sceneHeadline{Ops}

In Ops, Victor is losing his shit.  He and Trenton are talking technobabble very rapidly and intensely.

``What is going on?'' asks Jonah.

``Shut up for a moment, Jonah!'' says Trenton and goes back to arguing with Victor, talking a mile a minute.



Rook has half turned toward Trenton and Victor but he still has that slightly distant look in his eyes.

Morgan is looking at a datapad, her expression still and thoughtful.

Karil is in the room, fully armored up.

Hayley has moved to stand by Carruthers, in a guard position.



Victor finally yells, ``I just gotta know!''

Trenton rolls his eyes and says, ``I can't believe I'm saying this but \textit{let me ask}.''

``No!  You'll \hl{goof}\footnote{\textbf{Nathaniel Ford }Victor doesn't swear like a sailor, but rather like a person with awkward rules of politeness. \textsubscript{12/25/14 11:28am}}\footnote{$\rightarrow$\textbf{Suko T }Victor is so cute. \textsubscript{12/25/14 4:35pm}} it up!'' exclaims Victor.  The two of them leave the room.




\sceneHeadline{Comfy Chair Room- Jaya, Trenton and Victor}

Jaya decides to reattach her arm, murmuring her key phrase. 

Micah looks over at her, ``What?''

Jaya flips him off with her reattached arm.



A few seconds later, Trenton and Victor burst into the room.  Victor yells, ``Jaya!''

Jaya pops her blade and Victor flings himself backward with a startled squeak.

Trenton jumps in front of Victor and shoves him away from Jaya.

Micah is looking at all of them in consternation, trying to decide if he should go for his gun or his truncheon or...



Trenton puts his hands out placatingly toward Jaya, ``Calm down!  Calm down, we're all good here.  We just need to ask you a question.''

``Get your hand out of my fucking face!'' snarls Jaya.

Trenton says, ``Calm down, we realize that you just got Operated.''

``It's cool!  I'm fine.  Fine.  Not like it's never happened before.  I'm like a fucking pro at it!  What's going on?''

``Just... were you...dissociated at all?  Did you hallucinate?'' Trenton asks.

``Yeah, I tripped a little bit. Happened last time too.  So?''

Victor pipes up, ``I'm right!  I'm right!!''

``What did you trip about?'' asks Trenton.

Jaya says rapidly, defensively, ``It's my trip!  It's my own business.  It's none of your fucking business!  I don't have to tell you my private fantasies. You're not the one in my fucking head!''

 {\color[RGB]{74,134,232}::Just.  Tell them}  {\color[RGB]{74,134,232}\hl{.::}} \footnote{\textbf{Suko T }Color blue now for Lackovich to Jaya.  And red is Jaya to Lackovich but it really should be the other way around, shouldn't it? :D \textsubscript{12/25/14 4:21am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Lackovich's is a cold rage. A cold, cold rage of blazing hot cold rage. \textsubscript{02/11/15 5:10pm}}

 {\color[RGB]{255,0,0}::Fuck fuck fuck.  FUCK!::} 

Jaya starts pacing.

 {\color[RGB]{74,134,232}::Get. Your shit. Together.::} 

Jaya punches the wall.  ``FINE!'' she yells. ``I just imagined I was having dinner with my family!  Okay??  Nothing weird about that.  I was just with my family.''  Jaya swings at Victor and Trenton with her fleshy hand.

``Yeah!'' crows Victor, and at Jaya's glare, he ducks behind Trenton again.

 {\color[RGB]{74,134,232}::You need to calm the fuck down::} 

``It's my brain!'' complains Jaya.

Still hiding behind Trenton, Victor asks excitedly, ``But it was you- \textit{you} right? Did you have both your hands??''

``That's a personal question!'' yells Jaya.

Trenton looks at Jaya in disbelief, ``It's a \textit{question}.  Come \textit{on}.''

``I mean, they weren't my hands.  They didn't have the-'' Jaya gestures to her tatoos.

``Can you tell us anything else about it?  Was there anything familiar about it?  Had you been there before?'' Victor pelts Jaya with questions.

Jaya says hesitatingly, ``There was... meat.''

``Meat?  Meat?  What kind of meat?'' asks Victor eagerly.

``I don't know.  It was \textit{really} fucking good,'' says Jaya, smiling at the memory.

``Was it a klipspringer?  A chicken?''

``Yeah it was like a big chicken, like five chickens but just one chicken,'' and Jaya gestures to demonstrate how large.

Victor says, ``Chickens don't get that big.''

``Fuck you!  I can fantasize about big birds!'' says Jaya loudly.



Trenton asks, ``Do you remember any names?''

``Kali,'' Jaya responds immediately.

``Who was that?'' asks Victor.``None of your business!  No one on base.  It's nobody.''

Victor mutters to Trenton, ``Yeah, we don't know anyone by that name.'' Trenton looks skeptical.

Jaya rubs her tummy slightly and then rubs her hands together.  In her head she is singing gleefully to herself  {\color[RGB]{255,0,0}::My daughter, my daughter is fucking awesome!::} 

There is a dampening down of Agnes' anger and then  {\color[RGB]{74,134,232}::Wait. } \textit{ {\color[RGB]{74,134,232}\hl{Daughter}} }\footnote{\textbf{Nathaniel Ford }Though I didn't pull it off at the time, this is not dissimilar to Vader saying, ``Sis...ter.'' \textsubscript{12/27/14 7:49pm}} {\color[RGB]{74,134,232}?::}  and there is the sensation that someone threw a huge fucking log on the fire.



Rook walks in, greets Jaya, and dismisses Trenton and Victor.  They leave, resuming their technobabble.  Rook smiles at Jaya.  Jaya smiles back and salutes.




\sceneHeadline{Ops}

Morgan turns to Jonah.  ``I believe we are done here.  Get some rest.  We'll start your operation very soon.  You feeling alright?''

``I believe so.  Signe is still unconscious right?'' says Jonah.

``Yes.''

``Will you need us any further for this process?'' Jonah asks.  Morgan shakes her head.  Jonah thanks her and leaves.




\sceneHeadline{\hl{Comfy Chair Room}}\footnote{\textbf{Nathaniel Ford }Let us disambiguate this from Jonah's Comfy Chair Room, which is elsewhere. \textsubscript{12/25/14 11:31am}}\textbf{- Jaya and Rook}

Rook asks Jaya, ``How do you feel?''

``Different.  You know...different.''  Jaya clears her throat and then looks over at Micah, still standing by the door, ready for \hl{close combat with a rifle}\footnote{\textbf{Suko T }See Morgan?  It's a thing.  A fighting style.  Oliver started it.  :) \textsubscript{12/25/14 11:58pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Morgan didn't say it *wasn't* a thing. I don't think Morgan would ever claim 'x form of combat isnt' a thing'. Morgan thinks everything is a form of combat. 

That said, some forms are clearly better than others for hurting people in a particular way. \textsubscript{12/26/14 5:42pm}}\footnote{$\rightarrow$\textbf{Suko T }Ha!  Morgan is so great.  :) \textsubscript{12/27/14 1:52am}}.  Jaya leans close to Rook and whispers, ``I think, maybe, Lackovich has some anger management issues.''

Rook replies in a normal voice, ``Actually, I think she is markedly talented at anger management, considering what she's been through.''

Jaya looks over at Micah and whispers again, ``I just think you should keep an eye on her.''

``Oh I have, but of everyone who has damaged base property, she is not the worst offender.'' Rook does not look at the dent in the wall. ``Go get some rest.''

``Actually I'm feeling pretty good-''

``Then go for a run and then go get some rest,'' amends Rook.

Jaya looks at Rook considerably.  ``Hey you want to spar?''

Rook looks at her.

``Because sometimes Morgan and I...'' says Jaya.  ``You know....I'm pretty tough so it would be pretty damaging to Hayley if I went against her, so... you know..''

``I know that Morgan enjoys sparring with you.  I will see if she is available.'' says Rook

``No!  No... I was not talking about Morgan.  I was just...seeing if you wanted to... uh....'' says Jaya.

``Normally I would take you up on the offer but I have an operation to prepare for.''

``Uh okay.'' says Jaya and she looks over at Micah.  ``How about you?''

Micah snorts derisively.``What the fuck is that for?'' demands Jaya and she walks out of the room.



Jaya can feel that Lackovich has attenuated the connection between them.  Unlike with Jonah there aren't as many clear articulated thoughts, but there are strong emotions and sometimes they are strong enough that Jaya feels occasionally compelled by them.  When Lackovich tells her to calm down, Jaya actually feels compelled to calm down.




\sceneHeadline{Ops}

Jaya swings by Ops.  Lackovich is in the tank and she meets Jaya's eyes when she walks in.  Jaya looks at Lackovich  {\color[RGB]{255,0,0}::Damn she be a skinny bitch.  Needs some ink.::} 

Lackovich has a thought reply to that.  It is not nice.

Carruthers is also watching Jaya.  Jaya nods to both of them.

Hayley greets Jaya, ``Hello, Sir.''

``Hey.''  Jaya looks around Ops and seems a little disappointed.  ``I was looking for Jonah,'' says Jaya.  ``I was gonna fucking gloat and say 'guess what I'm thinking now'!'' she says gleefully.  At Hayley's polite, blank look, Jaya explains excitedly, ``'cause he \textit{can't}.''  No one laughs.  Jaya keeps looking at the tank and looking away.  ``Uh....I just wanted to see if there's anything I need to do...''

``I believe we are supposed to get some rest before our mission,'' says Hayley.

``Ooookay.  Yeah.  I'm gonna go rest now....'' says Jaya.  She lingers for a bit longer and then leaves.   From Lackovich she gets  {\color[RGB]{74,134,232}::I'm not going to stop you.::} 



Jaya goes back to the train platform and smokes.



When Larissa gives Carruthers the go ahead, Hayley stays in Ops to help Carruthers out of the tank and get cleaned up and dressed.  




\sceneHeadline{MedBay- Hayley and Signe}

Dr. Gerhauser tells Jonah that they are waking up Signe. ``Let us know if you feel anything unusual.''

``Thank you,'' says Jonah.

Dr. Gerhauser pauses and says, ``There's a lot of that going around lately.''



Hayley is called down to MedBay.  They are waking Signe up.  Trenton is also there.  Seeing that Signe is still strapped down to the bed, Hayley doesn't want her to be afraid so she leans over Signe, making sure that Signe can see her right away.



Dr. Gerhauser is the one waking Signe up.  As Signe wakes up, the connection between her and Jonah actually feel a bit easier (for Jonah).  He can sense a lot of grief from Signe.  Jonah can also tell that the first person Signe looks for is Trenton, but Hayley is a close second.  



Signe smiles at Hayley.  Hayley smiles back and tells her to stay still while they run some tests and remove the straps.  Signe's words are a bit slurred but she seems otherwise okay.  Signe shyly looks over at Trenton a lot but does focus on Hayley when Hayley is talking to her.



After an hour of tests, Dr. Gerhauser (who had been performing all the tests herself), says, ``She is cleared to return to quarters.''  She looks at Hayley, ``I suppose you are welcome to escort them.  But be aware that you have an operation in less than 24 hours.''

``I understand.  Thank you,'' says Hayley.



Hayley helps Signe get dressed, whispering excitedly, ``I have so much to tell you!'' 

Trenton says awkwardly, ``I guess we should go back to quarters...?'' 

Hayley doesn't notice his unusual discomfort but she offers, ``Signe can stay with me if she wants, I have permission.''

They all go back to Trenton's room on the Lab Level.  

Since he can tell where Signe is, Jonah intercepts them on the way.  He pulls Trenton aside, ``So look, I'm not going to be... knocking on any doors.  But I don't know what's going to happen for the next 24 hours.  I don't know how easily I can filter it out.  I just want you to be aware of that.''

Trenton puts his hand on Jonah's shoulder and says a bit cheekily, ``I guess... just take notes?''

``Just letting you know, man,'' says Jonah.

``Appreciate that,'' says Trenton.



Signe, Trenton and Hayley arrive at Trenton's room.  His bed is large, clearly made up of other beds shoved together.

Trenton says to Hayley, ``You're welcome to stay here if you want but I don't want things to be weird aaaaand.....why don't you two discuss it?''

Hayley looks puzzled.  ``But I do have my own bed.''

Signe interprets, ``I think he just means, if you wanted to stay.  With us.  Because you stayed with me before.  But you don't have to.''

``Would you like me to?'' asks Hayley, surprised, but pleased.

``Of course!'' says Signe.

``I need to ask permission for that,'' says Hayley.  She leaves and goes back to her bunk to look for Jaya.



Jaya is lying down with a pillow over her head.  

Hayley wakes her gently, ``Sir.''

``What?'' grumbles Jaya.

``Sorry sir, but I wanted to ask permission.  Can I stay the night with Signe?''

Jaya pulls the pillow from her face, and says more favorably, ``What??  Yeah!  Do you- do you need the bunk?''

``Oh no, I'll stay with her,'' says Hayley.

``Yeah, it's cool,'' says Jaya and puts the pillow back over her head.





\textbf{\hl{Trenton's Room- Hayley, Signe and Trenton}}\footnote{\textbf{Nathaniel Ford }Jonah gets any of this from Signe's perspective that he chooses to observe. She has no filter, but her connection is not particularly pushy.

One thing this IS apparent regardless is that Signe is incredibly physically aware of her body. Sensations are very strong. Lack of touch is disconcerting to her. \textsubscript{12/25/14 11:40am}}



Hayley returns to Trenton's room.  She and Signe chatter away excitedly to each other, mostly ignoring Trenton, though neither of them ask him to leave or try to prevent him from hearing anything they are saying.  Once or twice Trenton offers to leave, but Signe gets very agitated and both she and Hayley ask him to stay.  



Hayley asks Signe what happened to her.  Signe just says that Octavius tried to ``take her'' and defers to Trenton to explain what really happened.  Hayley doesn't press for details once Signe assures her that it is a lot better now that Jonah is there.  Signe admits it was very exhausting and loud.  She says that she tried to remember all the things that Trenton and Hayley told her, but it was hard.



Hayley is concerned about Signe's lengthy inactivity and leads her through some muscle strengthening exercises.  Signe plays along but to anyone else, she is clearly indulging Hayley and not taking it super seriously.



After that, Hayley changes into her nightgown and brushes Signe's hair and braids it prettily.  Signe pulls both Hayley and Trenton into bed with her, much like a kid gathering up her stuffed animals before bed.



Hayley lies next to Signe (she's on one side of Signe, and Trenton on the other) and tells Signe about her wonderful five days with Drake.  She is super excited and goes into graphic and excruciating detail about everything (sex and rainbows alike), not caring if Trenton hears any of it.  Signe is a rapt audience and asks many questions about everything and Hayley is more than happy to answer them, although Hayley carefully avoids any mention of details related to her mission.  Signe seems genuinely happy for Hayley.



Trenton is uncharacteristically quiet and stays in the background, not doing anything to distract them.  He eventually seems to relax and even participates in the conversation in a frank and nonchalant way, if he is brought in (usually by Signe).   His lack of bluster makes Hayley less wary of him and she relaxes too.



After they have talked themselves hoarse, they go to sleep.  Hayley doesn't sleep well, though when Signe curls up next to her, she does eventually drift off a bit.  But being so well rested from last night and a little keyed up from recounting her time with Drake, Hayley is restless and keeps startling awake at the slightest noise, reaching for her rifle anxiously.  At some point, Signe slips away from Hayley and has sex with Trenton.  Hayley lies awake during this, watching and listening carefully.  She is alert for any sign that \hl{Signe is not enjoying herself}\footnote{\textbf{Nathaniel Ford }Jonah would know, if he checks in, that she is immensely. She feels very safe here, and more than a little desperate for the physical connection. There is an element of needing to get enough of Trenton before letting him go away for a bit.

If Jonah looks pretty closely at Trenton, there is a bit of Trenton knowing he's 'on stage', but the act of looking would be fairly intense. \textsubscript{12/25/14 12:20pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Hayley watching, Jonah watching, both Geirhauser girls and their close circuit cameras watching, Rook watching with his Praetor-ness... no wonder Trenton's a little ``on stage''... \textsubscript{01/02/15 11:11pm}}\footnote{$\rightarrow$\textbf{Suko T }Don't forget Carruthers! :) \textsubscript{01/02/15 11:24pm}}, but says nothing to interrupt them.  Watching them, the whole thing actually seems to reassure/comfort Hayley in some odd way.  When they are done, Signe kicks Trenton out to go do lab work and curls up with Hayley again.  With Trenton gone and Signe next to her, Hayley finally slips into a deep, truly restful sleep.




\sceneHeadline{Train platform}

The next morning, we get an elaborate breakfast.  Hayley's not there to wake Jaya up, so Jaya is late to breakfast.  Afterward we all suit up. 



They are told that there has been a lot of trouble in the Directorate and in particular Jonah's old neighborhood in the Bucket has been hit extra hard.  They don't describe the attacks but say that the Directorate is \hl{holding its own}\footnote{\textbf{Nathaniel Ford }For Jonah as a veteran, and Jaya with scraps of Oliver's attitude, this description is equivalent to ``We are getting our ass handed to us, lots of people are dying but maybe we'll pull through if we don't let our morale flag too much.'' \textsubscript{12/25/14 11:42am}}.

Sakhander is relieved that he's not there but conflicted to know his friends may all be dead.

Carruthers can hear Hayley muttering annoyedly in her head that they should have gone to Bonventure.



Morgan meets us all on the Ready Line.  Javier is with us, but Lackovich and Carruthers are not there.

Morgan addresses Jaya, ``We've got Lackovich and Carruthers on your shoulders.  You know what to do right?  Find the Beacon and activate it.''

``Yeah, we're good!  We're going fucking rock this mission.'' says Jaya, a bit half-heartedly as she looks at her tiny team.

``I'm confident you will,'' says Morgan.  ``Important to know: probably only you and/or Hayley, Javier and/or Rook will be able to activate the Beacon.  Just based on the biometrics that we are reading off of your implants.  Agents are somewhat better equipped for this sort of thing.''``Duly noted,'' says Jaya. 

``Also, keep your calm.  This is an extremely... opaque area.  As I believe we mentioned.  I would prefer not to see combat arise, if it is not needed.  We have a backup train prepared if you need extraction.  But again, given the opacity of the situation, don't count on it.  I would rather you guys pull out and try again later then for this to go really south.  Are we clear?''

``Yes sir,'' says Hayley promptly.

``Yes sir,'' says Jonah and Javier.

Morgan looks at Jaya.  Jaya says slowly, ``Yessss, ma'am sir.''

Morgan pulls Jaya aside and says to her quietly, ``You can trust Rook.  I know trust can be a difficult thing from time to time but just remember that.  I have a lot of faith in you and your ability to complete this mission.''

Jaya looks very serious as she says, ``Thank you, Sir Ma'am. Agent.''

Morgan smiles, ``I wasn't lying about the thing I said earlier.''

Jaya looks panicked and stuttered, ``Don't- I never-um, yes ma'am....''  Lackovich gets an abbreviated version of the Jaya-Morgan scene, or at least Jaya's interpretation of it.

``I look forward to seeing your team return in one piece, Comrade'' says Morgan.\footnote{\textbf{Nathaniel Ford }I'd like to make a small retcon here and append, ``Comrade'' to the end. If people are cool with this. \textsubscript{12/25/14 11:45am}}\footnote{$\rightarrow$\textbf{Rebecca S. }It'd weaken Jaya's response from ``firmly'' to perhaps ``waveringly'' or ``startled'' but I'm happy to +1 such a fun retcon \textsubscript{12/30/14 8:38pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Wolves are so cuddly. \textsubscript{12/30/14 9:09pm}}

``We'll be back!'' says Jaya firmly.



We board the train.



Jaya asks Rook if she can try the plate again.  

``Maybe another time,'' says Rook. 

``Right!  Right let's strategize people!'' says Jaya loudly.

Rook returns to the cockpit.

Hayley leans forward and says to Jaya, ``So Agent Javier and myself first, and then two beats and then you will follow?''

``Yes!  Yes.  That's exactly what I was thinking,'' blusters Jaya.  ``Lackovich must have passed that along to Carruthers.''

Hayley nods.

 {\color[RGB]{74,134,232}::Don't do that.::} 

 {\color[RGB]{255,0,0}::Shut up!::} 

 {\color[RGB]{74,134,232}::Just don't say I'm doing things that I'm not.::} 

 {\color[RGB]{255,0,0}::Shutupshutup!::} 



The train starts moving and we feel that familiar wave of nausea.  Then sometime later, another, stronger wave of nausea.  Then another one.  Then another one.  



Jaya puts her hand on her stomach.



There is a long stretch of time and then over the intercom, Rook says, ``You ready?  Get hot.''

We all get ready.  

``Remember, we're supposed to avoid combat and avoid dying.  So let's make sure we do things in that order,'' \hl{exhorts Jaya}\footnote{\textbf{Rebecca S. }what?! What?! I have no memory of saying that... \textsubscript{12/25/14 1:01pm}}\footnote{$\rightarrow$\textbf{Suko T }Jaya was being super leader-y!  Must be Lackovich's influence :D \textsubscript{12/25/14 4:37pm}}.



There is one last wave of nausea, and then we are in a tunnel, with the occasional light going by.  



Then all hell breaks loose.  There is an explosion and the sound of grinding metal and flashing lights  We are all thrown down to the floor.  Through the din we hear Rook say very calmly, ``Brace for impact.''



There is a grinding, metal-screaming crash.






\jumpHeadline{Quotes: }

Ion: Does she ever pay attention to what {[}Jonah{]} is reading?

Rebecca: No.  There is a box.  No, she can't even visualize a box.  But if she \textit{could} visualize a box, the Jonah part would be inside of it and there would be heavy things on top of it.  But she can't visualize that.  It's too complicated.

Nate: I think the point is you see pregnancy books in the room and he's asking if you'd notice.

Rebecca: She sees the pictures of pregnant ladies and assumes it's his wank material.



Suko: But you have a friend!  Isn't that wonderful?  Why are you crying?



Morgan: As her sister, and as an \textit{unholy bitch}, if you \textit{ever} disrespect her again, publicly, privately.... or even in the dark recesses of your mind...my response is going to be.... disproportionate.



Ion: Does {[}Jaya{]} know what Morgan was talking about?

Rebecca: No!  But she doesn't like Dr. G so of course she thinks horrible things about her in the recesses of her mind.  And clearly Morgan can read her thoughts.  That passing comment about Oliver in no way made any impression on Jaya's brain.



Rebecca: We would like to highlight...because {[}Jonah{]} is a paranoid bastard, that it might occur to him that this book could be a passive aggressive note from Dr. Gerhauser to Jonah, letting him know that he fucked Carruthers and now-

Suko: He's a baby daddy!



Dr. G: Dear Hayley, what do you have for me today?

Hayley: I want to share with you that... the \textit{very} last, the very last memory that he held onto the longest-

Dr. G: Stop.  Absolutely stop.  \textit{Leave}.



Jaya: Fuck you!  I can fantasize about big birds!



Nate: And there is a crash.

Rebecca and Suko in happy chorus: YAYYYYY!!!!


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to understand footnote <3, too many options & none that matched \footnote{$\rightarrow$\textbf{Suko T }<3 \textsubscript{02/11/15 10:34am}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }<3 \textsubscript{02/11/15 10:34am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }<3 \textsubscript{02/11/15 11:27am}}\footnote{\textbf{Suko T }<3 \textsubscript{12/24/14 3:03am}}\footnote{\textbf{Suko T }<3 \textsubscript{12/23/14 11:40pm}} 

	Unable to highlight for footnote: I love this contrast between Lackovich and Jaya's way of dealing with their squads :) because:GivenExpectedJaya looks at her squad and asks with a touch of confusion, So... whatre you guys doing?Jaya looks at her squad and asks, So, whatre you guys doing?

	Unable to highlight for footnote: Iiiiiiiiinteresting!, unable to correctly match (exceeded acceptable limit):ExpectedIt is not that you dont know anything about it, its that your people chose to eschew it for religious reasons.

	Unable to highlight for footnote: No confidence issues with this gal :D  Go Dr. G! because:GivenExpectedAnd I trust in my judgement.And I trust that judgement.

	Unable to highlight for footnote: It somewhat surprises me to say it, but Jonah is really making a pile o' valid remarks in this conversation., unable to correctly match (exceeded acceptable limit):ExpectedChoice again.  Did I have a choice?

	Unable to highlight for footnote: New crazy fan theory!!! - sweet lovable Swan  is actually a deep cover Octavian spy who has been slowly working to alter Hayley's mind so she can be Operated like Signe by Octavious.  (which would make Morgan's recommendations that she train against our security staff a Very Bad Idea)  Luckily Rook will uncover the plot Just In Time and save us all!  (or not... in which case PG1 will have to put Hayley down like the lovable family pet that has contracted rabies and is trying to kill everyone....), unable to correctly match (exceeded acceptable limit):ExpectedBut my eyes were closed, so actually maybe he did.
Swan looks even paler at this

	Unable to understand footnote +1, too many options & none that matched \footnote{\textbf{Rebecca S. }New crazy fan theory!!! - sweet lovable Swan is actually a deep cover Octavian spy who has been slowly working to alter Hayley's mind so she can be Operated like Signe by Octavious. (which would make Morgan's recommendations that she train against our security staff a Very Bad Idea) Luckily Rook will uncover the plot Just In Time and save us all! (or not... in which case PG1 will have to put Hayley down like the lovable family pet that has contracted rabies and is trying to kill everyone....) \textsubscript{12/25/14 10:04am}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{02/26/15 11:16am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{12/25/14 4:34pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{12/25/14 4:27pm}} 

	Unable to find a matching comment for footnote: QUOTE: Nathaniel Ford12/30/2014 11:52 PM
I can't comment.

	Unable to highlight for footnote: I'd like to make a small retcon here and append, "Comrade" to the end. If people are cool with this. because:GivenExpectedI look forward to seeing your team return in one piece, Comrade says Morgan.I look forward to seeing your team return in one piece, says Morgan.


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:49pm
\end{flushright}

