\setcounter{chapter}{ 3 }
\chapter{\textbf{Cardoza Station, Part 2} }


\subChapterTitle{``Ire of the Orc of Anglia''} 

\deets{Rebecca}{July 24, 2012}

\noindent\hrulefill





Other Dudes:  Citizen Cyril Magnin: He is pro-Directorate and isolationist, believes Directorate should not have gone to war with Nicklepan or be allied with Anglia.



Our Dudes: Oliver Langdon, Jonah Gemayel, Jaya Parvadi, Hayley.



\begin{itemize}
\item OMG - The doorbell is about to be rung ... RANG! Jonah nearly flubs it, but Jaya \& Jonah bully themselves through the front door.
\item Oliver, lookin' for power cables. Spots the 3B Trunk line on the north side of this building here and a 130 power gauge coupling there.  TA business to investigate them.  Talks to a burned face man working for the power repair about how to find them.  This leads Oliver to climbing a fire escape.  As he glances over his shoulder and spots buddy Roger watching him.  Oliver flashes the TA patch and all is cool. 
\item TA Team 6 approaches!   Jaya and Hayley and Oliver chat briefly on the walkie-talkie.  Hayley is ordered to avoid detection and to enter the premises. 
\item Jonah interviews Ruth (the maid) an odd lady.  (Incorporated, MMDVI company, whole life.) Talk about recent guests of Cyril Magnin's.  A recent dinner party was composed of DeVries, John Bay (and escort), Lady Potter (and escort), and Sutter (unescorted).  Ruth is usually the only person there, but for parties they hire extra help.  There was a new staff member, Rowan.
\item Hayley sees some locked doors and trash cans.  She *totally* ninja climbs up the wall all quiet like!  She is not spotted as TA Team 6 passes by the alley.  Whoo! 
\item Oliver is on the roof, peeping in people's windows with his rifle.  He sees a dude running across the rooftops toward Cyril Magnin's house!  He tries to radio in.
\item Jaya thinks creeping up stairs is super easy... turns out not so much.  Steps on squeaky floorboard, swears, and has a gun pulled on her!   {[}\textbf{Flaw 1: Flat Footed (Jaya)}{]} {[}\textit{5 threat tokens enter pool}.{]}   Him: ``Don't move!''  Jaya: ``TRANSIT AUTHORITY! DROP THE GUN!''    Gunfire is exchanged! It's totally intense!  Jaya gets a dramatic flesh wound and that just spurs her on- she sprints down the hall and bludgeons the fellow.  YEAH!  Oops! Gotta' reload the gun.... 
\item Hayley tumbles into the house and onto Jonah.  Oops!   They collapse in a heap.
\item \hl{The Orc of Anglia! introduced!  {[}\textit{10 threat tokens enter pool}.{]} }\footnote{\textbf{Nathaniel Ford }So few tokens. \textsubscript{01/07/15 10:45am}} Oliver tries to shoot the roof rat and gets a solid shot and knocks 'im back on a deck!  {[}\textbf{Flaw 3: Ire of the Orc of Anglia (Oliver)}{]}. Buuuuut there was body armour...  Oh shit! It turns out that it was the same guy on the street that gave him directions! Burn Face Man!  In retaliation Burn Face Man chucks a grenade at him - dramatic shit goes down!  KAPOW! EXPLODE! 
\item Injured bodyguard/thug tries to knife Jonah!  Jonah gets a leg wound but Hayley stomps on bad man's leg to deflect most of the blow.  Ouch!  {[}\textbf{Flaw 1: Leg wound (Jonah)}{]}.
\item Jaya kicks down the door and she and Hayley run through the room.  They see a secret stairway that had been hidden behind a bookshelf and head straight for it.  Jonah follows at a slower pace, hampered by his wounded leg.   He pauses long enough to give the room a quick once over and steals some books/papers covered with notations and equations on his way through the room.  
\item Oliver, still outside, starts firing wildly at Burn Face Man.  This is ineffective and attracts Team 6's attention.  They shoot at him \& the Orc for a bit.  Oliver shouts out something effective and military like (\textit{Reputation: Veteran}) and convinces them to shoot the other dood. 
\item Jaya and Hayley reach the bottom of the stairs where there is a steel door.  Hayley flings herself at the door and batters it open, earning herself a {[}\textbf{Flaw 1: Torn shoulder ligament (Hayley)}{]}.  They run for a while down an old tunnel, following the footsteps of their quarry.  
\item Oliver fails to save some folks (2 TA agents and Ruth the maid) from being shot by the Orc because his gun jams (shit happens) {[}\textit{Refresh: Sniper Rifle}{]}.
\item Jaya and Hayley run.  There's another door, but they don't let that stop them.  Jaya orders Hayley to open the door - it's effective! (and painful for one of them).  What's a wrenched back when you're in hot pursuit?  {[}\textbf{Flaw 1: Torn shoulder ligament -\textgreater  Flaw 2: Strained back (Hayley)}{]}  They run some more!  Through some... sand?  Odd terrain?  It is grey and soft like snow (but not cold) and crunches slightly underfoot.
\item Orc goes through the skylight, some Team 6 dudes follow him into the building. Oliver chats with Jonah about the weather.  He bugs out of his crow's nest and heads into the building.
\item Jonah goes through the door that Hayley and Jaya just busted through...  but is a little surprised by the ``Dead People Here'' sigil on the door.  It is a sigil that is often found on gravestones for the rare time that people are buried.  It means ``Primus''?  So distracting!  He is not so distracted he doesn't take a small sample of the odd substance they are running through. 
\item Eshkani is fairly seriously hurt, with a gaping gut wound.  Oliver just breezes by him ``Buck up, Eshkani, it's not so bad!'' -- ``Fuck you, Brown Bagger!'' he says back.  He seems furious that he's being left behind but Oliver is hardened to this sort of thing and doesn't have time to help.
\item Jaya shoots the running person!  But unfortunately he shoots back. Bloody times... Jaya gets a {[}\textbf{Flaw 2: Head wound (Jaya)}{]}.  Hayley just strains herself *even more* {[}\textbf{Flaw 2: Strained back -\textgreater  Flaw 3: Slipped disc (Hayley)}{]}.
\item Oliver is in the house -- the house of BLOOD!  Sees ``Plain Jane'' on the stairs.  ``Useless'' Oliver mutters after the wounded woman gives no intel.   He creeps up the steps...  Rupley is dead up the steps, hand on his throat.  The house is a mess!  Decker is at the top of the secret stairway... he's still alive, but is kinda froze up.  ``My whole squad is down there'', Oliver says.  ``Your whole squad is dead!'' replies Decker.  ``Not them too!'' says Oliver mostly to himself.  Down the stairs he goes! bum Bum BUM!!
\item Jonah gives Jaya drugs and a really big bandaid.  She feels awesome {[}\textbf{Flaw 2: Head wound -\textgreater  Flaw 1: Head wound (Jaya)}{]}.  Hayley starts crying because he's getting away!  Jonah isn't as effective with her, grumbles about being out of stims....
\item Oliver slinks through the dark tunnels...  His radio crackles with Jaya's voice ``Longjohn! ... Train!  ...''  He turns off the the radio, looks around, and turns it back on: ``How. Do. I. Find. You?''  Then there's a raspy voice down the tunnel  ``I'm right here''.  This is Not Good.  Oliver drops to the ground (switches off the radio and flashlight) and starts to army crawl towards the voice.  Mr. Orc chuckles softly. Oliver inches towards the wall... he thinks. ``Where's he going?'' asks the Orc.  Oliver declines to respond, not wanting to give away his position.  After a moment the voice says ``Ah well...  I'm going to make this long and painful.  You have 60 seconds.'' Oliver hears something thud to the ground and sees slight ripples in the water.  There's some ominous beeping.  He gets the hell out of there -- and manages to stagger through the door that he just came out of before the bomb goes off.  
\item Cyril is headed toward a train station, we can hear a train arriving.  We are on the tracks, and can't see anything that is happening on the train platform (and vice versa).  Jaya runs off nearly on her own after Cyril.  Jonah gets Hayley to her feet but she staggers and trips and can't make it onto the train before it leaves.  Jonah makes it onto the train.
\item Jaya and Jonah confront Cyril, who is at the train's front driving it faster.  He has a small box (mechanical device) slung around his neck and is holding a cylindrical steel device.  Jaya tell him to surrender and give up his bomb.  Cyril laughs at them and mocks their ignorance.  There is no bomb he says.  They used ``bomb'' as a way of talking about what they (they?) really have, which is a ... ``camera'' (whatever that is).  They were going to cause massive change, very quickly, like a bomb.  Cyril rants for some time about how the device will show the ``truth about Anglia, not the 'proxy Anglia', the 'real Anglia'''.  Which is not the place where we think everyone is being sent.  Jonah, morbidly curious, tries to find out what ``real Anglia'' means, and learns only that Cyril thinks the Anglia is keeping ``our people'' prisoner in the real Anglia.  Jonah is confused by this and thinks Cyril is working for Anglia, which Cyril denies furiously.  Jonah tries, unsuccessfully,  to convince him that the team also has a bomb which will blow up if they can't stop him.  {[}\textbf{Flaw 1: Burning Curiosity (Jonah)}{]}  Jaya distracts Cyril.   Jonah mans up and shoots Cyril.  Cyril attempts to slam the cylindrical device to the ground but Jaya throws her baton at Cyril and prevents him from doing that.  She knocks it out of his hand, and while he scrambles to get it, Jonah tackles him and zipties him. Jaya slows the train down but not in time for Jonah to treat Cyril and he bleeds out.   Jonah passes the cylindrical device to Jaya and says ``here is the bomb''.  Jonah is an ASS and he steals the ``camera'' portion of the devices, and Jaya doesn't notice although she senses something is up.  The end.  Mission successful!
\item Debriefing!  Jaya has a bandaged head and Hayley has a sexy steel corset.  Everyone gathers in the ops room the next day.    Morgan shows us pictures of Rupley, Ruth, Cyril Magnin and the bodyguard.  ``4 dead'' she says.  She shows us pictures of two more TA agents, Eshkani and ``Plain Jane'' Lackovich and adds, ``and 2 wounded''.  She shows us more slides with numbers.  ``And considerable damages and delays to the trains due to your actions.''  She grudgingly concedes that the mission was successful, but she says it was ``loud''.  
\item Oliver reports the person whom we know OOC as the Orc of Anglia.  Turns out the guy has worked for Anglia 10 years ago!  His face in the photo Morgan displays is very badly burned.  Buuuuurn victim, Krueger style.  Oliver thinks it is the same guy, although it was hard to tell as he had a pitmask on when Oliver met him.  The Orc does dirty work for Anglia and is very skilled. Don't tangle with him!
\item Oliver challenges Morgan about the lack of accurate information and the claim that the mission was ``loud''.  He not so politely points out that keeping it quiet when the mission out was rushed there was a rival TA group that we weren't coordinated with (this seems to particularly anger Oliver), and a random unstoppable goon out of nowhere was also running interference.  {[}Note: Oliver doesn't explicitly say that most of the deaths weren't because of our team.  Actually nearly all of them were the Orc.  We only got Cyril and his bodyguard.{]}  {[}Adam's note: Oliver was basically saying, three groups were here with roughly the same objective and they mostly ended up killing and wounding each other due to lack of communication/coordination.{]}
\item OMG, Oliver just walked out on Morgan! *That's* going to go well...  
\item Jonah asks about the device and whether it was the bomb.  Turns out it is a beacon (which all trains have apparently).  It was not a bomb.  Morgan lectures us that she does not have unlimited resources and that she has to go with what she has.  She admits that she doesn't always have very good information.  She also says that, in the future, we may get more autonomy over how we run our missions.  This is the first sign she's given our group that she has any confidence in us at all.
\item Jaya starts talking to Morgan about why the other TA patrol group was there and how to prevent that in the future.  Jonah interrupts her which earns him a dressing down from Jaya later on.  Morgan says that the other patrol group was sent by a senator.
\item Morgan mentions volunteering for some experimental research-y... stuff.  She directs this to Jaya and Jonah saying she assumes Oliver won't want to, which she seems to think is a shame.  She doesn't include Hayley, presumably because she specifically states that the volunteering is for those who ``are legally able'', which as an Incorporated, Hayley is not.
\end{itemize}



BTW - Mention something about buying skills?   Nate did! It's awesome! Kinda' like 2 for 1!



{[}Rules modification: All point spent on skills will be matched by equal points for the group stash.  This allows us to grow the common pool of useful devices and perks, and helps compensate for the pain point of being separated and being out of skills.{]}



\underline{  {\LARGE Challenges }  }



- Notice challenges: 1x3.  Failed.

- Let Us IN!: 2.  \textit{Grim Visage: 2} (Jaya).  Matched. 

- Find some power cable locations: 2.  \textit{Outgoing: 2} (Oliver). Matched. 

- Not be tattled on by Roger: 1.  \textit{TA Uniform: 1} (Oliver). Matched.

- Noise Detection Challenge: 1. Failed.

- Ninja window climb: 3.  \textit{Dancer: 1 }(Hayley)\textit{, Uniform: 1} (Hayley)\textit{, Athletics: 2 }(Hayley). Matched.

- Notice challenge: 1.  \textit{Sniper rifle: 2} (Oliver). \textbf{ {\color[RGB]{0,0,255}Overcome: 1 VP (Oliver).} }

- Creeping challenge!: 2.  \textbf{ {\color[RGB]{255,0,0}Flaw: Flat Footed: -1 (Jaya). } }Failed.

- Bodyguard Man!: 3.  \textit{Adrenaline Junkie: 1} (Jaya)\textit{, Truncheon: 1} (Jaya)\textit{, Sidearms: 2} (Jaya). \textbf{ {\color[RGB]{0,0,255}Overcome: 3 VP (Jaya).} }

- Shoot the roof rat!: 3.  \textit{Crackshot: 3} (Oliver), \textbf{ {\color[RGB]{255,0,0}Flaw: Ire of the Orc of Anglia: -3 (Oliver). } }\textbf{ {\color[RGB]{0,0,255}Overcome: 3 VP (Oliver).} }

- Grenade headed your way!: 2.  \textit{Hardened: 2} (Oliver). Matched.

- Knife in the gut from a wounded man!: 2.  \textit{Bodyguard: 1} (Hayley), \textbf{ {\color[RGB]{255,0,0}Flaw: Knife wound: -1 (Jonah)} }. Matched. 

- Kick down the door all dramatic like!: 1. \textit{Outfit: 1} (Jaya). Matched.

- Shoot the other dude!: 2.  \textit{Veteran: 2} (Oliver). Matched. 

- Open the damn door: 1.  \textbf{ {\color[RGB]{255,0,0}Flaw: Torn shoulder ligament: -1 (Hayley)} }. Matched. 

- Open the other door!: 2.  \textit{Conditioning: 2} (Hayley). Matched. 

- Where are you, Jonah?: 2.  Failed.

- What's that sigil there?: 1. \textit{Street Medic: 2} (Jonah). \textbf{ {\color[RGB]{0,0,255}Overcome: 1 VP (Jonah).} }

- Run faster!: 1 x 2.  \textit{Dancer: 1} (Hayley), \textbf{ {\color[RGB]{255,0,0}Flaw: Torn shoulder ligament: 1 (Hayley)} } -\textgreater  \textbf{ {\color[RGB]{255,0,0}Flaw: Strained back: -2 (Hayley)} }, \textit{Team Leader: 1} (Jaya). Matched.

- Hit the moving target!: 3.  \textit{Sidearms: 3} (Jaya). Matched. 

- Don't get hit!: 3.  \textbf{ {\color[RGB]{255,0,0}Flaw: Strained back: 2 (Hayley)} } -\textgreater  \textbf{ {\color[RGB]{255,0,0}Flaw: Slipped disk (Hayley)} },  \textbf{ {\color[RGB]{255,0,0}Flaw: Fucked up face: 2 (Jaya)} }. Matched. 

- Escape the bomb!: 2.  \textit{Arm Strength: 1} (Oliver).  Failed.

- Shooting Cyril Magnin and preventing him from setting off the ``bomb'': 2. \textit{Vigilant: 2} (Jonah), \textit{Small Arms: 1} (Jonah), \textbf{ {\color[RGB]{255,0,0} Flaw: Burning curiosity: -1 (Jonah)} }.  \textbf{ {\color[RGB]{0,0,255}Overcome: 2 VP (Jonah)} }\textbf{.}

- Don't blow up the maybe bomb?: 3.  \textit{Truncheon: 1} (Jaya). Failed. 

- Don't let Jonah steal TA evidence: 1.  \textit{No appropriate skill} (Jaya).  Failed.



\underline{  {\LARGE Refreshes }  }



- Jonah acted retarded at the front gate - refreshes Social Chameleon.

- Oliver meets his buddy Roger - refreshes Citizen.

- Hayley creates a pile of constables in the hallway - refreshes Dancer.

- Jaya reloads the gun - refreshes Sidearms.

- Oliver fires wildly at the building - refreshes Crackshot.

- Oliver fails to shoot the Orc due to a gun jamming - refreshes Sniper Rifle.

- Jonah is confused about where he is - refreshes Streetwise.

- Jonah is distracted by all the dead people dust - refreshes Medic.

- Oliver says something jerk-face to the injured guy - refreshes Veteran. (or was it Hardened?)

- Hayley starts crying! - refreshes Conditioned.

- Jonah fails to help Hayley the first time - refreshes Medic.

- Jaya fumbles with the truncheon - refresh Truncheon. 

- Hayley trips and stumbles on the way to the train - refreshes Athletic.



\underline{  {\LARGE Quotes }  }



``Agent! Morgan! Agent! Morgan!''

\extraIndent{- Running mantra}



``Oh he looks like a thug?  Why didn't you say so?  It's okay then.''

\extraIndent{- Rebecca, relieved to have someone it's clearly okay to beat up.
}

\quotedDialog{
``You get to the door before he can lock it''

``Good, because I only had two shoulders''
}
\extraIndent{- Nate and Suko, referring to Hayley's accumulating injuries going through the last two doors.}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/22/15 1:10pm
\end{flushright}
