\setcounter{chapter}{ 39 }
\chapter{\textbf{``The Beacon, part 1''} }

\subChapterTitle{\hl{``Derailed''}
\footnote{\textbf{Suko T }https://www.youtube.com/watch?v=pL4eIpRYet0\#t=142 \textsubscript{02/23/15 2:21am}}}

\deets{Suko}{Feb 11th,  2015}



Rook didn't die.  And some other stuff happened.



More visions from other-us in DC.  Our train is messed up and off the track.  We shoot some spider-like things that try to steal parts of our wrecked train.  We meet Leibowitz and find out about his Monastery.  He promises to help us get our train back onto another track (with a hill) and tells us that if we are interested in the Beacon we have to see someone.  We ask him to introduce us and we walk for a while through this mist and fog enshrouded world.  There are a lot of hills and weird little robot-creatures everywhere (autos).  We eventually get to a large gate and are granted an audience. On the other side of the gate, we meet the King in Yellow.





\noindent\hrulefill




\sceneHeadline{Our Gear}

Jaya

Transit Authority MOPP Battle Dress Uniform (3)

Vacuum-sealed Infantry Heavy Combat Armor (4) 

AMP (Automated Medical Pack) (3)

Hush Radio (1)

\textbf{2x} Gauss Pistol (2) (pistol and extra ammo)

HE Grenades (2)

Alloy Cannon (3)

Rangefinder Binoculars (2)

Heads-up Display (4)



Jonah

Transit Authority Battle Dress Uniform (2)

Vacuum-sealed Infantry Light Combat Armor (3)

HESP Radio (2)

\textbf{2x} Gauss Pistol (2) (pistol and extra ammo)

HE Grenades (2)

Heavy Pulse Rifle (3)

Electronic Bypass Kit (3)

Heads-up Display (4)



Hayley

Transit Authority Battle Dress Uniform (2)

Vacuum-sealed Infantry Light Combat Armor (3)

AMP (Automated Medical Pack) (3)

Hush Radio (1)

Gauss Pistol (2)

HE Grenades (2)

\textbf{2x} Heavy Pulse Rifle (3) (rifle and extra ammo)

Hand Arc Welder (2)

Heads-up Display (4)





\textbf{{[}6 Tokens in the pool{]}}



Rook says calmly, ``Brace for impact'' and there is a terrible crash.  Time seems to slow down and we all feel very alert and alive as we get that ``I'm about to die oh shit what is going on?'' surge of adrenaline.  We can hear things crashing into the outside of the train. There is the horrible sound of screeching and crunching metal. The whole train shakes and we all have to grab something to catch our balance.  Jaya, Jonah and Javier manage to grab ahold of something but Hayley gets a little tangled up in her rifle and is knocked off her feet.



A jagged metal claw, like a giant can opener, starts ripping the side of the train open.  Jaya shouts, ``Down!'' and lunges to the side of the train away from the claw.  {[}\textit{Challenge 2: Don't get caught by claw. Air of Command 3 (Jaya) → Overcome! }\textit{\textbf{2 VP (Jaya)}}{]}.{]}.  Javier hears Jaya and also dives out of the way.  With all his war-trained reflexes, Jonah manages to evade the shards of metal flying toward him from the damaged train wall {[}\textit{Challenge 1: Avoid shrapnel. Trigger Reflex 2 (Jonah) → Overcome! }\textit{\textbf{1 VP (Jonah)}}{]}{]}.



The train goes in one direction and then reverses suddenly.  Hayley flies past Jaya, missing her by scant centimeters and collides with the far wall with a sickening crunch of equipment.  The claw snaps and goes ricocheting inside the train.  The train flips up and starts to spin.  Hayley gets bounced around.  Jaya and Jonah are clinging on for dear life.  No one can see where Javier is.  As she hangs on, Jaya gets a rush of burning intensity and instinctively crouches into a defensible position.



The lights are flickering and there are showers of sparks outside.  From the outside there is a burst of diffuse light.  We feel the train flip all the way around laterally and go tumbling. There is no way it is on the tracks now.



Then something weird happens.  For Jaya and Jonah, what happens next is very flickery, for Hayley much less so.




\sceneHeadline{Other-Jonah and Riva}

Jonah gets that starting-to-be familiar sense of dissociation.  He flickers between the associated state where he is tumbling in the train car, and the dissociated state.  In the dissociated state, he is walking up a cement staircase.  Riva is talking to him about something, but he's not really listening to her.  There is a ringing noise in his ears. They reach the top level of what appears to be a parking lot.  The streetlamps are flickering, oddly synchronized to the flickers of lights and sparks in the associated state.



Jonah is disconcerted by the streetlights (\hl{electricity used so casually?}\footnote{\textbf{q.google }Used at all.  He has no concept of street lights.

SAC-09 and some Citizen buildings have lights but those are inside. \textsubscript{02/25/15 3:20pm}}) but is also feeling an overwhelming sense of paranoia.  He looks across the parking lot and see two people next to a car.  One of them is holding a lit cigarette but is not smoking it, and the other one has a dog on a leash.  Not that Jonah knows what a dog is, he just sees some sort of giant furry rat-like creature.  The dog is facing the person who holding its leash and pulling away from them, backing away in Jonah's direction.



Riva is dressed in a suit, carrying a briefcase. She looks older again.  ``Get down!'' says Jonah urgently and pulls Riva behind a car.  He looks for his gun and finds he is weaponless, dressed in jeans and a button down shirt.  Riva is saying something, but he can't hear her over the ringing in his ears.



He looks back the way he came and beyond the edges of the parking lot is just inky darkness, like there was in the mirror.  He continues to rapidly flicker between the parking lot and the train.  Jonah braces himself against the car like he is holding on.   

He hears Riva very clearly say, ``Timon, what is going on?''

``Those people, who are they?'' ask Jonah.  Riva starts to stand up and Jonah yanks her back down again.

``I didn't see them!'' she protests.

``One of them is smoking and one has a... I don't even know what the hell that is.''

Riva peeks around the car more carefully and says slowly, ``It's a ...dog?''

The ringing is getting very loud.

``What is it doing?''

``It's... that's weird.  It's trying to get away from its owner.''

``Something is wrong.  Is there another way out of here?''

``We can go back the way we came,'' says Riva dubiously.

The idea of doing that doesn't seem to trigger as much feeling of paranoia so Jonah says, ``Okay let's do that.''  As he turns toward the stairs, the ringing gets to a very intense level, which causes Jonah to run even faster for the stairs.  In his mind, when there is a loud noise, you don't stay out in the open.



He snaps back into his associated state and is back on the train.


\sceneHeadline{Other-Jaya and Kali}

Jaya is also alternating between associated and dissociated states as the lights flicker.  If Jaya knew what ``shaky cam'' meant, she would be able to describe how it feels and looks when she is in her dissociated state.  She is running, dragging another person behind her.  It's Kali.  They are both looking ahead of them and there's a huge empty space of...grass?  Even though it's night, she knows that it's green.  There's a large white obelisk in the distance and as she looks over her shoulder she sees a road that cuts across the grass.  On the road there's a car and another car has smashed into it.  Beyond the cars is a large white palace-like building.



It takes a moment but she recognizes two of the figures as the people who came to her house.  They have guns out and are shooting at the car that seems to have smashed into their car.  They are backing away in Jaya's direction and there's shouting.  There are several other people in the area.  One of the other people has a rifle and is shooting at the man and the woman, which means the bullets are also flying in Jaya's direction.



Kali is keeping pace and Jaya has an iron grip on her arm.  Kali is shrieking and Jaya realizes that she is too.  She stops that immediately.  Even though she keeps flashing back and forth between the train and this, she is able to keep running, though she stumbles a bit.  She gets the sense that she's running away from something, rather than running toward a goal.  She pats herself down for her gun, and then part of her wonders ``Why would I have a gun?''  To her disgust, she realizes that she's wearing a dress, the same one she was wearing at the dinner with Padme and Kali.  There is a ringing sound in her ears.



Suddenly there's a woman in front of Jaya.  \hl{Blond}\footnote{\textbf{Suko T }Apparently she looks like Robin Wright. \textsubscript{02/18/15 3:10pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }http://i.telegraph.co.uk/multimedia/archive/02813/Robin-Wright\_2813841b.jpg \textsubscript{02/23/15 2:32am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }http://s3-ec.buzzfed.com/static/enhanced/webdr03/2013/2/27/23/enhanced-buzz-11596-1362024829-0.jpg \textsubscript{02/23/15 2:33am}}, wearing a running outfit, with a bottle of \hl{high end water}\footnote{\textbf{Nathaniel Ford }VOSS to be exact. \textsubscript{02/23/15 2:33am}} in her hand.  There's a weird concerned look on her face and then she looks at Jaya and smiles.  Jaya doesn't like this at all and starts closing with the woman. The woman moves to meet her. Jaya extends her fist, and punches the woman as she moves past her.  The ringing gets very loud.  {[}Spend \textit{Agent (Jaya)} to stay in scene{]}



The woman goes down and Jaya sprints past her, dragging Kali.  The woman gets up and starts chasing after them.  She catches up to them easily as she's in running shoes and Jaya's in a dress.  She tackles Jaya.  Jaya lets go of Kali and they tumble to the ground.  Jaya lunges for the woman's neck and bites down hard.  There is blood everywhere.  The woman is screaming and pulls Jaya's head back and slams it into the ground. There is a flash of pain. The ringing is getting very loud again.



Jaya screams, ``Kali, RUN!''  The blond woman puts her hands around Jaya's neck and starts trying to strangle her.  Jaya tries to gouge the woman's eyes out.  Just as she's starting to lose consciousness, Jaya sees something large-ish come out of nowhere and hit the woman on the back of the head.   The woman's eyes rolls back and she collapses on top of Jaya.



And Jaya is firmly back on the train.


\sceneHeadline{Other-Hayley and Trenton}

Hayley is knocked unconscious.  She wakes up and finds herself rubbing her eyes sleepily.  She feels tired and muzzy-headed.  She can feel cold tile under her feet as she walks across a room.  She sees her hand reach up to flip the deadbolt on a door and open it. 



Trenton is standing there, on what seems to be a back porch.  He's nicely dressed, wearing a blazer and a scarf, and nice shoes.  He does have a baseball cap on though, pulling his hair back..  He's facing away from Hayley and has his hands in his pockets.



He turns to face Hayley and raises an eyebrow.  ``Uh... don't you think you're sending a bit of a mixed message?''

Hayley looks behind herself in puzzlement, wondering if he's talking to someone else.

``I mean, I don't \textit{mind},'' clarifies Trenton.

Hayley looks down at herself.  She's wearing nothing but a t-shirt that is definitely not long enough and some cute lacy panties.  She looks back up at Trenton.  ``Hello, Mr. Hadef,'' she says politely.

``Sorry to catch you at this time.  I just need to borrow your car.''

``My... card?'' asks Hayley in confusion.

``Your \textit{car}.  You know. The Z3?  Convertible top.''

``No...''

``No... I can't?''

``I mean, I don't know what that is,'' explains Hayley.

``You have a weird sense of humor,'' says Trenton.  ``Do you mind-?'' and he starts to walk past Hayley into the apartment. 

Hayley moves out of the way but just stands in the doorway, holding onto the doorknob in confusion.  ``Can I...help you?''

``Yeah!  I need to borrow your car.  I think the police tagged mine.''  Trenton heads to a cupboard in the kitchen and opens it.

Hayley looks alarmed, ``Is Signe in trouble?''

Trenton goes very still.  He turns around and says sharply, ``\textit{What?}''

``Is she- Is she- Has there been another attack?'' worries Hayley.

``Explain yourself.''

``Uh- I uh- don't- what am I supposed to explain?''

``What do you mean by 'another attack'?''

``You know Signe, right?  The attack where she got hurt?'' Vaguely thinking that perhaps something might be wrong, Hayley starts looking around the apartment.  It's very well appointed, tidy and tastefully decorated.  It looks nothing like what she's used to seeing in Terminus.



Trenton takes a step toward Hayley, stops, turns around, pulls a bottle of some brownish liquid out of the cabinet.  He walks up to her and asks, ``Are you on something right now?'' 

Hayley blinks at him as she parses his question and then replies, ``I did start the treatments. But I-''

Before she can finish speaking, Trenton simultaneously shuts the back door behind her and pops the cork from the bottle. He says to her, ``Alright, you need to sit down.  \textit{What treatments?}  What are you talking about?''

Hayley sits down obediently.  She looks up at Trenton.  ``Is Signe alright?'' she asks again.

``Don't joke about that,'' says Trenton sharply.

``I'm sorry.  How is that funny?'' says Hayley, puzzled.

``It's really \textit{not}.  That's the point.''

Getting increasingly worried that he's not answering her question, Hayley stammers, ``I just- I just want to know if she's okay.  There was- was-''

``Hayley I need you to be really really clear with me right now, are you sure you're not on anything?  Are you taking any medication?''

``Yes!  The hormone treatments.''

``What hormone treatments?''

``The ones to make me smarter-'' she corrects herself immediately, ``\textit{wiser}.''  She pouts.  ``Fatter too.  I'm not looking forward to that.''

``Who is giving these to you?''

``Dr. Gerhauser.''

``WHO?''

``Dr. Gerhauser.  Do you not remember?'' asks Hayley.

Trenton is at a loss for words for a moment.

Hayley asks, worried, ``Have you been hit on the head?  I hear that memory can be a problem.  I- I forget a lot of things too.''

There's a distant ringing noise.

With some effort, Trenton holds onto his composure and says very clearly, ``Hayley. I have not been hit on the head.  I need you to think back- what was the last thing you remember?''

``Crashing in the train,'' says Hayley promptly.

``Okay.  So you don't remember the hospital after that?''

``Noooo....?  But usually, sometimes I forget things like that.''  She looks down at herself to check for injuries.

Trenton looks at her intently, and she looks up again when he starts talking.  He says, ``You brought the device back to me.  Right?  The one with the readings?  You made them let you out early?  At my office.  You don't remember that?''

Hayley thinks hard and then remembers something and says brightly, ``No.  Oh!  No, that was Agent Parvadi who brought you the device.''

``Who's Agent Parvadi?'' asks Trenton.  Hayley wonders if she mispronounced the name but before she can repeat it, Trenton says rapidly, ``Nonono, you mean\textit{ Officer} Parvadi?  I've never met her.''  

``Did she get a new title?'' wonders Hayley.

``I don't know.  She's the \hl{mall cop}\footnote{\textbf{Suko T }\textless 3 \textsubscript{02/15/15 1:11am}}\footnote{$\rightarrow$\textbf{Rebecca S. }Fucking Trenton... \textsubscript{02/23/15 8:49am}} or whatever.  Who was hurt with you in the train crash.''

``Oh she was hurt too?'' says Hayley alarmed.  

``Yeah, there were five of you that were severely injured.  There was the one psycho girl who got away, the Major guy who got killed-''

Hayley gasps as she belatedly catches up, ``All of us- \textit{Jonah} got hurt??''

``-Jonah?'' repeats Trenton, not recognizing the name.  ``I don't know the last names.''

``Operator Gemayel,'' says Hayley with a smile.

``There was you, there was Major Langdon-''

``No no no, he \textit{died},'' stresses Hayley.

``Yes, he's dead.  There's the doctor, Natekar,  Timon Natekar.''

``Who?  No.  Not Jonah Gemayel?  Operator.  He's also a doctor. Kind of a strange doctor,'' she adds, more to herself than Trenton.

``Okay who is giving you these hormone treatments?  Who is this Dr. Gerhauser? Give me your phone,'' says Trenton.

``My what?''

``Your phone. Where is your phone?''

``I don't know.  What's a phone?'' asks Hayley, bewildered.



Trenton looks at Hayley for a long moment and then says decisively, ``Alright!  You're coming with me to California. Come on, let's get you dressed.''

``What station is California?'' asks Hayley as she stands up and follows him into the bedroom.

The ringing is getting louder.

``Come on,'' he says, leading her down a hallway.

``Are we going to a station?  Should I put on my uniform?'' asks Hayley as she trails after him.

``Well you should get dressed.  Because as much as I appreciate the show, and I do, the first time we get pulled over for speeding is going to be a problem.''  He walks into a bedroom.  



It's a nice room, luxuriously appointed, definitely a high ranking Citizen woman's room.  There's a queen sized bed, the covers rumpled.  Clearly someone was sleeping in it recently.  There are framed pictures on the walls.  They are photos of many people.  Hayley only recognizes Trenton and Signe, though some of the people feel like they should be familiar.  Only a few of the photos include Hayley and there are none of her by herself.  There is one portrait of Signe, smiling and looking happy and not vacant at all. There are several photos of Signe and Trenton (one where they are holding hands), one of Hayley and Signe, and a couple of all three of them.  There are no pictures of just Trenton and Hayley, though in the pictures of the three of them, all of their physical proximity is very close and comfortable.  The pictures span over several years, in the earlier ones Hayley and Signe look clearly younger, perhaps college-aged.



Trenton opens the closet.  ``Damn this is so organized,'' he says admiringly as he starts pulling out clothing. The closet is full of clothing, stylish, though very little appears to be strictly practical.  Hayley, not knowing what to do, starts making the bed with military tidiness.  That done, she starts looking for her uniforms.  She can't find them. The ringing is getting louder.

Trenton puts a suitcase on the bed and starts piling clothes into it.  He tosses in some black-with-neon-highlights yoga pants, a few skirts and blouses, sports bras, a jacket. It's a fairly haphazard collection mostly centered on 'sporty', but branching towards 'sexed up casual'. 



Trenton picks up something off of the dresser, ``Ah, here's your phone!  I don't know who this Gerhauser is but...'' 

Hayley looks at the phone curiously, ``It's so tiny!  What does it do?''  {[}Spend \textit{Operator (Hayley)} to stay in scene.{]}

Trenton shakes his head.  ``Look, I'm going to go to the bathroom and look for illicit substances.  You get some pretty underwear, and some more pants and I guess some more shirts, and put them in the suitcase.  You can do that right?''

``Am I packing?  Where are we going?'' asks Hayley.

``Yes. California.''

``What station is that?  I haven't heard of it.  Is it past Arc Station?'' asks Hayley curiously.

``Why do you keep calling it a station?  It's a \textit{state}.  It's not a station.''

``What is a state?'' asks Hayley.

Trenton walks over to Hayley, and looks at her in concern, ``Do you mind?  I'm going to check for concussions.''

``I didn't think you were that kind of doctor,'' comments Hayley, but she stands still and lets him check her over.

``Well I've taken a first aid course. And I'm not an idiot. There is Wikipedia, you know.''

``Who is that?''  Something occurs to Hayley and she asks excitedly, ``Is that \hl{Doctor Swan}\footnote{\textbf{Rebecca S. }Wikipedia Swan is kinda' an awesome name.  :D
I don't remember this dialog from the game. Must have been laughing too hard at the time... \textsubscript{02/23/15 8:52am}}'s first name?''

``Who is that?''

``Doctor Swan.  I'm so pleased that he got promoted.''

``Is this that Gerhauser guy?''

``Hmmm??  No. No.  Dr. Gerhauser is a woman.''

Trenton gets an odd look on his face.  ``Where did you meet Dr. Gerhauser?  She's not in your phone.''  He holds up Hayley's phone.  

Hayley looks at the phone in confusion and then says, patiently, ``That would be strange.  It is very tiny.  She's at SAC-09.   Where we are.  Were.''  She looks around and whispers confidingly.  ``I think this is perhaps not SAC-09.''

``No, this is your apartment.''

``I don't have an apartment,'' says Hayley.

Trenton just points at the pictures on the walls.  Hayley looks at the pictures but doesn't get it.  She smiles, ``Oh!  Actually I might.  But not for a year.  Ms. Vorrutyer has been very generous.''

Trenton looks at Hayley intently, ``Where do you think you are right now?''

Hayley says uncertainly, ``I think I am in an apartment?  You said?   Not... California.  I think not probably SAC-09 either.  And I think not Nicklepan either because I didn't see any dead bodies.''

``How do you spell Nicklepan?''

``N.  I.  C.... ummm....uhhh...''

``Okay don't worry about it.''  Trenton checks her forehead.  Hayley waits patiently.  He removes his hand and says, ``Look we can't stay here.  They're probably still looking for me. We have to get going.  But I don't want to leave you in this condition.''

``Did you \textit{run away}?'' asks Hayley, sounding a little scandalized.  ``They'll be so mad!''

``Well they're the FBI. What the fuck do I care?''

``The who?''

``Look get some clothes, put them in the suitcase.  I'm going to go and look for something you might be having an adverse reaction to.''

``This is very confusing.  I'm sorry.'' apologizes Hayley.

``Yeah,'' agrees Trenton and then points to her and orders, ``Pack.'' and he leaves the room.



Hayley starts packing, but is totally befuddled by this modern fashionable clothing.  All these strange fabrics and cuts.  Absently she pulls off her shirt to get dressed and then notices herself in the full length mirror.  She walks over to the mirror and stares at her naked body in fascination.  Her scars are gone, all of them except an unfamiliar small one on her abdomen, very faint and healed some time ago.  Her hair is glossier and looks fabulous.  She's fit, but her overall physique is softer.  She no longer has the sharply defined tone that Hayley has worked so hard to maintain.  \hl{She definitely looks older}\footnote{\textbf{q.google }So does Riva, and Jaya's daughter is older (hard not to be...).

This is the patrol in the future of the past. \textsubscript{02/25/15 3:37pm}}.  However the overall effect is that she looks significantly more attractive and sexier.  Her breasts are fuller and larger, and her whole body is more sensual.  Just looking at herself is a bit of a turn on.  She poses in front of the mirror, examining all the changes curiously.



Trenton walks into the room, stops, and looks away quickly.  When she doesn't cover herself (she pretty much ignores his presence) he turns back and just stares at her openly.  ``Yeah, that's really nice,'' he agrees.  He asks carefully, ``I thought we had this conversation though.  I thought we weren't going to do this anymore...?  I mean, that was \textit{your} request.''

Hayley turns to him, puzzled.  ``Doing what?  Getting dressed?  I thought I was supposed to be getting dressed.''

``But- but you're the... opposite of that?'' says Trenton, his voice a little strained.  He adds quickly, ``Not that I mind!  Not that I mind \textit{at all}.  But we should go.''

Hayley looks back at herself in the mirror and says, ``Is this what she meant by bigger?'' while looking down at her chest and frowning.  ``She said I would get bigger.''

``She who?''

``Dr. Gerhauser.  With the hormone treatments.''

Trenton starts to say something and then gives up and says instead, ``Your breasts are lovely. They don't need to be any bigger.  You don't need any plastic surgery or hormone treatments.''

Hayley disagrees with confidence, still staring at her breasts suspiciously, ``No, they are definitely bigger.  I should know.  I am very familiar with them.''

``Ah...I would say they're about the same size as...\textit{I've} ever known them to be.  Uh-''  He stops and clears his throat.  ``If you say so.  Woman's always right, isn't she?''

Hayley looks at him, surprised.  ``We are?''

``Yes... You are.''

Hayley smiles happily, ``That is nice.  Usually I'm wrong.  I would like to be right.''

Trenton clears his throat again and starts opening some drawers.  He pulls out a fairly sexy bra (to be fair, all of the underwear in the drawer is racy in some way) and tosses it to Hayley.  ``Here, put that on.''  He starts rifling through the rest of her clothes, clearly rejecting some items and tossing others her way.  She gets dressed in these odd things, though it takes a while for her to figure out how to put it all on.  Trenton ends up picking a surprisingly well-coordinated outfit, though it's definitely on the sexy side.  A soft clingy wrap top and while the skirt is calf length, it has a long slit up the side.  Much like her underwear, most of her clothing tends that way.  



As Hayley gets dressed, Trenton's expression is conflicted.  He keeps looking up at her and then dragging his gaze away.

Once dressed, Hayley admires herself in the mirror again.  She says with delight, ``These are nice!  They fit really nicely.''

``I know,'' mutters Trenton.

Hayley chatters excitedly, `` I like these colors better!  I wish we could get my uniforms in this color.  It would look so much better-''

Trenton interrupts, ``We can talk about that in the car!  Why don't we focus on my problems for a while.''

``You have problems?'' asks Hayley, surprised.

``That's why I'm here.  Do you remember where your keys are?''

``My.... access key?''

``Yesss, your access key.  \textit{To your car.}''

``It should be clipped to my uniform. Which I can't find.''

Trenton puts his hands on Hayley's shoulders.  ``Hayley, you don't have a uniform.  Unless you mean some sort of sexy schoolgirl uniform.  In which case we need to talk.  Or not talk.  But.... let's talk about that later.''  He refocuses, ``Alright.  Do you need anything else?''

Hayley looks at him worriedly, ``Did they take them away?''

``Who?''

``Agent Morgan.''

``Who is Agent Morgan?''

``She's my commanding officer.  And she gave me the uniforms.''  Hayley looks alarmed, ``Perhaps crashing the train... made her unhappy so she...took them away.'' Hayley's voice drops to a whisper on the last part.  She looks sad.



Trenton sits Hayley down on the bed and pulls up a chair to sit across from her.  His face is very serious and concerned, ``This is too detailed to be a psychological break.  Especially as this has never happened before.''

\hl{``I haven't broken,'' says Hayley quickly and firmly.  ``I'm just psychosomatic.''}\footnote{\textbf{q.google }QooC \textsubscript{02/25/15 3:40pm}}

``Explain.''

She leans a little closer and says in a confidential whisper, ``It means it's imaginary.''

``So you think this is all imaginary,'' says Trenton, neutrally.

``No.  Just the pain in my leg.  And the fact that I need to go to the Cistern.''

``The Cistern,'' Trenton repeats.

``Yes. Because Oli-Ol- Operator Langdon is there.  I find that comforting.''

``Langdon is dead.'' says Trenton flatly.

``I know,'' Hayley says patiently, not upset.  ``That's where I put my memories of him.  Because I promised him that I would remember him.''  She smiles happily.

``Okay, sit there for a second,'' says Trenton and he picks up her phone.  Hayley peers at the phone curiously, trying to figure out what he is doing.  Trenton scrolls through the various phone histories.  ``Okay you have no Langdon-''

Hayley looks up at Trenton, ``Am I in the Tank?''

The ringing is getting louder.

``The tank?  You're not in a tank.''  Trenton says carefully, slowly, ``You're in your apartment.  Your name is Hayley.  What's my name?''

``Trenton. Hadef.  Citizen.'' says Hayley promptly.

``So you know my name.  And you know Signe.  And then you know a bunch of people who don't exist,'' says Trenton.

``\hl{They don't exist}\footnote{\textbf{q.google }For people who don't exist they are \_awfully\_ opinionated.... \textsubscript{02/25/15 3:41pm}}?''

``Well I've never heard of them and we work together.  And they're not in your phone...  So unless you're a secret spy for the CIA.  Which-'' he shrugs, ``I wouldn't be surprised if they did that, frankly.  'Cause...'' he gestures to himself with a smirk.  ``\hl{But I really doubt it because I'm good.}\footnote{\textbf{q.google }Yeah, that's what they all say. \textsubscript{02/25/15 3:42pm}}  And there's no way-''

``You're very smart!  That's why we kidnapped you,'' interrupts Hayley earnestly.  ``I mean- I don't know if it was really kidnapping.  It was a mission.  So you could help with the math-''

``So you're from SAC-09?'' Trenton asks slowly.

``No.  No!  I'm from Redemarrer.'' 

``Do you know how to spell \textit{that}?''

``Um.  \hl{It has a lot of ``r''s in it}\footnote{\textbf{Rebecca S. }I appreciate that Hayley and I are about on the same level for spelling... \textsubscript{02/23/15 8:58am}},'' offers Hayley.  She continues, ``And then I was sold, and then... I was...  then my contract was transferred to SAC-09 and that's when we came to get you.''

The ringing is getting very loud now.

Hayley looks at Trenton curiously, ``Why don't you know these things?  You're very smart.''

Trenton replies, ``\hl{Because \textit{either}: these things aren't true, or you've had a set of experiences of which I am \textit{completely} unaware}\footnote{\textbf{q.google }If that Trenton is as smart as the ``real'' Trenton, he might actually have a chance in hell of figuring out what's going on. More than the patrol does actually. \textsubscript{02/25/15 3:44pm}}.''

They stare at each other.  After a long pause, Hayley leans forward, her eyes wide, and whispers anxiously, ``Which one is it?

Trenton takes a deep breath and takes Hayley's hands.  ``I need to ask you a question.  And I apologize because I know we said we weren't going to talk about this anymore.''  A very long pause.  The ringing is very loud.  He looks at her intently, and asks, ``Do you remember Signe dying?''



Hayley goes blank for a moment and then so forcibly rejects this idea that \hl{she's thrown back into herself on the train}\footnote{\textbf{q.google }I really, really want to know how the Other Hayley reacts afterwards.  It will be pretty funny.  Plus I wonder if it will get the Other Trenton thinking. \textsubscript{02/25/15 3:46pm}}\footnote{$\rightarrow$\textbf{Suko T }Rebecca and I are pretty sure that other-Trenton's getting slapped or punched by an extremely pissed off other-Hayley. \textsubscript{02/25/15 4:18pm}}.



\textbf{{[}3 Tokens remaining in the pool{]}}


\sceneHeadline{On the Train}

The memories of the events during the dissociated state are more vivid this time, partially because they had been flashing back and forth and having the reinforcement of the details from the previous time does make it a little easier to remember.  But because the train is crashing, it's also hard to hold onto all the details.



The train turns over on its side and seems to slide for a very long time before coming to a halt.  There is a big hole rent in the side (now top) of the train.  The light coming through it is diffuse and a little weird to our eyes.  There are sparks from various electrical things.  Everyone's in a bit of a tangle.  Javier is groaning and cursing.  Hayley is unmoving.  As Jaya and Jonah assess the situation, the train doors slide open incongruously with a ding.



\textbf{{[}``Page in Brown'' activated.  10 tokens enter the pool.{]}}



Jaya leans over Hayley and shakes her.  The combat armor makes this somewhat ineffective so Jaya starts yelling loudly, ``Hayley!  Hayley!''  Hayley doesn't respond.



The cockpit door opens and Rook climbs out.  ``Everyone alright back here?''

``Hayley's not moving!'' says Jaya and she grips Hayley's shoulders to shake her harder.

``Don't move her,'' says Rook calmly.  Jonah repeats the instruction, a little more urgently.  Rook gracefully climbs over to where Jaya and Hayley are.  Jaya is tapping on Hayley's helmet.



``I need you to carefully remove her helmet without moving her body.  In case she suffered spinal damage,'' instructs Rook.  Jaya starts scrabbling at Hayley's helmet locks and Rook stops her and says, ``Actually Jonah, why don't you give me a hand with this?''  Jonah is helping Javier to his feet and starts heading over to Hayley.  Rook looks at Jaya, ``And perhaps you could take a step back?''

``Yeah, okay,'' says Jaya, stepping back.  ``She's not moving!'' she adds helpfully.

Jaya points at Javier and orders, ``Javier!  With me.'' and she starts climbing out of the train.  As she climbs onto the new ``roof'' of the train, she mentally asks Lackovich  {\color[RGB]{255,0,0}\hl{::Hey.  Check with Carruthers about what is going on with Hayley.::}} \footnote{\textbf{Suko T }Lackovich never told Jaya what Carruthers thought was going on with Hayley (while Hayley was unconscious), did she? \textsubscript{02/25/15 3:28pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }I sort of assumed things were hand-waved resolved on this.  L doesn't seem like she'd drop the ball on something like that. \textsubscript{02/25/15 4:28pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Lackovich didn't get back to Jaya, it's true. But that is likely because 'why bother?' \textsubscript{03/09/15 5:13pm}}

 {\color[RGB]{74,134,232}::I'll ask her.  But what the fuck } \textit{ {\color[RGB]{74,134,232}happened} } {\color[RGB]{74,134,232}?::} 

 {\color[RGB]{255,0,0}::Train is sideways.::} 

 {\color[RGB]{74,134,232}::No, I mean the other thing.::} 

 {\color[RGB]{255,0,0}::Train is fucking sideways and exploding...::} 

 {\color[RGB]{74,134,232}::No!  I mean the fucking woman whose neck you bit!:: }  As Lackovich thinks this, Jaya can feel the coppery taste of blood in her mouth.

 {\color[RGB]{255,0,0}::I just got stressed out and I hallucinated a little.  Happens all the time.::} 

 {\color[RGB]{74,134,232}::\hl{I would ask you what drugs you take but }}{\color[RGB]{74,134,232}\hl{I do }}\textit{{\color[RGB]{74,134,232}\hl{not}}}{\color[RGB]{74,134,232}\hl{ want to know}} \footnote{\textbf{q.google }You have chosen ... poorly. \textsubscript{02/25/15 3:47pm}}\footnote{$\rightarrow$\textbf{Suko T }Please, like Jonah ever wanted to know either :D \textsubscript{02/25/15 4:19pm}} {\color[RGB]{74,134,232}.::} 

Jaya reaches the roof of the train and and looks around.  The whole area is shrouded in a thick mist.  She snaps at Javier to be careful.  The visibility is very poor.  There is sunlight somewhere above, the light diffused and muted in the gloom.  There is a torn up patch of grass to one side of the train.  In the distance Jaya can see what look like buildings, but it's hard to make out details.



``Agent, where are we?'' Jonah asks Rook as he assists in taking Hayley's helmet off.

``Near Portal Station.. well actually we're about one station past that.  We were moving somewhat faster than I was expecting, leaving the portal.''

``So we passed the hub?'' asks Jonah.

``Yes it appears the station was defended in a... fairly unique fashion.''

They assess Hayley's condition.  She appears to be mostly unhurt, but still unconscious.  Rook looks at Jonah, ``What is your prognosis?''

``I can't tell about internal injuries but she doesn't seem to have any external injuries.  Skin color is alright.''

``I concur,'' says Rook, and rests his hand on her forehead.  ``She seems to have some eye movement.''  He calls out to Jaya on the ``roof'' of the train, ``Agent Parvadi!''

``Rook!  Yeah?'' asks Jaya peering down into the train car.  ``Is she okay?  I'm asking Carruthers but-''

``She's unconscious but I'm detecting something strange and I was wondering if you would prefer to have a learning experience.''

``Is now the right time? There's fucking mist everywhere!  It could get us!  Again.  Fucking mist!''  Jaya draws her gun and looks around her in paranoia.

``Agent, what should we expect to see here?  Where are we?'' Jonah asks Rook.

``It has been some time since I've been here, so I couldn't exactly tell you what's here now.''

``People?  Are there any immediate threats?'' asks Jonah.

``I need your help with a diagnosis,'' says Rook to Jaya.

``What?  Why me?''

``Because you're the \hl{most experienced}\footnote{\textbf{Suko T }Added this because surely Rook wouldn't forget that Javier's an Agent too. :) \textsubscript{02/18/15 4:37pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }:D True, he wouldn't. That was Nate being a dumbass. \textsubscript{02/23/15 2:48am}} Agent who is still conscious and likely to be able to interface,'' says Rook. 

``Do I need my gun?'' asks Jaya.  Rook shakes his head and Jaya drops down into the car with a loud thud.



``Please take the glove off of your...flesh hand,'' instructs Rook.  ``I know that this will not be easy for you, but place your hand on her forehead and clear your mind.  I have to go get something from the cockpit.''

``Does Lackovich need to go away?  'Cause she's really fucking chatty,'' says Jaya, even though Lackovich is saying nothing at all.  Rook looks back at Jaya repressively.

 {\color[RGB]{74,134,232}::Clear my mind.  My mind is clear.  Clearing my mind.  My mind is clear.:: } repeats Jaya over and over in her head.  There is a sensation of being surrounded in a rising tide of anger, but Lackovich does try to help as best she can.



Rook returns with a device. It's got a plate that Jaya recognizes, with a cable attached to it.  He puts his hand on one plate.  Jaya takes her hand off of Hayley's forehead and reaches for the plate.

``Please leave your hand on the Agent's forehead,'' requests Rook.  He places one hand on Jaya's shoulder and puts the other on the plate.  After a moment, he asks Jaya, ``Do you feel anything?''

{[}\textit{Challenge 1: Notice.  6th Sense 1 (Jaya) → Matched}{]}  Jaya stares at Hayley and is pretty sure nothing's going to happen.  Then she looks more closely at Hayley- are there bugs under Hayley's skin?  And then a weirder thought- are there bugs \textit{under} the bugs under her skin??  For the briefest of moments Jaya can see radiating lines of color, made up of streams of tiny globules and pinpoints of light, traveling along the paths of Hayley's nervous system.  They are in two different colors, red and blue, overlaid over each other.  \hl{One set is somewhat superimposed and stronger over the other.}\footnote{\textbf{Rebecca S. }which color is dominant? \textsubscript{02/23/15 9:06am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Let's say red? \textsubscript{03/09/15 5:14pm}}

``Uh, fuck,'' reports Jaya.  ``She's kind of... sparkly?  Oh man, I didn't take anything this morning, but it's kinda fucking sparkly.  Blue and red.''  Jaya pushes a little harder on Hayley's forehead to try to induce the vision again.

``Interesting,'' says Rook and removes his hand from Jaya's shoulder.

``What is this?'' asks Jonah.

``I don't fucking know!  I'm not making it up!'' exclaims Jaya defensively.

``I'm not asking you, sir,'' says Jonah.

``It's an interesting...hmm....side effect of the Agent and the VTX wherein they can have abnormally strong connections to other quantumly entangled mechanical parts.''

``Why does the plate help?''

``Mostly because I need to boost her signal because she's...insensitive,'' says Rook.

Jaya doesn't even hear Rook as she keeps taking her hand on and off of Hayley's forehead.  ``I'm not getting it again,'' Jaya frowns.  ``I'm not seeing it anymore.''

``If she were better at it, she might be able to control a train, but I believe her resources are at capacity, given her hand,'' Rook comments to Jonah.

``The hand inhibits the effect?'' asks Jonah

\hl{``It's more that if I were already holding a wrench in my hand, it would be difficult to hold a hammer as well.''}\footnote{\textbf{Rebecca S. }fuck you, Rook. Jaya can totally dual wield! \textsubscript{02/23/15 9:07am}}Jaya is still ignoring Jonah and Rook and starts slapping Hayley's cheeks, ``'Cmon!  Wake up.''

Rook attempts to stop her, ``Agent Parvadi, if you would kindly not-''

``I'm trying to maintain the connection thing!'' protests Jaya.



Hayley is slowly coming to.  She has a moment of confusion to wonder why Trenton is slapping her, and then remembering what Trenton said, she screams, ``No!  Signe!''  

Jaya stumbles back, startled, and Rook moves smoothly out of her way.  Hayley flails, trying to get upright, confusedly trying to get to Signe.   Carruthers can tell Hayley's thoughts are pretty much incoherent and completely hysterical.  Hayley keeps repeating, ``Where's Signe?  Where's Signe??'' 

 {\color[RGB]{153,0,255}::Oh shit!::} 

Jonah tries to catch Hayley's attention.  ``Hayley!''

Hayley suddenly stops flailing.  She's still panicked but her body is still...as if her Operator had stepped in to keep her from hurting herself.  Hayley whimpers but doesn't fight Carruthers.

Jonah looks Hayley directly in the eye,  ``Hayley, Signe is fine.''

 {\color[RGB]{153,0,255}::That's correct.  She is fine.::}  thinks Carruthers emphatically.

``Hayley!  Sorry I hit you,'' interjects Jaya.

Hayley says despondently, ``But Mr. Hadef said Signe was dead.''

``Fuck Trenton!'' says Jaya with disgust. 

 {\color[RGB]{153,0,255}::How did you speak to Trenton?  I see him and he's not there.::} 

``How did you speak to Trenton?'' echos Jonah.

Jaya says firmly, ``Hayley, you just had a bad dream.''

Hayley looks down and relaxes a little, ``Oh I have my uniform back!  That's better.''

Jaya keeps on talking, ``You never took it off, you just had a bad dream. 'Cmon, get up. We gotta get the fuck outta here.  The train is off its tracks and who the fuck knows where we are-'' 

``Are we in California?'' asks Hayley, sounding lost.  Jaya and Hayley look at Rook.

``What?  Hayley, you probably hit your head,'' says Jonah.

Rook gives Hayley a quizzical look and cocks his head.  ``California?  Where does \textit{that }name come from?''

``He is taking me to California,'' replies Hayley.



At that point, from the roof of the train, Javier calls out, ``Uh, guys? \textit{Guys??}''

Jaya pops back up to see what's got him concerned.



Down in the train, Jonah says to Rook and Hayley, ``Something happened, something strange happened during this-'' he pauses and says frustratedly, ``We don't have time for this.''

``We should talk about it at our earliest opportunity,'' says Rook.  ``But we should first see what is concerning Agent Javier.''

Hayley is still breathing too fast, her skin pale, eyes wide.

Jonah tells her, ``Hayley, if Signe was harmed, I would know.  \textit{Calm down}.''

She only half-hears him, still a little muddled in her head.  Her thoughts are still panicky.   {\color[RGB]{255,153,0}::She's not dead.  She's not dead?   Right?  Not dead.::} 

 {\color[RGB]{153,0,255}::She's fine. They contacted her in Medbay and she's coming up here so I can visually confirm it for you.  I don't think you should worry.  Victor is very excited. He says there was a }  {\color[RGB]{153,0,255}\hl{parallel quantum valence event, proving the last one wasn't a fluke}} \footnote{\textbf{q.google }Oh of \_course\_.  A \_parallel\_ quantum valence event.  We should have realized! \textsubscript{02/25/15 4:07pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{03/09/15 5:14pm}} {\color[RGB]{153,0,255}. Hold on.::} 

 {\color[RGB]{255,153,0}::I don't know those words.  He asked if I remembered it.  Why would he ask that?  Why would he lie to me about that??::  } Carruthers gets a mental replay of the scene of Trenton asking Hayley if she remembered Signe dying.  Carruthers feels Hayley's reflexive surge of panic and intense denial, and then that image is forcibly repressed with a  {\color[RGB]{255,153,0}::This is untrue::}   Carruthers hears her own voice and Jonah's voice telling Hayley that Signe's fine, and the panic recedes.

 {\color[RGB]{153,0,255}::I don't think Trenton lied to you. I saw most of what you did, I think. It seemed pretty real. But that probably wasn't Trenton. He smelled a little differently, and was so much... sadder.::} 

A momentary lull as Hayley is surprised by the idea that one can tell people apart by their sadness.  The two Trentons seemed the same to her.   {\color[RGB]{255,153,0}::Why would he ask if I remember- oh!  Is this like Burrough Station?   Where I remember things happening that haven't happened yet?:: } Another spike of worry from Hayley.

 {\color[RGB]{153,0,255}::Hold on.:: }  A pause.   {\color[RGB]{153,0,255}::I asked Victor, and he said that it wasn't like Burrough Station. He can't prove that happened. Trenton agrees: you'd need a way to slow down time or bounce energy off a different spacetime lattice. Wait. Now they're arguing too fast for me to follow. Uh...::}  There is an awkward pause and a connection attenuation.  {\color[RGB]{153,0,255}::Look, uh, don't worry.  And see, there's Signe, she's fine.  Morgan says stay on task.::} 

Hayley is relieved and finally calms down.   {\color[RGB]{255,153,0}::Okay.  Thank you for clarifying.::}   And her thoughts settle and focus.



Jonah checks Hayley for a concussion.  ``Physically you're fine.  We need to get up there.''

``Okay,'' says Hayley, suddenly more coherent and calm.

``Don't forget what you saw, but we'll talk about it later.''  He pauses and then looks at her and says with emphasis, ``The train has crashed.''

``I remember that,'' says Hayley, unperturbed.  ``We got really hurt... but ... you are all okay?''

``Yeah.''




\sceneHeadline{Roof of the Train}

Jaya pulls herself onto the roof of the train.  Javier is there, checking his weapon repeatedly.  On the green, coming toward the train is a... thing.  It's got a sort of central abdomen-like part with metal bits/limbs coming out of it. Sort of like a giant spider except that it moves oddly, jerkily.  It is approaching in a weird pattern.  There's an odd noise.

``Stop right where you are!'' yells Jaya, putting her hand on her sidearm.  The thing stops.  Jaya looks pleased and throws Javier a 'See I got this' look.  The noise that the thing was making has stopped, but now Jaya can hear other similar noises faintly in the mist.



Still down below, Jonah asks Rook, ``Agent, should we go up?''

``Probably.  We should secure the train,'' replies Rook.

``How?  From outside?''

``This is a poor defensive position,'' says Rook.

Jonah turns to Hayley, ``Hayley get up, we have to get moving.''

Hayley finds her rifle and then gets to her feet, staggering a bit dizzily.  Rook helps her steady herself.



Above, still looking at the spider-thing, Jaya shouts, ``Identify yourself!'' There is no reply.  She repeats herself, even louder.

``Chief, show us what you're seeing!'' yells Jonah, trying to get Jaya to share the visuals on her HUD.

``Just get your fucking ass up here now!''

``I will, but we need to know what to bring up with us.''  Jonah coaches Jaya through the menus in the HUD to link their displays.

``Okay, now get your fucking asses up here!  NOW!  That's an order!''

``With... all... due... respect -- we have a patient and I have to make sure she's okay or we'll have \textit{two} patients down here,'' says Jonah.

{[}\textit{Refresh: Air of Command 3 (Jaya)}{]} Jaya leans down into the train and shrieks, ``That is a FUCKING ORDER!!  Get your ass up here RIGHT NOW.''

As Jaya turns away, the spider-bot leaps on Javier as he fires at it in a panic.  {[}\textit{Challenge 3: Don't let the spider get Javier.  Left Arm 3  → Matched}{]}.  Jaya's left arm grabs the spider midair before it is able to wrap its limbs around Javier.  She flings it away from the train and sees it hit the dirt and roll.  Its limbs twist inhumanly and it skids to a stop.  She sees more of them coming out of the mist. 



``Agent, report!'' says Rook, giving Jonah a hand up.

``There's a fucking thing and it jumped at Javier...I didn't shoot it!'' Jaya yells back.  She looks over at Javier and asks him, ``You good?''

``Yeah,'' says Javier, fumbling his reload.

``I think we are outnumbered, and we're probably going to die unless you get up here \textit{right now} and assume a very fucking defensive position,'' orders Jaya to Jonah and Hayley.

Jonah shares his HUD visuals with Hayley so she can see what he sees when he emerges from the train.  Hayley follows Jonah, Rook gives her a hand up and then she leans down to give him a hand up.



As they do this, the spider thing starts running at the train. 

``Halt!'' yells Jaya.  The spider doesn't stop.

Remembering Morgan's instructions, Jaya fires a warning shot right in front of the creature. The dirt in front of it explodes in a spray of debris.  The spider thing skitters to one side, dodges around the crater, and keeps going.  It grabs a piece of shrapnel from the train and then starts running back into the mist.

Without looking away from the spiders, Jaya asks Rook, ``Ah, it took part of the train and ran away. Is that a problem? Are we cool with that?  Do we need to stop it?''

``I feel it would be a fairly poor position to be placed in, to lack a train,'' says Rook calmly.

``Are you going to fucking drive this wreck?  Can we barter it to them.....?''

Jaya's not looking at Rook, but the rest of us can see a smile quirk the corner of Rook's mouth as he says, ``As Commanding Officer, that's my end to worry about.''

Jaya's head whips over to look at him, her expression helpfully hidden behind her helmet, but after a beat she calmly says, ``Very well sir.''



Up on the train roof for the first time, Hayley looks around.  There is a track that we have come off of and now the train is on its side, lying in a lawn.  The track stretches out sort of in front of us and there are buildings and a street of some kind.  Behind us is hole in a hill that the tracks are emerging out of, somewhat like we saw in Nicklepan.  There's a walkway through the lawn that our train is lying in.   Along the walkway it's got a weird series of short black posts in the ground, connected by a chain.  It would be sort of like a fence but it's totally useless in actually keeping anyone out.  In the middle of the lawn is an odd cement pillar with what looks like a sink on top of it.



Jonah turns to Rook and gestures to the stuff we are seeing, ``Sir, what is all that? Do you know?''

``You need to be more specific,'' says Rook

``All of it.  The metal construct-''.

``That appears to be a... I'm not entirely sure what that is.''

``Should we move?  Or guard the position?'' asks Jonah.

``Until we can secure some other train, I am loathe to give up this one,'' says Rook.

``Will this one be rendered operational again?'' asks Jonah.

``I have not yet had time to make that assessment.''

``How much time do you need sir?  Should we go out and scout the area first?'' asks Hayley.

``Possibly,'' says Rook.

``Is it cool if I blow up one of these motherfuckers?'' asks Jaya.  She glares at the spider things. Some of them are creeping up again, trying to ``stay low''. Others are skittering back and forth, seeing how we respond.  They definitely seem to be fanning out.

``What do you advise?'' Rook asks Jaya.

She snaps, ``I thought you were the commanding officer!  Sir.''

``I am given to understand that it's common for commanding officers to ask their agents and operators for their professional advice in situations that are new.''

``Really?'' says Jaya in surprise.  She looks startled but, again, no one can see her expression through her helmet.  There's a low spiteful chuckle in Jaya's head.

``You know more about weird fucking stations.  You know more about these-'' Jaya waves her hands at the spider things.

``Let's give them a name,'' says Rook.

``Motherfuckers,'' suggests Jaya immediately.

``Too generic.''

``Spiders?'' says Jonah.

``Very well.  Spiders,'' agrees Rook.  ``Should we shoot the spiders?''

``Well, depends how much you want your train-'' says Jaya.  She whips her head around and points her gun at one of the spiders threateningly, ``Stay the fuck back spider!  I SEE YOU.''



Jonah watches the spiders and notices that they are stealing parts of the train, scuttling away into the mist and then come creeping back. ``They're scavengers,'' he says.

``I came to the same conclusion,'' says Rook.  Jaya fires another warning shot at the spiders.

``Which means,'' says Jonah, ``They'll take what they can.  And if they can get the drop on us, they will, but they would prefer not to be destroyed. So we could...scare them.''

``Perspicacious analysis,'' comments Rook.

``Should we retrieve what was taken?'' asks Hayley.  ``It cannot be far, based on their rate of return''

``As long as you don't mind a little wind going back, what they've taken so far is \textit{probably }not an issue,'' says Rook.

Another warning shot from Jaya.

{[}\textit{Challenge 1: Notice.  Concealment 1 (Jonah) → Matched}{]}  Jonah notices that one of the spiders has stealthily crept up the side of the train, unnoticed until now.  It's a large one and it's halfway up the side of the train car.  

{[}\textit{Challenge 3: Blow off one of the spider's limbs.  Small arms 2 (Jonah) + Gauss Pistol 2 (Jonah) + Small Unit Tactics 3 (Jonah) → Overcome! }\textit{\textbf{3 VP (Jonah)}}{]}   As soon as it realizes that Jonah has spotted it, it starts rushing him. Jonah blows off a leg and it falls back to the ground.  It scoops up the shattered leg and retreats back into the mist. The other ones have all frozen in place.  ``Apparently, they don't seem to mind being injured,'' says Jonah. ``That's unexpected.''

``I dunno,'' says Jaya with a shrug.  ``I lost an arm and I kept moving.''



Hayley readies her rifle and looks at Rook. ``Shall I shoot more of them?  We have already begun... aggression.''

``Then if I may make a suggestion?  The injury trick didn't work the way I expected. I would go for blowing their heads off,'' says Jonah.

``What fucking heads?'' demands Jaya.

``The middle of them then,'' clarifies Jonah.

Jaya sighs in annoyance.  ``Rook!  Can you start fixing the train now?''

Hayley is still patiently waiting for Rook's reply, ``Is that...?''

``Defend the train,'' says Rook.

``Very well Sir,'' says Hayley equally calmly and she turns to the spiders.

Rook says to Jaya, ``Agent, you're in command until I return.''  He drops down and re-enters the cockpit.



{[}\textit{Challenge 4: Defend the train.  Pulse Rifle 3 (Hayley) + HUD 4 (Hayley) + Grenades 2 (Hayley) + Snap Reflexes 2 (Hayley) → Overcome! }\textit{\textbf{4 VP (Hayley)}}{]}  \hl{With no preamble, Hayley goes to one knee for stability, shoulders her rifle and starts picking off the spiders methodically}\footnote{\textbf{q.google }This is the point in the video game version where you get to rack up lots of points. \textsubscript{02/25/15 4:15pm}}.  She focuses on those stealing parts from the train (especially the small sneaky ones that seem to be aiming for particular parts) and those advancing the most aggressively.  Her reflexes are fast enough to catch them before they get too close.  The spiders do have a thermal signature on the HUD and she uses the occasional grenade to herd the spiders to where she can shoot them most efficiently.  As she shoots the spiders, we can see others emerging from the mist and attempting to gather up the pieces of the injured/dead ones and carry them away.  Jaya enjoys this, yells encouraging advice and cheers.  Jonah and Javier sit back and watches the show.



The spiders are pretty tenacious so it's almost 20 minutes before they stop advancing.  About midway through, Jonah leans down and yells to Rook, ``My diagnosis is that the patient is fine.''

Rook pops his head out of the cockpit briefly and replies, ``Thank you medic.''

When it is clear the train is not being threatened by the spiders anymore, Hayley finally stops.

``That was... very cool,'' says Jonah.

Grinning widely, Jaya slaps Hayley on the back.  Still hyped on combat adrenaline, Hayley staggers and spins to face this new attacker, but relaxes when she sees that it's Jaya. 

``That was excellent shooting!'' says Jonah, approvingly.

``Thank you!'' says Hayley.  You can't really see it but she smiles hugely.

``I concur,'' says Javier, admiringly.  ``Do you need to even out on ammo?''

``Oh... yes I do need to take a minute to evaluate that...'' says Hayley  {\color[RGB]{255,153,0}::Oliver would be so disappointed that I wasn't tracking my ammo toward the end.::} 

 {\color[RGB]{153,0,255}::Don't worry, I was.::} 

 {\color[RGB]{255,153,0}::Thank you!  That is so nice of you.::}  Carruthers can feel a strong wave of delighted surprise and gratitude from Hayley, followed by a contented and pleased thought, not directed at Carruthers, but loud enough to 'hear'  {\color[RGB]{255,153,0}::Just like Oliver did:: } 

There is a pause and a flood of warmth from Carruthers. She very clearly transmits  {\color[RGB]{153,0,255}::I will always have your back. }  {\color[RGB]{153,0,255}\hl{I will be the angel on your shoulder}} \footnote{\textbf{q.google }You can count on me.  And I will count your bullets. \textsubscript{02/25/15 4:16pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I forget which is the archangel of bullet counting... \textsubscript{03/09/15 5:15pm}} {\color[RGB]{153,0,255}::}  The connection attenuates suddenly, but not before Hayley gets an 'unspoken' thought from Carruthers  {\color[RGB]{153,0,255}::Like I failed to be for Davis.::} 



Lackovich thinks  {\color[RGB]{74,134,232}::Don't worry, Morgan wasn't } \textit{ {\color[RGB]{74,134,232}too} } {\color[RGB]{74,134,232} displeased that this turned into a combat within the first hour of getting there...::} 

Jaya's happy smile immediately droops. She snarls, ``Everyone stay fucking alert!  We're here until Rook gets us... not here.''

 {\color[RGB]{74,134,232}::Hey, don't take it out on them.:: } thinks Lackovich very directly.

Jaya stomps over to a corner of the roof and moodily starts standing guard.




\sceneHeadline{Leibowitz}

Some time passes.  The mist swirls, but never fades away.  {[}\textit{Refresh: Gauss Pistol 2 (Jonah)}{]}  After about 15 minutes, as Jonah is reloading his gauss pistol, we hear a voice call out to us, ``Don't shoot!''

``Don't fucking move or we're going to fucking shoot you!'' yells Jaya, even though she doesn't know where the voice is coming from.

``Come out with your hands up!'' yells Jonah.

``I prefer not to, if it's all the same to you,'' the voice replies.

``We won't shoot you.  But if we don't know where you are... \hl{we can't not shoot you}\footnote{\textbf{q.google }It's not a \_threat\_, it's a \_warning\_.  Really \textgreater :). \textsubscript{02/25/15 4:17pm}},'' shouts Jonah.

We hear a chuckle.  ``Yeah.... on the other hand, this way, you're a lot less likely to be able to shoot me,'' says the voice reasonably.  ``And I'm not really keen on being shot today.''

``We won't shoot, what do you want?'' says Jonah loudly.  Jaya is cycling through her HUD sensor readings.

``Uh, just want to talk.  I see that you're newcomers...making some friends...sort of...''

``What are those things?'' says Jonah.

``Well I don't know that they have a proper name \textit{per se}... well mostly we call them autos.  But they come in all sizes and shapes.  So that is an.. I dunno... an Auto-8?''

``Nice place you got here,'' says Jonah.

``There are nicer sections. But this isn't too bad.  The Historic District, well preserved, lots of cleanup...''

``I'm sure.  So what do visitors do for fun around here?'' asks Jonah

``Can't really say, we don't really get many?'' says the voice.

They chat while Jaya searches for the guy.

{[}Challenge 1: Notice.  Binoculars 2 (Jaya) → Overcome! \textbf{1 VP(Jaya)}{]}  Jaya spots a faint heat signature by one of the buildings.  She tells Hayley to cover her and she starts walking over in that direction.

``Could you...stop coming toward me please?'' says the voice nervously.

``What brings you here?'' says Jonah.

``I'm the steward of the area so it's actually my duty to check these things out..... Alright!  Alright!  I'll stand up if you promise not to shoot me.''

``I'm not shooting, get your ass out here,'' orders Jaya.

The guy stands up, Jaya is pointing her gun at the ground, though Hayley is still covering both of them.



The guy is wearing brown robes, a bag around his shoulders, an air filtration mask, and sandals.  His skin is lined, dark (darker than Jaya's) and weathered.  The guy asks Jaya if he can pick up his staff.  Jaya checks it out, it's just a wooden walking stick, no buttons.  Jaya lets him take it and motions with her gun for him to walk toward the train.

``Got a name?'' Jonah asks him.

``Uh yeah, they call me Leibowitz,'' says the guy.

``Good to meet you, I'm Jonah,'' says Jonah to Leibowitz.  ``So tell us a bit about this place.  Is it alway this foggy?''

``Yup. That's why you brought the masks, I assume.''

``Part of it,'' hedges Jonah.  ``And the Autos, are they coming back?'' 

``Uh, well they kind of live here.''

``Are they animals or people?'' asks Jonah.``Well, they're not people.''

``They don't hurt \textit{you},'' comments Jonah.

``Well I don't have much that they want,'' says Leibowitz.  He asks, ``Can I ask why y'all are here?''

``We didn't exactly plan to stop here, in case you fucking didn't notice,'' says Jaya gesturing to the train on its side.  ``Did the spiders do this?''

``I wouldn't say it was the auto-8s.  But there is the occasional tiger.''

``What's a tiger?'' asks Jaya.

``What do they look like?  How big are they?'' asks Jonah.

``Well I haven't really stuck around one of them long enough to know for sure.  They like hunting things,'' says Leibowitz.

 {\color[RGB]{255,153,0}::Do you know anything about these tigers or auto-8s or this man?::} 

 {\color[RGB]{153,0,255}::We know that the area is populated but we don't know much.  As per the briefing, Rook was... opaque?::} 

``Sorry you got stopped, anything I can do to help?  Where were you headed?'' asks Leibowitz.

``None of your business!'' says Jaya quickly and defensively.

``Do you know how to repair a train?'' Hayley asks Leibowitz.

``Nope.''

``Do you know anyone who does?  We need our train fixed,'' asks Hayley.

Rook pokes his head out of the train, ``Actually we don't need it fixed.  We may just need a hill.''

``Do you have a hill?'' Hayley asks Leibowitz.

``Oh yeah.  Lots of them.  Known for 'em,'' he replies.  We ask him about the hills and then look at Rook for guidance on what kind of hill.

``A hill with a track on it, preferably with a portal at the end,'' says Rook.  Leibowitz says that he thinks he knows a place.  We discuss how to get the train to that place.  Leibowitz says that he can get some help from the Monastery (where he lives) about one mile away, maybe wrangle some domesticated autos to help out.  Jonah asks what Leibowitz would like in return.

``We would appreciate a small donation, but you don't need to,'' says Leibowitz.

``What would you like?'' presses Jonah.

``Oh we're open to all sorts of donations. I mean we don't \textit{need} things but...''

Over the hush mike, Jaya mutters, ``Should we offer them their lives?''

``Agent,'' says Rook repressively over the hush mike.  

``Can you suggest anything? We're pressed for time,'' says Jonah.

``Trading goods are always good.  Apart from that... a good story?  I don't suppose you have any books on you?'' suggests Liebowitz.

We confer over the hush radios.  Hayley wonders where Rook got a hush radio but says nothing.



Rook says to Leibowitz, ``Do you know where the Beacon is?''

Leibowitz raises an eyebrow, ``Is that where you're headed?''

Jonah tries to get a read on the guy, Leibowitz is clearly intrigued.

``You tell us why you care, and we'll tell you why we do,'' challenges Jonah.

``Uh, well it's just that not many folk go there.  Lots of things in the way.  You understand,'' says Leibowitz.

``We ain't scared of the tigers,'' says Jaya.

``I think we hit one of those things,'' says Hayley.

``Tigers are not-  They're not the largest... uh, they wouldn't be the obstacle I'd worry about.''

``What \textit{should }we worry about?'' says Jaya intently.  ``We're fucking new here.  Help us out.''

``There's a....You'll forgive me, there are certain rules we have to live by at the Monastery...  Let's just say there's a man...'' says Leibowitz a little awkwardly.  Rook smiles.  Leibowitz continues ``who likes to keep the place...to himself.  But I could arrange a meeting if you what you want.  I won't even charge you for it.''

``Yes!'' says Jaya.  ``Is it close?''

``Yeah it's like four miles from here or so,'' says Leibowitz.

Jonah looks at Rook who says nothing.

``Is he a problem for you?'' asks Hayley.

``Oh no!  Quite the opposite.  He's sort of the reason we're here.''

Jaya holsters her gun.  ``We'd love to meet him.  Take us there now.''

We negotiate logistics for a bit.  Hayley offers to stay with the train and have Lackovich and Carruthers communicate between the groups.  We agree to have Leibowitz send a message signal to his Monastery and then take us directly to this person who knows about the beacon.

Rook tells Hayley, ``Agent, please tell Carruthers to have all Causeways flooded.''

Hayley repeats this to Carruthers.

 {\color[RGB]{153,0,255}:Oooookay.  Hold on.  \textless a pause\textgreater   Morgan is asking if this is a good idea.::} 

``Uh Sir, Agent Morgan is asking for clarification on whether this is a good idea... from you Agent Rook, Sir,'' says Hayley quietly over the hush radio.

``Have her prepare to empty Causeway 1, in case we are able to get the train back on track, but unfortunately I don't see any other way to do this.''

Hayley repeats this verbatim to Carruthers.

 {\color[RGB]{153,0,255}::Morgan says go::} 

``Agent Morgan says go,'' says Hayley to Rook. 

``Very well,'' says Rook and he turns to Jaya.  ``Agent, you are to take command of an away team and go to the Beacon and complete the mission.  I will get the train back on track and prepare to leave.''

``Very good, are you going to need anyone to stay to assist you?'' asks Jaya.

``I think I'll be alright.  But stay on your radio in case that situation changes.  Similarly, if you are to get in trouble, you are to contact me immediately. Do you understand?''

``We'll contact you if there's any trouble we can't handle, Sir,'' says Jaya confidently.

``Please keep me appraised of \textit{all }events that happen,'' says Rook with emphasis.

``Should I stay, Sir?'' Hayley asks Rook, looking a little worried.  ``So that if the radios are not effective, we can still communicate?''

``I can answer that that question directly, or I can ask you, Hayley, if you think if it's of prime importance to get the Beacon activated?''

``But there would still be two Agents-'' says Hayley.

``I'm not saying that Agent Parvardi and Agent Javier are not capable of doing their jobs.  However I do believe that the obstacles they will encounter will be significant.''

``I would like to go, Sir,'' clarifies Hayley, ``I just wanted to make sure that you would be able to communicate with us.''

``Are radios insufficient?'' asks Rook.

``We don't know sir, I think that's what Agent Hayley is-'' says Jonah.

``You are carrying \hl{a}\footnote{\textbf{Suko T }I can't do math.  We only have one HESP and two hush radios.  I gave the HESP to Jonah.  Because the ladies have their network all set :D \textsubscript{02/25/15 3:58pm}} Harsh Environment Signal Processing radio, you should be fine,'' says Rook.

``Very well, thank you sir,'' says Hayley.

``The distances here are very small.'' adds Rook.



Jonah asks him, ``Do you know what we should expect?  Do you know anything about this person that our guest is taking us to go see?  Do you know anything about them?''

``Yes,'' says Rook.

``Anything that \textit{we} can usefully know?'' asks Jonah.

``I recommend dealing with him straight,'' says Rook.

Over the radio, Jonah hears from Rook privately, ``Do not let the Agent get into combat with him.  She will lose.''

``Knowing who he is in the advance won't be helpful?'' asks Jonah.

``Not as it stands now.  I'm not certain how he will react to my person, so I prefer not to be there unless necessary.''

``Is he a Praetor?'' asks Jonah.

``No.''

``What is he likely to demand of us?''

``I have no idea what he will ask of you but ... it is likely to be odd,'' says Rook.

``What if he wants information about where we are going and why?''

``I would see no problem in telling him that,'' says Rook and then adds, ``Be aware that while he is not a Praetor, he is still dangerous in other ways.  I wish I could tell you more but I don't actually know.''



Jonah tells Leibowitz to send the message and we can get started.  Rook hops off the train and walks up to us.  He politely asks Leibowitz to turn around.  Leibowitz turns around to face us and away from Rook.  Jaya sidles around to see what Rook is looking at.  However Rook blocks her view and pulls the back of Leibowitz' shirt collar down and to the side (like where one might have a tattoo), nods, and pulls the collar back up.  Leibowitz seems unsurprised at this.  Behind her helmet Jaya raises an unseen eyebrow at Rook.



``I'll wait here,'' says Rook and walks back to the train.

Leibowitz takes something out of his satchel and takes out a cylinder thing with many dials on it and starts fiddling with it.  After a bit, Leibowitz picks up the cylinder and raises it up to slam it into the ground.  Hayley had been scanning the area for more Auto-8s but at this she spins around and points her gun at Leibowitz.   {\color[RGB]{255,153,0}::Ack!  Portal?  Enemies incoming?::} 

 {\color[RGB]{153,0,255}::Augh Portal!::} 

 {\color[RGB]{74,134,232}::Portal!!::} 

Jonah stands by, relaxed and unworried. 

Jaya looks around for a portal, she mutters, ``I don't see a fucking portal!  Where's the portal?''

The baton hits the ground and unlike the other batons they have seen, a very bright beam shoots up into the sky and then bunch of rapid flickers.  Hayley can tell it's a pattern that is repeated several times.




\sceneHeadline{The Historic District}

We head out.  We start walking through the Historic District.  The buildings are weird.  They seem to be made of \hl{something that isn't cement}\footnote{\textbf{Suko T }It's wood but we can't imagine some place having enough wood to make buildings out of it. \textsubscript{02/22/15 11:40pm}} They are \hl{brightly painted and have artistic flourishes}\footnote{\textbf{Suko T }Like these?
http://en.wikipedia.org/wiki/File:Haight\_Ashbury11.JPG \textsubscript{02/22/15 11:38pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Yes \textsubscript{02/23/15 3:07am}}. The buildings are quite nice.

``Where are all the Citizens?'' asks Hayley.

``Citizens?  None of the people live here. This is the historic district.''

Jonah asks him some more about the people in the area. It seems like there might be some people living in the hills.  

Jaya and Hayley have a hushed discussion about the strangeness of this area. They are both a bit on edge- this area is so defensible that walking through it is very nerve-wracking.  So many windows for snipers to look out of, so many blocked lines of sight and lots of straight line avenues, limiting ability to approach under cover.



Jonah talks with Leibowitz.  He offers bits of generic info about us to lure Leibowitz into telling more about himself.  Hayley is limping a bit more than usual.  



Leibowitz advises that once we leave the historic district there are likely to be more tigers and many many more Auto-8s.  ``I highly recommend that you don't interact with any of them unless they interact with you.''``Don't shoot them?''asks Hayley.

``The only reason we shot at them was because they were taking parts of our train,'' says Jonah.

``Oh, totally reasonable, but I highly recommend that you keep your guns and weapons to yourself unless directly threatened.  I think most things will probably ignore you.  Don't get between them and their... for lack of a better term... children.''  

Jaya holsters her gun.

``Is there anything that we \textit{should} shoot at?'' asks Hayley.

``Well I'm a big believer in pacifism...''

Jaya snorts.

``What about tigers?'' asks Jonah.

``They're hunters so don't be prey,'' says Leibowitz helpfully.  ``If you have a prey mentality, then predators have a tendency to find you.''



We start hearing a buzzing noise.  Hayley stops and looks upward, reminded unpleasantly of Nicklepan.  ``What's that?'' she asks.

``Probably Drones... Oh yeah, there they are,'' points out Leibowitz and a flock of flying autos buzz by overhead.

``Will they drop bombs on us?'' asks Hayley.

``I've never known a drone to have a bomb....'' says Leibowitz.



``How many people are there like us?'' asks Jonah.``Oh well... there's the Monastery... and travellers who come through.  Usually they're lost and confused.  Sometimes they get killed.''

``You mean, no people but the Monastery and the person you are taking us to go see,'' says Hayley.

``\hl{Well... I use the word person lightly}\footnote{\textbf{q.google }Didn't answer the question. \textsubscript{02/25/15 4:24pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It's kinda epidemic. \textsubscript{03/09/15 5:16pm}}.  Royalty is bigger than a person, right?'' says Leibowitz.



``Who built the autos?'' asks Jonah.

``That's hard to say.  I''m sure someone did.  In fact if his Royal Highness agrees to an audience, he may tell you.  If he chooses to.''

``Is his Royal Highnesses' name Poseidon?'' asks Hayley, curiously.

``No.''

``How should we address him?'' asks Jonah.

``As His Royal Highness or Your Majesty.  \hl{But I recommend not addressing him unless he addresses you first.}\footnote{\textbf{q.google }Good to know, good to know.  So helpful to have a tour guide who knows the local customs, and volunteers information so easily. \textsubscript{02/25/15 4:25pm}}````What else can you tell us about royal protocol?  We don't want to be rude,'' says Jonah.

``Absolutely!  Don't approach him.  Allow him to approach you or summon you to him.  Never walk more than three paces in his direction when he summons you.  And allow yourself to be summoned again for each additional three paces,'' advises Leibowitz.

``You've talked to him?'' asks Jonah.

``I haven't had a conversation with him but I was brought before him when I took my oaths,'' says Leibowitz.

``How do you know what he wants if you don't talk to him?'' asks Jonah.

``Well, the Abbot has made it clear that he wants us to continue our jobs as we have for several generations....'' Leibowitz says in an aside ``some say \textit{many} generations but I'm a little skeptical about that sometimes.''  He continues, ``But he hasn't ever had any demands of me or any of my brothers with whom I have had conversations with.''

Jaya has popped her blade and is rubbing it against her armor, making a raspy metallic noise.

``So how do you know these things are true?'' asks Jonah.

``We have many tapestries indicating protocol.  And when it is broken he... reacts.''

``Will he speak in a way we understand?'' asks Jonah.

``Gosh I sure hope so!'' says Leibowitz in surprise.  ``I never thought of that. But some of the brothers say that they see him watching them as they go about their tasks and he seems to understand what they say amongst themselves.''

``What does your Monastery do?'' asks Jonah.

``Oh we are stewards of this place and the knowledges that happen to come through this place.''

``I see.   We are stewards of a sort too... of our homeland.  To protect it,'' says Jonah.



``May I ask a question?'' says Hayley to Leibowitz, turning off the opacity of her helmet so he can see her and she can see him more clearly.

``Absolutely!''

``You said that others that are lost come through here.  Do they always arrive in a train?'' asks Hayley.

``Most of them.  But not through that portal though, I believe the tigers particularly like feeding there,'' says Leibowitz.

``\hl{Do any of them say that their name is Octavius}\footnote{\textbf{q.google }Right between the eyes. \textsubscript{02/25/15 4:26pm}}?'' asks Hayley.

{[}\textit{Challenge 2: Convince Leibowitz to answer.  Gorgeous 3 (Hayley) → Overcome! }\textit{\textbf{2 VP (Hayley)}}{]}

Leibowitz nods thoughtfully, ``You know...As a matter of fact, I believe that a traveller that my brother referred to as Octavius came through recently and requested an audience with the King.''

``How recently?'' asks Jonah

``I believe a few months ago,'' says Leibowitz.

``Did the King see him?'' asks Jaya.

``Yes''

``FUCK.'' mutters Jaya.

``The King sees most people who request an audience. That does not mean His Royal Highness acquiesced to whatever they wanted to request during that audience,'' elaborates Leibowitz.

``Do any of those who request an audience with the King ever not return?'' asks Jonah.

``Well, usually those who come and request an audience do so with the hope of following the Silver Trail.''``What is that?'' asks Jonah.

``The trail that leads to the Beacon.  Though very few are allowed on it.  Obviously I have no way of knowing for sure.  We are not allowed on it.''

``Why?  If I may ask,'' asks Hayley

``It is not our place,'' says Leibowitz matter-of-factly.  Hayley nods in understanding.  Jaya snorts derisively.  Jonah says nothing, but tries not to say it too loudly.




\sceneHeadline{Past the Historic District}

As we leave the ``historic district'' the buildings become much taller and haphazard.  The buildings have been partially torn down and rebuilt in different styles so they appear to be a bunch of different buildings mashed together.  We see a lot more autos crawling over buildings.  Some are taking some buildings apart and laying parts in orderly piles, and others are putting buildings together. \hl{There's one part where an auto is building something and is followed by another auto who immediately disassembles whatever the first one just built.}\footnote{\textbf{Rebecca S. }My mental picture of the Auto city is entirely defined by this music video: https://www.youtube.com/watch?v=SuQGfk9Gmgo \textsubscript{02/23/15 9:35am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Pretty much, yeah. But foggier. \textsubscript{02/23/15 12:12pm}}  



Some are just sitting there.  There's one on its side and an auto-8 comes up to it and drags it away.  Drones are flying around and occasionally landing.  A few of the drones are carrying things.  Eventually the buildings get tall enough that we can't see the tops of them in the mist anymore.  Hayley is pleased by the orderly purposefulness of everything {\color[RGB]{74,134,232} ::This is rather nice:} :



Jonah contacts Rook and gives him a brief update, ``Other travelers have come through and one of them, recently, belonged to our antagonist.''

``Do you mean Octavius?  I am not wholly surprised by that.  The Beacon is... fairly powerful,'' replies Rook

``I assume that the entity that we are going to speak to calls it The Silver Trail which leads to the Beacon.  And the entity appears to be the guardian of it.''

``I would recommend not having any preconceived notions of his role regarding this place,'' advises Rook.  ``It may be a protocol error to call him 'guardian'.  Thank you for keeping me informed.''



There are hills, and we have to hike uphill and down quite a bit.  Hayley smiles to herself, thinking of SAC-04.  



We get to one building that is notable in that it is lit up.  There are weird balcony-like windows or glass rooms that bulge out of the sides of the building.  The rooms appear to be filled with yellow-grey fluid, and there are humanoid bodies floating in them.  Their bodies have strange tumor like things that have grown out of their orifices and parts of their skin and are now floating in the water around them like tentacles.



Jonah asks Leibowitz, ``Are those \textit{people}?''

``I am told they were once people like you and me, yes.''

``Did the autos do that to them?'' asks Jonah.

``Oh no!  That is their... life now. They have chosen a different path.''

``Are those Tanks?'' asks Hayley.

``No, those are luxury apartments,'' says Leibowitz.

Jaya says nothing but is thinking in her head {\color[RGB]{255,0,0} ::Oh my god, what the fuck is wrong with this place?  Let's get the fuck out of here!!::} 



Hayley is both horrified and oddly fascinated by the ``people'' in the luxury apartments and falls behind a little, staring at them curiously.   {\color[RGB]{255,153,0}::That would be an interesting way to have done it::  } The people are/were clearly attractive well-formed people, but they are also bloated and distorted by the growths (or the glass).  She is having trouble reconciling her gut instinct that these are pretty people and the fact that they look horrid.  The others notice her lingering and tell her to hurry up so she hastens to rejoin them.




\sceneHeadline{The Gate}

We go over a hill and cross some tracks.  Leibowitz mentions, ``I think this is where we'll put your train. In case you care.''

``There's a portal in which direction?'' asks Hayley.

``Down that way,'' he points down a steep hill. 



We notice that the buildings are getting shorter.  There are things strung between the buildings, sometimes glorious wooden bridges and sometimes they are orbs with very soft lights that seem to hang hang in the air.  Other times they are flags which occasionally flutter in the breeze.  There are autos all over the place.  It is much more colorful here, with oranges and reds in the buildings.



Eventually we come to a wide plaza surrounded by a wall.  We walk up to a large ornate wrought iron gate set in a stone wall.  Over it is a huge wooden structure.  Leibowitz tells us, ``Wait here a moment and I will request an audience for you.'' 

``Thank you,'' says Jonah.

``Don't delay, we don't want to be here long.'' says Jaya.  She's looking around suspiciously and is not happy to see movement in the recesses of the wooden structure above us.

Leibowitz opens a small portico in the gate and passes through.  We can see him cross over a very large bridge and disappear into the fog.



Over the hush radio, Jonah says, ``Rook said it was very important that we stay calm and negotiate.''

Jaya continues to fidget with her knife.

``It's pretty here,'' comments Hayley.

``Hayley...'' Jaya sighs.  ``Just- stay alert.  You too, Javier.''

``You're not going to catch me sleeping,'' says Javier.



After a few minutes Leibowitz comes out of the portico and says, ``His Majesty will see you now.''  He gestures and the gates slowly open.  Hayley moves to enter first.  Leibowitz says, ``When you see the Dragon Tile, stop.''  Hayley nods.

Jonah says to Hayley, ``You understand about the Dragon Tile and the three steps?''

Hayley turns to him, puzzled, ``Yes. Did I miss something else?''

``Hayley knows her fucking protocol!'' Jaya admonishes Jonah.

``She does!  I was just making sure she heard it,'' says Jonah.

The gate closes behind us.



\hl{Just after passing through the gate}\footnote{\textbf{Suko T }Thank goodness Rebecca remembered this happening, I totally forgot to add this in. \textsubscript{02/26/15 11:49am}}, Carruthers and Lackovich indicate to Hayley and Jaya (and Signe confirms if contacted) that SAC-09 has lost main power. Some sort of system overload. Backup systems are online and functioning, if sporadically. Jonah learns via Signe: this means most of the lights are out, those that are on are struggling to stay that way, and non-essential computer terminals have gone out. Lots of beeping noises coming from power supplies and battery backups. Carruthers and Lackovich are in tanks, but getting out under procedural instructions from Morgan, and for safety in case the life support becomes affected. Both Operators indicate they're fine, and that Morgan indicates that the Patrol Group should proceed. Via Signe, Morgan seems more annoyed than worried.



Hayley walks forward slowly toward the bridge that Leibowitz had walked over before.  It's almost like a wide stone road with ramparts on either side of it, but there is the sensation of mist and emptiness on either side of it and nothing but mist ahead of us.

Hayley whispers in her head  {\color[RGB]{255,153,0}::Operator Carruthers, what's a dragon?::} 

 {\color[RGB]{153,0,255}::Uh, hang on, I'll find out...::} 



The mist makes it seem like we are suspended in on the bridge with nothing around us.  We can sense movement to either side of us on the edges of the bridge and hear drones above us.  Jaya is really not happy about this.  This feels like a gauntlet.  Definitely not a defensible position.



Hayley is looking around and sees something just as Carruthers chimes in.  {\color[RGB]{153,0,255} ::It's a large lizard or snake with claws and... wings?::} 



Hayley sees a large tile with an elaborate red and gold image on it.  It doesn't immediately seem like a lizard but she can see that it is a thing with wings and she stops immediately in front of it.  Jaya stops too, careful not to run into Hayley, and retracts her blade.



Somewhere in the fog of ahead of us, we get the sense that there is a stairway and beyond that a looming darkness, like a tower of some kind.  There is a baleful diffuse red light from the tower.  The light changes and brightens, like some sort of giant eye opening.  We hear something start to move.  There are... odd noises.  We hear what our brains decide is dusty fabric dragging across the ground.  The glow gets slowly brighter and then starts to slowly, smoothly, descend.



We hear a voice say, ``Remove your masks, little ones.''

Jonah removes his helmet.

Hayley puts her hand to her helmet latches and looks over at Jaya.Jonah looks at Jaya, ``That means helmets off.''

``Fuck,'' mutters Jaya.  ``Maybe try to hold your fucking breath.  Jonah, you dying here?''

``Not yet sir.''

``Fuck,'' grumbles Jaya again and starts taking off her helmet.  In her head she rages  {\color[RGB]{255,0,0}::Fucking hate when people use that language.  I'm NOT a fucking little one.::} 

Hayley removes her helmet and fixes her hair with a practiced toss of her head.  Javier also removes his helmet.



Once we are helmet-less, everything seems much more vivid, and the light more ominous.   The dampness of the mist clings to us.



We see a shape begin to form out of the mist and darkness.  There is a sparkle of red light that passes over our eyes.



\textbf{{[}}\textbf{\hl{King in Yellow}}\footnote{\textbf{Suko T }http://simply-sithel.tumblr.com/image/110819349269 \textsubscript{02/23/15 2:16am}}\textbf{ is activated.  20 Tokens enter the pool.{]}}



\textbf{{[}20 Tokens remaining{]}}




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 6
\item Challenge 2: Don't get caught by claw.. Air of Command 3 (Jaya) → Overcome! \textbf{2 VP (Jaya)}
\item Challenge 1: Avoid shrapnel. Trigger Reflex 2 (Jonah) → Overcome! \textbf{1 VP (Jonah)}
\item 3 Scenes
\item Pool: 3
\item Pool: 3+10 (Page in Brown)
\item Challenge 1: Notice.  6th Sense 1 (Jaya) → Matched
\item Refresh: Air of Command 3 (Jaya)
\item Challenge 3: Don't let the spider get Javier.  Left Arm 3  → Matched
\item Challenge 1: Notice.  Concealment 1 (Jonah) → Matched
\item Challenge 3: Blow off one of the spider's limbs.  Small arms 2 (Jonah) + Gauss Pistol 2 (Jonah) + Small Unit Tactics 3 (Jonah) → Overcome! \textbf{3 VP (Jonah)}
\item Challenge 4: Defend the train.  Pulse Rifle 3 (Hayley) + HUD 4 (Hayley) + Grenades 2 (Hayley) + Snap Reflexes 2 (Hayley) → Overcome! \textbf{4 VP (Hayley)}
\item Refresh: Gauss Pistol 2 (Jonah)
\item Challenge 1: Notice.  Binoculars 2 (Jaya) → Overcome! \textbf{1 VP(Jaya)}
\item Challenge 2: Convince Leibowitz to answer.  Gorgeous 3 (Hayley) → Overcome! \textbf{2 VP (Hayley)}
\item Pool: 0+20 (King in Yellow)
\item Pool: 20
\end{itemize}




\jumpHeadline{VP Totals }

Hayley 6

Jaya 3

Jonah 4


\jumpHeadline{Quotes: }

\quotedDialog{
Ion: Can you be your own Operator?

Rebecca: She swings both ways.

Suko: Yeah, she does.

Ion: That's just \textit{unnatural}.

Suko: Hey, gotta be adaptable. It's the fuuuuuture.

Rebecca: It's the future, Jonah.

Suko: Get with the program, Jonah.\\[4mm]
}


Rebecca: I don't feel comfortable with someone smiling at me so as soon as she's in reach, I'm fucking slugging her.\\[4mm]


\quotedDialog{
\hl{Rebecca: We're going to spirit-chain you awake!  I'm going to pray you well.

Suko:  Hallelujah!  Praise Gerhauser!}\footnote{\textbf{Nathaniel Ford }Lulz \textsubscript{02/23/15 3:16am}}\\[4mm]
}

\quotedDialog{
Jonah: Why does the plate help?

Rook: Mostly because I need to boost her signal because she's... insensitive.\\[4mm]
}


Rebecca: I like how our \textit{medic }is starting the fight.  We shouldn't have given him a gun.\\[4mm]


\quotedDialog{
Jonah: Apparently, they don't seem to mind being injured. That's unexpected.

Jaya (with a shrug): I dunno...I lost an arm and I kept moving.\\[4mm]
}

\quotedDialog{
Rebecca (regarding Jonah quizzing Rook): It's a battle of the most questions person \hl{against the most evasive person}\footnote{\textbf{q.google }Rook \_answers\_ questions.  It's just that he doesn't give you his cribsheet for what the answers \_mean\_. \textsubscript{02/25/15 4:33pm}}.

Suko: Fight!\\[4mm]
}

\quotedDialog{
Ion: I will radio Rook.

Suko: Warning!  The buildings are super nice here!

Rebecca: Let's move in!\\[4mm]
}

\quotedDialog{
Rebecca: We getting some Sauron action?

Nate: A bit like that...

Ion: No one has a ring, right?

Nate: Javier says (in surprise), ``Uh, hey, what's this in my pocket?''
}

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 4:51pm
\end{flushright}

