\setcounter{chapter}{ 40 }
\chapter{\textbf{``The Beacon, part 2''} }




\begin{center}
 {\LARGE \textbf{(a.k.a. The King in Yellow)} } 
\end{center}




\textit{Notes:} Suko\footnote{\textbf{Rebecca S. }Let the record show that Suko posted this transcript for public reading at 5:29am, on a work Monday. And will be playing 4T later that night.  
``How is she even alive?'' asks Adam... \textsubscript{03/09/15 8:30am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }We would all like to know. \textsubscript{03/09/15 8:59am}}\footnote{$\rightarrow$\textbf{Suko T }Made an agreement with the King in Yellow probably.  And/or caffeine and broken circadian rhythms. :) \textsubscript{03/09/15 10:45am}}

\textit{Date:} Feb 25th, 2015



Rook backstory!  So.  Many.  Tokens.





\noindent\hrulefill




\sceneHeadline{Our Gear}

Jaya

Transit Authority MOPP Battle Dress Uniform (3)

Vacuum-sealed Infantry Heavy Combat Armor (4) 

AMP (Automated Medical Pack) (3)

Hush Radio (1)

\textbf{2x} Gauss Pistol (2) (pistol and extra ammo)

HE Grenades (2)

Alloy Cannon (3)

Rangefinder Binoculars (2)

Heads-up Display (4)



Jonah

Transit Authority Battle Dress Uniform (2)

Vacuum-sealed Infantry Light Combat Armor (3)

HESP Radio (2)

\textbf{2x} Gauss Pistol (2) (pistol and extra ammo)

HE Grenades (2)

Heavy Pulse Rifle (3)

Electronic Bypass Kit (3)

Heads-up Display (4)



Hayley

Transit Authority Battle Dress Uniform (2)

Vacuum-sealed Infantry Light Combat Armor (3)

AMP (Automated Medical Pack) (3)

Hush Radio (1)

Gauss Pistol (2)

HE Grenades (2)

\textbf{2x} Heavy Pulse Rifle (3) (rifle and extra ammo)

Hand Arc Welder (2)

Heads-up Display (4)





\textbf{{[}20 Tokens in the pool{]}}



Retcon: We left Javier at the gate to watch Leibowitz.



The voice addressing us doesn't appear to come from any particular place.  When the red light passes over our faces, we feel like the world skipped a beat.  Hayley is standing in front with Jonah and Jaya one pace behind her.  None of us want to really move from the spots where we are standing.  We're not paralyzed, we just... don't want to move.  



The figure is about 25 paces away from the dragon tile/Hayley.  He is the tallest humanoid figure we've seen, maybe just shy of 8 feet tall.


\sceneHeadline{Hayley}

The voice, still seeming to come from everywhere and nowhere, says, ``The one in front, the Weapon or the Warrior, you may approach.''

Hayley can move.  Jaya and Jonah are conscious but cannot move.  Hayley looks over her shoulder at Jaya and when Jaya doesn't say no, Hayley steps forward exactly three paces and stops.  She keeps her gaze fixed on the ground before the figure.

``Perhaps you would care to announce your intention?'' says the voice.



Keeping her eyes downcast respectfully, Hayley takes a breath and says slowly but clearly, ``We wish to go to the Silver Trail, Your Royal Highness.'' 

Its head inclines ever so slightly.  There is a the faint smell of wildflowers that all of us can perceive.

``That's an interesting quest,'' says the King in Yellow.  ``Certainly one I've seen tried before.  Tell me why one would do such a thing...as walk the Silver Trail.''



Hayley clears her throat and says carefully, ``I cannot speak for anyone else, Your Majesty, but we seek what we think is at the end of the Silver Trail.''

``Hmm.  Hunting wounded bears,'' says the King in Yellow. thoughtfully. ``Interesting notion.''  A pause. ``And you come at the behest of Tertius?''



At this, Hayley casts a glance back at Jaya.

``I spoke to you!'' booms the voice and there is the smell of brimstone.  There is a faint reddish tinge to our vision.

During this Jaya is babbling to Lackovich in her head  {\color[RGB]{255,0,0}::Lackovich!  What are we gonna do?  What are we gonna do??::  } 

At the booming voice there is a spike of interest from Lackovich.  This whole situation makes Lackovich uneasy and she has her hackles up.   {\color[RGB]{74,134,232}::If it were } \textit{ {\color[RGB]{74,134,232}me} } {\color[RGB]{74,134,232}, I'd let Jonah talk, but we'll get through it.  Just don't say anything rude.  \textless pause\textgreater .  If you're } \textit{ {\color[RGB]{74,134,232}about} } {\color[RGB]{74,134,232} to say something rude, let me know.::} 

Unaware of this conversation, Hayley brings her attention back to the King in Yellow and says, ``Not as far as I understand it, Your Majesty.''

``Then who?''

``The Transit Authority of the Directorate, Your Royal Highness,'' says Hayley.

We hear a low snicker that echoes from different directions.  ``I see.  Fair enough.'' says the King in Yellow.  ``The Transit Authority of the Directorate wishes you, Little Weapon... or was it Warrior?, to walk the Silver Trail.  And then...'' he looks at Hayley.  Even though her gaze is cast firmly down, the camera angles during this whole conversation have been weird and she can see that he is looking at her directly.  He gestures and a red light passes over her face and she is \textit{Paused}.  



Carruthers has been an agitated ball of stress through this whole thing.




\sceneHeadline{Jaya}

The King in Yellow's attention focuses on Jaya and all of a sudden she can move.  Her wrist on her left arm starts spinning madly with a whirring noise.  This captures the interest of the King in Yellow and he looks at it curiously.  Jaya stands at military parade rest, but her gaze bounces all over the place, looking up,down, to the side, pretty much everywhere.  Lackovich mentally takes control and forces Jaya's gaze to settle down and look at his feet.  Jaya lets her but grumbles a bit.

``Bearer of the Apparatus, \hl{Sleeping Name}\footnote{\textbf{q.google }??? \textsubscript{03/16/15 3:58pm}}, you may approach,'' says the King in Yellow.

Jaya doesn't move immediately, she looks over at Jonah and then feels a swift kick to the butt.  Jaya stumbles forward.  She takes three steps and is about to take a fourth step to catch up to Hayley but Lackovich pulls her back.  There's a moment where Jaya sways, as they fight for balance.   {\color[RGB]{74,134,232}::Fucking relax!::} 

 {\color[RGB]{255,0,0}::}  {\color[RGB]{255,0,0}\hl{It's my fucking body}} \footnote{\textbf{q.google }So how \_does\_ he do that?  And can he do it to people who aren't on a VTX? \textsubscript{03/16/15 3:58pm}} {\color[RGB]{255,0,0}!::} 

There's a sensation of wind, a restless stirring, even though there's no movement of air, and the faint tinkling sound of broken glass or windchimes.  Jaya's foot goes back down, not taking the fourth step.

``You too, seek to walk the Silver Path for this Directorate of yours....'' says the King in Yellow.

``Yes sir!  Yes we do.  Yes, your Majesty sir...'' says Jaya, looking up and then hastily pulling her gaze back down again.  Looks over at Hayley and then looks back down again. ``Yes Sir, Majesty Sir.''

``And you come, bearing a... very interesting piece of equipment.''

Jaya flexes her hand but doesn't say anything.

``One might almost call familiar, though it has been a long... time....'' the voice ends on a whisper.

Jaya looks up in surprised confusion and then looks down again, ``That's- That's very interesting, Sir Majesty Sir!  You know it's quite familiar to me by now but if you wanna share any information, I'd be \textit{very} interested in any information...about the hand...'' she looks up, looks down. ``Sir. Thank you....''

The King in Yellow says, ``Yes... let's share information'' and suddenly the camera angle is very far away.  ``Let's share information that.... could be of interest.  Why don't you tell its story and perhaps I can fill in a few details for you.  Perhaps not....''

``Uhhhhh.... Uh.....''

 {\color[RGB]{255,0,0}::He wants me to tell him a story, what the fuck is he talking about?::} 

 {\color[RGB]{74,134,232}::He wants to know how you lost your arm and how you got a new one.::} 

 {\color[RGB]{255,0,0}::That's not a fucking story!::} 

Jaya clears her throat, ``Uh... well you know I was in this fight and uh...there were these guys... and my team was in danger...''

``\hl{Take one step back}\footnote{\textbf{q.google }This is what happens when you check social distance to too many degrees of precision. \textsubscript{03/16/15 4:00pm}}!'' commands the King in Yellow.

Jaya shuts up and takes one step back.

``Now tell me about the equipment,'' says the King in Yellow more calmly.

``It's- it's attached to my arm!!'' Jaya looks all around and a vein starts throbbing in her forehead as she starts getting angry. Her tongue fidgets with her new tooth, which glints visibly through her grimace.



The camera suddenly zooms in close and the figure leans forward. Even though it's still about 23 paces away, it feels close and Jaya instinctively leans back.  There is a sensation of tingling.  The King in Yellow says slowly, ``And.... the tooth as well... is of interesting manufacture.''

Jaya looks around and brings her flesh hand up to rub her tooth.  ``Oh that?  There's no story...There was another brawl... It's cool.  Uh....should I take another step back?  I can take another step back.''  Jaya looks back at the gate behind her.

``Stay where you are,'' says the King in Yellow.

``Yes sir, Majesty sir.''  Jaya looks up and then back down again. ``If you are looking for a story I recommend, uh.... uh....'' Jaya can't remember Jonah's name so she just gestures in his direction.

``\hl{So he is in command of your unit}\footnote{\textbf{q.google }He's never heard of having diplomats speak for executives?  Happens all the time. \textsubscript{03/16/15 4:03pm}}\footnote{$\rightarrow$\textbf{q.google }Jonah is Broca's area.  Jaya is the amygdala. \textsubscript{03/16/15 4:04pm}},'' says the King in Yellow.

``NO.'' says Jaya instantly, glaring at him with angry eyes before she drops her gaze. ``No. I am Senior...uh...\textless pause\textgreater ''

 {\color[RGB]{74,134,232}::Agent::} 

``I am the Senior Agent and commanding officer on this operation.''

 {\color[RGB]{74,134,232}::That's not true::} 

``\textit{Shut up!}`` Jaya mutters aloud to Lackovich, having a hard time keeping the verbal and mental conversations straight.  She says more loudly to the King in Yellow, ``I am currently in charge of this expedition and I am here to make sure we optimally succeed and make sure we achieve all our objectives optimally-''

The King in Yellow interrupts, ``Because I know your servitor...\textless pause\textgreater  your servant... looked to you with great expectation.  As if you could answer the questions she could not.''

``Oh yeah, I can definitely answer all of Hayley's questions,'' says Jaya with bravado. ``Definitely... Hayley looks up to me in a lot of ways and I feel I'm a good role model for my team...''

 {\color[RGB]{74,134,232}::Stop talking. Stop talking NOW.....  Your Majesty.::} 

Jaya cuts herself off and adds, ``Your majesty, sir.''

``Why the Silver Path then?  To what end?''

``Uh... to the end of activating the Beacon... to achieve our mission objectives,'' says Jaya, looking around again.

``And... you.... wish what?'' asks the King in Yellow.

``To activate the Beacon,'' repeats Jaya.

``Yes you've made that very clear.  Take one step back.''

``Thank you sir, very much sir!'' says Jaya rapidly and takes a big step backwards.  A red light plays over her face and she is \textit{Paused}.

 {\color[RGB]{255,0,0}\hl{::I think that went well.::}} \footnote{\textbf{Suko T }I feel that, just like when Hayley said the same thing, Lackovich probably thought, ``I think you would be wrong.'' \textsubscript{03/09/15 2:47pm}}




\sceneHeadline{Jonah}

``\hl{Interlocutor}\footnote{\textbf{q.google }What's with the big words?  Speak pidgin, like normal folk. \textsubscript{03/16/15 4:06pm}}.  Watcher,'' the King in Yellow and Jonah can move again.  ``You may approach.''

Jonah takes three steps forward, lowers his head and says, ``Your Majesty.''

``Let us begin by clearing up one detail, if you can, that is of interest to me.  Her arm, her tooth... what are they, who made them?''

Jonah says slowly, ``I do not know who made them, but I know how she acquired them.  \hl{Is that sufficient}\footnote{\textbf{q.google }Bleh.  Jonah is hanging around Rook and the Gerhausers too much. \textsubscript{03/16/15 4:07pm}}?''

``Let us begin there.''

``We were in a great fight.  With a great deal of gunfire and many things moving... hard to track.   There were portals and we had no familiarity with them, at least not that we knew.  A portal appeared through which our enemies tried to escape-''

The King in Yellow interrupts, ``Your enemies?  Perhaps you will be more specific?  I have my guesses but...''

``They are called Octavius.''

``Yes.  Continue.''

``They are invading our home.''

``Yes \hl{Octavius is quite mad}\footnote{\textbf{q.google }I'm not sure if that should be alarming, that Brother-to-Rook, who hangs out in a huge asylum for wayward mecha building high-tech sandcastles, thinks Octavius is mad. \textsubscript{03/16/15 4:09pm}}\footnote{$\rightarrow$\textbf{q.google }On the other hand it might be a little comforting that he doesn't think Octavius is \_sane\_.
``We're all mad here.  If you weren't mad you wouldn't be here. \textsubscript{03/16/15 4:10pm}},'' says the King in Yellow with an indulgent laugh.  Jonah has a sensation of cherry blossoms falling, something he is completely unfamiliar with.  And yet he also has a weird deja vu feeling that this \textit{is} something he is familiar with.... but he doesn't know what they are. And then that feeling is gone.

Jonah says, ``The Agent attempted to capture one of them and grabbed them but they were already through the portal and it closed.  I'm not an expert on portals but it's my understanding is that this is never a good idea and what this one did was remove her arm.''

``Yes, I have experienced something similar,'' says the King in Yellow.

``\hl{Oh!}\footnote{\textbf{q.google }Let me elaborate on that: Wait, \_what\_?  Oh do tell!

We can name this Spatial Dysplasic Limb Syndrome. \textsubscript{03/16/15 4:12pm}}`` says Jonah surprised.

``But the one she has now...'' says the King in Yellow.

``Was given to her by our superiors as a replacement,'' says Jonah.

``By the Transit Authority of the Directorate?'' 

``\hl{That is who we \textit{work for},'' says Jonah carefully.  ``Our superiors are.... part of them but are from far away and not part of the Directorate.  Originally.}\footnote{\textbf{q.google }If that seems like TMI from Jonah, he's going on the fact that Rook told them to be open, and secondarily that being even slightly uncooperative seems to have gotten the others in trouble.  He is opting to give extra information so as to be able to hold back actually critical information if asked later, and not seem like he is being generally uncooperative. \textsubscript{03/16/15 4:15pm}}''

``Superiors.....'' murmurs the King in Yellow thoughtfully.  He says more loudly, ``You may approach.'' 

Jonah takes three more steps forward and is now two paces ahead of Hayley.  ``Your Majesty.''

``Perhaps, as we are being so open and sharing information... there are things I can share with you...'' says the King in Yellow.

``Are you asking what I want to know?'' asks Jonah.

``No,'' says the King in Yellow.  ``But you may tell me.  You have my permission.''

``We would like to know how to get on the Silver Trail to reach our destination.  I am curious about things but they are not as important as what \textit{we} want to know.   \hl{I will elaborate on those if you want}\footnote{\textbf{q.google }''You have permission to give me permission to ask you lots of questions instead of you asking \_me\_ lots of questions.'' \textsubscript{03/16/15 4:18pm}},'' says Jonah.

``As it happens....you've come to the right place to fulfill your foolish quest.  I can... construct a map for you to the Beacon.  If you are truly bent on this objective.  Whether I \textit{will} is a different question. \textless pause\textgreater   But as we begin to discuss what it is that we wish to know, what it is that we are willing to do....then we may come to some sort of arrangement.''

``That would be excellent, your Majesty,'' says Jonah and he is \textit{Paused}.




\sceneHeadline{Hayley, sans Jaya and Jonah.}

A more intense red light passes over Jaya and Jonah's faces and it's as if they fell asleep for a moment.  They are not cognizant of what happens with Hayley next.  



Hayley is a little concerned that Jaya and Jonah's eyes seem to become unfocused and their shoulders slump a little.  They aren't appearing to react to anything that happens next.



``You may approach, little one,'' says the King in Yellow.

Hayley takes another three steps (now one step ahead of Jonah), her eyes still firmly fixed at the the King in Yellow's feet.

``You have many hands upon you,'' comments the King in Yellow.  ``Some present, some past... Some barely perceptible...some you wear like a robe.''  There is a dusty smell.

Carruthers feels distant from Hayley all of sudden.

The King in Yellow continues, ``Tell me, what do you want?  Do you want to be the Weapon?  Do you want to be the Warrior?  Do you just want to walk the Silver Path as your superiors want you to?  Do you question why?''

Hayley looks thoughtful through these questions.  ``Your Majesty, these are questions that I have...not thought of before.  I-''

``So think.  We have nothing but time.''

 {\color[RGB]{153,0,255}::Uh... Lackovich is acting funny... Sorry!  Not to alarm you.  Stay calm!  Stay calm.::} 

 {\color[RGB]{255,153,0}::Huh?::}  thinks Hayley cleverly as her thoughts are derailed, but she refocuses on the King in Yellow.  Carruthers can feel her thinking of several replies and rejecting them rapidly.

``I want... not to be afraid,'' says Hayley slowly.

 {\color[RGB]{153,0,255}::Be specific.::} 

``What makes you afraid?'' asks the King in Yellow.

``It seems like everything... is frightening.  Unfamiliar.  And... and painful.''  Hayley falls silent.

``What is it that pains you right now?'' asks the King in Yellow.

Hayley doesn't reply for several long seconds, thinking over her answer carefully.  ``I... I don't.... think I'm in pain right now, Your Majesty.  Not any more than usual.''

``When you stepped forward, your gait was uneven.  An old wound?''

Hayley frowns, ``Not old.  Not to me, your Majesty.''

``Then a new wound?''

``Yes, yes that is correct,'' says Hayley firmly.

``Not old to you... So.  A wound with history....''

``Yes!'' says Hayley looking delighted. ``Yes, yes it is.''  She pauses and adds, ``If I may clarify, Your Majesty... it has memories.''

``Yes....'' says the King in Yellow softly.  The air lightens with a diffuse glow.  ``Memories.  Everything is threaded together with memories....  The present is made of memories one stitched to another, all woven together.  That is what we're made of.  \textless pause\textgreater    And it so happens I have a knack for following them back to.. the source... To re-live.  To see with new eyes the beginnings.  Or at least to follow the thread back to see the truth.  To meet again the ones that we knew, that we loved. \textless pause\textgreater    I just wanted you to know that.''

``Thank you, Your Majesty,'' says Hayley with a pleased smile.  ``That is... very kind of you.''

``No... I have not done you any kindness yet.  But I may.... if you desire it.''

Hayley tilts her head curiously, still not looking up at him, and says hesitantly, ``I... do prefer it. Your Majesty.''  She adds, ``But I don't expect it, your Highness.''

``If you will tell me, specifically for a change, who it is that leads you, that has sent you to me... then I would happily do you a kindness.''

Hayley blinks in surprise and clears her throat. ``The person who ordered this mission is our commanding officer-''

 {\color[RGB]{153,0,255}::Uhhhhh....:: } there is a wave of anxiety from Carruthers.

 {\color[RGB]{255,153,0}::What?::}  thinks Hayley in confusion/alarm.   {\color[RGB]{255,153,0}::He asked a question- I was not aware it was a secret?::} 

 {\color[RGB]{153,0,255}::It's not but I feel weird...::} 

 {\color[RGB]{255,153,0}::Oh.  Okay.  Hmm... specifics....::} 

After a confused pause, Hayley continues, ``Ah!  And also my contract holder, Agent Morgan-''

 {\color[RGB]{153,0,255}::Agent Morgan Gerhauser::} 

 {\color[RGB]{255,153,0}::Ah yes, full name, thank you.::} 

``Agent Morgan Gerhauser,'' amends Hayley aloud.

The figure cocks his head curiously to one side.  He seems further away.  The camera switches to an overhead view above the two of them.  ``And she made this armor?  The hand?  The tooth?  All the marks of authority that that you carry upon you... the art...are hers?''

Hayley looks puzzled, ``Uh, they are hers by right of her control over the location and the resources within. But as for making them.... I believe others manufactured them, your Majesty.  I am sorry if that's not what you were asking.''

``Perhaps they were simply salvaged from the dust of history.  That is the likeliest explanation.  \hl{Take three steps back and have your memory}\footnote{\textbf{q.google }Following Nate's often stated dictum that ``there are no psionics in this game'' I'm guessing again that the KiY can't do that to just anyone.  One has to have VTX connection or other network to tap into.

I'm also guessing that while he \_can\_ dig into memories without permissions he (apparently) prefers not to, and also finds it easier if the person in question is cooperating. \textsubscript{03/16/15 4:25pm}},'' says the King in Yellow quietly.

Hayley takes three steps back and is again two paces behind Jonah.



Hayley feels that the King in Yellow is trying to meet her eyes so she raises her gaze up to meet his, slowly, for the first time.



There is a flash of different memories, most of them connected to her leg.  A lot of them involve Oliver, some of them recent, but others go all the way back to the things Oliver experienced while Hayley was in his head.  Another branch of memories concern Hayley's own scars.  Interspersed in all this are a few other memories, very brief.  One is of Drake's hand on her leg. The others are a conglomeration of several memories, a mix of of Trenton's hand on her leg, the sensation running through... a hospital? and the intense pain from when her shoe slips out from under her and she falls very badly on her right leg.



The memories start stabilizing.  First, the sharp visceral feelings evoked by the memory of Oliver reliving being shot, and her memory of dying with him afterward. Then an echo from that carries her to countless nights spent thinking about dying and the pain of her own wounds, her scars.  Both branches of memories find the the pain that she keeps with her always and finally coalesce in the Cistern.



Hayley finds herself in the \hl{Cistern}\footnote{\textbf{Suko T }In the session, Nate noted that the Cistern was familiar to the KiY. \textsubscript{03/09/15 3:17pm}}\footnote{$\rightarrow$\textbf{q.google }Huh. \textsubscript{03/16/15 4:25pm}} again with Oliver.  He's in the water, looking up at her.  Hayley is standing on the ledge.  He is convincing her to jump in.  He beckons to her, ``No no, it's perfectly safe! The ledge is right here and I can catch you when you land.  I can hold you up if you have any trouble.  It's not that bad.''

``But I know- yes.''

``It's a little cold,'' admits Oliver.

``I remember this...'' Hayley says as she jumps in, but this time knowing how to swim, she doesn't nearly drown herself.

``See! You took right to it,'' says Oliver encouragingly, sounding a little surprised.  Hayley smiles happily at him and says nothing.  Oliver helps Hayley over to the ledge and they tread water side by side.  His hand lingers and he looks at her like he did last time.  But this time Hayley can read his expression and she sees that he is hungry for innocence and there's something in Hayley's seeming-naivete and innocence that is very attractive to him.  His hand rests on her arm just a little too long, long enough that even Hayley can sense that it is skirting that fine line between little sister and something else.  

Not perturbed by this, Hayley's smile grows even wider and she says, ``I really miss you.  And I remember.''

``What do you mean, 'you miss me'?'' asks Oliver, puzzled, as he pulls his hand away.

``I.... I mean...'' hesitates Hayley.

``You are here with me right now,'' says Oliver softly.  

``Yes I am!'' says Hayley, pleased.

``There is no one else here.  That's why I like this place.  It's... private.''

Hayley is reminded of the memory of the last time she was in the Cistern with Oliver and she looks at the water level in alarm.  It hasn't changed and she is filled with the certainty that Octavius is not here.  \hl{Though, oddly, she is also certain that Rook \textit{is}}\footnote{\textbf{q.google }Hmm.  Given later conversation: \_which\_ Rook?  The KiY might count as \_a\_ Rook. \textsubscript{03/16/15 4:26pm}}.

``Huh,'' says Hayley when that thought occurs to her and she starts turning around to look for Rook.

``Is something wrong?'' asks Oliver.  As she turns, he says in alarm, ``Your back!''

``Oh!'' Hayley turns back to him in surprise and then relaxes.  ``Yes...you know...''

Oliver's hand starts to trace her scars, ``Did someone do this to you?''

``Do you not- Oh...''

Oliver pulls back and his constellation shifts.  Hayley somehow knows that his mind flashes to Dr. Gerhauser for a second, accompanied by a feeling of confusion.

Hayley looks sad.  ``I didn't... I didn't get to tell you.  So you wouldn't know.''

``Wouldn't know what?  Hayley, you are very strange.  Sometimes.''

``I know, I know.  I still don't know why you like it,'' says Hayley honestly.

Oliver gives an awkward shrug.  ``I don't know why I do a lot of the things that I do.''

``Neither do I,'' Hayley smiles cheerfully.

``I won't let them hurt you, Hayley,'' promises Oliver.

``I know,'' says Hayley in a small voice.  Then, more confidently, ``You didn't.''

The scene starts to attenuate and Hayley can feel it growing distant.

``Goodbye,'' she says.

``I'm right here,'' she hears him say.



And the scene is gone and Hayley is standing where she was before, in the misty courtyard before the King in Yellow.  \hl{There is something tickling at the back of her mind about Oliver though.}\footnote{\textbf{Suko T }So curious to know what Hayley will realize about Oliver!  Am I getting a new/different flaw? \textsubscript{03/09/15 3:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Wait for it. \textsubscript{03/09/15 3:20pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Flaw: Crushing For A Dead Man (weak) \textsubscript{03/09/15 3:38pm}}+1



``Is that what you were hoping for?'' asks the King in Yellow.  ``Is that what you were hoping would ease the pain a little bit?''

``It made me happy, Your Majesty,'' says Hayley with a contented expression.

``There is so much more we could explore, should you prove yourself worthy.''

``I would like to, Your Majesty,'' says Hayley honestly.

 {\color[RGB]{255,153,0}::Is Lackovich okay now?::} 

 {\color[RGB]{153,0,255}::She has it under control.::} 



The King in Yellow makes a gesture, a flash of red light and Hayley is on \textit{Hiatus}.




\sceneHeadline{Jaya, sans Jonah and Hayley}

In the back of Jaya's head is the rising sound of a scream.  When she ``wakes up'' again, the scream breaks off with a gasp.  The fires of Lackovich's anger feel a little muted.

``You may approach,'' says the King in Yellow.

Jaya counts under her breath, and steps forward 3 paces, drawing even with Hayley.  In her head she goes through a little mental checklist.   ``Okay I've approached, Your Majesty,'' says Jaya, and for good measure repeats, ``Your Majesty.'' and checks that off the list.  She keeps her eyes fixed on his toes, even though they are kinda grody peeking out from under his rags.

``So you serve... Morgan.''

``Uh.. yes.  Sir majesty, I do report to Morgan.  Gerhauser.  \textit{Agent}.  Morgan. Gerhauser.  Yeah,'' says Jaya.

There is the scent of salt in the air, and the feeling of pressure, as what might precede a storm.

``So \textit{she} is the one who seeks the Beacon.''

``Uhh..... \hl{really it's a group effort... we came to a consensus as a team}\footnote{\textbf{q.google }That's actually true. \textsubscript{03/16/15 4:28pm}}...''

 {\color[RGB]{74,134,232}::Just say yes.::} 

``-Er.   Yeessss,'' says Jaya slowly.  She works her jaw for a second and then adds with growing force, ``But we really did come to a team consensus.''

 {\color[RGB]{255,0,0}::Fuck you Lackovich!  } \textit{ {\color[RGB]{255,0,0}I'm} } {\color[RGB]{255,0,0} on this mission.:: } 

Jaya continues with a swelling sense of - perhaps poorly placed - self confidence, ``And we were presented with multiple options and you know, the whole end objective...we were informed that we would be assisted by the completion of this mission... so we, uh...what was the question?'' Her gaze flicks up and then back down again and she presses her lips together, content now that she decided to stop talking on her own and that she most likely answered the question- whatever it may have been.

``You wish to be part of a team then?''

``I \textit{am} part of- I am actually \textit{leading} a team.  I am the current \textit{team leader}.  Of both Patrol Group One and this expedition right now.  I'm currently reporting to \hl{Rook}\footnote{\textbf{q.google }That's the first mention of Rook to the KiY?  Not that it matters much, he would've gotten it out of someone no matter what. \textsubscript{03/16/15 4:30pm}} but that's just part of this mission. Temporarily.''

 {\color[RGB]{74,134,232}::Jaya, there's movement in the mist, it's different than before.::}  There's a sensation of a chill from Lackovich. 

Jaya's blade pops out and stays out this time.  The King in Yellow's attention is almost involuntarily pulled over to her arm again.

``Er... sorry!  This is a slightly, uh... \textit{emotionally distressing} situation...uh...just give me a second... I can make it go down...'' Jaya take some deep breaths and tries to focus.

``I know that mechanism,'' says the King in Yellow.  ``That was \textit{his}.''

``Uh.... okay...'' says Jaya, distracted, still staring at her arm.  ``Just gimme a second.''

{[}\textit{Refresh: Left Arm 3 (Jaya)}{]}

``Do you truly not know where it came from?'' asks the King in Yellow.

``I dunno... Rook pulled it out of his room of... stuff.  He's got lots of stuff.  I mean-''

``Finally then, we agree that it's my brother's handiwork,'' interrupts the King in Yellow.



Jaya raises her head and blatantly looks the King in Yellow up and down dubiously and says, ``No, I think you're confused.  Rook is... uh...'' and Jaya makes a gesture of Rook's approximate height (significantly shorter than herself).  She is grinning with amusement, thinking to herself that the idea is absolutely absurd.

The mist grows thicker, hazier, and blue-ish, and it becomes harder to see.

``Fucking hate mist,'' mutters Jaya under her breath as she sweeps her gaze left and right through the mist, certain it's crawling with problems.

``Make that gesture again,'' says the King in Yellow.  ``His height.''

Jaya pauses.   {\color[RGB]{255,0,0}::Shit! Did I fuck up?::} 

 {\color[RGB]{74,134,232}::Oh you want me to help } \textit{ {\color[RGB]{74,134,232}now} } {\color[RGB]{74,134,232}?  I thought you were in charge of this mission.::} 

Jaya feels her hand rising again and she wrestles control away from Lackovich.  Jaya repeats the gesture but is now much more vague, indicating a range of heights.  ``Er, I've never been very good at heights, heh... spotting perps was never one of my strong points.''  Lackovich is feeling less and less muted.  ``Well you know... he's shorter than I am,'' says Jaya and then changes the subject. ``So we were talking about the Beacon.  And the Silver Path.''

``I suppose we were,'' says the King in Yellow thoughtfully.

``Yeah,'' says Jaya as she looks up and then looks down again and then looks at her hand.  The knife is still out and she says, ``Sorry.. this doesn't usually happen...  Your Majesty.  So are you gonna... show us that path?  You heard it now from all of us and you've got all the details and objectives and I feel you can, uh, render judgement or whatever and let us in.  'Cause this mist is coming in and I don't know if it's the same mist but I had some mist recently.... uh, I was wondering if maybe we could move locations to a \textit{less misty location}...\hl{I don't know if you're familiar with it but mist- sometimes ... people... die.''}\footnote{\textbf{Suko T }\textless 3 Jaya \textsubscript{03/09/15 3:39pm}}

There is the scent of cinnamon.  Jaya rubs her nose.

 {\color[RGB]{74,134,232}::Now is the time to calm down::} 

``I am\textit{ fucking calm}!'' growls Jaya aloud, turning her head to the side slightly.

``I am certainly prepared to bargain for the map that you seek.

``Excellent.  Excellent!  I brought my bargaining Agent.  I mean Operator.  Like, uh... team member?  I'll just let you negotiate with him... with my authority.  He can.. with our authority and the mission objective and Morgan's authority, I feel he will be able to bargain...''

The smell of cinnamon grows sharp, mixing with peppermint or something to gain a caustic burning edge.  The King in Yellow says disapprovingly, ``If you are in charge of the mission, as you keep insisting, then I will have dealings directly with \textit{you}.''

``Yes.  Very good sir.   Your majesty!  Yeah, let's, uh, bargain!'' says Jaya, rubbing her hands together  ``What do you...uh...''

 {\color[RGB]{255,0,0}::}  {\color[RGB]{255,0,0}\hl{How does he do this}} \footnote{\textbf{q.google }She should ask him.  If nothing else she can see him actually do a surprised double take. \textsubscript{03/16/15 4:32pm}} {\color[RGB]{255,0,0}?::} 

 {\color[RGB]{74,134,232}::} \textit{ {\color[RGB]{74,134,232}You} } {\color[RGB]{74,134,232} were in his head, not me.::} 

``Why don't we begin in which, you tell me about the place where you saw my brother.  And I, in return, would be happy to open negotiations for the Silver Path and the map thereto.''

Jaya frowns, ``When you say 'open negotiations', aren't we actively negotiating right now?''

 {\color[RGB]{74,134,232}::Do you accept his agreement or not?  Don't dilly-dally with fucking semantics.::} 

 {\color[RGB]{255,0,0}::I'm just trying to wrap my head around this! Jeez.  Calm the fuck down!::} 

``As you have not yet made any offers of any value to me, we are not negotiating.''

Jaya hazards a guess.  ``Uhh... okay.... well how do you like...guns?  We've got guns.''

 {\color[RGB]{74,134,232}::God you're such a fuck.::} 

Jaya sees movement all around her.  There are many autos clustering around. There are lots of odd shapes, a few auto-8s and some darker shadows further out.

The King in Yellow gestures grandly at the autos surrounding them.  ``I need no guns.  This place is mine''

``Yes, that's totally not....Okay... umm....how about some drugs?  Got some drugs.  Not a lot but...''

 {\color[RGB]{74,134,232}::Ask him what he wants.  } \textit{ {\color[RGB]{74,134,232}Not fucking drugs.} } {\color[RGB]{74,134,232}  }  {\color[RGB]{74,134,232}\hl{YOU want drugs.}} \footnote{\textbf{Suko T }Also \textless 3 Lackovich for this. \textsubscript{03/09/15 3:40pm}}\footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{03/16/15 4:33pm}} {\color[RGB]{74,134,232} It's not about what you want.  Ask him what HE wants.::} 

``Okay...uh....What...Do... You....want...Majesty.  Sir.''

 {\color[RGB]{74,134,232}::See, it's not that hard, you even added Majesty at the end.::} 

Jaya growls in her head.  {\color[RGB]{255,0,0}::Fuck.  Off.::} 

``I'm interested...very interested... in when you've seen my brother and where.''

``So...when you say 'your brother' you're jumping to the conclusion that I sorta mentioned someone named-''

 {\color[RGB]{74,134,232}::Don't question him!::} 

Jaya makes a frustrated noise and says in exasperation to the King in Yellow, ``Do you want me to talk about Rook?''  She looks up and makes eye contact, trying to see his reaction to this.

``Yes.   My brother,'' says the King in Yellow.  Jaya starts to speak and he talks over her, ``\textit{Also} of interest to me, because I like to have options in negotiations-''

``That's very generous of you,'' says Jaya and then mutters to herself, ``I often don't do that.''

The King in Yellow continues, ``Any among you who may wish to be knighted-''

``Is that... a good thing?'' Jaya gestures behind them.  ``It's not like those bubble tanks?  I don't think any of us are into that...''

``It need not interfere overmuch with your other duties, but it is a form of service.''

``Yeah so we're servicing some other people pretty hard, so why don't we... Rook.  Yeah. Good guy, Rook.  Not seeing a lot of family resemblance but-''

``It's been a long time,'' says the King in Yellow.

Jaya says, ``Well he's looking pretty good these days...and not... so... you want to know where I've seen him?  He runs the base.  Can't tell you where that is.  If I knew- well, I don't even know.''  She looks up and then looks down again.  ``Uh...but they won't tell me for some reason where the base is so I can't tell you where the base is. But he's usually hanging out at the base. SAC-09. As opposed to some of the other SACs.  \hl{Sometimes he's on a train...Sometimes he's not on the train. Sometimes fucking Jari drives the train.}\footnote{\textbf{Adam Kenney }Indeed, Jaya! Indeed. \textsubscript{03/09/15 6:12pm}}  But usually he's at the base. SAC-09.  But nobody knows where it is.  Is that cool?  We cool?  That good?  \textit{Great.}''

``Mmm... that is certainly a good start.  You may approach.''

Jaya takes one step forward.

 {\color[RGB]{74,134,232}::Two more.::}  says Lackovich as Jaya starts feeling a sense of vertigo.

Jaya takes two more steps and draws one pace ahead of Jonah.

``Very well.  One of three has been granted.''

``Wha-What?''

``One of three.  The name, the location and the keys of access.''

``What about the keys of access?''

``That, with your permission, I believe I could.... find.''

Jaya protests, ``I don't think we have any keys of access.  Jari keeps a pretty tight-''

The King in Yellow interrupts, ``We know so much.  That we don't know we know.  It's a part of us.  We couldn't recite it upon command.  But this I will do.  So one of three.  A good start.

``Uh... okay.  So how many is it going to take to get the map?''

``Three,'' says the King in Yellow.

``Really?''

``Or the other option of course.''

``Can we go over the option again?  Maybe with more details maybe?'' asks Jaya.

``Before we do, I would like to offer you a reward.''

Jaya says loudly, ``Uh... no that's... no... I feel pretty fine.  Let's just keep negotiating...or uh...how about if the mist went away?  That would be a pretty great reward.''

 {\color[RGB]{74,134,232}::I'll make sure to tell Morgan about your loyalty.::} 

 {\color[RGB]{255,0,0}::Fuck off!  I didn't even know we weren't supposed to mention SAC-09.  I'm under a lot of pressure!::} 

The mist recedes.  There is the scent of jasmine.

``Er, thanks!'' says Jaya.

``You have pleased me and I wish to reward you.  Are there pleasant memories that you would like to revisit?''``Uh, I'm pretty good on the memory... uh I revisit them a lot on my own.  I'm pretty good.  Thanks!'' says Jaya quickly.

``Things that have happened to you that you wish gain insight into?''``I've got all the insight I need.  I'm doing pretty good. Thanks,'' says Jaya.

Jaya hears an outburst of derisive laughter in her head from Lackovich.

Jaya says carefully, ``Thank you, Your Majesty, for the offer but let's uh... you rewarded me with the mist...feeling a lot better...''

``You have an interesting connection to Tertius' VTX.  But there are only \hl{six}\footnote{\textbf{Suko T }six?  Not seven?  who isn't being counted?  Jaya, Lackovich, Jonah, Carruthers, Hayley, Signe and Javier... or does he not count since he's not plugged in?  Poor Javier. \textsubscript{03/08/15 1:58pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Due to my messing up a detail, this number should actually be different, but I'm not sure I want to retcon it because I'm not sure how much y'all reacted to it. \textsubscript{03/09/15 9:23am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }But yes, poor Javier. \textsubscript{03/09/15 9:24am}}\footnote{$\rightarrow$\textbf{Suko T }Javier
Capability: Blessed 10
Flaw: Arcane (Strong)
Flaw: Not Davis (Strong) \textsubscript{03/10/15 12:44am}} of you now.  There used to be so many more.''

``Uhhhhhh okay.''

``Three are present. Why so few?  I knew he had been in decline, visited less frequently...''

``Ummmm, there are three people on this mission because that is the size of my team. We're sorta like a secret operation that operates below the radar.  We're not really overstaffed. I mean my Directorate is kind of at war right now-''

``Octavius, yes,'' says the King in Yellow.

``Yeah so that's why we're here for the Silver Trail map.''

``You know you're not the only one interested in this map.''

``Yep.  We heard that from brown robe.''

 {\color[RGB]{74,134,232}::Leibowitz.::} 

Jaya clears her throat and ignores Lackovich, ``Others, hoping to get the drop on us.  But we're hoping we can cooperate. We got some expert bargainers here...''

``Others have made rich offers.''

Jaya says quickly, ``Our offers can be rich!  We can be as rich as needed.  Or not... if that's not what you want.  Let's talk about this other thing, the service thing. What service can we provide for you here?''

``We shall discuss it momentarily.''



And Jaya is put on \textit{Hiatus}.




\sceneHeadline{Jonah, sans Jaya and Hayley}

Jonah ``wakes up''.  He sees that Jaya is now suddenly a pace in front of him and Hayley is two paces behind him.  \hl{He has the sensation of lost time}\footnote{\textbf{q.google }As noted elsewhere, while he doesn't show it, this makes Jonah very paranoid. \textsubscript{03/16/15 4:39pm}}.



``I've been very rude,'' says the King in Yellow, ``because I have not introduced myself or asked you your name.  You may call me, as others do, the King in Yellow.  What name would you like to be called, Watcher?''

``My name is Jonah.  Gemayel,'' replies Jonah.

``It is...'' says the King in Yellow, his tone not quite a question, not quite a statement.

``Yes.''

``And you are here in the service of Morgan.  Gerhauser.''

``That is correct.''

The King in Yellow mutters, ``\hl{She waits at the guarding of your death.}\footnote{\textbf{q.google }? \textsubscript{03/16/15 4:40pm}}``  His attention returns to Jonah.  ``And \textit{you} are here at her behest, and it seems at the behest of my \textit{brother}.  Though how that can be, I do not know.  To seek the Silver Path.''

``Your brother, Your Majesty?''

``My brother.  The one who made the arm, the tooth and whom I'm certain had some hand in the shells of armor that you wear.  Among other things....My brother... yes...'' his voice trails off and then he stays more strongly, ``And what are you prepared to trade for your access?  Will you tell me the location of SAC-09?  Will you grant me access to its keys?''

Jonah says slowly, ``I am prepared to exchange and bargain for as much information as I can, with some few limitations.  I cannot give you access to SAC-09 for two reasons. Your Majesty.''

``Just to be clear, 'cannot' is a very strong turn of phrase,'' says the King in Yellow.

``Yes.  I do not know where it is.  I have only recently come to understand even a little bit about how portals and trains work.  I believe it to be near to the Directorate.  To the best of my knowledge, it could be anywhere.  I only know how to get there.''

``You could tell me that, if you wished.  It could be part of our bargain,'' says the King in Yellow softly.

Jonah continues, ``The other is not a 'cannot'.  There are people there whose safety is my concern.  If they are at risk-''

``I have no ill will toward SAC-09... or its inhabitants.''

``You would not bargain away their location to Octavius, Your Majesty?''

\hl{``That could be part of our bargain.''}\footnote{\textbf{Suko T }Note to Jonah that I don't know that this was actually included in the final bargain (''the map and no more'') so he may wish to be paranoid for the safety of his family :) \textsubscript{03/09/15 3:46pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }For the record, it was. It was put on the table and not taken off. The KiY and Rook don't play dumb games like that. \textsubscript{03/09/15 4:18pm}}\footnote{$\rightarrow$\textbf{Suko T }Really?  That's good.  Because clarifying ``and no more'' seems like it is keeping the terms to just the map for knighthood.   We need a Fili. \textsubscript{03/09/15 4:55pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }A Fili would perhaps lack his particular sense of abstraction, but you can read it as, 'and no more additional conditions (beyond that which has been discussed)'. \textsubscript{03/09/15 5:02pm}}

``As I said, I am willing to tell you what I can about a great many things. \textless pause\textgreater  But I cannot risk the safety of the people in that place.''

``'Cannot' again,'' says the King in Yellow thoughtfully.  ``I understand.  You have your constraints, as I have mine.''

``Yes, I am obviously willing to hear any... any offers you wish to make, I will consider.''``I am interested as well in a form of... service.  I could knight...perhaps one... perhaps two of your number... depending on how many pieces of information you are willing to give me.  And that could also be acceptable in exchange for the map.''

``The map being the way to reach the Beacon?'' clarifies Jonah.

``Yes, as it is no small trouble for me to sift... to scavenge... to scour... to search... to decrypt..... its pieces which lie in so many different dreams.  So you come to me, hat in hand...''

Jonah realizes that they are literally holding their helmets in their hands.

The King in Yellow continues, ``I must have some service or.... well for one of my position there is very little information that interests me and I have told you what it is.''

``What form does such service take?'' asks Jonah.

``I am prepared to go into greater detail, but I don't wish to repeat myself so I will say it only once, and to the three of you.  Until that moment, there are a few more things I wish to discuss with you,'' says the King in Yellow.

``Very well,'' says Jonah.

``You've been very forthcoming.  Which I appreciate.  How is it, I wonder, that you came to bear so many marks, so many different hands upon you?  In particular, that you carry the VTX of Tertius.  \hl{All three of you are a part of Tertius}\footnote{\textbf{Rebecca S. }ugh, such an icky thought! makes the whole Agent/Operator thing even more icky! \textsubscript{03/09/15 9:30am}}\footnote{$\rightarrow$\textbf{Suko T }Hayley thinks it's awesome!  Brain-share for everyone!  Whee!!! \textsubscript{03/09/15 3:48pm}}\footnote{$\rightarrow$\textbf{q.google }Jonah does not like the idea at \_all\_.  He'd like it even less if he knew what Hayley knew about Tertius.

That might be a thing for him to poke at the Weird Sisters and Rook about. \textsubscript{03/16/15 4:47pm}}.  And three others not here.  How?  I thought him much larger.''

Jonah says, ``I will tell you what I know.  But what I know is hampered by my not completely understanding it.  There are questions or points that are unclear.  Please understand that there may be some detail that I am missing but don't know that I am missing it.  So please do ask.''  Jonah pauses, gathering his thoughts, and then continues, ``My understanding is that Tertius and Octavius are... similar but not the same.  They are able to form a connection between lives.  Octavius is many people.  Tertius... used to be?'' he ends on a questioning note.

``Yes,'' confirms the King in Yellow.

``And used to live where we live... but it is not-''

Jonah has the sensation of touching cold stone, of history passing.

Jonah continues, ``If it remains, we do not... the people that we work for have implied that it is not a significant player anymore.  \hl{I'm not clear it even exists}\footnote{\textbf{q.google }Turning an answer into a fishing expedition.  If he didn't already have skills in that he should buy some. \textsubscript{03/16/15 4:49pm}}.''

``You are out of focus with the interface.  Slightly...slightly out of focus.  It is perhaps something I could... improve.  \hl{Not the interface itself, but your connection to it and things}\footnote{\textbf{q.google }When I think something would strike Jonah \_and\_ Jaya as a terrible idea, I usually go for ``uh, no''. \textsubscript{03/16/15 4:50pm}}.  The trains, all such protocols perhaps could be enhanced.  Are you an Agent?''

``I am an Operator,'' says Jonah.

``Perhaps.''

``A distinction, again, that I only somewhat understand.''``Who is the wielder and\hl{who is the tool}\footnote{\textbf{Rebecca S. }insert juvenile snickering here \textsubscript{03/09/15 12:05pm}}?  That is the question.''

``That is not clear, even from the definition, Your Majesty.  One provides \hl{understanding and control and information}\footnote{\textbf{Suko T }I'd scold Jonah for Operator snobbism here, except that it's true.   At least as far as Hayley's concerned.  Her Operators have definitely been the providers of understanding, control and information. \textsubscript{03/09/15 3:52pm}}\footnote{$\rightarrow$\textbf{q.google }It's snobbism: it's fishing again.  Jonah doesn't really care about the titles other than their being equivalent in rank.  He figures the KiY might know more about the difference than he does. \textsubscript{03/16/15 4:52pm}}\footnote{$\rightarrow$\textbf{q.google }Also I'm not sure the metaphor of this conversation is something he really appreciates.  I think he interprets the comment as ``the distinction is who is in charge'', which from Jonah's POV is very obviously \_not\_ the distinction. \textsubscript{03/16/15 4:56pm}}, but that does not make them the wielder.''

``It is a way of answering your earlier question about knighthood, as I call it. Every form of service, every skill that we learn, every tool that we wield... shapes \textit{us}.  And so it is with that.  It is discipline.  A kindness.  A kind of service.  A tool of kinds.  A connection of kinds....'' says the King in Yellow.

``Does it allow for freedom of the participants?  \hl{It is our understanding that Octavius is a form of... bondage}\footnote{\textbf{q.google }Translation: Please go screw with someone else's head.  Jonah is unsympathetic to attempts to treat his mind as real estate.  Which is a limiting viewpoint for someone who likes deals as much as he does. \textsubscript{03/16/15 5:00pm}}.''The King in Yellow says in a measured voice, ``Bondage would be too strong a term.  But it implies a connection.  A kind of service in a way.  But... I will elaborate more later.  \textit{You...} have learned a great many things for one in your position.  You have watched and gathered very carefully.  What is it that you want?  Other than this fool's errand of climbing a flaming mountain that you so ardently pursue for your masters?  What is it that \textit{you} want\footnote{\textbf{q.google }Heh.  That's a question with an answer I was about to give, when I realized its rather best saved for later. \textsubscript{03/16/15 5:01pm}}?''

``I want my home to be safe again.  If that is possible.  I want us to be able to have the lives that we had, without being destroyed by war or eaten by some... thing that thinks people are simply pieces of it.''

``A butterfly cannot renter its cocoon and become a caterpillar again.  Do you know of such things?''  

``No...'' says Jonah.

``\hl{An old man cannot curl up into himself and become a young man or a child again}\footnote{\textbf{Rebecca S. }Frightening and yet excellent mental image. \textsubscript{03/09/15 12:06pm}}. But a home has certain meaning.  Certain ritual, certain people, certain places that define it.

``Yes.''

``If you wish insight into what those are, I may be able to help you find it.  Help you carry your home.''

``\hl{I... might understand}\footnote{\textbf{q.google }Not really.  Not in the time available.  Though it's at least progress to find ``home'' is a solid concept in all the abstractions.

This entire conversation is \_Social Chameleon\_ on full.  Except the part about protecting home. \textsubscript{03/16/15 5:04pm}}.''  Jonah is quiet for a moment.  ``I wanted to say that this may be a fools errand but I am not entirely doing it because I am \textit{told} to do it.  I am doing it because I believe it will protect that home.  Even if it is unlikely that it will help, I \textit{want} to do it.''

``It matters little to me if you fling yourself from the cliff as you seem so intent to do for whatever reasons.  I do not think, for all you have learned, you are fully cognizant about what it is you are about to do.''

``That is very likely the case.  We are not told everything.  It is frustrating.  I would like to know more about this if that is something that is being... offered,'' says Jonah.

``That is \textit{possible}... though that particular dream is liable to be very unpleasant if you wish to dream it.''

``Dream?

``Yes. Dream.'' says the King in Yellow.

``How can one choose dreams?'' asks Jonah.

``When one has dreamed every dream, as I have...every order of the infinity of dreams that I have yet explored, of which more still beckon....Horizons... and horizons...of possibility.  Then within that set, that very infinite set of possibilities, one may revisit a dream that one has dreamed.''

 {\color[RGB]{221,126,107}::He should hang out with Trenton.:}  {\color[RGB]{221,126,107}\hl{:}} \footnote{\textbf{Rebecca S. }is this Jonah talking to Signe? \textsubscript{03/09/15 12:07pm}}\footnote{$\rightarrow$\textbf{Suko T }Ion just said it was a very loud thought in his head. \textsubscript{03/09/15 1:08pm}}

``How is this done?'' asks Jonah and then immediately says, ``Forgive me, I have seen many strange things in the world.  I assume you are describing something that can be done.''

``Do you wish to dream this.... to learn more about what it is that you approach?''

``I think I do,'' says Jonah slowly,  ``What would you be asking in return, Your Majesty?''

``Because you have been forthright with me, and have followed the proper forms, I am willing to grant you this as a gesture of good faith in our negotiation,'' says the King in Yellow.

``Thank you.''



There is a flash of red.



Jonah gets a bunch of images.  He is on the train, and it is moving.  Things are going by.  At first he recognizes the train stations he goes through and then they start becoming interspersed with ones he doesn't know.   He sees various SAC numbers pass by as well.  There is a ``ding!'' and he sees Transit Minor but the Minor part flickers and becomes Major.  There's a burst of light from the windows that at first Jonah thinks is a bomb but the light is steadier than that.  His vision clears and he sees a brilliant swooping landscape with train tracks everywhere.  He's travelling along one of them and he feels his train slowing down.



He feels lightheaded and his stomach is unsettled.  He steps out onto a platform.  \hl{It is gorgeous with greenery everywhere, blue water and bright light}\footnote{\textbf{Rebecca S. }does this resemble SAC-04's greenery? \textsubscript{03/09/15 12:11pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }No. Where SAC-04 had chaotic, lush, wet greenery, this was more manicured, intentional, lightly-misted greenery. \textsubscript{03/09/15 1:05pm}}.  It is almost too much for him to take in.  He turns and there is a figure there.  Behind the figure there are bodies.  In the back of Jonah's head he feels like they should have different faces and forms, and the faces of Drake and Supay pop into his head briefly.  But what he \textit{actually} sees is a pile of bodies of Rooks\footnote{\textbf{Rebecca S. }can I get some wild speculation here on what's going on?  Does it mean my constant flubbing of Drake/Rook name is sorta' legit/ok?  Is Drake the same as Rook? Leveling up to Rook level eventually? \textsubscript{03/09/15 12:21pm}}\footnote{$\rightarrow$\textbf{Suko T }Do not even go there and conflate the two.  My heart might explode. \textsubscript{03/09/15 1:09pm}}.



The figure, male, steps forward, grabs him by the throat and starts to try to choke Jonah to death.  There seems to be a lot of history going on and the language being spoken is not one Jonah understands.  The man suddenly seems to feel threatened by Jonah and throws him back onto the train like a white hot brand.  He makes a gesture and the train starts going in reverse. As it starts moving, Jonah sees doors slamming shut.



Jonah's mind latches onto the piles of bodies he saw, wondering, ``Are these all supposed to \textit{be} Rook? Or are they many people who happen to look like Rook?''

A disembodied voice says, ``They all could have been Rook.  They were all like Rook.'' There is a bit of contempt in the voice as it continues, ``But the ones that fell are not.  He is just one.''

When the voice says ``fell'', Jonah knows that it means there was a fight and many died.

``Who am I on this train?'' asks Jonah in his mind.  ``Was I travelling as me, or was I travelling as the memory someone else?''

He can feel that the memory is a conglomeration and abstraction of many things... One word floats to the surface... ``\hl{Secundus}\footnote{\textbf{q.google }The \_meanings\_ of the various group mind names don't come through -- but do they sound enough alike to realize that this is another one?  Esp. given the ``we were many, then we were one''? \textsubscript{03/16/15 5:33pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }The word does sound like it has similar etymology, yes. \textsubscript{03/16/15 5:52pm}}``... and then a phrase ``We were many, then we were one.''  The voice says, ``\hl{If you can get all the warring kingdoms of your mind to agree, then you would become a god.}\footnote{\textbf{q.google }Quote of the Mission.  Possibly the Chapter -- and a contender for Quote of the Game. \textsubscript{03/16/15 5:36pm}} \textless pause\textgreater   But we never did agree.''

``Are these Praetors?'' asks Jonah.

``No, those are \textit{dead} Praetors.  And for a brief time...\hl{he was King amongst them}\footnote{\textbf{Nathaniel Ford }Jonah would know this references the man who choked him out/threw him back on the train. (Versus Rook, which this could be read as.) \textsubscript{03/09/15 9:12am}}\footnote{$\rightarrow$\textbf{Suko T }I totally read it as Rook and I will continue to do so because Rook rules over all, so it just makes sense. :) \textsubscript{03/09/15 4:00pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Truth \textsubscript{03/09/15 4:26pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Rook is not so presumptuous. \textsubscript{03/09/15 4:42pm}}\footnote{$\rightarrow$\textbf{Suko T }Because he is also the most humble-est.  He need not trumpet his awesomeness. He just IS. \textsubscript{03/10/15 12:47am}}\footnote{$\rightarrow$\textbf{q.google }I read it as Rook in game.  I don't see any reason to assume otherwise yet. \textsubscript{03/16/15 5:37pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I was unclear at the time, but the way he was speaking would cause the 'he' to be pretty clear as not-Rook. \textsubscript{03/16/15 5:50pm}},'' says the voice.\footnote{\textbf{Nathaniel Ford }My favorite exchange of the night. \textsubscript{03/09/15 12:41pm}}

``Good enough,'' says Jonah.  The vision fades.



The eyes of the King in Yellow were dark, but as Jonah starts coming to, there is a flicker of red.  There is a sense of his attention on Jonah again.

``I trust you found that informative...enlightening...interesting at least?''

``I think so.  Interesting, certainly,'' says Jonah.

``Does it fill you with joy for your great...adventure?'' says the King in Yellow.

``Is that what is there?''

``Yes.''

``Ah.  No, I don't have any tremendous joy for any of this,'' says Jonah.

``But you do it to protect your family and your home.  From Octavius.''

``I have been in one war, and it was terrible.  But it was a war where only those of us sent to fight, fought.  But Octavius wants to come into our home and fight.  I don't want that to happen again,'' says Jonah

``Octavius is mad.''

``\hl{That is my impression.  It seems mad to me}\footnote{\textbf{q.google }Even madder than the rest of you crazy... whatever you are. \textsubscript{03/16/15 5:34pm}},'' says Jonah.

The King in Yellow laughs softly.

Jonah asks hesitantly, ``This is a point of curiosity and I'm not asking this as a point of our negotiation.  You know Octavius in some way, yes?''

``Aware of it?  Just a moment,'' says the King in Yellow and there is a flash of red and Jonah is in \textit{Hiatus} again.




\sceneHeadline{Jaya, sans Hayley and Jonah}

\hl{Jaya hears screaming}\footnote{\textbf{Rebecca S. }is this ``I'm so pissed off!'' screaming, or more of a ``my brain is melting, help!'' screaming? \textsubscript{03/09/15 12:51pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }More of a ``I'm on fire!'' screaming. So more the latter. That sense goes away unexpectedly rapidly. \textsubscript{03/09/15 12:54pm}}\footnote{$\rightarrow$\textbf{q.google }Whoa. \textsubscript{03/16/15 5:37pm}}in the back of her head again.  She clutches the back of her neck and clears her throat. ``Service.  So you gonna tell us about it and my team and I will consider our options.''

``I will momentarily.  But first, I would like to know why you lied to me,'' says the King in Yellow.

Jaya is a bit taken aback.  ``I would like to know this as well!  When do you think this, uh, potential lie might have happened?  Because we have been discussing a number of things, all of which are truthful, but truth is often in the eye of the person who's talking...so help me.''  Jaya starts sweating.

``There are many kinds of truth.  You may have lied to me on purpose-''

``No!'' interjects Jaya.

The King in Yellow continues smoothly, ``You may have lied to me by mistake.  And that will affect your punishment.''

``Uh... \hl{what is this lie}\footnote{\textbf{q.google }Yeah.  Which of all the many truths, partial truths, non-truths, and undefinable statements was the one which set him off? \textsubscript{03/16/15 5:39pm}}?'' Jaya looks behind herself and thinks about taking a step back.

As she does the King in Yellow says, ``You may step back.''

Jaya takes a step back to draw even with Jonah and yet the King in Yellow seems even closer than before.  Jaya's sweating heavily now.  She smells a smoky smell like coals burning.  The King in Yellow seems to loom even closer and larger.

 {\color[RGB]{74,134,232}::Three.  Fucking.  Steps.::}  says Lackovich through gritted teeth.

Jaya scratches at the scabbed over loyalty tattoo on her neck and manages to remember to look away.

REBECCAxxBEGINxxHIGHLIGHTxxThe voice booms, ``I TOLD YOU, YOU MAY WITHDRAW!''

Jaya says disingenuously, ``I - I choose not to- May?  So could I- may I not withdraw then?''

 {\color[RGB]{74,134,232}::} \textit{ {\color[RGB]{74,134,232}THREE} } {\color[RGB]{74,134,232}. } \textit{ {\color[RGB]{74,134,232} STEPS} } {\color[RGB]{74,134,232}.  YOU.  FUCKING.  MORON!::} 

Jaya takes three more stumbling steps back, now a pace behind Hayley.  Jaya blusters, ``Sorry!  Sorry Sir!  Not really.... Majesty!  I'm just not used to royalty.  That is not a lie!  I assure you I am very VERY unfamiliar with royalty.  Just help me understand-''xxENDxxHIGHLIGHT\footnote{\textbf{Suko T }My favorite Jaya scene of many for this session. \textsubscript{03/09/15 4:03pm}}

``For your breach of protocol, we will be exploring together... certain of the alterations performed on you,'' says the King in Yellow sternly.

``Uh... I don't recall any 'alterations' performed on me...'' says Jaya.

``Look.  At.  Me.'' commands the King in Yellow.

``Oh yes sir,'' Jaya's gaze snaps up.  There is a flash of red.



Jaya is on a gurney, there is a white surgical field and Rook is saying, ``Tell me you love me.''

``Jesus! We've already gone over this.  I don't have to say it to you.  Fuck. Fuck!  Am I in the fucking Tank?''  Jaya looks around and doesn't see the King in Yellow.  She leans forward toward Rook and says intently, ``Rook, I might have fucked up.  Are you \textit{actually }here or are you 'fake' here?''

``You don't have to actually mean it,'' says Rook.

``Nononono it's actually important!''

``So is this.  Just say the words,'' says Rook patiently.

``I FUCKING LOVE YOU!'' yells Jaya.

``No no, just 'I love you''' says Rook.

``Okay!'' Jaya looks away and spits out, ``I.  Love.  You.''

The arm detaches and there's a sensation in her head of ``wait... that's how that works?''  \hl{There's a flood of realization about how the arm and musculature and connections all work together.}\footnote{\textbf{q.google }Cool :) \textsubscript{03/16/15 5:40pm}} Jaya's thoughts also land on the plate on the train and has the thought that this is almost the same...

Jaya looks back at Rook.  He's there and yet he's kind of around her at the same time.  The sensation is unsettling.  Jaya cradles her arm and says, ``Rook, I may have told your brother that you exist and I understand why you're being weird about this, can you hear me?  \textit{\hl{I'm in the Tank}}\footnote{\textbf{q.google }That's a damned useful way to look at it. \textsubscript{03/16/15 5:40pm}}\textit{.} Or something. Rook!  We're going back, it's the past.  What do I do?  It's your brother.''

\hl{``I find in stressful situations the number one thing to always do is to take a deep breath,'' says Rook soothingly.}\footnote{\textbf{Adam Kenney }+1 for this line. \textsubscript{03/09/15 6:24pm}}

Jaya takes a deep breath.  

``Take some time...'' continues Rook.

``No!  There's no time!'' protests Jaya in a sudden exhalation of breath.

Suddenly Jaya realizes Rook's hand is on her shoulder (when did he move??) and he says quietly, ``There is always time.''

``So there's time right now?  We can talk about this?  Okay...So your brother's crazy and he's gonna kill us and he's gonna make us do something and he wants to know where SAC-09 is.'' Jaya's voice drops into a hushed whisper, ``and we might accidentally tell him.  So don't tell me where SAC-09 is.''



She is looking at Rook's face and his hand is still on her shoulder and then his hand is suddenly on his gun, which he hardly ever seems to wear and they are on \hl{a train}\footnote{\textbf{Nathaniel Ford }Specifically the first train they were on together. \textsubscript{03/09/15 9:07am}}.

The stations pass by in a blur and suddenly she's on the platform of SAC-09.  She's looking around but Jaya forces her gaze downward to avoid spotting anything telling.  Unfortunately she sees on the edge of one of the tiles at the platform's lip a serial number.  Immediately she tries to cover her eyes and backs away.  As she staggers back she runs into something, something male.  It's someone familiar and roughly her size.



She turns and sees Jayce.  He is saying something.  Jaya moves to put her hand over his mouth.  As she does, another train door shuts between them and she sees another number there, finger painted into the dust on the window, along with symbols that reminds her of Trenton's books.  She \hl{shuts her eyes}\footnote{\textbf{Nathaniel Ford }Really, I should remember on vision quests shutting your eyes is somewhat harder than real life. \textsubscript{03/09/15 1:06pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }maybe if there had been a CHALLENGE about shutting one's eyes, things would have gone waaaay differently....  
just saying \textsubscript{03/09/15 1:07pm}}\footnote{$\rightarrow$\textbf{q.google }Agreed.  This was one of a couple of places a challenge would've made sense. \textsubscript{03/16/15 5:41pm}}\footnote{$\rightarrow$\textbf{q.google }Also I can't highlight what Nate just said, but that's a wonderful QooC all its own ;). \textsubscript{03/16/15 5:42pm}} hastily again.



Jaya opens her eyes and she's back in the courtyard with the King in Yellow.  \hl{Jaya puts her hand on her gun and yells angrily, ``Fuck you!!  Stay the fuck out of my head!''}\footnote{\textbf{Rebecca S. }second image at http://simply-sithel.tumblr.com/post/113142143954/and-i-return-from-vacation-dragged-all-my-sketch \textsubscript{03/09/15 1:17pm}} 




\sceneHeadline{Jaya, with Jonah and Hayley }\textit{\textbf{Paused}}

Jonah and Hayley are taken off \textit{Hiatus} but still \textit{Paused}.  As they come to, they hear Jaya screaming, ``That is fucking cheating!  I did not give you that fucking information!!!''

Hayley whispers in alarm, ``Sir! SIR!''

Jaya orders Hayley, ``Don't think anything!'' her face is flushed red.  

``Please do not antagonize him-'' pleads Hayley anxiously.

Jaya pulls out her hush radio and says, ``Rook, SAC-09 may soon be compromised.''

The radio makes an odd hissing noise.

``You did not end your sentence to me with 'Your Majesty''' says the King in Yellow, disapprovingly.

``Stay the FUCK out of my head, your FUCKING Majesty!'' screams Jaya, a bit of spittle flying.

The King in Yellow adds, ``Nor did I give you permission to access your sidearm or your communication tool.''

``It's \textit{my} fucking communication tool!''

``And you are in my domain!'' responds the King in Yellow sharply.

Jaya takes her hand off her pistol and puts her hands up and runs her hands through her hair.

``\textit{No combat, Sir!}`` whispers Hayley urgently.

 {\color[RGB]{255,0,0}::Did you guys follow that?::} 

 {\color[RGB]{74,134,232}::Mostly.  My } \textit{ {\color[RGB]{74,134,232}head} } {\color[RGB]{74,134,232}.  Oh my } \textit{ {\color[RGB]{74,134,232}god} } {\color[RGB]{74,134,232}.::}  replies Lackovich sounding like she's in pain.

``Chief!'' says Jonah.

 {\color[RGB]{255,0,0}::You may want to disconnect.  I think shit's going bad here soon.  And also SAC-09 may be compromised soon.::} 

``Chief!'' repeats Jonah loudly.

``What??  I'm \textit{thinking}!'' yells Jaya.

``I know!  We can \textit{hear} you\footnote{\textbf{q.google }And not in the VTX sort of way. \textsubscript{03/16/15 5:44pm}}.  Please calm down.''

``I'm fucking calm. Everybody's calm.  No sidearms...Nobody's armed...'' Jaya's blade slides out and she suddenly feels like it's easier to control than it had been before.

``Would it make you feel better to discharge your sidearm?'' asks the King in Yellow.

``In your fucking face, your Majesty?'' sneers Jaya.

``Sir!'' gasps Hayley.

``Nah, I think I'm fine,'' says Jaya, cracking her neck.

``I just thought I would offer, since it seems so important to you,'' says the King in Yellow pleasantly.   He pauses and then continues, ``We find ourselves in a moment of perhaps, achieving... agreement in our negotiations.  For...you have something I want, which is to see someone that I am very surprised to find outside of my own memories.  And I have something you want, despite all common sense.  \textless pause\textgreater  Well... I suppose it is quite valuable to some people.  But you wish to use it to climb to the lair of the wounded bear.  So.  I have the name of SAC-09.  I have the location of SAC-09.''

 {\color[RGB]{255,0,0}::Tell Morgan I'm sorry.::} 

 {\color[RGB]{74,134,232}::}  {\color[RGB]{74,134,232}\hl{Nothing you can do}} \footnote{\textbf{Nathaniel Ford }...anymore. \textsubscript{03/09/15 9:21am}} {\color[RGB]{74,134,232}.  Focus on the future.::} 

``If you will but grant me permission to gather its access keys-''

``NO,'' says Jaya firmly.  ``That is not-''

``I will give you your map,'' says the King in Yellow.  ``I do not \textit{need }your permission.  But you've come here in good faith.  \hl{And I am kind and gentle to my guests}\footnote{\textbf{q.google }Uh... I guess I agree with him.  He's a little unclear on his house rules, and he has tendency to read people's personal journals whenever he likes, but he wasn't unkind or ungentle.

I think they got lucky. \textsubscript{03/16/15 5:46pm}}.''

Hayley smiles at the King in Yellow.

``Your Majesty?'' asks Jonah.

``Mr. Gemayel.''

``You wish access to SAC-09 so as to find this person that you have not seen in so long that they are only a memory?  Or are there other purposes?''

 {\color[RGB]{255,153,0}::What?  Who are they talking about?::} 

 {\color[RGB]{153,0,255}::Whaaaaa???:: }  Carruther's thoughts are fuzzy and slurred like she's drunk.

``That is my main intention,'' says the King in Yellow.  ``\hl{A name of great power was spoken here.  A name that is a harbinger of change, destruction and rebirth}\footnote{\textbf{q.google }@\#\$!.  Might no be so bad if it wasn't followed by all those ``meanwhiles''... \textsubscript{03/16/15 5:47pm}}.  Meanwhile, \hl{Octavius claws at the door howling like a cat}\footnote{\textbf{q.google }*laughs*.  Ok I have a vivid image of Octavius actually having started as a collective of \_cats\_.... \textsubscript{03/16/15 5:48pm}}...Meanwhile I find some tattered remnant of Tertius... artifacts I have not seen since... I find a presence of great interest.''  His voice drops to a whisper.  ``Yes I wish to see my brother again. If it can be done.  If this is not a ruse or a deception of some kind.''

``If it is, we are not aware of it,'' says Jonah.  ``But, your brother, if I understand things correctly, has been kind to us. Will this information harm him?''

``He and I....it is safe to say we intend each other no harm.  \hl{What you claim to be true and what I have seen, I know to be impossible}\footnote{\textbf{q.google }Why impossible?  So curious! \textsubscript{03/16/15 5:48pm}}. So I must go and see it myself,'' says the King in Yellow.




\sceneHeadline{Rook}

There is movement in the mist.  There is a turret off to one side.  One moment it is unoccupied and the next Rook is perched there, with no space or time between those moments. 

``You and I both know that would be unwise,'' says Rook to the King in Yellow. 



There is a sensation of swirling wind, and the sound of distant banging, confused howling and alarms.  The King in Yellow seems to draw away from Rook, ``How is it that you are present here, brother?  How is that you are alive?''

``You and I know both know that I am fairly difficult to kill.  What you are \textit{really} asking is what brought me back,'' says Rook.

``Yes,'' whispers the King in Yellow.

Jaya's hand is back on her sidearm.

Jonah looks at Rook suspiciously. Rook seems to really be there and he's dressed in the same uniform and looks similar to how he did when we left him several hours ago.



Rook looks at Jaya and says, ``Agent.  Remember your standing orders.''

``Sir,'' says Jaya, taking her hand off her sidearm and salutes Rook. She flips off the King in Yellow with her other hand and runs her hand through her hair.

The flicker of a frown passes over Rook's face. ``No commanding officer brought me,'' says Rook.

``One moment, brother,'' says the King in Yellow to Rook.  His attention turns to Jaya.  ``Step.  Back.''

Jaya puts up her hands and takes three steps back, now further back than when she started.

``Brother, that was unnecessary,'' says Rook.

``And what she did was not?  Protocols and forms must be observed, that is what you said, is it not?'' says the King in Yellow.

``You use my words against me.''  Rook pauses.  ``I don't want you in this fight.''

There is a very long pause as the brothers look at each other.

``I do not intend to \textit{be} in this fight,'' says the King in Yellow finally.

``Then it is best you don't know how to get to potential battlegrounds,'' says Rook.

``You think I cannot keep myself out of harm's way?''

``I'm sure that you could... if you choose to,'' says Rook.

``I have no horse in this game,'' says the King in Yellow.

``I see you have managed to extract some information from my compatriots.''

``We have been negotiating,'' says the King in Yellow.

``You always did have a silver tongue,'' says Rook.

Hayley is just looking back and forth between them as they talk, \hl{smiling happily}\footnote{\textbf{Rebecca S. }oh Hayley... \textsubscript{03/09/15 1:46pm}}\footnote{$\rightarrow$\textbf{Suko T }What?  Minus all the emotional subtext, they are being so nice to each other!  Everyone's so nice! ;-) \textsubscript{03/09/15 4:10pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Aw! Brothers! \textsubscript{03/09/15 6:29pm}}.

``And you have always been beloved of those in command,'' replies the King in Yellow.``I do not know that I would choose 'beloved' but I can see how it would look that way from the outside.''

``I'm sure you'd have me think that you had your price to pay.''

``It has nothing to do with prices, it has to do with the way things are.  And the way things are now... I believe my compatriots would like to cross your Silver Trail to the Beacon,'' says Rook.

``You know what happened last time you met... Praetor Major,'' says the King in Yellow.

``I have no intention of going there myself.''

``And you would send them instead?  That seems unlike you.''

``It does, doesn't it?'' says Rook, pleasantly.  ``That might be a clue that it is not me who is sending them.''

Rook turns to Jaya.  ``Agent, who is your commanding officer?''

``Uh, Agent Morgan.  Sir.  Ger- Gerhauser. Sir.  Agent Gerhauser,'' says Jaya.

``But she has standing orders from you as well?'' the King in Yellow asks Rook.

``Gerhauser.... gives me certain...  leverage, yes,'' replies Rook.

``I''m not here to nitpick your chain of command... and indeed who am I to say anymore that I know you?  It certainly seems unlike you to hold back and open the door and send them into Transit Major.  These little things,'' says the King in Yellow.

Jaya straightens out to her full height.

``If they do not wish to go, I will not make them,'' says Rook calmly.



``Do you wish to go, Mr. Gemayel?'' the King in Yellow asks Jonah.

``Yes. With the understanding that what I am doing is helping the people I told you I wanted to help,'' says Jonah.

``Do you suppose it is?'' 

``To the best of my knowledge, yes.'' says Jonah.  ``I grant that that is not a great deal but...it is enough.''

The King in Yellow turns back to Rook, ``Well, who has the silver tongue now?  You have certainly done a number on them.''

``Why do you always blame me?'' asks Rook curiously.

``Claiming that I don't owe you... I owe you!'' whispers the King in Yellow.

``You don't.  My door would be open to you first and foremost.  If it could be.''

``And truly it cannot?'' asks the King in Yellow, almost plaintively.

``Not at this time.''

``Well I don't need to run under your skirts.  I have my own protections and my own realm.  My own Kingdom.  Here.''

``It is much vaster than mine.''

``Much different, than yours,'' says the King in Yellow.  ``So you lurk... what did bring you back, brother?''

``One moment,'' says Rook to the King in Yellow.  



Rook turns to Hayley and says, ``Agent?''

``Yes sir?'' says Hayley.

``Please tell Carruthers to tell Larissa HD zero.''

 {\color[RGB]{255,153,0}::Carruthers?  Please tell Larissa, HD zero.  The message is from Agent Rook.::} 

``Done, sir,'' says Hayley to Rook.

Jonah, Jaya and Hayley start feeling something odd in the back of our heads.  It is like when the connections are getting attenuated but to a degree we have not felt before.



Rook turns back to the King in Yellow. ``We can talk now.''

 {\color[RGB]{255,0,0}::Lackovich??::}   Jaya gets no response from Lackovich and gasps audibly.

``A couple of sisters, in particular need, happened to find me and executed certain protocols.  REBECCAxxBEGINxxHIGHLIGHTxxAs you are aware, those protocols are both empowering and restricting.''

``And I suspect... in this situation... temporary,'' says the King in Yellow.xxENDxxHIGHLIGHT\footnote{\textbf{Rebecca S. }A) totes need to figure out these protocols in game
B) I have a vivid mental image of a Dr. G \& Morgan sacrificing a pile of babies or something before an epic stone statue of Rook \textsubscript{03/09/15 2:08pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Please. Dr. G. would never hurt a baby. Physically. \textsubscript{03/09/15 2:11pm}}+1

``That was our agreement,'' says Rook. ``I do not know if you've had their pleasure, but they are quite...driven.''

``I know their name, that is all.  And all that implies.... ``  the King in Yellow pauses. ``So... I do believe I understand better your restrictions now.  But.  \textit{You} don't have to give me access to SAC-09.''

``I will not give you access to SAC-09.''

``You have made that very clear,'' says the King in Yellow.

\hl{``Not at this time,'' adds Rook.  ``I ask you to be patient.''}\footnote{\textbf{Rebecca S. }so much fucking foreboding in this comment.  Frankly though, if Rook brought the roof down on SAC-09 at the end of the game, I think I'd be cool with that. \textsubscript{03/09/15 2:10pm}}\footnote{$\rightarrow$\textbf{Suko T }Me too. \textsubscript{03/09/15 4:12pm}}

``No one is more patient than I,'' says the King in Yellow.  Rook just smiles kindly.  The the King in Yellow continues, ``But you cannot keep protecting me.''

``That is only true when you step in the way of bullets.''

``I do not fear bullets,'' says the King in Yellow.

Jaya frowns at this idea.

``\hl{I apologize for the use of metaphor then}\footnote{\textbf{Rebecca S. }randomly, something I was reading the other day, but I still find interesting in the context of Rooks metaphors and the world of 4T : http://www.sfwa.org/2010/01/the-moss-troll-problem/ \textsubscript{03/09/15 2:13pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Interesting! I run into this problem all the time! It's a little easier in games because you can make a out-of-game comparison without disrupting things too much. \textsubscript{03/09/15 2:16pm}}+1,'' says Rook.  A very long pause.

The King in Yellow speaks first.  ``I don't think that you've ever appreciated... my way of doing things.  My place, my home, my power, my path.''

``Do you think the same could be said of you, with regards to me?'' asks Rook.

Another pause.  ``I suppose it could,'' muses the King in Yellow.  ``And so...here we are. You want to fulfill your service.  I owe you a debt.  As much as I am loathe to admit it.''

``You owe me no debt,'' says Rook immediately.

``But you insist that is not the case.  I suppose that you would say that you did it of love.  Duty.'' says the King in Yellow, disdainfully.

``You and I both know it was a necessity more than anything else.''

``It was no necessity that I survive.''

``I know th-that you see it that way,'' \hl{stutters Rook.}\footnote{\textbf{Rebecca S. }Emotional? Preventing a slip of the tongue that would expose too much info? Totally a first though, yes? \textsubscript{03/09/15 2:14pm}}

``That much of a life that you gave me, built all of this!'' says the King in Yellow in a harsh whisper.

``And it is impressive,'' says Rook soothingly.

``But everything we can be.. it is \textit{limited}.''

``Limitation is part of nature.''

``To dream is part of our nature.  To dream is to be without limits.''

``Here I think we meet the horizon of our agreement.''

``Yes...''



Rook says, ``You just have to let them pass.  It is of no cost to you.''

``Call in your debt, and I will do it,'' says the King in Yellow. ``To be free of that burden.... if you continue to insist that I owe you nothing... how can it be that I should do this because you ask it?  What you ask for \textit{does} have value.''

``Yes it does.  But why do you insist on making this a transaction?''

``Do you not think if I give you this access that there will not be consequences for me from others who have sought it?  To give it first to you and not to them?'' says the King in Yellow.

Rook sighs.  ``There must be another way than what you ask. I will not have that relationship with you.''

``There are two other ways...''

``Name them.''

``Access...'' says the King in Yellow.

``I will not give you access to SAC-09.  Nor will I allow you to take it from them.''

``Or... I could knight them.''

``I could not ask that of them,'' says Rook.

``I could.  They wish to serve you-''

Jaya coughs loudly.

``To serve their family.  To serve their country,'' continues the King in Yellow.  ``Why should they not wish to receive this option?''

``I do not know if they do wish to pursue it.  I ask enough of them that I would not ask that...''

Jaya continues to clear her throat loudly and is giving them the side-eye.

``Do you have something to say, Agent?'' asks Rook.

``Sorry to interfere with this very... intense family reunion.... we could wait outside the gate for, you know... but you had mentioned the knighting thing and said we'd talk about it.  And I'm really not liking the SAC-09 thing.  Clearly you made your point, so why don't we talk about this knighting thing as a potential... uh...''

``For example,'' says the King in Yellow, ``your connection to Tertius connects you to something outside of yourself. Gives you abilities-''

``I'd really call it more of a burden- er yeah. Sure,'' says Jaya.

``Something that has changed you-''

Jaya disagrees, ``Well I wouldn't say it really \textit{changed} me.  Now my arm in the portal, that-''``The arm is an excellent example,'' says the King in Yellow.

``Great, thanks.  REBECCAxxBEGINxxHIGHLIGHTxxEr great craftsmanship,'' says Jaya to Rook

``It was nothing,'' says Rook modestly.xxENDxxHIGHLIGHT\footnote{\textbf{Adam Kenney }I love this random aside. \textsubscript{03/09/15 6:36pm}}

``The arm is another excellent example.  You lost something.  And you gained something.  And you were changed,'' says the King in Yellow.

``Okay, Okay, I can follow this,'' says Jaya, nodding.

``It is a skill, it is a service, it is a connection...'' says the King in Yellow.

``Are you asking for someone's arm?'' asks Jaya.

``No.''

At a loss, Jaya's eyes flicker over to Jonah briefly.

``What he is saying is that knighthood would be a service, and would change you,'' says Rook.

``I mean, I wake up every morning, changing every day,'' says Jaya.  ``Uh... you know Hayley talks about contracts and stuff.  Let's make this clear. Are you requesting a body part?''

``No.''``Are you requesting to be an... Operator?'' says Jaya slowly.

``It is more like that, but there is no implication of control.''``He wouldn't be any more of an Operator on you than your hand is,'' says Rook to Jaya.

``Precisely.  It is a tool.  A technique,'' says the King in Yellow.

``So he's going to be my tool?'' asks Jaya.  ``So we're making some progress... someone's being a tool, someone's getting a tool... Uh...\hl{Who's the tool}\footnote{\textbf{Rebecca S. }Oh Jaya.... \textless 3 my darling darling girl.

http://www.urbandictionary.com/define.php?term=tool\&defid=1403153 Reads almost like a character description, yes?  :D \textsubscript{03/09/15 2:19pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Awww! But Morgan wants you there! \textsubscript{03/09/15 2:21pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Also, if you look around the table and you can't spot the tool... \textsubscript{03/09/15 2:23pm}}?''

``The realm in which I operate is not... so literal, so quotidian, so physical, so blunt, as that which you spend 16 hours a day,'' says the King in Yellow.

``Roughly 17 hours and 15 minutes,'' amends Rook. ``With some variance.''

Jaya looks blank.

``Dreams, sir,'' whispers Hayley to Jaya.

``Yes, primarily I live in dreams,'' says the King in Yellow.

``Uh... sorry to hear that,'' says Jaya.

``No it is a great thing.  They can be most disconcerting if you have no control over them... hallucinations... terror...''

``Yeah I've had some bad trips,'' nods Jaya.  ``I know what you're talking about.''  She looks at the King in Yellow questioningly, ``So you're looking to get rid of the dreams?''

``No.  Because I have control over them,'' says the King in Yellow.

Jonah looks like he is thinking hard through this exchange.

Jaya says, ``Uh... great!  So you want to help someone with their dreams.''

``You are getting closer,'' says the King in Yellow. ``It is a protocol.''

``Hayley's really good at protocols!'' exclaims Jaya.

``I have no doubt that she'd excel at this method should she choose to pursue it.  She could be a most distinguished knight.''

Hayley looks pleased and very flattered.

``She is a very distinguished trainee- I mean, \textit{Agent},'' stresses Jaya.

``I do not believe the two are exclusive,'' says the King in Yellow.



``Chief,'' says Jonah. ``Can I ask a question?''

``Uh... Your Majesty... can we, uh... huddle?  I feel a little awkward...'' Jaya indicates how far apart they all are.

``I will allow you five minutes of conversation amongst yourselves,'' says the King in Yellow and turns away so he is not facing us.

``Very good, Your Majesty,'' says Jaya in a dry tone and hurries to draw her team together.



Jaya turns to Hayley, ``Hayley, how do you feel about this?  How do you feel about being a knight?''

``I will do whatever will help the mission sir.  Except that my services cannot be promised to anyone.''

``So you can't agree to be a knight?'' frowns Jaya.

``I''m afraid not sir.  I would need permission from my contract holders,'' says Hayley.

``Uhhhhh.... Am \textit{I} your contract holder?'' asks Jaya.

``No sir.''

``Is \textit{Rook} your contract holder?''

``No sir.''

``Can Rook... sorta... give permission as a sorta contract holder?''

``I'm afraid not sir, he was not designated as one of my alternates.''

``Well, can you lie and say that you can be a knight anyway?'' asks Jaya.

``No sir, that would violate my contract,'' says Hayley firmly.



Jonah asks Rook, ``I think \hl{the Agent}\footnote{\textbf{Rebecca S. }fuck you, Jonah! Jaya is standing RIGHT THERE.  ``the Agent''. wtf... \textsubscript{03/09/15 2:35pm}}is asking, what is the \textit{price}?  What is the cost of saying yes?  Can you explain what he is offering?''

Rook says, ``The issue is that, any change you make to yourself is a change.  As I said to you,'' he looks at Jaya. ``When you gained your arm, do not go too far down that path or you will lose yourself.  You lose some degree of freedom.  That what you had before is not what you have now.''

``Actually, I feel like I've got better control over it now,'' Jaya comments in an offhand way, giving the wrist its unnatural turn once around.

``I'm very happy to hear that, Agent,'' says Rook.``Chief, would you want to be the Agent to everybody?'' Jonah asks Jaya.

``Fuck no!'' says Jaya loudly, face twisting in anger.

``So what it comes down to is this,'' says Rook.  ``Everything you touch, you create a bond with.  Too many bonds is bondage.''

Jaya make a ``this is gross'' face.

``Sir, at the risk of being blunt, when we were made Agents and Operators, we were not told the consequences and risks of it.  What are the consequences and risks of this?  What does it mean on a daily level or a long term level?  What is he \textit{actually} going to be doing?''

Rook says, ``I can only answer to the best of my knowledge because I do not have the capabilities he has.  Your VTX has a certain interaction with organic... molecules.  It also has a interactions with certain \textit{non}-organic molecules.  Specifically non-organic systems that have been designed, such as your arm, to interact with.  I think- I know that he can enhance that interaction.  What he is offering to do is to enhance those systems that interface with your VTXs.  Assuming you learn to do that.  What that means on a \textit{daily} level is that your perception of the world will be altered.  As it would be wearing different clothes or having different weapons in your hand.''

Hayley nods thoughtfully.

``My perception is altered every day based on blue pill or red pill so... I'm not seeing a big problem with this.   I'm happy to alter some more if it will \textit{get us the fucking map},'' says Jaya in a growl.

``What does he get out of it?'' asks Jonah.

``The same thing every leader gets out of everyone looking at the world in the same way.  But in more practical terms he gains an increased perception of the things you do.''

``So it's like having an Operator follow you around all the time?''

Rook hesitates.

``Imprecise, I know,'' says Jonah.  ``But more like that than-''

``He grows his empire,'' says Rook with a sigh.

``Doesn't everybody,'' says Jaya wryly.  She says loudly and confidently, ``Great!  I think we have a plan of action.  I'm gonna be a knight, we're gonna get the map and go to the Beacon.'' 



Hayley looks at Rook, ``Sir, may I ask a question?''

``Hayley, we've been over this,'' sighs Rook.

``Sorry,'' apologizes Hayley.  ``I don't believe that myself or Operator Gemayel have augmentations like that,'' she indicates Jaya's arm.  ``What would happen to us?  What would this... person... interact with?''

``It could be any number of devices-'' says Rook.



``Your five minutes have ended,'' interrupts the King in Yellow turning back around to face us.

Jaya declares, ``Great!  I think we've come to the conclusion that we'd love to have the map and I know that our protocols don't really \textit{align} really well but I'm gonna be your knight and you know, scratch your back, you scratch my back, stay out of SAC-09, it's all good.  Excellent. Right?''``Your majesty,'' prompts Rook.

``Er, your majesty,'' adds Jaya belatedly.

There is a very slight smile at the corner of the the King in Yellow's mouth.  ``It is agreeable to me.''

``Excellent.  Excellent.  Not compromising SAC-09?'' clarifies Jaya.

``That is the agreement,'' confirms the King in Yellow.



``Very well, the terms of the agreement has been struck.  Specifically that I shall knight...'' he looks at Jaya.  ``How, formally, shall I name you as I knight you?''

``Uh.... let's keep this pretty informal...'' says Jaya.

``\textit{Formally}, how shall I name you?'' repeats the King in Yellow.

``Your \textit{name}, sir.  Your formal name,'' whispers Hayley to Jaya.

``Uh, Agent.  Agent Jaya Parvadi,'' says Jaya.

``Very well. The bargain specifically then is that I shall knight Agent Jaya Parvadi.  Inducting her.  And in return, I shall provide a map to the Beacon.  And no more.''

``Excellent,'' says Jaya. ``You know as team leader, I feel that it's my burden...''



The King in Yellow turns to Rook. ``And so you go back to SAC-09?  Since you will not be accompanying them?  And I see you no more?''

``For now,'' says Rook.  ``But time is very long.''

``Until some other sister finds your protocol again?  Perhaps by then I will have the key?  Is that what you are implying?''

``All I am saying is that I know a great deal about time, but I do not know the future,'' says Rook.

``Nor do I.  If... I should not see you again... I wonder if you will tell me why...you did what you did?''

``Because you are my brother.  For that reason and no more,'' says Rook

``That's not an answer.''

``I know you never thought that I was,'' says Rook.




\sceneHeadline{Jaya is Knighted}

The King in Yellow turns to Jaya.  ``Approach.''

Jaya takes three very obvious steps.

``Approach.''

Jaya takes another three steps and asks, ``How many times we gonna do this?  Can I just walk up there?''

``Just three at a time, sir,'' whispers Hayley.

``Approach,'' says the King in Yellow.

Jaya takes another three big steps and rolls her eyes.



There is a very long pause and he has Jaya approach one more time and she realizes she is very close to him indeed.  The fog seems to recede and the space expands and Jaya feels like she's in a broad plane with some fairy lights in the distance.  She looks behind her and sees her team behind her, but very distant from her.  The robes part and there is just darkness underneath.  A sword emerges and is raised over Jaya's head.\footnote{\textbf{Rebecca S. }held by a wacko looking metal tentacle arm? Like an auto-8's arm? \textsubscript{03/09/15 3:03pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Parts of it look like a weirdly gloved/sheathed hand/arm. Parts of it is tentacley. Parts don't seem to totally connect. But you don't really focus on all that very much. \textsubscript{03/09/15 3:05pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Anything wonky about the sword? You're not going to ret-con it into a gun-looking thing again, are you? ;) \textsubscript{03/09/15 3:05pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Nope. It's a sword. I'll draw it for you. \textsubscript{03/09/15 3:06pm}}  She raises her hand instinctively to block it.  She is close enough to see that there is something writhing/moving in the darkness.



Hayley is on high alert.  She knows she cannot run to Jaya in time so she puts her hand on her rifle.

Rook says quietly, ``Agent, be still.''

Hayley removes her hand from her rifle, but she's still anxious.



``Bow your head.  Lower your hand that I may knight thee.''

Jaya lowers her hand, white knuckled.

``I do proclaim thee,'' says the King in Yellow, and the sword lightly touches her shoulder.   Light trails after the sword as it moves, ``I do proclaim thee, Agent Jaya Parvadi,'' he touches her other shoulder, ``Knight and sworn vassal'' he touches to top of her head, ``of my kingdom'' and the sword dissolves into shimmers of light that shower over Jaya.



Jaya feels something.  It's weird. She feels alert and supercharged like she does when she's first tied to an Operator.  It's like putting her hand on the plate.  It's kind of good, which causes Jaya to smirk slightly.



``You may withdraw if you desire,'' says the King in Yellow.

She takes three steps back and looks at him.  He just nods at her and addresses the whole group, ``The map then.''  He turns and starts walking into the mist.  Fires light up.  There's a building behind him that we didn't notice before. The fires, lit up, show an opening, an arch-way through the center of the building.  And beyond the opening there is a long curving, clear concourse, with tron-like lighting, that goes up to another tower to the left.  The King in Yellow disappears into the building/arch/mist.



Shortly thereafter there's a giant burst of light that cuts across the sky.  Then we see a bunch of drones pass over and there's a lot of movement around us. 

Rook is still there, and we can all move again.

``Do we have what we want then?'' asks Jonah.

``He was nice!   Do you feel okay?'' Hayley asks Jaya.

``Yeah... do I look any different?'' asks Jaya.   Hayley shakes her head.

``I did not know how he'd react to me,'' says Rook.

``He knew you were involved from the beginning, I think,'' says Jonah.

``He always was the smart one,'' says Rook.

``Excuse me, this is a personal question,'' says Hayley, ``Is he family?'' she asks Rook.

Jaya snickers.  Rook looks at her askance, ``Yes.''

\hl{``That's nice!'' says Hayley brightly.}\footnote{\textbf{Adam Kenney }Yay! \textsubscript{03/09/15 6:42pm}}



Rook looks up and looks concerned.

``You can't go where we're going because you're from there?'' asks Jonah.

``Transit Major?''

``Yes.''

``No, I can't go because I would compromise the mission,'' says Rook.  ``But you're not going there now, just complete the mission and get home.''

``To activate the Beacon?'' asks Jaya.

``Yes.''  He looks distracted, ``Something's going on.''

There are lights coming on in the sky.  Not stars appearing, they are burning things falling from the sky.

``Do we need to hurry sir?'' asks Hayley.

``Yes... meet me at the train as soon as you can,'' says Rook.

``Very good sir.  Let's go,'' says Hayley to Jaya and Jonah.

``Aren't you walking back with us-'' asks Jonah.

``You need to go to the Beacon. I need to go secure the train.  Go,'' orders Rook.

We doubletime it through the tunnel. There's a giant bridge, with buildings between the two towers.. The flaming things fall among the buildings and just before they hit the ground, they burst open and humanoid figures drop from them.  Jonah can see up in the sky flashes that look like mortars.  ``That's Octavius,'' says Jonah.  Hayley nods.

As we go further up the trail, several figures drop onto the concourse in front of us.

``Shoot to kill!'' yells Jaya.





\textbf{{[}Queen in Red is activated.  40 Tokens enter the pool.{]}}



\textbf{{[}61 Tokens remaining{]}}




\jumpHeadline{Challenges \& Refreshes \& Pool tracking }

\begin{itemize}
\item Pool: 20
\end{itemize}

\begin{itemize}
\item Refresh: Left Arm 3(Jaya)
\item Pool: 21+40 (Queen in Red)
\item \hl{Pool: 61}\footnote{\textbf{Rebecca S. }insert dramatic swearing and panic here \textsubscript{03/09/15 3:26pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }It's roughly only half as bad as it could have been. \textsubscript{03/09/15 3:43pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }''The X in Y'' \textsubscript{03/09/15 6:43pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Let the record show that tonight we kicked those 61 tokens' asses.  Excellent cleanup, I think down to 1 or 2 tokens of backlash (from flaws only) \textsubscript{03/09/15 11:46pm}}\footnote{$\rightarrow$\textbf{Suko T }We totally did.  So much that we even took 28 of those tokens as VP trophies!  Phat loot!  And Rook didn't die, which is really the important part. \textsubscript{03/10/15 12:54am}}
\end{itemize}




\jumpHeadline{VP Totals }

Hayley 0

Jaya 0

Jonah 0




\jumpHeadline{Quotes: }

Adam: There is a faint reddish tinge to your vision.

Nate: Jaya always sees red.



Nate: You know who I'm talking about.

Rebecca: Murder McMurder?

Suko: Hey, he has a name!



Ion: I'm glad I'm not involved in this mess now.

Rebecca: I know!  I have someone to hate that's not you.  It's totally going to improve everything.



King in Yellow: It need not interfere overmuch with your other duties, but it is a form of service.

Jaya:Yeah so we're servicing some other people pretty hard.



Rebecca: Who \textit{wouldn't} be okay with severing a deep mental connection with Jaya?  I mean, even Jaya would be for that.  She does \textit{drugs}.

Suko: Hayley would be fine with it.

Ion: That's true, Hayley would do it.

Rebecca: Hayley would do anything.

Suko: She's had put up with so much, it would probably seem normal to her.

Rebecca: Just imagine how educational it would be!

Suko: Soooo educational!  I could find out what being drunk feels like!



Rebecca: So we're all in agreement we're not giving away SAC-09?

Suko: Yeahhhhhhh.....

Ion: Maybe....

Rebecca: No!



Suko: And {[}Hayley{]} kinda likes {[}the King in Yellow{]} because he was nice to her...

Rebecca: Yeah you two were BFFs from the first moment- I was like, UGH!



Rebecca: I wrote down ``Hayley just strokes that ego like a good hooker does.''

Suko: Well, when you have been \textit{trained }to...

Nate: Are you servicing hard enough?



Nate: And {[}Jonah{]} sees doors slamming shut.  Does he have any questions?  What is the thing he is focusing on?

Suko: What's a Praetor?



Jaya: Rook, I might have fucked up.  Are you \textit{actually }here or are you ``fake'' here?



Nate: It's not threatening.

Rebecca: Nah... I feel threatened.

Nate: Well, you're Jaya...



Jaya: So we're making some progress... someone's being a tool, someone's getting a tool... Uh...Who's the tool?



Rebecca: Do I feel special? Do I feel like a fairy princess?

\hl{Ion: Not again.}\footnote{\textbf{Rebecca S. }:D  Clarice was an ICE princess, not a FAIRY princess, sheesh... \textsubscript{03/09/15 3:29pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Maybe he was referring to Lilly Fletcher. \textsubscript{03/09/15 6:46pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }I think you're confused, Lilly was a fairy *prisoner*, not a princess. \textsubscript{03/09/15 11:45pm}}




\jumpHeadline{Pet Names Used By The King In Yellow }


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: Let the record show that Suko posted this transcript for public reading at 5:29am, on a work Monday. And will be playing 4T later that night.  
"How is she even alive?" asks Adam..., unable to correctly match (exceeded acceptable limit):ExpectedNotes: Suko

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Rebecca S. }Flaw: Crushing For A Dead Man (weak) \textsubscript{03/09/15 3:38pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{03/16/15 4:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/10/15 12:39am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:14pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:12pm}} 

	Unable to highlight for footnote: Heh.  That's a question with an answer I was about to give, when I realized its rather best saved for later., unable to correctly match (exceeded acceptable limit):ExpectedWhat is it that you want

	Unable to highlight for footnote: can I get some wild speculation here on what's going on?  Does it mean my constant flubbing of Drake/Rook name is sorta' legit/ok?  Is Drake the same as Rook? Leveling up to Rook level eventually?, unable to correctly match (exceeded acceptable limit):ExpectedIn the back of his head he feels like they should have different faces and forms, and the faces of Drake and Supay pop into his head briefly.  But what he actually sees is a pile of bodies of Rooks

	Unable to highlight for footnote: My favorite exchange of the night., unable to correctly match (exceeded acceptable limit):ExpectedAre these Praetors? asks Jonah.
No, those are dead Praetors.  And for a brief timehe was King amongst them, says the voice.

	Unable to highlight for footnote: And not in the VTX sort of way., unable to correctly match (exceeded acceptable limit):ExpectedWe can hear you

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }Please. Dr. G. would never hurt a baby. Physically. \textsubscript{03/09/15 2:11pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{03/16/15 4:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/10/15 12:39am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:14pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:12pm}} 

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Nathaniel Ford }Interesting! I run into this problem all the time! It's a little easier in games because you can make a out-of-game comparison without disrupting things too much. \textsubscript{03/09/15 2:16pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{q.google }+1 \textsubscript{03/16/15 4:33pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/10/15 12:39am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:14pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{03/09/15 4:12pm}} 

	Unable to highlight for footnote: held by a wacko looking metal tentacle arm? Like an auto-8's arm? because:GivenExpectedA sword emerges and is raised over Jayas head.A sword emerges to raise over Jayas head.


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/24/15 5:01pm
\end{flushright}

