\setcounter{chapter}{ 4 }
\chapter{\textbf{SAC-09, Interlude} }




\subChapterTitle{``Shore Leave''} 

\deets{Suko}{August 13th, 2012}



So.  Many.  Words.



\noindent\hrulefill





We purchase some communal assets, spending 16 points.

{
\parskip=0pt

\textit{Equipment} \textbf{Dispensary }(2): Stocked with first aid kits, painkillers, bandages, antiseptic, cleaning alcohol and basic medications along with handy satchels and pouches to carry such, this is located in a corner of the Requisition cage.

\begin{itemize}
\item \textit{Outfit} \textbf{Medkit} (1): A bundle of bandages, one-use painkillers and antiseptic ointments, this pouch attaches to the leg of a Transit Authority Uniform and is useful for a number of light to medium medical emergencies.
\end{itemize}



\textit{Equipment} \textbf{Radio Network }(2)

\begin{itemize}
\item \textit{Equipment} \textbf{Hush Radio} (1)
\end{itemize}



\textit{Equipment} \textbf{Closet }(1)

\begin{itemize}
\item \textit{Outfit} \textbf{Urban Camouflage} (1)
\end{itemize}



\textit{Equipment} \textbf{Armory }(1)

\begin{itemize}
\item \textit{Weapon} \textbf{Rifle} (1)
\end{itemize}

}



\jumpHeadline{SAC-09 } 



After the last session Tiburon and Morgan take us to the Transit Authority HQ where we are subjected to a bit of cross examination about Cardoza.  Nothing too severe though and we aren't there long.


\sceneHeadline{Jaya and Rook }

Agent Tiburon Rook meets with Jaya in the room with various tanks in it.  There are a few more than last time and some are filled.  He tells Jaya that he has a new mission for her - helping them test some delicate equipment.



Through a series of questions, Jaya figures out that this may be related to the ``drowning'' incident for Hayley and is concerned for her own safety if she agrees to this ``new mission''.



Tiburon asks if Hayley was injured after her test of the equipment and Jaya says it was hard to tell because they went from the test straight to the shooting.   It dawns on Jaya that perhaps the testing was responsible for Hayley getting so injured on the last mission.  It may not be her fault at all!  She lets go of that faint twinge of guilt with relief.



She negotiates a pay raise for herself and Jonah in return for participating in this ``testing'' and swaggers out of the room feeling very satisfied with herself.  Her strut falters as she walks down the hall and she begins to realize just what she may have signed herself up for.


\sceneHeadline{Jonah and Oliver }

Jonah approaches Oliver and brings up Oliver's storming out of Morgan's debriefing.  He mentions that after Oliver left, Morgan actually apologized to them, which proves that sometimes it is good to yell and be angry.  The thought of Morgan apologizing makes Oliver smile, ``I would have paid to see that''.  Jonah advises Oliver to use this approach strategically, to be deliberate about using his anger for the greatest effect.  Oliver says there are lines he draws and he's not really that much of a strategist.  Jonah says that all he's asking is for Oliver to keep it in mind and if he can, give his squadmates a heads up so they can play off of his confrontational actions to hopefully gain beneficial results, like Morgan's apology.  Jonah says that Morgan seems to be more open to trusting them and working with them, and ventures that this could, potentially. be really good for us.  \hl{Jonah, with some hesitation and reluctance on his part}\footnote{\textbf{q.google }The hesitation is not just about Oliver, though Oliver has no reason to know that. \textsubscript{09/02/12 10:34pm}}, obliquely brings up the war, but just that much of a reference to it distresses Oliver and the conversation dies.



Jaya, fresh from her conversation with Tiburon, runs into the two of them in the hallway and brags about the payraise she just got for herself and Jonah for just a ``few extra duties''.  Jonah is openly alarmed by this and asks what they are.  Jaya says it's a mission, or at least some sort of testing of equipment will send us on missions.  Jonah is suspicious and not too pleased with this, and lets his concern be known.  Jaya exhibits her authority in a more forceful manner than she usually does, and tells Jonah on no uncertain terms, that he is going to do this new mission, whether or not he's suspicious about its purpose or safety.  She looms over him in an intimidating manner to get him to agree that he will.  Jonah's displeasure very abruptly disappears, and he seemingly unconcernedly agrees to do what she asks.



\jumpHeadline{ Shore Leave! } 


\sceneHeadline{Shore Leave: Jaya }

Jaya is at Padme's tattoo parlor again.  It is after hours and the sisters are looking at Jaya's new war wounds in the mirror.  Micah is crying on the floor.  They are both showing a lot of bravado as Jaya tries to convince Padme how the bullet wound just makes her look more hardcore and Padme tries not to show how upset she is at seeing how close her sister came to being killed.  Padme asks when Jaya will get a (safer?) desk job and Jaya claims that her competence and intimidating visage keep her in the field.  Padme mentions that they are not getting as many water rations (presumably from Simon's work in the Plantations) anymore, and she's heard that everyone gets free water if they are willing to move to New Station.  Jaya tells Padme not to move there, it's not safe and she points to her wounds from that mission.


\sceneHeadline{Shore Leave: Oliver }

Oliver is ambushed by his well-intentioned mother with a surprise dinner with his old schoolmate and acquaintance Roger.  His mother hopes that Roger can help be Oliver's entrée into more rarefied social circles than the ones he is currently in.  She doesn't know that Roger is the one who spotted Oliver in Cardoza when Oliver was there on the mission hunting Cyril Magnin.  



At dinner, Roger refers to seeing Oliver ``before'' (referring to seeing him in Cardoza) but Oliver deflects the questions and says he can't talk about why he was there. Oliver shifts the focus off of him and asks about Roger and what he has been up to.  Roger is doing well, starting a new business brokering trade agreements and working with Senator Pierce (the younger).  Oliver's father uses this evidence of success to further denigrate Oliver.  



Oliver's mother asks his father to get a second bottle of wine and he does so begrudgingly.  He is gone for a while and there is the sound of a crash.  Oliver's father returns, enraged and spoiling for a fight.



Oliver's mother and Roger start trying to defuse the situation, but it is too late.  There are several more vicious exchanges and Oliver excuses himself and leaves the dinner.


\sceneHeadline{Shore Leave: Jonah }

Jonah briefly speaks with Trenton regarding maps, particular kinds of maps.



Jonah meets with a business contact of his, \hl{Zara Thustra}\footnote{\textbf{q.google }Yes, that's his name. \textsubscript{09/02/12 10:45pm}}, in the Annex.  He asks Zara for a subway map but one of the old ones, a higher quality one than the ones you get for free at the train stations.



Zara says he may be able to find something like that.  His first price is 3 flashlights and the name of the person who gave Jonah the flashlights.  He then reduces that to 3 flashlights and just the name of the station where Jonah got the flashlights.  They haggle a little longer and then settle on one TA flashlight now, and two on delivery and Jonah asks his contact if they'd be open to working with Zara.  Zara asks Jonah if he knows anything about the (presumably) elite team that those flashlights came from.  Jonah is not willing to sell that information at this time.



Zara leaves, but then returns to pay the bill and adds that he could set Jonah up with a buyer should he ever want to sell any info on his source or on this TA team.



Jonah's sister Riva shows up and asks what was going on, having witnessed at least part of that conversation.  Jonah puts her off and she asks him when he's going to come home.  Sounds like things aren't going well at home.  Riva mentions that they are thinking of moving somewhere else.  Apparently you can get free water if you go to one of the new stations the TA is opening up.  Jonah realizes that she's talking about New Station and warns her not to go there.  Riva is noncommittal, but says their parents are divided on whether to go.  Jonah tries to tell her he knows New Station is really hazardous, but is trying not reveal how he knows, which allows her to change the subject.  He does promise to both try and get the family more animals, as well as bring Riva something special, though he does warn it will take some time.


\sceneHeadline{Shore Leave: Hayley }

Hayley returns home to find Gillian dressed to leave.  She hastily changes out of her uniform and joins Gillian on the subway train to Cardoza. Gillian warns Hayley that she will probably have to stay up most of the night, and of course Hayley says it will be no problem.



Gillian has been invited to dinner at Mr. Garrett Stanislav's house and she expects him to blackmail her.  He is one of the vultures hovering around Veridian Dynamics and Gillian, looking to take them down, buy them out, or pounce on a weakness (or all three).



Gillian hands Hayley a card with some numbers on it and tells her to memorize them and then destroy the card, which Hayley does.



Hayley asks Gillian if there are any specific dangers she should be looking out for at this upcoming dinner.  Knowing the source of the blackmail may help Hayley figure how to help Gillian.  Apparently one of the projects Gillian worked on for her father (before she left) was heavily involved in Mr. DeVries' business, and if this connection should come to light in the current political climate, it would be very damaging for her.



Hayley apologizes again for getting injured on the last mission.  Apparently she can't be discharged just from being injured, so that is not an option.  Gillian tells her that she was offered more money from the TA to keep Hayley's contract, so she can't get Hayley back that way.  Gillian is frustrated, but says her Fili says that the contract negotiations are solid and TA can keep Hayley so long as they keep paying for her time. 



Gillian is visibly agitated and scared. She asks Hayley how she deals with knowing she could die or worse.  Hayley says that it takes a while but eventually she discovered that in those situations, the only thing she could control was how she reacted to the fear, so she learned to not let that fear debilitate her.  It had the consequence of making things very bad ``with him'' (both Gillian and Hayley clearly know who she is talking about but no names are mentioned).



This seems to help Gillian less than Hayley intended, although Hayley loyally stresses how strong Gillian was to survive this far, so she must be strong enough for this.  Unfortunately Hayley's references to past trauma brings up old bad memories and Gillian is even more distressed.  



Gillian changes the subject and discusses the blackmail situation in more detail.  This is a very real threat and a substantial one as well.  Stanislav has Filis who will testify under oath, details about the project that tie Veridian Dynamics and Gillian to Mr. DeVries.  This is bad, while the Filis are alive, the connection remains and can be used against Gillian.



Hayley speculates obliquely that if the Filis weren't alive, then that would solve the problem.  Alarmed at this sort of talk, Gillian ends the conversation.



They arrive at Mr. Stanislav's house and after a stilted and awkward dinner, Gillian and Garrett retire to the drawing room together and stay there for the rest of the night.  Hayley attempts to make some conversation with the staff but no one really talks to her.



\jumpHeadline{SAC-09 } 



Jonah is told to report to Dr. Gerhauser.  When he walks into MedBay, \hl{he finds Dr. Gerhauser playing the harmonica}\footnote{\textbf{q.google }There's something weirdly disturbing about this sentence, just sitting there, as if nothing else was going on. \textsubscript{09/02/12 10:54pm}}.



She says that they analyzed the strange grey dust that Jonah brought back from the tunnel under Cardoza.  It is aged bone dust.  Maybe ground up bones, or crushed bones, but either way they are \underline{ very } old.  In the amounts that Jonah described seeing in the room where he got the sample, this would have been a very large number of bodies.  She speculates that the bodies were probably incinerated or crushed.  Jonah doubts that fire could break down bone that much, but Dr. Gerhauser scornfully says that Jonah is not thinking creatively enough, there are ways of getting that much heat.  Like the sun, perhaps.



She asks if there's anything else he knows about that area.  Jonah mentions the sigil (he refers to it as a ``cryptmarker'') on the door, and she says that she read about that in his report but she doesn't know anything about it.  She quizzes him on what the Sigil could mean but Jonah doesn't know much more than her, he's just seen it used on burials and graves, by certain people who hold to that old (implied: out of favor) tradition.



Dr. Gerhauser encourages Jonah to look into this and she says she is fairly certain there are more rooms like the one we found underneath Cardoza.  He says he will.



Jonah asks about these experiments that they will be participating in.  To answer him, she pulls out a strange object (a tuning fork but he's never seen one before) and sets it near two glasses of water.  She demonstrates how the tuning fork makes one glass vibrate, while the other is unaffected.  She talks about music and notes but Jonah has too little experience in such things to really follow the analogy.  So she talks about frequencies and vibrations and says that like the tuning fork, people can generate the proper frequency.  As long as they have the proper tool.  Here at SAC-09 they have tech that they hope to resuscitate, the equipment is very special.  It replaces your sensations with something else. 



Certain people generate the proper frequency to use this equipment.  She is not compatible with it.  Historical records show that it is safe, although no one knows from firsthand experience how to use it or what the side effects are.



Jonah is still not comfortable with this and asks if he gets a choice about participating.  Dr. Gerhauser says, ``You do have a choice.  But... we will try to convince you it is in your best interest to participate.''  He presses her further, but in the end the full parameters of the choice are not clear.



He asks to borrow some medical tomes and Dr. Gerhauser sends him an anatomy book (like Grey's Anatomy) with a note attached: ``When you are finished, I'll quiz you.''



Quotes:

``I somewhat think you would not be comfortable knowing what it is. But it's safe.'' Nate as Dr. Gerhauser



``I believe it is safe if you are psychologically stable.  Are you psychologically stable?''  Nate as Dr. Gerhauser

``\hl{How would I know if I was}\footnote{\textbf{q.google }Simple: none of the characters are psychologically stable.  (Mostly for very understandable reasons.) \textsubscript{09/02/12 10:58pm}}?'' Ion as Jonah


\sceneHeadline{Oliver and Morgan }

Oliver is swimming and finds Agent Morgan waiting for him by the edge of the cistern in battle dress uniform.  He gets dressed and meets her outside the cistern.  She asks if he's had a chance to cool down from his ``outburst'' a few days before.  He apologizes for his rudeness but says that it happened because Morgan put him into the same situation he was in, in the war.  



As they step into the elevator he asks, ``Were you directly involved in the war?'' 

``Which one?''

``Nicklepan.''

``No.  I was not directly involved.''



They ride the rest of the way in silence, it seems to go up and up for a long time.  They emerge in a small octagonal room.  There are some very detailed paintings on the walls and a desk with two chairs in front of it.  There is a narrow bed in one corner, made with military neatness.  Morgan sits behind the desk and Oliver seats himself in one of the chairs after asking permission.



She continues their conversation from the elevator, ``You don't want to talk about your experiences in the war, do you?  Well you'll understand if I don't either.''



Oliver says that he knows what he signed up for: ``to jump when you say so, to die when you say die.''



Agent Morgan says that she doesn't want him to die, she wants his cooperation and his buy-in.  ``What is it going to take {[}to get this{]}?''



Oliver sits back.  ``My cooperation you have.  My 'buy in' you are going to have to earn.''

``And how do I do that?'' asks Morgan



Oliver thinks about it and says that right now it feels like we're making a mess.  We're under-prepared for the missions we get sent on and barely pull them off.  Also, we're doing missions that other groups are doing, and yet we're not being treated like regular TA agents.  Morgan interrupts to ask if he's concerned about the other teams {[}since this was something he brought up during the debriefing earlier{]} and Oliver says he's just giving her a hard time about that at the moment.



For his 'buy in' he wants to know that there's a purpose to all of this.  That someone up there is working for the greater good of the Directorate, even if on the ground level it seems like chaos.



Morgan looks thoughtful at this answer.  She seems to come to some decision and says Oliver can ask her one question.  ``I will answer to the best of my ability except if-'' she stops herself, looks at Oliver consideringly, and amends firmly, ``no, I will answer it to the best my ability,'' with no qualifiers.



Oliver asks simply, ``Why me?''



Morgan answers, ``Your genetic profile allows you to interact with some old technology to reach out to a lost installation.  This would allow us a form of direct influence that is currently not available.''

``So why are we being sent out on all these small missions?  Any one of us could die on these missions, wouldn't that be a problem for you?'' counters Oliver.

Morgan sighs.  ``This is not a science lab, we do field work.  And we need you to learn to be a team.''

``So out of all the TA agents out there, you just coincidentally happen to have four people who can work with this technology?'' asks Oliver

``I don't believe in coincidence, do you?'' says Morgan dryly. ``There are two sets of critical factors.  One of them you share with many people, but the other is one that you only share with each other.  That is why it's important that you learn to work together, especially in stressful situations.  If you want more information on how it works you can talk to Kate.''



The meeting wraps up and Oliver departs.



Notes:

\begin{itemize}
\item At one point Morgan says that Hecate (she calls her Kate) is her sister, Dr. Gerhauser.
\end{itemize}


\sceneHeadline{Hayley and Jaya }

Hayley gets a letter.  Soon after reading it, she goes to Jaya and asks her for clarification. Hayley wants to know if Jaya really was ordering her to be rude to Trenton.  Jaya appears to not remember this order at all, but realizes it's a good one and confirms it.  Jaya notices the letter which Hayley is holding in her hands and reaches for it.  Hayley uncharacteristically snatches it away before Jaya can touch it and backs away out of arm's reach, looking alarmed and saying it's personal.  She clutches the letter to her chest and eyes Jaya warily.



Jaya gets suspicious and says that if that letter is a love letter from Trenton, Hayley has to burn it.  Hayley nods but doesn't move to do anything to the letter, which earns her more suspicious looks from Jaya.  Jaya stresses again that she orders Hayley to burn Trenton's love letters.  All of them.  Right away.  As soon as she gets them.  Well, maybe not in front of Agent Morgan, but as soon as possible.  Haley looks a little relieved for some unknown reason, and nods again.



Jaya levels a measuring look at Hayley but doesn't say anything further.  Hayley waits a beat to make sure Jaya is done talking and then thanks her for the clarification and leaves.


\sceneHeadline{Oliver and Hayley }

Oliver approaches Hayley and asks her if she has had another test.  Hayley doesn't think so, but last time she had some memory loss so perhaps she just doesn't remember.  She asks if she's been gone for a long time without noticing and Oliver didn't think so.



He politely asks after her health and she happily tells him that she is almost completely free of using the brace and should be able to get rid of it entirely soon.  ``It's nice that you got a \textit{good }doctor,'' Oliver says (with a trace of bitterness/self-deprecation).  Hayley glances at his leg and nods in agreement.



Hayley asks Oliver if he really does go swimming or if he was just teasing her like Jaya and Jonah said he was.  He tells her that he really does go swimming in the cistern 15 floors down. She says wistfully that she's seen pools and they look like fun.  Oliver offers to see if he can take her swimming with him.  She looks a little confused by the offer but seems pleased.



The topic of Oliver's storming out of the debriefing comes up and Hayley is disapproving of his rudeness to Agent Morgan.  Oliver defends himself with ``sometimes the squeaky wheel gets the grease''.  Hayley seems horrified by this concept and on that awkward note they part ways.



{[}\hl{Interestingly, my memory/interpretation of this last bit is quite different.}\footnote{\textbf{Suko T }Feel free to amend it if you wish!  I don't mind, it will just make it better.  Two sides to that scene after all!  Anyhow this is fascinating.  To be fair, most things are over Hayley's head. :P  Here Hayley felt like she was being so daring in calling him on his rudeness to Agent Morgan (criticizing a Citizen's behavior?? Gasp!) and he doesn't even notice.  Heh.  Oddly she sort of understood the first part of what he was trying to get across, she just is having a huge problem understanding the second part.  23 years of learning to keep your head down (or it's slammed down for you) will not be easy to change.  But she's working on it! :)  -Suko \textsubscript{08/15/12 12:45am}} In character as Oliver, I didn't really notice the disapproval.  Oliver's main purpose in approaching Hayley was to help her understand his motivations in confronting Agent Morgan, and the (perceived) benefits of doing so since it got him additional information.  But, clearly this subtext was over her head. :)  - Adam {]}


\sceneHeadline{Jonah and Hayley }

Jonah approaches Hayley while she is exercising and asks her if she was hurt during the test.  Hayley promptly says no, she wasn't hurt, but she was a little dehydrated, and since she didn't get a chance to eat afterward, it took a little while to recover from that.  But nothing else.



She says her employer was upset that she got damaged on the last mission, which surprises Jonah.  Hayley doesn't understand his surprise since she is quite valuable.  He asks her if her employer sent her here (to the TA) to die.  Hayley says that she could have, but she did not. 



He asks her for a favor, and she asks, 'As a friend, or an ally?'' referring to one of their earlier conversations {[}that Ion and I had offline{]} where he explained the differences between the two.  Jonah thinks about it and gives her an honest answer, ``Both.''  She accepts this answer and nods her agreement.



Jonah then asks if she knows why they are here.  Or at least why she is here.  Rather than answering promptly like usual, she thinks very hard about something.  She asks if she can trust him.  He says yes, but his tone is hesitant.  That's good enough for her.  She leans in and says that the TA are leasing her contract from her employer.  They are paying a lot of money for it too.  She asks Jonah not to tell anyone because she thinks that may be a secret.  Secret from whom, she does not specify.



He says she has been helpful and Hayley looks very happy to hear this, smiling widely.


\sceneHeadline{Jonah, Oliver, and Hayley }

Jonah then goes to speak with Oliver.  Over a game of cards the two speculate on what is going on.  Early on in the card game, Jonah passes Oliver a card that has a note attached to it, ``I think they are listening to us.''



They talk about the experiments and a bit of what they've learned since.



Hayley arrives at the end of the card game and seems surprised and a bit thrown off to see the two of them in the room.  She awkwardly asks if they need help.  With, uh, anything.  She doesn't seem to actually have any idea of what they might need help with, and just stands there looking rather lost.  Oliver rescues her from floundering and suggests that now would be a good time for her to learn to break down and clean a rifle.  



Hayley looks cheered by the suggestion, saying that she is supposed to learn to use a real weapon.  Her earlier hesitation vanishes as she applies herself to the task of learning the parts of the rifle and how they fit together.  



They go to the ready line and practice shooting blanks and discuss gun safety.  Jonah and Oliver try to engage her in small talk but it is not terribly successful as her mind is focused on learning something new.  They suspect something is up with her but don't know what.


\sceneHeadline{Hayley and Dr. Gerhauser }

Jari finds Hayley and escorts her to MedBay for her requested appointment with Dr. Gerhauser.  Dr. Gerhauser is working and barely looks up to acknowledge Hayley's entrance into MedBay.



She asks to know what the experiments are.  She says that her employer didn't feel she understood what exactly they were going to do to Hayley.  Dr. Gerhauser pointedly asks, ``Did you ever think that maybe it was because your employer wasn't able to understand the explanation given to her?''

``Oh no, it couldn't be that, she's very smart,'' says Hayley confidently.

``Oh really?  And she knows about Bio-medical research?  Biology?  Physics?''

``No,'' says Hayley.  ``But if you could try to explain it again, that would be helpful.  Oh!  You should probably explain it to all of my squadmates, I'm sure they would be interested.''

``Why don't I just do a lecture?'' Dr. Gerhauser says sarcastically.

Hayley misses the tone entirely and looks delighted, ``Yes that would be great!  I learn a lot from lectures.''

Dr. Gerhauser rolls her eyes and asks, ``Is that all?''



Hayley tells Dr. Gerhauser that if she would tell Hayley more about what she expects from the tests, then Hayley would do better.  She brags that she's good at tests.  She knows her body well and she knows almost all of her baseline medical numbers.  For example, if she'd been told about the last test, she might have done better at it.  Dr. Gerhauser actually looks mildly intrigued and seems to fully pay attention to Hayley for the first time.  She asks Hayley about the test and they discuss how she might have done better.  She tells Hayley, ``Next time, don't drown and try to find air.''   Hayley says she'll try but that she was pretty sure there was no air in the box.  She says she remembers breaking her hands although she's not sure how much pain she felt since it's all a little hazy.  Hayley suddenly remembers something and asks Dr. Gerhauser why she (Hayley) was wearing a wig during the test.  This seems to make Dr. Gerhauser pause and look at Hayley curiously, but she doesn't answer Hayley's question.  She just tells her, ``next time try to take control of the situation.''



Hayley smiles with relief and says, ``Thank you, that helps a lot.  Thank you for clarifying that.''  Dr. Gerhauser seems a little taken aback by this response but lets it go, saying, ``Well like I said, I have lots of work to do.''  She turns back to her work and pointedly ignores Hayley.  Hayley asks again to confirm that Dr. Gerhauser will explain the experiments at some point.  Dr. Gerhauser makes an noncommittal noise and doesn't look up again.  Hayley waits to make sure that was a dismissal and then she leaves.


\sceneHeadline{Oliver and Dr. Gerhauser }

Oliver goes to MedBay to speak with Dr. Gerhauser.  He tries to call her Kate (or Hecate) but she ask him to call her Dr. Gerhauser.  Even if she doesn't technically have any authority over him.  He says that Agent Morgan is acting a bit more congenially, and asks if she intervened.  Dr. Gerhauser implies that she did intervene (\hl{``we have the same goals, but we approach them in different ways''}\footnote{\textbf{Suko T }Right!  I totally forgot this bit.  It's a really important line of dialog to have in here too.  Thanks! \textsubscript{08/15/12 12:46am}}) without admitting it.  Oliver thanks her for doing so.



Oliver mentions that his physical therapy is going well and voluntarily makes an appointment for a check-up.  He asks about whether any more tests have been done (with the tank) and she says no.  After a few more awkward exchanges, Oliver leaves.



\jumpHeadline{Quotes }  



``We're testing new equipment that will put us in missions. And we will \textit{handle }them.''

\extraIndent{- Jaya}


\quotedDialog{
``You can be skeptical while testing the equipment.  But you are still going to do this.  Is that clear?''

``Sure Chief.  Whatever you say.''
}
\extraIndent{                - Jaya and Jonah}



``Yeah well..you should see the other guy!  We, like, killed him.''

\extraIndent{- Jaya, defending her new war wound's badass-ness.}



``A desk job in {[}Jaya's{]} world is someone chucking a desk at her.''

\extraIndent{- Ion}



``You know.  Mind maps.  Maps of minds.''

\extraIndent{- Trenton, explaining what mind maps are to Jonah}

{[}GM Note: Actually, Trenton was saying\hl{'Mine'}\footnote{\textbf{Suko T }Suko Note: Huh, I heard ``Mine'' also. that's what I had originally, or at least what I meant to type if the typo is mine (heh).  I remember because I was thinking to myself that mine maps would actually be really useful. \textsubscript{08/15/12 12:44am}}\footnote{$\rightarrow$\textbf{q.google }Hah!  I really did hear ``mind maps''.  It didn't seem out of character for Trenton, so I didn't, er, map it back to what Jonah would have been more likely to hear. \textsubscript{09/02/12 10:45pm}}, so it's a bit ironic it was heard differently.{]}



``Well I got your drink, so I think you gotta show me yours first.''

\extraIndent{- Zara Thustra, to Jonah}


\quotedDialog{
``I'm not young and stupid you know.''

``Yeah, I know.  You're not young anymore.''
}
\extraIndent{- Riva and Jonah (who is being brotherly)}


\quotedDialog{
``They haven't killed me yet.''

``How do you handle it?''

``Handle what?  Knowing you might die?''

``Or worse.''

``Hmm.  You're right, worse IS worse. \textless Pauses to think\textgreater  At first I couldn't handle it.  It was hard.  I was scared and I screamed a lot.  Then I couldn't scream anymore since my voice gave out, and it didn't stop him anyway, so I had to do something else.''
}
\extraIndent{                - Hayley and Gillian}


\quotedDialog{
``As long as {[}the Filis{]} are alive, there is nothing that can be done!''

``Alright, at least there's an option then.''
}
\extraIndent{                - Gillian and Hayley}




\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/22/15 1:22pm
\end{flushright}

