\setcounter{chapter}{ 7 }
\chapter{\textbf{Terminus} }


\subChapterTitle{``a.k.a. Jaya's Terrible Horrible No Good Very Bad Day''} 

\deets{Suko}{Oct 19th, 2012}

Update (first cistern scene): Nov 1st, 2012



Jaya pretty much got kicked in the metaphorical teeth a lot, Oliver's Flaws caused problems for him and the team, and Hayley's fractured psyche is taking a beating.  Not so fun for the characters but hilarious and enjoyable for us!  We missed you Ion!



Please fill in the gaps and correct errors.  Also you should always feel free to add/correct the perspective of your character.



\noindent\hrulefill





 {\LARGE SAC-09 } 



Oliver slowly wakes up, feeling groggy and in pain.  He is lying in a hospital bed, and he is having trouble seeing clearly.  There appear to be bandages wrapped around his forehead, there's a deep pain in his chest and his leg is hurting worse than usual.  There are IV tubes attached to his arm.



When he struggles to sit up, hands press him back into the bed and a voice tells him ``Don't worry, you're safe.  Don't mess with your IV.''

``Where's Hayley?  Where's Jonah?'' slurs Oliver, still woozy.

The bed shifts as someone sits down next to him and a hand rests on his shoulder, both calming and keeping him from sitting up again.  ``Hayley is just over there.  Remember, stay calm.''

``What happened?'' asks Oliver.

``We don't know, we were hoping you could tell us.''



Oliver realizes that the person speaking is Dr. Gerhauser.  She tells him that Lackovich pulled us ``out of the drink''.  Oliver doesn't recognize Lackovich's name (at first).



Hayley wakes up as Dr. Gerhauser is speaking, but doesn't say anything once she realize who it is.  Hayley runs through her usual ``I don't know where I am or what happened but I seem to be injured'' system check: wiggling her toes, flexing her fingers, etc.  Her ribs and right thigh appear to be severely bruised, and she is a bit hazy as well.



Dr. Gerhauser checks Hayley over briefly and then turns back to talking to Oliver.  Still spacy from the sedatives, Oliver asks her if she could bring him some pie.  Like his mom's pie.  She almost cracks a smile and says she will do what she can.


\jumpHeadline{Bunker }

Meanwhile, Jaya wakes up in her bunk, with no memory of how she got there.  She feels very out of it and exhausted.  She staggers out of bed and realizes that she's fully dressed and in one hand she is clutching a bottle with two pills in it. She watches as the pills slide out of the bottle and bounce across the floor toward Oliver's bed.  She stumbles after them and takes them both.  As the numbness spreads, she collapse with a sigh of relief on the edge of Oliver's bed.



Eventually she staggers into the mess hall and Jari greets her.  As he's fixing her something to eat, Agent Morgan enters.  Jaya pushes herself to her feet and salutes, ``Sergeant!  Agent.  Sir.  Ma'am.''



Agent Morgan asks how Jaya is doing and if she is ready for a debriefing.  Jaya of course claims she is doing great and she's ready for the debrief.  She asks for some more pills, and is told to take that up with Dr. Gerhauser.  Jaya is not happy to learn that one of her teammates is in ICU, and is even unhappier to learn that it isn't Oliver.  



Oliver and Hayley are talking, trying to figure out what happened.  They can somewhat remember the scenes up to the opening of the domed vault in the glassed in room, but after that it gets hazy.  Oliver remembers running and noise.  Hayley remembers climbing and that everything went quiet.  Neither of them remember how they got injured.



Agent Morgan and Dr. Gerhauser drop by and quiz them on what they remember, but get nothing very useful.  Hayley asks about Jonah and is assured that he will recover.  Agent Morgan, with a faint air of annoyance, gives Oliver a gel pack, saying it's the closest thing to a sweet they have.  Oliver says to Agent Morgan, ``Tell whoever got this for me thank you.''  and sends a meaningful look at the doctor



Jaya debriefs with Agent Rook (to her relief). Agent Rook tells her that we were pulled out of the water. He confirms that the woman was still with us and that she is currently a prisoner at SAC-09.  He said that they aren't quite sure why Jaya thought she was so important. Jaya says that the woman seemed to be a combatant and in the middle of all this important stuff so she probably has lots of important information.  He tells Jaya that she has to write up a report on the mission.  This report will be submitted to Agent Morgan at 0800.  



Jaya goes in search of Jari to ask him to lead her to where Hayley and Oliver are.  Lackovich and young man walk into the room.  Jaya thanks Lackovich for helping save her team, which Lackovich stiffly acknowledges and then walks past Jaya, ending the conversation.  Jari leads Jaya to MedBay where Oliver and Hayley are recuperating.



Oliver is teaching Hayley to play 20 questions, which goes \hl{about as well as you might expect}\footnote{\textbf{Suko T }To my later amusement, it actually worked well for her later testimony- it reminded me how very literally she can take questions and how hard a simple yes/no can be for someone like that. \textsubscript{10/21/12 1:12am}}. Jaya arrives midway through the game.  She claims that we have to make a report as a team, and \hl{she asks Hayley to start transcribing a report as they talk through what happened}\footnote{\textbf{Adam Kenney }Oliver is jockeying to be the one to write the report (so he can deny the authorities the juicy details they desire) and is frustrated when Jaya appoints Hayley instead.  So he instead keeps changing the subject, derailing their narrative. \textsubscript{10/22/12 7:50pm}}\footnote{$\rightarrow$\textbf{Suko T }Heh! \textsubscript{10/22/12 10:18pm}}.  It's possible that ``Shit got real'' and ``Next time make sure to kill the person'' were on the list. :)



After 20 minutes, Medical Aide Swan tells Jaya that she needs to let the patients rest.  Frustrated, Jaya grabs the sheet of notes and leaves.  Oliver is given permission to resume his swimming therapy for his leg and he invites Hayley to join him.



A burly guard (the same one who usually escorts them) takes the two down to the Cistern.  Oliver looks away as Hayley casually strips off her hospital gown (completely naked underneath) and then stands at the edge of the water.  He can see there is something odd about her skin but he doesn't look closely enough to see what.  When he jokingly tells her to ``jump in'', she jumps in before he can finish with ``slowly''.  The water is much deeper than she thought and the shock of the cold makes her lose her breath.  As she sinks, it triggers a flashback to the nightmare of being trapped in the tank of goo and she panics.



Oliver rescues the flailing (and very naked) Hayley, and she clings to him, whimpering ``that she didn't like that at all''.  Both of them are breathing hard, for an assortment of reasons.  Holding her this closely, Oliver realizes that he can feel scar tissue under his fingers.  He ignores that while he concentrates on keeping Hayley from drowning again.  Once she is holding onto the wall, he lets her go and asks her, ``Are you okay?''



\hl{Hayley takes a few deep breaths and is suddenly much calmer}\footnote{\textbf{Suko T }Adam, please feel free to edit with Oliver's thoughts and reactions.  Given how delicate and complex some of the issues raised are, I didn't want to guess what Oliver's state of mind was unless you actually said so IG.  Personally, I thought he handled it quite well. :) \textsubscript{11/02/12 12:39am}}\footnote{$\rightarrow$\textbf{Adam Kenney }I think this writeup is very faithful - I actually don't have a lot to add re: Oliver's thoughts, since a) sometimes they are kind of mysterious to me, and b) you managed to capture a lot of the nuances I was trying to get across quite well.

I think the biggest effect of this scene on Oliver is bringing into the open, and making unavoidable, some of the problematic things about Hayley that he was trying to gloss over in a lot of their earlier interactions.  Because of his upbringing, he has a strongly ingrained instinct not to talk about his (or other peoples') problems, so he can't really tackle this kind of situation head on.  So, much subject-changing resulted, but still tinged by the suppressed emotions. \textsubscript{11/04/12 4:29pm}}\footnote{$\rightarrow$\textbf{Suko T }Stiff upper lip, eh?  whatwhat?  :)  Yes I totally get that (dear lord, look at Oliver's PARENTS).  Hayley is a terrible compliment to that because she's been trained not to ask personal questions of her superiors... which is pretty much everyone. I only recently started having her ask about other people's health and well being because honestly, she never really cared/noticed before.  Indeed, I'm rather surprised that we managed to get this far without her Flaws and emotional issues coming up.  I do appreciate you indulging in playing this out, it was very character-important for me. :) \textsubscript{11/04/12 4:48pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Hahaha, yes, Oliver's parents.  Wow.  Talk about a bad situation that just keeps getting worse.

But yeah, I'm glad we played out the scene.  It was interesting and dramatically rich, and I think it will keep having interesting/weird effects on Oliver and Hayley's dynamic.  Thank you! \textsubscript{11/04/12 5:18pm}}\footnote{$\rightarrow$\textbf{Suko T }It's sad that Jaya's home life is like the happiest and most stable/normal of all of us.  

Glad you found the scene interesting too. Yes the dynamic is going to be weird and I'm excited to see how that will affect things given what could potentially be happening.  Also given what is going on with Jonah and Jaya's going to come back and go WTF GUYS, I leave for a week and you all get smacked with the angst fish! :D \textsubscript{11/04/12 8:03pm}}.  Almost abnormally calm, given how freaked out she was just seconds ago.  Her breathing is normal and unhurried, her eyes are no longer wide with panic.  She smiles, ``Yes, thank you.  Is that swimming?  I don't like it.''



As the ripples in the water smooth out, Oliver can see Hayley's body more clearly now.  Her torso is covered in scars.  They cover her from shoulder to shoulder, clavicles to thigh, front and back.  The ugly purpling bruises on her ribcage probably make several of them look even worse than they are.  The scars are varied- some are thin almost delicate tattoo-like patterns, like someone was carving abstract designs into her skin with a scalpel, others are burn scars.  Bits of her skin have been neatly removed and new skin grown back.  There are puckered patches of various sizes that are likely puncture and stab wounds, possibly a small caliber gunshot wound.  Some of the scars overlay the others, and they are all completely healed.



Oliver asks again with a bit more emphasis, ``But are you \textit{okay}?'' Hayley still doesn't realize what he's talking about and tells him that the drowning reminded her of her nightmare and she panicked.  She apologizes for panicking.



Oliver asks Hayley to turn around and she does without hesitation.  He places a hand on her back.  \hl{She goes very still but does not move away, tense or flinch}\footnote{\textbf{Suko T }I spelled this out because I was trying convey how much Hayley instinctively trusts Oliver.  He's like her protective big brother.  Or at least that's the vibe I've been working off of.  Though I imagine it's just happenstance, he has done several very actively protective things that not even Hayley could miss. Like keeping her from plunging down the Shaft when she fell, killing the guy who tried to attack her in the Plaza, pulling her out of danger in SAC-01. \textsubscript{11/02/12 1:27am}}\footnote{$\rightarrow$\textbf{Adam Kenney }They definitely have a big brother / little sister dynamic.  He kind of realizes at this point that she has no idea what the heck she's doing, and will follow orders unquestioningly, and that combination is pretty alarming. \textsubscript{11/04/12 4:31pm}}\footnote{$\rightarrow$\textbf{Suko T }Jonah tipped onto this early on and was likewise alarmed.  And this is Hayley *after* Jonah coached her on pausing to think a second before rushing into certain harm/death. :D  Of course he phrased it as ``if you rush out and get hurt, then *I* have to run out and help you and I could get hurt too''.  Which actually worked better than any other reasoning. \textsubscript{11/04/12 4:51pm}}\footnote{$\rightarrow$\textbf{q.google }It was a deliberate decision on Jonah's part. Trying to get Hayley to care about herself doesn't work very well, but making her feel like she has an obligation works better.  (It's a big deal for Jonah to have put it like that, because it admits to a vulnerability.  I don't think he would have said that to anyone else, or even to Hayley with anyone else around.) \textsubscript{11/28/12 11:23am}}\footnote{$\rightarrow$\textbf{Suko T }Verrry smart of Jonah.  That's a very reliable way to motivate her. And his vulnerability is safe with Hayley- it wouldn't even occur to her that it was a vulnerability because he's a doctor and Doctors are Important and of course they shouldn't be put in situations where they might get hurt. \textsubscript{11/28/12 11:20pm}}. He asks, ``What \textit{happened }to you?''



Hayley starts to answer but he can feel the moment she realizes what he is talking about.  Her back tenses and she gasps a little.  She twists around to look at him, eyes wide and distressed again.  ``I forgot!''  Another pause.  ``I can trust you, right?''  Oliver says yes.  Hayley continues anxiously, ``I'm not supposed to let anyone see.  You won't tell?''  Oliver has to reassure her twice that he won't tell before she seems to calm down.  



Hayley then asks him, ``You won't like me less because I'm not perfect, will you?''

``I might like you more,'' replies Oliver with an expression \hl{Hayley can't read}\footnote{\textbf{Suko T }To be fair, that's most expressions, but mixed emotions are particularly difficult for her. \textsubscript{11/02/12 12:38am}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{11/04/12 4:31pm}}.

``You are very strange,'' says Hayley.  When Oliver looks away and an awkward pause stretches out, Hayley adds earnestly, ``They are mostly healed, if that is what you are worried about.''  Oliver is blushing, although it is hard to see in the dim light.



Oliver patiently shows Hayley how to tread water. While she practices, Hayley asks if the swimming is helping his leg, and Oliver says that he mostly does it to get away from everybody.  \hl{Hayley immediately offers to leave, but Oliver says that she isn't everybody.}\footnote{\textbf{Adam Kenney }Just wait until Oliver gets to amend this statement next session!  It's going to be awesome...ly squalid. \textsubscript{11/04/12 5:47pm}}\footnote{$\rightarrow$\textbf{Suko T }And it's likely to just get worse from there.  I can't wait! :D  Mmmm... squalor.... \textsubscript{11/04/12 8:04pm}}  Hayley nods with understanding.  But they don't stay in the water long after that.  They cover up with towels and head to the elevator. 



They talk about Oliver's leg again and the subject of him dying and coming back comes up.  Hayley curiously asks what it was like.  Oliver says he doesn't remember but ``if you know what it was like, you probably don't get to come back.''  Hayley says that she thinks about it {[}death{]} all the time.  When Oliver looks inquiring, she elaborates, ``because it was my purpose.''  Then she then looks alarmed again and says that she's not supposed to talk about that either.  Oliver says that she doesn't have to talk about it if she doesn't want to, which relieves her. She complains about having to remember so many rules.  Hayley says that she is glad that Oliver isn't dead, it would be sad if he died.  Oliver \hl{looks away and says nothing}\footnote{\textbf{Suko T }Tragic Hero pose \#4 \textsubscript{11/02/12 1:04am}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{11/04/12 4:31pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }There was an awful lot of this. \textsubscript{11/04/12 5:46pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/04/12 8:05pm}}.



They ride the elevator up to the MedBay level, just wearing towels.  Oliver says that he's not returning to MedBay, he's going back to his bunk.  Hayley hesitates for a moment but then decides to return to MedBay.  



Oliver returns to their bunk and finds Jaya there.  They butt heads for a while but eventually Jaya backs down when Oliver offers to write the report.  Grudgingly she offers to get him something to eat and then vanishes for a really long time.  Oliver throws away the page of notes that Hayley started and that Jaya had laboriously added a few extra lines to, and starts fresh.  \hl{He writes a carefully crafted report that goes into excessive detail on certain actions and descriptions, but glosses over certain other events such as the details of how we attacked Jayce}\footnote{\textbf{q.google }The absent Jonah approves thoroughly. \textsubscript{10/23/12 1:14pm}}.  He describes the Water Rats in detail and says they are territorial.  On the way to the Shaft, he says we were attacked and that he shot and killed the attacker, but the details are a little thin and the altercation with Jayce is entirely left out.  He describes in detail the train station area, the tunnel and the bat attack.  He is less detailed in how we got into the compound and the details within the compound are not complete.  He describes the medical symbol (caduceus) in detail, and the voice that we heard.  He talks about spotting the guns/cameras and searching through the space.  He mentions resistance from ``locals'' and describes the woman in detail (since they already have her, there was no reason not to).  He very deliberately does not mention the man.



While he is writing the report, a short woman with hair pulled back in a bun and a TA uniform knocks on the door.  She is Constable Carruthers and is part of Patrol Group 2, which is led by Lackovich.  Carruthers has a rather shy and nervous demeanor.  She has a letter that she says was delivered to his house and then brought here.  Oliver thanks her and she leaves.  He does not open the letter and instead places it under his pillow. (It had been a very long day.)



Jaya comes back after Oliver finishes the report and stomps around trying to find it (he'd gone to sleep in another bunk since Jaya messed up his during her pill-fueled stupor).  Oliver wakes up enough to tell her that he put it under her pillow.  After annoying him by putting his food on his bed, Jaya puts the food she brought for him on the table and she reads through the report so she knows what is in it.  She is very pleased with what she reads, although her running commentary annoys Oliver.



In the morning, several minutes before 0800, Jaya heads off to the Ops room to give ``her'' report.  Oliver is still sleeping.  On the way there, she is surprised by Tech Larissa, who is escorting Hayley to the room as well.  Larissa says that she was under the impression that Jaya's whole team (well minus Jonah) were going to be assembling.



Jaya enters the room with just Hayley and they sit down across from Agent Morgan (the tech sits nearby).  Jaya submits her report and Agent Morgan reads through it.  Agent Morgan makes a note to Larissa to send a handbook to Senior Constable Pavardi, and then pointedly asks Jaya why her team is not assembled.  



Jaya goes to fetch Oliver, leaving Hayley to sit there alone with Agent Morgan and Tech Larissa.  On the way, Jaya runs into Lackovich, or rather Lackovich runs into Jaya.  They have a small pissing contest in the hall.  When Lackovich deliberately shoulder checks Jaya, Jaya pulls a street brawling move and falls into her- elbow first.  Mutual dislike well-established, Jaya moves on to find Oliver in our dorm.  Oliver gets dressed.  While he's getting ready, Jaya waits in the hall and \hl{speaks with a guy}\footnote{\textbf{Suko T }I missed this conversation, what did you say? \textsubscript{10/21/12 2:28am}}\footnote{$\rightarrow$\textbf{Adam Kenney }I think she warmed up to him when she found out he has a tattoo, although they weren't on close enough terms yet for him to undress and show it to her. \textsubscript{10/22/12 7:56pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Five o'clock shadow guy!! :D  He complimented her on her ink to start with. \textsubscript{10/23/12 12:34am}}with a 5 o'clock shadow. He bounces a small rubber ball as they talk. 



When Oliver is ready, they walk back.  As they pass one of the other dorm rooms the door opens and Lackovich walks out.  Oliver sees her and turns sheet white, like he's seen a ghost.



When they return to Ops, they sit down across from Morgan and she starts by apologizing for the actions of Patrol Group 2.  The measures taken were necessary but have had repercussions.  Hayley asks what measures and how were they injured.  Oliver had a concussion, leg damage and had drowned (lung damage). He had been dosed with neurotoxins that were necessary to bring him back from clinical death.  Hayley had injuries to her side and leg, and was likewise drowning but had not died yet (we find out at this point or later that she was also given something similar to the neurotoxins given to Oliver).  Jonah is still in critical condition and very injured.  Jaya was less injured and released under her own recognizance.



Agent Morgan excuses Larissa from the room and then tells Oliver, Hayley and Jaya that they have an opportunity to get increased security access.  We would have to abide by the Directorate Security Act, but we would have nearly full access to all of SAC-09 (places like the Brig would be excluded).  



Oliver says that the spaces that he has access to now are sufficient for his needs, but what would be really enticing would be extra shore leave.  Agent Morgan seems surprised but agrees that this would be an acceptable option.



Agent Morgan says that we will be meeting with the Security Triumvirate (which is a political/senatorial group, so Hayley and Oliver recognize their name right away and are suitably impressed).  We are going to be cross examined. During this cross examination we are to leave out any speculation on the nature of the slides (and I think also symbols we encountered?), do not mention the woman or the man, do not mention Patrol Group 2 (say we extracted ourselves from the situation unaided), and do not mention the specific location we were at.



Oliver asks about the woman.  Agent Morgan confirms that she is a prisoner, and that Oliver's suspicions were correct, the woman is a soldier.  No one knows the language she speaks.  \hl{Agent Morgan says that the woman is somewhat the equivalent in position and responsibilities as Jaya is.}\footnote{\textbf{Nathaniel Ford }I really don't remember saying this, but it's possible I did. \textsubscript{10/22/12 4:53pm}}\footnote{$\rightarrow$\textbf{Suko T }It was while Jaya was bragging on how easy it was to subdue the woman and I think you (as AM) said something like ``you should be more respectful of {[}the woman{]} because she's like you, with similar responsibilities and you would not have done so well if you were in her place''. Jaya vehemently denied this of course.  Feel free to modify or remove if that was not your intent. :) \textsubscript{10/22/12 5:04pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }Ah, yes. I recall how that went, specifically now. (Sometimes I have difficulty reconciling the thoughts I was having whilst saying something and the notes about what was said.) \textsubscript{10/23/12 12:00pm}}\footnote{$\rightarrow$\textbf{q.google }Hehe.  That's a very interesting problem, not just in games :). \textsubscript{10/23/12 1:23pm}}  She mentions that the woman had to go from a static state to an active one very quickly.  Feeling as though her reputation was being besmirched, Jaya trash-talks the woman a little and Agent Morgan is displeased at the disrespect. 



Oliver asks to get a copy of the report that Jaya \hl{``wrote''}\footnote{\textbf{Suko T }what a team player! \textsubscript{10/21/12 2:30am}}\footnote{$\rightarrow$\textbf{Adam Kenney }I wish Google Doc comments had a ``like'' button. \textsubscript{10/22/12 7:57pm}}\footnote{$\rightarrow$\textbf{q.google }.  Or perhaps given that this is \_Google\_ docs: +1. \textsubscript{10/23/12 1:26pm}} so he could study it.  Agent Morgan gives the original to him and tells him to make three copies and return two of them to her.



They leave Ops and see Patrol Group 2 (Lackovich ``Plain Jane'', Carruthers, the guy Jaya ran into earlier, and a burly guy with tattoos on his neck), smartly assembled in the hallway, all of them neatly dressed and looking textbook-perfect.  Even Jaya can't miss the contrast between the two Patrol Groups and \hl{can see that her Patrol is not showing to advantage}\footnote{\textbf{q.google }''Chief, you realize that's only because they haven't gone any actual \_missions\_, right?'' \textsubscript{10/23/12 1:27pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{10/24/12 9:06am}}.  



To make things even better, we return to our bunks to find Trenton sitting there, holding a letter over his head.  He taunts Oliver with it, who snatches the letter back.  Jaya yells at Trenton to get out.  Trenton says that he's the one who triangulated the position of our radios (using math!) and enabled Patrol Group 2 to find us and rescue us.  Jaya doesn't believe him (or doesn't want to be indebted to him), and again yells at him to leave.  Trenton leaves but Hayley follows him out.  She asks him, ``Is she okay?''  Once Trenton realizes who she is talking about, he tells her that Hayley should go visit Signe sometime.  Hayley says she would like to, but she doesn't think it is possible. 



Their conversation is cut short by Jaya.  She just realized who Hayley is talking to and comes out into the hallway to get Hayley away from Trenton.  Trenton seems amused.  He curls his hand around the back of Hayley's head and kisses her on the forehead, as Jaya drags Hayley into the dorm room.  Hayley seems to barely register the kiss, other than to flick Trenton a confused look.  She apologizes to Jaya for forgetting to follow her order to be rude to Trenton.  Jaya is upset and orders Hayley to stop talking to Trenton altogether.  \hl{This is one thing Oliver can agree with}\footnote{\textbf{q.google }We call this a Fundamental Universal Constant. \textsubscript{10/23/12 1:29pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }?? \textsubscript{10/24/12 9:06am}}\footnote{$\rightarrow$\textbf{q.google }Anything Jaya and Oliver agree on must be something it isn't actually possible to disagree with.  Hence enforced by the fundamentals of the universe. \textsubscript{11/28/12 11:39am}} and he and Jaya scold Hayley for ``trusting that low life scumbag''.  This upsets Hayley and she asks why she can't talk to Trenton.  Jaya starts ranting about over-privileged spoiled Citizens, which pisses off Oliver and he brings up his less-than-idyllic life to prove Jaya wrong.  Hayley asks why they both seemed to hate Trenton so much.  Jaya reels off a list of colorful descriptors and name-calling, getting so worked up she can barely speak coherently.  Hayley looks more distressed and says that Trenton is nice, helpful and really smart, so why all the hate?   \hl{Oliver says he could possibly have misjudged Trenton's character but his tone seems to indicate that he's pretty sure Trenton is scum.}\footnote{\textbf{Adam Kenney }This is how Citizens deal with their social problems. \textsubscript{10/22/12 7:59pm}}\footnote{$\rightarrow$\textbf{Suko T }Heh.  Poor tone-deaf Hayley, she thinks that Oliver will be nicer to Trenton now.  She's bound for disappointment. :) \textsubscript{10/22/12 10:30pm}}



When asked why she needs to talk to Trenton, Hayley tells them that Signe, her friend, asked her to help Trenton.  Oliver suggests that Signe was lying to Hayley which Hayley denies, insisting that Signe would never lie to her.  Jaya says that Trenton is using Hayley and Hayley has to stop seeing him. Hayley asks Jaya to reconsider the order, a note of pleading in her voice, but Jaya firmly reiterates her order.  Hayley nods but looks unhappy.



Jaya sends Hayley to go get something for her to eat.  \hl{Jari teaches Hayley how to make an egg-and-potato hash}\footnote{\textbf{q.google }Ah-HA!  \_Now\_ we get to the important part. \textsubscript{10/23/12 1:33pm}}.  Hayley mangles several eggs, and Jari tells her to not tell Agent Morgan because the budget for potatoes and eggs is carefully monitored.  



Oliver makes copies of the reports and leaves out the items that Agent Morgan told them not to talk about.  He gives a copy of this amended report to Jaya and Hayley (when she returns with Jaya's food) and tells them to read them and memorize them before their cross examination.  This is the ``official report''.



Oliver reads the letter, which turns out to be from the Orc of Anglia.  It has veiled but unmistakable threats to Oliver's parents' continuing well-being.



Oliver leaves to give the copies to agent Morgan and asks to speak to her.  He is escorted to her office.  {[}\textit{Ongoing Challenge: Gerhauser Sisters}{]}.  He tells her about the letter and that he intends to ``finish what he started.''  He implies that this is why he requested extra shore leave -- to start hunting the Orc.



Agent Morgan tells him that the Orc is suspected of assassinating over 2 scores of people, over 5 city-states.  In open combat, his body count is even higher.



Oliver says that since he's going to die anyway, he might as well do some good.  Now that Agent Morgan has the much more capable Patrol Group 2, his group is no longer needed.  Agent Morgan denies that his group is obsolete and asks him if he trusts his team.  He says he trusts everyone but Jonah, and \hl{then clarifies that he doesn't trust Jonah, but he likes him}\footnote{\textbf{q.google }Awwwww!  Spoken like a true comrade-in-arms :). \textsubscript{10/23/12 1:36pm}}.  He trusts Jaya, but doesn't like her.  \hl{He doesn't mention his opinion on Hayley}\footnote{\textbf{Suko T }at least so far as I recall although my notes are a bit sketchy in this spot with all the dialog going on \textsubscript{10/21/12 2:56am}}\footnote{$\rightarrow$\textbf{Adam Kenney }I think he said that he trusts everyone but Jonah.  Then he clarified with the bit about liking/not trusting, trusting/not liking. \textsubscript{10/22/12 8:01pm}}\footnote{$\rightarrow$\textbf{Suko T }Oh right!  I forgot the first bit.  I even chuckled about it because it was a pity Ion wasn't there to hear it :D \textsubscript{10/22/12 10:19pm}}\footnote{$\rightarrow$\textbf{q.google }Suko and I have had several conversations about this issue of trust vs liking (or allies vs friends) at this point both IG and OOG.  The distinction between what Oliver is calling trust and what Jonah would call trust has proved very insightful for me.  One of the surprising consequences was realizing that Jonah's reaction to learning that Oliver likes but doesn't trust him, would be to \_trust Oliver more\_. \textsubscript{11/28/12 11:47am}}\footnote{$\rightarrow$\textbf{Adam Kenney }Oliver tends to trust people when he can read them.  He doesn't have to understand their thought processes or reasoning, but if he feels like he has a sense of how they're reacting to things and what their emotional positioning is towards him, then he will tend to trust them.  An odd definition of trust by most means.  Probably comes out of having parents whose projected attitude towards him is sometimes very different from their real emotions/thoughts. \textsubscript{11/28/12 2:23pm}}\footnote{$\rightarrow$\textbf{q.google }I must revise what I said then because that's mostly Jonah's definition.  He also tends to trust people when he can read them, though he's less worried about their attitude towards him and more about what they want, and how they are likely to act under stress.

The distinction between liking and trusting is still very interesting.  The two are \_very\_ distinct for Jonah. \textsubscript{11/30/12 1:10pm}}\footnote{$\rightarrow$\textbf{Suko T }''An odd definition of trust by most means.''
Hmm, I don't know that it's an odd definition of trust as it makes sense, both for the character and in general.

Hayley's so bad at reading people these measures used by Oliver and Jonah really aren't available to her.  Plus her bar for trust and liking is so extremely low that it hardly matters anyway. :P  But probably a lot like Oliver and Jonah, she has dozens of gradations of trust levels (emotional/physical/social/professional/personal).  The list of people she highly trusts on multiple levels is a VERY short list (I expect that's the same for paranoid Jonah as well :) ). \textsubscript{11/30/12 3:53pm}}.



Oliver asks Agent Morgan what she would do if she was going to go about stopping the Orc -- with all the resources she currently has.  She thinks for a moment and says that she would send someone out as bait to lure the Orc out into the open and then kill him.  The bait would likely die.   Oliver replies, ``Well, if I had been you... and if I had sent me out as bait to lure the Orc out into the open and then kill him..\hl{. I would at least have told me to shoot for the head.''}\footnote{\textbf{Suko T }So dramatic. \textsubscript{10/22/12 10:22pm}}\footnote{$\rightarrow$\textbf{q.google }Zing!

And by ``Zing!'' I mean ``hell yeah, you tell her brother''.  I think what Jonah resents about the higher ups is not having our lives risked by being sent on dangerous missions, but having our lives risked \_unnecessarily\_ by not getting enough information.  (I realize OOG this is deliberate.  But it's fun to see pushback, and one of the reasons Jonah likes Oliver is Oliver can say these things.) \textsubscript{10/23/12 1:39pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Yes, that's one of Oliver's big beefs as well.  Out of game I really enjoy it because it creates a great power / emotion dynamic between the squad and the higher ups.  It also reflects the fact that in complicated real world situations, the higher ups are often acting with imperfect information; and they won't necessarily disclose everything to everyone (for good reasons). \textsubscript{11/28/12 2:25pm}}\footnote{$\rightarrow$\textbf{q.google }''That's one of Oliver's big beefs as well.''
Clearly.  Oliver makes that very obvious.  There's a constant strong reminder about the difference in social status between Citizens and others in him being able to do so. \textsubscript{11/30/12 1:13pm}}\footnote{$\rightarrow$\textbf{Suko T }Indeed, that's what makes it so nice we have a representation of all social levels in the party.  More than just having a Franchise ordering around a Citizen, it's neat the way it plays out with other people too. \textsubscript{11/30/12 3:27pm}}



As Oliver leaves, Agent Morgan says, ``\hl{I can see what my sister sees in you}\footnote{\textbf{q.google }That sounds profound ... but I have \_no idea\_ if it's a good or a bad thing. \textsubscript{10/23/12 1:40pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }I'm not sure if it came through in the notes, but Hecate and Oliver have been continuing to come onto each other - in their respective halting, damaged ways.  (The convalescent / apple pie scene; the non-Hayley cistern scene.)  I took Agent Morgan's line as having a subtext that Hecate's affections can be revoked if Oliver steps out of line. \textsubscript{10/24/12 9:10am}}.''



 {\LARGE Terminus } 



Back at the bunks, Agent Rook wakes up Jaya at 0500. He's in his dress uniform and he hands her a dress uniform also.  Jaya attempts to scramble to attention, and Rook informs her that she and her team have 3 hours to get ready to leave for Terminus.



The team gets showered and dressed, and makes it to the ready line in time.  They get on the train, and to Jaya's displeasure, Agent Morgan is coming with them.  Jaya was telling a colorful story about a card game that she won when Agent Morgan joins the conversation and tells her to continue the story.  Jaya gets rather jittery under Agent Morgan's terrifyingly polite attention.  During the ride, Hayley asks Agent Morgan why there's that moment of nausea.  Agent Morgan says that when you take the train often enough, you get used to it.  Jaya is starting to perspire heavily.  The train passes Enmann (sp?) Station in Cardoza and stops in Terminus, the Seat of the Directorate.



As they walk from the train, Hayley catches the eye of a man who does a double take and flushes with embarrassment when he recognizes her.  \hl{Oliver notices.}\footnote{\textbf{Suko T }given the amended cistern scene, this bit may be more informative/distressing to Oliver than it was before \textsubscript{11/02/12 12:56am}}\footnote{$\rightarrow$\textbf{Adam Kenney }Ack. \textsubscript{11/06/12 4:17pm}}



Once they get to the capitol building, they are escorted through a maze of passages to a nicely appointed sitting room and are told to wait.  It would be a library but there are no books.  Several other people are in the room.   



Jaya is in serious panic mode now and asks to go to the ladies' room.  On the way there, Jaya recognizes the gorgeous Anglia woman that she met in DX Station, Octavia.  Octavia recognizes Jaya and gets up to speak to her.  She greets her kindly and escorts Jaya to the ladies' room.  Over Octavia's shoulder, Jaya can see that Agent Morgan is quietly furious and Jaya is getting the death stare.  Jaya is terrified and locks herself in a stall and shakily smokes a cigarette while trying to figure out what to do.  



Jaya takes so long that Hayley is sent after Jaya to fetch her back.  On the way, Hayley is pulled aside by her contract holder, Gillian Vorrutyer. Gillian is glad that she caught Hayley in time and tells her that she and Agent Morgan have spoken and it is imperative that Hayley report that her contract is a normal contract.  Hayley nods and says that she assumes this applies to her other contracts too.  Gillian seems a little alarmed that she forgot that possible loophole and repeats the order and instructions again with urgent emphasis.  Hayley patiently agrees again, trying to reassure Gillian that she understands.  Gillian calms down a little.  Knowing that their time is limited, Hayley quickly tells Gillian that her reports may get a lot thinner from here out because she's being given a higher level of security clearance and that comes with some agreements on what not to say.  She says that Agent Morgan should hopefully have spoken to Gillian about this.  Gillian waves off Hayley's concerns, saying it will be fine.  Hayley tells her that she has a new friend, Signe, the one who wrote the letter that Hayley showed her.  This seems to please Gillian.  As Gillian rushes off, Hayley pleads with her to stay safe and be careful.  Gillian seems touched by Hayley's concern and tells her she's sweet.



Hayley finds Octavia in the ladies room but before they can speak more than a simple greeting, Jaya barrels out of the stall, grabs Hayley and says she has to go back now.  Meanwhile Agent Morgan points out that Oliver's father is in the room.  Oliver chooses to not go speak to him and hopes that his father doesn't notice him.  Agent Morgan asks why, and Oliver says that people aren't called to speak to the Security Triumvirate because they've done well.  To his surprise, Agent Morgan reveals that Oliver's father has been called here several times, in connection to the incident in Cardoza and Cyril Magnin.  She adds that those who knew Cyril have worked very hard to distance themselves from the whole mess and some have been faster at it than others.



Hayley and Jaya return to the room just in time to get summoned to see the Security Triumvirate.  By this point Jaya's dress uniform has turned a darker color as it is completely soaked through with sweat.  She is perspiring heavily and looks faintly ill.



We are led to a room with a raised semi-circular bench, with three people in senatorial robes sitting there.  They are backlit and hard to see clearly.  In front of them is a table and three chairs.  Morgan motions for us to stay back and sits in the central chair.  Senator Marechenko says that under Prop 3072.78 article 709.C, Morgan is requesting \hl{additional security clearance}\footnote{\textbf{Nathaniel Ford }That wasn't exactly what she requested. \textsubscript{10/22/12 5:00pm}}\footnote{$\rightarrow$\textbf{Suko T }higher level security clearance would be better?  Or is there a specific term you prefer? \textsubscript{10/22/12 5:12pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }I thought she was playing the ``I need more funds'' game? \textsubscript{10/23/12 12:45am}}\footnote{$\rightarrow$\textbf{Suko T }Could be!  Feel free to amend. :) \textsubscript{10/23/12 12:50am}} for her team.



Marechenko says that in a vote of 2 to 1, they concur.  They have read the report and will now begin the cross examination.  Senator Bennett excuses Morgan.



Jaya sits in the center chair and Hayley and Oliver sit on either side of her.  We introduce ourselves, and Jaya is so nervous she mangles her own name.  The senators ask if we have anything to add about the symbology found.  Oliver takes this one and describes the caduceus in detail, saying that he believes it had to do with regeneration of tissues and nerves.  When the senators question his interpretation, Oliver says that he's pretty certain it's true because ``how else were the guards able to survive so long in the tanks.''



There is a pregnant pause while Jaya and Hayley try not to stare at Oliver in horror and astonishment.  After he'd been so careful to coach them on what to say, he blurted it out in the first minute?  {[}Yay flaws!{]}



The senators pounce and Oliver and Jaya frantically backpedal and try to defuse the situation.  First Oliver tries to convince them that it's not important, they were just some guards, so that's why they weren't mentioned in the report.  Then Jaya mentions the locals in the area and how hostile they were.  Oliver picks up that thread and says that the guards were locals.  There is a tense moment when they all (Hayley included) are required to swear that they think the guards were local vermin.  Oliver does so readily. Jaya stumbles through it, \hl{saying that since one of her team members is still in a coma, perhaps her report is not entirely complete so this is what she says for now}\footnote{\textbf{q.google }Heh.  I wonder if anyone will think to actually brief said team member when he wakes up.  That will be ``interesting''. \textsubscript{10/23/12 1:50pm}}\footnote{$\rightarrow$\textbf{Suko T }I suspect it could be like Rashomon- Jonah could get three very different stories of how everything went :) \textsubscript{10/23/12 3:57pm}}.  Hayley uses \hl{the bimbo defense}\footnote{\textbf{Nathaniel Ford }''The Bimbo Defense'' now has legal precedent! \textsubscript{10/22/12 5:02pm}}\footnote{$\rightarrow$\textbf{Suko T }Excellent, I expect it will be used again in the future :) \textsubscript{10/22/12 5:12pm}} and says, ``It's possible, but I'm not very smart.''



The senators ask if we think the technology is greater than that of Anglia, and if we saw signs of other interests in the area.  Oliver says yes to the first and all three say no to the second question. 



Senator Marechenko says that Jaya, Oliver and Hayley appear to have acted in the interests of the Directorate.  They excuse Oliver and Hayley.



Jaya is told that this will now be ``off the record''.  She is asked if she fully supports the mission of SAC-09.  In halting, stumbling language, Jaya says that she supports the mission, at least what part of the mission she has been told about.  They confirm that she's not a Citizen, and emphasize to her that if any of this should come to light, it would make things very difficult with our allies in Anglia.



The senators excuse Jaya and call in Oliver.  This is also off the record.  They say that Patrol Group 1 has retrieved many things of benefit to the Directorate and thank him for his service.  They ask if he is happy as a Constable and how does he feel about his current assignment?  He says something noncommittal.  They inquire more deeply and he asks if this is still off the record.  They ask why that matters and he replies that if he's sworn to tell the truth, then he's been taught that if you can't say something nice, it's better not to say anything at all.



Senator Bennett says, half to Oliver, half to Marechenko, ``Your father is James Langdon, correct?''  Oliver confirms it. {[}They say something else that I failed to write down legibly.{]}  They note Oliver's 2 years of service, and then excuse him.



Hayley is called in, and she gets up from where she was helping calm Jaya down so she didn't puke all over the floor.  Hayley walks in and waits until one of the senators impatiently tells her to sit down.  She sits.  They ask her if she has ever been ask to do anything that violates her contract.  Hayley easily and firmly says, ``No.''  They pry a bit about injury but she seems unconcerned.  They ask if there are any details missing from the report.  Hayley doesn't answer immediately and the silence stretches out for several heartbeats.  Hayley says slowly and uncertainly, ``Maybe, could you repeat the question?''  The senators repeat it, perhaps with a bit of eagerness.  Hayley, in a more assured voice, says that she can't answer the question because there are several people on her team and each one experienced something different, and so there will always be details left out of any report.  Is that what they meant?  They ask if any \textit{significant} details were omitted, but without getting a more satisfying answer.  With some annoyance and frustration (and probably some disgust at her idiocy), they excuse Hayley and call in Agent Morgan.



When Agent Morgan is called back into the room, Jaya runs for the ladies' room with Hayley trailing after her.  Hayley runs into Octavia again and they exchange names and a friendly handshake.  Hayley says that she has to go help her Senior Constable.  Octavia asks if Jaya is alright, and Hayley says yes, she just is freshening up.



Hayley and Jaya return to the waiting room just before Agent Morgan is excused from the cross examination room.  They head back to the train.  Hayley lags behind a half step, clearly looking around for someone.  When they get to the train, Jaya collapses into one of the seats on the train in relief.  Morgan also seems relieved.  Oliver asks how they did and Morgan gives him a slightly hard time, but overall goes easy on him.  Hayley stares out the window, but as they pull away from the station, she sighs with disappointment.  Morgan interrogates Jaya angrily about Octavia.  Jaya protests that she doesn't know her and didn't seek her out.  Hayley, unhelpfully, says that Octavia seems to like Jaya and asked after her health.  Jaya asks who Octavia is, and Morgan says that all she knows is that Octavia is from Anglia.  She doesn't know anything else about her.  



 {\LARGE SAC-09 } 



They return to SAC-09.  Oliver goes immediately to swim in the Cistern, where Dr. Gerhauser finds him.  She takes off her boots and dips her feet in the water while he remains awkwardly naked in the water.  {[}\textit{Ongoing Challenge: Gerhauser sisters}{]}  After some awkward introductory comments, Oliver asks her why she became a doctor.  The question evokes a very strong reaction and she finally says, ``My sister.''  Then she talks about doing things that are needed for the common good and making sacrifices.  Oliver sympathizes whole-heartedly.



Jaya meets with Dr. Gerhauser and asks about Jonah.  Dr. Gerhauser is confident that Jonah will recover.  Then Jaya asks if there's anything wrong with her, because The Security Triumvirate asked if she was retarded.  Dr. Gerhauser doesn't seem to know what to do with that question.  Jaya then asks for more pills.  Dr. Gerhauser asks what Jaya did with the pills she gave her.  Jaya claims they weren't working.  In a flash of inspiration, she says that the old pills were probably why she wasn't operating at peak efficiency and why she seemed retarded at the cross examination.  Dr. Gerhauser does not appear to be buying Jaya's story.  Jaya then moves to threatening and ordering Dr. Gerhauser to give her pills.  \hl{Dr. Gerhauser says, ``No.''}\footnote{\textbf{Rebecca S. }There was something following this where Gerhauser was, like, ``See me after your shore leave'' and Jaya chose to interpreted that to mean she'd get more pills when she came back... \textsubscript{10/23/12 12:44am}}\footnote{$\rightarrow$\textbf{Suko T }Jaya, the ever hopeful junkie... :) \textsubscript{10/23/12 3:52pm}}



Hayley is exercising at the ready line when she notices Lackovich watching her.  She greets her in a friendly manner, but doesn't quite remember who Lackovich is.  Lackovich asks how long Hayley has been here, to which Hayley replies ``a few months I think.''  Lackovich asks if she likes it here, and Hayley nods cheerfully.  Hayley asks if Lackovich is a part of Patrol Group 2, and then thanks her for saving them.  Lackovich realizes that Hayley works for ``that fucking bitch in Patrol Group 1''.  She mentions how all of her team died due to Hayley and the rest of Patrol Group 1.  Hayley finally realizes just who Lackovich is and tries to give her condolences for the death of Lackovich's teammates.  Infuriated, Lackovich slaps Hayley.  Hayley accepts the slap and stays very still and tense for a second, as if braced for further abuse.  When none follows, she relaxes and looks back at Lackovich and says earnestly, ``I really am very sorry.''  \hl{Lackovich pretty much loses her shit at this point and starts screaming at Hayley that she is so very very fucked.}\footnote{\textbf{q.google }We call \_this\_ Professional Decorum. \textsubscript{10/23/12 1:55pm}}\footnote{$\rightarrow$\textbf{Suko T }Clearly the members of Morgan's teams are chosen for their mental stability and social graces. \textsubscript{10/23/12 3:50pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }+1 \textsubscript{10/24/12}}  Concerned, Hayley reaches out to Lackovich with a placating gesture, asking if she is okay and if she needs a doctor.  Lackovich hisses at Hayley to stay the hell away away from her.   Hayley agrees and backs away and Lackovich storms off.



{[}this part I would like to add- didn't have time to play it out/describe it as we had to run out the door{]}

Hayley returns to her physical therapy but her rhythm is off, and she ends sooner than normal.  She goes back to their bunks, avoiding meeting or speaking to anyone to as much as she can.  She goes into the bathroom, looks at the reddening mark on her face, turns on the shower, curls up on the floor of the shower and cries.  Unlike the sobbing she has done before when overcome with pain or fear, this one is nearly silent.  When she eventually emerges, she looks utterly exhausted but calm, and her damp hair is carefully combed to fall over her cheeks, hiding the \hl{fading mark}\footnote{\textbf{Suko T }I'm assuming the slap was not one that will leave a lasting bruise \textsubscript{10/21/12 3:42am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }No. It was solid; solid enough that Hayley would know that Lackovich isn't a wilting lily. But not so bad as to leave a lasting mark. It was a slap not a blow to the face. \textsubscript{10/23/12 12:03pm}}\footnote{$\rightarrow$\textbf{Suko T }Figured as much, that works for me. \textsubscript{10/23/12 3:51pm}}.  It's fairly unlikely anyone will notice it that night unless they are paying her particular attention (thank goodness Mr. Vigilant is in MedBay).  She goes straight to bed to avoid talking to anyone.



\underline{  {\LARGE Challenges \& Refreshes }  }



\begin{itemize}
\item Gerhauser Sisters. \textit{Hardened: 2} (Oliver), \textit{Anti-Authoritarian: 1} (Oliver)  Ongoing challenge
\item Gerhauser Sisters. \textit{Outgoing: 1} (Oliver)  Ongoing challenge
\end{itemize}



\underline{  {\LARGE Quotes }  }



``Agent Sir Ma'am, I'm mostly recovered, but some more pills would help.  Oh, uh. Have you seen my team?''

\extraIndent{- Jaya}


\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Nathaniel Ford} @ 05/07/15 4:28pm}
% Exported @ 08/22/15 4:13pm
\end{flushright}

