\setcounter{chapter}{ 8 }
\chapter{\textbf{SAC-09, Interlude} }


\subChapterTitle{``20 Questions''}

\deets{Suko and Ion}{November 1st, 2012}



More talky talky. Jonah woke up and got caught up. Oliver has woman troubles and gets taunted by his Arch Nemesis.  Hayley figures out how to get around a direct order. \footnote{\textbf{Suko T }This would be an actual summary. :) \textsubscript{11/02/12 11:05pm}}



Also: Redid cistern scene between Hayley and Oliver.  That is updated in the Session 8 notes.  Adam, if you would like to add Oliver's perspective, please do.



Next session: THE TANK.  Yay!!!!!



As always, please fill in the gaps and correct errors.  Also you should always feel free to add/correct the perspective of your character.



\noindent\hrulefill



\underline{  {\LARGE Trait Purchases }  }



Oliver: Hardened 2 ‚Üí 3, Focus 1 ‚Üí 2, buy down Obsession from 1 ‚Üí 0

Jonah: Small Unit Tactics 0 ‚Üí 2

Hayley: Rifle 0 ‚Üí 1 (may also be buying down a Flaw)



VP expenditures on Character spreadsheet. We have communal points to spend!  Suggestions were for body armor. And lasers. :D

\noindent\hrulefill





 {\LARGE SAC-09 } 



After we return from Terminus, 3-4 days pass without incident.  Then Jaya is called to the Ops room and disappears.  A week Four days later\footnote{\textbf{Suko T }Had to amend this to make the timeline work for later events.  I made it so it was ``a week from the return from Terminus but only 4 days from Jaya's disappearance. \textsubscript{11/28/12 2:33am}}, she is still gone.  \hl{Patrol Group 2 is also gone for most of this time.}\footnote{\textbf{Suko T }My speculation is that Jaya is in her personal hell of being part of Patrol Group 2 (under Lackovich) on some mission. :D \textsubscript{11/02/12 4:24pm}}\footnote{$\rightarrow$\textbf{Rebecca S. }Odds are she got in a fight with Lackovich on her way to the the Ops room and shived the bitch... \textsubscript{11/06/12 2:25pm}}+1\footnote{$\rightarrow$\textbf{q.google }Pretty close it turns out, yeah?

(Jonah thought she was in the Tank.  The fact that it's been so long only reinforced that suspicion.) \textsubscript{11/28/12 11:59am}}



Oliver and Hayley spend most of the time in physical therapy and being bored.  Hayley actually learns to use a Rifle for reals.  Hayley rejoins Oliver a few times swimming and seems intent on conquering her nascent fear of drowning, often staying submerged so long Oliver gets worried.



Each day Hayley asks after Jonah, and one day in the cafeteria, Jari tells Oliver and Hayley that Jonah has been out of the coma for a few days but they have been keeping him asleep for a while.  Oliver asks Jari to see if they can see Jonah, but Jari is unable to help them.  Oliver searches for another way in and tracks down Micah, the guard that usually escorts them around the base.



Oliver deliberately lets Hayley take the lead, and she asks to see Dr. Gerhauser please.  Micah says he will ask.



Meanwhile, Jonah slowly awakens to find he is in a medbay room.  He is fairly certain he is not in SAC-01 but it is hard to be 100\% certain.  It seems possible he is in SAC-09.  He is surrounded by lots of fancy medtec.  He can see he has some IVs and also discovers he has a catheter.



Dr. Gerhauser walks in and asks how Jonah is feeling.  He says he is confused, and she assures him that this will pass.  She asks him some basic questions, and tests his pupil response and eye tracking.  She seems satisfied by what she sees.



Jonah asks what happened.  Dr. Gerhauser explains that the end of our mission appears to have gone south.  Patrol Group 2 pulled us out of the drink.  We managed to keep the wounded woman alive, but we were in bad shape.  Constable Langdon died but was revived.  She adds, ``I'm sure that's one he won't let Morgan forget.''  She says that we retrieved the slides and some frozen samples. She confirms that the mission was a success, even though we were found near death. ``Yes, my sister was quite pleased.''  says Dr. Gerhauser, and then amends with ``... less with the near death portion'' when Jonah gives her a look.



While waiting for Micah to pass the message along to Dr. Gerhauser, Hayley and Oliver go swimming again.  When they return to their bunks, Dr. Gerhauser shows up and says she will escort the two of them to see Jonah.



``How are you, Kate?'' asks Oliver,  Dr. Gerhauser casts a glance over at Hayley, who is walking a pace or two behind them, before replying, ``Busy, and you?''  They chat for a bit and Dr. Gerhauser says that if Oliver came for a checkup the next day, she can probably clear him for leave.  ``But Morgan won't let you go for long.''  \hl{Oliver raises an eyebrow at this and looks annoyed}\footnote{\textbf{Adam Kenney }(because he asked for more/longer shore leave in return for signing the national security clearance agreement) \textsubscript{11/08/12 12:20pm}}.



Once they are in the elevator, Oliver asks Hayley, ``How are you doing?''

``Good,'' replies Hayley, a little confused.  \hl{``I've been learning to swim....but you know that already.''}\footnote{\textbf{Suko T }I could not resist stirring up a little trouble. :D \textsubscript{11/04/12 1:38am}}\footnote{$\rightarrow$\textbf{Adam Kenney }OMG. \textsubscript{11/08/12 12:20pm}}

Dr. Gerhauser asks Hayley, ``Have you been swimming a lot?''

``Maybe five or six times, is that a lot?  He's been teaching me to swim.  He's a good teacher,'' says Hayley cheerfully.

``Oh really?'' drawls Dr. Gerhauser, giving Oliver a very Pointed Look.

``Ah, I thought that it would help...uh...I didn't think it would be a problem...that you wouldn't mind....'' Oliver flounders.

Awkward silence for the rest of the elevator ride to MedBay.



They reach Jonah's room.  With a chilly professional demeanor Dr. Gerhauser shows them how to scrub up to see the patient.  She says that Micah will come back to escort them back to their rooms when their time is up and she leaves.  Jonah can see Oliver watching Dr. Gerhauser, a series of emotions passing over his face.



Oliver walks into the area where Jonah is.  Hayley lags behind, shyly peeking into the room, waiting until Oliver starts talking to Jonah to enter.  She interrupts Oliver to say hi to Jonah, her body language uncharacteristically fidgety and a huge smile on her face.  Neither of them have seen her ever look so happy before, and her eyes are shimmering with unshed tears.  Oliver does most of the talking but Hayley interjects a few times, interrupting Oliver mid sentence several times and not apologizing for it.  Mostly her attention is fixed on Jonah, watching his face like if she blinked it might disappear.



Oliver gives Jonah a quick update on what happened, the Security Triumvirate, Morgan's instructions regarding leaving some information out of the official report, Patrol Group 2, Lackovich, Trenton saving our lives using the radios and something called ``triangulation'', and what little we have learned about what happened to us.  Oliver sums up the information issues by saying ``A general guideline is don't talk about stuff unless you have to.''  Jonah is told that we are not supposed to mention the guards we ran into in SAC-01, its location or its defenses.  Also if we agree to the Directorate Security Act we will get more access to SAC-09. 



Micah indicates that their time is up and Oliver and Hayley leave.  Jonah, exhausted by the massive info-dump, falls asleep soon after.



The next day, Oliver goes to his check-up appointment with Dr. Gerhauser.  The MedBay room has a chair next to a table with some fat cylinders on it.  Dr. Gerhauser nods for Oliver to take a seat in the chair.

``How are you feeling today?''

``Pretty well considering I died and came back. Do you know, I don't think I ever thanked you for that.'' says Oliver.

``No.''  Dr. Gerhauser says shortly, and then adds, ``You're welcome.''



Dr. Gerhauser then confirms that Oliver signed off of the testing.  While going over the forms, she asks him if Hayley will be accompanying him on his Leave.  Oliver swiftly says no, and asks why she thought that.  Dr. Gerhauser makes some weak explanation about Oliver being the senior officer in the Patrol Group now and...and.... let's just get started, shall we?



She places a monitoring device on Oliver's head and starts asking him some questions to establish a baseline, starting with his name, age and Mother's name (Evelyn Langdon).

``Did you ever keep a pet?'' asks Dr. Gerhauser

``Yes, a cat named Grey, I wasn't very creative.''

``Where were you when you suffered your injury?''

``DX station.''

``How do you feel about Hayley?''

``She's a nice girl.  I feel sorry for her.  She's had a hard life.\footnote{\textbf{Suko T }or something like this.  Sorry I was snickering too hard at the question and I missed it. \textsubscript{11/03/12 12:02am}}\footnote{$\rightarrow$\textbf{Adam Kenney }It was more like, ``She's nice, but pretty messed up.'' \textsubscript{11/08/12 12:22pm}}, but pretty messed up.``  Oliver looks over at Dr. Gerhauser and \hl{she's smirking a little}\footnote{\textbf{q.google }To be fair, Hayley is \_particularly\_ messed up. \textsubscript{11/28/12 12:31pm}}.

``What is your biggest dream?''

\hl{``To do something that matters.''}\footnote{\textbf{Suko T }Did I hear this right?  'cause that's what my notes say but my brain is like, what?? \textsubscript{11/03/12 12:07am}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }I'm pretty sure it wasn't that. More like, ``To do something that makes a difference'' \textsubscript{11/05/12 10:30am}}\footnote{$\rightarrow$\textbf{Rebecca S. }I like the ``evil'' response better- you should just retcon that in :) \textsubscript{11/06/12 2:29pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }changed to ``that matters'' - sorry guys! \textsubscript{11/08/12 12:23pm}}

``How do you calculate the area of a triangle?''

``Isn't it something like half the height times the width?''

``How many pieces in your sniper rifle?''

``57,'' replies Oliver instantly, and then adds, ``but really it's part of 5 modules.''

``And how do they fit together?''

``It would be easier for me to show you but...'' and Oliver describes the process as best he can.

``Do you trust Agent Morgan?''

``About as far as I can throw her.''

``Have you had sex recently?''

``No.''

``Do you suffer from headaches?''

``No.  Say, can I ask you questions?''

``I suppose.  Depends on the question.''

``How do you feel about me?'' asks Oliver.

``It's complicated.''

``Can I change my answer?''

``Which answer?''

``Morgan.  It's complicated.''

``Ah.''

\hl{``So why complicated?''}\footnote{\textbf{Suko T }Just guessing at the question asked, I don't have it in my notes. \textsubscript{11/03/12 12:23am}} asks Oliver.

\hl{``I think you're liable to get yourself killed.''}\footnote{\textbf{q.google }This isn't a problem restricted to Oliver.  Although presumably Dr. G doesn't have as complicated emotions about the rest of us.

(Also, to be fair to us and even more to Oliver, one of the main reasons he may get himself killed is being sent on dangerous missions.  This isn't to criticize the SAC command for sending the team on them, but it really does go with the territory if you are paramilitary.) \textsubscript{11/28/12 12:42pm}}

``I agree, I'm trying to do something that matters, and I only have one thing to give.''

``That is where I disagree with you.'' says Dr. Gerhauser.



Dr. Gerhauser tells Oliver that she's established enough of a baseline.  She warns that the next part will sting.  She injects the contents of the fat cylinder into his carotid artery. It does hurt but Oliver doesn't flinch.  ``Do I get more apple pie?'' he asks teasingly.

``Don't talk.  Sorry, it's just that there's a needle under your jaw.''

Procedure complete, Oliver leaves Medbay.  Later, Tiburon stops by to tell him that he has been approved for a 48 hour Leave pass.  Hayley asks if it would be possible to visit Signe, and to her surprise Tiburon says it would be fine and she can have a 48 hour pass as well.  There is a train leaving soon, so both of them start packing.



Jonah enters as they are packing.  Oliver gives him a few more updates and hands him \sout{the letter from the Orc of Anglia} \hl{a sealed envelope, telling him to give it to Jaya if he (Oliver) doesn't come back}\footnote{\textbf{Adam Kenney }(correction) \textsubscript{11/08/12 12:25pm}}\footnote{$\rightarrow$\textbf{Suko T }Oh right!  my notes just said ``letter'' and that's the only letter I remembered. \textsubscript{11/08/12 2:53pm}}.  \hl{Hayley offers Jonah a copy of the ``official'' report that Oliver prepared}\footnote{\textbf{q.google }While I'm still fuzzy on details, we should assume that Jonah memorizes it also. \textsubscript{11/28/12 12:47pm}} (the one that she and Jaya memorized before their cross examination - the one that leaves out the woman and the SAC-01 location).



\hl{Hayley then asks if she can call in that favor that Jonah owes her.  She asks him to watch over Mr. Hadef (Trenton) and to help him if he can.  She hopes it won't be a big problem because he was already going to talk to Trenton about triangulation anyway.  Jonah agrees and Hayley looks very relieved and happy.  Oliver adds (to Jonah), ``and don't fall in love with him.''}\footnote{\textbf{Suko T }Re-reading these summaries, this passage made me LOL considering the bromance. \textsubscript{06/19/15 4:28pm}}



Oliver and Hayley leave.  



Jonah goes to meet with Dr. Gerhauser the next day. She asks him if he read the book. He asks about the slides.  She says that they have run into a bit of an encoding issue, but that we appear to have grabbed the right slides. Trenton was surprised.



Dr. Gerhauser gives more details about what they can reconstruct happened to us.  Apparently we made it out of the facility under our own power, with the prisoner in tow.  It wasn't easy and we all got rather banged up and bruised.  Oliver appears to have sustained a blow to the head at some point.  Jaya got us mostly out when Patrol Group 2 found us.  Apparently there was a burst of radiation that knocked out our radios for a while and then a massive underground explosion. The explosion appears to have broken some dams that were holding back water and the area flooded.



The woman prisoner is a little strange, and when Jonah asks about the strange language she spoke, Dr. Gerhauser says that the woman was ``from far away.''



Jonah asks if SAC-01 was a variation of SAC-09, and Dr. Gerhauser says that i\hl{t seems more likely that it is the other way around}\footnote{\textbf{q.google }Jonah assumes that she is dodging the question and doesn't press the point. \textsubscript{11/28/12 12:58pm}}.



Jonah asks about the amnesia... why do we all only remember back to a certain point?  She says that the revival drugs have a retroactive memory effect that is a certain length of time (so the amnesia is not event-specific).



Dr. Gerhauser and Jonah talk more about the book she loaned him and he uses that opening to capture her interest and make \hl{her feel like he is a colleague}\footnote{\textbf{q.google }Or at least worth talking to further. \textsubscript{11/28/12 1:05pm}}. {[}\textit{Ongoing Challenge: The Gerhauser Sisters}: Social Chameleon 3{]} 



Dr. Gerhauser mentions that Jaya indicated that Jonah would take part in the testing.  Jonah said he had some concerns about the effects these ``tests''.

``Which effect are you concerned with?''

``The drowning,'' says Jonah referring to Hayley's experience that it felt like drowning.

Dr. Gerhauser assures him that she doesn't believe it will harm him.  ``This will not be harmful to you as a person.  Not at this stage anyway.''

She mentions that Hayley's experience was in part due to her mind already being somewhat pre-conditioned for the tests.  Dr. Gerhauser would like to start testing the rest of the team soon as they have further to go.



 {\LARGE Shore Leave } 


\jumpHeadline{Shore Leave: Hayley, part 1 }

Hayley goes to visit Signe in the Warehouse district, dressed in her bodyguard uniform (a well tailored, high quality dark colored suit).  It is dusk when she arrives at the Warehouse Station.  Not being used to going anywhere by herself, she has to ask Tiburon a lot of last minute questions, such as Signe's address and how Hayley might get from this place to where Gillian lives. 



Address in hand, Hayley heads into the Warehouse district and promptly gets lost.  The buildings in the area are brick, and many are boarded up.  Hayley asks a young teenage girl for directions but when the girl asks what's in it for her, Hayley doesn't even understand the question.  Undeterred, Hayley asks the next person, a young man, Tim, for help.  He is much more receptive and helps her find Signe's address while flirting with her.  He asks if she is looking for the Mad Monk or the Emperor-Monk, a crazy guy who lives there.  Hayley doesn't know who he's talking about or what an Emperor is and says no.  Tim gives her his address and she agrees to stop by some other time for a drink, even though she can't actually drink alcohol and can't tell him where she's from.  She thanks him for his help and goes to Signe's place.



Hayley knocks and Signe opens the door, surprised to see Hayley.  Hayley explains that she didn't think she'd be allowed to visit but she was, so here she is.  Signe asks about Trenton, and Hayley explains that she can't talk to Mr. Hadef and has orders to be rude to him, so she doesn't know how he is doing.  Signe is kind of appalled to hear this.  Hayley promises to find out if he is okay, probably by asking Jonah.  Signe offers Hayley food or drink...or a massage.  Hayley politely declines all three, but offers Signe a massage if she wants one.



Signe asks what life is like where Hayley lives.  ``Boring, but I'm used to that.''  Signe says that she's not used to it.  Hayley tells Signe that Mr. Hadef saved their lives, and asks if Signe knows who doesn't like Mr. Hadef. Other than Senior Constable Jaya, that is.  Signe can't be more specific than ``a lot of people.''  Hayley asks if she knows more about what she mentioned in her letter- something that is causing problems for Mr. Hadef.  But Signe doesn't know anything more.



Signe asks if Hayley (meaning SAC-09) is near the Annex.  Hayley doesn't know.  Signe tells her that the Annex is dangerous, there are riots and people disappearing.  Hayley thanks her for the information.



Signe offers a place to stay for the night, and Hayley is delighted to accept.  Signe says that it would just be sharing her bed, but Hayley has no problems with that.  Apparently not all of Trenton's family is there and ``one of them left.''  Signe doesn't know why.  Signe apologizes for the level of accommodations (less than what she had before) she has to offer.



Hayley assures her that they are fine, and the neighbors seem nice.  Hayley tells Signe about the nice man Tim, who helped her find this place.  She shows Signe Tim's address and mentions that she is supposed to meet him at some point for drinks.  Perhaps the next time she visits Signe..?



Hayley thanks her for the letter, mentioning that it is the first letter she ever received.  Signe says Trenton thought it would be helpful for her to write the letter.  Hayley asks if they can continue to write to each other.  Signe agrees but grows pale and excuses herself to go vomit in the other room.  When she returns, Hayley asks her if she is feeling well, and Signe says yes.  Hayley doesn't press her further.  Hayley introduces Signe to ``this new game I just learned, 20 Questions'' and they play that through the night.  When they grow tired, Signe leads her to a bedroom with a large queen bed in the middle and a small bed tucked into an alcove.  Signe indicates that the small bed is her bed and they lie down there and go to sleep.  It does not even occur to Hayley to ask about using the other, much larger bed in the room.


\jumpHeadline{Shore Leave: Oliver }

Oliver arrives in Cardoza, carrying his gun (in a nondescript backpack) but wearing civvies.  He scouts around to get the lay of the land and sticks to the shadows and tries to avoid running into people he knows.  If its unavoidable, he ends the conversation quickly and stays as vague as possible.  



He notices that there are many more TA patrols than usual, and these are full squads of 3-4 people, instead of the usual single patrol cop.  The TA groups are not acting super vigiliant however, but they do pass through in regular intervals.  The streets are more clear and subdued than usual, but there are still parties and various events.



Oliver observes his parents house, noting that lights are on but it seems more subdued than normal.  He wanders around some more, making sure to pass by his parents house several more times.  He goes to rent a room in a nondescript anonymous motel for the night.



In the morning, he changes into his TA uniform and heads to his parents house.  The butler, Jeffries, opens the door and Oliver says that he has a job in the neighborhood and thought he would stop by briefly.  Jeffries directs him to the breakfast room, where he finds his father dining alone (which is somewhat unusual).  Mr. Langdon greets Oliver and Oliver reiterates his story about stopping by because he was in the area for work.  Oliver learns that his mother has gone to stay with her sister.



Mr. Langdon asks if Oliver has heard about the incident (in Cardoza).  Oliver is vague and says that he had heard something about it.  Oliver asks about his father's business and is told that it is going poorly.  ``They decided I had something to do with that incident. Magnin and I shared some investments.''



When Mr. Langdon says that he doesn't trust Oliver to give him a straight answer, Oliver says that he can ask any question and Oliver will try to answer it if he can.  Mr. Langdon asks, ``When did you start lying to me?'' and reminds Oliver that he had spent some of his funds in Cardoza, so Mr. Langdon knows that Oliver was there during ``The Incident'' and didn't just ``hear something about it.''



When Oliver says that he thought that his income was a discretionary allowance, Mr. Langdon counters with ``Discretionary allowances are supposed to be used \textit{with discretion}.'' and mentions that questions about such spending has caused him more problems.



\hl{The conversation pretty much dies at this point}\footnote{\textbf{q.google }That was kind of sad.  They had begun to actually say some hard things without running away. \textsubscript{11/28/12 1:11pm}}\footnote{$\rightarrow$\textbf{Adam Kenney }Their relationship is always at an impasse - Oliver bristles at his father's disapproval, his father despises Oliver for his failures (real and perceived).

The only things I could think of off the top of my head that would fundamentally change this dynamic would be if Oliver's father fell into such dire straights that he actually needed Oliver's help (though he still might not ask for it); or if Oliver tried to ``prove himself'' yet again and actually succeeded in some way that was meaningful/very useful to his father. \textsubscript{11/28/12 2:12pm}}\footnote{$\rightarrow$\textbf{q.google }Oh I don't expect it to change easily.  It just came a lot closer to the (possibly surprising) point of mutual perspective than it has before.  What Oliver is doing might actually be something his father could be proud of.  Of course, poetic tragedy, he's not allowed to share it -- yet  his father already knows something is being kept from him, and even may know there's a good reason for it.  This is not at all the same as Oliver just not wanting to share. They actually \_could\_ talk about that -- but they are so used to not doing so they don't see it. \textsubscript{11/30/12 1:22pm}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/30/12 3:55pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{05/27/14 12:03am}} and Oliver is excused with a ``Sorry your mother is not here to greet you and sorry you can't stay.''



Oliver leaves his father but finds Jeffries.  He asks him about the letter and who delivered it.  Jeffries says that one of the maids received it and Oliver goes to speak with her.  She said that it was left in the post box, the one in the foyer.  She thinks that the courier that Mr. Langdon usually uses, brought it by.


\jumpHeadline{Shore Leave: Hayley, part 2 }

Signe brings Hayley breakfast (gel pack) in bed.  Hayley says that she slept well but overslept because she isn't used to the light here.  Hayley can't stay but is happy that she could come to visit.  Signe says she is glad she came too.  



Hayley says that it is a shame that Signe can't join Mr. Hadef at work and help him.  Signe looks very excited and asks if that is possible.  Hayley promises to ask, saying that since Signe already knows about his work, it seems like she would be helpful to him.  



Hayley asks if she can come visit again and Signe says yes.  Signe gives Hayley directions to the train station (she knows the route well because she goes every day to see if Trenton is there or if he sent something that day).  



Hayley leaves and heads home to Gillian's house.  Gillian practically meets Hayley at the door.  She says she is glad to see Hayley but her demeanor/vibe is a little ``off''.  Hayley asks about the man that they went to see last time and Gillian brushes it off with a ``let's not talk about that.''  She takes Hayley to a more private room and they sit down to talk.  Gillian asks about the Senate Testimony.  Hayley proudly says that she told them what she was told to say.  Gillian asks if they asked about her businesses, and Hayley says no.  ``They tried to ask more questions but gave up because I am stupid.''  Gillian shoots her a sharp look and says, ``you're not \textit{that }stupid.'' ``Well, no but because I couldn't answer anything, I sounded even stupider,'' explains Hayley.



Gillian says that she is beginning to find out who is trying to destroy her.  She and Agent Gerhauser have come to an arrangement.  She stresses that Hayley is to follow Agent Gerhauser's orders because they are working together.  Gillian says with some regret that she wishes she had met Agent Gerhauser earlier.



Hayley mentions that she went to visit Signe.  Gillian seems happy that Hayley has a friend, but cautions her not to get distracted by things like that and keep a clear head.  Gillian may need to act soon and Hayley has to be ready to help her.  



Gillian says that she is going to be moving to be nearer to Terminus.  Hayley warns her about the riots and kidnapping in the Annex but Gillian brushes most of that off as the hysterics of common folk.  Gillian says that Anglia agreed to help, and Hayley asks if Anglia are friends.  Gillian says no.  They are allies but they can't be trusted.  Hayley mentions that she has met someone from Anglia, a beautiful woman named Octavia.  Gillian seems to know who she is talking about.



Gillian says that she is about to leave for Terminus and Hayley helps her get ready.  Gillian stresses that Hayley can trust Agent Gerhauser.  Hayley mentions Signe again and Gillian asks if she would be a good employee.  Hayley says that Signe is already attached to someone but Gillian waves away that small concern.  Hayley seems at a loss for what to do and changes the topic to asking about the equations that Hayley reported several weeks ago.  Gillian hands her some sheets of notes but says that they were mostly nonsense.  Hayley asks, ``Should I learn math?  It kept us from dying.''  Gillian replies, ``Every accountant I've ever heard of would agree with you.''



Hayley then mentions learning to swim and that Constable Langdon, Oliver, is teaching her.  Gillian is intrigued by the fact that this Constable Langdon is Citizen Langdon's son.  Even though she already knew the names from Hayley's earlier reports, she had not put that together before. ``Hmm, many people will be very interested in talking to him.''



 {\LARGE SAC-09 } 


\jumpHeadline{Jonah and Trenton }

Jonah goes to meet with Trenton.  He heads down to Trenton's lab.  The place is empty and Trenton walks in with a bottle in hand.  Jonah thanks Trenton for finding us and asks if he found out what he wanted to know from the slides.  Trenton says that while the facilities here are wondrous, they leave something to be desired.  Jonah, looking around at tech that is already far beyond his experience, wonders what else one could want.



Trenton pours the wine, just standard street swill, but Jonah is used to it.  Jonah asks what Trenton heard through the radios, since he wasn't subject to the amnesia drugs.  Trenton says he heard Jaya say something about someone ``pulled the pin'' and then there was a lot of seismic activity. Probably the explosion underground shaking the area above it.  A radiation pulse scrambled the radios.



Jonah asks Trenton to teach him triangulation. Trenton pulls out some ... smokes ... of a rather rare variety, and they both light up.  Trenton starts talking about radiation, light and then starts drawing \hl{diagrams.}\footnote{\textbf{Suko T }which was VERY funny.  Not hard to tell who was Hayley and who was Jaya, even if they were stick figures... \textsubscript{11/04/12 1:19am}}



Trenton asks why Jonah wants to know this when he has no background in it and Jonah says that he likes to know things that save his life.  Jonah then mentions that Hayley asked Jonah to help Trenton.  This seems to please Trenton.  ``Help is better when they are good to look at, don't you agree?  Gets the juices going.''  Jonah agrees amiably but without commenting on particular individuals.



Trenton then spends considerable time trying to explain ``triangulation'' and the math behind it, using the analogy of people walking away from a common point and time taken to travel.  Jonah appears to understand the gist, but whether he gets the specifics is unclear.  The process is complicated by the fact that Trenton is not really able to keep things simple, but even more so from the effect of the ``smokes'' which are making both men rather ... mellow.  It's unclear how long the conversation lasts or whether anyone really learns anything though to all appearances both of them appear delighted.  Jonah does learn that Trenton grew up in the Academy, which \hl{begins to explain some of Trenton's behavior}\footnote{\textbf{q.google }I imagine Trenton to be a lot like Zane from Eureka:

http://eureka.wikia.com/wiki/Zane\_Donovan \textsubscript{11/28/12 2:20pm}}.



 {\LARGE Shore Leave } 


\jumpHeadline{Shore Leave: Oliver, part 2 }

Oliver tracks down the courier and makes it clear that he is not here on his father's business and that this needs to be discreet.  The courier remembers the letter because it was weird. It was actually sent straight to the courier office, and then inside that envelope was the letter to Oliver, with instructions on delivery.  Since the bill of receipt was good, they went ahead and delivered it.



Oliver gets the receipt number and tracks it back to Transit Minor.   He is attempting to leave a reply somewhere.  Oliver talks to the postal service at Transit Minor, saying that the letter arrived but had no return address.  While the clerk looks for the information, Oliver gets paranoid and looks for snipers.  He is beginning to think he's being silly but then sees a familiar face (Lackovich) walking out of the station.  Before he can follow her, the clerk interrupts with a letter, saying ``It's the weirdest thing.''  The letter was to be handed to whomever inquires after the original letter.  They don't know who did it, but the clerk who received it is not present.



Oliver tries to follow Lackovich but feels too exposed to search outside.  He gets on a train and in plain sight, reads the letter.



``Mr. Langdon, if you are reading this, I commend you on your thoroughness.  But don't worry.  \textit{You} don't need to find \textit{me}.''



\underline{  {\LARGE Challenges \& Refreshes }  }



\begin{itemize}
\item Gerhauser Sisters. \textit{Social Chameleon: 3} (Jonah) ‚Üí Ongoing challenge
\end{itemize}



\underline{  {\LARGE Quotes }  }



``Yes, my sister was quite pleased... though less with the near death portion.''

\extraIndent{Äù- Dr. Gerhauser to Jonah.}


\quotedDialog{
``Do I get more apple pie?''

``Don't talk.  Sorry, it's just that there's a needle under your jaw.''
}
\extraIndent{Äù                - Oliver and Dr. Gerhauser}


\quotedDialog{
``Which effect are you concerned with?''

``The drowning.''
}
\extraIndent{Äù                - Dr. Gerhauser and Jonah}



``This will not be harmful to you as a person.  Not at this stage anyway.''

\extraIndent{Äù- Dr. Gerhauser to Jonah}



``Discretionary allowances are supposed to be used \textit{with discretion}.''

\extraIndent{Äù- Mr. Langdon to Oliver}


\hl{
``It's a little strange around here with the light and everything.''}

\extraIndent{Äù\hl{- Hayley}\footnote{\textbf{Adam Kenney }Hahaha, I didn't catch this at the time! \textsubscript{11/08/12 12:32pm}}}


\quotedDialog{
``Should I learn math?  It kept us from dying.''

``Every accountant I've ever heard of would agree with you.''
}
\extraIndent{Äù- Hayley and Gillian}


\iffalse

======================
THESE ARE ERRORS ENCOUNTERED DURING THE EXPORT PROCESS
======================

	Unable to highlight for footnote: This would be an actual summary. :) because:GivenExpectedore talky talky. Jonah woke up and got caught up. Oliver has woman troubles and gets taunted by his Arch Nemesis.  Hayley figures out how to get around a direct order.More talky talky.

	Unable to highlight for footnote: Had to amend this to make the timeline work for later events.  I made it so it was "a week from the return from Terminus but only 4 days from Jaya's disappearance., unable to correctly match (exceeded acceptable limit):ExpectedA week Four days later

	Unable to understand footnote +1, too many options & none that matched \footnote{$\rightarrow$\textbf{Rebecca S. }Odds are she got in a fight with Lackovich on her way to the the Ops room and shived the bitch... \textsubscript{11/06/12 2:25pm}}. Optional comment markups: \footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/30/12 3:55pm}}\footnote{$\rightarrow$\textbf{Nathaniel Ford }+1 \textsubscript{05/27/14 12:03am}}\footnote{$\rightarrow$\textbf{Suko T }+1 \textsubscript{11/06/12 3:11pm}} 

	Unable to highlight for footnote: or something like this.  Sorry I was snickering too hard at the question and I missed it., unable to correctly match (exceeded acceptable limit):ExpectedI feel sorry for her.  S

	Unable to highlight for footnote: Did I hear this right?  'cause that's what my notes say but my brain is like, what?? because:GivenExpected‚ÄúTo do something that matters.‚Äù‚ÄúTo do something evil.‚Äù


\fi

\vspace{\fill}

\begin{flushright}
\textsubscript{last edited by \textbf{Suko T} @ 06/19/15 4:28pm}
% Exported @ 08/22/15 4:29pm
\end{flushright}

